### 2015-05-04 doc/201504_vnlbayes_params/slides_vnlb_prms.tex
Adds project documentation to repo

% \documentclass{beamer}
\documentclass[mathserif, 8pt]{beamer}

\mode<presentation> {
% \usetheme{Madrid}
%\usetheme{default}
\usetheme{Boadilla}
% \usecolortheme{beaver}
% \usecolortheme{rose}
}
% removes navigation symbols
\setbeamertemplate{navigation symbols}{}

\usepackage[english,activeacute]{babel}
\usepackage[english]{layout}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{pgf}
%\usepackage{movie15}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage[multidot]{grffile}
\usepackage{ucs}
% \usepackage[T1]{fontenc}
%\usepackage{subfigure}

% from rida's preamble
\usepackage{epsfig,xspace}
\usepackage{setspace}
\usepackage{threeparttable}
\usepackage{subfloat}
\usepackage{pstricks,pst-node}
\usepackage[normal,tight,center]{subfigure}
\usepackage{pifont}
\usepackage{multimedia}
%\usepackage{media9}
%\usepackage{enumitem}
\usepackage{animate}
\usepackage{caption}
\usepackage{multirow}

% the following is used to bind frames with the same frame number
\usepackage{etoolbox}

\newcounter{multipleslide}

\makeatletter%
\newcommand{\multipleframe}{%
\setcounter{multipleslide}{\value{framenumber}}
\stepcounter{multipleslide}
\patchcmd{\beamer@@tmpl@footline}% <cmd>
	{\insertframenumber}% <search>
	{\themultipleslide}% <replace>
	{}% <success>
	{}% <failure>
}
\newcommand{\restoreframe}{%
\patchcmd{\beamer@@tmpl@footline}% <cmd>
	{\themultipleslide}% <search>
	{\insertframenumber}% <replace>
	{}% <success>
	{}% <failure>
\setcounter{framenumber}{\value{multipleslide}}%
}
\makeatother%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Running 'pdflatex --shell-escape...' will automatically recognize
% the eps files in the includegraphics and convert them to pdf.
% No file rename nor change to the document is needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{ifpdf}
\ifpdf
\DeclareGraphicsRule{.eps}{pdf}{.pdf}{`epstopdf #1}
\usepackage{epstopdf}
\epstopdfsetup{suffix=-\SourceExt-converted-to}
\pdfcompresslevel=0   %\pdfcompresslevel=9
\pdfcompresslevel0
\fi

% para poder incluir figuras .pdftex del xfig
\DeclareGraphicsRule{.pdftex}{pdf}{.pdftex}{}

\newcommand{\nada}[1]   {}

\newcommand{\best}[1]{\textbf{\textcolor{MyOrange}{#1}}}

\newcommand{\ma}[1]{\boldsymbol{#1}}
\newcommand{\ie}{\textit{i.e.} }
\newcommand{\eg}{\textit{e.g.} }
\newcommand{\etal}{\textit{et al}. }
\newcommand{\tras}[1]{#1^{\mathrm{T}}}
\newcommand{\herm}[1]{#1^{\mathrm{H}}}
\newcommand{\con}[1]{#1^{\mathrm{*}}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\tech}[1]{\overline{#1}}
\newcommand{\nspace}{\!\!\!\!}
\newcommand{\nmbr}[1]{\oldstylenums{#1}}

\newcommand{\eps}{\varepsilon}
\newcommand{\R}{{\mathbb R}}
\newcommand{\Q}{{\mathbb Q}}
\newcommand{\N}{{\mathbb N}}
\newcommand{\Z}{{\mathbb Z}}
\newcommand{\C}{{\mathcal C}}
\renewcommand{\H}{{\mathcal H}}
\newcommand{\F}{{\mathcal F}}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\median}{median}

\definecolor{MyOrange}  {cmyk}{0,0.73,1.0,0}
\definecolor{MyGreen}   {cmyk}{1,0,1,0.0}

% Rida's colors and commands
\definecolor{Red}{rgb}{0.9,0.0,0.1}
\definecolor{Brown}{rgb}{0.55,0.27,0.1}
\definecolor{Brownie}{rgb}{0.75,0.27,0.1}
\definecolor{Yellow}{rgb}{1,1,0}
\definecolor{White}{rgb}{1,1,1}
\definecolor{formule}{rgb}{0.75,0.27,0.1}
\definecolor{formule}{rgb}{.7,1,0}
\definecolor{violet}{rgb}{0.7,0,.9}
\definecolor{darkgreen}{rgb}{0,.7,0}

%\newcommand{\reference}[1] {{\scriptsize \color{gray}  #1 }} 
\newcommand{\reference}[1] {{\color{gray}  #1 }} 
\newcommand{\rmk}[1]{{\color{Red} #1}}

%\theoremstyle{plain}\newtheorem{theorem}{Theorem}[chapter]
%\theoremstyle{plain}\newtheorem{proposition}{Proposition}[chapter]
%\theoremstyle{plain}\newtheorem{lemma}{Lemma}[chapter]
%\theoremstyle{definition}\newtheorem{definition}{Definition}[chapter]

% New definition of square root:
% it renames \sqrt as \oldsqrt
\let\oldsqrt\sqrt
% it defines the new \sqrt in terms of the old one
\def\sqrt{\mathpalette\DHLhksqrt}
\def\DHLhksqrt#1#2{%
\setbox0=\hbox{$#1\oldsqrt{#2\,}$}\dimen0=\ht0
\advance\dimen0-0.2\ht0
\setbox2=\hbox{\vrule height\ht0 depth -\dimen0}%
{\box0\lower0.4pt\box2}}

%gets rid of bottom navigation bars
% \setbeamertemplate{footline}[frame number]{}

%gets rid of navigation symbols
\setbeamertemplate{navigation symbols}{}

\title[VNLB - Parameter Analysis]{$\,$ \\ $\,$ \\ Parameter analysis for Video NL-Bayes}
\author[Pablo Arias]{March 31, 2015}
\institute[CMLA]{}
\date[]{}

%\author[Pablo Arias]{Pablo Arias$^*$, Vicent Caselles$^*$, Gabriele Facciolo$^\dagger$ \\ Rida Sadek$^*$, Guillermo Sapiro$^\ddagger$ \\ $\,$ \\  $\,$ \\ $\,$ \\ $\,$ \\
%\institute[UPF]{* Universitat Pompeu Fabra\\ $\dagger$ ENS Cachan \\ $\ddagger$ Duke University}

% \AtBeginSection[]  % "Beamer, do the following at the start of every section"
% {\begin{frame}<beamer>
% \frametitle{Outline} % make a frame titled "Outline"
% \tableofcontents[currentsection]  % show TOC and highlight current section
% \end{frame}}
%
% \AtBeginSubsection[]  % "Beamer, do the following at the start of every section"
% {\begin{frame}<beamer>
% \frametitle{Outline} % make a frame titled "Outline"
% \tableofcontents[currentsection,currentsubsection]  % show TOC and highlight current section
% \end{frame}}

\graphicspath{{./figures/}}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\section{Introduction}

\begin{frame}{Introduction}

	\begin{center}
	Experiments on 5 sequences of the Middlebury optical flow dataset:

	\bigskip

	\emph{Army}, \\
	\emph{DogDance}, \\
	\emph{Evergreen}, \\
	\emph{Mequon}, \\
	\emph{Walking},

	\bigskip

	with white additive Gaussian noise of

	\bigskip

	$\sigma = 10$, \\ 
	$\sigma = 25$, \\ 
	$\sigma = 40$.
	\end{center}

\end{frame}

\begin{frame}{Parameters for step 2: final estimate}
	\begin{center}

	Default parameters:

	\bigskip

	\begin{tabular}{l | c c | c c | c c }
		& \multicolumn{2}{c|}{$\sigma = 10$} 
		& \multicolumn{2}{c|}{$\sigma = 25$} 
		& \multicolumn{2}{c}{$\sigma = 40$} \\
		                            & 1st  & 2nd  & 1st  & 2nd  & 1st  & 2nd \\\hline\hline
		Patch size                  &  3   &   3  &  5   &   3  &  5   &   3 \\
		Number of patches           & 135  & 135  & 375  & 135  & 375  & 135 \\
		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
		Spatial search window       & 13   & 13   & 37   & 13   & 37   & 13  \\
		Temporal search range       & 5    & 5    & 5    & 5    & 5    & 5   \\\hline
		Beta                        & 1    & 1.2  & 1    & 1.2  & 1    & 1.2 \\\hline
	\end{tabular}

	\bigskip
	\bigskip
	\bigskip

	We consider varying the 2nd step spatial search window $W_x$ and patch size $p$.\\ All other parameters are kept constant.

	\end{center}
\end{frame}

\multipleframe
\begin{frame}{Parameters for step 2: final estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s10_army}%
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s25_army}%
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s40_army}

		\bigskip

		Results for Army.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}

\begin{frame}{Parameters for step 2: final estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s10_dogdance}%
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s25_dogdance}%
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s40_dogdance}

		\bigskip

		Results for DogDance.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}

\begin{frame}{Parameters for step 2: final estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s10_evergreen}%
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s25_evergreen}%
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s40_evergreen}

		\bigskip

		Results for Evergreen.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}

\begin{frame}{Parameters for step 2: final estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s10_mequon}%
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s25_mequon}%
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s40_mequon}

		\bigskip

		Results for Mequon.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}

\begin{frame}{Parameters for step 2: final estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s10_walking}%
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s25_walking}%
		\includegraphics[width=.33\textwidth]{prms_step2/psnr_bars-final_s40_walking}

		\bigskip

		Results for Walking.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}
\restoreframe

\multipleframe
\begin{frame}{Parameters for step 2: final estimate}
	\begin{center}
		\begin{tabular}{l | c c c c }
			 $W_x$\textbackslash $p$ & 3  & 5  & 7  & 9 \\\hline\hline
			 13 & 13.68 &  40.34 & 156.42 & 427.04 \\
			 21 & 14.94 &  49.54 & 195.54 & 666.86 \\
			 29 & 17.72 &  61.52 & 226.98 & 774.20 \\
			 37 & 19.42 &  70.20 & 270.96 & 895.74 \\
		\end{tabular}

		\bigskip

		Average running times (s) accross sequences for $\sigma = 10$.
	\end{center}
\end{frame}

\begin{frame}{Parameters for step 2: final estimate}
	\begin{center}
		\begin{tabular}{l | c c c c }
			 $W_x$\textbackslash $p$ & 3  & 5  & 7  & 9 \\\hline\hline
			 13 & 27.48 &  55.62 & 176.20 & 489.34  \\
			 21 & 29.82 &  67.06 & 220.26 & 735.90  \\
			 29 & 33.12 &  75.06 & 262.62 & 878.22  \\
			 37 & 35.64 &  87.16 & 303.82 & 1014.76 \\
		\end{tabular}

		\bigskip

		Average running times (s) accross sequences for $\sigma = 25$.
	\end{center}
\end{frame}

\begin{frame}{Parameters for step 2: final estimate}
	\begin{center}
		\begin{tabular}{l | c c c c }
			 $W_x$\textbackslash $p$ & 3  & 5  & 7  & 9 \\\hline\hline
			 13 & 28.14 &  59.42 & 200.92 & 616.32  \\
			 21 & 29.24 &  69.86 & 260.32 & 897.90  \\
			 29 & 32.46 &  79.86 & 308.46 & 1080.72 \\
			 37 & 36.52 &  95.78 & 362.98 & 1256.66 \\
		\end{tabular}

		\bigskip

		Average running times (s) accross sequences for $\sigma = 40$.
	\end{center}
\end{frame}
\restoreframe

\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}

	Default parameters:

	\bigskip

	\begin{tabular}{l | c c | c c | c c }
		& \multicolumn{2}{c|}{$\sigma = 10$} 
		& \multicolumn{2}{c|}{$\sigma = 25$} 
		& \multicolumn{2}{c}{$\sigma = 40$} \\
		                            & 1st  & 2nd  & 1st  & 2nd  & 1st  & 2nd \\\hline\hline
		Patch size                  &  3   &   3  &  5   &   3  &  5   &   3 \\
		Number of patches           & 135  & 135  & 375  & 135  & 375  & 135 \\
		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
		Spatial search window       & 13   & 13   & 37   & 13   & 37   & 13  \\
		Temporal search range       & 5    & 5    & 5    & 5    & 5    & 5   \\\hline
		Beta                        & 1    & 1.2  & 1    & 1.2  & 1    & 1.2 \\\hline
	\end{tabular}

	\bigskip
	\bigskip
	\bigskip

	We consider varying the 1st step spatial search window $W_x$ and patch size $p$.\\
	Two patch sizes will be consider in the second step: 3 and 5.\\
	All other parameters are kept constant.

	\end{center}
\end{frame}

\multipleframe
\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s10_army}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s25_army}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s40_army}

		\bigskip

		Results for Army and $p^{(2)} = 3$.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}
\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s10_dogdance}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s25_dogdance}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s40_dogdance}

		\bigskip

		Results for DogDance and $p^{(2)} = 3$.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}
\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s10_evergreen}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s25_evergreen}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s40_evergreen}

		\bigskip

		Results for Evergreen and $p^{(2)} = 3$.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}
\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s10_mequon}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s25_mequon}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s40_mequon}

		\bigskip

		Results for Mequon and $p^{(2)} = 3$.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}
\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s10_walking}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s25_walking}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps3/psnr_basic-vs-final_s40_walking}

		\bigskip

		Results for Walking and $p^{(2)} = 3$.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}
\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s10_army}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s25_army}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s40_army}

		\bigskip

		Results for Army and $p^{(2)} = 5$.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}

\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s10_dogdance}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s25_dogdance}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s40_dogdance}

		\bigskip

		Results for DogDance and $p^{(2)} = 5$.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}
\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s10_evergreen}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s25_evergreen}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s40_evergreen}

		\bigskip

		Results for Evergreen and $p^{(2)} = 5$.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}
\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s10_mequon}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s25_mequon}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s40_mequon}

		\bigskip

		Results for Mequon and $p^{(2)} = 5$.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}
\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s10_walking}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s25_walking}%
		\includegraphics[width=.33\textwidth]{prms_step1_step2_ps5/psnr_basic-vs-final_s40_walking}

		\bigskip

		Results for Walking and $p^{(2)} = 5$.\\From left to right: $\sigma = 10, 25$ and $40$.
	\end{center}
\end{frame}
\restoreframe

\multipleframe
\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\begin{tabular}{l | c c c c }
			 $W_x$\textbackslash $p$ & 3  & 5  & 7  & 9 \\\hline\hline
			 13 & 40.68 &  44.38 &  67.16 & 127.86 \\
			 21 & 42.48 &  46.10 &  74.72 & 152.92 \\
			 29 & 42.26 &  47.82 &  83.90 & 177.02 \\
			 37 & 43.28 &  52.10 &  91.70 & 200.28 \\
		\end{tabular}

		\bigskip

		Average running times (s) accross sequences for $\sigma = 10$.
	\end{center}
\end{frame}

\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\begin{tabular}{l | c c c c }
			 $W_x$\textbackslash $p$ & 3  & 5  & 7  & 9 \\\hline\hline
			 13 & 48.52 &  52.96 &  86.74 & 180.52 \\
			 21 & 48.92 &  56.26 &  96.10 & 206.70 \\
			 29 & 49.40 &  57.12 & 100.72 & 216.30 \\
			 37 & 49.88 &  60.14 & 105.68 & 229.04 \\
		\end{tabular}

		\bigskip

		Average running times (s) accross sequences for $\sigma = 25$.
	\end{center}
\end{frame}

\begin{frame}{Parameters for step 1: basic estimate}
	\begin{center}
		\begin{tabular}{l | c c c c }
			 $W_x$\textbackslash $p$ & 3  & 5  & 7  & 9 \\\hline\hline
			 13 & 53.44 &  56.12 &  92.62 & 190.76 \\
			 21 & 54.00 &  59.84 & 101.28 & 222.16 \\
			 29 & 54.90 &  62.36 & 107.18 & 235.28 \\
			 37 & 55.00 &  63.00 & 111.58 & 250.36 \\
		\end{tabular}

		\bigskip

		Average running times (s) accross sequences for $\sigma = 40$.
	\end{center}
\end{frame}
\restoreframe

\multipleframe
\begin{frame}{PSNRs of basic estimates}

	\begin{center}
	\begin{tabular}{| c | c |c c c c c|}
		\hline \hline
		$\sigma$  & Method \textbackslash Video & Army & DogDance & Evergreen & Mequon & Walking \\\hline\hline
		\multirow{5}{*}{$10$} & BM4D           & \best{37.48} & \best{35.60} & \best{35.29} & \best{37.89} & \best{38.67} \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &       14.30  &       18.98  &       15.87  &       16.83  &       16.28  \\%\cline{2-7}
		                      & VNLB $W_t = 1$ &       36.21  &       34.86  &       34.50  &       37.16  &       37.54  \\%\cline{2-7}
		                      & VNLB $W_t = 2$ &       36.77  &       35.22  &       34.82  &       37.69  &       38.20  \\\hline
%									 
		\multirow{5}{*}{$25$} & BM4D           & \best{32.24} & \best{31.07} & \best{30.48} &       32.89  & \best{33.54} \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &       30.13  &       29.51  &       29.07  &       30.91  &       30.00  \\%\cline{2-7}
		                      & VNLB $W_t = 1$ &       31.92  &       30.85  &       30.33  &       32.86  &       33.00  \\%\cline{2-7}
									 & VNLB $W_t = 2$ & \best{32.21} & \best{31.02} & \best{30.50} & \best{33.14} &       33.31  \\\hline
%									 
		\multirow{5}{*}{$40$} & BM4D           & \best{29.53} & \best{28.59} &       27.93  &       29.94  & \best{30.55} \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &       27.03  &       26.62  &       26.27  &       27.59  &       27.65  \\%\cline{2-7}
		                      & VNLB $W_t = 1$ &       29.13  &       28.30  &       27.88  &       29.79  &       29.91  \\%\cline{2-7}
									 & VNLB $W_t = 2$ & \best{29.50} & \best{28.55} & \best{28.13} & \best{30.15} &       30.29  \\\hline\hline
	\end{tabular}

	\bigskip
	Results of VNLB corresponding to patch sizes of $5$ in both steps.\\The rest of parameters are the default ones.
	\end{center}

\end{frame}

\begin{frame}{PSNRs of final estimates}

	\begin{center}
	\begin{tabular}{| c | c |c c c c c|}
		\hline \hline
		$\sigma$  & Method \textbackslash Video & Army & DogDance & Evergreen & Mequon & Walking \\\hline\hline
		\multirow{5}{*}{$10$} & BM4D           & \best{37.77} &       35.70  & \best{35.40} &       38.09  &       38.85  \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &       34.46  &       33.61  &       33.05  &       35.65  &       35.90  \\%\cline{2-7}
		                      & VNLB $W_t = 1$ &       37.65  & \best{35.87} & \best{35.42} & \best{39.10} & \best{39.70} \\%\cline{2-7}
									 & VNLB $W_t = 2$ & \best{37.75} & \best{35.92} & \best{35.47} & \best{39.06} & \best{39.79} \\\hline
%									 
		\multirow{5}{*}{$25$} & BM4D           &       32.91  &       31.50  &       30.94  &       33.60  &       34.27  \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &       32.33  &       31.17  &       30.39  &       33.69  &       33.74  \\%\cline{2-7}
									 & VNLB $W_t = 1$ &       33.48  & \best{31.98} & \best{31.22} & \best{35.10} &       35.25  \\%\cline{2-7}
		                      & VNLB $W_t = 2$ & \best{33.58} & \best{31.98} & \best{31.22} & \best{35.08} & \best{35.38} \\\hline
%									 
		\multirow{5}{*}{$40$} & BM4D           &       30.42  &       29.29  &       28.65  &       31.02  &       31.64  \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &       29.94  &       28.95  &       28.24  &       30.98  &       30.95  \\%\cline{2-7}
									 & VNLB $W_t = 1$ &       31.36  &       29.96  & \best{29.19} & \best{32.70} &       32.71  \\%\cline{2-7}
									 & VNLB $W_t = 2$ & \best{31.55} & \best{30.01} & \best{29.24} & \best{32.75} & \best{32.94} \\\hline\hline
	\end{tabular}

	\bigskip
	Results of VNLB corresponding to patch sizes of $5$ in both steps.\\The rest of parameters are the default ones.
	\end{center}

\end{frame}
\restoreframe

\begin{frame}{}
	\centering
   \vspace{1.7cm}
   \textcolor{MyOrange}{\textbf{\Huge{Merci.}}}\\
   \vspace{5cm}
\end{frame}

% 
%

\end{document}

### 2015-05-04 doc/201504_acivs/paper.tex
Add avics paper

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
%

\usepackage[english,activeacute]{babel}
\usepackage[english]{layout}
\usepackage{amsfonts,amssymb}
\usepackage{amsmath}
\usepackage{amsopn} % DeclareMathOperator
\usepackage{amsbsy} % boldsymbol
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{subfig}
\usepackage{colonequals}
\usepackage[latin1]{inputenc}
\usepackage{url}
\usepackage{epsfig}
\usepackage{dsfont}
\usepackage{multirow}

\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{setspace}
\usepackage{afterpage}
%\usepackage{showkeys}
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
% \usepackage{latexsym}

%\usepackage[left=1.2in,right=1.2in]{geometry}

% \graphicspath{{../iccv09/}}

\newcommand{\ma}[1]{\boldsymbol{#1}}
\newcommand{\tras}[1]{#1^{\mathrm{T}}}
\newcommand{\herm}[1]{#1^{\mathrm{H}}}
\newcommand{\con}[1]{#1^{\mathrm{*}}}
\newcommand{\E}{\mathds{E}}
\newcommand{\tech}[1]{\overline{#1}}
\newcommand{\nspace}{\!\!\!\!}
\newcommand{\nmbr}[1]{\oldstylenums{#1}}

\newcommand{\eg}{\emph{e.g}. } \newcommand{\Eg}{\emph{E.g}. }
\newcommand{\ie}{\emph{i.e}. } \newcommand{\Ie}{\emph{I.e}. }
\newcommand{\cf}{\emph{c.f}. } \newcommand{\Cf}{\emph{C.f}. }
\newcommand{\etc}{\emph{etc}. } \newcommand{\vs}{\emph{vs}. }
\newcommand{\wrt}{w.r.t\onedot } \newcommand{\dof}{d.o.f. }
\newcommand{\etal}{\emph{et al}. }

\newcommand{\R}{\mathds{R}}
\newcommand{\sign}{\mathrm{sign}}
\newcommand{\eps}{\varepsilon}
\newcommand{\To}{\longrightarrow}
% \newcommand{\II}{1{\hskip -2.5 pt}\hbox{I}}

\newcommand{\best}[1]{\textbf{#1}}

% c++ code
\usepackage{listings}
\usepackage{xcolor}
\usepackage{textcomp}
\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
	backgroundcolor=\color{lbcolor},
	tabsize=4,    
%  rulecolor=,
	language=Matlab,
	basicstyle=\scriptsize\ttfamily,
	upquote=true,
	aboveskip={1.5\baselineskip},
	columns=fixed,
	showstringspaces=false,
	extendedchars=false,
	breaklines=true,
	prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
	frame=single,
	numbers=left,
	showtabs=false,
	showspaces=false,
	showstringspaces=false,
	identifierstyle=\ttfamily,
	keywordstyle=\color[rgb]{0,0,1}\ttfamily,
	commentstyle=\color[rgb]{0,0.5,0}\ttfamily,
	stringstyle=\color[rgb]{0.627,0.126,0.941}\ttfamily,
	numberstyle=\color[rgb]{0.5, 0.5, 0.5}\ttfamily,
%  \lstdefinestyle{C++}{language=C++,style=numbers}’.
}
%\lstset{
%	backgroundcolor=\color{lbcolor},
%	tabsize=4,
%	language=C++,
%	captionpos=b,
%	tabsize=3,
%	frame=lines,
%	numbers=left,
%	numberstyle=\tiny,
%	numbersep=5pt,
%	breaklines=true,
%	showstringspaces=false,
%	basicstyle=\footnotesize,
%	identifierstyle=\color{magenta},
%	keywordstyle=\color[rgb]{0,0,1},
%	commentstyle=\color{green},
%	stringstyle=\color{red}
%}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\nota}[1]{\textcolor{blue}{\textbf{#1}}}
\newcommand{\suggest}[1]{\textcolor{yellow}{#1}}
\newcommand{\add}[1]{\textcolor{green}{#1}}
\newcommand{\remove}[1]{\textcolor{red}{#1}}
\newcommand{\dosdv}[1] {#1}
\newcommand{\uncite}[1] {}
% \newcommand{\tachar}[1]{
% \setbox4=\hbox{\ } \setbox3=\hbox{#1} \hbox{#1} \kern -\wd3 \kern
% -\wd4 \raise 0.3\ht3 \hbox{ \vrule width \wd3 height 0.5pt} }

% \theoremstyle{plain}\newtheorem{theorem}{Theorem}[chapter]
% \theoremstyle{plain}\newtheorem{proposition}{Proposition}[chapter]
% \theoremstyle{plain}\newtheorem{lemma}{Lemma}[chapter]
% \theoremstyle{definition}\newtheorem{definition}{Definition}[chapter]

% New definition of square root:
% it renames \sqrt as \oldsqrt
\let\oldsqrt\sqrt
% it defines the new \sqrt in terms of the old one
\def\sqrt{\mathpalette\DHLhksqrt}
\def\DHLhksqrt#1#2{%
\setbox0=\hbox{$#1\oldsqrt{#2\,}$}\dimen0=\ht0
\advance\dimen0-0.2\ht0
\setbox2=\hbox{\vrule height\ht0 depth -\dimen0}%
{\box0\lower0.4pt\box2}}

\begin{document}
%
%
\mainmatter              % start of the contributions
%
\title{Towards a Bayesian video denoising method}
%
\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Pablo Arias\inst{1} \and Jean-Michel Morel\inst{2}}

\authorrunning{P. Arias and J.-M. Morel} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Pablo Arias, Jean-Michel Morel}

\institute{CMLA, ENS Cachan, France, \texttt{pariasm@gmail.com}
\and
CMLA, ENS Cachan, France, \texttt{jean-michel.morel@ens-cachan.fr}}
%

\maketitle              % typeset the title of the contribution

\begin{abstract}
	The quality provided by image/video sensors increases steadily, and
	for a fixed spatial resolution the sensor noise has been gradually reduced.
	However, modern sensors are also capable of acquiring at higher spatial
	resolutions which are still affected by noise, specially at low lighting
	conditions. The situation is even worse in video cameras, where the capture
	time is bounded by the frame rate. The noise in the video degrades its visual 
	quality and hinders its analysis.
	In this paper we present a new video denoising method extending 
	the non-local Bayes image denoising algorithm. The method does not require 
	motion estimation, and yet preliminary results show that it outperforms the
	state-of-the-art methods in terms of PSNR.
	\keywords{video denoising, Bayesian methods, patch-based methods}
\end{abstract}
%
\section{Introduction}
%

Advances in video sensor hardware have steadily improved the acquisition
quality. However, due to the reduction in the price of video cameras
and data storage, video cameras are being used more each time, and in less
favorable situations, such as low lighting conditions. This results in high 
levels of noise, which negatively affects the visual quality of the video and
hinders its use for any application.

In principle, video denoising should be easier than image denoising, due to 
strong temporal redundancy along motion trajectories. However, there are
several challenges: the first one is how to obtain a reliable motion
estimate. Motion estimation is a paramount problem in noiseless sequences,
and noise makes it
much harder. This is perhaps why there has always been interest in video denoising
methods which do not require motion estimation.

Early works proposed temporal or spatio-temporal filters which either compensate
for motion on estimated motion trajectories or used some kind of mechanism to
adapt to the changes in the video signal at a fixed location due to the motion.
We refer the reader to \cite{Brailean1995a} and references therein for more details.
Other video denoising works apply temporal filtering to the wavelet coefficients 
of the frames \cite{Jin2006,Zlokolica2006a}.

Some methods do not distinguish between the temporal and spatial dimensions,
and treat the video as a volume, which is denoised in a transformed domain
\cite{Rajpoot2003,Wilson2004,Selesnick2003}.

Until the advent of patch-based approaches, methods that do not compensate
motion failed for sequences with moderate motion, and their main interest resided
in their simplicity and low computational cost. First state-of-the-art results
obtained without motion estimation were reported in \cite{Buades2005v}, with the
non-local means algorithm. The authors argued that for their method, based on
averaging similar patches, motion estimation was not only unnecessary but
counterproductive: while textured regions are problematic for motion
estimation, they are a source of a large number of similar patches across
different frames. Even if the motion trajectory could be reliably estimated, it
makes more sense to use all similar patches, rather than using only the ones on the
trajectory.
%
A similar approach was followed by the authors of \cite{Dabov2007v}. This method is based
on collaborative filtering of similar patches in a
spatio-temporal neighborhood.

While these methods exploit spatio-temporal redundancy, they do not impose
coherence of the trajectories, resulting in flickering
artifacts which become noticeable for high levels of noise.

This issue was addressed in \cite{Protter2007,Protter2009} where the authors extend
the K-SVD \cite{Elad2006} image denoising method to video by learning a
dictionary of spatio-temporal 3D patches.

It has been shown by \cite{Liu2010} and \cite{Maggioni2011,Maggioni2012} that motion estimation can still be
beneficial for patch-based methods. 
%
In \cite{Liu2010} the authors proposed a method based on non-local means, in which the set of
similar patches averaged to denoise each pixel varies smoothly along motion
trajectories. This yields results with higher temporal consistency, and
permits to handle better structured noise. To estimate motion, their method resorts
to a robust optical flow algorithm based on \cite{Bruhn2005}.

In \cite{Maggioni2011,Maggioni2012}, the authors introduced a non-trivial extension of BM3D to video by
collaborative filtering of similar patch trajectories (motion compensated 3D
patches). Trajectories are computed with a block matching strategy based on the
sum of squared differences (SSD) and a temporal regularization term, which
favours trajectories with small velocity and low acceleration. The results of this
algorithm show higher PSNR and temporal consistency, resulting in a higher
overall quality.

\bigskip

In this work we present an extension to video of the non-local Bayes image
denoising method \cite{Lebrun2013a,Lebrun2013ipol}, which does not compensate for motion. We
show that this algorithm is a valid option for moderate values of noise, due 
to it simplicity and the fact that it provides state-of-the-art results in
terms of PSNR.

The rest of the paper is structured as follows: in \S
\ref{sec:review_nonlocal_Bayes} we review the Bayesian patch denoising principle 
and describe our extension to video. In \S \ref{sec:parameters}
we discuss its parameters. Some results, including a comparison with VBM4D, are shown
in \S \ref{sec:results}. Concluding remarks are given in \S \ref{sec:conclusion}

\section{Bayesian video denoising}
\label{sec:review_nonlocal_Bayes}

A patch based Bayesian algorithm can assume that the patches similar to a given
patch follow a Gaussian distribution.
The problem 
of denoising can then be formulated as a problem of optimal Bayesian inference, where the
parameters of the prior are learnt from the noisy data.

\subsection{A nonlocal Bayesian principle}

Consider a grayscale video $u:\Omega\times \{1,\cdots,T\}\rightarrow
\mathbb R$, where $\Omega$ is the spatial domain (a rectangular discrete grid).
We assume that $v$ is a noisy version of $u$, contaminated with additive,
Gaussian, white noise $n$ of known variance $\sigma^2$,
\[v = u + n.\]

Given a square patch $\ma q$ of side $s$ of the noisy video $v$, and the 
corresponding patch $\ma p$ of the clean video $u$, We assume the following 
Gaussian linear model of $\ma p$ and $\ma q$:
\begin{align}
	\mathds{P}(\ma p) &= \mathcal N(\overline {\ma p}, C_{\ma p}) \propto \exp\left(-\frac12\langle \ma p - \overline{\ma p}, C_{\ma p}^{-1}(\ma p - \overline{\ma p})\rangle\right) \label{eq:prior}\\
	\mathds{P}(\ma q|\ma p) &= \mathcal N(\ma p, \sigma I) \propto \exp\left(-\frac1{2\sigma^2}\|\ma q - \ma p\|^2\right) \label{eq:obs}
\end{align}
Once the mean patch $\overline{\ma p}$ and the
covariance matrix $C_{\ma p}$ have been estimated from the image itself, the MAP
estimate $\widetilde{\ma p}$ given a noisy patch $\ma q$ is obtained as:
\[ \widetilde{\ma p} = \argmax_{\ma p} \mathds P(\ma p | \ma q) = \argmin_{\ma p} -\log \mathds P(\ma p | \ma q). \]
Since we are working with Gaussian distributions, the log-posterior is a quadratic (positive definite)
function and the MAP can be computed explicitly as (see  \cite{Lebrun2013a})
\begin{equation}
	\widetilde{\ma p} = \overline{\ma p} + C_{\ma p}(C_{\ma p} + \sigma^2 I)^{-1}(\ma q - \overline{\ma p})
	\label{eq:map}
\end{equation}
This equation is equivalent to a Wiener filter on the projections 
of the patch over the eigenvectors of $C_{\ma p}$, the principal directions of
the Gaussian. 
%
%In practice, we introduce a parameter $\beta$ (with $\beta \approx 1$)
%multiplying $\sigma^2I$ to be able to control the amount of filtering.

\subsection{Learning the \textit{a priori} model}

The parameters of the \textit{a priori} model, are learnt from the noisy video as
follows. For each noisy patch $\ma q$, we select the most $N_{\text{sim}}$
similar patches found in a search region centered at $\ma q$. The
search region is a spatiotemporal rectangle of size $n_x \times
n_x \times n_t$ ($n_x, n_t$ are odd numbers).

Let us note by $\ma q_i$, $i = 1, \dots, N_{\text{sim}}$ the set of patches
similar to $\ma q$ (with $\ma q_1 = \ma q$). We assume that these 
patches correspond to different noisy observations of the Gaussian linear model
\eqref{eq:prior} and \eqref{eq:obs}. The corresponding marginal distribution is given by
\[\mathds P(\ma q) = \mathcal N(\overline{\ma p}, C_{\ma p} + \sigma^2I). \]
Therefore, the maximum likelyhood estimates for $\overline{\ma p}$ and $C_{\ma
p}$ are given by 
\begin{equation}
	\widehat{\overline{\ma p}} = \frac1{N_{\text{sim}}}\sum_{i = 1}^{N_{\text{sim}}}\ma q_i \quad\text{and}\quad 
		\widehat C_{\ma p}= \frac1{N_\text{sim}}\sum_{i = 1}^{N_{\text{sim}}}\ma q_i^T\ma q_i - \sigma^2I.
	\label{eq:learn_parameters}
\end{equation}

Other methods for image denoising have been proposed in the
literature based on Gaussian models for the patch density. In \cite{Yu2012},
the authors introduce a framework for solving inverse problems, based on the
assumption that the patches of an image are distributed according to a Gaussian
Mixture Model (GMM). A method is proposed to learn the parameters of the model from
the image. A GMM is also used in \cite{Zoran2011}, but it is tranined from a
database of $2\cdot 10^6$ patches randomly sampled from the Berkeley database.

In \cite{Zhang2010} a PCA-based algorithm is introduced which is equivalent to 
the nonlocal Bayes method. In fact, nonlocal Bayes can be regarded as a Bayesian 
interpretation of \cite{Zhang2010}.

The BLS-GSM method \cite{Portilla2003} (Bayes least square estimate of Gaussian
scale mixture) models noisless ``wavelet coefficient neighborhoods'' with a
Gaussian scale mixture defined as a random scaling of a zero-mean Gaussian
density. The wavelet coefficient neighborhood turns out to be a patch of an
oriented channel of the image at a given scale.

\subsection{Description of the algorithm}

Let us now describe the video denoising algorithm. As in
\cite{Dabov2007tip,Dabov2007v,Maggioni2012,Lebrun2013a} we perform two stages.
In the first
stage we compute a \emph{basic} estimate, which we denote $u^{(1)}$.

In the second stage, the basic estimate is used as an oracle. The computation
of the patch distances is performed using the patches of the basic estimate
instead of the noisy ones. In addition, we assume that the patches of the basic estimate
are drawn from the \textit{a priori} Gaussian model and use them to learn the mean and
covariance matrix as explained in the Algorithm \ref{alg:nlbayes}.

\begin{algorithm}
	\caption{Video NL-Bayes}
	\label{alg:nlbayes}
	\begin{algorithmic}
		\REQUIRE Noisy video $v$, noise standard deviation $\sigma$ \\
		\ENSURE Estimate of noiseless video $\widetilde u$
		\FORALL{patches $\ma q$ in $v$}
		\STATE Find the $N_{\text{sim}}$ most similar patches to $\ma q$ in a search volume centered at $\ma q$
		\STATE Compute $\widehat{\overline{\ma p}}\,\!^{(1)}$ and $\widehat C_{\ma p}^{(1)}$ according to \eqref{eq:learn_parameters}
		\STATE Obtain the first stage estimate $\widetilde{\ma p}^{(1)}$ by \eqref{eq:map}
		\ENDFOR
		\FORALL{pixel $(x,t)$ in $\Omega\times {1,\dots,T}$}
		\STATE Obtain the basic estimate $\widetilde u^{(1)}(x,t)$ by averaging
		the values of all patches $\widetilde{\ma p}^{(1)}$ containing $(x,t)$.
		\ENDFOR
		\FORALL{patches $\ma q$ in $v$}
		\STATE Find the $N_{\text{sim}}$ most similar patches to $\ma q$ in a
		search volume centered at $\ma q$ by comparing the estimates $\widetilde{\ma
		p}^{(1)}$. We denote them, and their corresponding basic estimates as 
		$\ma q_i$ and $\widetilde{\ma p}_i^{(1)}$ respectively.
		\STATE Compute $\widehat{\overline{\ma p}}\,\!^{(2)}$ and $\widehat C_{\ma p}^{(2)}$ according to
\[
	\widehat{\overline{\ma p}}\,\!^{(2)} = \frac1{N_{\text{sim}}}\sum_{i = 1}^{N_{\text{sim}}}\widetilde{\ma p}_i^{(1)} \quad\text{and}\quad 
	\widehat C_{\ma p}^{(2)}= \frac1{N_\text{sim}}\sum_{i = 1}^{N_{\text{sim}}}\left(\widetilde{\ma p}_i^{(1)}\right)^T \widetilde{\ma p}_i^{(1)}.
\]
		\STATE Obtain the second stage estimate $\widetilde{\ma p}^{(2)}$ as in \eqref{eq:map}
		\ENDFOR
		\FORALL{pixel $(x,t)$ in $\Omega\times {1,\dots,T}$}
		\STATE Obtain the final estimate $\widetilde u(x,t)$ by averaging
		the values of all patches $\widetilde{\ma p}^{(2)}$ containing $(x,t)$.
		\ENDFOR

	\end{algorithmic}
\end{algorithm}

\begin{figure}[thpb!]
	\begin{center}
		\includegraphics[trim=0cm 2cm 4cm 1cm, clip=true, width=0.3\textwidth]{figs/bus_nisy_s10_044.png}
		\includegraphics[trim=0cm 2cm 4cm 1cm, clip=true, width=0.3\textwidth]{figs/bus_nisy_s20_044.png}
		\includegraphics[trim=0cm 2cm 4cm 1cm, clip=true, width=0.3\textwidth]{figs/bus_nisy_s40_044.png}\\
		\includegraphics[trim=0cm 2cm 4cm 1cm, clip=true, width=0.3\textwidth]{figs/bus_vnlb_s10_tr2_044.png}
		\includegraphics[trim=0cm 2cm 4cm 1cm, clip=true, width=0.3\textwidth]{figs/bus_vnlb_s20_tr2_044.png}
		\includegraphics[trim=0cm 2cm 4cm 1cm, clip=true, width=0.3\textwidth]{figs/bus_vnlb_s40_tr2_044.png}\\
		\includegraphics[trim=0cm 2cm 4cm 1cm, clip=true, width=0.3\textwidth]{figs/bus_s10_bm4d_044.png}
		\includegraphics[trim=0cm 2cm 4cm 1cm, clip=true, width=0.3\textwidth]{figs/bus_s20_bm4d_044.png}
		\includegraphics[trim=0cm 2cm 4cm 1cm, clip=true, width=0.3\textwidth]{figs/bus_s40_bm4d_044.png}\\
		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/tennis_nisy_s10_140.png}
		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/tennis_nisy_s20_140.png}
		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/tennis_nisy_s40_140.png}\\
		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/tennis_vnlb_s10_tr2_140.png}
		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/tennis_vnlb_s20_tr2_140.png}
		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/tennis_vnlb_s40_tr2_140.png}\\
		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/tennis_s10_bm4d_140.png}
		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/tennis_s20_bm4d_140.png}
		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/tennis_s40_bm4d_140.png}
	\end{center}
	\caption{Comparison of results obtained with VNLB ($n_t =5$) and V-BM4D-np.
	The first three rows, correspond to a frame of the bus sequence. From top to
	bottom: noisy input data. The last three rows correspond to the tennis sequence.
	Each column shows results obtained for $\sigma = 10$, $20$ and $40$.}
	\label{fig:results}
\end{figure}

\subsection{Implementation details}

\paragraph{Handling of color.} Color videos are handled as in \cite{Lebrun2013a}.
%
In the first stage, we express the video in a luminance-chrominance colorspace,
specifically we apply the opponent color transform (see \cite{Dabov2007tip,Lebrun2013a}).
Patch distances are computed using the luminance only. Using the 
$N_{\text{sim}}$ most similar patches, a group is built for each channel. These
groups are filtered independently (a Gaussian model is learnt for each of them).
%
In the second stage, the patch distance is computed using the RGB patches, and
a single \textit{a priori} Gaussian model is built for the each set
of similar RGB patches.

\paragraph{Variance correction factor.} In practice, when computing the MAP
estimate by eq. \eqref{eq:map}, we introduce a parameter $\beta$ (with $\beta \approx 1$) multiplying
$\sigma^2I$ to be able to control the amount of filtering.

\paragraph{Patch distance threshold.} When building the group of similar
patches during the second stage, more than $N_{\text{sim}}$ patches are allowed
if their distances with respect to the reference patch are smaller than a
threshold $\tau$.  As in \cite{Lebrun2013ipol}, we set $\tau = 4$ (the distance between
patches is normalized by the number of elements in the patch and the number of
channels).

\paragraph{Speed-ups.} To accelerate the computation we apply two tricks
considered in \cite{Lebrun2013ipol}. The first one visits a patch each $N_{\text{step}}$
patches (similar to \cite{Dabov2007tip}). The second trick consists on the following.
After filtering the patches in a group, these patches are not considered again
as reference patches for a group. This reduces the number of groups of patches
that need to be processed by a factor of $N_{\text{sim}}$.

\subsection{Selection of parameters}
\label{sec:parameters}

For the experiments shown in \S \ref{sec:results} we used the following 
parameters.
\begin{description}
	\item[Patch size:] In both stages, we fixed the patch size at $s = 5$. Better 
		results can be obtained with higher patch sizes, but the computational cost
		scales considerably (e.g. the inversion of the covariance matrix is of $O(s^6)$).
	\item[Number of similar patches:] For the first stage, we set
		$N^{(1)}_{\text{sim}} = 3s^2n_t$  (recall that $n_t$ is the temporal
		extend of the search region). For the second step we 
		found better results using fewer patches, thus we set $N^{(2)}_{\text{sim}} = 3/4 s^2n_t$.
	\item[Search region:] In both stages, we used $n_x = s^2/2$.
		For the temporal search region, we found a good trade-off
		between computational time and quality of the results for $n_t = 5$. 
	\item[Patch distance threshold:] When building the group of similar patches
		in the second stage, more than $N_{\text{sim}}$ patches are allowed if their 
		distances with respect to the reference patch are smaller than a threshold $\tau$.
		As in \cite{Lebrun2013ipol}, we set $\tau = 4$ (the distance between patches is normalized by 
		the number of elements in the patch and the number of channels).
\end{description}

% stage 1
%
% patch size $s = 5$
% spatial search region $n_x = 37$
% temporal search region $n_t = 0,3,5$
% number of similar patches $3 s^2 n_t$, 3/4 s^2 n_t$$
% beta $\beta = 1; 1.2$
% tau n/a $\tau = 16$  
% offset $= s/2$

% stage 2
%
% patch size 
% spatial search region
% temporal search region
% number of similar patches
% beta
% tau
% offset

\begin{table}[htp!]
	\begin{center}
	\renewcommand{\tabcolsep}{3mm}
	\renewcommand{\arraystretch}{1.0}
	\begin{tabular}{ c | l |c c c c}
		\hline
		\rule{0pt}{12pt}$\sigma$ & Method     & Tennis       & Coastguard   & Foreman      & Bus          \\\hline
		\multirow{5}{*}{$10$} & V-BM4D \cite{Maggioni2012}       & \best{36.42} & \best{37.27} &       37.92  &       36.23  \\
		                      & V-BM4D-np     &       35.56  &       36.20  &       36.90  &       35.09  \\
		                      & V-BM3D        &       36.04  &       36.82  &       37.52  &       34.96  \\
		                      & VNLB $n_t = 0$ &       34.43  &       36.70  &       37.21  &       35.58  \\
		                      & VNLB $n_t = 3$ &       35.04  &       37.19  &       37.88  &       36.19  \\
									 & VNLB $n_t = 5$ &       35.28  & \best{37.30} & \best{38.11} & \best{36.37} \\\hline
%									 
		\multirow{5}{*}{$20$} & V-BM4D  \cite{Maggioni2012}       & \best{32.88} & \best{33.61} & \best{34.62} &       32.27  \\
		                      & V-BM4D-np     &       31.67  &       32.24  &       33.34  &       30.95  \\
		                      & V-BM3D        &       32.54  &       33.39  &       34.49  &       31.03  \\
		                      & VNLB $n_t = 0$ &       30.65  &       32.70  &       33.64  &       31.39  \\
									 & VNLB $n_t = 3$ &       31.26  &       33.35  &       34.25  &       32.11  \\
									 & VNLB $n_t = 5$ &       31.49  &       33.55  &       34.45  & \best{32.35} \\\hline
%									 
		\multirow{5}{*}{$40$} & V-BM4D   \cite{Maggioni2012}      & \best{29.52} & \best{30.00} & \best{31.30} &       28.32  \\
		                      & V-BM4D-np     &       27.97  &       28.43  &       29.69  &       27.02  \\
		                      & V-BM3D        &       29.20  &       29.99  &       31.17  &       27.34  \\
		                      & VNLB $n_t = 0$ &       27.43  &       28.88  &       30.15  &       27.60  \\
									 & VNLB $n_t = 3$ &       27.97  &       29.60  &       30.72  &       28.23  \\
									 & VNLB $n_t = 5$ &       28.11  &       29.78  &       30.82  & \best{28.40} \\\hline
	\end{tabular}
	\end{center}
	\caption{PSNRs obtained for the four classic color test sequences reported in
	\cite{Maggioni2012}. See text for details.}
	\label{tab:psnr}
\end{table}

\begin{table}[htp!]
	\begin{center}
	\renewcommand{\tabcolsep}{2mm}
	\renewcommand{\arraystretch}{1.0}
	\begin{tabular}{ c | l |c c c c c}
		\hline
		\rule{0pt}{12pt}$\sigma$ & Method     & Army & DogDance & Evergreen & Mequon & Walking  \\\hline
		\multirow{5}{*}{$10$} & V-BM4D-np      &       37.77  &       35.70  &       35.40  &       38.09  &       38.85  \\
		                      & VNLB $n_t = 0$ &       36.90  &       35.42  &       34.84  &       38.43  &       38.86  \\
		                      & VNLB $n_t = 3$ &       37.65  &       35.87  &       35.38  &       39.09  &       39.69  \\
									 & VNLB $n_t = 5$ & \best{37.88} & \best{36.01} & \best{35.53} & \best{39.20} & \best{39.74} \\\hline
%									                                                                                           
		\multirow{5}{*}{$20$} & V-BM4D-np      &       32.91  &       31.50  &       30.94  &       33.60  &       34.27  \\
		                      & VNLB $n_t = 0$ &       33.77  &       32.44  &       31.68  &       35.61  &       35.60  \\
									 & VNLB $n_t = 3$ &       34.45  &       32.90  &       32.15  &       35.89  &       36.12  \\
									 & VNLB $n_t = 5$ & \best{34.59} & \best{33.02} & \best{32.27} & \best{35.90} & \best{36.12} \\\hline
%									                                                                                           
		\multirow{5}{*}{$40$} & V-BM4D-np      &       30.42  &       29.29  &       28.65  &       31.02  &       31.64  \\
		                      & VNLB $n_t = 0$ &       30.55  &       29.41  &       28.66  &       31.78  &       31.86  \\
									 & VNLB $n_t = 3$ & \best{31.02} & \best{29.73} & \best{29.03} & \best{31.88} & \best{31.92} \\
									 & VNLB $n_t = 5$ & \best{31.06} & \best{29.74} & \best{29.08} &       31.70  &       31.74  \\\hline
	\end{tabular}
	\end{center}
	\caption{PSNRs obtained for the five color sequences from the Middlebury
	dataset \cite{middleburyOflow}. See text for details.}
	\label{tab:psnr}
\end{table}

\section{Results}
\label{sec:results}

In this section we present preliminary results obtained with the proposed
method on the classic color test sequences \emph{tennis}, \emph{coastguard}, \emph{foreman},
\emph{bus}. In order to measure the effect of the additional temporal
dimension, we tested our method considering temporal search ranges of $1, 3$ and $5$ frames.
The results are shown in Table \ref{tab:psnr}. The proposed method is labeled VNLB.
For these sequences, the best results were obtained with
$n_t = 5$ (two frames before and after the frame of the current patch). Larger 
values of $n_t$ do not necessarily lead to better results. One possible reason
for that is that our search does not take motion into account. As a
consequence, in the presence of motion, similar patches might exit of the
search range after a certain number of frames.

For comparison, we also show the result of V-BM3D and two versions of V-BM4D.
The method labeled V-BM4D-\cite{Maggioni2012} corresponds to the results reported
in \cite{Maggioni2012}. The result labeled V-BM4D-np was obtained using the implementation
available online \cite{bm4dcode}. This implementation provides three parameter
profiles of increasing quality and complexity: ``low complexity profile'', ``normal
profile'' and ``modified profile''. The results shown here were obtained with the
``normal profile'' which is the default. We have included this result, because
it has a computation time comparable to the one of our method. Running with a
single core in a Intel Xeon X7560 (2.27GHz) CPU, 
our current implementation takes on average $9s$ per frame. V-BM4D takes $12s$
per frame with the normal profile and three times more with the modified profile.

In terms of PSNR, the best results for these sequences is obtained by
V-BM4D-\cite{Maggioni2012}. Our method seems to do better for $\sigma = 10$,
and for the bus sequence, and has problems with the tennis sequence. For
$\sigma = 20$ and $40$ our method performs similar to V-BM3D (except for the
tennis sequence).

We also show quantitative results obtained in for some sequences from the
optical flow Middlebury dataset (the sequences have 8 frames each), and compare
agaist V-BM4D-np. For these sequences, the proposed method outpeforms V-BM4D-np.

For a qualitative analysis we show in Figure \ref{fig:results} results obtained
with nonlocal Bayes (setting $n_t = 5$) and V-BM4D-np. Interestingly, for $\sigma = 20$
and $40$, V-BM4D-np is able to better recover the wallpaper texture in tennis,
but does worse than VNLB for the foliage texture of the trees in bus. 
%One
%plausible reason for this is that the spatial bi-orthogonal wavelets and
%DCT transforms used by BM4D are very well suited to the structured pattern of the
%wallpaper.
For high levels of noise, the wallpaper texture is masked by the noise. 
It is possible that when comparing 2D patches the noise dominates in the
comparison. Using spatio-temporal volumes reduces the distance noise,
allowing to find similar patches with the same regular texture pattern.

For $\sigma = 40$ the VNLB method exhibits some noise in flat or over-smoothed
regions (e.g. wallpaper in tennis sequence). It seems that the
Wiener filter of eq. \eqref{eq:map} is not aggressive enough for this noise level.

% \textcolor{red}{ 
% An important aspect of the quality of any video processing algorithm is the 
% temporal consistency of the result. The proposed method does not enforce
% temporal consistency. To visualize that we compute the absolute value of the 
% time difference between two successive frames of the estimated video:
% \[d(x,t) = \|\widetilde{u}(x,t) - \widetilde{u}(x,t+1)\|.\]
% Figure shows the results obtained by averaging $d(x,t)$ for four consecutive
% frames in the tennis sequence for V-BM4D-np and VNLB, with $n_t =5$. Since the camera
% is static one should expect a low value of the difference in the walls and the table.
% The result of VNLB shows higher values than V-BM4D (in the figure the
% differences were computed between the luminance channel and the white
% represents a difference of 20 levels.}
% 
% \begin{figure}[thpb!]
% 	\begin{center}
% 		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_vnlb_s10.png}
% 		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_vnlb_s20.png}
% 		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_vnlb_s40.png}\\
% 		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_bm4d_s10.png}
% 		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_bm4d_s20.png}
% 		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_bm4d_s40.png}
% 	\end{center}
% 	\caption{\textcolor{red}{Temporal coherency of the denoising. Average absolute value of time difference
% 	between five successive frames of the denoising result for tennis  with
% 	$\sigma=20$ (the time difference was computed between the luminance
% 	channels). Top row corresponds to VNLB ($n_t =2$) and bottom
% 	V-BM4D-np. The columns correspond to noise of level $\sigma = 10, 20, 40$.
% 	Darker values means lower average time difference.}} \label{fig:time-diff}
% \end{figure}

% \begin{table}
% 	\begin{center}
% 	\renewcommand{\tabcolsep}{3mm}
% 	\renewcommand{\arraystretch}{1.3}
% 	\begin{tabular}{ c | c |c c c c}
% 		\hline
% 		\rule{0pt}{12pt}$\sigma$ & Method     & Tennis       & Coastguard   & Foreman      & Bus          \\\hline
% 		\multirow{5}{*}{$10$} & V-BM4D        & \best{36.42} & \best{37.27} &       37.92  & \best{36.23} \\
% 		                      & V-BM3D        &       36.04  &       36.82  &       37.52  &       34.96  \\
% 		                      & VNLB $n_t = 0$ &       32.13  &       33.75  &       34.60  &       32.71  \\
% 		                      & VNLB $n_t = 3$ &       35.12  &       37.20  &       37.89  &       36.14  \\
% 									 & VNLB $n_t = 5$ &       35.19  & \best{37.26} & \best{38.00} &       36.11  \\\hline
% %									 
% 		\multirow{5}{*}{$25$} & V-BM4D        & \best{32.88} & \best{33.61} & \best{34.62} & \best{32.27} \\
% 		                      & V-BM3D        &       32.54  &       33.39  &       34.49  &       31.03  \\
% 		                      & VNLB $n_t = 0$ &       30.58  &       32.47  &       33.44  &       31.26  \\
% 									 & VNLB $n_t = 3$ &       31.22  &       33.39  &       34.28  &       32.01  \\
% 		                      & VNLB $n_t = 5$ &       31.25  &       33.44  &       34.34  &       31.94  \\\hline
% %									 
% 		\multirow{5}{*}{$40$} & V-BM4D        & \best{29.52} & \best{30.00} & \best{31.30} & \best{28.32} \\
% 		                      & V-BM3D        &       29.20  &       29.99  &       31.17  &       27.34  \\
% 		                      & VNLB $n_t = 0$ &       27.24  &       28.55  &       29.74  &       27.37  \\
% 									 & VNLB $n_t = 3$ &       27.96  &       29.68  &       30.85  &       28.17  \\
% 									 & VNLB $n_t = 5$ &       28.02  &       29.76  &       30.94  &       28.14  \\\hline
% 	\end{tabular}
% 
% 	\bigskip
% 	\end{center}
% 	\caption{PSNR for sequences taken from the Middlebury optical flow benchmark.}
% \end{table}

\section{Conclusions}
\label{sec:conclusion}

We presented a Bayesian video denoising algorithm assuming a Gaussian model for similar patches. 
We show preliminary results and compare it with two methods from the
state-of-the-art, V-BM3D and V-BM4D.
The resulting method does not require motion estimation.%, and as such it shows
%lower temporal coherency than V-BM4D.
In terms of PSNR
the results obtained show state-of-the-art performance for low levels of noise.
For higher levels of noise the performance is comparable to V-BM3D and improves
over the default version of V-BM4D.

%
% ---- Bibliography ----
%

\bibliography{image_denoising.bib,video_denoising.bib}
\bibliographystyle{splncs03}

\end{document}

### 2015-05-04 doc/201504_acivs/figs/time_coherence_image.m

@@ -1,0 +1,28 @@
+v1 = mean(single(imread('/data/pablo/boucantrin/denoising/projects/video_nlbayes/results/vnlbayes/table_1ps5_2ps5_2wx37_2np93/tennis_s40_tr2/deno_121.png')),3);
+v2 = mean(single(imread('/data/pablo/boucantrin/denoising/projects/video_nlbayes/results/vnlbayes/table_1ps5_2ps5_2wx37_2np93/tennis_s40_tr2/deno_122.png')),3);
+v3 = mean(single(imread('/data/pablo/boucantrin/denoising/projects/video_nlbayes/results/vnlbayes/table_1ps5_2ps5_2wx37_2np93/tennis_s40_tr2/deno_123.png')),3);
+v4 = mean(single(imread('/data/pablo/boucantrin/denoising/projects/video_nlbayes/results/vnlbayes/table_1ps5_2ps5_2wx37_2np93/tennis_s40_tr2/deno_124.png')),3);
+v5 = mean(single(imread('/data/pablo/boucantrin/denoising/projects/video_nlbayes/results/vnlbayes/table_1ps5_2ps5_2wx37_2np93/tennis_s40_tr2/deno_125.png')),3);
+
+td1 = abs(v1 - v2) + ...
+      abs(v2 - v2) + ...
+      abs(v3 - v3) + ...
+      abs(v4 - v5) / 4;
+
+td1 = min(td1/20*255,255);
+
+u1 = mean(single(imread('/data/pablo/purple/dev/results/VBM4D/tennis_s40/deno_121.png')),3);
+u2 = mean(single(imread('/data/pablo/purple/dev/results/VBM4D/tennis_s40/deno_122.png')),3);
+u3 = mean(single(imread('/data/pablo/purple/dev/results/VBM4D/tennis_s40/deno_123.png')),3);
+u4 = mean(single(imread('/data/pablo/purple/dev/results/VBM4D/tennis_s40/deno_124.png')),3);
+u5 = mean(single(imread('/data/pablo/purple/dev/results/VBM4D/tennis_s40/deno_125.png')),3);
+
+td2 = abs(u1 - u2) + ...
+      abs(u2 - u2) + ...
+      abs(u3 - u3) + ...
+      abs(u4 - u5) / 4;
+
+td2 = min(td2/20*255,255);
+
+imwrite(uint8(td1),'time_diff_vnlb_s40.png');
+imwrite(uint8(td2),'time_diff_bm4d_s40.png');

### 2015-05-17 src/NlBayes/VideoNLBayes.cpp
Minor: output name of weights image

@@ -410,7 +410,7 @@ int runNlBayes(
 			VideoUtils::subBuildTight(subWeights, weight, p_prms1.boundary);
 
 			// Write to disk
-			weight.saveVideo("weight_step1_%03d.png", 1);
+			weight.saveVideo("wei1_%03d.png", 1);
 		}
 #endif
 
@@ -467,7 +467,7 @@ int runNlBayes(
 			VideoUtils::subBuildTight(subWeights, weight, p_prms1.boundary);
 
 			// Write to disk
-			weight.saveVideo("weight_step2_%03d.png", 1);
+			weight.saveVideo("wei2_%03d.png", 1);
 		}
 #endif
 	}

### 2015-05-17 doc/201505_vnbayes3d/slides_vnlb3d.tex
[doc] Add slides with results of VNLB3D

% \documentclass{beamer}
\documentclass[mathserif, 8pt]{beamer}

\mode<presentation> {
% \usetheme{Madrid}
%\usetheme{default}
\usetheme{Boadilla}
% \usecolortheme{beaver}
% \usecolortheme{rose}
}
% removes navigation symbols
\setbeamertemplate{navigation symbols}{}

\usepackage[english,activeacute]{babel}
\usepackage[english]{layout}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{pgf}
%\usepackage{movie15}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage[multidot]{grffile}
\usepackage{ucs}
% \usepackage[T1]{fontenc}
%\usepackage{subfigure}

% from rida's preamble
\usepackage{epsfig,xspace}
\usepackage{setspace}
\usepackage{threeparttable}
\usepackage{subfloat}
\usepackage{pstricks,pst-node}
\usepackage[normal,tight,center]{subfigure}
\usepackage{pifont}
\usepackage{multimedia}
%\usepackage{media9}
%\usepackage{enumitem}
%\usepackage{animate}
\usepackage{caption}
\usepackage{multirow}

% the following is used to bind frames with the same frame number
\usepackage{etoolbox}

\newcounter{multipleslide}

\makeatletter%
\newcommand{\multipleframe}{%
\setcounter{multipleslide}{\value{framenumber}}
\stepcounter{multipleslide}
\patchcmd{\beamer@@tmpl@footline}% <cmd>
	{\insertframenumber}% <search>
	{\themultipleslide}% <replace>
	{}% <success>
	{}% <failure>
}
\newcommand{\restoreframe}{%
\patchcmd{\beamer@@tmpl@footline}% <cmd>
	{\themultipleslide}% <search>
	{\insertframenumber}% <replace>
	{}% <success>
	{}% <failure>
\setcounter{framenumber}{\value{multipleslide}}%
}
\makeatother%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Running 'pdflatex --shell-escape...' will automatically recognize
% the eps files in the includegraphics and convert them to pdf.
% No file rename nor change to the document is needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{ifpdf}
\ifpdf
\DeclareGraphicsRule{.eps}{pdf}{.pdf}{`epstopdf #1}
\usepackage{epstopdf}
\epstopdfsetup{suffix=-\SourceExt-converted-to}
\pdfcompresslevel=0   %\pdfcompresslevel=9
\pdfcompresslevel0
\fi

% para poder incluir figuras .pdftex del xfig
\DeclareGraphicsRule{.pdftex}{pdf}{.pdftex}{}

\newcommand{\nada}[1]   {}

\newcommand{\best}[1]{\textbf{\textcolor{MyOrange}{#1}}}
\newcommand{\Best}[1]{\textbf{\textcolor{MyOrangeBrighter}{#1}}}

\newcommand{\ma}[1]{\boldsymbol{#1}}
\newcommand{\ie}{\textit{i.e.} }
\newcommand{\eg}{\textit{e.g.} }
\newcommand{\etal}{\textit{et al}. }
\newcommand{\tras}[1]{#1^{\mathrm{T}}}
\newcommand{\herm}[1]{#1^{\mathrm{H}}}
\newcommand{\con}[1]{#1^{\mathrm{*}}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\tech}[1]{\overline{#1}}
\newcommand{\nspace}{\!\!\!\!}
\newcommand{\nmbr}[1]{\oldstylenums{#1}}

\newcommand{\eps}{\varepsilon}
\newcommand{\R}{{\mathbb R}}
\newcommand{\Q}{{\mathbb Q}}
\newcommand{\N}{{\mathbb N}}
\newcommand{\Z}{{\mathbb Z}}
\newcommand{\C}{{\mathcal C}}
\renewcommand{\H}{{\mathcal H}}
\newcommand{\F}{{\mathcal F}}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\median}{median}

\definecolor{MyOrange}  {cmyk}{0,0.73,1.0,0}
\definecolor{MyOrangeBrighter}  {cmyk}{0,0.53,7.0,0}
\definecolor{MyGreen}   {cmyk}{1,0,1,0.0}

% Rida's colors and commands
\definecolor{Red}{rgb}{0.9,0.0,0.1}
\definecolor{Brown}{rgb}{0.55,0.27,0.1}
\definecolor{Brownie}{rgb}{0.75,0.27,0.1}
\definecolor{Yellow}{rgb}{1,1,0}
\definecolor{White}{rgb}{1,1,1}
\definecolor{formule}{rgb}{0.75,0.27,0.1}
\definecolor{formule}{rgb}{.7,1,0}
\definecolor{violet}{rgb}{0.7,0,.9}
\definecolor{darkgreen}{rgb}{0,.7,0}

%\newcommand{\reference}[1] {{\scriptsize \color{gray}  #1 }} 
\newcommand{\reference}[1] {{\color{gray}  #1 }} 
\newcommand{\rmk}[1]{{\color{Red} #1}}

%\theoremstyle{plain}\newtheorem{theorem}{Theorem}[chapter]
%\theoremstyle{plain}\newtheorem{proposition}{Proposition}[chapter]
%\theoremstyle{plain}\newtheorem{lemma}{Lemma}[chapter]
%\theoremstyle{definition}\newtheorem{definition}{Definition}[chapter]

% New definition of square root:
% it renames \sqrt as \oldsqrt
\let\oldsqrt\sqrt
% it defines the new \sqrt in terms of the old one
\def\sqrt{\mathpalette\DHLhksqrt}
\def\DHLhksqrt#1#2{%
\setbox0=\hbox{$#1\oldsqrt{#2\,}$}\dimen0=\ht0
\advance\dimen0-0.2\ht0
\setbox2=\hbox{\vrule height\ht0 depth -\dimen0}%
{\box0\lower0.4pt\box2}}

%gets rid of bottom navigation bars
% \setbeamertemplate{footline}[frame number]{}

%gets rid of navigation symbols
\setbeamertemplate{navigation symbols}{}

\title[NLB3D]{$\,$ \\ $\,$ \\ Preliminary results for NL-Bayes 3D}
\author[Pablo Arias]{May 11, 2015}
\institute[CMLA]{}
\date[]{}

%\author[Pablo Arias]{Pablo Arias$^*$, Vicent Caselles$^*$, Gabriele Facciolo$^\dagger$ \\ Rida Sadek$^*$, Guillermo Sapiro$^\ddagger$ \\ $\,$ \\  $\,$ \\ $\,$ \\ $\,$ \\
%\institute[UPF]{* Universitat Pompeu Fabra\\ $\dagger$ ENS Cachan \\ $\ddagger$ Duke University}

% \AtBeginSection[]  % "Beamer, do the following at the start of every section"
% {\begin{frame}<beamer>
% \frametitle{Outline} % make a frame titled "Outline"
% \tableofcontents[currentsection]  % show TOC and highlight current section
% \end{frame}}
%
% \AtBeginSubsection[]  % "Beamer, do the following at the start of every section"
% {\begin{frame}<beamer>
% \frametitle{Outline} % make a frame titled "Outline"
% \tableofcontents[currentsection,currentsubsection]  % show TOC and highlight current section
% \end{frame}}

\graphicspath{{./figures/}}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\section{Introduction}

\begin{frame}{Introduction}

	\begin{center}
	Experiments on 5 sequences of the Middlebury optical flow dataset:

	\bigskip

	\emph{Army}, \\
	\emph{DogDance}, \\
	\emph{Evergreen}, \\
	\emph{Mequon}, \\
	\emph{Walking},

	\bigskip

	with white additive Gaussian noise of

	\bigskip

	$\sigma = 10$, \\ 
	$\sigma = 20$, \\ 
	$\sigma = 40$.
	\end{center}

\end{frame}

\begin{frame}{Parameters}
	\begin{center}

	\begin{tabular}{l | c c | c c | c c }
		& \multicolumn{2}{c|}{$\sigma = 10$} 
		& \multicolumn{2}{c|}{$\sigma = 20$} 
		& \multicolumn{2}{c}{$\sigma = 40$} \\
		                            & 1st  & 2nd  & 1st  & 2nd  & 1st  & 2nd \\\hline\hline
		Patch size (spatial)        &  5   &   5  &  5   &   5  &  5   &   5 \\
		Number of patches           & 375  & 375  & 375  & 375  & 375  & 375 \\
		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
		Spatial search window       & 13   & 37   & 37   & 37   & 37   & 37  \\
		Temporal search range       & 5    & 5    & 5    & 5    & 5    & 5   \\\hline
		Beta                        & 1    & 1.2  & 1    & 1.2  & 1    & 1.2 \\\hline
	\end{tabular}

	\bigskip
	\bigskip
	\bigskip

	We consider varying the temporal size of the patch.\\ All other parameters are kept constant.

	\end{center}
\end{frame}

\multipleframe
\begin{frame}{PSNRs of basic estimates}

	\begin{center}
	{\tiny
	\renewcommand{\tabcolsep}{2mm}
	\renewcommand{\arraystretch}{1.0}
	\begin{tabular}{ c | l |c c c c c}
		% NOTE: These results were obtained with the ACIVS paramter set. These
		% parameters were tuned to the DERF database, but perform a little worse in
		% the Middleburry sequences.
		\hline
		\rule{0pt}{6pt}$\sigma$ & Method           & Army & DogDance & Evergreen & Mequon & Walking  \\\hline
		\multirow{5}{*}{$10$} & V-BM4D-np        & \best{37.48} & \best{35.60} & \best{35.29} & \best{37.89} & \best{38.67} \\%\cline{2-7}
%		                      & VNLB2D $n_t = 0$ &       34.98  &       34.03  &       33.60  &       35.93  &       36.19  \\%\cline{2-7}
%		                      & VNLB2D $n_t = 1$ &       36.49  &       35.02  &       34.56  &       37.65  &       38.06  \\%\cline{2-7}
		                      & VNLB2D $n_t = 5$ &       36.66  &       35.10  &       34.64  &       37.74  &       38.30  \\
		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
		                      & VNLB3D $s_t = 2$ &       37.66  &       35.52  &       35.34  &       37.68  &       38.53  \\
		                      & VNLB3D $s_t = 3$ &       37.60  &       35.57  &       35.33  &       37.37  &       38.19  \\
		                      & VNLB3D $s_t = 4$ &       37.22  &       35.38  &       35.17  &       36.96  &       37.69  \\\hline
%
		\multirow{5}{*}{$20$} & V-BM4D-np        & \best{32.24} & \best{31.07} & \best{30.48} &       32.89  & \best{33.54} \\%\cline{2-7}
%		                      & VNLB2D $n_t = 0$ &       31.45  &       30.75  &       30.28  &       32.29  &       32.43  \\%\cline{2-7}
%		                      & VNLB2D $n_t = 1$ &       33.13  &       31.95  &       31.42  &       34.15  &       34.35  \\%\cline{2-7}
		                      & VNLB2D $n_t = 5$ &       33.38  &       32.09  &       31.56  &       34.39  &       34.64  \\
		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
		                      & VNLB3D $s_t = 2$ &       34.42  &       32.71  &       32.30  &       34.69  &       35.30  \\
		                      & VNLB3D $s_t = 3$ &       34.40  &       32.73  &       32.33  &       34.48  &       35.17  \\
		                      & VNLB3D $s_t = 4$ &       34.10  &       32.56  &       32.18  &       34.16  &       34.83  \\\hline
%
		\multirow{5}{*}{$40$} & V-BM4D-np        & \best{29.53} & \best{28.59} &       27.93  &       29.94  & \best{30.55} \\%\cline{2-7}
%		                      & VNLB2D $n_t = 0$ &       26.91  &       26.53  &       26.19  &       27.45  &       27.53  \\%\cline{2-7}
%		                      & VNLB2D $n_t = 1$ &       29.06  &       28.25  &       27.84  &       29.72  &       29.84  \\%\cline{2-7}
		                      & VNLB2D $n_t = 5$ &       29.44  &       28.52  &       28.10  &       30.09  &       30.24  \\
		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
		                      & VNLB3D $s_t = 2$ &       30.50  &       29.28  &       28.90  &       30.68  &       31.10  \\
		                      & VNLB3D $s_t = 3$ &       30.46  &       29.27  &       28.90  &       30.48  &       31.02  \\
		                      & VNLB3D $s_t = 4$ &       30.09  &       29.04  &       28.66  &       30.12  &       30.70  \\\hline
		\end{tabular}}

	\bigskip

	PSNRs obtained for the five color sequences from the Middlebury dataset.

	\end{center}

%	\begin{center}
%	\begin{tabular}{| c | c |c c c c c|}
%		\hline \hline
%		$\sigma$  & Method \textbackslash Video & Army & DogDance & Evergreen & Mequon & Walking \\\hline\hline
%		\multirow{5}{*}{$10$} & BM4D           & \best{37.48} & \best{35.60} & \best{35.29} & \best{37.89} & \best{38.67} \\%\cline{2-7}
%		                      & VNLB $W_t = 0$ &       14.30  &       18.98  &       15.87  &       16.83  &       16.28  \\%\cline{2-7}
%		                      & VNLB $W_t = 1$ &       36.21  &       34.86  &       34.50  &       37.16  &       37.54  \\%\cline{2-7}
%		                      & VNLB $W_t = 2$ &       36.77  &       35.22  &       34.82  &       37.69  &       38.20  \\\hline
%%
%		\multirow{5}{*}{$25$} & BM4D           & \best{32.24} & \best{31.07} & \best{30.48} &       32.89  & \best{33.54} \\%\cline{2-7}
%		                      & VNLB $W_t = 0$ &       30.13  &       29.51  &       29.07  &       30.91  &       30.00  \\%\cline{2-7}
%		                      & VNLB $W_t = 1$ &       31.92  &       30.85  &       30.33  &       32.86  &       33.00  \\%\cline{2-7}
%									 & VNLB $W_t = 2$ & \best{32.21} & \best{31.02} & \best{30.50} & \best{33.14} &       33.31  \\\hline
%%
%		\multirow{5}{*}{$40$} & BM4D           & \best{29.53} & \best{28.59} &       27.93  &       29.94  & \best{30.55} \\%\cline{2-7}
%		                      & VNLB $W_t = 0$ &       27.03  &       26.62  &       26.27  &       27.59  &       27.65  \\%\cline{2-7}
%		                      & VNLB $W_t = 1$ &       29.13  &       28.30  &       27.88  &       29.79  &       29.91  \\%\cline{2-7}
%									 & VNLB $W_t = 2$ & \best{29.50} & \best{28.55} & \best{28.13} & \best{30.15} &       30.29  \\\hline\hline
%	\end{tabular}
%
%	\bigskip
%	Results of VNLB corresponding to patch sizes of $5$ in both steps.\\The rest of parameters are the default ones.
%	\end{center}

\end{frame}

\begin{frame}{PSNRs of final estimates}

	\begin{center}
	{\tiny
	\renewcommand{\tabcolsep}{2mm}
	\renewcommand{\arraystretch}{1.0}
	\begin{tabular}{ c | l |c c c c c}
		% NOTE: These results were obtained with the ACIVS paramter set. These
		% parameters were tuned to the DERF database, but perform a little worse in
		% the Middleburry sequences.
		\hline
		\rule{0pt}{6pt}$\sigma$ & Method        & Army & DogDance & Evergreen & Mequon & Walking  \\\hline
		\multirow{5}{*}{$10$} & V-BM4D-np        &       37.77  &       35.70  &       35.40  &       38.09  &       38.85  \\
%		                      & VNLB2D $n_t = 0$ &       36.90  &       35.42  &       34.84  &       38.43  &       38.86  \\
%		                      & VNLB2D $n_t = 3$ &       37.65  &       35.87  &       35.38  &       39.09  &       39.69  \\
		                      & VNLB2D $n_t = 5$ & \best{37.88} & \best{36.01} & \best{35.53} & \Best{39.20} & \best{39.74} \\
		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
		                      & VNLB3D $s_t = 2$ &       38.51  &       36.20  &       35.97  & \best{38.54} & \Best{39.79} \\
		                      & VNLB3D $s_t = 3$ &       38.73  & \Best{36.46} & \Best{36.19} &       38.31  & \Best{39.79} \\
		                      & VNLB3D $s_t = 4$ & \Best{39.05} & \Best{36.51} & \Best{36.27} & \best{38.54} & \Best{39.78} \\\hline
%
		\multirow{5}{*}{$20$} & V-BM4D-np        &       32.91  &       31.50  &       30.94  &       33.60  &       34.27  \\
%		                      & VNLB2D $n_t = 0$ &       33.77  &       32.44  &       31.68  &       35.61  &       35.60  \\
%		                      & VNLB2D $n_t = 3$ &       34.45  &       32.90  &       32.15  &       35.89  &       36.12  \\
		                      & VNLB2D $n_t = 5$ & \best{34.59} & \best{33.02} & \best{32.27} & \Best{35.90} & \best{36.12} \\
		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
		                      & VNLB3D $s_t = 2$ &       35.28  &       33.33  &       32.77  & \best{35.30} &       36.88  \\
		                      & VNLB3D $s_t = 3$ &       35.45  & \Best{33.54} &       33.05  &       35.05  & \Best{37.00} \\
		                      & VNLB3D $s_t = 4$ & \Best{35.82} & \Best{33.63} & \Best{33.18} &       35.12  & \Best{36.98} \\\hline
%
		\multirow{5}{*}{$40$} & V-BM4D-np        &       30.42  &       29.29  &       28.65  &       31.02  &       31.64  \\
%		                      & VNLB2D $n_t = 0$ &       30.55  &       29.41  &       28.66  &       31.78  &       31.86  \\
%		                      & VNLB2D $n_t = 3$ & \best{31.02} & \best{29.73} & \best{29.03} & \best{31.88} & \best{31.92} \\
		                      & VNLB2D $n_t = 5$ & \best{31.06} & \best{29.74} & \best{29.08} & \best{31.70} & \best{31.74} \\
		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
		                      & VNLB3D $s_t = 2$ &       32.12  &       30.59  &       29.91  & \Best{32.15} &       33.61  \\
		                      & VNLB3D $s_t = 3$ &       32.33  & \Best{30.82} &       30.20  &       31.89  & \Best{33.87} \\
		                      & VNLB3D $s_t = 4$ & \Best{32.40} & \Best{30.87} & \Best{30.33} &       31.28  & \Best{33.88} \\\hline
%
		\end{tabular}}

	\bigskip

	PSNRs obtained for the five color sequences from the Middlebury dataset.

	\end{center}

%	\begin{center}
%	\begin{tabular}{| c | c |c c c c c|}
%		% NOTE: These results were obtained with a set of experiments run in
%		order to tune the parametrs.
%		\hline \hline
%		$\sigma$  & Method \textbackslash Video & Army & DogDance & Evergreen & Mequon & Walking \\\hline\hline
%		\multirow{5}{*}{$10$} & BM4D           & \best{37.77} &       35.70  & \best{35.40} &       38.09  &       38.85  \\%\cline{2-7}
%		                      & VNLB $W_t = 0$ &       34.46  &       33.61  &       33.05  &       35.65  &       35.90  \\%\cline{2-7}
%		                      & VNLB $W_t = 1$ &       37.65  & \best{35.87} & \best{35.42} & \best{39.10} & \best{39.70} \\%\cline{2-7}
%		                      & VNLB $W_t = 2$ & \best{37.75} & \best{35.92} & \best{35.47} & \best{39.06} & \best{39.79} \\\hline
%%
%		\multirow{5}{*}{$25$} & BM4D           &       32.91  &       31.50  &       30.94  &       33.60  &       34.27  \\%\cline{2-7}
%		                      & VNLB $W_t = 0$ &       32.33  &       31.17  &       30.39  &       33.69  &       33.74  \\%\cline{2-7}
%		                      & VNLB $W_t = 1$ &       33.48  & \best{31.98} & \best{31.22} & \best{35.10} &       35.25  \\%\cline{2-7}
%		                      & VNLB $W_t = 2$ & \best{33.58} & \best{31.98} & \best{31.22} & \best{35.08} & \best{35.38} \\\hline
%%
%		\multirow{5}{*}{$40$} & BM4D           &       30.42  &       29.29  &       28.65  &       31.02  &       31.64  \\%\cline{2-7}
%		                      & VNLB $W_t = 0$ &       29.94  &       28.95  &       28.24  &       30.98  &       30.95  \\%\cline{2-7}
%		                      & VNLB $W_t = 1$ &       31.36  &       29.96  & \best{29.19} & \best{32.70} &       32.71  \\%\cline{2-7}
%		                      & VNLB $W_t = 2$ & \best{31.55} & \best{30.01} & \best{29.24} & \best{32.75} & \best{32.94} \\\hline\hline
%	\end{tabular}
%
%	\bigskip
%	Results of VNLB corresponding to patch sizes of $5$ in both steps.\\The rest of parameters are the default ones.
%	\end{center}

\end{frame}
\restoreframe

\multipleframe
\begin{frame}{PSNRs of final estimates}
	\begin{center}
		{\tiny
		\renewcommand{\tabcolsep}{3mm}
		\renewcommand{\arraystretch}{1.0}
		\begin{tabular}{ c | l |c c c c}
			\hline
			\rule{0pt}{6pt}$\sigma$ & Method             & Tennis       & Coastguard   & Foreman      & Bus          \\\hline
			\multirow{5}{*}{$10$} & V-BM4D [Maggioni'12] & \best{36.42} & \best{37.27} &       37.92  &       36.23  \\
			                      & V-BM4D-mp            &       35.90  &       36.30  &       37.21  &       35.38  \\
			                      & V-BM4D-np            &       35.56  &       36.20  &       36.90  &       35.09  \\
			                      & V-BM3D               &       36.04  &       36.82  &       37.52  &       34.96  \\
%			                      & VNLB $n_t = 0$       &       34.43  &       36.70  &       37.21  &       35.58  \\
%			                      & VNLB $n_t = 3$       &       35.04  &       37.19  &       37.88  &       36.19  \\
			                      & VNLB $n_t = 5$       &       35.28  & \best{37.30} & \best{38.11} & \best{36.37} \\
			                      & VNLB3D $s_t = 1$     &       todo   &       todo   &       todo   &       todo   \\
			                      & VNLB3D $s_t = 2$     &       35.86  &       37.81  &       33.60  &       36.24  \\
			                      & VNLB3D $s_t = 3$     &       36.28  &       38.16  &       33.86  &       36.42  \\
			                      & VNLB3D $s_t = 4$     &       36.49  &       38.32  &       34.05  &       36.56  \\\hline
%
			\multirow{5}{*}{$20$} & V-BM4D [Maggioni'12] & \best{32.88} & \best{33.61} & \best{34.62} & \best{32.27} \\
			                      & V-BM4D-mp            &       31.98  &       32.44  &       33.70  &       31.34  \\
			                      & V-BM4D-np            &       31.67  &       32.24  &       33.34  &       30.95  \\
			                      & V-BM3D               &       32.54  &       33.39  &       34.49  &       31.03  \\
%			                      & VNLB $n_t = 0$       &       30.65  &       32.70  &       33.64  &       31.39  \\
%			                      & VNLB $n_t = 3$       &       31.26  &       33.35  &       34.25  &       32.11  \\
			                      & VNLB $n_t = 5$       &       31.49  & \best{33.55} &       34.45  & \best{32.35} \\
			                      & VNLB3D $s_t = 1$     &       todo   &       todo   &       todo   &       todo   \\
			                      & VNLB3D $s_t = 2$     &       32.15  &       34.08  &       32.27  &       32.23  \\
			                      & VNLB3D $s_t = 3$     &       32.67  &       34.34  &       32.58  &       32.47  \\
			                      & VNLB3D $s_t = 4$     &       32.94  &       34.48  &       32.73  &       32.63  \\\hline
%
			\multirow{5}{*}{$40$} & V-BM4D [Maggioni'12] & \best{29.52} & \best{30.00} & \best{31.30} &       28.32  \\
			                      & V-BM4D-mp            &       28.14  &       28.73  &       30.09  &       27.44  \\
			                      & V-BM4D-np            &       27.97  &       28.43  &       29.69  &       27.02  \\
			                      & V-BM3D               &       29.20  & \best{29.99} &       31.17  &       27.34  \\
%			                      & VNLB $n_t = 0$       &       27.43  &       28.88  &       30.15  &       27.60  \\
%			                      & VNLB $n_t = 3$       &       27.97  &       29.60  &       30.72  &       28.23  \\
			                      & VNLB $n_t = 5$       &       28.11  &       29.78  &       30.82  & \best{28.40} \\
			                      & VNLB3D $s_t = 1$     &       todo   &       todo   &       todo   &       todo   \\
			                      & VNLB3D $s_t = 2$     &       28.83  &       30.64  &       30.61  &       28.47  \\
			                      & VNLB3D $s_t = 3$     &       29.28  &       30.96  &       30.84  &       28.71  \\
			                      & VNLB3D $s_t = 4$     &       29.53  &       31.10  &       30.95  &       28.87  \\\hline
		\end{tabular}}

% Command to print rounded psnrs
% for i in $(cat bus_s40_pt*/measures | grep PSNR_final | sed "s/^-PSNR_final\ =\ "//); do  echo "scale=2;(((10^2)*$i)+0.5)/(10^2)" | bc; done

		\bigskip

		PSNRs obtained for the four classic color test sequences.
	\end{center}
\end{frame}
\restoreframe

\begin{frame}{Computation time}

	Computations performed in \texttt{boucantrin} server, using 8 CPU cores.\\
	For CIF (352x288) RGB videos, with $\sigma = 40$:

	\bigskip

	\begin{center}
	\begin{tabular}{r | c c c c}
		$p_t$ & 1 & 2 & 3 & 4 \\
		$s/\textnormal{frame}$ & x & 7 & 15 & 30 \\
	\end{tabular}
	\end{center}

	\vspace{2cm}

	For example, with $p_t = 4$, it takes 2.5 hours ($\times 8$ cores) for 300 CIF frames!

\end{frame}
% 
%

\end{document}

### 2015-05-25 src/NlBayes/NlBayes.cpp
CMake links with CBLAS & LAPACKE. Removed video_NLMeans, the original NlBayes and old stuff from branch.

@@ -1,860 +1,0 @@
-/*
- * Copyright (c) 2013, Marc Lebrun <marc.lebrun.ik@gmail.com>
- * All rights reserved.
- *
- * This program is free software: you can use, modify and/or
- * redistribute it under the terms of the GNU General Public
- * License as published by the Free Software Foundation, either
- * version 3 of the License, or (at your option) any later
- * version. You should have received a copy of this license along
- * this program. If not, see <http://www.gnu.org/licenses/>.
- */
-
-/**
- * @file NlBayes.cpp
- * @brief NL-Bayes denoising functions
- *
- * @author Marc Lebrun <marc.lebrun.ik@gmail.com>
- **/
-
-#include <iostream>
-#include <stdlib.h>
-#include <algorithm>
-#include <math.h>
-
-#include "NlBayes.h"
-#include "LibMatrix.h"
-#include "../Utilities/LibImages.h"
-#include "../Utilities/Utilities.h"
-
-#ifdef _OPENMP
-#include <omp.h>
-#endif
-
-using namespace std;
-
-/**
- * @brief Initialize Parameters of the NL-Bayes algorithm.
- *
- * @param o_paramStep1 : will contain the nlbParams for the first step of the algorithm;
- * @param o_paramStep2 : will contain the nlbParams for the second step of the algorithm;
- * @param p_sigma : standard deviation of the noise;
- * @param p_imSize: size of the image;
- * @param p_useArea1 : if true, use the homogeneous area trick for the first step;
- * @param p_useArea2 : if true, use the homogeneous area trick for the second step;
- * @param p_verbose : if true, print some informations.
- *
- * @return none.
- **/
-void initializeNlbParameters(
-	nlbParams &o_paramStep1
-,	nlbParams &o_paramStep2
-,	const float p_sigma
-,	const ImageSize &p_imSize
-,	const bool p_useArea1
-,	const bool p_useArea2
-,	const bool p_verbose
-){
-	//! Standard deviation of the noise
-	o_paramStep1.sigma = p_sigma;
-	o_paramStep2.sigma = p_sigma;
-
-	//! Size of patches
-	if (p_imSize.nChannels == 1) {
[…]

### 2015-05-25 src/NlBayes/VideoNLMeans.cpp

@@ -1,1127 +1,0 @@
-/*
- * Original work Copyright (c) 2013, Marc Lebrun <marc.lebrun.ik@gmail.com>
- * Modified work Copyright (c) 2014, Pablo Arias <pariasm@gmail.com>
- * All rights reserved.
- *
- * This program is free software: you can use, modify and/or
- * redistribute it under the terms of the GNU General Public
- * License as published by the Free Software Foundation, either
- * version 3 of the License, or (at your option) any later
- * version. You should have received a copy of this license along
- * this program. If not, see <http://www.gnu.org/licenses/>.
- */
-
-/**
- * @file VideoNLBayes.cpp
- * @brief Video NL-Bayes denoising functions
- *
- * @author Marc Lebrun <marc.lebrun.ik@gmail.com>
- * @author Pablo Arias <pariasm@gmail.com>
- **/
-
-#include <stdexcept>
-#include <iostream>
-#include <stdlib.h>
-#include <algorithm>
-#include <math.h>
-
-#include "VideoNLMeans.h"
-#include "LibMatrix.h"
-#include "../Utilities/Utilities.h"
-
-#ifdef _OPENMP
-#include <omp.h>
-#endif
-
-#define IPOL_WEIGHTS
-#define STEP1_ONECHANNEL
-
-namespace VideoNLM
-{
-
-/**
- * @brief Initialize Parameters of the NL-Bayes algorithm.
- *
- * @param o_params   : will contain the nlbParams for the first step of the algorithm;
- * @param p_step     : select first or second step;
- * @param p_sigma    : standard deviation of the noise;
- * @param p_size     : size of the video;
- * @param p_flatArea : if true, use the homogeneous area trick for the first step;
- * @param p_verbose  : if true, print some informations.
- * @param p_timeSearchRagneFwd : temporal search range forwards.
- * @param p_timeSearchRagneBwd : temporal search range backwards.
- *
- * @return none.
- **/
-void initializeNlbParameters(
-	nlbParams &o_params
-,	const unsigned p_step
-,	const float p_sigma
-,	const VideoSize &p_size
-,	const bool p_flatArea
-,	const bool p_verbose
-,	const unsigned timeSearchRangeFwd
-,	const unsigned timeSearchRangeBwd
-){
[…]

### 2015-05-25 src/unit_tests/testLibVideo.cpp

@@ -1,152 +1,0 @@
-/*
- * Copyright (c) 2015, Pablo Arias <pariasm@gmail.com>
- * All rights reserved.
- *
- * This program is free software: you can use, modify and/or
- * redistribute it under the terms of the GNU General Public
- * License as published by the Free Software Foundation, either
- * version 3 of the License, or (at your option) any later
- * version. You should have received a copy of this license along
- * this program. If not, see <http://www.gnu.org/licenses/>.
- */
-
-#include <iostream>
-#include <stdio.h>
-#include <stdlib.h>
-#include <fstream>
-
-#include <string>
-#include <sstream>
-
-#include "Utilities.h"
-#include "LibVideo.h"
-
-/**
- * @file   testLibVideo.cpp
- * @brief  Executable file to test libVideo
- *
- *
- *
- * @author PABLO ARIAS  <pariasm@gmail.com>
- **/
-
-
-
-void print_video_size(const std::string& name, const Video_f32& vid)
-{
-	printf("%s", name.c_str());
-	printf("\tFrames: %d - Channels: %d - Height: %d - Width %d\n", 
-			vid.frames, vid.channels, vid.height, vid.width);
-}
-
-int main(int argc, char **argv)
-{
-	//! Check if there is the right call for the algorithm
-	if (argc != 6)
-	{
-		fprintf(stdout, "Usage: %s path-to-frames first-frame last-frame frame-step sigma\n", argv[0]);
-		return EXIT_FAILURE;
-	}
-
-	//! Get command line inputs
-	const char* i_video_path =    argv[1] ;
-	const int i_firstFrame = atoi(argv[2]);
-	const int i_lastFrame  = atoi(argv[3]);
-	const int i_frameStep  = atoi(argv[4]);
-	const int i_sigma      = atoi(argv[5]);
-
-	//! Create empty video
-	Video_f32 vid1;
-	print_video_size("empty video", vid1);
-
-	//! Save video / should do nothing!
-	vid1.saveVideo("/tmp/vid1_empty_%02d.png",i_firstFrame, i_frameStep);
-
-	//! Load a video through loadVideo 
[…]

### 2015-05-25 src/unit_tests/testVideoNLMeans.cpp

@@ -1,502 +1,0 @@
-/*
- * Copyright (c) 2015, Pablo Arias <pariasm@gmail.com>
- * All rights reserved.
- *
- * This program is free software: you can use, modify and/or
- * redistribute it under the terms of the GNU General Public
- * License as published by the Free Software Foundation, either
- * version 3 of the License, or (at your option) any later
- * version. You should have received a copy of this license along
- * this program. If not, see <http://www.gnu.org/licenses/>.
- */
-
-#include <iostream>
-#include <stdio.h>
-#include <stdlib.h>
-#include <fstream>
-
-#include <string>
-#include <sstream>
-
-#include "Utilities.h"
-#include "VideoNLMeans.h"
-#include "cmd_option.h"
-
-#include <algorithm>
-
-/**
- * @file   testVideoNLMeans.cpp
- * @brief  Executable file to test VideoNLMeans
- *
- *
- *
- * @author PABLO ARIAS  <pariasm@gmail.com>
- **/
-
-void print_patch_from_group(
-	std::vector<std::vector<float> > &group3d
-,	VideoNLM::nlbParams prms
-,	unsigned idx
-){
-	const unsigned sP    = prms.sizePatch;
-	const unsigned nSimP = prms.nSimilarPatches;
-
-	assert(idx < nSimP);
-
-
-	for (unsigned hy = 0, k = 0; hy < sP; hy++)
-	{
-		for (unsigned hx = 0; hx < sP; hx++, k++)
-		{
-			printf("% 3f,% 3f,% 3f   ", group3d[0][k*nSimP + idx], 
-			                            group3d[1][k*nSimP + idx],
-			                            group3d[2][k*nSimP + idx]);
-		}
-		printf("\n");
-	}
-}
-
-void compare_patch_groups(
-	std::vector<std::vector<float> > &group3d
-,	std::vector<std::pair<float, unsigned> > &patch_dists
-,	VideoNLM::nlbParams prms
-,	VideoSize sz
-,	unsigned idx
-){
-	assert(idx < patch_dists.size());
-
-	const unsigned w  = sz.width;
-	const unsigned wh = sz.wh;
-
-	unsigned px, py, pt, pc;
-	sz.coords(patch_dists[0].second, px, py, pt, pc);
-
-	printf("patch %d from stack, anchored at: [%d, %d, %d]:\n", 0, px, py, pt);
[…]

### 2015-05-25 src/NlBayes/LibMatrix.h
computeBayesEstimateStep2 using only leading eigenvectors

@@ -80,4 +80,32 @@ void productMatrix(
 ,	const unsigned p_l
 );
 
+/**
+ * @brief Compute a specified number of eigenvectors and eigenvalues of a
+ * symmetric matrix.
+ *
+ * NOTES:
+ * - matrices are stored in column-major ordering
+ * - columns of input matrices are contiguous in memory
+ * - only the upper triangular triangular part of o_mat is used 
+ * - the upper triangular part of o_mat is destroyed
+ * - the output o_U contains the eigenvectors as columns, and is 
+ *   stored ini column-major ordering (i.e. it returns the eigenvectors
+ *   as rows in row-major ordering)
+ *
+ * @param i_mat: contains input matrix;
+ * @param p_n  : size of the matrix;
+ * @param p_r  : number of eigenvectors and eigenvalues.
+ * @param o_S  : vector with the r eigenvalues
+ * @param o_U  : matrix with the r eigenvectors
+ *
+ * @return none.
+ **/
+int matrixEigs(
+	std::vector<float> &i_mat
+,	const unsigned p_n
+,	const unsigned p_r
+,	std::vector<float> &o_S
+,	std::vector<float> &o_U
+);
 #endif // LIB_MATRIX_H_INCLUDED

### 2015-05-25 src/NlBayes/VideoNLBayes.h

@@ -68,11 +68,13 @@ struct nlbParams
  * @param covMatTmp: allocated memory. Used to process the Bayes estimate;
  * @param tmpMat: allocated memory. Used to process the Bayes estimate.
  **/
-struct matParams
+struct matWorkspace
 {
 	std::vector<float> group3dTranspose;
 	std::vector<float> baricenter;
 	std::vector<float> covMat;
+	std::vector<float> covEigVecs;
+	std::vector<float> covEigVals;
 	std::vector<float> covMatTmp;
 	std::vector<float> tmpMat;
 };
@@ -338,7 +340,7 @@ int computeHomogeneousAreaStep2(
  **/
 void computeBayesEstimateStep1(
 	std::vector<std::vector<float> > &io_group3d
-,	matParams &i_mat
+,	matWorkspace &i_mat
 ,	unsigned &io_nInverseFailed
 ,	nlbParams const& p_params
 ,	const unsigned p_nSimP
@@ -363,10 +365,39 @@ void computeBayesEstimateStep1(
  *
  * @return none.
  **/
-void computeBayesEstimateStep2(
+void computeBayesEstimateStep2_FR(
 	std::vector<float> &io_group3dNoisy
 ,	std::vector<float>  &i_group3dBasic
-,	matParams &i_mat
+,	matWorkspace &i_mat
+,	unsigned &io_nInverseFailed
+,	const VideoSize &p_imSize
+,	nlbParams const& p_params
+,	const unsigned p_nSimP
+);
+
+/**
+ * @brief Compute the Bayes estimation assuming a low rank covariance matrix.
+ *
+ * @param io_group3dNoisy: inputs all similar patches in the noisy image,
+ *                         outputs their denoised estimates.
+ * @param i_group3dBasic: contains all similar patches in the basic image.
+ * @param i_mat: contains :
+ *    - group3dTranspose: allocated memory. Used to contain the transpose of io_group3dNoisy;
+ *    - baricenter: allocated memory. Used to contain the baricenter of io_group3dBasic;
+ *    - covMat: allocated memory. Used to contain the covariance matrix of the 3D group;
+ *    - covMatTmp: allocated memory. Used to process the Bayes estimate;
+ *    - tmpMat: allocated memory. Used to process the Bayes estimate;
+ * @param io_nInverseFailed: update the number of failed matrix inversion;
+ * @param p_imSize: size of the image;
[…]

### 2015-05-25 src/NlBayes/LibMatrix.cpp
computeBayesEstimateStep2 using only leading eigenvectors

@@ -18,12 +18,14 @@
  * @author Marc Lebrun <marc.lebrun.ik@gmail.com>
  **/
 
- #include "LibMatrix.h"
+#include "LibMatrix.h"
 #include <iostream>
- #include <math.h>
- #include <stdlib.h>
+#include <cmath>
+#include <cstdlib>
+#include <cstdio>
+#include <lapacke.h>
 
- using namespace std;
+using namespace std;
 
 /**
  * @brief Invert (in place) a symmetric real matrix, V -> Inv(V).
@@ -177,4 +179,71 @@ void productMatrix(
 			o_mat[i + j * p_l] = z;
 		}
 	}
+}
+
+/**
+ * @brief Compute a specified number of eigenvectors and eigenvalues of a
+ * symmetric matrix.
+ *
+ * NOTES:
+ * - matrices are stored in column-major ordering
+ * - columns of input matrices are contiguous in memory
+ * - only the upper triangular triangular part of o_mat is used 
+ * - the upper triangular part of o_mat is destroyed
+ * - the output o_U contains the eigenvectors as columns, and is 
+ *   stored ini column-major ordering (i.e. it returns the eigenvectors
+ *   as rows in row-major ordering)
+ *
+ * @param i_mat: contains input matrix;
+ * @param p_n  : size of the matrix;
+ * @param p_r  : number of eigenvectors and eigenvalues.
+ * @param o_S  : vector with the r eigenvalues
+ * @param o_U  : matrix with the r eigenvectors
+ *
+ * @return none.
+ **/
+int matrixEigs(
+	vector<float> &i_mat
+,	const unsigned p_n
+,	const unsigned p_r
+,	vector<float> &o_S
+,	vector<float> &o_U
+){
+	// set parameters for LAPACKE SSYEV function
+	// SSYEVX: Single SYmmetric EigenValues and eigenvectors eXpert
+	lapack_int m;          //< total values of eigenvalues found
+
+	o_S.resize(p_n);       //< array of dimension n. The first m entries 
+	                       //< contain the eigenvalues found in ascending order.
+
+	o_U.resize(p_n*p_r);   //< the first m columns contain the output eigenvectors
+
+	lapack_int lda = p_n;  //< leading dimension for input matrix
+	lapack_int ldu = p_n;  //< leading dimension for output eigenvectors matrix
+
+	lapack_int ifail[p_n]; //< if jobz == 'V' and info > 0, then ifail contains
[…]

### 2015-05-26 doc/201505_vnbayes3d/slides_vnlb3d.tex

@@
 		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
-		                      & VNLB3D $s_t = 2$ &       37.66  &       35.52  &       35.34  &       37.68  &       38.53  \\
-		                      & VNLB3D $s_t = 3$ &       37.60  &       35.57  &       35.33  &       37.37  &       38.19  \\
-		                      & VNLB3D $s_t = 4$ &       37.22  &       35.38  &       35.17  &       36.96  &       37.69  \\\hline
+		                      & VNLB3D $s_t = 2$ &       37.68  &       35.57  &       35.34  &       37.72  &       38.54  \\
+		                      & VNLB3D $s_t = 3$ &       37.60  &       35.58  &       35.33  &       37.37  &       38.18  \\
+		                      & VNLB3D $s_t = 4$ &       37.20  &       35.38  &       35.16  &       36.99  &       37.67  \\\hline
 %
@@
 		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
-		                      & VNLB3D $s_t = 2$ &       34.42  &       32.71  &       32.30  &       34.69  &       35.30  \\
-		                      & VNLB3D $s_t = 3$ &       34.40  &       32.73  &       32.33  &       34.48  &       35.17  \\
-		                      & VNLB3D $s_t = 4$ &       34.10  &       32.56  &       32.18  &       34.16  &       34.83  \\\hline
+		                      & VNLB3D $s_t = 2$ &       34.43  &       32.70  &       32.29  &       34.73  &       35.30  \\
+		                      & VNLB3D $s_t = 3$ &       34.42  &       32.71  &       32.31  &       34.50  &       35.14  \\
+		                      & VNLB3D $s_t = 4$ &       34.09  &       32.53  &       32.15  &       34.16  &       34.79  \\\hline
 %
@@
 		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
-		                      & VNLB3D $s_t = 2$ &       30.50  &       29.28  &       28.90  &       30.68  &       31.10  \\
-		                      & VNLB3D $s_t = 3$ &       30.46  &       29.27  &       28.90  &       30.48  &       31.02  \\
-		                      & VNLB3D $s_t = 4$ &       30.09  &       29.04  &       28.66  &       30.12  &       30.70  \\\hline
+		                      & VNLB3D $s_t = 2$ &       30.49  &       29.26  &       28.88  &       30.66  &       31.07  \\
+		                      & VNLB3D $s_t = 3$ &       30.44  &       29.24  &       28.86  &       30.46  &       30.97  \\
+		                      & VNLB3D $s_t = 4$ &       30.06  &       29.00  &       28.61  &       30.09  &       30.65  \\\hline
 		\end{tabular}}
@@
 		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
-		                      & VNLB3D $s_t = 2$ &       38.51  &       36.20  &       35.97  & \best{38.54} & \Best{39.79} \\
-		                      & VNLB3D $s_t = 3$ &       38.73  & \Best{36.46} & \Best{36.19} &       38.31  & \Best{39.79} \\
-		                      & VNLB3D $s_t = 4$ & \Best{39.05} & \Best{36.51} & \Best{36.27} & \best{38.54} & \Best{39.78} \\\hline
+		                      & VNLB3D $s_t = 2$ &       38.69  &       36.26  &       35.97  & \best{39.02} & \Best{39.95} \\
+		                      & VNLB3D $s_t = 3$ &       39.06  & \Best{36.48} & \Best{36.20} & \best{38.96} & \Best{39.97} \\
+		                      & VNLB3D $s_t = 4$ & \Best{39.17} & \Best{36.55} & \Best{36.29} &       38.86  & \Best{39.90} \\\hline
 %
@@
 %		                      & VNLB2D $n_t = 3$ &       34.45  &       32.90  &       32.15  &       35.89  &       36.12  \\
-		                      & VNLB2D $n_t = 5$ & \best{34.59} & \best{33.02} & \best{32.27} & \Best{35.90} & \best{36.12} \\
+		                      & VNLB2D $n_t = 5$ & \best{34.59} & \best{33.02} & \best{32.27} & \best{35.90} & \best{36.12} \\
 		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
-		                      & VNLB3D $s_t = 2$ &       35.28  &       33.33  &       32.77  & \best{35.30} &       36.88  \\
-		                      & VNLB3D $s_t = 3$ &       35.45  & \Best{33.54} &       33.05  &       35.05  & \Best{37.00} \\
-		                      & VNLB3D $s_t = 4$ & \Best{35.82} & \Best{33.63} & \Best{33.18} &       35.12  & \Best{36.98} \\\hline
+		                      & VNLB3D $s_t = 2$ &       35.55  &       33.37  &       32.78  & \Best{36.19} &       36.95  \\
+		                      & VNLB3D $s_t = 3$ &       35.94  & \Best{33.58} &       33.06  & \Best{36.13} & \Best{37.07} \\
+		                      & VNLB3D $s_t = 4$ & \Best{36.08} & \Best{33.65} & \Best{33.20} &       36.04  & \Best{37.05} \\\hline
 %
@@
 		                      & VNLB3D $s_t = 1$ &       todo   &       todo   &       todo   &       todo   &       todo   \\
-		                      & VNLB3D $s_t = 2$ &       32.12  &       30.59  &       29.91  & \Best{32.15} &       33.61  \\
-		                      & VNLB3D $s_t = 3$ &       32.33  & \Best{30.82} &       30.20  &       31.89  & \Best{33.87} \\
-		                      & VNLB3D $s_t = 4$ & \Best{32.40} & \Best{30.87} & \Best{30.33} &       31.28  & \Best{33.88} \\\hline
+		                      & VNLB3D $s_t = 2$ &       32.60  &       30.63  &       29.91  & \Best{33.00} &       33.63  \\
+		                      & VNLB3D $s_t = 3$ &       33.03  & \Best{30.87} &       30.20  & \Best{33.05} & \Best{33.89} \\
+		                      & VNLB3D $s_t = 4$ & \Best{33.17} & \Best{30.95} & \Best{30.34} & \Best{33.00} & \Best{33.95} \\\hline
 %
@@
 			                      & VNLB3D $s_t = 1$     &       todo   &       todo   &       todo   &       todo   \\
-			                      & VNLB3D $s_t = 2$     &       35.86  &       37.81  &       33.60  &       36.24  \\
-			                      & VNLB3D $s_t = 3$     &       36.28  &       38.16  &       33.86  &       36.42  \\
-			                      & VNLB3D $s_t = 4$     &       36.49  &       38.32  &       34.05  &       36.56  \\\hline
+			                      & VNLB3D $s_t = 2$     &       35.95  &       37.81  &       38.46  &       36.31  \\
+			                      & VNLB3D $s_t = 3$     &       36.34  &       38.16  &       38.74  &       36.50  \\
+			                      & VNLB3D $s_t = 4$     & \Best{36.54} & \Best{38.31} & \Best{38.86} & \Best{36.60} \\\hline
 %
-			\multirow{5}{*}{$20$} & V-BM4D [Maggioni'12] & \best{32.88} & \best{33.61} & \best{34.62} & \best{32.27} \\
+			\multirow{5}{*}{$20$} & V-BM4D [Maggioni'12] & \Best{32.88} & \best{33.61} & \best{34.62} & \best{32.27} \\
 			                      & V-BM4D-mp            &       31.98  &       32.44  &       33.70  &       31.34  \\
@@
 			                      & VNLB3D $s_t = 1$     &       todo   &       todo   &       todo   &       todo   \\
-			                      & VNLB3D $s_t = 2$     &       32.15  &       34.08  &       32.27  &       32.23  \\
-			                      & VNLB3D $s_t = 3$     &       32.67  &       34.34  &       32.58  &       32.47  \\
-			                      & VNLB3D $s_t = 4$     &       32.94  &       34.48  &       32.73  &       32.63  \\\hline
+			                      & VNLB3D $s_t = 2$     &       32.19  &       34.08  &       34.98  &       32.25  \\
+			                      & VNLB3D $s_t = 3$     &       32.69  &       34.34  &       35.33  &       32.49  \\
+			                      & VNLB3D $s_t = 4$     & \Best{32.96} & \Best{34.48} & \Best{35.48} & \Best{32.66} \\\hline
 %
@@
 			                      & VNLB3D $s_t = 1$     &       todo   &       todo   &       todo   &       todo   \\
-			                      & VNLB3D $s_t = 2$     &       28.83  &       30.64  &       30.61  &       28.47  \\
-			                      & VNLB3D $s_t = 3$     &       29.28  &       30.96  &       30.84  &       28.71  \\
-			                      & VNLB3D $s_t = 4$     &       29.53  &       31.10  &       30.95  &       28.87  \\\hline
+			                      & VNLB3D $s_t = 2$     &       28.89  &       30.63  &       31.67  &       28.48  \\
+			                      & VNLB3D $s_t = 3$     &       29.37  &       30.95  &       32.07  &       28.72  \\
+			                      & VNLB3D $s_t = 4$     & \Best{29.64} & \Best{31.09} & \Best{32.26} & \Best{28.88} \\\hline
 		\end{tabular}}
-
 % Command to print rounded psnrs

### 2015-05-27 src/NlBayes/VideoNLBayes.h
Number of eigenvecs is a command line parameter. Matrix product in LibMatrix. Skip pixels in x and y directions.

@@ -13,7 +13,6 @@
 #ifndef VIDEO_NL_BAYES_H_INCLUDED
 #define VIDEO_NL_BAYES_H_INCLUDED
 
-//#include "../Utilities/LibVideo.h"
 #include "../Utilities/LibVideoT.hpp"
 #include "../Utilities/Utilities.h"
 
@@ -28,7 +27,7 @@ namespace VideoNLB
  * @param nSimilarPatches: minimum number of similar patches wanted;
  * @param sizeSearchWindow: size of the search window around the reference patch;
  * @param boundary: must be > sizeSearchWindow. Boundary kept around sub-images when the image is
- *      subdivided for parallelization;
+ *        subdivided for parallelization;
  * @param offSet: step between two similar patches;
  * @param useHomogeneousArea: if true, use the homogeneous area trick;
  * @param gamma: threshold to detect homogeneous area;
@@ -36,7 +35,7 @@ namespace VideoNLB
  * @param tau: parameter used to determine similar patches;
  * @param isFirstStep: true if the first step of the algorithm is wanted;
  * @param doPasteBoost: if true, patches near denoised similar patches will not be used as reference
- *		patches;
+ *        patches;
  * @param verbose: if true, print informations.
  **/
 struct nlbParams
@@ -46,12 +45,13 @@ struct nlbParams
 	unsigned sizePatchTime;    // user given
 	unsigned nSimilarPatches;  // depends on sigma, sizeSearchTimeRange (1 channel) or sizePatch (3 channels)
 	unsigned sizeSearchWindow; // depends on nSimilarPatches
-	unsigned sizeSearchTimeRangeFwd; //< VIDEO how many forward  frames in search cube
-	unsigned sizeSearchTimeRangeBwd; //< VIDEO how many backward frames in search cube
+	unsigned sizeSearchTimeRangeFwd; // how many forward  frames in search cube
+	unsigned sizeSearchTimeRangeBwd; // how many backward frames in search cube
 	unsigned boundary;         // depends on sizeSearchWindow
 	unsigned offSet;           // depends on sizePatch
 	bool useHomogeneousArea;
 	float gamma;
+	unsigned rank;             // rank of covariance matrix
 	float beta;                // depends on sigma
 	float tau;                 // depends on sizePatch
 	bool isFirstStep;
@@ -103,6 +103,7 @@ void initializeNlbParameters(
[…]

### 2015-05-27 src/main_vnlb.cpp

@@ -47,7 +47,7 @@ int main(int argc, char **argv)
 	const string  final_path = clo_option("-deno" , "deno_%03d.png" , "> denoised sequence");
 	const string  basic_path = clo_option("-bsic" , "bsic_%03d.png" , "> basic denoised sequence");
 	const string   diff_path = clo_option("-diff" , "diff_%03d.png" , "> difference sequence");
-	// TODO: this should be determined automatically from the other outputs.
+	// TODO: these should be determined automatically from the other outputs.
 	const string   bias_path = clo_option("-bdeno", "bdeno_%03d.png", "> bias sequence");
 	const string bbasic_path = clo_option("-bbsic", "bbsic_%03d.png", "> bias basic sequence");
 	const string  bdiff_path = clo_option("-bdiff", "bdiff_%03d.png", "> bias difference sequence");
@@ -75,6 +75,8 @@ int main(int argc, char **argv)
 	const int patch_sizet2  = clo_option("-pt2", 1, "> Temporal patch size, step 2");
 	const int num_patches1  = clo_option("-np1",-1, "> Number of similar patches, step 1");
 	const int num_patches2  = clo_option("-np2",-1, "> Number of similar patches, step 2");
+	const int rank1         = clo_option("-r1" , 4, "> Rank or covariance matrix, step 1");
+	const int rank2         = clo_option("-r2" , 4, "> Rank or covariance matrix, step 2");
 
 	//! Only print parameters
 	if (print_prms)
@@ -94,6 +96,9 @@ int main(int argc, char **argv)
 		if (patch_sizex2  >= 0) VideoNLB::setSizePatch(prms2, tmp, (unsigned)patch_sizex2);;
 		if (num_patches1  >= 0) VideoNLB::setNSimilarPatches(prms1, (unsigned)num_patches1);
 		if (num_patches2  >= 0) VideoNLB::setNSimilarPatches(prms2, (unsigned)num_patches2);
+
+		prms1.rank = rank1;
+		prms2.rank = rank2;
 
 		VideoNLB::printNlbParameters(prms1);
 		VideoNLB::printNlbParameters(prms2);	
@@ -142,6 +147,10 @@ int main(int argc, char **argv)
 	if (patch_sizex2  >= 0) VideoNLB::setSizePatch(prms2, noisy.sz, (unsigned)patch_sizex2);;
[…]

### 2015-07-10 doc/201505_vnbayes3d/slides_vnlb3d.tex
[doc] Added rank vs. nsim tables to vnlbayes internal slides

@@
 
-\title[NLB3D]{$\,$ \\ $\,$ \\ Preliminary results for NL-Bayes 3D}
-\author[Pablo Arias]{May 11, 2015}
+\title[VNLB]{$\,$ \\ $\,$ \\ Preliminary results for Video NL-Bayes}
+\author[Pablo Arias]{V0: May 11, 2015\\V1: July 10, 2015}
 \institute[CMLA]{}
@@
 
+\begin{frame}{Update}
+
+	We now present updated results. Relevant commits since the original results: 
+	\begin{description}
+		\item[{\tt 9f65b63}] Three implementations of low-rank Bayesian estimation in the first stage.
+		\item[{\tt 40d8858}] Number of eigenvecs is a command line parameter. Skip pixels in x and y directions.
+		\item[{\tt 289505c}] computeBayesEstimateStep2 using only leading eigenvectors
+	\end{description}
+
+	\bigskip
+
+	\bigskip
+
+	\bigskip
+
+	Before presenting definite tables of PSNR, we will first analyze the new
+	parameters: the rank of the covariance matrix in the first and second stages.
+
+\end{frame}
+% 
+%
+
+\multipleframe
+\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
+
+	We set the following parameters fixed, and vary the rank and the number of similar
+	patches in the second step.
+
+	\begin{center}
+	\begin{tabular}{l | c c | c c | c c }
+		& \multicolumn{2}{c|}{$\sigma = 10$} 
+		& \multicolumn{2}{c|}{$\sigma = 20$} 
+		& \multicolumn{2}{c}{$\sigma = 40$} \\
+		                            & 1st  & 2nd  & 1st  & 2nd  & 1st  & 2nd \\\hline\hline
+		Patch size (spatial)        &  5   &   5  &  5   &   5  &  5   &   5 \\
+		Patch size (temporal)       &  4   &   4  &  4   &   4  &  4   &   4 \\
+		Number of patches           & 375  &      & 375  &      & 375  &     \\
+		Rank of cov. matrix         & full &      & full &      & full &     \\
+		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
+		Spatial search window       & 13   & 37   & 37   & 37   & 37   & 37  \\
+		Temporal search range       & 5    & 5    & 5    & 5    & 5    & 5   \\\hline
+		Beta                        & 1    & 1    & 1    & 1    & 1    & 1   \\\hline
+	\end{tabular}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_army.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_walking.eps}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_army.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_walking.eps}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_army.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_walking.eps}
+	\end{center}
+
+\end{frame}
+\restoreframe
+
+\multipleframe
+\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_army.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_walking.eps}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_army.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_walking.eps}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_army.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_walking.eps}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{Conclusions - rank vs. number of patches, stage 2}
+
+	From the preceeding results, we conclude that a good trade-off between PSNR and running time
+	is given by:
+
+	\[\text{rank} = 16 \quad\text{ and }\quad n_{\text{sim}} = 160.\]
+
+\end{frame}
+\restoreframe
+
+\multipleframe
+\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
+
+	We set the following parameters fixed, and vary the rank and the number of similar
+	patches in the second step.
+
+	\begin{center}
+	\begin{tabular}{l | c c | c c | c c }
+		& \multicolumn{2}{c|}{$\sigma = 10$} 
+		& \multicolumn{2}{c|}{$\sigma = 20$} 
+		& \multicolumn{2}{c}{$\sigma = 40$} \\
+		                            & 1st  & 2nd  & 1st  & 2nd  & 1st  & 2nd \\\hline\hline
+		Patch size (spatial)        &  5   &   5  &  5   &   5  &  5   &   5 \\
+		Patch size (temporal)       &  4   &   4  &  4   &   4  &  4   &   4 \\
+		Number of patches           &      & 160  &      & 160  &      & 160 \\
+		Rank of cov. matrix         &      &  16  &      &  16  &      & 16  \\
+		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
+		Spatial search window       & 13   & 37   & 37   & 37   & 37   & 37  \\
+		Temporal search range       & 5    & 5    & 5    & 5    & 5    & 5   \\\hline
+		Beta                        & 1    & 1    & 1    & 1    & 1    & 1   \\\hline
+	\end{tabular}
+	\end{center}
+
+	\bigskip
+
+	\structure{In the following plots, the values of PSNR for the basic and
+		final estimates, obtained with the previous settings for the stage 1 (full
+		rank and $n_{\text{sim}} = 375$) are shown by two horizontal dashed
+		lines.}
+
+\end{frame}
+
+\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_army.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_walking.eps}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_army.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_walking.eps}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_army.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_walking.eps}
+	\end{center}
+
+\end{frame}
+\restoreframe
+
+\multipleframe
+\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_army.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_walking.eps}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_army.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_walking.eps}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
+
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_army.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_dogdance.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_evergreen.eps}\\
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_mequon.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_walking.eps}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{Conclusions - rank vs. number of patches, stage 1}
+	\begin{itemize}\itemsep=2cm
+		\item We can improve the basic estimate, but we cannot improve the final estimate.
+		\item The qualitative behaviour depends on the noise level.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Conclusions - rank vs. number of patches, stage 1}
+	For $\sigma = 40$:
+	\begin{itemize}\itemsep=.3cm
+		\item The basic and final PSNRs increase with $n_{\text{sim}}$.
+		\item For a fixed $n_{\text{sim}}$, the basic PSRN incease when the
+			rank decreases until $r = 8$, \textbf{but the final PSNR does not change!}
+		\item The basic estimate can improve substantially w.r.t. to the
+			full rank reference, but the final estimate cannot be improved.
+		\item Best basic results seem to be obtained with $n_{\text{sim}} = 
+			600$ and $r = 8$.
+		\item Best final results seem to be obtained with $n_{\text{sim}}\in
+			[300,600]$ and $r > 8$.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Conclusions - rank vs. number of patches, stage 1}
+	For $\sigma = 20$:
+	\begin{itemize}\itemsep=.3cm
+		\item Excluding $n_{\text{sim}} = 600$, for a fixed
+			$n_{\text{sim}}$, the basic PSRN inceases when the rank decreases
+			until $r = 8$ (and until $r = 12$ for $n_{\text{sim}} = 300$.
+			The final PSNR does not have a clear behaviour.
+		\item For fixed $r > 8$, increasing $n_{\text{sim}}$ is beneficial for the
+			basic estimate, but not for the final estimate.
+		\item The basic estimate can improve w.r.t. to the
+			full rank reference, but the final estimate cannot be improved.
+		\item Best basic results seem to be obtained with $n_{\text{sim}} = 
+			600$ and $r = 12$.
+		\item Best final results seem to be obtained with $n_{\text{sim}}=
+			160$ and $r = 12$, or $n_{\text{sim}}=
+			300$ and $r = 16$.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Conclusions - rank vs. number of patches, stage 1}
+	For $\sigma = 10$:
+	\begin{itemize}\itemsep=.3cm
+		\item Since the data has more details, one cannot model large sets of patches
+			with low rank covariances as before. Increasing $n_{\text{sim}}$ now can drops
+			the quality, and this happens earlier the lower the rank.
+		\item For a fixed $n_{\text{sim}}$, decreasing the rank does not
+			improve the basic PSRN any more.
+		\item The basic and final estimates have opposing behaviours w.r.t. $n_{\text{sim}}$.
+		\item Best basic results seem to be obtained with $n_{\text{sim}} > 
+			160$ and $r > 8$.
+		\item Best final results seem to be obtained with $n_{\text{sim}}<
+			300$ and $r > 4$.
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Conclusions - rank vs. number of patches, stage 1}
+	Based on this observations, we propose the following parameters:
+	\[r = 160\quad\quad n_{\text{sim}} = \max(15\sigma,cr).\]
+
+	Notes:
+	\begin{itemize}\itemsep=.3cm
+		\item The rank $r$ could be smaller, but there is not much difference in
+			computational time nor in PSNR. We therefore choose a more
+			conservative higher rank.
+		\item The linear relation $n_{\text{sim}} = 15\sigma$ comes from observing that
+			for good results are obtained at
+			\begin{center}
+				\begin{tabular}{l | c c c}
+					$\sigma$         &  10 &  20 &  40 \\ 
+					$n_{\text{sim}}$ & 150 & 300 & 600 
+				\end{tabular}
+			\end{center}
+		\item $c\geqslant1$ is a constant multiplying the rank. When $15\sigma$
+			is too small, we ignore the linear relation and take a fixed number of
+			patches which depend on the rank. \textbf{We should do more experiments
+			to determine an appropriate value for $c$. For the moment, we will choose
+         5.} With this choice,
+			\[
+				n_{\text{sim}} =
+				\left\{
+				\begin{array}{l l}
+					15\sigma & \text{if }\sigma \geqslant r/3\\
+					5r       & \text{if }\sigma < r/3
+				\end{array}
+				\right.
+			\]
+			For $r = 16$, $5r = 80$ and $r/3 \approx 5.33$.
+	\end{itemize}
+\end{frame}
+
+\restoreframe
+
 \end{document}

### 2015-07-10 tools/psnr_vs_rank_np_bars.m

@@ -1,30 +1,44 @@
 % load data
 
-basedir = '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_rank2_1ps5x5x4_2ps5x5x4_2wx37/';
+% basedir = '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_rank2_1ps5x5x4_2ps5x5x4_2wx37/';
+% ranks = [  4,   8,  12,  16,  20];
+% nsim  = [ 40,  80, 120, 160, 375];
 
+basedir2 = '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_rank2_1ps5x5x4_2ps5x5x4_2wx37/';
+basedir = '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_rank1_1ps5x5x4_2ps5x5x4_2wx37/';
 ranks = [  4,   8,  12,  16,  20];
-nsim  = [ 40,  80, 120, 160, 375];
+nsim  = [ 80, 120, 160, 300, 600];
 
-% PSNR point cloud plots
-seqs = {'army', 'dogdance', 'evergreen', 'mequon', 'walking'};
-sigmas = {'10', '20', '40'};
-
-ylims = [33,40;  % sigma 10
-         30,37;  % sigma 25
-         28,35]; % sigma 40
+ylims = [33,41;  % sigma 10
+         30,38;  % sigma 25
+         28,36]; % sigma 40
 
 ylimstime = [70,400;  % sigma 10
              70,400;  % sigma 25
              70,400]; % sigma 40
+
+% PSNR point cloud plots
+seqs = {'army', 'dogdance', 'evergreen', 'mequon', 'walking'};
+sigmas = {'10', '20', '40'};
 
 for i = 1:length(seqs),
 for p = 1:length(sigmas),
 
 	% plots of psnr
 	% rows in final indicate fixed rank, columns fixed num of patches
-	final = load([basedir 'table_psnr_' seqs{i} '_s' sigmas{p}]);
+	final = load([basedir 'table_fpsnr_' seqs{i} '_s' sigmas{p}]);
+	basic = load([basedir 'table_bpsnr_' seqs{i} '_s' sigmas{p}]);
 
[…]

### 2015-08-05 tools/compute_oflow_derivative.m
Tools developed for TIP paper

@@ -1,6 +1,6 @@
 % computes convective derivative of a result on a sequence of sintel database
 
-% add things to patch
+% add folders to path
 addpath ~/Work/denoising/projects/video_nlbayes3d/tools/
 addpath ~/Work/doctorado/codigo/algos/video_poisson/rida/vp_clean/matlab/paper_code
 addpath ~/Work/doctorado/codigo/algos/optical_flow/flow-code-matlab/               
@@ -8,11 +8,12 @@ addpath ~/Work/doctorado/codigo/algos/optical_flow/flow-code-matlab/
 % sequence name
 seq = 'bandage_1';
 sigma = '40';
-pt = '4';
+pt = '3';
 
 root_folder = '/media/pariasm/tera/funes/denoising/';
 
 % flow data folder
+orig_pat = [root_folder 'data/sintel_training/final/'      seq '/frame_%04d.png'];
 occl_pat = [root_folder 'data/sintel_training/occlusions/' seq '/frame_%04d.png'];
 flow_pat = [root_folder 'data/sintel_training/flow/'       seq '/frame_%04d.flo'];
 
@@ -23,20 +24,27 @@ vnlb_pat = [root_folder 'projects/video_nlbayes3d/results/vnlbayes/' ...
                         seq '_s' sigma '_pt' pt '/deno_%03d.png'];
 
 % load denoised sequence
+orig =    load_sequence(orig_pat,1,50);
 deno =    load_sequence(vnlb_pat,1,50);
 occl =    load_sequence(occl_pat,1,49);
 flow = readFlowSequence(flow_pat,1,50);
+
+% diff = deno - orig;
+%diff = orig;
+diff = deno;
 
 % compute convective derivative
 flow_x = squeeze(flow(:,:,1,:));
 flow_y = squeeze(flow(:,:,2,:));
 occl = 1 - occl/255;
 
-Dflow = convective_derivative(flow_x, flow_y, [], [], occl, [], 'forward');   
+%Dflow = convective_derivative(flow_x, flow_y, [], [], occl, [], 'forward');   
 
 % filter sequences
-for ch = 1:size(deno,3),
-	chnl = double(deno(:,:,ch,1:49));    
+for ch = 1:size(diff,3),
+	chnl = double(diff(:,:,ch,1:49));    
 	chnl = single(Dflow * chnl(:));
[…]

### 2015-08-05 tools/generate_cubes.sh

@@ -1,0 +1,61 @@
+#! /bin/bash
+
+./print_cube.sh Army 10 PSNR_final >> cube_fpsnr_army_s10
+./print_cube.sh Army 20 PSNR_final >> cube_fpsnr_army_s20
+./print_cube.sh Army 40 PSNR_final >> cube_fpsnr_army_s40
+
+./print_cube.sh DogDance 10 PSNR_final >> cube_fpsnr_dogdance_s10
+./print_cube.sh DogDance 20 PSNR_final >> cube_fpsnr_dogdance_s20
+./print_cube.sh DogDance 40 PSNR_final >> cube_fpsnr_dogdance_s40
+
+./print_cube.sh Evergreen 10 PSNR_final >> cube_fpsnr_evergreen_s10
+./print_cube.sh Evergreen 20 PSNR_final >> cube_fpsnr_evergreen_s20
+./print_cube.sh Evergreen 40 PSNR_final >> cube_fpsnr_evergreen_s40
+
+#./print_cube.sh Mequon 10 PSNR_final >> cube_fpsnr_mequon_s10
+#./print_cube.sh Mequon 20 PSNR_final >> cube_fpsnr_mequon_s20
+#./print_cube.sh Mequon 40 PSNR_final >> cube_fpsnr_mequon_s40
+
+./print_cube.sh Walking 10 PSNR_final >> cube_fpsnr_walking_s10
+./print_cube.sh Walking 20 PSNR_final >> cube_fpsnr_walking_s20
+./print_cube.sh Walking 40 PSNR_final >> cube_fpsnr_walking_s40
+
+./print_cube.sh Army 10 PSNR_basic >> cube_bpsnr_army_s10
+./print_cube.sh Army 20 PSNR_basic >> cube_bpsnr_army_s20
+./print_cube.sh Army 40 PSNR_basic >> cube_bpsnr_army_s40
+
+./print_cube.sh DogDance 10 PSNR_basic >> cube_bpsnr_dogdance_s10
+./print_cube.sh DogDance 20 PSNR_basic >> cube_bpsnr_dogdance_s20
+./print_cube.sh DogDance 40 PSNR_basic >> cube_bpsnr_dogdance_s40
+
+./print_cube.sh Evergreen 10 PSNR_basic >> cube_bpsnr_evergreen_s10
+./print_cube.sh Evergreen 20 PSNR_basic >> cube_bpsnr_evergreen_s20
[…]

### 2015-08-05 tools/psnr_vs_px_rank_np_bars.m

@@ -1,0 +1,330 @@
+% load data
+
+basedir2 = ['/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/'...
+            'cube_1r_1np_1px_1pt3_2px5x5x3_2r16_2np160/'];
+basedir1 = ['/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/'...
+            'cube_1r_1np_1px_1pt3_2px5x5x3_2r16_2np160/'];
+
+patchx  = [  3,  5,  7,  9];
+rank = [ 8 , 16 , 32 , 64 ];
+nsim = [ 80, 160, 320, 640];
+
+ylims = [26,41;  % sigma 10
+         23,38;  % sigma 20
+         21,36]; % sigma 40
+
+ylimstime = [0,1000;  % sigma 10
+             0,1000;  % sigma 20
+             0,1000]; % sigma 40
+
+% PSNR point cloud plots
+seqs = {'army', 'dogdance', 'evergreen', 'walking'};
+sigmas = {'10', '20', '40'};
+
+step = 1;
+plot_average = true;
+plot_sequences = false;
+
+mean_final = zeros(length(rank),length(nsim),length(patchx),length(sigmas));
+mean_basic = zeros(length(rank),length(nsim),length(patchx),length(sigmas));
+mean_times = zeros(length(rank),length(nsim),length(patchx),length(sigmas));
+if step == 2,
+	mean_final_ref = zeros(1,length(sigmas));
+	mean_basic_ref = zeros(1,length(sigmas));
+	mean_times_ref = zeros(1,length(sigmas));
+end
+
+for i = 1:length(seqs),
+for p = 1:length(sigmas),
+
+	if step == 1, basedir = basedir1;
+	else          basedir = basedir2;
+	end
+
+	% plots of psnr
+	final = load([basedir 'cube_fpsnr_' seqs{i} '_s' sigmas{p}]);
+	basic = load([basedir 'cube_bpsnr_' seqs{i} '_s' sigmas{p}]);
+	times = load([basedir 'cube_time_'  seqs{i} '_s' sigmas{p}]);
+
+	final = reshape(final', [length(nsim), length(rank), length(patchx)]);
[…]

### 2015-08-05 tools/psnr_vs_px_wx_bars.m

@@ -1,19 +1,20 @@
 % load data
 
-basedir1 = '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_rank1_1ps5x5x4_2ps5x5x4_2wx37/';
-basedir2 = '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_rank2_1ps5x5x4_2ps5x5x4_2wx37/';
-ranks1 = [  4,   8,  12,  16,  20];
-ranks2 = [  4,   8,  12,  16,  20];
-nsim1  = [ 80, 120, 160, 300, 600];
-nsim2  = [ 40,  80, 120, 160, 375];
+rank = '64';
+basedir2 = ['/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/'...
+            'table_sizes2_1ps5x5x4_2pt4_2r' rank '_2np160/'];
+basedir1 = ['/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/'...
+            'table_sizes1_1ps5x5x4_2pt4_2r' rank '_2np160/'];
+searchx = [ 13, 25, 37, 49];
+patchx  = [  3,  5,  7,  9];
 
 ylims = [33,41;  % sigma 10
-         30,38;  % sigma 25
+         30,38;  % sigma 20
          28,36]; % sigma 40
 
-ylimstime = [70,400;  % sigma 10
-             70,400;  % sigma 25
-             70,400]; % sigma 40
+ylimstime = [0,2000;  % sigma 10
+             0,2000;  % sigma 20
+             0,2000]; % sigma 40
 
 % PSNR point cloud plots
 seqs = {'army', 'dogdance', 'evergreen', 'mequon', 'walking'};
@@ -23,9 +24,9 @@ step = 2;
 plot_average = true;
 plot_sequences = true;
 
-mean_final = zeros(5,5,length(sigmas));
-mean_basic = zeros(5,5,length(sigmas));
-mean_times = zeros(5,5,length(sigmas));
+mean_final = zeros(4,4,length(sigmas));
+mean_basic = zeros(4,4,length(sigmas));
+mean_times = zeros(4,4,length(sigmas));
 if step == 1,
 	mean_final_ref = zeros(1,length(sigmas));
[…]

### 2015-08-05 tools/psnr_vs_rank_px_np_bars.m

@@ -1,0 +1,311 @@
+% load data
+
+basedir2 = ['/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/'...
+            'cube_2r_2np_2px_2pt3_1px5x5x3_1rs_1nps/'];
+basedir1 = ['/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/'...
+            'cube_1r_1np_1px_1pt3_2px5x5x3_2r16_2np160/'];
+
+step = 2;
+
+patchx  = [  3,  5,  7,  9];
+rank = [ 8 , 16 , 32 , 64 ];
+nsim = [ 80, 160, 320, 640];
+
+ylims = [26,41;  % sigma 10
+         23,38;  % sigma 20
+         21,36]; % sigma 40
+
+ylimstime = [0,1500;  % sigma 10
+             0,1500;  % sigma 20
+             0,1500]; % sigma 40
+
+% PSNR point cloud plots
+seqs = {'army', 'dogdance', 'evergreen', 'walking'};
+sigmas = {'10', '20', '40'};
+
+plot_average = true;
+plot_sequences = false;
+
+mean_final = zeros(length(patchx),length(nsim),length(rank),length(sigmas));
+mean_basic = zeros(length(patchx),length(nsim),length(rank),length(sigmas));
+mean_times = zeros(length(patchx),length(nsim),length(rank),length(sigmas));
+%if step == 2,
+%	mean_final_ref = zeros(1,length(sigmas));
+%	mean_basic_ref = zeros(1,length(sigmas));
+%	mean_times_ref = zeros(1,length(sigmas));
+%end
+
+for i = 1:length(seqs),
+for p = 1:length(sigmas),
+
+	if step == 1, basedir = basedir1;
+	else          basedir = basedir2;
+	end
+
+	% plots of psnr
+	final = load([basedir 'cube_fpsnr_' seqs{i} '_s' sigmas{p}]);
+	basic = load([basedir 'cube_bpsnr_' seqs{i} '_s' sigmas{p}]);
+	times = load([basedir 'cube_time_'  seqs{i} '_s' sigmas{p}]);
+
+	final = reshape(final', [length(nsim), length(rank), length(patchx)]);
[…]

### 2015-08-07 src/NlBayes/VideoNLBayes.cpp
[src] Bug fix: one can now set rank = 0

@@ -37,7 +37,7 @@
 //#define USE_SVD_LAPACK
 //#define USE_SVD_IDDIST
 
-#define DEBUG_SHOW_WEIGHT
+//#define DEBUG_SHOW_WEIGHT
 //#define DEBUG_SHOW_PATCH_GROUPS
 //#define CENTRED_SEARCH
 
@@ -126,7 +126,8 @@ void initializeNlbParameters(
 
 	//! Offset: step between two similar patches
 	o_params.offSet     = std::max((unsigned)1, o_params.sizePatch     / 2);
-	o_params.offSetTime = std::max((unsigned)1, o_params.sizePatchTime / 2);
+//	o_params.offSetTime = std::max((unsigned)1, o_params.sizePatchTime / 2);
+	o_params.offSetTime = 1;
 
 	//! Use the homogeneous area detection trick
 	o_params.useHomogeneousArea = p_flatArea;
@@ -1354,67 +1355,81 @@ float computeBayesEstimateStep1_LR_EIG_LAPACK(
 		//! Center 3D group
 		centerData(io_group[c], i_mat.baricenter, p_nSimP, sPC);
 
-		//! Compute the covariance matrix of the set of similar patches
-		covarianceMatrix(io_group[c], i_mat.covMat, p_nSimP, sPC);
-
-		//! Compute leading eigenvectors
-		int info = matrixEigs(i_mat.covMat, sPC, r, i_mat.covEigVals, i_mat.covEigVecs);
-
-		//! Substract sigma2 and compute variance captured by the r leading eigenvectors
-		for (int i = 0; i < r; ++i)
+		if (r > 0)
 		{
-			i_mat.covEigVals[i] -= std::min(i_mat.covEigVals[i], sigma2);
-			rank_variance  += i_mat.covEigVals[i];
-			total_variance += i_mat.covEigVals[i];
+			//! Compute the covariance matrix of the set of similar patches
+			covarianceMatrix(io_group[c], i_mat.covMat, p_nSimP, sPC);
+
+			//! Compute leading eigenvectors
+			int info = matrixEigs(i_mat.covMat, sPC, r, i_mat.covEigVals, i_mat.covEigVecs);
+
+			//! Substract sigma2 and compute variance captured by the r leading eigenvectors
+			for (int i = 0; i < r; ++i)
+			{
+				i_mat.covEigVals[i] -= std::min(i_mat.covEigVals[i], sigma2);
+				rank_variance  += i_mat.covEigVals[i];
[…]

### 2015-08-07 doc/201507_tip/paper.tex

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass[10pt, journal, twocolumn, final, a4paper]{IEEEtran}
%
\usepackage{makeidx}  % allows for indexgeneration
%

% allow for compress references ranges (IEEEtran_HOWTO S.VII)
% noadjust removes a leading space before the []
\usepackage[noadjust]{cite}

\usepackage[english,activeacute]{babel}
\usepackage[english]{layout}
\usepackage{amsfonts,amssymb}
\usepackage[cmex10]{amsmath}
\usepackage{amsopn} % DeclareMathOperator
\usepackage{amsbsy} % boldsymbol
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{subfig}
\usepackage{colonequals}
\usepackage[latin1]{inputenc}
\usepackage{url}
\usepackage{epsfig}
\usepackage{dsfont}
\usepackage{multirow}

\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{setspace}
\usepackage{afterpage}
%\usepackage{showkeys}
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
% \usepackage{latexsym}

%\usepackage[left=1.2in,right=1.2in]{geometry}

% \graphicspath{{../iccv09/}}

%\newcommand{\best}[1]{\textbf{\textcolor{MyOrange}{#1}}}
\newcommand{\best}[1]{#1}
\newcommand{\bsic}[1]{\textcolor{black}{\textit{#1}}}
\newcommand{\Bsic}[1]{\textcolor{black}{\textbf{\textit{#1}}}}
\newcommand{\Best}[1]{\textbf{\textcolor{black}{#1}}}

\newcommand{\ma}[1]{\boldsymbol{#1}}
\newcommand{\tras}[1]{#1^{\mathrm{T}}}
\newcommand{\herm}[1]{#1^{\mathrm{H}}}
\newcommand{\con}[1]{#1^{\mathrm{*}}}
\newcommand{\E}{\mathds{E}}
\newcommand{\tech}[1]{\overline{#1}}
\newcommand{\nspace}{\!\!\!\!}
\newcommand{\nmbr}[1]{\oldstylenums{#1}}

\newcommand{\eg}{\emph{e.g}. } \newcommand{\Eg}{\emph{E.g}. }
\newcommand{\ie}{\emph{i.e}. } \newcommand{\Ie}{\emph{I.e}. }
\newcommand{\cf}{\emph{c.f}. } \newcommand{\Cf}{\emph{C.f}. }
\newcommand{\etc}{\emph{etc}. } \newcommand{\vs}{\emph{vs}. }
\newcommand{\wrt}{w.r.t\onedot } \newcommand{\dof}{d.o.f. }
\newcommand{\etal}{\emph{et al}. }

\newcommand{\R}{\mathds{R}}
\newcommand{\sign}{\mathrm{sign}}
\newcommand{\eps}{\varepsilon}
\newcommand{\To}{\longrightarrow}
% \newcommand{\II}{1{\hskip -2.5 pt}\hbox{I}}

\renewcommand{\algorithmiccomment}[1]{\bgroup\hfill\small\textcolor{gray}{//~#1}\egroup}

% c++ code
\usepackage{listings}
\usepackage{xcolor}
\usepackage{textcomp}
\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
	backgroundcolor=\color{lbcolor},
	tabsize=4,    
%  rulecolor=,
	language=Matlab,
	basicstyle=\scriptsize\ttfamily,
	upquote=true,
	aboveskip={1.5\baselineskip},
	columns=fixed,
	showstringspaces=false,
	extendedchars=false,
	breaklines=true,
	prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
	frame=single,
	numbers=left,
	showtabs=false,
	showspaces=false,
	showstringspaces=false,
	identifierstyle=\ttfamily,
	keywordstyle=\color[rgb]{0,0,1}\ttfamily,
	commentstyle=\color[rgb]{0,0.5,0}\ttfamily,
	stringstyle=\color[rgb]{0.627,0.126,0.941}\ttfamily,
	numberstyle=\color[rgb]{0.5, 0.5, 0.5}\ttfamily,
%  \lstdefinestyle{C++}{language=C++,style=numbers}’.
}
%\lstset{
%	backgroundcolor=\color{lbcolor},
%	tabsize=4,
%	language=C++,
%	captionpos=b,
%	tabsize=3,
%	frame=lines,
%	numbers=left,
%	numberstyle=\tiny,
%	numbersep=5pt,
%	breaklines=true,
%	showstringspaces=false,
%	basicstyle=\footnotesize,
%	identifierstyle=\color{magenta},
%	keywordstyle=\color[rgb]{0,0,1},
%	commentstyle=\color{green},
%	stringstyle=\color{red}
%}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\nota}[1]{\textcolor{blue}{\textbf{#1}}}
\newcommand{\suggest}[1]{\textcolor{cyan}{#1}}
\newcommand{\add}[1]{\textcolor{green}{#1}}
\newcommand{\remove}[1]{\textcolor{red}{#1}}
\newcommand{\todo}[1]{\textcolor{red}{\noindent\textsc{todo}: #1}}
\newcommand{\dosdv}[1] {#1}
\newcommand{\uncite}[1] {}
% \newcommand{\tachar}[1]{
% \setbox4=\hbox{\ } \setbox3=\hbox{#1} \hbox{#1} \kern -\wd3 \kern
% -\wd4 \raise 0.3\ht3 \hbox{ \vrule width \wd3 height 0.5pt} }

% \theoremstyle{plain}\newtheorem{theorem}{Theorem}[chapter]
% \theoremstyle{plain}\newtheorem{proposition}{Proposition}[chapter]
% \theoremstyle{plain}\newtheorem{lemma}{Lemma}[chapter]
% \theoremstyle{definition}\newtheorem{definition}{Definition}[chapter]

% New definition of square root:
% it renames \sqrt as \oldsqrt
\let\oldsqrt\sqrt
% it defines the new \sqrt in terms of the old one
\def\sqrt{\mathpalette\DHLhksqrt}
\def\DHLhksqrt#1#2{%
\setbox0=\hbox{$#1\oldsqrt{#2\,}$}\dimen0=\ht0
\advance\dimen0-0.2\ht0
\setbox2=\hbox{\vrule height\ht0 depth -\dimen0}%
{\box0\lower0.4pt\box2}}

\begin{document}

\title{A Non-local Bayesian Video Denoising Method}

\author{Pablo~Arias, Jean-Michel~Morel%
\thanks{P. Arias (\texttt{pablo.arias@upf.edu}) and J.-M. Morel
(\texttt{jean-michel.morel@cmla.ens-cachan.fr}) are with the \emph{Centre de
math\'ematiques et de leurs applications} (CMLA), \'Ecole Normale Sup\'eriore
de Cachan, 61 Av. du Pr\'esident Wilson, F-94230 Cachan, France}}

\markboth{IEEE Transactions of Image Processing,~Vol.~X, No.~X, Month~2015}%
{Arias, Morel: A Non-local Bayesian Video Denoising Method}

\maketitle              % typeset the title of the contribution

\begin{abstract}
	The quality provided by image/video sensors increases steadily, and
	for a fixed spatial resolution the sensor noise has been gradually reduced.
	However, modern sensors are also capable of acquiring at higher spatial
	resolutions which are still affected by noise, specially at low lighting
	conditions. The situation is even worse in video cameras, where the capture
	time is bounded by the frame rate. The noise in the video degrades its visual 
	quality and hinders its analysis.
	In this paper we present a new video denoising method extending 
	the non-local Bayes image denoising algorithm. The method does not require 
	motion estimation, and yet preliminary results show that it outperforms the
	state-of-the-art methods in terms of PSNR.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
	video denoising, Bayesian methods, patch-based methods
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

%
\section{Introduction}
%

Advances in video sensor hardware have steadily improved the acquisition
quality. However, due to the reduction in the price of cameras
and data storage, video cameras are being used more each time, and in less
favorable situations, such as low lighting conditions. This results in high 
levels of noise, which negatively affects the visual quality of the video and
hinders its use for any application. 
\todo{Add references for claims about sensors, camera prices, etc.}

Video denoising has received much less attention than still image denoising. 
In principle, video denoising should be easier than image denoising, since the
strong temporal redundancy along motion trajectories favours the denoising
task. However, this additional form of redundancy creates challenges.  On one
hand, the amount of data is much larger than for still images, and efficient
ways of navigating through this data are needed. On the other hand, the output
of the denoising algorithm should be temporally consistent according to the
motion of the original sequence.

Early works proposed temporal or spatio-temporal filters which either compensate
for motion on estimated motion trajectories or used some kind of mechanism to
adapt to the changes in the video signal at a fixed location due to the motion.
We refer the reader to \cite{Brailean1995a} and references therein for more details.
Other video denoising works apply temporal filtering to the wavelet coefficients 
of the frames \cite{Jin2006,Zlokolica2006a}.

Some methods do not distinguish between the temporal and spatial dimensions,
and treat the video as a volume, which is denoised in a transformed domain
\cite{Rajpoot2003,Wilson2004,Selesnick2003}. 
\todo{Read these references. Even if they consider a 3D transform, I think
they DO distinguish between space and time}

Until the advent of patch-based approaches, methods that do not compensate
motion failed for sequences with moderate motion, and their main interest resided
in their simplicity and low computational cost. First state-of-the-art results
obtained without motion estimation were reported in \cite{Buades2005v}, with the
non-local means algorithm. The authors argued that for their method, based on
averaging similar patches, motion estimation was not only unnecessary but
counterproductive: while textured regions are problematic for motion
estimation, they are a source of a large number of similar patches across
different frames. Even if the motion trajectory could be reliably estimated, it
makes more sense to use all similar patches, rather than using only the ones on the
trajectory.
%
A similar approach was followed by the authors of \cite{Dabov2007v}. This method is based
on collaborative filtering of similar patches in a
spatio-temporal neighborhood.

The methods in \cite{Buades2005v} and \cite{Dabov2007v} are extensions to video
of still image patch-based denoising algorithms (non-local means REF and BM3D
REF respectively). They are based on \suggest{filtering} similar 2D patches
searched for in a 3D spatio-temporal neighborhood.  These methods exploit both
spatial and temporal redundancy, however, since each 2D patch is processed
independently, there is no mechanism to impose coherence along trajectories.
This results in flickering artifacts which become noticeable for high levels of
noise. 
%
While these methods exploit spatio-temporal redundancy, they do not impose
coherence of the trajectories, resulting in flickering
artifacts which become noticeable for high levels of noise.

A natural next step is to consider 3D spatio-temporal patches. This has two
main advantages (at the expense of a higher computational cost). First it
provides a mechanism to impose some temporal consistency on the result, since
now, the temporally continguous 2D spatial slices of a spatio-temporal patch
are filtered jointly. Secondly, a 3D patch has a higher number of pixels
resulting in a reduction of the noise in the distance between patches. On the
other hand, to get the same reduction in the distance noise with 2D patches one
needs to increase their spatial size which leads to a smaller number of similar
patches.

Two types of 3D patches have been used: rectangular and motion-compensated.
Motion-compensated 3D patches follow a motion trajectory previously estimated.
Each approach has its pros and cons.

Motion-compensated patches have the benefit that their spatial slices are very
similar between each other (or the same, assuming purely translational pixelic
motion). As a consequence, temporal filtering can be easily performed by
filtering inside the patch in the temporal direction. 
Because of this, methods that use motion-compensated 3D patches only look for
similar motion-compensated 3D patches starting in the same frame.

%It has been shown by \cite{Liu2010} and \cite{Maggioni2011,Maggioni2012} that motion estimation can still be
%beneficial for patch-based methods. 
%
An example of this is the method presented in \cite{Liu2010}. The authors
propose a method based on non-local means. The method is described in terms of
2D patches. To denoise a target 2D patch, the $k$ nearest neighbors in the current
frame are found. The 2D patches in their forward and backward trajectories are
used also to denoising the target patch. As a consequence the set of similar
patches averaged to denoise each pixel varies smoothly along motion
trajectories. This yields results with high temporal consistency. 
To estimate motion, their method resorts to a robust optical flow algorithm
based on \cite{Bruhn2005}.

In \cite{Maggioni2011,Maggioni2012}, the authors introduced V-BM4D, an
extension of BM3D to video by collaborative filtering of similar motion
compensated 3D patches. Trajectories are computed with a block matching
strategy based on the sum of squared differences (SSD) and a temporal
regularization term, which favours trajectories with small velocity and low
acceleration. The results of this algorithm show higher PSNR and temporal
consistency, resulting in a higher overall quality.

One of the main difficulties in using motion-compensated patches is estimating
motion. Motion estimation is a paramount problem in noiseless sequences, and
noise makes it much harder.

Rectangular 3D patches offer an appealing
alternative, since they do not require estimating motion. 
In \cite{Protter2007,Protter2009} the authors extend the K-SVD \cite{Elad2006}
image denoising method to video by learning a dictionary of spatio-temporal
rectangular 3D patches.

Each rectangular 3D patch results from the combination of a 2D texture and a
motion pattern. For arbitrary motion, each combination of texture and motion is
not likely to occur together again. Thus rectangular 3D patches should have
less repeatability in the video compared to motion compensated patches.  An
exception is when the motion is a global translation of the frame, in which
case, the motion pattern is equal for each patch. Furthermore, if there is no
acceleration (uniform motion), rectangular 3D patches are constant along motion
trajectories. Global uniform motion is indeed a too restrictive model, but in
many cases, it is a valid approximation in a local neighborhood in space and
time.

\bigskip

In this work we present an extension to video of the non-local Bayes image
denoising method \cite{Lebrun2013a,Lebrun2013ipol} using 3D rectangular
patches and which does not require motion estimation. Yet, it provides
results which compare favourably to the current state-of-the-art,
both quantitatively by a significant marging and qualitatively, specifically in
terms of the temporal consistency attained.

\bigskip

The rest of the paper is structured as follows: in \S
\ref{sec:review_nonlocal_Bayes} we review the Bayesian patch denoising principle 
and describe our extension to video. In \S \ref{sec:parameters}
we discuss its parameters. Some results, including a comparison with VBM4D, are shown
in \S \ref{sec:results}. Concluding remarks are given in \S \ref{sec:conclusion}

\section{Bayesian video denoising}
\label{sec:review_nonlocal_Bayes}

A patch based Bayesian algorithm can assume that the patches similar to a given
patch follow a Gaussian distribution.
The problem 
of denoising can then be formulated as a problem of optimal Bayesian inference, where the
parameters of the prior are learnt from the noisy data.

\subsection{A nonlocal Bayesian principle}

Consider a grayscale video $u:\Omega\times \{1,\cdots,T\}\rightarrow
\mathbb R$, where $\Omega$ is the spatial domain (a rectangular discrete grid).
We assume that $v$ is a noisy version of $u$, contaminated with additive,
Gaussian, white noise $n$ of known variance $\sigma^2$,
\[v = u + n.\]

Given a rectangular 3D patch $\ma q$ of size $s_x\times s_x\times s_t$ of the noisy video $v$, and the 
corresponding patch $\ma p$ of the clean video $u$, we assume the following 
Gaussian linear model of $\ma p$ and $\ma q$:
\begin{align}
	\mathds{P}(\ma p) &= \mathcal N(\overline {\ma p}, C) \propto \exp\left(-\frac12\langle \ma p - \overline{\ma p}, C^{-1}(\ma p - \overline{\ma p})\rangle\right) \label{eq:prior}\\
	\mathds{P}(\ma q|\ma p) &= \mathcal N(\ma p, \sigma I) \propto \exp\left(-\frac1{2\sigma^2}\|\ma q - \ma p\|^2\right) \label{eq:obs}
\end{align}
Once the mean patch $\overline{\ma p}$ and the
covariance matrix $C$ have been estimated from the image itself, the MAP
estimate $\widetilde{\ma p}$ given a noisy patch $\ma q$ is obtained as:
\[ \widetilde{\ma p} = \argmax_{\ma p} \mathds P(\ma p | \ma q) = \argmin_{\ma p} -\log \mathds P(\ma p | \ma q). \]
Since we are working with Gaussian distributions, the log-posterior is a quadratic (positive definite)
function and the MAP can be computed explicitly as (see  \cite{Lebrun2013a})
\begin{equation}
	\widetilde{\ma p} = \overline{\ma p} + C(C + \sigma^2 I)^{-1}(\ma q - \overline{\ma p})
	\label{eq:map}
\end{equation}
The matrix in the above equation can be diagonalized in the basis of
principal directions of the covariance matrix $C$.
Let $C = U\Lambda U^T$ denote the eigendecomposition of $C$. Then we have that
\[U^T(\widetilde{\ma p} - \overline{\ma p}) \,\,\,\, = \,\,\,\, 
	\Lambda(\Lambda + \sigma^2 I)^{-1}\,\,\,\,
	U^T (\ma q - \overline{\ma p}).\]
The diagonal operator $W = \Lambda(\Lambda + \sigma^2I)^{-1}$
has the following coefficients:
\begin{equation}
w_{ii} = \frac{\lambda_i}{\lambda_i + \sigma^2}
	%	       = (1 + \sigma^2/\lambda_i)^{-1}
				 = (1 + \text{snr}_i^{-1})^{-1}
				 \label{eq:wiener_coeffs}
\end{equation}
which correspond to a Wiener filter on the principal components.

%
%In practice, we introduce a parameter $\beta$ (with $\beta \approx 1$)
%multiplying $\sigma^2I$ to be able to control the amount of filtering.

\subsection{Learning a low-rank \textit{a priori} model}

The parameters of the \textit{a priori} model, are learnt from the noisy video as
follows. For each noisy patch $\ma q$, we select the most $N_{\text{sim}}$
similar 3D patches found in a search region centered at $\ma q$. The
search region is a spatio-temporal rectangle of size $n_x \times
n_x \times n_t$ ($n_x, n_t$ are odd numbers).

Let us note by $\ma q_i$, $i = 1, \dots, N_{\text{sim}}$ the set of patches
similar to $\ma q$ (with $\ma q_1 = \ma q$). We assume that these 
patches correspond to different noisy observations of the Gaussian linear model
\eqref{eq:prior} and \eqref{eq:obs}. The corresponding marginal distribution is given by
\[\mathds P(\ma q) = \mathcal N(\overline{\ma p}, C + \sigma^2I). \]
Therefore, the maximum likelihood estimates for $\overline{\ma p}$ and $C$ are given by 
\begin{equation}
	\widehat{\overline{\ma p}} = \frac1{N_{\text{sim}}}\sum_{i = 1}^{N_{\text{sim}}}\ma q_i \quad\text{and}\quad 
		\widehat C= \frac1{N_\text{sim}}\sum_{i = 1}^{N_{\text{sim}}}\ma q_i\ma q_i^T - \sigma^2I.
	\label{eq:learn_parameters}
\end{equation}

We will also assume that the covariance matrix has a lower rank $k$.  In this
case, it has been shown REF PPCA that maximum likelihood estimate is given by
truncated the spectral decomposition of $\widehat C$ to the $k$ largest
eigenvalues.
\begin{equation}
\widehat C_k = \sum_{i = 1}^k\widehat \lambda_i\widehat U_i\widehat U_i^T,
\end{equation}
where $\widehat \lambda_i$, $\widehat U_i$ denote the $i$-th largest
eigenvalue and its corresponding eigenvector respectively.

\bigskip

Other methods for image denoising have been proposed in the
literature based on Gaussian models for the patch density. In \cite{Yu2012},
the authors introduce a framework for solving inverse problems, based on the
assumption that the patches of an image are distributed according to a Gaussian
Mixture Model (GMM). A method is proposed to learn the parameters of the model from
the image. A GMM is also used in \cite{Zoran2011}, but it is trained from a
database of $2\cdot 10^6$ patches randomly sampled from the Berkeley database.

In \cite{Zhang2010} a PCA-based algorithm is introduced which is equivalent to 
the nonlocal Bayes method. In fact, nonlocal Bayes can be regarded as a Bayesian 
interpretation of \cite{Zhang2010}.

The BLS-GSM method \cite{Portilla2003} (Bayes least square estimate of Gaussian
scale mixture) models noiseless ``wavelet coefficient neighborhoods'' with a
Gaussian scale mixture defined as a random scaling of a zero-mean Gaussian
density. The wavelet coefficient neighborhood turns out to be a patch of an
oriented channel of the image at a given scale.

\section{Description of the algorithm}

Let us now describe the video denoising algorithm. As in
\cite{Dabov2007tip,Dabov2007v,Maggioni2012,Lebrun2013a} we perform two stages, described in 
Algorithms \ref{alg:nlbayes} and \ref{alg:nlbayes2}. In the first stage we
compute a \emph{basic} estimate, which we denote $\widetilde u^{(1)}$.

In the second stage computes the final estimate $\widetilde u^{(2)}$ using the
basic estimate as an oracle. This entails two modifications with respect to the
first stage (highlighted in italics in Algorithm \ref{alg:nlbayes2}). Firstly, the
computation of the patch distances is performed using the patches of the basic
estimate instead of the noisy ones. And secondly, we assume that the patches of
the basic estimate are drawn from the \textit{a priori} Gaussian model and use
them to learn the mean and covariance matrix. Note that in the second stage,
when estimating the covariance matrix, we assume that the patches of the basic
estimate have no noise. Thus we set $\sigma = 0$ in Eq.
\eqref{eq:learn_parameters}.

\begin{algorithm}
	\caption{Video NL-Bayes - Step 1: basic estimate}
	\label{alg:nlbayes}
		\begin{algorithmic}[1]
		\REQUIRE Noisy video $v$, noise standard deviation
		$\sigma$
		\ENSURE Basic estimate of noiseless video $\widetilde u^{(1)}$
		\STATE Set $\mathcal P = \{\ma q \,:\, \ma q \text{ patch of }  v\}$ \COMMENT{patches to process}
		\WHILE{$\mathcal P \neq \emptyset$}
		\STATE Get a patch $\ma q$ from $\mathcal P$ \COMMENT{``center'' of Gaussian model}
			\STATE Retrieve  the $n_{\text{sim}}$ nearest neighbors to $\ma
			q$ in a spatio-temporal volume around $\ma q$
			\STATE Compute $\widehat{\overline{\ma p}}\,\!^{(1)}$ and
			$\widehat C_{r}^{(1)}$ 
			\FORALL{$n_{\text{sim}}$ neighbors $\ma q_i$ of $\ma q$}
				\STATE Obtain the MAP estimate $\widetilde{\ma p}_i^{(1)}$
				\STATE Aggregate estimated patch on $\widetilde u^{(1)}$
				\STATE Remove $\ma q_i$ from $\mathcal P$
			\ENDFOR
		\ENDWHILE
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Video NL-Bayes - Step 2: final estimate}
	\label{alg:nlbayes2}
	\begin{spacing}{1.3}
		\begin{algorithmic}[1]
		\REQUIRE Noisy video $v$, noise standard
		deviation $\sigma$, \emph{basic estimate $\widetilde u^{(1)}$} 
		\ENSURE Final estimate of noiseless video $\widetilde u^{(2)}$
		\STATE Set $\mathcal P = \{\ma q \,:\, \ma q \text{ patch of }  v\}$ \COMMENT{patches to process}
		\WHILE{$\mathcal P \neq \emptyset$}
		\STATE Get a patch $\ma q$ from $\mathcal P$ \COMMENT{``center'' of Gaussian model}
			\STATE Retrieve the $n_{\text{sim}}$ nearest neighbors to $\ma
			q$ in a spatio-temporal volume around $\ma q$.
			\emph{The distance is computed between the basic estimates
				$\widetilde{\ma p}^{(1)}$}
			\STATE Compute $\widehat{\overline{\ma p}}\,\!^{(2)}$ and $\widehat
					 C_{r}^{(2)}$ \emph{from the basic estimates
						 $\widetilde{\ma p}_i^{(1)}$, setting $\ma{\sigma = 0}$.}
			\FORALL{$n_{\text{sim}}$ neighbors $\ma q_i$ of $\ma q$}
				\STATE Obtain the MAP estimate $\widetilde{\ma p}_i^{(2)}$
				\STATE Aggregate estimated patch on $\widetilde u^{(2)}$
				\STATE Remove $\ma q_i$ from $\mathcal P$
			\ENDFOR
		\ENDWHILE
	\end{algorithmic}
	\end{spacing}
\end{algorithm}

%\begin{algorithm}
%	\caption{Video NL-Bayes}
%	\label{alg:nlbayes}
%	\begin{algorithmic}
%		\REQUIRE Noisy video $v$, noise standard deviation $\sigma$ \\
%		\ENSURE Estimate of noiseless video $\widetilde u$
%		\FORALL{patches $\ma q$ in $v$}
%		\STATE Find the $N_{\text{sim}}$ most similar patches to $\ma q$ in a search volume centered at $\ma q$
%		\STATE Compute $\widehat{\overline{\ma p}}\,\!^{(1)}$ and $\widehat C^{(1)}$ according to \eqref{eq:learn_parameters}
%		\STATE Obtain the first stage estimate $\widetilde{\ma p}^{(1)}$ by \eqref{eq:map}
%		\ENDFOR
%		\FORALL{pixel $(x,t)$ in $\Omega\times {1,\dots,T}$}
%		\STATE Obtain the basic estimate $\widetilde u^{(1)}(x,t)$ by averaging
%		the values of all patches $\widetilde{\ma p}^{(1)}$ containing $(x,t)$.
%		\ENDFOR
%		\FORALL{patches $\ma q$ in $v$}
%		\STATE Find the $N_{\text{sim}}$ most similar patches to $\ma q$ in a
%		search volume centered at $\ma q$ by comparing the estimates $\widetilde{\ma
%		p}^{(1)}$. We denote them, and their corresponding basic estimates as 
%		$\ma q_i$ and $\widetilde{\ma p}_i^{(1)}$ respectively.
%		\STATE Compute $\widehat{\overline{\ma p}}\,\!^{(2)}$ and $\widehat C^{(2)}$ according to
%\[
%	\widehat{\overline{\ma p}}\,\!^{(2)} = \frac1{N_{\text{sim}}}\sum_{i = 1}^{N_{\text{sim}}}\widetilde{\ma p}_i^{(1)} \quad\text{and}\quad 
%	\widehat C^{(2)}= \frac1{N_\text{sim}}\sum_{i = 1}^{N_{\text{sim}}}\left(\widetilde{\ma p}_i^{(1)}\right)^T \widetilde{\ma p}_i^{(1)}.
%\]
%		\STATE Obtain the second stage estimate $\widetilde{\ma p}^{(2)}$ as in \eqref{eq:map}
%		\ENDFOR
%		\FORALL{pixel $(x,t)$ in $\Omega\times {1,\dots,T}$}
%		\STATE Obtain the final estimate $\widetilde u(x,t)$ by averaging
%		the values of all patches $\widetilde{\ma p}^{(2)}$ containing $(x,t)$.
%		\ENDFOR
%
%	\end{algorithmic}
%\end{algorithm}

\begin{figure*}[thpb!]
	\begin{center}
		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_nisy_s10_044.png}
		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_nisy_s20_044.png}
		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_nisy_s40_044.png}\\
		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_vnlb_s10_tr2_044.png}
		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_vnlb_s20_tr2_044.png}
		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_vnlb_s40_tr2_044.png}\\
		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_s10_bm4d_044.png}
		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_s20_bm4d_044.png}
		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_s40_bm4d_044.png}\\
		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_nisy_s10_140.png}
		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_nisy_s20_140.png}
		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_nisy_s40_140.png}\\
		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_vnlb_s10_tr2_140.png}
		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_vnlb_s20_tr2_140.png}
		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_vnlb_s40_tr2_140.png}\\
		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_s10_bm4d_140.png}
		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_s20_bm4d_140.png}
		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_s40_bm4d_140.png}
	\end{center}
	\caption{Comparison of results obtained with VNLB ($n_t =5$) and V-BM4D-np.
	The first three rows, correspond to a frame of the bus sequence. From top to
	bottom: noisy input data. The last three rows correspond to the tennis sequence.
	Each column shows results obtained for $\sigma = 10$, $20$ and $40$.}
	\label{fig:results}
\end{figure*}

\subsection{Implementation details}

\paragraph{Handling of color} Color videos are handled as in \cite{Lebrun2013a}.
%
In the first stage, we express the video in a luminance-chrominance colorspace,
specifically we apply the opponent color transform (see \cite{Dabov2007tip,Lebrun2013a}).
Patch distances are computed using the luminance only. Using the 
$N_{\text{sim}}$ most similar patches, a group is built for each channel. These
groups are filtered independently (a Gaussian model is learnt for each of them).
%
In the second stage, the patch distance is computed using the RGB patches, and
a single \textit{a priori} Gaussian model is built for the each set
of similar RGB patches.

% \paragraph{Variance correction factor} In practice, when computing the MAP
% estimate by eq. \eqref{eq:map}, we introduce a parameter $\beta$ (with $\beta \approx 1$) multiplying
% $\sigma^2I$ to be able to control the amount of filtering.

\paragraph{Patch distance threshold} When building the group of similar
patches during the second stage, more than $N_{\text{sim}}$ patches are allowed
if their distances with respect to the reference patch are smaller than a
threshold $\tau$.  As in \cite{Lebrun2013ipol}, we set $\tau = 4$ (the distance between
patches is normalized by the number of elements in the patch and the number of
channels).

\paragraph{Speed-ups} To accelerate the computation we apply two tricks
considered in \cite{Lebrun2013ipol}. The first one visits a patch each $N_{\text{step}}$
patches (similar to \cite{Dabov2007tip}). The second trick consists on the following.
After filtering the patches in a group, these patches are not considered again
as reference patches for a group. This reduces the number of groups of patches
that need to be processed by a factor of $N_{\text{sim}}$.
\todo{Also describe that the 4 neighbors are flagged as processed.}

\subsection{Computational complexity}
\label{sec:complexity}

Let us consider the complexity associated to the building and filtering of a
group of $N_{\text{sim}}$ similar patches. Due to the speed-ups described in
the previous section, the actual number of groups of similar patches processed
might vary, but it is typically a fraction of the number of pixels in the video.

Processing each group of similar patches is of asymptotic order $\mathcal
O(n_x^2 n_t s_x^2 s_t + s_x^4s_t^2r + N_{\text{sim}}s_x^4s_t^2)$.
The first term comes from the exhaustive search of the $N_{\text{sim}}$ most
similar patches in the search window. 
The second term comes from the computation of the truncated eigen-decomposition
of the covariance matrix, and the last term contemplates computing the
covariance matrix.

The more expensive operations are the computation of the covariance matrix and
of its principal directions.
Let us note that there are methods for computing the $r$ principal directions
of a set of points that do not require computing the covariance matrix\todo{referencia}. Instead
these methods efficiently approximate a truncated SVD of the data matrix, and would 
allow to improve the computational complexity to $\mathcal O(n_x^2 n_t s_x^2
s_t + s_x^2s_trN_{\text{sim}})$.

\todo{Statistics of group of patches.}

\subsection{Selection of parameters}
\label{sec:parameters}

Each stage of the algorithm has the following 6 parameters: the spatial and temporal patch sizes
$s_x$ and $s_t$, the spatial and temporal sizes of the search region $w_x$ and
$w_t$, the number of similar patches $n_{\text{sim}}$ and the rank of the a priori
covariance matrix $r$. Each of these parameters needs to be determined for both
stages.

\paragraph{Search region} Setting the size of the search region implies a
trade-off between denoising performance and running time: A larger search
region takes longer to traverse but yields better the results, since better
neighbors can be found. In the following experiments, we will fix the search
region for both stages of the algorithm at 
\begin{equation}
w_x = 37 \quad \text{ and } \quad w_t = 5.
\label{eq:search_region_parameters}
\end{equation}
If the patch in the center of the search region moves slower than $37/5 = 7.4$
pixels/frame, then it stays in the search region for the $5$ frames.

\paragraph{Patch size} We have found that the

\paragraph{Patch size, rank and number of similar patches} We have found that the
final PSNR has a non-trivial behaviour with respect to any of these parameters.
To set them, we explore the parameter space varying the rank $r$, the spatial
patch size $s_x$ and the number of similar patches $n_{\text{sim}}$. The reduce
the dimensionality of the parameter space, for the moment we fix the temporal
patch size at $s_t = 3$.

First we fix the parameters of the second stage at 
\[r = 16,\,\, n_{\text{sim}} = 160,\,\, s_x = 5,\,\, s_t = 3,\,\, w_x = 37,\,\, w_t = 5,\]
and vary the parameters of the first stage. We considered ranks $r = 8, 16, 32, 64$,   
patch sizes $s_x = 3,5,7,9$ and number of patches $n_{\text{sim}} = 80, 160, 320, 640$.
For all $4^3 = 64$ combinations, we considered three levels of noise $\sigma = 10, 20, 40$
and run our method on four sequences. The
sequences used were \emph{army, dog dance, evergreen} and \emph{walking} from
the Middlebury optical flow benchmark \cite{middleburyOflow}.
The sequences have 8 frames of size $584 \times 388$ (\emph{army}) and $640
\times 480$ (\emph{dog dance, evergreen} and \emph{walking}).
These sequences were chosen to have some variety of motions, textures, etc.

Figure \ref{fig:rank-px-nsim-table-stage1} shows for each configuration of
parameters and level of noise, the average PSNR over the four sequences. The
cyan bars correspond to the basic estimate and the ones in magenta to the final
estimate.

It can be observed that several parameter configurations can give very similar
results. For example, with $\sigma = 10$, equivalent results can be obtained 
with $s_x = 3, r = 16, n_{\text{sim}} = 80$, $s_x = 5, r = 32, n_{\text{sim}} = 160$
or  $s_x = 7, r = 64, n_{\text{sim}} = 320$.
The one with the least computational cost is chosen. This means,
smaller patches sizes, smaller ranks, and a larger number of similar patches.

Another thing to notice is that the final and the basic PSNRs do not always
have the same behaviour. Improving the basic PSNR does not always lead to an
improvement in the final one. The reason for this is that it is preferable to
apply a conservative noise reduction leaving some noise in the basic estimate
(high variance but small bias). In the second step, this residual noise has
little effect on the estimation of the patch distances and the \emph{a priori} covariance
matrix. On the other hand, applying a more aggressive denoising in first step
might increase the basic PSNR, but the second step cannot recover the lost
signal components.

The strength of the denoising is controlled through the rank and the number of
patches in the group. For lower levels of noise, \ie $\sigma = 10$, better
PSRNs can be achieved with a higher rank and using a smaller number of similar
patches. When increasing the noise, the rank should be decreased and the number 
of similar patches increased.

In accordance to these observations, we will set the parameters as a function of
$\sigma$ as follows:
\begin{equation}
	s_t = 5,\quad\quad r = \min(640/\sigma, r_{\text{max}}), \quad\quad n_{\text{sim}} = 16\sigma.
	\label{eq:stage1_parameters}
\end{equation}
%\begin{align}
%	s_t &= 5\\
%	r &= \min(640/\sigma, r_{\text{max}}) \\
%	n_{\text{sim}} &= 16\sigma. 
%	\label{eq:stage1_parameters}
%\end{align}
We set the maximum rank to be $r_{\text{max}} = \min(128,s_x^2s_t)$. Note that
$r = s_x^2s_t$ corresponds to the full rank.

We now search for the optimum parameters for the second stage, setting the 
first stage parameters according to \eqref{eq:stage1_parameters}. The temporal
patch size is again set as $s_t = 3$ for both stages and the search regions are
kept as in \eqref{eq:search_region_parameters}. Figure
\ref{fig:rank-px-nsim-table-stage2} shows the average PSNRs over the four
sequences, obtained for each parameter configuration and each noise level.

From these results, we fix the parameters as follows:
\begin{equation}
	s_x = 5,\quad r = \max( \min(320/\sigma, r_{\text{max}}), r_{\text{min}}), \quad n_{\text{sim}} = 160.
	\label{eq:stage1_parameters}
\end{equation}
For the second stage, we set $r_{\text{max}} = \min(64,s_x^2s_t)$ and $r_{\text{min}} = 16$.

%We will fix the temporal size and for the
%temporal size of the patch we will vary it between $s_t = 1$ and $s_t = 4$ in
%the results section.

\begin{figure*}[htpb!]
	\begin{center}
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r2-np2-image_s10_average_derf.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r2-np2-image_s20_average_derf.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r2-np2-image_s40_average_derf.eps}\\
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r2-np2-image_s10_average_derf.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r2-np2-image_s20_average_derf.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r2-np2-image_s40_average_derf.eps}\\
	\end{center}
	\caption{Top row: average PSNRs over four sequences, obtained by varying the second stage parameters
		$r$ and $n_{\text{sim}}$. From left to right, results for $\sigma = 10,
		20, 40$. In each image, the contrast has been stretched so that white
		corresponds to the maximum PSNR and black to a decay of 1dB bellow the
		maximum. 
		Bottom: corresponding average running times. White corresponds to $50$ s/frame (using parallelization with four threads).}
	\label{fig:rank-nsim-image-stage2}
\end{figure*}

\begin{figure*}[htpb!]
	\begin{center}
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s10_bus.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s20_bus.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s40_bus.eps}\\
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s10_bus.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s20_bus.eps}%
		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s40_bus.eps}\\
	\end{center}
	\caption{Same as Figure \ref{fig:rank-nsim-image-stage2} but for the first stage.}
	\label{fig:rank-nsim-image-stage1}
\end{figure*}

%figs/params_tables/psnr_r1-np1-image_s10_bus.eps
%figs/params_tables/psnr_r1-np1-image_s20_bus.eps
%figs/params_tables/psnr_r1-np1-image_s40_bus.eps
%figs/params_tables/time_r1-np1-image_s10_bus.eps
%figs/params_tables/time_r1-np1-image_s20_bus.eps
%figs/params_tables/time_r1-np1-image_s40_bus.eps

%\begin{figure*}[htpb!]
%	\begin{center}
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r8_s10_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r16_s10_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r32_s10_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r64_s10_average.eps}\\
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r8_s20_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r16_s20_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r32_s20_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r64_s20_average.eps}\\
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r8_s40_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r16_s40_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r32_s40_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px1-np1-bars_1r64_s40_average.eps}\\
%	\end{center}
%	\caption{Average PSNRs for 64 configurations of the first stage parameters
%		$r$, $n_{\text{sim}}$ and $s_x$. From top to bottom, results for $\sigma = 10, 20, 40$.
%		From left to right: results for $r = 8, 16, 32, 64$.}
%	\label{fig:rank-px-nsim-table-stage1}
%\end{figure*}
%
%\begin{figure*}[htpb!]
%	\begin{center}
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r8_s10_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r16_s10_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r32_s10_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r64_s10_average.eps}\\
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r8_s20_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r16_s20_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r32_s20_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r64_s20_average.eps}\\
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r8_s40_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r16_s40_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r32_s40_average.eps}%
%		\includegraphics[width=.25\textwidth,height=.19\textwidth]{figs/params_tables/zoom_psnr_px2-np2-bars_2r64_s40_average.eps}\\
%	\end{center}
%	\caption{Average PSNRs for 64 configurations of the second stage parameters
%		$r$, $n_{\text{sim}}$ and $s_x$. From top to bottom, results for $\sigma = 10, 20, 40$.
%		From left to right: results for $r = 8, 16, 32, 64$.}
%	\label{fig:rank-px-nsim-table-stage2}
%\end{figure*}

%For the experiments shown in \S \ref{sec:results} we used the following 
%parameters.
%\begin{LaTeXdescription}
%	\item[Patch size:] In both stages, we fixed the patch size at $s = 5$. Better 
%		results can be obtained with higher patch sizes, but the computational cost
%		scales considerably (e.g. the inversion of the covariance matrix is of $O(s^6)$).
%	\item[Number of similar patches:] For the first stage, we set
%		$N^{(1)}_{\text{sim}} = 3s^2n_t$  (recall that $n_t$ is the temporal
%		extend of the search region). For the second step we 
%		found better results using fewer patches, thus we set $N^{(2)}_{\text{sim}} = 3/4 s^2n_t$.
%	\item[Search region:] In both stages, we used $n_x = s^2/2$.
%		For the temporal search region, we found a good trade-off
%		between computational time and quality of the results for $n_t = 5$. 
%	\item[Patch distance threshold:] When building the group of similar patches
%		in the second stage, more than $N_{\text{sim}}$ patches are allowed if their 
%		distances with respect to the reference patch are smaller than a threshold $\tau$.
%		As in \cite{Lebrun2013ipol}, we set $\tau = 4$ (the distance between patches is normalized by 
%		the number of elements in the patch and the number of channels).
%\end{LaTeXdescription}

% stage 1
%
% patch size $s = 5$
% spatial search region $n_x = 37$
% temporal search region $n_t = 0,3,5$
% number of similar patches $3 s^2 n_t$, 3/4 s^2 n_t$$
% beta $\beta = 1; 1.2$
% tau n/a $\tau = 16$  
% offset $= s/2$

% stage 2
%
% patch size 
% spatial search region
% temporal search region
% number of similar patches
% beta
% tau
% offset

\paragraph{Temporal patch size}

\begin{table*}[htp!]
	\begin{center}
		{%\small
		\renewcommand{\tabcolsep}{1.6mm}
		\renewcommand{\arraystretch}{1.3}
		\begin{tabular}{ c | l |c c | c c | c c | c c | c c | c c}
			\hline
			\rule{0pt}{10pt}$\sigma$ & Method            & \multicolumn{2}{c}{Tennis}  & \multicolumn{2}{c}{Coastguard}&\multicolumn{2}{c}{Foreman}& \multicolumn{2}{c}{Bus}     &\multicolumn{2}{c|}{Football}& \multicolumn{2}{c}{Average}\\\hline
			\multirow{1}{*}{$ 5$}
%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
			                      & V-BM3D               & \bsic{     } &       39.45  & \bsic{     } &       40.18  & \bsic{     } &       40.16  & \bsic{     } &       39.07  & \bsic{     } &              & \bsic{     } &              \\
			                      & V-BM4D-tip           & \bsic{     } & \best{39.98} & \bsic{     } & \best{41.13} & \bsic{     } & \best{41.38} & \bsic{     } & \best{40.21} & \bsic{     } & \best{     } & \bsic{     } & \best{     } \\
			                      & V-BM4D-mp            & \bsic{39.61} &       39.60  & \bsic{40.20} &       40.28  & \bsic{40.73} &       40.78  & \bsic{39.45} &       39.56  & \bsic{39.91} &       40.00  & \bsic{todo } &       todo   \\
%			                      & V-BM4D-np            & \bsic{toto } &       31.67  & \bsic{toto } &       32.24  & \bsic{toto } &       33.34  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  \\
%			                      & VNLB $n_t = 0$       & \bsic{toto } &       30.65  & \bsic{toto } &       32.70  & \bsic{toto } &       33.64  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  \\
%			                      & VNLB $n_t = 3$       & \bsic{toto } &       31.26  & \bsic{toto } &       33.35  & \bsic{toto } &       34.25  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  \\
%			                      & VNLB $n_t = 5$       & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 2$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
%                                                                                                                                                                                                                                         
			\multirow{1}{*}{$10$}
%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
			                      & V-BM3D               & \bsic{     } &       36.04  & \bsic{     } &       36.82  & \bsic{     } &       37.52  & \bsic{     } &       34.96  & \bsic{     } &              & \bsic{     } &              \\
			                      & V-BM4D-tip           & \bsic{     } & \best{36.42} & \bsic{     } & \best{37.27} & \bsic{     } &       37.92  & \bsic{     } &       36.23  & \bsic{     } &              & \bsic{     } &              \\
			                      & V-BM4D-mp            & \bsic{35.64} &       35.90  & \bsic{36.06} &       36.30  & \bsic{36.96} &       37.21  & \bsic{35.10} &       35.38  & \bsic{35.79} &       36.08  & \bsic{todo } &       todo   \\
%			                      & V-BM4D-np            & \bsic{toto } &       35.56  & \bsic{toto } &       36.20  & \bsic{toto } &       36.90  & \bsic{toto } &       35.09  & \bsic{toto } &       35.09  & \bsic{toto } &       35.09  \\
%			                      & VNLB $n_t = 0$       & \bsic{toto } &       34.43  & \bsic{toto } &       36.70  & \bsic{toto } &       37.21  & \bsic{toto } &       35.58  & \bsic{toto } &       35.58  & \bsic{toto } &       35.58  \\
%			                      & VNLB $n_t = 3$       & \bsic{toto } &       35.04  & \bsic{toto } &       37.19  & \bsic{toto } &       37.88  & \bsic{toto } &       36.19  & \bsic{toto } &       36.19  & \bsic{toto } &       36.19  \\
%			                      & VNLB $n_t = 5$       & \bsic{34.51} &       35.28  & \bsic{36.80} & \best{37.30} & \bsic{37.22} & \best{38.11} & \bsic{35.43} & \best{36.37} & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 2$     & \bsic{35.65} &       36.19  & \bsic{37.42} &       38.05  & \Bsic{37.86} &       38.74  & \Bsic{35.80} &       36.63  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \bsic{35.94} &       36.51  & \Bsic{37.57} &       38.35  & \Bsic{37.94} &       38.95  & \Bsic{35.86} &       36.79  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{36.02} & \Best{36.65} & \Bsic{37.53} & \Best{38.46} & \Bsic{37.85} & \Best{38.99} & \Bsic{35.86} & \Best{36.85} & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
%                                                                                                                                                                                                                                         
			\multirow{1}{*}{$15$}
			                      & CIFIC                & \bsic{     } &       32.76  & \bsic{     } &              & \bsic{     } &              & \bsic{     } &       33.47  & \bsic{     } &       31.59  & \bsic{     } &              \\
%			                      & V-BM3D               & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
%			                      & V-BM4D-tip           & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } \\
			                      & V-BM4D-mp            & \bsic{33.10} &       33.67  & \bsic{33.66} &       34.05  & \bsic{34.78} &       35.17  & \bsic{32.59} &       33.02  & \bsic{33.34} &       33.82  & \bsic{todo } &       todo   \\
%			                      & V-BM4D-np            & \bsic{toto } &       31.67  & \bsic{toto } &       32.24  & \bsic{toto } &       33.34  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  \\
%			                      & VNLB $n_t = 0$       & \bsic{toto } &       30.65  & \bsic{toto } &       32.70  & \bsic{toto } &       33.64  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  \\
%			                      & VNLB $n_t = 3$       & \bsic{toto } &       31.26  & \bsic{toto } &       33.35  & \bsic{toto } &       34.25  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  \\
%			                      & VNLB $n_t = 5$       & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 2$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
%                                                                                                                                                                                                                                         
			\multirow{1}{*}{$20$}
%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
			                      & V-BM3D               & \bsic{     } &       32.54  & \bsic{     } &       33.39  & \bsic{     } &       34.49  & \bsic{     } &       31.03  & \bsic{     } &              & \bsic{     } &              \\
			                      & V-BM4D-tip           & \bsic{     } & \best{32.88} & \bsic{     } & \best{33.61} & \bsic{     } & \best{34.62} & \bsic{     } & \best{32.27} & \bsic{     } & \best{     } & \bsic{     } & \best{     } \\
			                      & V-BM4D-mp            & \bsic{31.33} &       31.98  & \bsic{31.91} &       32.44  & \bsic{33.16} &       33.70  & \bsic{30.81} &       31.34  & \bsic{31.58} &       32.22  & \bsic{todo } &       todo   \\
%			                      & V-BM4D-np            & \bsic{toto } &       31.67  & \bsic{toto } &       32.24  & \bsic{toto } &       33.34  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  \\
%			                      & VNLB $n_t = 0$       & \bsic{toto } &       30.65  & \bsic{toto } &       32.70  & \bsic{toto } &       33.64  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  \\
%			                      & VNLB $n_t = 3$       & \bsic{toto } &       31.26  & \bsic{toto } &       33.35  & \bsic{toto } &       34.25  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  \\
%			                      & VNLB $n_t = 5$       & \bsic{30.76} &       31.49  & \bsic{32.94} & \best{33.55} & \bsic{33.69} &       34.45  & \bsic{31.58} & \best{32.35} & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 2$     & \bsic{32.12} &       32.56  & \bsic{33.98} &       34.30  & \bsic{34.55} &       35.32  & \bsic{32.11} &       32.71  & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \bsic{32.52} &       33.00  & \Bsic{34.15} &       34.60  & \Bsic{34.71} &       35.64  & \Bsic{32.26} &       32.97  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{32.67} & \Best{33.22} & \Bsic{34.15} & \Best{34.78} & \Bsic{34.63} & \Best{35.75} & \Bsic{32.30} & \Best{33.12} & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
%                                                                                                                                                                                                                                         
			\multirow{1}{*}{$25$}
			                      & CIFIC                & \bsic{     } &       29.74  & \bsic{     } &              & \bsic{     } &              & \bsic{     } &       30.48  & \bsic{     } &       28.82  & \bsic{     } &              \\
%			                      & V-BM3D               & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
%			                      & V-BM4D-tip           & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } \\
			                      & V-BM4D-mp            & \bsic{30.01} &       30.73  & \bsic{30.60} &       31.24  & \bsic{31.91} &       32.59  & \bsic{29.46} &       30.07  & \bsic{30.22} &       30.96  & \bsic{todo } &       todo   \\
%			                      & V-BM4D-np            & \bsic{toto } &       31.67  & \bsic{toto } &       32.24  & \bsic{toto } &       33.34  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  \\
%			                      & VNLB $n_t = 0$       & \bsic{toto } &       30.65  & \bsic{toto } &       32.70  & \bsic{toto } &       33.64  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  \\
%			                      & VNLB $n_t = 3$       & \bsic{toto } &       31.26  & \bsic{toto } &       33.35  & \bsic{toto } &       34.25  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  \\
%			                      & VNLB $n_t = 5$       & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 2$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
%                                                                                                                                                                                                                                         
%			\multirow{1}{*}{$30$}
%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
%			                      & V-BM3D               & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
%			                      & V-BM4D-tip           & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } \\
%			                      & V-BM4D-mp            & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%%			                      & V-BM4D-np            & \bsic{toto } &       31.67  & \bsic{toto } &       32.24  & \bsic{toto } &       33.34  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  \\
%%			                      & VNLB $n_t = 0$       & \bsic{toto } &       30.65  & \bsic{toto } &       32.70  & \bsic{toto } &       33.64  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  \\
%%			                      & VNLB $n_t = 3$       & \bsic{toto } &       31.26  & \bsic{toto } &       33.35  & \bsic{toto } &       34.25  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  \\
%%			                      & VNLB $n_t = 5$       & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
%%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%%			                      & VNLB   $s_t = 2$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%%			                      & VNLB   $s_t = 3$     & \bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 4$     & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
%%                                                                                                                                                                                                                                         
			\multirow{1}{*}{$40$}
%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
			                      & V-BM3D               & \bsic{     } &       29.20  & \bsic{     } & \best{29.99} & \bsic{     } &       31.17  & \bsic{     } &       27.34  & \bsic{     } &              & \bsic{     } &              \\
			                      & V-BM4D-tip           & \bsic{     } & \best{29.52} & \bsic{     } & \best{30.00} & \bsic{     } & \best{31.30} & \bsic{     } &       28.32  & \bsic{     } &              & \bsic{     } &              \\
			                      & V-BM4D-mp            & \bsic{27.34} &       28.14  & \bsic{27.81} &       28.73  & \bsic{29.01} &       30.09  & \bsic{26.67} &       27.44  & \bsic{27.45} &       28.35  & \bsic{todo } &       todo   \\
%			                      & V-BM4D-np            & \bsic{toto } &       27.97  & \bsic{toto } &       28.43  & \bsic{toto } &       29.69  & \bsic{toto } &       27.02  & \bsic{toto } &       27.02  & \bsic{toto } &       27.02  \\
%			                      & VNLB $n_t = 0$       & \bsic{toto } &       27.43  & \bsic{toto } &       28.88  & \bsic{toto } &       30.15  & \bsic{toto } &       27.60  & \bsic{toto } &       27.60  & \bsic{toto } &       27.60  \\
%			                      & VNLB $n_t = 3$       & \bsic{toto } &       27.97  & \bsic{toto } &       29.60  & \bsic{toto } &       30.72  & \bsic{toto } &       28.23  & \bsic{toto } &       28.23  & \bsic{toto } &       28.23  \\
%			                      & VNLB $n_t = 5$       & \bsic{27.17} &       28.11  & \bsic{28.81} &       29.78  & \bsic{29.72} &       30.82  & \bsic{27.65} & \best{28.40} & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 2$     & \bsic{28.44} &       29.28  & \bsic{30.18} &       30.94  & \bsic{30.87} &       32.00  & \bsic{28.21} &       28.96  & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \Bsic{28.86} &       29.73  & \Bsic{30.43} &       31.23  & \Bsic{31.03} &       32.39  & \Bsic{28.32} &       29.23  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{28.99} & \Best{29.96} & \Bsic{30.40} & \Best{31.34} & \Bsic{30.95} & \Best{32.55} & \Bsic{28.31} & \Best{29.39} & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
		\end{tabular}}
	\end{center}
% Command to print rounded psnrs
% for i in $(cat bus_s40_pt*/measures | grep PSNR_final | sed "s/^-PSNR_final\ =\ "//); do  echo "scale=2;(((10^2)*$i)+0.5)/(10^2)" | bc; done
	\caption{PSNRs obtained for the four classic color test sequences used in
	\cite{Maggioni2012}. See text for details.}
	\label{tab:psnr-classic-color}
\end{table*}

\begin{table*}[htp!]
	\begin{center}
		{\small
		\renewcommand{\tabcolsep}{1.6mm}
		\renewcommand{\arraystretch}{1.3}
		\begin{tabular}{ c | l |c c | c c | c c | c c | c c | c c | c c}
			\hline
			\rule{0pt}{6pt}$\sigma$ & Method             & \multicolumn{2}{c}{Tennis}  & \multicolumn{2}{c}{Salesman} &\multicolumn{2}{c}{Fl. garden}& \multicolumn{2}{c}{Mobile}  & \multicolumn{2}{c}{Bicycle}  & \multicolumn{2}{c|}{Stefan} & \multicolumn{2}{c}{Average} \\\hline
			\multirow{1}{*}{$10$}
			                      & LZD                  & \bsic{     } &       36.45  & \bsic{     } &       40.49   & \bsic{     } &       34.46   & \bsic{     } &       37.03  &              &               &              &              & \bsic{     } &       37.13  \\
			                      & V-BM4D-tip           & \bsic{     } &       35.22  & \bsic{     } &       37.30   & \bsic{     } &       32.81   &              &              &              &       37.66   &              &              & \bsic{     } &       35.11  \\
			                      & V-BM4D-mp            & \bsic{34.32} &       34.95  & \bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  & \bsic{todo } &       todo   \\\hline
%
			\multirow{1}{*}{$20$}
			                      & LZD                  & \bsic{     } &       33.36  & \bsic{     } &       37.52   & \bsic{     } &       31.35   & \bsic{     } &       33.47  &              &               &              &              & \bsic{     } &       34.08  \\
			                      & V-BM4D-tip           & \bsic{     } &       31.59  & \bsic{     } &       33.79   & \bsic{     } &       28.63   &              &              &              &       34.10   &              &              & \bsic{     } &       31.34  \\
			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \bsic{32.18} &       33.46   & \bsic{28.12} &       28.32   & \bsic{29.67} &       30.49  & \bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} & \bsic{todo } &       todo   \\\hline
%
			\multirow{1}{*}{$30$}
			                      & LZD                  & \bsic{     } &       31.62  & \bsic{     } &       36.05   & \bsic{     } &       29.09   & \bsic{     } &       30.36  &              &               &              &              & \bsic{     } &       32.25  \\
			                      & V-BM4D-tip           & \bsic{     } &       29.72  &              &       31.75   & \bsic{     } &       26.29   &              &              &              &       31.83   &              &              & \bsic{     } &       29.25  \\
			                      & V-BM4D-mp            & \bsic{28.89} &       29.37  & \bsic{29.56} &       31.02   & \bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \Bsic{todo } &       todo   & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{todo } &       todo   & \Bsic{todo } & \Best{todo }  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \Bsic{todo } &       todo   & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{todo } &       todo   & \bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo } & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{todo } & \Best{todo } & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } & \Best{todo } & \bsic{todo } &       todo    & \bsic{todo } & \Best{todo } & \bsic{todo } &       todo   \\\hline
%
			\multirow{1}{*}{$40$}
			                      & LZD                  & \bsic{     } &       30.79  & \bsic{     } &       35.12   & \bsic{     } &       27.56   & \bsic{     } &       28.93  &              &               &              &              & \bsic{     } &       31.16  \\
			                      & V-BM4D-tip           & \bsic{     } &       28.49  & \bsic{     } &       30.35   & \bsic{     } &       24.60   &              &              &              &       30.10   &              &              & \bsic{     } &       27.81  \\
			                      & V-BM4D-mp            & \bsic{27.67} &       28.38  & \bsic{27.81} &       29.37   & \bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} & \Bsic{todo } & \Best{todo } \\
			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} & \Bsic{todo } & \Best{todo } \\\hline
		\end{tabular}}
% Command to print rounded psnrs
% for i in $(cat bus_s40_pt*/measures | grep PSNR_final | sed "s/^-PSNR_final\ =\ "//); do  echo "scale=2;(((10^2)*$i)+0.5)/(10^2)" | bc; done
	\end{center}
	\caption{Quantitative denoising results for some classic grayscale test sequences. See text for details.}
	\label{tab:psnr-classic-gray}
\end{table*}

%\begin{table*}[htp!]
%	\begin{center}
%	\renewcommand{\tabcolsep}{2mm}
%	\renewcommand{\arraystretch}{1.0}
%	\begin{tabular}{ c | l |c c c c c}
%		\hline
%		\rule{0pt}{12pt}$\sigma$ & Method     & Army & DogDance & Evergreen & Mequon & Walking  \\\hline
%		\multirow{5}{*}{$10$} & V-BM4D-np      &       37.77  &       35.70  &       35.40  &       38.09  &       38.85  \\
%		                      & VNLB $n_t = 0$ &       36.90  &       35.42  &       34.84  &       38.43  &       38.86  \\
%		                      & VNLB $n_t = 3$ &       37.65  &       35.87  &       35.38  &       39.09  &       39.69  \\
%									 & VNLB $n_t = 5$ & \best{37.88} & \best{36.01} & \best{35.53} & \best{39.20} & \best{39.74} \\\hline
%%									                                                                                           
%		\multirow{5}{*}{$20$} & V-BM4D-np      &       32.91  &       31.50  &       30.94  &       33.60  &       34.27  \\
%		                      & VNLB $n_t = 0$ &       33.77  &       32.44  &       31.68  &       35.61  &       35.60  \\
%									 & VNLB $n_t = 3$ &       34.45  &       32.90  &       32.15  &       35.89  &       36.12  \\
%									 & VNLB $n_t = 5$ & \best{34.59} & \best{33.02} & \best{32.27} & \best{35.90} & \best{36.12} \\\hline
%%									                                                                                           
%		\multirow{5}{*}{$40$} & V-BM4D-np      &       30.42  &       29.29  &       28.65  &       31.02  &       31.64  \\
%		                      & VNLB $n_t = 0$ &       30.55  &       29.41  &       28.66  &       31.78  &       31.86  \\
%									 & VNLB $n_t = 3$ & \best{31.02} & \best{29.73} & \best{29.03} & \best{31.88} & \best{31.92} \\
%									 & VNLB $n_t = 5$ & \best{31.06} & \best{29.74} & \best{29.08} &       31.70  &       31.74  \\\hline
%	\end{tabular}
%	\end{center}
%	\caption{PSNRs obtained for the five color sequences from the Middlebury
%	dataset \cite{middleburyOflow}. See text for details.}
%	\label{tab:psnr-middlebury}
%\end{table*}

\section{Results}
\label{sec:results}

In this section we present results obtained with the proposed
method on some classic test sequences with Gaussian noise added.

\subsection{Results on color videos}

We considered five color test sequences, \emph{tennis}, \emph{coastguard},
\emph{foreman}, \emph{bus} and \emph{football}. The first four were chosen
because they were used in \cite{Maggioni2012}. The fifth one, \emph{football},
was added to test the performance of our method on a sequence with complex motions.

We compared our method with CIFIC \cite{Dai2013} and V-BM4D \cite{Maggioni2012}, two recent
state-of-the-art methods. For V-BM4D, we show results corresponding to two
different choices of parameters. The method labeled V-BM4D-\cite{Maggioni2012}
corresponds to the results reported
in \cite{Maggioni2012}. The result labeled V-BM4D-mp was
obtained using the implementation available online \cite{bm4dcode}. This
implementation provides three parameter profiles of increasing quality and
complexity: ``low complexity profile'', ``normal profile'' and ``modified
profile''. We show the results obtained with the modified (V-BM4D-mp) profile.

Let us note that the modified profile has a
computation time lower to that of our method. Running with a
single core in a Intel Xeon X7560 (2.27GHz) CPU, 
our current implementation takes on average $XXs$ per frame for a video of CIF
resolution ($352\times288$). V-BM4D takes $44s$ with the modified profile.
\todo{Compute running times!!!}

The results are shown in Table \ref{tab:psnr-classic}. The proposed method is
labeled VNLB. It achieves the highest PSNR values on all the considered
sequences and levels of noise, with a significant difference. The difference
increases for higher levels of noise. A possible reason for this is that both 
CIFIC and V-BM4D rely on motion estimation by 2D block matching, which might
not be reliable for high noise levels.

%We also show quantitative results obtained in for some sequences from the
%optical flow Middlebury dataset (the sequences have 8 frames each), and compare
%against V-BM4D-np (see table \ref{tab:psnr-middlebury}. For these sequences, the
%proposed method outpeforms V-BM4D-np.

For a qualitative analysis we show in Figure \ref{fig:results} results obtained
with nonlocal Bayes (setting $n_t = 5$) and V-BM4D-np. Interestingly, for $\sigma = 20$
and $40$, V-BM4D-np is able to better recover the wallpaper texture in tennis,
but does worse than VNLB for the foliage texture of the trees in bus. 
%One
%plausible reason for this is that the spatial bi-orthogonal wavelets and
%DCT transforms used by BM4D are very well suited to the structured pattern of the
%wallpaper.
For high levels of noise, the wallpaper texture is masked by the noise. 
It is possible that when comparing 2D patches the noise dominates in the
comparison. Using spatio-temporal volumes reduces the distance noise,
allowing to find similar patches with the same regular texture pattern.

\subsection{Evaluating temporal consistency}

An important aspect of the quality of any video processing algorithm is the 
temporal consistency of the result. Similar to previous works \cite{Liu2010, Sutour2014}
we evaluate quantitatively the temporal consistency of our denoising results.
To that aim run VNLB and V-BM4D-mp on four sequences of MPI Sintel's training
dataset. These are CGI color sequences with ground truth forward optical flow, which we
denote by $v:\Omega\times\{1,\dots,T-1\}\rightarrow \mathds R^2$. 
The forward optical flow $v(x,t)$ encodes the motion displacement of pixel $x$
between frames $t$ and $t +1$.
We use the optical flow to evaluate the variations along motion trajectories
added by the denoising algorithm. To that aim we estimate the derivative along
motion trajectories of the denoising error $e = \widetilde u - u$ as follows:
\[\partial_v e(x,t) =
\left\{
\begin{array}{l l}
	e(x + v(x,t), t+1) - e(x,t), & \text{if } (x,t)\not\in \mathcal{K},\\
	0 & \text{if } (x,t)\in \mathcal{K}.
\end{array}
\right.\]
Here $\mathcal K$ is the set of pixels that are occluded or escape out of the video
domain. The occlusion set $\mathcal K$ is also provided in MPI Sintel's database.
Note that since the optical flow is sub-pixelic, the value of $e(x + v(x,t),t+1)$
needs to be interpolated. We use bilinear interpolation.

We define a temporal consistency error as follows:
\[\text{TCE} = 10 \log_{10}\left(\frac{255^2 c|\Omega|T}{\|\partial_v e\|_2^2}\right)\]
where $\|\,\cdot\,\|_2^2$ is the $\ell_2$ norm, and $c, T, |\Omega|$ are the numbers
of channels, frames, and pixels in each frame, respectively.

Table \ref{tab:sintel} shows the PSNR and the TCE results obatained for four sequences of the
Sintel's database, and four levels of noise. For non-local Bayes, we show results obtained with 
the temporal patch length $s_t$ varying from $1$ to $4$. We can observe that the best results
are obtained by the proposed method with a patch of $3$ or $4$ frames depending
on the sequence. The TCE gap with V-BM4D-mp increases with the noise level. 
\todo{Comment on these results, but after the results have been recomputed with the right parameters!}

\begin{table*}[htp!]
	\begin{center}
		{%\small
		\renewcommand{\tabcolsep}{1.6mm}
		\renewcommand{\arraystretch}{1.3}
		\begin{tabular}{ c | l |c c | c c | c c | c c | c c}
			\hline
			\rule{0pt}{10pt}         & Sequence          &\multicolumn{2}{c|}{Bamboo 1}&\multicolumn{2}{c|}{Bandage 1}&\multicolumn{2}{c|}{Cave 4} &\multicolumn{2}{c|}{Market 5}& \multicolumn{2}{c}{Average} \\
			\rule{0pt}{10pt}$\sigma$ & Method            & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         \\\hline
			\multirow{1}{*}{$10$}
			                      & V-BM4D-mp            & \bsic{37.47} &       38.85  & \bsic{38.67} &       40.02  & \bsic{37.30} &       38.40  & \bsic{39.52} &       40.41  & \bsic{38.24} &       39.42  \\
			                      & VNLB   $s_t = 1$     & \bsic{37.48} &       39.74  & \bsic{39.85} &       41.83  & \Bsic{38.80} & \Best{40.82} & \Bsic{42.16} & \Best{44.10} & \bsic{39.57} &       41.62  \\
			                      & VNLB   $s_t = 2$     & \bsic{39.01} &       41.10  & \Bsic{40.74} & \Best{42.40} & \bsic{38.70} &       40.65  & \Bsic{42.23} & \Best{44.14} & \Bsic{40.17} & \Best{42.07} \\
			                      & VNLB   $s_t = 3$     & \bsic{39.40} & \Best{41.37} & \Bsic{40.74} & \Best{42.36} & \bsic{38.50} &       40.35  & \Bsic{42.17} & \Best{44.08} & \Bsic{40.20} & \Best{42.04} \\
			                      & VNLB   $s_t = 4$     & \Bsic{39.44} & \Best{41.33} & \bsic{40.51} &       42.12  & \bsic{38.30} &       40.05  & \bsic{42.07} &       43.97  & \bsic{40.08} &       41.86  \\\hline
%
			\multirow{1}{*}{$20$}
			                      & V-BM4D-mp            & \bsic{33.23} &       34.70  & \bsic{34.63} &       35.98  & \bsic{33.85} &       34.94  & \bsic{35.30} &       36.13  & \bsic{34.25} &       35.44  \\
			                      & VNLB   $s_t = 1$     & \bsic{33.19} &       35.53  & \bsic{35.60} &       37.76  & \bsic{35.35} &       37.31  & \bsic{37.90} &       39.88  & \bsic{35.51} &       37.62  \\
			                      & VNLB   $s_t = 2$     & \bsic{34.95} &       36.93  & \bsic{37.03} &       38.69  & \Bsic{35.60} & \Best{37.52} & \Bsic{38.60} & \Best{40.52} & \bsic{36.55} &       38.41  \\
			                      & VNLB   $s_t = 3$     & \bsic{35.48} &       37.40  & \Bsic{37.27} & \Best{38.86} & \Bsic{35.54} & \Best{37.43} & \Bsic{38.60} & \Best{40.54} & \Bsic{36.72} & \Best{38.56} \\
			                      & VNLB   $s_t = 4$     & \Bsic{35.65} & \Best{37.54} & \Bsic{37.26} & \Best{38.84} & \bsic{35.44} &       37.32  & \Bsic{38.50} & \Best{40.48} & \Bsic{36.71} & \Best{38.55} \\\hline
%
			\multirow{1}{*}{$40$}
			                      & V-BM4D-mp            & \bsic{29.07} &       30.46  & \bsic{30.45} &       31.82  & \bsic{30.50} &       31.57  & \bsic{30.93} &       31.74  & \bsic{30.24} &       31.40  \\
			                      & VNLB   $s_t = 1$     & \bsic{29.25} &       31.57  & \bsic{31.44} &       33.67  & \bsic{31.70} &       33.70  & \bsic{33.47} &       35.44  & \bsic{31.46} &       33.60  \\
			                      & VNLB   $s_t = 2$     & \bsic{31.18} &       32.99  & \bsic{33.40} &       35.06  & \Bsic{32.60} & \Best{34.61} & \bsic{34.76} &       36.63  & \bsic{32.98} &       34.82  \\
			                      & VNLB   $s_t = 3$     & \bsic{31.69} &       33.46  & \Bsic{33.76} & \Best{35.32} & \Bsic{32.70} & \Best{34.69} & \Bsic{34.91} & \Best{36.79} & \Bsic{33.27} & \Best{35.07} \\
			                      & VNLB   $s_t = 4$     & \Bsic{31.88} & \Best{33.64} & \Bsic{33.82} & \Best{35.37} & \Bsic{32.70} & \Best{34.66} & \Bsic{34.89} & \Best{36.77} & \Bsic{33.22} & \Best{35.11} \\\hline
		\end{tabular}}
	\end{center}
	\caption{PSNRs and TCEs obtained for the four CGI sequences from MPI
	Sintel's database. See text for details.}
	\label{tab:sintel}
\end{table*}

\begin{figure*}[thpb!]
	\begin{center}
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_orig_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_nisy_s10_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_nisy_s20_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_nisy_s40_row220_col040-180_fra080-220.png}\\
%		               \hspace{0.2\textwidth}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_nisy_s10_row220_col040-180_fra080-220.png}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_nisy_s20_row220_col040-180_fra080-220.png}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_nisy_s40_row220_col040-180_fra080-220.png}\\
		               \hspace{0.2\textwidth}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_bm4d_s10_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_bm4d_s20_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_bm4d_s40_row220_col040-180_fra080-220.png}\\
		               \hspace{0.2\textwidth}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_bm4d_s10_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_bm4d_s20_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_bm4d_s40_row220_col040-180_fra080-220.png}\\
%		               \hspace{0.2\textwidth}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt2_s10_row220_col040-180_fra080-220.png}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt2_s20_row220_col040-180_fra080-220.png}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt2_s40_row220_col040-180_fra080-220.png}\\
%		               \hspace{0.2\textwidth}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt2_s10_row220_col040-180_fra080-220.png}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt2_s20_row220_col040-180_fra080-220.png}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt2_s40_row220_col040-180_fra080-220.png}\\
%		               \hspace{0.2\textwidth}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt3_s10_row220_col040-180_fra080-220.png}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt3_s20_row220_col040-180_fra080-220.png}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt3_s40_row220_col040-180_fra080-220.png}\\
%		               \hspace{0.2\textwidth}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt3_s10_row220_col040-180_fra080-220.png}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt3_s20_row220_col040-180_fra080-220.png}%
%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt3_s40_row220_col040-180_fra080-220.png}\\
		               \hspace{0.2\textwidth}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt4_s10_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt4_s20_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt4_s40_row220_col040-180_fra080-220.png}\\
		               \hspace{0.2\textwidth}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt4_s10_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt4_s20_row220_col040-180_fra080-220.png}%
		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt4_s40_row220_col040-180_fra080-220.png}\\
%		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_vnlb_s10.png}
%		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_vnlb_s20.png}
%		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_vnlb_s40.png}\\
%		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_bm4d_s10.png}
%		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_bm4d_s20.png}
%		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_bm4d_s40.png}
	\end{center}
	\caption{Visualizing the temporal coherency of the denoising. The images
		show a horizontal slice of the \emph{mobile} video, at row $220$, showing
		the ball (gray tube) as it gets hit by the train (black region in the
		left). The vertical axis is time, and the horizontal axis is the $x$ axis
		in the video. On the first row: the original sequence and noisy version with
		noise $10$, $20$ and $40$. The following rows show the results obtained
		with V-BM4D and their corresponding error, and the results for VNLB with their
		error. Notice that the error introduced by VNLB varies smoothly in time, reducing
		the flickering effect. The contrast of the images has been enhanced for
		better visualization.
} \label{fig:time-diff}
\end{figure*}

% \begin{table}
% 	\begin{center}
% 	\renewcommand{\tabcolsep}{3mm}
% 	\renewcommand{\arraystretch}{1.3}
% 	\begin{tabular}{ c | c |c c c c}
% 		\hline
% 		\rule{0pt}{12pt}$\sigma$ & Method     & Tennis       & Coastguard   & Foreman      & Bus          \\\hline
% 		\multirow{5}{*}{$10$} & V-BM4D        & \best{36.42} & \best{37.27} &       37.92  & \best{36.23} \\
% 		                      & V-BM3D        &       36.04  &       36.82  &       37.52  &       34.96  \\
% 		                      & VNLB $n_t = 0$ &       32.13  &       33.75  &       34.60  &       32.71  \\
% 		                      & VNLB $n_t = 3$ &       35.12  &       37.20  &       37.89  &       36.14  \\
% 									 & VNLB $n_t = 5$ &       35.19  & \best{37.26} & \best{38.00} &       36.11  \\\hline
% %									 
% 		\multirow{5}{*}{$25$} & V-BM4D        & \best{32.88} & \best{33.61} & \best{34.62} & \best{32.27} \\
% 		                      & V-BM3D        &       32.54  &       33.39  &       34.49  &       31.03  \\
% 		                      & VNLB $n_t = 0$ &       30.58  &       32.47  &       33.44  &       31.26  \\
% 									 & VNLB $n_t = 3$ &       31.22  &       33.39  &       34.28  &       32.01  \\
% 		                      & VNLB $n_t = 5$ &       31.25  &       33.44  &       34.34  &       31.94  \\\hline
% %									 
% 		\multirow{5}{*}{$40$} & V-BM4D        & \best{29.52} & \best{30.00} & \best{31.30} & \best{28.32} \\
% 		                      & V-BM3D        &       29.20  &       29.99  &       31.17  &       27.34  \\
% 		                      & VNLB $n_t = 0$ &       27.24  &       28.55  &       29.74  &       27.37  \\
% 									 & VNLB $n_t = 3$ &       27.96  &       29.68  &       30.85  &       28.17  \\
% 									 & VNLB $n_t = 5$ &       28.02  &       29.76  &       30.94  &       28.14  \\\hline
% 	\end{tabular}
% 
% 	\bigskip
% 	\end{center}
% 	\caption{PSNR for sequences taken from the Middlebury optical flow benchmark.}
% \end{table}

\section{Conclusions}
\label{sec:conclusion}

We presented a Bayesian video denoising algorithm assuming a Gaussian model for similar patches. 
We show preliminary results and compare it with two methods from the
state-of-the-art, V-BM3D and V-BM4D.
The resulting method does not require motion estimation.%, and as such it shows
%lower temporal coherency than V-BM4D.
In terms of PSNR
the results obtained show state-of-the-art performance for low levels of noise.
For higher levels of noise the performance is comparable to V-BM3D and improves
over the default version of V-BM4D.

%
% ---- Bibliography ----
%

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,image_denoising,video_denoising}

\end{document}

### 2015-08-07 doc/201507_tip/paper.tex
[doc][tip] Preliminar version of parameter section

@@
 
-Let us consider the complexity associated to the building and filtering of a
-group of $N_{\text{sim}}$ similar patches. Due to the speed-ups described in
-the previous section, the actual number of groups of similar patches processed
-might vary, but it is typically a fraction of the number of pixels in the video.
+Let us consider the complexity of constructing and filtering a group of
+$N_{\text{sim}}$ similar patches. Due to the speed-ups described in the
+previous section, the actual number of groups of similar patches processed
+might vary between a $1\%$ and a $10\%$ of the total number of pixels in the
+video.
 
@@
 
-The more expensive operations are the computation of the covariance matrix and
+The most expensive operations are the computation of the covariance matrix and
 of its principal directions.
@@
 
-Each stage of the algorithm has the following 6 parameters: the spatial and temporal patch sizes
-$s_x$ and $s_t$, the spatial and temporal sizes of the search region $w_x$ and
+Each stage of the algorithm has the following 6 parameters: the spatial and temporal components of the patch size
+$s_x$ and $s_t$, the spatial and temporal components of the search region $w_x$ and
 $w_t$, the number of similar patches $n_{\text{sim}}$ and the rank of the a priori
@@
 
-\paragraph{Patch size} We have found that the
-
-\paragraph{Patch size, rank and number of similar patches} We have found that the
-final PSNR has a non-trivial behaviour with respect to any of these parameters.
-To set them, we explore the parameter space varying the rank $r$, the spatial
-patch size $s_x$ and the number of similar patches $n_{\text{sim}}$. The reduce
-the dimensionality of the parameter space, for the moment we fix the temporal
-patch size at $s_t = 3$.
-
-First we fix the parameters of the second stage at 
-\[r = 16,\,\, n_{\text{sim}} = 160,\,\, s_x = 5,\,\, s_t = 3,\,\, w_x = 37,\,\, w_t = 5,\]
-and vary the parameters of the first stage. We considered ranks $r = 8, 16, 32, 64$,   
-patch sizes $s_x = 3,5,7,9$ and number of patches $n_{\text{sim}} = 80, 160, 320, 640$.
-For all $4^3 = 64$ combinations, we considered three levels of noise $\sigma = 10, 20, 40$
-and run our method on four sequences. The
-sequences used were \emph{army, dog dance, evergreen} and \emph{walking} from
-the Middlebury optical flow benchmark \cite{middleburyOflow}.
-The sequences have 8 frames of size $584 \times 388$ (\emph{army}) and $640
-\times 480$ (\emph{dog dance, evergreen} and \emph{walking}).
-These sequences were chosen to have some variety of motions, textures, etc.
-
-Figure \ref{fig:rank-px-nsim-table-stage1} shows for each configuration of
-parameters and level of noise, the average PSNR over the four sequences. The
-cyan bars correspond to the basic estimate and the ones in magenta to the final
-estimate.
-
-It can be observed that several parameter configurations can give very similar
-results. For example, with $\sigma = 10$, equivalent results can be obtained 
-with $s_x = 3, r = 16, n_{\text{sim}} = 80$, $s_x = 5, r = 32, n_{\text{sim}} = 160$
-or  $s_x = 7, r = 64, n_{\text{sim}} = 320$.
-The one with the least computational cost is chosen. This means,
-smaller patches sizes, smaller ranks, and a larger number of similar patches.
-
-Another thing to notice is that the final and the basic PSNRs do not always
+\paragraph{Patch size} Let us consider first the spatial patch
+size $s_x$. The impact of a variation of the $s_x$ in the results
+depends on the value of the rank parameter. For instance, if the rank is set
+too low, then increasing the patch size has a negative effect on the results.
+For sufficiently high rank, increasing the size of the patch leads on average
+to an improvement of the results. This improvement however comes at a considerable
+increase in the computation time, since our current implementation is $\mathcal
+O(s_x^4)$.  We have found that a good trade-off between computation time and
+quality is given by $s_x = 5$.
+
+The impact of the temporal patch size $s_t$ will be discussed later in Section \ref{sec:results}.
+
+\paragraph{Rank and number of similar patches} These parameters are intimately linked.
+Intuitively, smaller groups obtained by keeping only the most similar patches have 
+only a few modes of variation and thus are better modelled with a low rank
+covariance matrix. As the group of patches grows bigger, patches in the group
+are not as similar anymore, and a higher rank is needed to model these additional 
+variation.
+To find appropriate values for these parameters, we compute denoising results
+varying the rank $r$ and the number of similar patches $n_{\text{sim}}$, while
+keeping all other parameters fixed. Results are computed for four 20 frames clips
+extracted from the sequences \emph{bus}, \emph{foreman}, \emph{football} and
+\emph{tennis}, adding noise of $\sigma = 10, 20, 40$.
+%
+We do this for each stage, starting by the second.
+
+On this first experiment, the parameters of the first stage are fixed at:
+\[w_x = 37,\,\,w_t = 5\,\,s_x = 5,\,\,s_t = 4,\,\,n_{\text{sim}} = 375,\,\,r = 100.\]
+\todo{Check these parameters}
+Note that $r = 100$ is the full rank.
+For the second stage, we fix $w_x = 37$, $w_t = 5$, $s_x = 5$ and $s_t = 3$, while varying 
+$r$ in $10,20,\dots,80$ and $n_{\text{sim}}$ in $50, 150,200,250$.
+The results can be visualized in Figure \ref{fig:rank-nsim-image-stage2}. The images in the 
+figure show the PSNR loss in dB with respect to the maximum value attained at each noise level.
+White means 0dB (\ie the set of parameters where the maximum was attained) and black means a loss
+greater or equal than 1dB.
+
+We can observe that, at constant $n_{\text{sim}}$ there is an optimal value for the rank. Bellow
+these value the PSNR drops sharply, and above it, the decay is slower. The
+optimal rank for a given $n_{\text{sim}}$ increases with $n_{\text{sim}}$ and decreases with $\sigma$.
+Best results are obtained for small $n_{\text{sim}}$. However, this also entails a higher running time, 
+since it increases the number of groups of similar patches that need to be
+processed. We found a good compromise by setting $n_{\text{sim}} = 150$ and $r$ as a decreasing function of $\sigma$:
+\[r(\sigma) = 40 - \frac1{10}(\sigma - 40),\]
+which corresponds to a line through $(s=10, r = 40)$ and $(s=40, r = 30)$.
+
+We now perform a similar search for the first stage, setting the second step parameters as:
+\[w_x = 37,\,\,w_t = 5\,\,s_x = 5,\,\,s_t = 3,\,\,n_{\text{sim}} = 150,\,\,r(\sigma).\]
+The first stage parameters are as before, expect that we now vary $r$ in $10,20,\dots,100$
+and $n_{\text{sim}}$ in $50,100,\dots,650$. Results are shown in Figure
+\ref{fig:rank-nsim-image-stage1}. Note that since our objective is to maximize
+the final PSNR, we show here the final PSNR. 
+The final and the basic PSNRs do not always
 have the same behaviour. Improving the basic PSNR does not always lead to an
@@
 
-The strength of the denoising is controlled through the rank and the number of
-patches in the group. For lower levels of noise, \ie $\sigma = 10$, better
-PSRNs can be achieved with a higher rank and using a smaller number of similar
-patches. When increasing the noise, the rank should be decreased and the number 
-of similar patches increased.
-
-In accordance to these observations, we will set the parameters as a function of
-$\sigma$ as follows:
+In fact, best results are obtained using the full rank covariance matrix. 
+In accordance to these observations, we will set the first values for $r$ and $n_{\text{sim}}$ as:
 \begin{equation}
-	s_t = 5,\quad\quad r = \min(640/\sigma, r_{\text{max}}), \quad\quad n_{\text{sim}} = 16\sigma.
+	r = s_x^2s_t \quad\quad n_{\text{sim}} = 350.
 	\label{eq:stage1_parameters}
 \end{equation}
-%\begin{align}
-%	s_t &= 5\\
-%	r &= \min(640/\sigma, r_{\text{max}}) \\
-%	n_{\text{sim}} &= 16\sigma. 
+
+%
+%
+%
+%First we fix the parameters of the second stage at 
+%\[r = 16,\,\, n_{\text{sim}} = 160,\,\, s_x = 5,\,\, s_t = 3,\,\, w_x = 37,\,\, w_t = 5,\]
+%and vary the parameters of the first stage. We considered ranks $r = 8, 16, 32, 64$,   
+%patch sizes $s_x = 3,5,7,9$ and number of patches $n_{\text{sim}} = 80, 160, 320, 640$.
+%For all $4^3 = 64$ combinations, we considered three levels of noise $\sigma = 10, 20, 40$
+%and run our method on four sequences. The
+%sequences used were \emph{army, dog dance, evergreen} and \emph{walking} from
+%the Middlebury optical flow benchmark \cite{middleburyOflow}.
+%The sequences have 8 frames of size $584 \times 388$ (\emph{army}) and $640
+%\times 480$ (\emph{dog dance, evergreen} and \emph{walking}).
+%These sequences were chosen to have some variety of motions, textures, etc.
+%
+%Figure \ref{fig:rank-px-nsim-table-stage1} shows for each configuration of
+%parameters and level of noise, the average PSNR over the four sequences. The
+%cyan bars correspond to the basic estimate and the ones in magenta to the final
+%estimate.
+%
+%It can be observed that several parameter configurations can give very similar
+%results. For example, with $\sigma = 10$, equivalent results can be obtained 
+%with $s_x = 3, r = 16, n_{\text{sim}} = 80$, $s_x = 5, r = 32, n_{\text{sim}} = 160$
+%or  $s_x = 7, r = 64, n_{\text{sim}} = 320$.
+%The one with the least computational cost is chosen. This means,
+%smaller patches sizes, smaller ranks, and a larger number of similar patches.
+%
+%Another thing to notice is that the final and the basic PSNRs do not always
+%have the same behaviour. Improving the basic PSNR does not always lead to an
+%improvement in the final one. The reason for this is that it is preferable to
+%apply a conservative noise reduction leaving some noise in the basic estimate
+%(high variance but small bias). In the second step, this residual noise has
+%little effect on the estimation of the patch distances and the \emph{a priori} covariance
+%matrix. On the other hand, applying a more aggressive denoising in first step
+%might increase the basic PSNR, but the second step cannot recover the lost
+%signal components.
+%
+%The strength of the denoising is controlled through the rank and the number of
+%patches in the group. For lower levels of noise, \ie $\sigma = 10$, better
+%PSRNs can be achieved with a higher rank and using a smaller number of similar
+%patches. When increasing the noise, the rank should be decreased and the number 
+%of similar patches increased.
+%
+%In accordance to these observations, we will set the parameters as a function of
+%$\sigma$ as follows:
+%\begin{equation}
+%	s_t = 5,\quad\quad r = \min(640/\sigma, r_{\text{max}}), \quad\quad n_{\text{sim}} = 16\sigma.
 %	\label{eq:stage1_parameters}
-%\end{align}
-We set the maximum rank to be $r_{\text{max}} = \min(128,s_x^2s_t)$. Note that
-$r = s_x^2s_t$ corresponds to the full rank.
-
-We now search for the optimum parameters for the second stage, setting the 
-first stage parameters according to \eqref{eq:stage1_parameters}. The temporal
-patch size is again set as $s_t = 3$ for both stages and the search regions are
-kept as in \eqref{eq:search_region_parameters}. Figure
-\ref{fig:rank-px-nsim-table-stage2} shows the average PSNRs over the four
-sequences, obtained for each parameter configuration and each noise level.
-
-From these results, we fix the parameters as follows:
-\begin{equation}
-	s_x = 5,\quad r = \max( \min(320/\sigma, r_{\text{max}}), r_{\text{min}}), \quad n_{\text{sim}} = 160.
-	\label{eq:stage1_parameters}
-\end{equation}
-For the second stage, we set $r_{\text{max}} = \min(64,s_x^2s_t)$ and $r_{\text{min}} = 16$.
+%\end{equation}
+%%\begin{align}
+%%	s_t &= 5\\
+%%	r &= \min(640/\sigma, r_{\text{max}}) \\
+%%	n_{\text{sim}} &= 16\sigma. 
+%%	\label{eq:stage1_parameters}
+%%\end{align}
+%We set the maximum rank to be $r_{\text{max}} = \min(128,s_x^2s_t)$. Note that
+%$r = s_x^2s_t$ corresponds to the full rank.
+%
+%We now search for the optimum parameters for the second stage, setting the 
+%first stage parameters according to \eqref{eq:stage1_parameters}. The temporal
+%patch size is again set as $s_t = 3$ for both stages and the search regions are
+%kept as in \eqref{eq:search_region_parameters}. Figure
+%\ref{fig:rank-px-nsim-table-stage2} shows the average PSNRs over the four
+%sequences, obtained for each parameter configuration and each noise level.
+%
+%From these results, we fix the parameters as follows:
+%\begin{equation}
+%	s_x = 5,\quad r = \max( \min(320/\sigma, r_{\text{max}}), r_{\text{min}}), \quad n_{\text{sim}} = 160.
+%	\label{eq:stage1_parameters}
+%\end{equation}
+%For the second stage, we set $r_{\text{max}} = \min(64,s_x^2s_t)$ and $r_{\text{min}} = 16$.
 
@@
 
-\paragraph{Temporal patch size}
-
 \begin{table*}[htp!]
@@
 			                      & V-BM4D-mp            & \bsic{39.61} &       39.60  & \bsic{40.20} &       40.28  & \bsic{40.73} &       40.78  & \bsic{39.45} &       39.56  & \bsic{39.91} &       40.00  & \bsic{todo } &       todo   \\
-%			                      & V-BM4D-np            & \bsic{toto } &       31.67  & \bsic{toto } &       32.24  & \bsic{toto } &       33.34  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  \\
-%			                      & VNLB $n_t = 0$       & \bsic{toto } &       30.65  & \bsic{toto } &       32.70  & \bsic{toto } &       33.64  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  \\
-%			                      & VNLB $n_t = 3$       & \bsic{toto } &       31.26  & \bsic{toto } &       33.35  & \bsic{toto } &       34.25  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  \\
-%			                      & VNLB $n_t = 5$       & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
-%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 2$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{38.73} &       39.26  & \bsic{40.90} &       41.38  & \bsic{41.19} &       41.82  & \bsic{39.85} &       40.32  & \bsic{41.10} &       41.64  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 2$     & \bsic{39.56} &       40.05  & \bsic{41.61} &       42.08  & \bsic{41.75} &       42.42  & \bsic{40.10} &       40.73  & \bsic{41.29} &       41.88  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \bsic{39.82} &       40.16  & \Bsic{41.75} &       42.39  & \Bsic{41.85} &       42.57  & \Bsic{40.16} &       40.96  & \Bsic{41.27} &       41.85  & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{39.92} & \Best{40.03} & \Bsic{41.76} & \Best{42.41} & \Bsic{41.84} & \Best{42.48} & \Bsic{40.18} & \Best{40.92} & \Bsic{41.23} & \Best{41.67} & \Bsic{todo } & \Best{todo } \\\hline
 %
@@
 			                      & V-BM4D-mp            & \bsic{35.64} &       35.90  & \bsic{36.06} &       36.30  & \bsic{36.96} &       37.21  & \bsic{35.10} &       35.38  & \bsic{35.79} &       36.08  & \bsic{todo } &       todo   \\
-%			                      & V-BM4D-np            & \bsic{toto } &       35.56  & \bsic{toto } &       36.20  & \bsic{toto } &       36.90  & \bsic{toto } &       35.09  & \bsic{toto } &       35.09  & \bsic{toto } &       35.09  \\
-%			                      & VNLB $n_t = 0$       & \bsic{toto } &       34.43  & \bsic{toto } &       36.70  & \bsic{toto } &       37.21  & \bsic{toto } &       35.58  & \bsic{toto } &       35.58  & \bsic{toto } &       35.58  \\
-%			                      & VNLB $n_t = 3$       & \bsic{toto } &       35.04  & \bsic{toto } &       37.19  & \bsic{toto } &       37.88  & \bsic{toto } &       36.19  & \bsic{toto } &       36.19  & \bsic{toto } &       36.19  \\
-%			                      & VNLB $n_t = 5$       & \bsic{34.51} &       35.28  & \bsic{36.80} & \best{37.30} & \bsic{37.22} & \best{38.11} & \bsic{35.43} & \best{36.37} & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
-%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 2$     & \bsic{35.65} &       36.19  & \bsic{37.42} &       38.05  & \Bsic{37.86} &       38.74  & \Bsic{35.80} &       36.63  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \bsic{35.94} &       36.51  & \Bsic{37.57} &       38.35  & \Bsic{37.94} &       38.95  & \Bsic{35.86} &       36.79  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{36.02} & \Best{36.65} & \Bsic{37.53} & \Best{38.46} & \Bsic{37.85} & \Best{38.99} & \Bsic{35.86} & \Best{36.85} & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{34.54} &       35.16  & \bsic{36.81} &       37.23  & \bsic{37.25} &       38.01  & \bsic{35.47} &       36.21  & \bsic{36.88} &       37.69  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 2$     & \bsic{35.67} &       36.28  & \bsic{37.42} &       38.10  & \Bsic{37.87} &       38.82  & \Bsic{35.82} &       36.69  & \Bsic{37.11} &       38.02  & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \bsic{35.94} &       36.61  & \Bsic{37.56} &       38.50  & \Bsic{37.93} &       39.08  & \Bsic{35.88} &       36.98  & \Bsic{37.03} &       38.08  & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{36.02} & \Best{36.73} & \Bsic{37.50} & \Best{38.64} & \Bsic{37.83} & \Best{39.12} & \Bsic{35.87} & \Best{37.11} & \Bsic{36.91} & \Best{38.03} & \Bsic{todo } & \Best{todo } \\\hline
 %
@@
 			                      & V-BM4D-mp            & \bsic{33.10} &       33.67  & \bsic{33.66} &       34.05  & \bsic{34.78} &       35.17  & \bsic{32.59} &       33.02  & \bsic{33.34} &       33.82  & \bsic{todo } &       todo   \\
-%			                      & V-BM4D-np            & \bsic{toto } &       31.67  & \bsic{toto } &       32.24  & \bsic{toto } &       33.34  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  \\
-%			                      & VNLB $n_t = 0$       & \bsic{toto } &       30.65  & \bsic{toto } &       32.70  & \bsic{toto } &       33.64  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  \\
-%			                      & VNLB $n_t = 3$       & \bsic{toto } &       31.26  & \bsic{toto } &       33.35  & \bsic{toto } &       34.25  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  \\
-%			                      & VNLB $n_t = 5$       & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
-%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 2$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{32.31} &       32.94  & \bsic{34.32} &       34.95  & \bsic{35.06} &       35.97  & \bsic{33.04} &       33.83  & \bsic{34.62} &       35.50  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 2$     & \bsic{33.36} &       34.12  & \bsic{35.24} &       36.03  & \bsic{35.74} &       36.82  & \bsic{33.39} &       34.29  & \bsic{34.83} &       35.83  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \bsic{33.59} &       34.58  & \Bsic{35.33} &       36.38  & \Bsic{35.74} &       37.05  & \Bsic{33.42} &       34.57  & \Bsic{34.72} &       35.88  & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{33.64} & \Best{34.78} & \Bsic{35.21} & \Best{36.52} & \Bsic{35.57} & \Best{37.11} & \Bsic{33.37} & \Best{34.76} & \Bsic{34.54} & \Best{35.86} & \Bsic{todo } & \Best{todo } \\\hline
 %
@@
 			                      & V-BM4D-mp            & \bsic{31.33} &       31.98  & \bsic{31.91} &       32.44  & \bsic{33.16} &       33.70  & \bsic{30.81} &       31.34  & \bsic{31.58} &       32.22  & \bsic{todo } &       todo   \\
-%			                      & V-BM4D-np            & \bsic{toto } &       31.67  & \bsic{toto } &       32.24  & \bsic{toto } &       33.34  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  \\
-%			                      & VNLB $n_t = 0$       & \bsic{toto } &       30.65  & \bsic{toto } &       32.70  & \bsic{toto } &       33.64  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  \\
-%			                      & VNLB $n_t = 3$       & \bsic{toto } &       31.26  & \bsic{toto } &       33.35  & \bsic{toto } &       34.25  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  \\
-%			                      & VNLB $n_t = 5$       & \bsic{30.76} &       31.49  & \bsic{32.94} & \best{33.55} & \bsic{33.69} &       34.45  & \bsic{31.58} & \best{32.35} & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
-%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 2$     & \bsic{32.12} &       32.56  & \bsic{33.98} &       34.30  & \bsic{34.55} &       35.32  & \bsic{32.11} &       32.71  & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \bsic{32.52} &       33.00  & \Bsic{34.15} &       34.60  & \Bsic{34.71} &       35.64  & \Bsic{32.26} &       32.97  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{32.67} & \Best{33.22} & \Bsic{34.15} & \Best{34.78} & \Bsic{34.63} & \Best{35.75} & \Bsic{32.30} & \Best{33.12} & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{30.78} &       31.38  & \bsic{32.95} &       33.45  & \bsic{33.71} &       34.37  & \bsic{31.60} &       32.19  & \bsic{33.20} &       33.85  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 2$     & \bsic{32.13} &       32.69  & \bsic{33.98} &       34.36  & \bsic{34.55} &       35.41  & \bsic{32.13} &       32.80  & \bsic{33.52} &       34.27  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \bsic{32.53} &       33.12  & \Bsic{34.14} &       34.74  & \Bsic{34.69} &       35.75  & \Bsic{32.27} &       33.13  & \Bsic{33.50} &       34.35  & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{32.67} & \Best{33.32} & \Bsic{34.13} & \Best{34.92} & \Bsic{34.60} & \Best{35.86} & \Bsic{32.31} & \Best{33.34} & \Bsic{33.41} & \Best{34.34} & \Bsic{todo } & \Best{todo } \\\hline
 %
@@
 			                      & V-BM4D-mp            & \bsic{30.01} &       30.73  & \bsic{30.60} &       31.24  & \bsic{31.91} &       32.59  & \bsic{29.46} &       30.07  & \bsic{30.22} &       30.96  & \bsic{todo } &       todo   \\
-%			                      & V-BM4D-np            & \bsic{toto } &       31.67  & \bsic{toto } &       32.24  & \bsic{toto } &       33.34  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  \\
-%			                      & VNLB $n_t = 0$       & \bsic{toto } &       30.65  & \bsic{toto } &       32.70  & \bsic{toto } &       33.64  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  \\
-%			                      & VNLB $n_t = 3$       & \bsic{toto } &       31.26  & \bsic{toto } &       33.35  & \bsic{toto } &       34.25  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  \\
-%			                      & VNLB $n_t = 5$       & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
-%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 2$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
-%
-%			\multirow{1}{*}{$30$}
-%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
-%			                      & V-BM3D               & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
-%			                      & V-BM4D-tip           & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } \\
-%			                      & V-BM4D-mp            & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%%			                      & V-BM4D-np            & \bsic{toto } &       31.67  & \bsic{toto } &       32.24  & \bsic{toto } &       33.34  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  & \bsic{toto } &       30.95  \\
-%%			                      & VNLB $n_t = 0$       & \bsic{toto } &       30.65  & \bsic{toto } &       32.70  & \bsic{toto } &       33.64  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  & \bsic{toto } &       31.39  \\
-%%			                      & VNLB $n_t = 3$       & \bsic{toto } &       31.26  & \bsic{toto } &       33.35  & \bsic{toto } &       34.25  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  & \bsic{toto } &       32.11  \\
-%%			                      & VNLB $n_t = 5$       & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } &       todo   & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
-%%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%%			                      & VNLB   $s_t = 2$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%%			                      & VNLB   $s_t = 3$     & \bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 4$     & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
-%%
+			                      & VNLB   $s_t = 1$     & \bsic{29.67} &       30.27  & \bsic{31.51} &       32.18  & \bsic{32.43} &       33.30  & \bsic{30.39} &       30.95  & \bsic{31.92} &       32.74  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 2$     & \bsic{30.88} &       31.57  & \bsic{32.79} &       33.40  & \bsic{33.46} &       34.30  & \bsic{30.89} &       31.50  & \bsic{32.34} &       33.16  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \bsic{31.30} &       32.05  & \Bsic{33.00} &       33.73  & \Bsic{33.60} &       34.61  & \Bsic{31.01} &       31.83  & \Bsic{32.32} &       33.22  & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{31.44} & \Best{32.30} & \Bsic{32.97} & \Best{33.88} & \Bsic{33.51} & \Best{34.73} & \Bsic{31.02} & \Best{32.05} & \Bsic{32.20} & \Best{33.21} & \Bsic{todo } & \Best{todo } \\\hline
+%
 			\multirow{1}{*}{$40$}
@@
 			                      & V-BM4D-mp            & \bsic{27.34} &       28.14  & \bsic{27.81} &       28.73  & \bsic{29.01} &       30.09  & \bsic{26.67} &       27.44  & \bsic{27.45} &       28.35  & \bsic{todo } &       todo   \\
-%			                      & V-BM4D-np            & \bsic{toto } &       27.97  & \bsic{toto } &       28.43  & \bsic{toto } &       29.69  & \bsic{toto } &       27.02  & \bsic{toto } &       27.02  & \bsic{toto } &       27.02  \\
-%			                      & VNLB $n_t = 0$       & \bsic{toto } &       27.43  & \bsic{toto } &       28.88  & \bsic{toto } &       30.15  & \bsic{toto } &       27.60  & \bsic{toto } &       27.60  & \bsic{toto } &       27.60  \\
-%			                      & VNLB $n_t = 3$       & \bsic{toto } &       27.97  & \bsic{toto } &       29.60  & \bsic{toto } &       30.72  & \bsic{toto } &       28.23  & \bsic{toto } &       28.23  & \bsic{toto } &       28.23  \\
-%			                      & VNLB $n_t = 5$       & \bsic{27.17} &       28.11  & \bsic{28.81} &       29.78  & \bsic{29.72} &       30.82  & \bsic{27.65} & \best{28.40} & \bsic{todo } & \best{todo } & \bsic{todo } & \best{todo } \\
-%			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 2$     & \bsic{28.44} &       29.28  & \bsic{30.18} &       30.94  & \bsic{30.87} &       32.00  & \bsic{28.21} &       28.96  & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \Bsic{28.86} &       29.73  & \Bsic{30.43} &       31.23  & \Bsic{31.03} &       32.39  & \Bsic{28.32} &       29.23  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{28.99} & \Best{29.96} & \Bsic{30.40} & \Best{31.34} & \Bsic{30.95} & \Best{32.55} & \Bsic{28.31} & \Best{29.39} & \Bsic{todo } & \Best{todo } & \Bsic{todo } & \Best{todo } \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{27.17} &       28.04  & \bsic{28.80} &       29.72  & \bsic{29.72} &       30.85  & \bsic{27.64} &       28.32  & \bsic{29.13} &       30.11  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 2$     & \bsic{28.43} &       29.38  & \bsic{30.16} &       31.03  & \bsic{30.84} &       32.09  & \bsic{28.21} &       29.07  & \bsic{29.63} &       30.67  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \Bsic{28.84} &       29.83  & \Bsic{30.40} &       31.32  & \Bsic{30.99} &       32.50  & \Bsic{28.31} &       29.38  & \Bsic{29.64} &       30.76  & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{28.97} & \Best{30.05} & \Bsic{30.36} & \Best{31.45} & \Bsic{30.89} & \Best{32.65} & \Bsic{28.29} & \Best{29.57} & \Bsic{29.52} & \Best{30.76} & \Bsic{todo } & \Best{todo } \\\hline
 		\end{tabular}}

### 2015-08-09 src/unit_tests/testLibMatrix.cpp
[src] Improved testLibMatrix (more command line params and addition of noise)

@@ -102,9 +102,17 @@ int main(int argc, char **argv)
 	const int i_lastFrame  = clo_option("-l", 0, "Last frame");
 	const int i_frameStep  = clo_option("-s", 1, "Frame step");
 	const int i_sigma      = clo_option("-sigma", 0, "Add noise of standard deviation sigma");
-	const unsigned px      = clo_option("-px", 0, "Current point of analysis");
-	const unsigned py      = clo_option("-py", 0, "Current point of analysis");
-	const unsigned pt      = clo_option("-pt", 0, "Current point of analysis");
+	const unsigned px      = clo_option("-PAx", 0, "Point of analysis");
+	const unsigned py      = clo_option("-PAy", 0, "Point of analysis");
+	const unsigned pt      = clo_option("-PAt", 0, "Point of analysis");
+
+	//! Video NLB parameters relevant to the computation of distances
+	const int time_search  = clo_option("-wt", 2, "> Search window temporal radius");
+	const int space_search = clo_option("-wx",-1, "> Search window spatial  radius");
+	const int patch_sizex  = clo_option("-px",-1, "> Spatial  patch size");
+	const int patch_sizet  = clo_option("-pt", 1, "> Temporal patch size");
+	const int num_patches  = clo_option("-np",-1, "> Number of similar patches");
+	const int rank         = clo_option("-r" ,-1, "> Covariance matrix rank");
 
 	//! Load video
 	Video<float> vid_ori;
@@ -118,16 +126,22 @@ int main(int argc, char **argv)
 		using std::vector;
 
 		//! RGB to YUV
-		Video<float> vid(vid_ori);
+		Video<float> vid;
+		VideoUtils::addNoise(vid_ori, vid, i_sigma, 1);
 		VideoUtils::transformColorSpace(vid, true);
 
 		//! Initialize parameter structures
-		VideoNLB::nlbParams prms1, prms2;
+		VideoNLB::nlbParams prms1;
 		{
-			VideoNLB::initializeNlbParameters(prms1, 1, i_sigma, vid.sz, 0, 1);
-			VideoNLB::initializeNlbParameters(prms2, 2, i_sigma, vid.sz, 0, 1);
+			//! Initialize parameter structures
[…]

### 2015-08-09 src/NlBayes/VideoNLBayes.cpp
[src] Fixed bug in total_variance estimation in Bayes estimate with LAPACK eig (stage 1)
	... and apply bayes filter in the principal components without
	using sqrtf.

@@ -1357,6 +1357,10 @@ float computeBayesEstimateStep1_LR_EIG_LAPACK(
 		//! Compute the covariance matrix of the set of similar patches
 		covarianceMatrix(io_group[c], i_mat.covMat, p_nSimP, sPC);
 
+		//! Estimate total variance
+		for (int i = 0; i < sPC; ++i)
+			total_variance += std::max(i_mat.covMat[i*sPC + i] - sigma2, 0.f);
+
 		//! Compute leading eigenvectors
 		int info = matrixEigs(i_mat.covMat, sPC, r, i_mat.covEigVals, i_mat.covEigVecs);
 
@@ -1364,37 +1368,26 @@ float computeBayesEstimateStep1_LR_EIG_LAPACK(
 		for (int i = 0; i < r; ++i)
 		{
 			i_mat.covEigVals[i] -= std::min(i_mat.covEigVals[i], sigma2);
+//			i_mat.covEigVals[i] -= sigma2;
 			rank_variance  += i_mat.covEigVals[i];
-			total_variance += i_mat.covEigVals[i];
-		}
-
-		for (int i = r; i < sPC; ++i)
-		{
-			i_mat.covEigVals[i] -= std::min(i_mat.covEigVals[i], sigma2);
-			total_variance += i_mat.covEigVals[i];
 		}
 
 		//! Compute eigenvalues-based coefficients of Bayes' filter
 		for (unsigned k = 0; k < r; ++k)
-			i_mat.covEigVals[k] = 1.f / sqrtf( 1. + sigma2 / i_mat.covEigVals[k] );
-
-		//! Scale eigenvectors using the filter coefficients
-		float *eigVecs = i_mat.covEigVecs.data();
-		for (unsigned k = 0; k < r  ; ++k)
-		for (unsigned i = 0; i < sPC; ++i)
-			*eigVecs++ *= i_mat.covEigVals[k];
+			i_mat.covEigVals[k] = 1.f / ( 1. + sigma2 / i_mat.covEigVals[k] );
 
 		/* NOTE: io_groupNoisy, if read as a column-major matrix, contains in each
 		 * row a patch. Thus, in column-major storage it corresponds to X^T, where
 		 * each column of X contains a centered data point.
 		 *
 		 * We need to compute the noiseless estimage hX as 
-		 * hX = U * U' * X
-		 * where U is the matrix with the normalized eigenvectors.
[…]

### 2015-08-19 tools/derf_generate_details.m
[tools] Improvements to ease creation of figures

@@ -6,54 +6,124 @@ base_path = '/media/pariasm/tera/funes/denoising/';
 bm4d_path = [base_path 'algos/results/VBM4D/'];
 orig_path = [base_path 'data/derf/'];
 %nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps5_2ps5_2wx37_2r16_2np160/'];
-nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/'];
+%nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/'];
+nlb3_colo_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps5_2ps5_tip/'];
+nlb3_mono_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps7_tip/'];
+nisy_path = bm4d_path;
 
 
 % generated tiles ------------------- %
-% tennis       050-090-030 150+150+30 %
-% tennis       040-150-070 150+150+30 %
-% bus          060-020-020 150+150+30 %
-% bus          110-150-010 150+150+30 %
-% stefan_mono  090-180-265 150+150+30 %
-% stefan_mono  060-130-005 150+150+30 %
-% mobile_mono  060-060-080 100+100+30 %
-% mobile_mono  188-188-065 100+100+30 %
+% tennis       050,090,030 150,150,30 %
+% tennis       040,150,070 150,150,30 %
+% bus          060,020,020 150,150,30 %
+% bus          110,150,010 150,150,30 %
+% stefan_mono  090,180,265 150,150,30 %
+% stefan_mono  060,130,005 150,150,30 %
+% mobile_mono  060,060,080 100,100,30 %
+% mobile_mono  188,188,065 100,100,30 %
 % ----------------------------------- %
 
-ti = 060;
-tj = 060;
-tt = 080;
-tile_i = [ti:ti + 100];
-tile_j = [tj:tj + 100];
-tile_t = [tt:tt +  30];
-
-addpath '../../../../time_filter/src/';
-
 % sequence data
-seqnames = {'football_mono','mobile_mono','stefan_mono','tennis_mono'};
[…]

### 2015-08-19 tools/psnr_vs_rank_np_images.m

@@ -1,7 +1,7 @@
 root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/';
 
 stage2_folder = [root_folder 'table_2r_vs_2np_derf/'];
-stage1_folder = [root_folder 'table_1r_vs_1np_bus/'];
+stage1_folder = [root_folder 'table_1r_vs_1np_derf/'];
 
 % % stage 2 ---------------------------------------------------
 % ranks = [10:10:80];
@@ -105,116 +105,164 @@ stage1_folder = [root_folder 'table_1r_vs_1np_bus/'];
 
 
 % stage 1 ---------------------------------------------------
-ranks = [10:10:120];
-nsims = [50:100:650];
-nseqs = 1;
-
-f10 = zeros(length(nsims),length(ranks),nseqs);
-f20 = zeros(length(nsims),length(ranks),nseqs);
-f40 = zeros(length(nsims),length(ranks),nseqs);
-
-f10(:,:,1) = load([stage1_folder 'table_fpsnr_bus_s10']);
-%f10(:,:,2) = load([stage1_folder 'table_fpsnr_football_s10']);
-%f10(:,:,3) = load([stage1_folder 'table_fpsnr_foreman_s10']);
-%f10(:,:,4) = load([stage1_folder 'table_fpsnr_tennis_s10']);
-
-f20(:,:,1) = load([stage1_folder 'table_fpsnr_bus_s20']);
-%f20(:,:,2) = load([stage1_folder 'table_fpsnr_football_s20']);
-%f20(:,:,3) = load([stage1_folder 'table_fpsnr_foreman_s20']);
-%f20(:,:,4) = load([stage1_folder 'table_fpsnr_tennis_s20']);
-
-f40(:,:,1) = load([stage1_folder 'table_fpsnr_bus_s40']);
-%f40(:,:,2) = load([stage1_folder 'table_fpsnr_football_s40']);
-%f40(:,:,3) = load([stage1_folder 'table_fpsnr_foreman_s40']);
-%f40(:,:,4) = load([stage1_folder 'table_fpsnr_tennis_s40']);
-
 ranks = [10:10:100];
-f10 = f10(:,1:end-2,:)
-f20 = f20(:,1:end-2,:)
-f40 = f40(:,1:end-2,:)
[…]

### 2015-08-19 tools/psnr_vs_rank_np_images_mono.m

@@ -1,0 +1,319 @@
+root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/';
+
+stage1_folder = [root_folder 'table_1r_vs_1np_mono/'];
+stage2_folder = [root_folder 'table_2r_vs_2np_mono/'];
+
+% % stage 2 ---------------------------------------------------
+% ranks = [10:10:80];
+% nsims = [50:50:200];
+% nseqs = 4;
+% 
+% f10 = zeros(length(nsims),length(ranks),nseqs);
+% f20 = zeros(length(nsims),length(ranks),nseqs);
+% f40 = zeros(length(nsims),length(ranks),nseqs);
+% 
+% f10(:,:,1) = load([stage2_folder 'table_fpsnr_tennis_mono_s10']);
+% f10(:,:,2) = load([stage2_folder 'table_fpsnr_mobile_mono_s10']);
+% f10(:,:,3) = load([stage2_folder 'table_fpsnr_foreman_s10']);
+% f10(:,:,4) = load([stage2_folder 'table_fpsnr_tennis_s10']);
+% 
+% f20(:,:,1) = load([stage2_folder 'table_fpsnr_tennis_mono_s20']);
+% f20(:,:,2) = load([stage2_folder 'table_fpsnr_mobile_mono_s20']);
+% f20(:,:,3) = load([stage2_folder 'table_fpsnr_foreman_s20']);
+% f20(:,:,4) = load([stage2_folder 'table_fpsnr_tennis_s20']);
+% 
+% f40(:,:,1) = load([stage2_folder 'table_fpsnr_tennis_mono_s40']);
+% f40(:,:,2) = load([stage2_folder 'table_fpsnr_mobile_mono_s40']);
+% f40(:,:,3) = load([stage2_folder 'table_fpsnr_foreman_s40']);
+% f40(:,:,4) = load([stage2_folder 'table_fpsnr_tennis_s40']);
+% 
+% mf10 = mean(f10,3);
+% mf20 = mean(f20,3);
+% mf40 = mean(f40,3);
+% 
+% ef10 = mf10 - max(mf10(:));
+% ef20 = mf20 - max(mf20(:));
+% ef40 = mf40 - max(mf40(:));
+% 
[…]

### 2015-08-19 src/NlBayes/VideoNLBayes.cpp
[src] beta set to one for grayscale images

@@ -150,8 +150,9 @@ void initializeNlbParameters(
 	//! Parameter used to estimate the covariance matrix
 	if (p_size.channels == 1)
 	{
-		if(s1) o_params.beta = (p_sigma < 15.f ? 1.1f : (p_sigma < 70.f ? 1.f : 0.9f));
-		else   o_params.beta = (p_sigma < 15.f ? 1.1f : (p_sigma < 35.f ? 1.f : 0.9f));
+		o_params.beta = 1.f;
+//		if(s1) o_params.beta = (p_sigma < 15.f ? 1.1f : (p_sigma < 70.f ? 1.f : 0.9f));
+//		else   o_params.beta = (p_sigma < 15.f ? 1.1f : (p_sigma < 35.f ? 1.f : 0.9f));
 	}
 	else
 	{

### 2015-08-19 doc/201507_tip/paper.tex
[doc] Updated grayscale PSNR tables with result of second attempt.
- Figures for first stage parameter selection (first attemp) based on derf average instead of bus.
- References added.

@@
 	\begin{center}
-		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s10_bus.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s20_bus.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s40_bus.eps}\\
-		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s10_bus.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s20_bus.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s40_bus.eps}\\
+		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s10_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s20_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s40_average_derf.eps}\\
+		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s10_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s20_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s40_average_derf.eps}\\
 	\end{center}
@@
 			\multirow{1}{*}{$10$}
-			                      & LZD                  & \bsic{     } &       36.45  & \bsic{     } &       40.49   & \bsic{     } &       34.46   & \bsic{     } &       37.03  &              &               &              &              & \bsic{     } &       37.13  \\
+			                      & LZD                  & \bsic{     } & \Best{36.45} & \bsic{     } & \Best{40.49}  & \bsic{     } & \Best{34.46}  & \bsic{     } & \Best{37.03} &              &               &              &              & \bsic{     } &       37.13  \\
 			                      & V-BM4D-tip           & \bsic{     } &       35.22  & \bsic{     } &       37.30   & \bsic{     } &       32.81   &              &              &              &       37.66   &              &              & \bsic{     } &       35.11  \\
-			                      & V-BM4D-mp            & \bsic{34.32} &       34.95  & \bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  & \bsic{todo } &       todo   \\\hline
+			                      & V-BM4D-mp            & \Bsic{34.32} &       34.95  & \Bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \Bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       33.29  & \bsic{34.62} &       35.15   & \bsic{30.80} &       31.22   & \bsic{32.34} &       32.79  & \bsic{36.21} &       37.72   & \bsic{33.20} &       33.79  & \bsic{todo } &       todo   \\
+										 & VNLB   $s_t = 2$     & \Bsic{34.35} &       34.68  & \bsic{35.87} &       36.62   & \bsic{32.41} &       32.92   & \Bsic{34.26} &       34.78  & \bsic{36.86} & \Best{38.55}  & \Bsic{33.73} & \Best{34.38} & \Bsic{todo } &       todo   \\
+										 & VNLB   $s_t = 3$     & \Bsic{34.34} &       35.23  & \bsic{35.63} &       37.08   & \bsic{32.39} &       33.18   & \bsic{34.02} &       35.25  & \bsic{36.57} & \Best{38.45}  & \bsic{33.45} & \Best{34.36} & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{34.25} &       35.40  & \bsic{35.39} &       37.21   & \Bsic{32.54} &       33.10   & \bsic{34.03} &       35.48  & \bsic{36.05} &       38.27   & \bsic{33.39} &       34.10  & \bsic{todo } &       todo   \\\hline
+%			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  & \bsic{todo } &       todo   \\\hline
 %
 			\multirow{1}{*}{$20$}
-			                      & LZD                  & \bsic{     } &       33.36  & \bsic{     } &       37.52   & \bsic{     } &       31.35   & \bsic{     } &       33.47  &              &               &              &              & \bsic{     } &       34.08  \\
+			                      & LZD                  & \bsic{     } & \Best{33.36} & \bsic{     } & \Best{37.52}  & \bsic{     } & \Best{31.35}  & \bsic{     } & \Best{33.47} &              &               &              &              & \bsic{     } &       34.08  \\
 			                      & V-BM4D-tip           & \bsic{     } &       31.59  & \bsic{     } &       33.79   & \bsic{     } &       28.63   &              &              &              &       34.10   &              &              & \bsic{     } &       31.34  \\
-			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \bsic{32.18} &       33.46   & \bsic{28.12} &       28.32   & \bsic{29.67} &       30.49  & \bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} & \bsic{todo } &       todo   \\\hline
+			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \Bsic{32.18} &       33.46   & \Bsic{28.12} &       28.32   & \Bsic{29.67} &       30.49  & \Bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 1$     & \bsic{29.62} &       30.16  & \bsic{30.76} &       31.54   & \bsic{26.17} &       26.56   & \bsic{27.89} &       28.39  & \bsic{32.41} &       33.77   & \bsic{28.69} &       29.26  & \bsic{todo } &       todo   \\
+										 & VNLB   $s_t = 2$     & \Bsic{30.81} &       31.37  & \bsic{31.98} &       33.08   & \bsic{27.89} &       28.41   & \Bsic{29.69} &       30.41  & \bsic{33.17} & \Best{34.97}  & \Bsic{29.32} & \Best{30.00} & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \bsic{29.88} &       31.62  & \bsic{30.60} &       33.05   & \bsic{27.50} &       28.89   & \bsic{29.02} &       30.86  & \bsic{31.23} &       34.26   & \bsic{28.51} & \Best{30.08} & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \bsic{29.49} &       31.64  & \bsic{30.10} &       32.94   & \bsic{27.47} &       29.07   & \bsic{28.86} &       31.12  & \bsic{30.51} &       33.88   & \bsic{28.26} & \Best{30.03} & \bsic{todo } &       todo   \\\hline
+%			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} & \bsic{todo } &       todo   \\\hline
 %
 			\multirow{1}{*}{$30$}
-			                      & LZD                  & \bsic{     } &       31.62  & \bsic{     } &       36.05   & \bsic{     } &       29.09   & \bsic{     } &       30.36  &              &               &              &              & \bsic{     } &       32.25  \\
+			                      & LZD                  & \bsic{     } & \Best{31.62} & \bsic{     } & \Best{36.05}  & \bsic{     } & \Best{29.09}  & \bsic{     } & \Best{30.36} &              &               &              &              & \bsic{     } &       32.25  \\
 			                      & V-BM4D-tip           & \bsic{     } &       29.72  &              &       31.75   & \bsic{     } &       26.29   &              &              &              &       31.83   &              &              & \bsic{     } &       29.25  \\
-			                      & V-BM4D-mp            & \bsic{28.89} &       29.37  & \bsic{29.56} &       31.02   & \bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 2$     & \Bsic{todo } &       todo   & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{todo } &       todo   & \Bsic{todo } & \Best{todo }  & \Bsic{todo } &       todo   & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \Bsic{todo } &       todo   & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{todo } &       todo   & \bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo } & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \bsic{todo } & \Best{todo } & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } & \Best{todo } & \bsic{todo } &       todo    & \bsic{todo } & \Best{todo } & \bsic{todo } &       todo   \\\hline
+			                      & V-BM4D-mp            & \Bsic{28.89} &       29.37  & \Bsic{29.56} &       31.02   & \Bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \Bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 1$     & \bsic{27.32} &       28.20  & \bsic{27.94} &       29.14   & \bsic{23.62} &       23.96   & \bsic{25.42} &       25.82  & \bsic{29.50} &       31.08   & \bsic{26.14} &       26.69  & \bsic{todo } &       todo   \\
+										 & VNLB   $s_t = 2$     & \bsic{28.65} &       29.51  & \Bsic{29.55} &       30.93   & \bsic{25.33} &       25.78   & \Bsic{27.31} &       27.90  & \bsic{30.70} & \Best{32.63}  & \Bsic{26.99} &       27.55  & \Bsic{todo } &       todo   \\
+										 & VNLB   $s_t = 3$     & \bsic{27.49} &       29.71  & \bsic{27.91} &       30.91   & \bsic{24.75} &       26.36   & \bsic{26.30} &       28.43  & \bsic{28.45} &       31.95   & \bsic{25.95} & \Best{27.72} & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \bsic{26.92} &       29.64  & \bsic{27.28} &       30.73   & \bsic{24.60} &       26.60   & \bsic{26.04} &       28.68  & \bsic{27.61} &       31.50   & \bsic{25.57} & \Best{27.71} & \bsic{todo } &       todo   \\\hline
 %
 			\multirow{1}{*}{$40$}
-			                      & LZD                  & \bsic{     } &       30.79  & \bsic{     } &       35.12   & \bsic{     } &       27.56   & \bsic{     } &       28.93  &              &               &              &              & \bsic{     } &       31.16  \\
+			                      & LZD                  & \bsic{     } & \Best{30.79} & \bsic{     } & \Best{35.12}  & \bsic{     } & \Best{27.56}  & \bsic{     } & \Best{28.93} &              &               &              &              & \bsic{     } &       31.16  \\
 			                      & V-BM4D-tip           & \bsic{     } &       28.49  & \bsic{     } &       30.35   & \bsic{     } &       24.60   &              &              &              &       30.10   &              &              & \bsic{     } &       27.81  \\
-			                      & V-BM4D-mp            & \bsic{27.67} &       28.38  & \bsic{27.81} &       29.37   & \bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo    & \bsic{todo } &       todo   & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} & \Bsic{todo } & \Best{todo } \\
-			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} & \Bsic{todo } & \Best{todo } \\\hline
+			                      & V-BM4D-mp            & \Bsic{27.67} &       28.38  & \Bsic{27.81} &       29.37   & \Bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \Bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 1$     & \bsic{25.65} &       26.83  & \bsic{25.97} &       27.49   & \bsic{21.89} &       22.25   & \bsic{23.57} &       24.11  & \bsic{27.32} &       29.03   & \bsic{24.27} &       24.97  & \bsic{todo } &       todo   \\
+										 & VNLB   $s_t = 2$     & \bsic{27.09} &       28.27  & \bsic{27.67} &       29.46   & \bsic{23.56} &       24.06   & \Bsic{25.48} &       26.17  & \bsic{28.64} & \Best{30.90}  & \Bsic{25.21} &       25.89  & \bsic{todo } &       todo   \\
+										 & VNLB   $s_t = 3$     & \bsic{25.66} &       28.33  & \bsic{25.93} &       29.31   & \bsic{22.84} &       24.65   & \bsic{24.35} &       26.69  & \bsic{26.31} &       30.11   & \bsic{24.11} & \Best{26.08} & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \bsic{24.98} &       28.16  & \bsic{25.18} &       29.03   & \bsic{22.62} &       24.89   & \bsic{23.98} &       26.90  & \bsic{25.41} &       29.59   & \bsic{23.64} & \Best{26.05} & \Bsic{todo } &       todo   \\\hline
+%			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} & \Bsic{todo } & \Best{todo } \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} & \Bsic{todo } & \Best{todo } \\\hline
 		\end{tabular}}
@@
 method on some classic test sequences with Gaussian noise added.
+We consider separatedly the cases of grayscale and color videos.
+
+\subsection{Results on grayscale videos}
+
+We present denoising results on six classic test sequences used commonly in the
+literature. We compare against two state-of-the-art methods: V-BM4D
+\cite{Maggioni2012}, and the method of Li, Zhang and Dai \cite{LiZhangDai2011}
+which we call I-SA-BM4D, since it can be regarded as an iterative version of BM4D \cite{Maggioni2013}
+using shape adaptive 3D patches, as in \todo{REF}.  
+For V-BM4D, we show results corresponding to two
+different choices of parameters. The method labeled V-BM4D-tip
+corresponds to the results reported
+in \cite{Maggioni2012}. The results labeled V-BM4D-mp were
+obtained using the implementation available online \cite{bm4dcode}. This
+implementation provides three parameter profiles of increasing quality and
+complexity: ``low complexity profile'', ``normal profile'' and ``modified
+profile''. We show the results obtained with the modified profile.
+
+Each sequence was contaminated with white Gaussian noise of $\sigma =
+10,20,30,40$. Table \ref{tab:psnr-classic-gray} shows the
+PSNR values obtained after denoising. For our method, we show results varying the temporal
+component of the patch size between $1$ (2D patch) and $4$ frames.
+For our method and V-BM4D-mp we show the PSNR of the basic estimate as well.
+
+The best results by a large margin are the ones reported in
+\cite{LiZhangDai2011}. This method builds uppon BM4D, which in \cite{Maggioni2013}
+is applied to volumetric imagery. In this work, its applicability to video is
+also explored, and the results show that it is inferior to V-BM4D, at least 
+for moderate noise levels. The method of Li, Zhang and Dai \cite{LiZhangDai2011} 
+considers shape adaptive patches, and also several iterations (in each iteration,
+the previous iterate is used as an oracle to compute patch distances and the
+signal energy in the Wiener filtering step) \todo{Check this}. It seems that both elements
+contribute to achieve this significant difference.
+
+We can see that our results are comarable with the ones of V-BM4D. \todo{We need to find new parameters
+for grayscale sequences. This discussion needs to be rewritten based on the updated results.}
 
@@
 We compared our method with CIFIC \cite{Dai2013} and V-BM4D \cite{Maggioni2012}, two recent
-state-of-the-art methods. For V-BM4D, we show results corresponding to two
-different choices of parameters. The method labeled V-BM4D-\cite{Maggioni2012}
+state-of-the-art methods. As with grayscale videos, for V-BM4D, we show results corresponding to two
+different parameter configurations: V-BM4D-tip
 corresponds to the results reported
-in \cite{Maggioni2012}. The result labeled V-BM4D-mp was
-obtained using the implementation available online \cite{bm4dcode}. This
-implementation provides three parameter profiles of increasing quality and
-complexity: ``low complexity profile'', ``normal profile'' and ``modified
-profile''. We show the results obtained with the modified (V-BM4D-mp) profile.
+in \cite{Maggioni2012}, and V-BM4D-mp corresponds to the ``modified profile''
+of the implementation available online \cite{bm4dcode}.
 
@@
 		\renewcommand{\arraystretch}{1.3}
+%		\begin{tabular}{ c | l |c c | c c | c c | c c | c c}
+%			\hline
+%			\rule{0pt}{10pt}         & Sequence          &\multicolumn{2}{c|}{Bamboo 1}&\multicolumn{2}{c|}{Bandage 1}&\multicolumn{2}{c|}{Cave 4} &\multicolumn{2}{c|}{Market 5}& \multicolumn{2}{c}{Average} \\
+%			\rule{0pt}{10pt}$\sigma$ & Method            & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         \\\hline
+%			\multirow{1}{*}{$10$}
+%			                      & V-BM4D-mp            & \bsic{37.47} &       38.85  & \bsic{38.67} &       40.02  & \bsic{37.30} &       38.40  & \bsic{39.52} &       40.41  & \bsic{38.24} &       39.42  \\
+%			                      & VNLB   $s_t = 1$     & \bsic{37.48} &       39.74  & \bsic{39.85} &       41.83  & \Bsic{38.80} & \Best{40.82} & \Bsic{42.16} & \Best{44.10} & \bsic{39.57} &       41.62  \\
+%			                      & VNLB   $s_t = 2$     & \bsic{39.01} &       41.10  & \Bsic{40.74} & \Best{42.40} & \bsic{38.70} &       40.65  & \Bsic{42.23} & \Best{44.14} & \Bsic{40.17} & \Best{42.07} \\
+%			                      & VNLB   $s_t = 3$     & \bsic{39.40} & \Best{41.37} & \Bsic{40.74} & \Best{42.36} & \bsic{38.50} &       40.35  & \Bsic{42.17} & \Best{44.08} & \Bsic{40.20} & \Best{42.04} \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{39.44} & \Best{41.33} & \bsic{40.51} &       42.12  & \bsic{38.30} &       40.05  & \bsic{42.07} &       43.97  & \bsic{40.08} &       41.86  \\\hline
+%%
+%			\multirow{1}{*}{$20$}
+%			                      & V-BM4D-mp            & \bsic{33.23} &       34.70  & \bsic{34.63} &       35.98  & \bsic{33.85} &       34.94  & \bsic{35.30} &       36.13  & \bsic{34.25} &       35.44  \\
+%			                      & VNLB   $s_t = 1$     & \bsic{33.19} &       35.53  & \bsic{35.60} &       37.76  & \bsic{35.35} &       37.31  & \bsic{37.90} &       39.88  & \bsic{35.51} &       37.62  \\
+%			                      & VNLB   $s_t = 2$     & \bsic{34.95} &       36.93  & \bsic{37.03} &       38.69  & \Bsic{35.60} & \Best{37.52} & \Bsic{38.60} & \Best{40.52} & \bsic{36.55} &       38.41  \\
+%			                      & VNLB   $s_t = 3$     & \bsic{35.48} &       37.40  & \Bsic{37.27} & \Best{38.86} & \Bsic{35.54} & \Best{37.43} & \Bsic{38.60} & \Best{40.54} & \Bsic{36.72} & \Best{38.56} \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{35.65} & \Best{37.54} & \Bsic{37.26} & \Best{38.84} & \bsic{35.44} &       37.32  & \Bsic{38.50} & \Best{40.48} & \Bsic{36.71} & \Best{38.55} \\\hline
+%%
+%			\multirow{1}{*}{$40$}
+%			                      & V-BM4D-mp            & \bsic{29.07} &       30.46  & \bsic{30.45} &       31.82  & \bsic{30.50} &       31.57  & \bsic{30.93} &       31.74  & \bsic{30.24} &       31.40  \\
+%			                      & VNLB   $s_t = 1$     & \bsic{29.25} &       31.57  & \bsic{31.44} &       33.67  & \bsic{31.70} &       33.70  & \bsic{33.47} &       35.44  & \bsic{31.46} &       33.60  \\
+%			                      & VNLB   $s_t = 2$     & \bsic{31.18} &       32.99  & \bsic{33.40} &       35.06  & \Bsic{32.60} & \Best{34.61} & \bsic{34.76} &       36.63  & \bsic{32.98} &       34.82  \\
+%			                      & VNLB   $s_t = 3$     & \bsic{31.69} &       33.46  & \Bsic{33.76} & \Best{35.32} & \Bsic{32.70} & \Best{34.69} & \Bsic{34.91} & \Best{36.79} & \Bsic{33.27} & \Best{35.07} \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{31.88} & \Best{33.64} & \Bsic{33.82} & \Best{35.37} & \Bsic{32.70} & \Best{34.66} & \Bsic{34.89} & \Best{36.77} & \Bsic{33.22} & \Best{35.11} \\\hline
+%		\end{tabular}}
 		\begin{tabular}{ c | l |c c | c c | c c | c c | c c}
@@
 			                      & V-BM4D-mp            & \bsic{37.47} &       38.85  & \bsic{38.67} &       40.02  & \bsic{37.30} &       38.40  & \bsic{39.52} &       40.41  & \bsic{38.24} &       39.42  \\
-			                      & VNLB   $s_t = 1$     & \bsic{37.48} &       39.74  & \bsic{39.85} &       41.83  & \Bsic{38.80} & \Best{40.82} & \Bsic{42.16} & \Best{44.10} & \bsic{39.57} &       41.62  \\
-			                      & VNLB   $s_t = 2$     & \bsic{39.01} &       41.10  & \Bsic{40.74} & \Best{42.40} & \bsic{38.70} &       40.65  & \Bsic{42.23} & \Best{44.14} & \Bsic{40.17} & \Best{42.07} \\
-			                      & VNLB   $s_t = 3$     & \bsic{39.40} & \Best{41.37} & \Bsic{40.74} & \Best{42.36} & \bsic{38.50} &       40.35  & \Bsic{42.17} & \Best{44.08} & \Bsic{40.20} & \Best{42.04} \\
-			                      & VNLB   $s_t = 4$     & \Bsic{39.44} & \Best{41.33} & \bsic{40.51} &       42.12  & \bsic{38.30} &       40.05  & \bsic{42.07} &       43.97  & \bsic{40.08} &       41.86  \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{37.00} &       39.57  & \bsic{39.70} &       41.82  & \Bsic{38.58} & \Best{40.77} & \Bsic{42.20} & \Best{44.38} & \bsic{39.37} &       41.64  \\
+										 & VNLB   $s_t = 2$     & \bsic{38.46} &       40.85  & \Bsic{40.49} & \Best{42.37} & \Bsic{38.52} & \Best{40.70} & \Bsic{42.22} & \Best{44.38} & \Bsic{39.92} & \Best{42.08} \\
+			                      & VNLB   $s_t = 3$     & \bsic{38.87} & \Best{41.19} & \Bsic{40.59} & \Best{42.46} & \bsic{38.42} &       40.60  & \bsic{42.09} &       44.25  & \Bsic{39.99} & \Best{42.13} \\
+										 & VNLB   $s_t = 4$     & \Bsic{38.99} & \Best{41.28} & \Bsic{40.55} & \Best{42.42} & \bsic{38.32} &       40.50  & \bsic{41.93} &       44.09  & \Bsic{39.94} & \Best{42.07} \\\hline
 %
@@
 			                      & V-BM4D-mp            & \bsic{33.23} &       34.70  & \bsic{34.63} &       35.98  & \bsic{33.85} &       34.94  & \bsic{35.30} &       36.13  & \bsic{34.25} &       35.44  \\
-			                      & VNLB   $s_t = 1$     & \bsic{33.19} &       35.53  & \bsic{35.60} &       37.76  & \bsic{35.35} &       37.31  & \bsic{37.90} &       39.88  & \bsic{35.51} &       37.62  \\
-			                      & VNLB   $s_t = 2$     & \bsic{34.95} &       36.93  & \bsic{37.03} &       38.69  & \Bsic{35.60} & \Best{37.52} & \Bsic{38.60} & \Best{40.52} & \bsic{36.55} &       38.41  \\
-			                      & VNLB   $s_t = 3$     & \bsic{35.48} &       37.40  & \Bsic{37.27} & \Best{38.86} & \Bsic{35.54} & \Best{37.43} & \Bsic{38.60} & \Best{40.54} & \Bsic{36.72} & \Best{38.56} \\
-			                      & VNLB   $s_t = 4$     & \Bsic{35.65} & \Best{37.54} & \Bsic{37.26} & \Best{38.84} & \bsic{35.44} &       37.32  & \Bsic{38.50} & \Best{40.48} & \Bsic{36.71} & \Best{38.55} \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       35.58  & \bsic{35.44} &       37.79  & \bsic{34.94} &       37.11  & \bsic{37.80} &       39.83  & \bsic{35.29} &       37.58  \\
+			                      & VNLB   $s_t = 2$     & \bsic{34.71} &       36.98  & \bsic{36.90} &       38.78  & \Bsic{35.28} & \Best{37.47} & \Bsic{38.61} & \Best{40.79} & \bsic{36.38} &       38.50  \\
+			                      & VNLB   $s_t = 3$     & \bsic{35.18} &       37.40  & \Bsic{37.16} & \Best{38.94} & \Bsic{35.28} & \Best{37.47} & \Bsic{38.67} & \Best{40.83} & \Bsic{36.57} & \Best{38.66} \\
+										 & VNLB   $s_t = 4$     & \Bsic{35.34} & \Best{37.54} & \Bsic{37.17} & \Best{38.95} & \Bsic{35.23} & \Best{37.42} & \Bsic{38.59} & \Best{40.72} & \Bsic{36.58} & \Best{38.65} \\\hline
 %
@@
 			                      & V-BM4D-mp            & \bsic{29.07} &       30.46  & \bsic{30.45} &       31.82  & \bsic{30.50} &       31.57  & \bsic{30.93} &       31.74  & \bsic{30.24} &       31.40  \\
-			                      & VNLB   $s_t = 1$     & \bsic{29.25} &       31.57  & \bsic{31.44} &       33.67  & \bsic{31.70} &       33.70  & \bsic{33.47} &       35.44  & \bsic{31.46} &       33.60  \\
-			                      & VNLB   $s_t = 2$     & \bsic{31.18} &       32.99  & \bsic{33.40} &       35.06  & \Bsic{32.60} & \Best{34.61} & \bsic{34.76} &       36.63  & \bsic{32.98} &       34.82  \\
-			                      & VNLB   $s_t = 3$     & \bsic{31.69} &       33.46  & \Bsic{33.76} & \Best{35.32} & \Bsic{32.70} & \Best{34.69} & \Bsic{34.91} & \Best{36.79} & \Bsic{33.27} & \Best{35.07} \\
-			                      & VNLB   $s_t = 4$     & \Bsic{31.88} & \Best{33.64} & \Bsic{33.82} & \Best{35.37} & \Bsic{32.70} & \Best{34.66} & \Bsic{34.89} & \Best{36.77} & \Bsic{33.22} & \Best{35.11} \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{29.03} &       31.57  & \bsic{30.93} &       33.36  & \bsic{30.82} &       32.77  & \bsic{32.81} &       34.69  & \bsic{30.90} &       33.10  \\
+			                      & VNLB   $s_t = 2$     & \bsic{31.02} &       33.09  & \bsic{33.11} &       35.09  & \bsic{32.08} &       34.25  & \bsic{34.52} &       36.60  & \bsic{32.68} &       34.76  \\
+										 & VNLB   $s_t = 3$     & \bsic{31.49} &       33.56  & \bsic{33.58} & \Best{35.41} & \Bsic{32.34} & \Best{34.55} & \Bsic{34.82} & \Best{36.96} & \Bsic{33.06} & \Best{35.12} \\
+			                      & VNLB   $s_t = 4$     & \Bsic{31.66} & \Best{33.73} & \Bsic{33.69} & \Best{35.47} & \Bsic{32.37} & \Best{34.59} & \Bsic{34.82} & \Best{36.95} & \Bsic{33.14} & \Best{35.19} \\\hline
 		\end{tabular}}

### 2015-08-19 src/NlBayes/VideoNLBayes.cpp
[src] User can select which step to run through CLI, providing pre-computed basic estimate.

@@ -378,18 +378,31 @@ std::vector<float> runNlBayes(
 	//! Video size
 	VideoSize imSize = i_imNoisy.sz;
 
+	//! Determine steps
+	int step = p_prms1.sizePatch ?
+	          (p_prms2.sizePatch ? 0 : 1) :
+	          (p_prms2.sizePatch ? 2 :-1) ;
+
+	if (step == -1)
+		throw std::runtime_error("VideoNLB::runNlBayes: Both patch sizes are zero.");
+
 	//! Initialization
-	o_imBasic.resize(imSize);
-	o_imFinal.resize(imSize);
+	if (step != 2) o_imBasic.resize(imSize);
+	if (step != 1) o_imFinal.resize(imSize);
+
+	if (step == 2 && imSize != o_imBasic.sz) 
+		throw std::runtime_error("VideoNLB::runNlBayes: sizes of noisy and "
+				"basic videos don't match");
 
 	//! Print parameters
-	if (p_prms1.verbose) printNlbParameters(p_prms1);
-	if (p_prms2.verbose) printNlbParameters(p_prms2);
+	if (p_prms1.verbose) if (step != 2) printNlbParameters(p_prms1);
+	if (p_prms2.verbose) if (step != 1) printNlbParameters(p_prms2);
 
 	//! Percentage of processed groups over total number of pixels
 	std::vector<float> groupsRatio(2,0.f);
 
 	//! Step 1
+	if (step != 2)
 	{
 		if (p_prms1.verbose)
 		{
@@ -461,9 +474,11 @@ std::vector<float> runNlBayes(
 	}
 
 	//! Step 2
+	if (step != 1)
 	{
 		if (p_prms2.verbose)
 		{
+			if (step == 2) for (int p = 0; p <= nParts; ++p) printf("\n");
 			printf("\x1b[%dF2nd Step\n",nParts+1);
 			for (int p = 0; p < nParts; ++p) printf("\x1b[2K\n");
 		}

### 2015-08-19 src/main_vnlb.cpp

@@ -43,6 +43,7 @@ int main(int argc, char **argv)
 	//! Paths to input/output sequences
 	using std::string;
 	const string  input_path = clo_option("-i"    , ""              , "< input sequence");
+	const string  inbsc_path = clo_option("-b"    , ""              , "< input basic sequence");
 	const string  noisy_path = clo_option("-nisy" , "nisy_%03d.png" , "> noisy sequence");
 	const string  final_path = clo_option("-deno" , "deno_%03d.png" , "> denoised sequence");
 	const string  basic_path = clo_option("-bsic" , "bsic_%03d.png" , "> basic denoised sequence");
@@ -101,7 +102,7 @@ int main(int argc, char **argv)
 		prms2.rank = rank2;
 
 		VideoNLB::printNlbParameters(prms1);
-		VideoNLB::printNlbParameters(prms2);	
+		VideoNLB::printNlbParameters(prms2);
 
 		return EXIT_FAILURE;
 	}
@@ -115,12 +116,23 @@ int main(int argc, char **argv)
 		return EXIT_FAILURE;
 	}
 
+	if (patch_sizex1 == 0 && inbsc_path == "")
+	{
+		fprintf(stderr, "%s: if px1 = 0, a basic sequence path must be given.\nTry `%s --help' for more information.\n",
+				argv[0], argv[0]);
+		return EXIT_FAILURE;
+	}
+
+	if (patch_sizex1 > 0 && inbsc_path != "")
+		fprintf(stderr, "\x1b[33;1mWarning:\x1b[0m a basic sequence path ignored since px1 > 0.\n");
+
+
 	//! Declarations
 	Video<float> original, noisy, basic, final, diff;
 
-	//! Load original video
-	original.loadVideo(input_path, firstFrame, lastFrame, frameStep);
-
+	//! Load input videos
+	                       original.loadVideo(input_path, firstFrame, lastFrame, frameStep);
+	if (patch_sizex1 == 0) basic   .loadVideo(inbsc_path, firstFrame, lastFrame, frameStep);
 
 	//! Add noise
 	if (sigma)
@@ -158,29 +170,29 @@ int main(int argc, char **argv)
 	groupsRatio = VideoNLB::runNlBayes(noisy, basic, final, prms1, prms2);
 
 	//! Compute PSNR and RMSE
-	float final_psnr, final_rmse, basic_psnr, basic_rmse;
[…]

### 2015-10-13 doc/201507_tip/paper.tex
[doc] Advances in TIP paper

@@
 
+\usepackage[normalem]{ulem} % allows the use of sout
+
 % \graphicspath{{../iccv09/}}
+
+% pablo's commands for comments and suggested modifications
+\newcommand{\pa}[1]{\textcolor{cyan}{#1}}
+\newcommand{\psub}[2]{\pa{\sout{#1}}\pa{/#2}}
+\newcommand{\prm}[1]{\pa{\sout{#1}}}
+\newcommand{\padd}[1]{\pa{#1}}
+\newcommand{\pcomment}[1]{\textit{\pa{#1}}}
 
@@
 
-% New definition of square root:
-% it renames \sqrt as \oldsqrt
-\let\oldsqrt\sqrt
-% it defines the new \sqrt in terms of the old one
-\def\sqrt{\mathpalette\DHLhksqrt}
-\def\DHLhksqrt#1#2{%
-\setbox0=\hbox{$#1\oldsqrt{#2\,}$}\dimen0=\ht0
-\advance\dimen0-0.2\ht0
-\setbox2=\hbox{\vrule height\ht0 depth -\dimen0}%
-{\box0\lower0.4pt\box2}}
+%% % New definition of square root:
+%% % it renames \sqrt as \oldsqrt
+%% \let\oldsqrt\sqrt
+%% % it defines the new \sqrt in terms of the old one
+%% \def\sqrt{\mathpalette\DHLhksqrt}
+%% \def\DHLhksqrt#1#2{%
+%% \setbox0=\hbox{$#1\oldsqrt{#2\,}$}\dimen0=\ht0
+%% \advance\dimen0-0.2\ht0
+%% \setbox2=\hbox{\vrule height\ht0 depth -\dimen0}%
+%% {\box0\lower0.4pt\box2}}
 
@@
 \author{Pablo~Arias, Jean-Michel~Morel%
-\thanks{P. Arias (\texttt{pablo.arias@upf.edu}) and J.-M. Morel
+\thanks{P. Arias (\texttt{pablo.arias@cmla.ens-cachan.fr}) and J.-M. Morel
 (\texttt{jean-michel.morel@cmla.ens-cachan.fr}) are with the \emph{Centre de
@@
 parameters of the prior are learnt from the noisy data.
+
+%Consider a grayscale video $u:\Omega\times \{1,\cdots,T\}\rightarrow
+%\mathbb R$, where $\Omega$ is the spatial domain (a rectangular discrete grid).
+%We assume that $v$ is a noisy version of $u$, contaminated with additive,
+%Gaussian, white noise $n$ of known variance $\sigma^2$,
+%\[v = u + n.\]
+%
+%We make the assumption that each patch $\ma p_{xt}$ of the noiseless video is a realisation 
+%of a Gaussian random variable, $N(\overline {\ma p}_{xt}, C_{xt})$.
+%%
+%The problem 
+%of denoising can then be formulated as a problem of optimal Bayesian inference, where the
+%parameters of the prior are learnt from the noisy data.
+%%
+%If the
+%mean and covariance are known (or leant from the data), then given a noisy observation
+%$\ma q_{xt} = \ma p_{xt} + \ma n_{xt}$, 
+%one can estimate $\ma p_{xt}$ as the expected value of the posterior
+%distribution $\mathds{P}(\ma p_{xt}, \ma q_{xt})$ or its
+%maximum (\ie the maximum \emph{a posteriori}, MAP).
 
@@
 The parameters of the \textit{a priori} model, are learnt from the noisy video as
-follows. For each noisy patch $\ma q$, we select the most $N_{\text{sim}}$
+follows. For each noisy patch $\ma q$, we select the most $n$
 similar 3D patches found in a search region centered at $\ma q$. The
-search region is a spatio-temporal rectangle of size $n_x \times
-n_x \times n_t$ ($n_x, n_t$ are odd numbers).
-
-Let us note by $\ma q_i$, $i = 1, \dots, N_{\text{sim}}$ the set of patches
+search region is a spatio-temporal rectangle of size $w_x \times
+w_x \times w_t$ ($w_x, w_t$ are odd numbers).
+
+Let us note by $\ma q_i$, $i = 1, \dots, n$ the set of patches
 similar to $\ma q$ (with $\ma q_1 = \ma q$). We assume that these 
@@
 \begin{equation}
-	\widehat{\overline{\ma p}} = \frac1{N_{\text{sim}}}\sum_{i = 1}^{N_{\text{sim}}}\ma q_i \quad\text{and}\quad 
-		\widehat C= \frac1{N_\text{sim}}\sum_{i = 1}^{N_{\text{sim}}}\ma q_i\ma q_i^T - \sigma^2I.
+	\widehat{\overline{\ma p}} = \frac1{n}\sum_{i = 1}^{n}\ma q_i \quad\text{and}\quad 
+		\widehat C= \frac1n\sum_{i = 1}^{n}\ma q_i\ma q_i^T - \sigma^2I.
 	\label{eq:learn_parameters}
@@
 
+The Figures \ref{fig:patch_groups_pos} and \ref{fig:patch_groups_patches}
+show two example of groups of similar patches. Figure \ref{fig:patch_group_pos}
+shows the position of 200 nearest neighbors of a reference patch. It can be noticed
+that inspite of the noise
+
 \bigskip
@@
 oriented channel of the image at a given scale.
+
+\begin{figure*}[htpb!]
+	\centering
+	\includegraphics[width = .8\textwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_coor.png}\\
+	\vspace{.2cm}
+	\includegraphics[width = .8\textwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_coor.png}
+%	\includegraphics[width = .8\textwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_coor.png}
+	\caption{Examples of sets of 200 nearest neighbors spatio-temporal patches,
+	for patches of size $9\times 9\times 4$.
+	The images in each row show the five frames of a $37\times37\times5$ search region. 
+	In red we show the positions of the 5 nearest neighbors, in green the next 40 and in blue the rest.
+	Note the points shown correspond to the top-left pixel of the first temporal
+	slice of each patch.
+	The reference patch is the red patch in the center of the search region.}
+	\label{fig:patch_groups_pos}
+\end{figure*}
+
+\begin{figure}[htpb!]
+	\centering
+%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
+%	\vspace{.1cm}
+	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
+	\vspace{.2cm}
+	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
+	\vspace{.2cm}
+	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
+	\vspace{.2cm}
+%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
+%	\vspace{.1cm}
+	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
+	\vspace{.2cm}
+	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
+	\vspace{.2cm}
+	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
+	\vspace{.2cm}
+%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
+%	\vspace{.1cm}
+%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
+%	\vspace{.1cm}
+%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
+%	\vspace{.1cm}
+%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
+%	\vspace{.1cm}
+	\caption{For each of the two sets of patches of Fig. \ref{fig:patch_groups_pos} we show
+	the 20 nearest neighbors (top), the corresponding MAP estimates (middle) and the sample mean 
+	and first 19 principal directions computed from the sample covariance matrix (bottom).
+	For each image, each column corresponds to the 4 temporal slices of a $9\times9\times4$ patch.}
+	\label{fig:patch_groups_patches}
+\end{figure}
+
+\section{Discussion}
+
+\subsection{Spatio-temporal patches}
+
+Patch-based methods filter similar patches to remove noise. When the noise is
+Gaussian, the patch similarity is determined based on the (squared) Euclidean distance 
+between patches. Due to the noise, the Euclidean distance follows a non-central
+$\chi^2$ distribution, with variance
+\[\textnormal{Var}\left\{\frac1{m}\|\ma q_1 - \ma q_2\|^2\right\} = \frac{8\sigma^2}{m}\left(\sigma^2 + \frac1{m}\|\ma p_1 - \ma p_2\|^2\right),\]
+where $\ma q_1, \ma q_2$ are the noisy versions of the patches $\ma p_1, \ma p_2$, 
+and $m$ denotes the number of pixels in the patch. The noise in the patch comparison
+can be reduced by considering larger patches.
+However, increasing the size of the patch also increases the distances between
+patches and reduces the likelihood of finding similar patches.
+%
+The additional temporal dimension in a spatio-temporal patch allows to increase
+the number of pixels in the patch, without increasing its spatial size.
+Due to the high redundancy of the video in the temporal dimension, increasing the 
+temporal size of the patch causes a much lower increase in the patch distances.
+%The high redundancy of the video in the temporal dimension, allows to have 
+%larger patches without affecting much the number of nearest neighbors of the patch.
+%
+
+Let us assume that 
+the brightness of the original video is constant along motion trajectories, so
+that $u(x,t + \tau) = u(\varphi(x,t + \tau; -\tau),t)$, where
+$\varphi(x,t+\tau;\, \cdot\, )$ denotes the motion trajectory passing though
+$(x,t + \tau)$.
+Furthermore, let us assume that the motion in the video is approximately
+translational.
+When the motion is known or can be estimated, then it is natural to consider
+motion compensated spatio-temporal patches. 
+With the assumptions we are considering, all spatial slices of a $s_x\times s_x\times s_t$ motion-compensated patch
+coincide, so the distance between two spatio-temporal patches is proportional to
+the distance of a 2D spatial patch of size $s_x\times s_x$.
+%
+As a consequence, by increasing $s_t$, on can reduce the 
+noise in the patch distance and have the same pattern of self-similarity as a 
+2D patch.
+
+However, motion estimation is challenging, and even more so in the presence of noise.
+%Most motion estimation techniques integrate spatial information either 
+%by matching 2D patches (or blocks, as they are commonly referred to in the
+%motion estimation literature) or by some spatial regularization term in an energy.
+An option that does not require motion is to use rectangular spatio-temporal patches.
+The distance between these can be also expressed as a distance between spatial patches,
+but their equivalent spatial support is larger than $s_x\times s_x$.
+
+%To see this, let us observe that the squared Euclidean distance can be expressed as
+%the convolution with a separable kernel.
+To see this, let us assume that the motion in the video is a constant translation $v$. 
+The squared Euclidean distance can be expressed as
+%\begin{multline*}
+%	d(\ma p_{xt}, \ma p_{ys})\\ %= [g_x\ast_x g_t \ast_t \left(u(x + \,\cdot\,,t + \,\cdot\,) -  u(y + \,\cdot\,,s + \,\cdot\,)\right)^2](0,0)\\
+%		 = \iint g_x(\rho)g_t(\tau) \left(u(x + \rho,t + \tau) -  u(y + \rho,s + \tau)\right)^2d\tau d\rho
+%\end{multline*}
+\[
+	d(\ma p_{xt}, \ma p_{ys}) = \iint g_x(\rho)g_t(\tau) f(\rho,\tau)d\tau d\rho
+\]
+where
+%$\ast_x, \ast_t$ denote the spatial and temporal convolution operators and 
+$f(\rho,\tau) = \left(u(x + \rho,t + \tau) -  u(y + \rho,s + \tau)\right)^2$,
+and 
+$g_xg_t$ is a separable spatio-temporal kernel which defines the
+shape of the spatio-temporal patch. For example, for a rectangular patch, $g_x$
+and $g_t$ are both box filters of sizes $s_x\times s_x$ and $s_t$ respectively.
+Because of the brightness constancy assumption, we have that $f(\rho,\tau) = f(\rho + v\tau, 0)$.
+%\pcomment{Note: this only holds if the motion at $t$ is equal than the one at $s$.}
+Using this fact, after some manipulations we can rewrite the distance as a distance between 2D patches:
+\[
+	d(\ma p_{xt}, \ma p_{ys}) = \int f(\rho,0)h(\rho) d\rho
+\]
+where \[h(\rho) = \int g_x(\rho - v\tau)g_t(\tau)  d\tau\] is the 
+equivalent spatial kernel. Note that this kernel is the result of integrating
+several shifted versions of the spatial patch kernel $g_x$ along a motion trajectory.
+%
+Thus, when the brightness constancy assumption holds under a constant
+translational motion $v$, the rectangular spatio-temporal patch is equivalent
+to a spatial patch whose support depends on $v$. When $v = 0$, then it reduces 
+to the $s_x\times s_x$ patch, and grows in the direction of the motion at $v$
+increases.
+%
+In these settings, rectangular spatio-temporal patches can be expected to perform as well
+as motion-compensated patches.
+
+For more complex types of motion, using rectangular spatio-temporal patches will result in
+a larger variability in the set of nearest neighbors of a given patch, due to the fact that
+both the spatial texture and the motion pattern may vary. At least in principle, better 
+results should be obtained using motion compensation. However, in practice, the bad quality of
+the estimated motion undermines the final result.
+
+%\begin{align*}
+%	d(\ma p_{xt}, \ma p_{ys}) %= [g_x\ast_x g_t \ast_t \left(u(x + \,\cdot\,,t + \,\cdot\,) -  u(y + \,\cdot\,,s + \,\cdot\,)\right)^2](0,0)\\
+%		 &= \iint g_x(\rho)g_t(\tau) f(\rho,\tau)d\tau d\rho\\
+%		 &= \iint g_x(\rho)g_t(\tau) f(\rho + v(\tau),0) d\tau d\rho\\
+%		 &= \iint g_x(\rho - v(\tau))g_t(\tau) f(\rho,0) d\tau d\rho\\
+%		 &= \int f(\rho,0)\int g_x(\rho - v(\tau))g_t(\tau)  d\tau d\rho\\
+%		 &= \int f(\rho,0)h(\rho) d\rho\\
+%\end{align*}
+
+%after some manipulations the distance 
+%can be written as the convolution with a spatial kernel:
+%\begin{equation*}
+%	d(\ma p_{xt}, \ma p_{ys}) = [h \ast_x \left(u(x + \,\cdot\,,t) -  u(y + \,\cdot\,,s)\right)^2](0),
+%\end{equation*}
+%where 
+%\[
+%	h(\xi) = [g_t \ast g_x(v\,\cdot\,)](\xi/v) 
+%		= \int g_t(\eta)g_x(\xi - v\eta)d\eta.
+%\]
+
+\pcomment{
+\begin{itemize}
+%	\item Justify why 3D patches: Greater distance noise reduction with roughly the same 
+%		degree of self-similarity. One way to see this is that the 3D patches can be 
+%		seen, for a video in which the brightness constancy assumption holds, as a 2D patch
+%		by back-projecting all the slices to the first frame.
+	\item Relation with respect other iterative methods found in the literature
+		(SOS, twicing, diffusion, BM3D, I-SA-BM4D).
+	\item Variation of the results tables for different sequences.
+\end{itemize}}
+
+\subsection{Estimation of the covariance matrix}
 
@@
 		\STATE Get a patch $\ma q$ from $\mathcal P$ \COMMENT{``center'' of Gaussian model}
-			\STATE Retrieve  the $n_{\text{sim}}$ nearest neighbors to $\ma
+			\STATE Retrieve  the $n$ nearest neighbors to $\ma
 			q$ in a spatio-temporal volume around $\ma q$
@@
 			$\widehat C_{r}^{(1)}$ 
-			\FORALL{$n_{\text{sim}}$ neighbors $\ma q_i$ of $\ma q$}
+			\FORALL{$n$ neighbors $\ma q_i$ of $\ma q$}
 				\STATE Obtain the MAP estimate $\widetilde{\ma p}_i^{(1)}$
@@
 		\STATE Get a patch $\ma q$ from $\mathcal P$ \COMMENT{``center'' of Gaussian model}
-			\STATE Retrieve the $n_{\text{sim}}$ nearest neighbors to $\ma
+			\STATE Retrieve the $n$ nearest neighbors to $\ma
 			q$ in a spatio-temporal volume around $\ma q$.
@@
 						 $\widetilde{\ma p}_i^{(1)}$, setting $\ma{\sigma = 0}$.}
-			\FORALL{$n_{\text{sim}}$ neighbors $\ma q_i$ of $\ma q$}
+			\FORALL{$n$ neighbors $\ma q_i$ of $\ma q$}
 				\STATE Obtain the MAP estimate $\widetilde{\ma p}_i^{(2)}$
@@
 %		\FORALL{patches $\ma q$ in $v$}
-%		\STATE Find the $N_{\text{sim}}$ most similar patches to $\ma q$ in a search volume centered at $\ma q$
+%		\STATE Find the $n$ most similar patches to $\ma q$ in a search volume centered at $\ma q$
 %		\STATE Compute $\widehat{\overline{\ma p}}\,\!^{(1)}$ and $\widehat C^{(1)}$ according to \eqref{eq:learn_parameters}
@@
 %		\FORALL{patches $\ma q$ in $v$}
-%		\STATE Find the $N_{\text{sim}}$ most similar patches to $\ma q$ in a
+%		\STATE Find the $n$ most similar patches to $\ma q$ in a
 %		search volume centered at $\ma q$ by comparing the estimates $\widetilde{\ma
@@
 %\[
-%	\widehat{\overline{\ma p}}\,\!^{(2)} = \frac1{N_{\text{sim}}}\sum_{i = 1}^{N_{\text{sim}}}\widetilde{\ma p}_i^{(1)} \quad\text{and}\quad 
-%	\widehat C^{(2)}= \frac1{N_\text{sim}}\sum_{i = 1}^{N_{\text{sim}}}\left(\widetilde{\ma p}_i^{(1)}\right)^T \widetilde{\ma p}_i^{(1)}.
+%	\widehat{\overline{\ma p}}\,\!^{(2)} = \frac1{n}\sum_{i = 1}^{n}\widetilde{\ma p}_i^{(1)} \quad\text{and}\quad 
+%	\widehat C^{(2)}= \frac1{nsum_{i = 1}^{n}\left(\widetilde{\ma p}_i^{(1)}\right)^T \widetilde{\ma p}_i^{(1)}.
 %\]
@@
 
-\begin{figure*}[thpb!]
-	\begin{center}
-		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_nisy_s10_044.png}
-		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_nisy_s20_044.png}
-		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_nisy_s40_044.png}\\
-		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_vnlb_s10_tr2_044.png}
-		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_vnlb_s20_tr2_044.png}
-		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_vnlb_s40_tr2_044.png}\\
-		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_s10_bm4d_044.png}
-		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_s20_bm4d_044.png}
-		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_s40_bm4d_044.png}\\
-		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_nisy_s10_140.png}
-		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_nisy_s20_140.png}
-		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_nisy_s40_140.png}\\
-		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_vnlb_s10_tr2_140.png}
-		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_vnlb_s20_tr2_140.png}
-		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_vnlb_s40_tr2_140.png}\\
-		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_s10_bm4d_140.png}
-		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_s20_bm4d_140.png}
-		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_s40_bm4d_140.png}
-	\end{center}
-	\caption{Comparison of results obtained with VNLB ($n_t =5$) and V-BM4D-np.
-	The first three rows, correspond to a frame of the bus sequence. From top to
-	bottom: noisy input data. The last three rows correspond to the tennis sequence.
-	Each column shows results obtained for $\sigma = 10$, $20$ and $40$.}
-	\label{fig:results}
-\end{figure*}
+%\begin{figure*}[thpb!]
+%	\begin{center}
+%		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_nisy_s10_044.png}
+%		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_nisy_s20_044.png}
+%		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_nisy_s40_044.png}\\
+%		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_vnlb_s10_tr2_044.png}
+%		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_vnlb_s20_tr2_044.png}
+%		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_vnlb_s40_tr2_044.png}\\
+%		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_s10_bm4d_044.png}
+%		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_s20_bm4d_044.png}
+%		\includegraphics[trim=0.0cm 2.0cm 4.0cm 1.0cm, clip=true, width=0.25\textwidth]{figs/bus_s40_bm4d_044.png}\\
+%		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_nisy_s10_140.png}
+%		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_nisy_s20_140.png}
+%		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_nisy_s40_140.png}\\
+%		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_vnlb_s10_tr2_140.png}
+%		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_vnlb_s20_tr2_140.png}
+%		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_vnlb_s40_tr2_140.png}\\
+%		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_s10_bm4d_140.png}
+%		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_s20_bm4d_140.png}
+%		\includegraphics[trim=3.5cm 2.0cm 1.5cm 0.5cm, clip=true, width=0.25\textwidth]{figs/tennis_s40_bm4d_140.png}
+%	\end{center}
+%	\caption{Comparison of results obtained with VNLB ($w_t =5$) and V-BM4D-np.
+%	The first three rows, correspond to a frame of the bus sequence. From top to
+%	bottom: noisy input data. The last three rows correspond to the tennis sequence.
+%	Each column shows results obtained for $\sigma = 10$, $20$ and $40$.}
+%	\label{fig:results}
+%\end{figure*}
 
@@
 Patch distances are computed using the luminance only. Using the 
-$N_{\text{sim}}$ most similar patches, a group is built for each channel. These
+$n$ most similar patches, a group is built for each channel. These
 groups are filtered independently (a Gaussian model is learnt for each of them).
@@
 \paragraph{Patch distance threshold} When building the group of similar
-patches during the second stage, more than $N_{\text{sim}}$ patches are allowed
+patches during the second stage, more than $n$ patches are allowed
 if their distances with respect to the reference patch are smaller than a
@@
 \paragraph{Speed-ups} To accelerate the computation we apply two tricks
-considered in \cite{Lebrun2013ipol}. The first one visits a patch each $N_{\text{step}}$
+considered in \cite{Lebrun2013ipol}. The first one visits a patch each $n$
 patches (similar to \cite{Dabov2007tip}). The second trick consists on the following.
@@
 as reference patches for a group. This reduces the number of groups of patches
-that need to be processed by a factor of $N_{\text{sim}}$.
+that need to be processed by a factor of $n$.
 \todo{Also describe that the 4 neighbors are flagged as processed.}
@@
 Let us consider the complexity of constructing and filtering a group of
-$N_{\text{sim}}$ similar patches. Due to the speed-ups described in the
+$n$ similar patches. Due to the speed-ups described in the
 previous section, the actual number of groups of similar patches processed
@@
 Processing each group of similar patches is of asymptotic order $\mathcal
-O(n_x^2 n_t s_x^2 s_t + s_x^4s_t^2r + N_{\text{sim}}s_x^4s_t^2)$.
-The first term comes from the exhaustive search of the $N_{\text{sim}}$ most
+O(w_x^2 w_t s_x^2 s_t + s_x^4s_t^2r + ns_x^4s_t^2)$.
+The first term comes from the exhaustive search of the $n$ most
 similar patches in the search window. 
@@
 these methods efficiently approximate a truncated SVD of the data matrix, and would 
-allow to improve the computational complexity to $\mathcal O(n_x^2 n_t s_x^2
-s_t + s_x^2s_trN_{\text{sim}})$.
+allow to improve the computational complexity to $\mathcal O(w_x^2 w_t s_x^2
+s_t + s_x^2s_trn)$.
 
@@
 
-Each stage of the algorithm has the following 6 parameters: the spatial and temporal components of the patch size
-$s_x$ and $s_t$, the spatial and temporal components of the search region $w_x$ and
-$w_t$, the number of similar patches $n_{\text{sim}}$ and the rank of the a priori
-covariance matrix $r$. Each of these parameters needs to be determined for both
-stages.
+For each stage of the algorithm we need to specify 6 parameters: the spatial
+and temporal components of the patch size, $s_x$ and $s_t$, the spatial and
+temporal components of the search region, $w_x$ and $w_t$, the number of similar
+patches $n$ and the rank of the a priori covariance matrix $r$.
+When needed, we will add a subscript indicating the stage, \eg
+$n_{1}$ and $n_{2}$.
 
@@
 trade-off between denoising performance and running time: A larger search
-region takes longer to traverse but yields better the results, since better
-neighbors can be found. In the following experiments, we will fix the search
+region takes longer to traverse but yields better results, since more
+similar patches can be found. We fix the search
 region for both stages of the algorithm at 
@@
 \end{equation}
-If the patch in the center of the search region moves slower than $37/5 = 7.4$
-pixels/frame, then it stays in the search region for the $5$ frames.
+With these values, the search region captures the $5$ frame trajectory of the
+target patch as long as it moves slower than $37/5 = 7.4$
+pixels/frame.
 
 \paragraph{Patch size} Let us consider first the spatial patch
-size $s_x$. The impact of a variation of the $s_x$ in the results
-depends on the value of the rank parameter. For instance, if the rank is set
-too low, then increasing the patch size has a negative effect on the results.
-For sufficiently high rank, increasing the size of the patch leads on average
-to an improvement of the results. This improvement however comes at a considerable
-increase in the computation time, since our current implementation is $\mathcal
-O(s_x^4)$.  We have found that a good trade-off between computation time and
-quality is given by $s_x = 5$.
-
-The impact of the temporal patch size $s_t$ will be discussed later in Section \ref{sec:results}.
-
-\paragraph{Rank and number of similar patches} These parameters are intimately linked.
-Intuitively, smaller groups obtained by keeping only the most similar patches have 
-only a few modes of variation and thus are better modelled with a low rank
-covariance matrix. As the group of patches grows bigger, patches in the group
-are not as similar anymore, and a higher rank is needed to model these additional 
-variation.
-To find appropriate values for these parameters, we compute denoising results
-varying the rank $r$ and the number of similar patches $n_{\text{sim}}$, while
-keeping all other parameters fixed. Results are computed for four 20 frames clips
-extracted from the sequences \emph{bus}, \emph{foreman}, \emph{football} and
-\emph{tennis}, adding noise of $\sigma = 10, 20, 40$.
-%
-We do this for each stage, starting by the second.
-
-On this first experiment, the parameters of the first stage are fixed at:
-\[w_x = 37,\,\,w_t = 5\,\,s_x = 5,\,\,s_t = 4,\,\,n_{\text{sim}} = 375,\,\,r = 100.\]
-\todo{Check these parameters}
-Note that $r = 100$ is the full rank.
-For the second stage, we fix $w_x = 37$, $w_t = 5$, $s_x = 5$ and $s_t = 3$, while varying 
-$r$ in $10,20,\dots,80$ and $n_{\text{sim}}$ in $50, 150,200,250$.
-The results can be visualized in Figure \ref{fig:rank-nsim-image-stage2}. The images in the 
-figure show the PSNR loss in dB with respect to the maximum value attained at each noise level.
-White means 0dB (\ie the set of parameters where the maximum was attained) and black means a loss
-greater or equal than 1dB.
-
-We can observe that, at constant $n_{\text{sim}}$ there is an optimal value for the rank. Bellow
-these value the PSNR drops sharply, and above it, the decay is slower. The
-optimal rank for a given $n_{\text{sim}}$ increases with $n_{\text{sim}}$ and decreases with $\sigma$.
-Best results are obtained for small $n_{\text{sim}}$. However, this also entails a higher running time, 
-since it increases the number of groups of similar patches that need to be
-processed. We found a good compromise by setting $n_{\text{sim}} = 150$ and $r$ as a decreasing function of $\sigma$:
-\[r(\sigma) = 40 - \frac1{10}(\sigma - 40),\]
-which corresponds to a line through $(s=10, r = 40)$ and $(s=40, r = 30)$.
-
-We now perform a similar search for the first stage, setting the second step parameters as:
-\[w_x = 37,\,\,w_t = 5\,\,s_x = 5,\,\,s_t = 3,\,\,n_{\text{sim}} = 150,\,\,r(\sigma).\]
-The first stage parameters are as before, expect that we now vary $r$ in $10,20,\dots,100$
-and $n_{\text{sim}}$ in $50,100,\dots,650$. Results are shown in Figure
-\ref{fig:rank-nsim-image-stage1}. Note that since our objective is to maximize
-the final PSNR, we show here the final PSNR. 
-The final and the basic PSNRs do not always
-have the same behaviour. Improving the basic PSNR does not always lead to an
-improvement in the final one. The reason for this is that it is preferable to
-apply a conservative noise reduction leaving some noise in the basic estimate
-(high variance but small bias). In the second step, this residual noise has
-little effect on the estimation of the patch distances and the \emph{a priori} covariance
-matrix. On the other hand, applying a more aggressive denoising in first step
-might increase the basic PSNR, but the second step cannot recover the lost
-signal components.
-
-In fact, best results are obtained using the full rank covariance matrix. 
-In accordance to these observations, we will set the first values for $r$ and $n_{\text{sim}}$ as:
-\begin{equation}
-	r = s_x^2s_t \quad\quad n_{\text{sim}} = 350.
-	\label{eq:stage1_parameters}
-\end{equation}
+size $s_x$. This is a key parameter in patch-based methods that
+exploit the image self-similarity \pcomment{CITAS}. The distribution of the 
+patch distances is a non-central Chi-squared distribution \cite{Dabov2007tip}
+\pcomment{CHECK!}
+with variance 
+\[\textnormal{Var}\left\{\frac1{m}\|\ma q_1 - \ma q_2\|^2\right\} = \frac{8\sigma^2}{m}\left(\sigma^2 + \frac{\|\ma p_1 - \ma p_2\|^2}{m}\right),\]
+where $m = s_x^2s_t$ is the total number of pixels in the patch.
+Increasing the spatial patch size $s_x$ reduces the variance of the noise in the patch
+distance. 
+However, for larger
+patches it becomes less likely to find other patches with a similar texture
+pattern. The use spatio-temporal patches helps in solving this trade-off: for
+instance, with a spatio-temporal patch of size $5\times 5\times 4$, we obtain
+the same patch distance noise as with a spatial patch of size $10\times 10
+\times 1$. Moreover, if the motion in the video is approximately uniform, then the 
+amount of similar neighbors of a $5\times 5\times 4$ patch is roughly the same
+as for a $5\times 5\times 1$ patch.
+\pcomment{This discussion would be nice to have in the introduction. Furthermore,
+we could add a short computation on the relation between the distance between
+3D patches and their 2D lids. In this way, we could speak of an equivalent 
+2D patch size.}
+
+We will set the spatial patch size at \[s_x = 5\] for both stages. Larger
+patches (up to $s_x = 9$) lead to an mild improvement of the results (on
+average). This improvement comes at a considerable increase in the
+computation time, since our current implementation is $\mathcal O(s_x^4)$. Thus,
+have found that a good compromise between computation time and quality is given
+by $s_x = 5$.
+
+The impact of the temporal patch size $s_t$ will be discussed later in Section
+\ref{sec:results}, where we show results varying $s_t$ between $s_t = 1$ and $s_t = 4$.
+
+\paragraph{Rank and number of similar patches} These parameters are intimately
+linked. Together they determine the estimation of the local Gaussian models
+and thus control the bias-variance trade-off of the denoiser.
+\pcomment{This is probably inaccurate. There should be other parameters
+contributing to this.}
+
+The number of similar patches $n$ affects the estimation of the covariance
+matrix $C$.
+%Let us consider the trade-offs involved in the estimation of the covariance
+%matrix $C$.
+The empirical covariance matrix $\widehat C$ converges to the true covariance matrix
+$C$ as the number of samples from the underlying Gaussian distribution grows to infinity.
+In our case, the number of samples we can ``draw'' from the Gaussian is limited:
+%The Gaussian is only an approximate density model for the set of
+%$n$ nearest neighbors of a target patch.
+As we increase the number $n$ of neighbors of a patch, we include patches
+that are not as similar to the reference patch and the Gaussian model becomes less valid. 
+%
+Thus there is a trade-off between accuracy of Gaussian model and precision of the
+covariance matrix.
+We find a compromise to this trade-off empirically, by trying different values of this parameter on a 
+few training sequences and use the one yielding the best PSNR.
+
+According to \cite{Vershynin2012}, the number of patches needed to achieve a given approximation
+error between the empirical and the true covariances grows linearly with the
+dimensionality of the space spanned by the data. 
+\pcomment{Comment 1: Actually, I found results relating the number of samples with
+the dimensionality of the ambient space. 
+However, if the data lies in a $p$-dimensional subspace, one could 
+compute a basis of this subspace from $n > p$ samples, and work in the low-dim
+coordinates to estimate a covariance matrix there. In that way, one could build
+a covariance matrix in the ambient space.}
+\pcomment{Comment 2: This reference may not be as relevant, in the light of the 
+results known for Gaussian covariance matrices. It would be interesting to see what 
+\cite{bunea2015} says regarding covariance matrices with low-effective rank.}
+
+The rank also plays a role in the estimation of the covariance matrix.
+As explained in \S \ref{sec:complexity}, alleviating the computational cost is
+one of the reasons for using a low rank approximation of the empirical
+covariance matrix. But there are also good reasons regarding the denoising
+performance. In situations in which the number of samples 
+is comparable to their dimension, the eigen-decomposition of the empirical
+covariance matrix $\widehat C$ can have considerable errors with respect to
+that of the population covariance matrix $C$. 
+%
+The case of Gaussian models with covariance matrices of the form $C + \sigma^2I$,
+where $C$ is of rank $r$, has been studied in the statistics and physics
+literature. The authors in \cite{johnstone2009,paul2007} study the
+limit when $n,p\to\infty$ such that $p/n\to\gamma < \infty$.
+All these works show that, for a non-zero ratio $\gamma$, the empirical eigenvectors 
+and eigenvalues are inconsistent estimators of the population ones.
+Furthermore, the smaller eigenvalues and their eigenvectors will have a higher
+error and eventually, if the signal-to-noise ratio drops bellow than $\sqrt{\gamma}$, 
+the eigenvector is confounded with the noise and the resulting estimate will be,
+in expectation, orthogonal to the actual value.
+A similar behaviour was analysed by \cite{nadler2008} for finite $p,n$.
+Therefore, when the dimension is high and comparable to the number of samples,
+smaller eigenvalues and eigenvectors are very noisy.
+
+%\prm{Intuitively speaking, by setting a lower rank we are estimating a covariance
+%matrix in a lower dimensional subspace. Then, according to
+%\cite{Vershynin2012}, we require a smaller number of samples for a given
+%precision.} \pcomment{The previous argument is not good. I would like to have
+%some theoretical estimate on the number of samples to approximate a lower
+%rank covariance matrix, or equivalently, the number of samples to approximate
+%the largest principal directions. The point I would like to make, is that
+%the number of similar patches required is less if one only wants to estimate
+%the first principal eigenvectors. Maybe the answer lies in \cite{Halko2011}.}
+
+The plots in Figure \pcomment{TODO} show the PSNR of the basic estimate as a function of the 
+rank $r_1$, for several values of $n_{1}$.
+%
+%
+These results behave as expected. Smaller groups obtained by keeping only the
+most similar patches have only a few modes of variation and thus are better
+modelled with a low-rank covariance matrix. As the group of patches grows
+bigger, patches in the group are not as similar anymore, and a higher rank is
+needed to allow for additional modes of variation.
+
+A similar qualitative behaviour can be observed for the second stage, as shown in Figure \pcomment{TODO}. 
+The plots in the figure result from varying the 2nd stage $r_2$ and
+$n_{2}$ parameters.
+%
+Note that for the 2nd stage best results are found with a much smaller value
+for $n_{2}$ than in the first stage.
+%
+A possible explanation is that the noise-less patches, as well as the basic
+estimates, lie close to a low-dimensional subspace. On the other hand, the
+noisy patches, which have been perturbed by isotropic noise and span the entire
+ambient space. Thus, following \cite{Vershynin2012}, more samples are required for
+estimating the covariance matrix in the presence of noise.
+\pcomment{Although we do not have an explanation about why higher levels of noise
+require more samples.}
+
+So far we have studied the parameters affecting the MAP estimation for each stage 
+independently. However, to determine the optimal parameters, we need to look at
+them jointly. The first stage parameters maximizing the PSNR of the basic
+estimate, yield a suboptimal result in terms of the end PSNR.
+%
+Figure \pcomment{TODO} shows a correlation plot for the PSNR of the first and
+second stages obtained when varying \pcomment{TODO}. It can be observed, that the 
+results with the highest basic and final PSNR do not coincide.
+
+The aims of the first and second stage are different: the output 
+of the first stage is used as an oracle in the second stage. As such, it can
+have more variance but it should have a small bias. The reason is that the
+second stage is robust to some noise in the basic estimate, but
+the signal components lost in the first stage are harder to recover.
+
+Due the coupling of the first and second stages, determining the optimal values
+for the pair ranks and number of patches requires a four dimensional parameter
+search, which would take a lot of time.
+%
+Instead, we fix the first stage parameters at
+\[r_1 = s_{x,1}^2s_{t,1}\quad\quad n_{1} = 400,\]
+which we found to give good results. We are being conservative and use the
+full rank covariance matrix to eliminate the least signal components.
+
+We then run a parameter search to determine $r_2$ and $n_{2}$.
+The result is the one in Figure \pcomment{figure used before}. From here
+establish the following values as a function of $\sigma$:
+\[r_2(\sigma) = 40 - \frac13(\sigma - 10)\quad\quad n_{2} = 150.\]
+Note that smaller value for $n_{2}$ could give better results,
+but this comes at a higher computational cost.
+
+%Intuitively, smaller groups obtained by keeping only the most similar patches have 
+%only a few modes of variation and thus are better modelled with a low rank
+%covariance matrix. As the group of patches grows bigger, patches in the group
+%are not as similar anymore, and a higher rank is needed to model these additional 
+%variation.
+%To find appropriate values for these parameters, we compute denoising results
+%varying the rank $r$ and the number of similar patches $n$, while
+%keeping all other parameters fixed. Results are computed for four 20 frames clips
+%extracted from the sequences \emph{bus}, \emph{foreman}, \emph{football} and
+%\emph{tennis}, adding noise of $\sigma = 10, 20, 40$.
+%%
+%We do this for each stage, starting by the second.
+%
+%On this first experiment, the parameters of the first stage are fixed at:
+%\[w_x = 37,\,\,w_t = 5\,\,s_x = 5,\,\,s_t = 4,\,\,n = 375,\,\,r = 100.\]
+%\todo{Check these parameters}
+%Note that $r = 100$ is the full rank.
+%For the second stage, we fix $w_x = 37$, $w_t = 5$, $s_x = 5$ and $s_t = 3$, while varying 
+%$r$ in $10,20,\dots,80$ and $n$ in $50, 150,200,250$.
+%The results can be visualized in Figure \ref{fig:rank-nsim-image-stage2}. The images in the 
+%figure show the PSNR loss in dB with respect to the maximum value attained at each noise level.
+%White means 0dB (\ie the set of parameters where the maximum was attained) and black means a loss
+%greater or equal than 1dB.
+%
+%We can observe that, at constant $n$ there is an optimal value for the rank. Bellow
+%these value the PSNR drops sharply, and above it, the decay is slower. The
+%optimal rank for a given $n$ increases with $n$ and decreases with $\sigma$.
+%Best results are obtained for small $n$. However, this also entails a higher running time, 
+%since it increases the number of groups of similar patches that need to be
+%processed. We found a good compromise by setting $n = 150$ and $r$ as a decreasing function of $\sigma$:
+%\[r(\sigma) = 40 - \frac1{10}(\sigma - 40),\]
+%which corresponds to a line through $(s=10, r = 40)$ and $(s=40, r = 30)$.
+%
+%We now perform a similar search for the first stage, setting the second step parameters as:
+%\[w_x = 37,\,\,w_t = 5\,\,s_x = 5,\,\,s_t = 3,\,\,n = 150,\,\,r(\sigma).\]
+%The first stage parameters are as before, expect that we now vary $r$ in $10,20,\dots,100$
+%and $n$ in $50,100,\dots,650$. Results are shown in Figure
+%\ref{fig:rank-nsim-image-stage1}. Note that since our objective is to maximize
+%the final PSNR, we show here the final PSNR. 
+%The final and the basic PSNRs do not always
+%have the same behaviour. Improving the basic PSNR does not always lead to an
+%improvement in the final one. The reason for this is that it is preferable to
+%apply a conservative noise reduction leaving some noise in the basic estimate
+%(high variance but small bias). In the second step, this residual noise has
+%little effect on the estimation of the patch distances and the \emph{a priori} covariance
+%matrix. On the other hand, applying a more aggressive denoising in first step
+%might increase the basic PSNR, but the second step cannot recover the lost
+%signal components.
+%
+%In fact, best results are obtained using the full rank covariance matrix. 
+%In accordance to these observations, we will set the first values for $r$ and $n$ as:
+%\begin{equation}
+%	r = s_x^2s_t \quad\quad n = 350.
+%	\label{eq:stage1_parameters}
+%\end{equation}
 
@@
 %First we fix the parameters of the second stage at 
-%\[r = 16,\,\, n_{\text{sim}} = 160,\,\, s_x = 5,\,\, s_t = 3,\,\, w_x = 37,\,\, w_t = 5,\]
+%\[r = 16,\,\, n = 160,\,\, s_x = 5,\,\, s_t = 3,\,\, w_x = 37,\,\, w_t = 5,\]
 %and vary the parameters of the first stage. We considered ranks $r = 8, 16, 32, 64$,   
-%patch sizes $s_x = 3,5,7,9$ and number of patches $n_{\text{sim}} = 80, 160, 320, 640$.
+%patch sizes $s_x = 3,5,7,9$ and number of patches $n = 80, 160, 320, 640$.
 %For all $4^3 = 64$ combinations, we considered three levels of noise $\sigma = 10, 20, 40$
@@
 %results. For example, with $\sigma = 10$, equivalent results can be obtained 
-%with $s_x = 3, r = 16, n_{\text{sim}} = 80$, $s_x = 5, r = 32, n_{\text{sim}} = 160$
-%or  $s_x = 7, r = 64, n_{\text{sim}} = 320$.
+%with $s_x = 3, r = 16, n = 80$, $s_x = 5, r = 32, n = 160$
+%or  $s_x = 7, r = 64, n = 320$.
 %The one with the least computational cost is chosen. This means,
@@
 %\begin{equation}
-%	s_t = 5,\quad\quad r = \min(640/\sigma, r_{\text{max}}), \quad\quad n_{\text{sim}} = 16\sigma.
+%	s_t = 5,\quad\quad r = \min(640/\sigma, r_{\text{max}}), \quad\quad n = 16\sigma.
 %	\label{eq:stage1_parameters}
@@
 %%	r &= \min(640/\sigma, r_{\text{max}}) \\
-%%	n_{\text{sim}} &= 16\sigma. 
+%%	n &= 16\sigma. 
 %%	\label{eq:stage1_parameters}
@@
 %\begin{equation}
-%	s_x = 5,\quad r = \max( \min(320/\sigma, r_{\text{max}}), r_{\text{min}}), \quad n_{\text{sim}} = 160.
+%	s_x = 5,\quad r = \max( \min(320/\sigma, r_{\text{max}}), r_{\text{min}}), \quad n = 160.
 %	\label{eq:stage1_parameters}
@@
 	\begin{center}
-		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r2-np2-image_s10_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r2-np2-image_s20_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r2-np2-image_s40_average_derf.eps}\\
-		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r2-np2-image_s10_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r2-np2-image_s20_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r2-np2-image_s40_average_derf.eps}\\
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s10_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s20_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s30_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s40_average_derf.eps}\\
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-image_s10_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-image_s20_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-image_s30_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-image_s40_average_mono.eps}\\
 	\end{center}
-	\caption{Top row: average PSNRs over four sequences, obtained by varying the second stage parameters
-		$r$ and $n_{\text{sim}}$. From left to right, results for $\sigma = 10,
-		20, 40$. In each image, the contrast has been stretched so that white
-		corresponds to the maximum PSNR and black to a decay of 1dB bellow the
-		maximum. 
-		Bottom: corresponding average running times. White corresponds to $50$ s/frame (using parallelization with four threads).}
+	\caption{Top row: average PSNRs over four sequences, obtained by varying the
+		second stage parameters $r$ and $n$. From left to right, results for
+		$\sigma = 10, 20, 40$. In each image, the contrast has been stretched so
+		that white corresponds to the maximum PSNR and black to a decay of 1dB
+		bellow the maximum. 
+		Bottom: same for grayscale sequences.} 
 	\label{fig:rank-nsim-image-stage2}
@@
 	\begin{center}
-		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s10_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s20_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s40_average_derf.eps}\\
-		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s10_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s20_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s40_average_derf.eps}\\
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s10_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s20_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s30_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s40_average_derf.eps}\\
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s10_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s20_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s30_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s40_average_mono.eps}\\
 	\end{center}
@@
 
-%figs/params_tables/psnr_r1-np1-image_s10_bus.eps
-%figs/params_tables/psnr_r1-np1-image_s20_bus.eps
-%figs/params_tables/psnr_r1-np1-image_s40_bus.eps
-%figs/params_tables/time_r1-np1-image_s10_bus.eps
-%figs/params_tables/time_r1-np1-image_s20_bus.eps
-%figs/params_tables/time_r1-np1-image_s40_bus.eps
+%\begin{figure*}[htpb!]
+%	\begin{center}
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r2-np2-image_s10_average_derf.eps}%
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r2-np2-image_s20_average_derf.eps}%
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r2-np2-image_s40_average_derf.eps}\\
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r2-np2-image_s10_average_derf.eps}%
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r2-np2-image_s20_average_derf.eps}%
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r2-np2-image_s40_average_derf.eps}\\
+%	\end{center}
+%	\caption{Top row: average PSNRs over four sequences, obtained by varying the second stage parameters
+%		$r$ and $n$. From left to right, results for $\sigma = 10,
+%		20, 40$. In each image, the contrast has been stretched so that white
+%		corresponds to the maximum PSNR and black to a decay of 1dB bellow the
+%		maximum. 
+%		Bottom: corresponding average running times. White corresponds to $50$ s/frame (using parallelization with four threads).}
+%	\label{fig:rank-nsim-image-stage2}
+%\end{figure*}
+%
+%
+%\begin{figure*}[htpb!]
+%	\begin{center}
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s10_average_derf.eps}%
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s20_average_derf.eps}%
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/psnr_r1-np1-image_s40_average_derf.eps}\\
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s10_average_derf.eps}%
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s20_average_derf.eps}%
+%		\includegraphics[width=.25\textwidth]{figs/params_tables/time_r1-np1-image_s40_average_derf.eps}\\
+%	\end{center}
+%	\caption{Same as Figure \ref{fig:rank-nsim-image-stage2} but for the first stage.}
+%	\label{fig:rank-nsim-image-stage1}
+%\end{figure*}
 
@@
 %	\caption{Average PSNRs for 64 configurations of the first stage parameters
-%		$r$, $n_{\text{sim}}$ and $s_x$. From top to bottom, results for $\sigma = 10, 20, 40$.
+%		$r$, $n$ and $s_x$. From top to bottom, results for $\sigma = 10, 20, 40$.
 %		From left to right: results for $r = 8, 16, 32, 64$.}
@@
 %	\caption{Average PSNRs for 64 configurations of the second stage parameters
-%		$r$, $n_{\text{sim}}$ and $s_x$. From top to bottom, results for $\sigma = 10, 20, 40$.
+%		$r$, $n$ and $s_x$. From top to bottom, results for $\sigma = 10, 20, 40$.
 %		From left to right: results for $r = 8, 16, 32, 64$.}
@@
 %	\item[Number of similar patches:] For the first stage, we set
-%		$N^{(1)}_{\text{sim}} = 3s^2n_t$  (recall that $n_t$ is the temporal
+%		$N^{(1)}_{\text{sim}} = 3s^2w_t$  (recall that $w_t$ is the temporal
 %		extend of the search region). For the second step we 
-%		found better results using fewer patches, thus we set $N^{(2)}_{\text{sim}} = 3/4 s^2n_t$.
-%	\item[Search region:] In both stages, we used $n_x = s^2/2$.
+%		found better results using fewer patches, thus we set $N^{(2)}_{\text{sim}} = 3/4 s^2w_t$.
+%	\item[Search region:] In both stages, we used $w_x = s^2/2$.
 %		For the temporal search region, we found a good trade-off
-%		between computational time and quality of the results for $n_t = 5$. 
+%		between computational time and quality of the results for $w_t = 5$. 
 %	\item[Patch distance threshold:] When building the group of similar patches
-%		in the second stage, more than $N_{\text{sim}}$ patches are allowed if their 
+%		in the second stage, more than $n$ patches are allowed if their 
 %		distances with respect to the reference patch are smaller than a threshold $\tau$.
@@
 % patch size $s = 5$
-% spatial search region $n_x = 37$
-% temporal search region $n_t = 0,3,5$
-% number of similar patches $3 s^2 n_t$, 3/4 s^2 n_t$$
+% spatial search region $w_x = 37$
+% temporal search region $w_t = 0,3,5$
+% number of similar patches $3 s^2 w_t$, 3/4 s^2 w_t$$
 % beta $\beta = 1; 1.2$
@@
 			\multirow{1}{*}{$10$}
-			                      & LZD                  & \bsic{     } & \Best{36.45} & \bsic{     } & \Best{40.49}  & \bsic{     } & \Best{34.46}  & \bsic{     } & \Best{37.03} &              &               &              &              & \bsic{     } &       37.13  \\
+			                      & I-SA-BM4D            & \bsic{     } & \Best{36.45} & \bsic{     } & \Best{40.49}  & \bsic{     } & \Best{34.46}  & \bsic{     } & \Best{37.03} &              &               &              &              & \bsic{     } &       37.13  \\
 			                      & V-BM4D-tip           & \bsic{     } &       35.22  & \bsic{     } &       37.30   & \bsic{     } &       32.81   &              &              &              &       37.66   &              &              & \bsic{     } &       35.11  \\
@@
 			\multirow{1}{*}{$20$}
-			                      & LZD                  & \bsic{     } & \Best{33.36} & \bsic{     } & \Best{37.52}  & \bsic{     } & \Best{31.35}  & \bsic{     } & \Best{33.47} &              &               &              &              & \bsic{     } &       34.08  \\
+			                      & I-SA-BM4D            & \bsic{     } & \Best{33.36} & \bsic{     } & \Best{37.52}  & \bsic{     } & \Best{31.35}  & \bsic{     } & \Best{33.47} &              &               &              &              & \bsic{     } &       34.08  \\
 			                      & V-BM4D-tip           & \bsic{     } &       31.59  & \bsic{     } &       33.79   & \bsic{     } &       28.63   &              &              &              &       34.10   &              &              & \bsic{     } &       31.34  \\
@@
 			\multirow{1}{*}{$30$}
-			                      & LZD                  & \bsic{     } & \Best{31.62} & \bsic{     } & \Best{36.05}  & \bsic{     } & \Best{29.09}  & \bsic{     } & \Best{30.36} &              &               &              &              & \bsic{     } &       32.25  \\
+			                      & I-SA-BM4D            & \bsic{     } & \Best{31.62} & \bsic{     } & \Best{36.05}  & \bsic{     } & \Best{29.09}  & \bsic{     } & \Best{30.36} &              &               &              &              & \bsic{     } &       32.25  \\
 			                      & V-BM4D-tip           & \bsic{     } &       29.72  &              &       31.75   & \bsic{     } &       26.29   &              &              &              &       31.83   &              &              & \bsic{     } &       29.25  \\
@@
 			\multirow{1}{*}{$40$}
-			                      & LZD                  & \bsic{     } & \Best{30.79} & \bsic{     } & \Best{35.12}  & \bsic{     } & \Best{27.56}  & \bsic{     } & \Best{28.93} &              &               &              &              & \bsic{     } &       31.16  \\
+			                      & I-SA-BM4D            & \bsic{     } & \Best{30.79} & \bsic{     } & \Best{35.12}  & \bsic{     } & \Best{27.56}  & \bsic{     } & \Best{28.93} &              &               &              &              & \bsic{     } &       31.16  \\
 			                      & V-BM4D-tip           & \bsic{     } &       28.49  & \bsic{     } &       30.35   & \bsic{     } &       24.60   &              &              &              &       30.10   &              &              & \bsic{     } &       27.81  \\
@@
 %		\multirow{5}{*}{$10$} & V-BM4D-np      &       37.77  &       35.70  &       35.40  &       38.09  &       38.85  \\
-%		                      & VNLB $n_t = 0$ &       36.90  &       35.42  &       34.84  &       38.43  &       38.86  \\
-%		                      & VNLB $n_t = 3$ &       37.65  &       35.87  &       35.38  &       39.09  &       39.69  \\
-%									 & VNLB $n_t = 5$ & \best{37.88} & \best{36.01} & \best{35.53} & \best{39.20} & \best{39.74} \\\hline
+%		                      & VNLB $w_t = 0$ &       36.90  &       35.42  &       34.84  &       38.43  &       38.86  \\
+%		                      & VNLB $w_t = 3$ &       37.65  &       35.87  &       35.38  &       39.09  &       39.69  \\
+%									 & VNLB $w_t = 5$ & \best{37.88} & \best{36.01} & \best{35.53} & \best{39.20} & \best{39.74} \\\hline
 %%									                                                                                           
 %		\multirow{5}{*}{$20$} & V-BM4D-np      &       32.91  &       31.50  &       30.94  &       33.60  &       34.27  \\
-%		                      & VNLB $n_t = 0$ &       33.77  &       32.44  &       31.68  &       35.61  &       35.60  \\
-%									 & VNLB $n_t = 3$ &       34.45  &       32.90  &       32.15  &       35.89  &       36.12  \\
-%									 & VNLB $n_t = 5$ & \best{34.59} & \best{33.02} & \best{32.27} & \best{35.90} & \best{36.12} \\\hline
+%		                      & VNLB $w_t = 0$ &       33.77  &       32.44  &       31.68  &       35.61  &       35.60  \\
+%									 & VNLB $w_t = 3$ &       34.45  &       32.90  &       32.15  &       35.89  &       36.12  \\
+%									 & VNLB $w_t = 5$ & \best{34.59} & \best{33.02} & \best{32.27} & \best{35.90} & \best{36.12} \\\hline
 %%									                                                                                           
 %		\multirow{5}{*}{$40$} & V-BM4D-np      &       30.42  &       29.29  &       28.65  &       31.02  &       31.64  \\
-%		                      & VNLB $n_t = 0$ &       30.55  &       29.41  &       28.66  &       31.78  &       31.86  \\
-%									 & VNLB $n_t = 3$ & \best{31.02} & \best{29.73} & \best{29.03} & \best{31.88} & \best{31.92} \\
-%									 & VNLB $n_t = 5$ & \best{31.06} & \best{29.74} & \best{29.08} &       31.70  &       31.74  \\\hline
+%		                      & VNLB $w_t = 0$ &       30.55  &       29.41  &       28.66  &       31.78  &       31.86  \\
+%									 & VNLB $w_t = 3$ & \best{31.02} & \best{29.73} & \best{29.03} & \best{31.88} & \best{31.92} \\
+%									 & VNLB $w_t = 5$ & \best{31.06} & \best{29.74} & \best{29.08} &       31.70  &       31.74  \\\hline
 %	\end{tabular}
@@
 PSNR values obtained after denoising. For our method, we show results varying the temporal
-component of the patch size between $1$ (2D patch) and $4$ frames.
+component of the patch size between $s_t = 1$ (2D patch) and $s_t = 4$ frames.
 For our method and V-BM4D-mp we show the PSNR of the basic estimate as well.
@@
 \cite{LiZhangDai2011}. This method builds uppon BM4D, which in \cite{Maggioni2013}
-is applied to volumetric imagery. In this work, its applicability to video is
-also explored, and the results show that it is inferior to V-BM4D, at least 
-for moderate noise levels. The method of Li, Zhang and Dai \cite{LiZhangDai2011} 
-considers shape adaptive patches, and also several iterations (in each iteration,
-the previous iterate is used as an oracle to compute patch distances and the
-signal energy in the Wiener filtering step) \todo{Check this}. It seems that both elements
-contribute to achieve this significant difference.
-
-We can see that our results are comarable with the ones of V-BM4D. \todo{We need to find new parameters
-for grayscale sequences. This discussion needs to be rewritten based on the updated results.}
+is applied to volumetric imagery. The authors explore its applicability to video 
+and the results show that it is inferior to V-BM4D, at least 
+for low to moderate noise levels. The method of Li, Zhang and Dai \cite{LiZhangDai2011} 
+considers shape adaptive patches, and performs several iterations. In each iteration,
+the previous iterate is used as an oracle to compute patch distances.
+\padd{An additional difference is that the oracle is not used to determine the
+signal components for the Wiener filter. Instead, these are estimated with a fixed
+point iteration from the original noisy patches.}
+
+We can see that our results outperform the ones of V-BM4D, for all sequences and 
+for all noise levels. The results reported by \cite{LiZhangDai2011} show that there
+is still room for improvement (albeit perhaps at a higher computational cost).
+%
+We have attempted iterating our method as in \cite{LiZhangDai2011},
+but we have not found yet a significant improvement. Something similar was
+reported in \cite{Lebrun2013ipol,Lebrun2013a} for the NL-Bayes method in still
+images. %It may be that the current parameters are not suitable for
+%iteration. 
+A more systematic study is has to be conducted before drawing any
+conclusions about iterative versions of the algorithm.
+%This is the matter of ongoing work, but is out of the scope of the paper.
+%Still, it is early to exclude iteration as an valid option to
+%further improve the denoising performance.
+
+\pcomment{TODO: qualitative comparison.}
+
+Regarding the running time, let us note that the modified profile has a
+computation time lower to that of our method. Running with a
+single core in an Intel Xeon X7560 (2.27GHz) CPU, 
+our current implementation takes on average $XXs$ per frame for a video of CIF
+resolution ($352\times288$). V-BM4D takes $44s$ with the modified profile.
+The running times of \cite{LiZhangDai2011} are not reported, but we expect them
+to be significantly higher given that the algorithm is iterative, with each iteration 
+being comparable to one of the stages of V-BM4D.
+\pcomment{TODO: Compute running times!!!}
+\pcomment{We should include computation times for grayscale videos, instead of color}
 
@@
 
-We compared our method with CIFIC \cite{Dai2013} and V-BM4D \cite{Maggioni2012}, two recent
-state-of-the-art methods. As with grayscale videos, for V-BM4D, we show results corresponding to two
-different parameter configurations: V-BM4D-tip
-corresponds to the results reported
-in \cite{Maggioni2012}, and V-BM4D-mp corresponds to the ``modified profile''
+As with grayscale videos, we compare our method with V-BM4D using two parameter profiles:
+V-BM4D-tip corresponds to the results reported in \cite{Maggioni2012}, and
+V-BM4D-mp corresponds to the ``modified profile''
 of the implementation available online \cite{bm4dcode}.
-
-Let us note that the modified profile has a
-computation time lower to that of our method. Running with a
-single core in a Intel Xeon X7560 (2.27GHz) CPU, 
-our current implementation takes on average $XXs$ per frame for a video of CIF
-resolution ($352\times288$). V-BM4D takes $44s$ with the modified profile.
-\todo{Compute running times!!!}
-
-The results are shown in Table \ref{tab:psnr-classic}. The proposed method is
+In addition, we also compare our method with CIFIC \cite{Dai2013}, a recent
+state-of-the-art method.
+
+The results are shown in Table \ref{tab:psnr-classic-color}. The proposed method is
 labeled VNLB. It achieves the highest PSNR values on all the considered
@@
 
+\pcomment{This paragraph has to change with the new qualitative results.}
 For a qualitative analysis we show in Figure \ref{fig:results} results obtained
-with nonlocal Bayes (setting $n_t = 5$) and V-BM4D-np. Interestingly, for $\sigma = 20$
+with nonlocal Bayes (setting $w_t = 5$) and V-BM4D-np. Interestingly, for $\sigma = 20$
 and $40$, V-BM4D-np is able to better recover the wallpaper texture in tennis,
@@
 allowing to find similar patches with the same regular texture pattern.
+
+\begin{figure*}[htpb!]
+	\centering
+
+	\includegraphics[trim=0cm 7.4cm 0cm 0.5cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/orig-nisy_004.png}
+
+%	\vspace{.1cm}
+%	\includegraphics[trim=0cm 6.9cm 0cm 0cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/vnlb_pt4-orig_004.png}
+%
+	\vspace{.1cm}
+	\includegraphics[trim=0cm 7.4cm 0cm 0.5cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/vnlb_pt4-vnlb_pt1_004.png}
+
+	\vspace{.1cm}
+	\includegraphics[trim=0cm 7.4cm 0cm 0.5cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/vnlb_pt4-bm4d_004.png}
+	\caption{Comparison of the results. To ease comparison and save space, we
+	juxtapose two results on each image in a checkerboard pattern. From top to
+	bottom: original and contaminated sequences, with $\sigma = 40$; result of
+	VNLB using $s_t = 1$ and $s_t = 4$; result of V-BM4D-mp and result of VNLB
+	with $s_t = 4$.}
+	\label{fig:results-army}
+\end{figure*}
+
+\begin{figure*}[htpb!]
+	\centering
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/mobile_mono/tile060-060-080_020.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s10_pt4/nisy_tile060-060-080_020.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s20_pt4/nisy_tile060-060-080_020.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s40_pt4/nisy_tile060-060-080_020.png}\\
+%	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/mobile_mono/tile060-060-080_020.png}%
+	\hspace               {0.2\textwidth}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/mobile_mono_mp_s10/tile060-060-080_020.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/mobile_mono_mp_s20/tile060-060-080_020.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/mobile_mono_mp_s40/tile060-060-080_020.png}\\
+%	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/mobile_mono/tile060-060-080_020.png}%
+	\hspace               {0.2\textwidth}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s10_pt4/tile060-060-080_020.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s20_pt4/tile060-060-080_020.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s40_pt4/tile060-060-080_020.png}\\
+
+	\vspace{.1cm}
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/mobile_mono/tile188-188-065_004.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s10_pt4/nisy_tile188-188-065_004.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s20_pt4/nisy_tile188-188-065_004.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s40_pt4/nisy_tile188-188-065_004.png}\\
+%	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/mobile_mono/tile188-188-065_004.png}%
+	\hspace               {0.2\textwidth}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/mobile_mono_mp_s10/tile188-188-065_004.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/mobile_mono_mp_s20/tile188-188-065_004.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/mobile_mono_mp_s40/tile188-188-065_004.png}\\
+%	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/mobile_mono/tile188-188-065_004.png}%
+	\hspace               {0.2\textwidth}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s10_pt4/tile188-188-065_004.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s20_pt4/tile188-188-065_004.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_mono/mobile_mono_s40_pt4/tile188-188-065_004.png}\\
+	\caption{Results for two details of the mobile grayscale sequence. For each
+	image, on the first row we show: the original image, and the noisy version
+	with $\sigma = 10,20$ and $40$. The second and third rows show the results
+	obtained with V-BM4D-mp and with VNLB with $s_t = 4$.}
+	\label{fig:results_mobile_mono}
+\end{figure*}
+
+\begin{figure*}[htpb!]
+	\centering
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/tennis/tile050-090-030_015.png}% 
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s10_pt4/nisy_tile050-090-030_015.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s20_pt4/nisy_tile050-090-030_015.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s40_pt4/nisy_tile050-090-030_015.png}\\
+%	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/tennis/tile050-090-030_015.png}% 
+	\hspace               {0.2\textwidth}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/tennis_mp_s10/tile050-090-030_015.png}% 
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/tennis_mp_s20/tile050-090-030_015.png}% 
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/tennis_mp_s40/tile050-090-030_015.png}\\
+%	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/tennis/tile050-090-030_015.png}% 
+	\hspace               {0.2\textwidth}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s10_pt4/tile050-090-030_015.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s20_pt4/tile050-090-030_015.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s40_pt4/tile050-090-030_015.png}\\
+
+	\vspace{.1cm}
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/tennis/tile040-150-070_015.png}% 
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s10_pt4/nisy_tile040-150-070_015.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s20_pt4/nisy_tile040-150-070_015.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s40_pt4/nisy_tile040-150-070_015.png}\\
+%	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/tennis/tile040-150-070_015.png}% 
+	\hspace               {0.2\textwidth}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/tennis_mp_s10/tile040-150-070_015.png}% 
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/tennis_mp_s20/tile040-150-070_015.png}% 
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/VBM4D/tennis_mp_s40/tile040-150-070_015.png}\\
+%	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/data/derf/tennis/tile040-150-070_015.png}% 
+	\hspace               {0.2\textwidth}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s10_pt4/tile040-150-070_015.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s20_pt4/tile040-150-070_015.png}%
+	\includegraphics[width=0.2\textwidth]{figs_local_cambridge/vnlb3d_color/tennis_s40_pt4/tile040-150-070_015.png}\\
+	\caption{Results for two details of the tennis color sequence. For each
+	image, on the first row we show: the original image, and the noisy version
+	with $\sigma = 10,20$ and $40$. The second and third rows show the results
+	obtained with V-BM4D-mp and with VNLB with $s_t = 4$.}
+	\label{fig:results-tennis}
+\end{figure*}
 
@@
 % 		                      & V-BM3D        &       36.04  &       36.82  &       37.52  &       34.96  \\
-% 		                      & VNLB $n_t = 0$ &       32.13  &       33.75  &       34.60  &       32.71  \\
-% 		                      & VNLB $n_t = 3$ &       35.12  &       37.20  &       37.89  &       36.14  \\
-% 									 & VNLB $n_t = 5$ &       35.19  & \best{37.26} & \best{38.00} &       36.11  \\\hline
+% 		                      & VNLB $w_t = 0$ &       32.13  &       33.75  &       34.60  &       32.71  \\
+% 		                      & VNLB $w_t = 3$ &       35.12  &       37.20  &       37.89  &       36.14  \\
+% 									 & VNLB $w_t = 5$ &       35.19  & \best{37.26} & \best{38.00} &       36.11  \\\hline
 % %									 
@@
 % 		                      & V-BM3D        &       32.54  &       33.39  &       34.49  &       31.03  \\
-% 		                      & VNLB $n_t = 0$ &       30.58  &       32.47  &       33.44  &       31.26  \\
-% 									 & VNLB $n_t = 3$ &       31.22  &       33.39  &       34.28  &       32.01  \\
-% 		                      & VNLB $n_t = 5$ &       31.25  &       33.44  &       34.34  &       31.94  \\\hline
+% 		                      & VNLB $w_t = 0$ &       30.58  &       32.47  &       33.44  &       31.26  \\
+% 									 & VNLB $w_t = 3$ &       31.22  &       33.39  &       34.28  &       32.01  \\
+% 		                      & VNLB $w_t = 5$ &       31.25  &       33.44  &       34.34  &       31.94  \\\hline
 % %									 
@@
 % 		                      & V-BM3D        &       29.20  &       29.99  &       31.17  &       27.34  \\
-% 		                      & VNLB $n_t = 0$ &       27.24  &       28.55  &       29.74  &       27.37  \\
-% 									 & VNLB $n_t = 3$ &       27.96  &       29.68  &       30.85  &       28.17  \\
-% 									 & VNLB $n_t = 5$ &       28.02  &       29.76  &       30.94  &       28.14  \\\hline
+% 		                      & VNLB $w_t = 0$ &       27.24  &       28.55  &       29.74  &       27.37  \\
+% 									 & VNLB $w_t = 3$ &       27.96  &       29.68  &       30.85  &       28.17  \\
+% 									 & VNLB $w_t = 5$ &       28.02  &       29.76  &       30.94  &       28.14  \\\hline
 % 	\end{tabular}

### 2015-10-13 src/unit_tests/patch_group.cpp
[tools] Update Matlab scripts for generating figures

@@ -324,7 +324,7 @@ int main(int argc, char **argv)
 	const int i_lastFrame  = clo_option("-l", 0, "Last frame");
 	const int i_frameStep  = clo_option("-s", 1, "Frame step");
 
-	const int sigma        = clo_option("-sigma", 0, "Add noise of standard deviation sigma");
+	const int sigma        = clo_option("-sigma", 0, "Standard deviation of the noise");
 	const unsigned px      = clo_option("-PAx", 0, "Point of analysis");
 	const unsigned py      = clo_option("-PAy", 0, "Point of analysis");
 	const unsigned pt      = clo_option("-PAt", 0, "Point of analysis");
@@ -344,12 +344,12 @@ int main(int argc, char **argv)
 	Video<float> vid_bsc;
 	{
 		vid_nsy.loadVideo(i_noisy_path.c_str(), i_firstFrame, i_lastFrame, i_frameStep);
-		print_video_size("loaded noisy video: ", vid_nsy);
+//		print_video_size("loaded noisy video: ", vid_nsy);
 		
 		if (step == 2)
 		{
 			vid_bsc.loadVideo(i_basic_path.c_str(), i_firstFrame, i_lastFrame, i_frameStep);
-			print_video_size("loaded basic video: ", vid_bsc);
+//			print_video_size("loaded basic video: ", vid_bsc);
 		}
 	}
 
@@ -365,14 +365,14 @@ int main(int argc, char **argv)
 		if (num_patches  >= 0) VideoNLB::setNSimilarPatches(prms, (unsigned)num_patches);
 
 		//! Print parameters
-		VideoNLB::printNlbParameters(prms);
+//		VideoNLB::printNlbParameters(prms);
 	}
 
 	//! Compute group of similar patches on selected pixel single pixel
 	{
 		using std::vector;
 
-		printf("computing patch distances for point: [% 3d,% 3d,% 2d]\n\n",px,py,pt);
+//		printf("computing patch distances for point: [% 3d,% 3d,% 2d]\n\n",px,py,pt);
 
 		//! Point
 		unsigned pind = vid_nsy.sz.index(px, py, pt, 0);
@@ -407,13 +407,13 @@ int main(int argc, char **argv)
 			patch_dists = VideoNLB::estimateSimilarPatchesStep1_debug(vid,
 					patch_stack_nsy, patch_index, pind, prms);
 
[…]

### 2015-10-13 tools/compute_bayes_estimate.m

@@ -1,4 +1,13 @@
-function [deno, mean_bsic, U, S] = compute_bayes_estimate(nisy, bsic, sigma, rank)
+function [deno, mean_nisy, U, S, bias] = compute_bayes_estimate(nisy, bsic, sigma, rank, orig, filter_type, U, S)
+
+if nargin < 6,
+	filter_type = 'pos';
+end
+
+if nargin < 7,
+	U = [];
+	S = [];
+end
 
 d = size(nisy,1);
 n = size(nisy,2);
@@ -11,35 +20,82 @@ end
 
 
 % center
+%mean_nisy = 128 + 0*mean(nisy, 2);
+%mean_bsic = 128 + 0*mean(bsic, 2);
 mean_nisy = mean(nisy, 2);
 mean_bsic = mean(bsic, 2);
 nisy = nisy - mean_nisy*ones(1,n);
 bsic = bsic - mean_bsic*ones(1,n);
 
-
-% covariance matrix
-C = 1/n*bsic*bsic';
-
-
-% eigendecomposition
-[U,S] = eigs(C,rank);
+if ~isempty(orig),
+	orig = orig - mean_nisy*ones(1,n);
+end
 
 
-% sort well
-tmp = sortrows([ diag(S) U'],-1);
-S = diag(tmp(:,1));
-U = tmp(:,2:end)';
+if isempty(S),
+
+	if isempty(U),
+		% covariance matrix
+		C = 1/n*bsic*bsic';
+		
+		% eigendecomposition
+		if rank > 0 && rank < d,
+			[U,S] = eigs(C,rank);
+		else
+			[U,S] = eig(C);
+		end
+		
+		U = real(U);
+		S = real(S);
+	else
+		% project data vectors onto basis
+		S = diag(mean((U'*bsic).^2,2));
+	end
+	
+	
+	% sort
+	tmp = sortrows([ diag(S) U'],-1);
+	S = diag(tmp(:,1));
+	U = tmp(:,2:end)';
+	
+	% wiener filter coefficients
+	%S = max(0, diag(S) - sigma_bsic*sigma_bsic);
+	if     strcmp(filter_type, 'pos'), 
+		S = min(max( 0  , diag(S) - sigma_bsic*sigma_bsic),Inf);
+		S = diag(1./(1 + sigma*sigma ./ S));
+%		S = diag(double(S > 0));
[…]

### 2015-10-13 tools/patch_group.m

@@ -10,8 +10,8 @@ prms.wx = 37;
 prms.wt = 2;
 prms.px = 9;
 prms.pt = 4;
-prms.np = 160;
-sigma = '0';
+prms.np = 200;
+sigma = 40;
 
 % binary that computes patch distances
 pgbin = '/home/pariasm/Work/denoising/projects/video_nlbayes3d/build/bin/patch_group';
@@ -33,19 +33,19 @@ clear seqnames first last
 seq = sequences(1);
 
 ori_pat = [orig_path seq.name '/%03d.png'];                     % ground truth
-if strcat(sigma,'0'),
+if (sigma == 0),
 	nsy_pat = ori_pat; % noisy
 else
-	nsy_pat = [nlb3_path seq.name '_s' sigma '_pt4/nisy_%03d.png']; % noisy
+	nsy_pat = [nlb3_path seq.name '_s' num2str(sigma) '_pt4/nisy_%03d.png']; % noisy
 end
-bsc_pat = [nlb3_path seq.name '_s' sigma '_pt4/bsic_%03d.png']; % nlb3 pt2
+bsc_pat = [nlb3_path seq.name '_s' num2str(sigma) '_pt4/bsic_%03d.png']; % nlb3 pt2
 
 command = [pgbin ...
            ' -i ' ori_pat ...
            ' -b ' ori_pat ...
            ' -f ' num2str(seq.first) ...
            ' -l ' num2str(seq.last) ...
-           ' -sigma ' sigma ...
+           ' -sigma ' num2str(sigma) ...
            ' -px ' num2str(prms.px) ...
            ' -pt ' num2str(prms.pt) ...
            ' -wx ' num2str(prms.wx) ...
@@ -148,7 +148,8 @@ while (goon)
 
 		gsz  = size(patches.nisy);
 		pdim = prod(gsz(1:4));
-		[dd,m,U,S] = compute_bayes_estimate(reshape(patches.nisy,[pdim gsz(5)]),[],40,16);
+		rank = 40;
+		[dd,m,U,S] = compute_bayes_estimate(reshape(patches.nisy,[pdim gsz(5)]),[],sigma,rank,[]);
 		dd = reshape(dd,gsz);
 		dd = min(255, max(0, dd));
 
@@ -160,8 +161,8 @@ while (goon)
 		imagesc([pp ; dd ; oo]/255), axis equal, axis off
 
 		% display also eigenvectors and eigenvalues
[…]

### 2015-10-13 tools/psnr_vs_rank_np_images.m

@@ -1,206 +1,421 @@
 root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/';
 
-stage2_folder = [root_folder 'table_2r_vs_2np_derf/'];
-stage1_folder = [root_folder 'table_1r_vs_1np_derf/'];
+%stage2_folder = [root_folder 'table_2r_vs_2np_derf/'];
+stage2_folder = [root_folder 'tip_table_2r_vs_2np_derf/'];
+stage1_folder = [root_folder 'tip_table_1r_vs_1np_derf/'];
 
-% % stage 2 ---------------------------------------------------
-% ranks = [10:10:80];
-% nsims = [50:50:200];
-% nseqs = 4;
-% 
-% f10 = zeros(length(nsims),length(ranks),nseqs);
-% f20 = zeros(length(nsims),length(ranks),nseqs);
-% f40 = zeros(length(nsims),length(ranks),nseqs);
-% 
-% f10(:,:,1) = load([stage2_folder 'table_fpsnr_bus_s10']);
-% f10(:,:,2) = load([stage2_folder 'table_fpsnr_football_s10']);
-% f10(:,:,3) = load([stage2_folder 'table_fpsnr_foreman_s10']);
-% f10(:,:,4) = load([stage2_folder 'table_fpsnr_tennis_s10']);
-% 
-% f20(:,:,1) = load([stage2_folder 'table_fpsnr_bus_s20']);
-% f20(:,:,2) = load([stage2_folder 'table_fpsnr_football_s20']);
-% f20(:,:,3) = load([stage2_folder 'table_fpsnr_foreman_s20']);
-% f20(:,:,4) = load([stage2_folder 'table_fpsnr_tennis_s20']);
-% 
-% f40(:,:,1) = load([stage2_folder 'table_fpsnr_bus_s40']);
-% f40(:,:,2) = load([stage2_folder 'table_fpsnr_football_s40']);
-% f40(:,:,3) = load([stage2_folder 'table_fpsnr_foreman_s40']);
-% f40(:,:,4) = load([stage2_folder 'table_fpsnr_tennis_s40']);
-% 
-% mf10 = mean(f10,3);
-% mf20 = mean(f20,3);
-% mf40 = mean(f40,3);
-% 
[…]

### 2015-10-13 tools/psnr_vs_rank_np_images_mono.m

@@ -1,7 +1,320 @@
 root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/';
+%
+%stage1_folder = [root_folder 'table_1r_vs_1np_mono/'];
+%stage2_folder = [root_folder 'table_2r_vs_2np_mono/'];
+stage1_folder = [root_folder 'table_1r_vs_1np_mono-gtoracle/'];
+stage2_folder = [root_folder 'table_2r_vs_2np_mono-gtoracle/'];
+%stage2_folder = [root_folder 'table_2r_vs_2np_mono-gtoracle-2nditer/'];
 
-stage1_folder = [root_folder 'table_1r_vs_1np_mono/'];
-stage2_folder = [root_folder 'table_2r_vs_2np_mono/'];
+
+
+
+% <--> % % stage 1 ---------------------------------------------------
+% <--> % ranks = [5:5:210];
+% <--> % nsims = [50:100:1250];
+% <--> % 
+% <--> % %seqs = {'tennis_mono', 'mobile_mono', 'stefan_mono', 'gflower', 'gsalesman'};
+% <--> % seqs = {'tennis_mono', 'mobile_mono', 'stefan_mono', 'gsalesman'};
+% <--> % nseqs = length(seqs);
+% <--> % 
+% <--> % mff   = zeros(length(nsims),length(ranks),4);
+% <--> % minff = zeros(length(nsims),length(ranks),4);
+% <--> % 
+% <--> % ranks_l = ranks(2:4:end);
+% <--> % [rr_l, nn_l] = meshgrid(ranks_l,nsims);
+% <--> % [rr_h, nn_h] = meshgrid(ranks  ,nsims);
+% <--> % 
+% <--> % for s = 10:10:40,
+% <--> % 
+% <--> % 	ff = zeros(length(nsims),length(ranks),nseqs);
+% <--> % 
+% <--> % 	for i = 1:length(seqs),
+% <--> % 		tmp = load([stage1_folder 'table_fpsnr_' seqs{i} '_s' num2str(s)]);
+% <--> % 		tmp(tmp == 0) = NaN;
+% <--> % 
+% <--> % 		tmp_l = tmp(:,2:4:end);
[…]

### 2015-10-13 tools/nlbayes.m
[tools] Matlab version of nlbayes for testing

@@ -1,0 +1,127 @@
+% loads a video and allows the user to select a pixel
+% for the selected pixel, it displays the locations 
+% of the most similar patches
+
+%clear all
+
+
+% parameters
+prms1.wx = 37;
+prms1.wt = 2;
+prms1.px = 7;
+prms1.pt = 3;
+prms1.np = 10;
+prms1.r  = -1;
+
+prms2.wx = 37;
+prms2.wt = 2;
+prms2.px = 7;
+prms2.pt = 3;
+prms2.np = 10;
+prms2.r  = -1;
+
+sigma = 40;
+
+% binary that computes patch distances
+pgbin = '/home/pariasm/Work/denoising/projects/video_nlbayes3d/build/bin/patch_group';
+
+% path to data
+base_path = '../../../';
+orig_path = [base_path 'data/derf/'];
+
+% sequence data
+seqnames = {'bus','coastguard','foreman','tennis'};
+first    = {1    , 1          , 1       , 1      };
+last     = {150  , 300        , 300     , 150    };
+
+sequences = struct('name',seqnames,'first',first,'last',last);
+clear seqnames first last
+
+% select a sequence
+seq = sequences(1);
+
+ori_pat = [orig_path seq.name '/%03d.png'];                     % ground truth
+
+% load
+orig = single(load_sequence(ori_pat, seq.first, seq.last));
+%randn('seed',0)
+%nisy = orig + sigma*randn(size(orig));
+
+% process only luminance
+%nisy = mean(nisy,3);
+%orig = 128 + 0*mean(orig,3);
+orig = mean(orig,3);
+%sigma = sigma/sqrt(3);
+
+%randn('seed',0)
+nisy = orig + sigma*randn(size(orig));
+
+% crop
+cropx = [170,270];
+cropy = [ 30,130];
+cropt = [  1, 10];
+
+nisy = nisy(cropy(1):cropy(2),cropx(1):cropx(2),:,cropt(1):cropt(2));
+orig = orig(cropy(1):cropy(2),cropx(1):cropx(2),:,cropt(1):cropt(2));
+
+
[…]

### 2015-10-15 doc/201507_tip/paper.tex
[doc] Advances in TIP paper. Parameter section.

@@
 
-According to \cite{Vershynin2012}, the number of patches needed to achieve a given approximation
+The problem of estimating the covariance matrix has received a lot of attention in the
+past ten years.
+According to \cite{Vershynin2012}, the number of samples needed to achieve a given approximation
 error between the empirical and the true covariances grows linearly with the
 dimensionality of the space spanned by the data. 
-\pcomment{Comment 1: Actually, I found results relating the number of samples with
-the dimensionality of the ambient space. 
-However, if the data lies in a $p$-dimensional subspace, one could 
-compute a basis of this subspace from $n > p$ samples, and work in the low-dim
-coordinates to estimate a covariance matrix there. In that way, one could build
-a covariance matrix in the ambient space.}
-\pcomment{Comment 2: This reference may not be as relevant, in the light of the 
+%\pcomment{Comment: Actually, I found results relating the number of samples with
+%the dimensionality of the ambient space. 
+%However, if the data lies in a $p$-dimensional subspace, one could 
+%compute a basis of this subspace from $n > p$ samples, and work in the low-dim
+%coordinates to estimate a covariance matrix there. In that way, one could build
+%a covariance matrix in the ambient space.}
+\pcomment{Comment: This reference may not be as relevant, in the light of the 
 results known for Gaussian covariance matrices. It would be interesting to see what 
@@
 %
-The case of Gaussian models with covariance matrices of the form $C + \sigma^2I$,
-where $C$ is of rank $r$, has been studied in the statistics and physics
-literature. The authors in \cite{johnstone2009,paul2007} study the
+The case of Gaussian models with covariance matrices of the form $C = A + \sigma^2I$,
+where $A$ is does not have full rank, has been studied in the statistics and physics
+literature. The authors in \cite{johnstone2009,paul2007,nadler2008} study the
 limit when $n,p\to\infty$ such that $p/n\to\gamma < \infty$.
-All these works show that, for a non-zero ratio $\gamma$, the empirical eigenvectors 
+These works show that, for a non-zero ratio $\gamma$, the empirical eigenvectors 
 and eigenvalues are inconsistent estimators of the population ones.
 Furthermore, the smaller eigenvalues and their eigenvectors will have a higher
-error and eventually, if the signal-to-noise ratio drops bellow than $\sqrt{\gamma}$, 
-the eigenvector is confounded with the noise and the resulting estimate will be,
+error and eventually, if the signal-to-noise ratio drops bellow $\sqrt{\gamma}$, 
+the eigenvector is confused with the noise and the resulting estimate will be,
 in expectation, orthogonal to the actual value.
-A similar behaviour was analysed by \cite{nadler2008} for finite $p,n$.
-Therefore, when the dimension is high and comparable to the number of samples,
-smaller eigenvalues and eigenvectors are very noisy.
+Finite sample bounds for the eigenvalues and eigenvectors have been also studied 
+by \cite{nadler2008}, in the case in which $A$ has rank 1.
+\pcomment{What can we say about this bounds.}
+These larger errors between the sample eigenvectors and their population
+counterparts manifest themselves as noise, which then affects the MAP estimate.
+This suggest that better denoising should be obtained by discarding the
+eigenvectors associated with lower eigenvalues.
 
@@
 
-The plots in Figure \pcomment{TODO} show the PSNR of the basic estimate as a function of the 
-rank $r_1$, for several values of $n_{1}$.
-%
-%
-These results behave as expected. Smaller groups obtained by keeping only the
-most similar patches have only a few modes of variation and thus are better
-modelled with a low-rank covariance matrix. As the group of patches grows
-bigger, patches in the group are not as similar anymore, and a higher rank is
-needed to allow for additional modes of variation.
-
-A similar qualitative behaviour can be observed for the second stage, as shown in Figure \pcomment{TODO}. 
-The plots in the figure result from varying the 2nd stage $r_2$ and
-$n_{2}$ parameters.
-%
-Note that for the 2nd stage best results are found with a much smaller value
+The plots in Figure \ref{fig:rank1-nsim1-bpsnr} show the PSNR of the basic
+estimate as a function of the rank $r_1$, for several values of $n_{1}$.
+The curves correspond to an average over 20 frames clips 
+extracted from four classical test
+sequences, namely \emph{bus}, \emph{foreman}, \emph{football} and \emph{tennis}.
+The sequences were contaminated with AGWN of standard deviation $\sigma = 10,
+20, 30, 40$. 
+%
+%
+We can interpret the results in the light of the theoretical results
+described above.
+For all noise levels, best results are obtained when using a larger number of
+samples $n_1$. All curves of fixed $n_1$ show a maximum at a given rank lower than
+the dimensionality of the patch. As the noise level increases, this optimal rank
+shifts to the left. This makes sense, since less eigenvectors are reliable estimates.
+%
+Also, for a fixed noise level, the optimal rank is smaller for smaller values of $n_1$.
+Smaller groups obtained by keeping only the
+most similar patches have less modes of variation, and thus a worse signal-to-noise ratio
+in the eigenvectors with lower eigenvalues.
+%As the group of patches grows
+%bigger, patches in the group are not as similar anymore, and a higher rank is
+%needed to allow for additional modes of variation.
+
+The results obtained for the final estimate when varying the second stage
+parameters $n_2$ and $r_2$ show a different behaviour, as shown in Figure
+\ref{fig:rank2-nsim2-fpsnr}.
+These curves where obtained fixing the first stage parameters at $n_1 = 400$
+and $r_1 = 100$ (full rank).
+\pcomment{It doesn't make much sense considering $r_1 = 100$ after saying that
+is best to consider a low $r_1$.}
+%
+In the second stage best results are found with a much smaller value
 for $n_{2}$ than in the first stage.
 %
-A possible explanation is that the noise-less patches, as well as the basic
-estimates, lie close to a low-dimensional subspace. On the other hand, the
-noisy patches, which have been perturbed by isotropic noise and span the entire
-ambient space. Thus, following \cite{Vershynin2012}, more samples are required for
-estimating the covariance matrix in the presence of noise.
-\pcomment{Although we do not have an explanation about why higher levels of noise
-require more samples.}
+The reason for this is that in the second stage the sample covariance is computed
+using patches from the basic estimate, with a much lower noise level.
+In this setting, there is no gain in increasing the number of patches,
+and there seems to be a loss possibly due to the fact that smaller groups of patches
+are better modelled by a Gaussian distribution.
+\pcomment{I don't have an explanation for the curves for $\sigma = 10$. Precisely
+in the lower noise level, the PSNR drops when $n_2$ is reduced, except for lower ranks.
+This contradicts the argument given: for less noise, it should be always better to consider
+less patches, not only for lower ranks.}
 
@@
 %
-Figure \pcomment{TODO} shows a correlation plot for the PSNR of the first and
-second stages obtained when varying \pcomment{TODO}. It can be observed, that the 
+Figure \ref{fig:rank1-nsim1-bpsnr-fpsnr} plots for the PSNR of the first and
+second stages obtained when varying $n_1$ and $r_1$ as in Figure
+\ref{fig:rank1-nsim1-bpsnr}. It can be observed, that the 
 results with the highest basic and final PSNR do not coincide.
-
+%
 The aims of the first and second stage are different: the output 
@@
 the signal components lost in the first stage are harder to recover.
+\pcomment{The figure shows actually the opposite!!}
 
 Due the coupling of the first and second stages, determining the optimal values
-for the pair ranks and number of patches requires a four dimensional parameter
-search, which would take a lot of time.
+for the ranks $r_1, r_2$ and the number of patches $n_1,n_2$ requires a four
+dimensional parameter search.
 %
@@
 \[r_1 = s_{x,1}^2s_{t,1}\quad\quad n_{1} = 400,\]
-which we found to give good results. We are being conservative and use the
-full rank covariance matrix to eliminate the least signal components.
-
+which we found to give good results. In doing so, we are being conservative and
+use the full rank covariance matrix to eliminate the least signal components.
+%
 We then run a parameter search to determine $r_2$ and $n_{2}$.
-The result is the one in Figure \pcomment{figure used before}. From here
+The results is the ones shown in Figure \ref{fig:rank1-nsim1-fpsnr}. From here
 establish the following values as a function of $\sigma$:
-\[r_2(\sigma) = 40 - \frac13(\sigma - 10)\quad\quad n_{2} = 150.\]
-Note that smaller value for $n_{2}$ could give better results,
-but this comes at a higher computational cost.
+%\[r_2(\sigma) = 40 - \frac13(\sigma - 10)\quad\quad n_{2} = 150.\]
+\[r_2(\sigma) = 35 - \frac12(\sigma - 10)\quad\quad n_{2} = 100.\]
+Note that a higher value for $n_{2}$ would give slightly worse results,
+at a lower computational cost.
 
@@
 	\begin{center}
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s10_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s20_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s30_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s40_average_derf.eps}\\
+
+		\vspace{1cm}
+		\pcomment{TODO: Figures for grayscale sequences}
+		\vspace{1cm}
+
+	\end{center}
+	\caption{Basic estimate PSNR, averaged over four sequences, when varying the
+		second stage parameters $r_1$ and $n_1$. From left to right, results for
+		$\sigma = 10, 20, 30, 40$. In the top row: results for RGB sequences, bottom
+		row, results for grayscale sequences.} 
+	\label{fig:rank1-nsim1-bpsnr}
+\end{figure*}
+
+\begin{figure*}[htpb!]
+	\begin{center}
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s10_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s20_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s30_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s40_average_derf.eps}\\
+
+		\vspace{1cm}
+		\pcomment{TODO: Figures for grayscale sequences}
+		\vspace{1cm}
+
+	\end{center}
+	\caption{PSNRs of final vs. basic estimate. Averages over four sequences, when varying the
+		second stage parameters $r_1$ and $n_1$. From left to right, results for
+		$\sigma = 10, 20, 30, 40$. Top: results for RGB sequences; bottom:
+		results for grayscale sequences. The width of the line is proportional to
+		the rank. \pcomment{These plots contradict the argument in favour of using
+		full rank in the first stage (supposedly introducing a higher variance, but a
+		smaller bias). It turns out, that (1) the final PSNR is pretty much
+		correlated with the basic PSNR, and (2) the optimal rank for the final
+		estimate is lower than that of the basic estimate. I do not have an explanation for this.}} 
+	\label{fig:rank1-nsim1-bpsnr-fpsnr}
+\end{figure*}
+
+\begin{figure*}[htpb!]
+	\begin{center}
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s10_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s20_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s30_average_derf.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s40_average_derf.eps}\\
+
+		\vspace{1cm}
+		\pcomment{TODO: Figures for grayscale sequences}
+		\vspace{1cm}
+
+	\end{center}
+	\caption{Final estimate PSNR, averaged over four sequences, when varying the
+		second stage parameters $r_1$ and $n_1$. From left to right, results for
+		$\sigma = 10, 20, 30, 40$. In the top row: results for RGB sequences, bottom
+		row, results for grayscale sequences.} 
+	\label{fig:rank1-nsim1-fpsnr}
+\end{figure*}
+
+\begin{figure*}[htpb!]
+	\begin{center}
 		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s10_average_derf.eps}%
@@
 		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s40_average_derf.eps}\\
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-image_s10_average_mono.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-image_s20_average_mono.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-image_s30_average_mono.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-image_s40_average_mono.eps}\\
+
+		\vspace{1cm}
+		\pcomment{TODO: Figures for grayscale sequences}
+		\vspace{1cm}
+
 	\end{center}
-	\caption{Top row: average PSNRs over four sequences, obtained by varying the
-		second stage parameters $r$ and $n$. From left to right, results for
-		$\sigma = 10, 20, 40$. In each image, the contrast has been stretched so
-		that white corresponds to the maximum PSNR and black to a decay of 1dB
-		bellow the maximum. 
-		Bottom: same for grayscale sequences.} 
-	\label{fig:rank-nsim-image-stage2}
-\end{figure*}
-
-\begin{figure*}[htpb!]
-	\begin{center}
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s10_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s20_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s30_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s40_average_derf.eps}\\
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s10_average_mono.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s20_average_mono.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s30_average_mono.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-image_s40_average_mono.eps}\\
-	\end{center}
-	\caption{Same as Figure \ref{fig:rank-nsim-image-stage2} but for the first stage.}
-	\label{fig:rank-nsim-image-stage1}
+	\caption{Final estimate PSNR, averaged over four sequences, when varying the
+		second stage parameters $r_2$ and $n_2$. From left to right, results for
+		$\sigma = 10, 20, 30, 40$. In the top row: results for RGB sequences, bottom
+		row, results for grayscale sequences.} 
+	\label{fig:rank2-nsim2-fpsnr}
 \end{figure*}

### 2015-10-15 tools/psnr_vs_rank_np_images.m

@@ -4,7 +4,10 @@ root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/res
 stage2_folder = [root_folder 'tip_table_2r_vs_2np_derf/'];
 stage1_folder = [root_folder 'tip_table_1r_vs_1np_derf/'];
 
-%-:-% % stage 2 ---------------------------------------------------
+% stage 2 ---------------------------------------------------
+
+%-:-% % USE THIS CODE TO INTERPOLATE MISSING VALUES IN THE TABLES
+%-:-% % THIS IS USEFULL FOR DISPLAYING RESULTS WITH IMAGESC
 %-:-% ranks = [5:5:110];
 %-:-% nsims = [50:50:350];
 %-:-% seqs = {'bus', 'football', 'foreman', 'tennis'};
@@ -30,21 +33,21 @@ stage1_folder = [root_folder 'tip_table_1r_vs_1np_derf/'];
 %-:-% 		ff(:,ranks <= 50,i) = tmp(:,ranks <= 50);
 %-:-% 	end
 %-:-% 
-%-:-% %	% ----------------------------
-%-:-% %	% final psnr for each sequence
-%-:-% %	for i = 1:length(seqs),
-%-:-% %		m = max(max(ff(:,1:end-1,i)));
-%-:-% %		imagesc(ff(:,:,i), m + [-.5 0]),
-%-:-% %		axis equal,axis tight, colormap default
-%-:-% %		colorbar
-%-:-% %		set(gca,'XTick',[1:length(ranks)])
-%-:-% %		set(gca,'YTick',[1:length(nsims)])
-%-:-% %		set(gca,'XTickLabel',ranks)
-%-:-% %		set(gca,'YTickLabel',nsims)
-%-:-% %		xlabel('r')
-%-:-% %		ylabel('n')
-%-:-% %%		print(gcf, '-depsc2', ['fpsnr_r1-np1-image_s' num2str(s) '_' seqs{i}]);
-%-:-% %	end
+%-:-% 	% ----------------------------
+%-:-% 	% final psnr for each sequence
+%-:-% 	for i = 1:length(seqs),
+%-:-% 		m = max(max(ff(:,1:end-1,i)));
+%-:-% 		imagesc(ff(:,:,i), m + [-.5 0]),
[…]

### 2015-10-16 doc/201507_tip/paper.tex
[doc] TIP paper text almost finished. Still missing updated experiments.

@@
 hinders its use for any application. 
-\todo{Add references for claims about sensors, camera prices, etc.}
-
-Video denoising has received much less attention than still image denoising. 
-In principle, video denoising should be easier than image denoising, since the
-strong temporal redundancy along motion trajectories favours the denoising
-task. However, this additional form of redundancy creates challenges.  On one
-hand, the amount of data is much larger than for still images, and efficient
-ways of navigating through this data are needed. On the other hand, the output
-of the denoising algorithm should be temporally consistent according to the
-motion of the original sequence.
+\pcomment{It would be nice to have some reference for these claims about
+sensors, camera prices, etc.}
+
+Video denoising has received much less attention than still image denoising in
+the literature.  In principle, denoising videos should be easier than still
+images, since the strong temporal redundancy along motion trajectories favours
+the denoising task. However, this additional form of redundancy creates
+challenges.  On one hand, the amount of data is much larger than for still
+images, and efficient ways of navigating through this data are needed. On the
+other hand, the output of the denoising algorithm should be temporally
+consistent according to the motion of the original sequence.
 
@@
 \cite{Rajpoot2003,Wilson2004,Selesnick2003}. 
-\todo{Read these references. Even if they consider a 3D transform, I think
+\pcomment{TODO: Read these references. Even if they consider a 3D transform, I think
 they DO distinguish between space and time}
 
-Until the advent of patch-based approaches, methods that do not compensate
-motion failed for sequences with moderate motion, and their main interest resided
+Until the advent of patch-based approaches, methods without motion compensation
+failed in the presence of moderate motion, and their main interest resided
 in their simplicity and low computational cost. First state-of-the-art results
@@
 The methods in \cite{Buades2005v} and \cite{Dabov2007v} are extensions to video
-of still image patch-based denoising algorithms (non-local means REF and BM3D
-REF respectively). They are based on \suggest{filtering} similar 2D patches
+of still image patch-based denoising algorithms (non-local means \cite{Buades2006} and BM3D
+\cite{Dabov2007tip} respectively). They are based on filtering similar 2D patches
 searched for in a 3D spatio-temporal neighborhood. These methods exploit both
@@
 terms of the temporal consistency attained.
+The method works by learning a Gaussian \emph{a priori} model from sets of 
+similar noisy patches. Each patch is denoised by computing the \emph{maximum a
+posteriori} (MAP) with the estimated prior.
+Learning the Gaussian prior amounts to estimating a covariance matrix with a
+limited number of samples in a high dimensional space. Motivated by recent 
+theoretical results and supported by an empirical analysis, we add the 
+assumtion that the \emph{a priori} model is of low rank (\ie the clean patches
+lie in a lower dimensional subspace). This assumtion lowers the computational cost
+of the algorithm, and improves the results.
 
@@
 
-The rest of the paper is structured as follows: in \S
+The rest of the paper is organized as follows: in \S
 \ref{sec:review_nonlocal_Bayes} we review the Bayesian patch denoising principle 
-and describe our extension to video. In \S \ref{sec:parameters}
-we discuss its parameters. Some results, including a comparison with VBM4D, are shown
-in \S \ref{sec:results}. Concluding remarks are given in \S \ref{sec:conclusion}
+and describe our extension to video. The final algorithm and details about its
+implementation are given in \S \ref{sec:algorithm}.
+Some relevant aspects of the proposed method are discussed in \S
+\ref{sec:discussion}.
+In \S \ref{sec:parameters}
+we explain the selection of the parameters. Some results, including a
+comparison with the state-of-the-art methods, are shown in \S
+\ref{sec:results}. Concluding remarks are given in \S \ref{sec:conclusion}.
 
@@
 The Figures \ref{fig:patch_groups_pos} and \ref{fig:patch_groups_patches}
-show two example of groups of similar patches. Figure \ref{fig:patch_group_pos}
-shows the position of 200 nearest neighbors of a reference patch. It can be noticed
-that inspite of the noise
+show two examples of groups of similar $9\times 9\times 4$ patches taken from
+a sequence contaminated with AGWN of $\sigma = 40$. Figure
+\ref{fig:patch_groups_pos} shows the position of 200 nearest neighbors of a
+reference patch searched in a $37\times 37\times 5$ search region. The
+reference patch is centered in the central frame. The position of the first 5
+similar patches are highlighted in red, and they follow the trajectory of the
+reference patch throughout the search region.  The next 40 similar patches are
+shown in red. In the first example they are spatially shifted versions of the
+five nearest neighbors. In the second example, in addition to these shifts
+other similar structures in the red sign are detected.  The next nearest
+neighbors are shown in blue.
+
+Figure \ref{fig:patch_groups_patches} shows the 20 nearest neighbors in 
+more detail. Each patch is displayed by vertically stacking its four $9\times
+9$ spatial slices. For the two examples shown in Figure \ref{fig:patch_groups_pos}
+the figure shows the noisy patches, the result of the MAP estimation (setting
+$r = 40$) and the mean patch together with the leading 19 principal directions.
+Since the patch is not motion-compensated, all spatial slices can be different,
+and thus the same applies to the principal directions.
+The spatial slices of the principal directions show oscillating patterns, with
+increasing frequency. In some cases these patterns are localized in a part of
+the spatial slice.
 
@@
 	In red we show the positions of the 5 nearest neighbors, in green the next 40 and in blue the rest.
-	Note the points shown correspond to the top-left pixel of the first temporal
+	Note the points shown correspond to the top-left pixel of the first spatial
 	slice of each patch.
-	The reference patch is the red patch in the center of the search region.}
+	The reference patch is the red patch in the center of the search region. To highlight the
+	position of the patches, the color of the images has been attenuated.}
 	\label{fig:patch_groups_pos}
@@
 	and first 19 principal directions computed from the sample covariance matrix (bottom).
-	For each image, each column corresponds to the 4 temporal slices of a $9\times9\times4$ patch.}
+	For each image, each column corresponds to the 4 spatial slices of a $9\times9\times4$ patch.}
 	\label{fig:patch_groups_patches}
@@
 
-\section{Discussion}
-
-\subsection{Spatio-temporal patches}
-
-Patch-based methods filter similar patches to remove noise. When the noise is
-Gaussian, the patch similarity is determined based on the (squared) Euclidean distance 
-between patches. Due to the noise, the Euclidean distance follows a non-central
-$\chi^2$ distribution, with variance
-\[\textnormal{Var}\left\{\frac1{m}\|\ma q_1 - \ma q_2\|^2\right\} = \frac{8\sigma^2}{m}\left(\sigma^2 + \frac1{m}\|\ma p_1 - \ma p_2\|^2\right),\]
-where $\ma q_1, \ma q_2$ are the noisy versions of the patches $\ma p_1, \ma p_2$, 
-and $m$ denotes the number of pixels in the patch. The noise in the patch comparison
-can be reduced by considering larger patches.
-However, increasing the size of the patch also increases the distances between
-patches and reduces the likelihood of finding similar patches.
-%
-The additional temporal dimension in a spatio-temporal patch allows to increase
-the number of pixels in the patch, without increasing its spatial size.
-Due to the high redundancy of the video in the temporal dimension, increasing the 
-temporal size of the patch causes a much lower increase in the patch distances.
-%The high redundancy of the video in the temporal dimension, allows to have 
-%larger patches without affecting much the number of nearest neighbors of the patch.
-%
-
-Let us assume that 
-the brightness of the original video is constant along motion trajectories, so
-that $u(x,t + \tau) = u(\varphi(x,t + \tau; -\tau),t)$, where
-$\varphi(x,t+\tau;\, \cdot\, )$ denotes the motion trajectory passing though
-$(x,t + \tau)$.
-Furthermore, let us assume that the motion in the video is approximately
-translational.
-When the motion is known or can be estimated, then it is natural to consider
-motion compensated spatio-temporal patches. 
-With the assumptions we are considering, all spatial slices of a $s_x\times s_x\times s_t$ motion-compensated patch
-coincide, so the distance between two spatio-temporal patches is proportional to
-the distance of a 2D spatial patch of size $s_x\times s_x$.
-%
-As a consequence, by increasing $s_t$, on can reduce the 
-noise in the patch distance and have the same pattern of self-similarity as a 
-2D patch.
-
-However, motion estimation is challenging, and even more so in the presence of noise.
-%Most motion estimation techniques integrate spatial information either 
-%by matching 2D patches (or blocks, as they are commonly referred to in the
-%motion estimation literature) or by some spatial regularization term in an energy.
-An option that does not require motion is to use rectangular spatio-temporal patches.
-The distance between these can be also expressed as a distance between spatial patches,
-but their equivalent spatial support is larger than $s_x\times s_x$.
-
-%To see this, let us observe that the squared Euclidean distance can be expressed as
-%the convolution with a separable kernel.
-To see this, let us assume that the motion in the video is a constant translation $v$. 
-The squared Euclidean distance can be expressed as
-%\begin{multline*}
-%	d(\ma p_{xt}, \ma p_{ys})\\ %= [g_x\ast_x g_t \ast_t \left(u(x + \,\cdot\,,t + \,\cdot\,) -  u(y + \,\cdot\,,s + \,\cdot\,)\right)^2](0,0)\\
-%		 = \iint g_x(\rho)g_t(\tau) \left(u(x + \rho,t + \tau) -  u(y + \rho,s + \tau)\right)^2d\tau d\rho
-%\end{multline*}
-\[
-	d(\ma p_{xt}, \ma p_{ys}) = \iint g_x(\rho)g_t(\tau) f(\rho,\tau)d\tau d\rho
-\]
-where
-%$\ast_x, \ast_t$ denote the spatial and temporal convolution operators and 
-$f(\rho,\tau) = \left(u(x + \rho,t + \tau) -  u(y + \rho,s + \tau)\right)^2$,
-and 
-$g_xg_t$ is a separable spatio-temporal kernel which defines the
-shape of the spatio-temporal patch. For example, for a rectangular patch, $g_x$
-and $g_t$ are both box filters of sizes $s_x\times s_x$ and $s_t$ respectively.
-Because of the brightness constancy assumption, we have that $f(\rho,\tau) = f(\rho + v\tau, 0)$.
-%\pcomment{Note: this only holds if the motion at $t$ is equal than the one at $s$.}
-Using this fact, after some manipulations we can rewrite the distance as a distance between 2D patches:
-\[
-	d(\ma p_{xt}, \ma p_{ys}) = \int f(\rho,0)h(\rho) d\rho
-\]
-where \[h(\rho) = \int g_x(\rho - v\tau)g_t(\tau)  d\tau\] is the 
-equivalent spatial kernel. Note that this kernel is the result of integrating
-several shifted versions of the spatial patch kernel $g_x$ along a motion trajectory.
-%
-Thus, when the brightness constancy assumption holds under a constant
-translational motion $v$, the rectangular spatio-temporal patch is equivalent
-to a spatial patch whose support depends on $v$. When $v = 0$, then it reduces 
-to the $s_x\times s_x$ patch, and grows in the direction of the motion at $v$
-increases.
-%
-In these settings, rectangular spatio-temporal patches can be expected to perform as well
-as motion-compensated patches.
-
-For more complex types of motion, using rectangular spatio-temporal patches will result in
-a larger variability in the set of nearest neighbors of a given patch, due to the fact that
-both the spatial texture and the motion pattern may vary. At least in principle, better 
-results should be obtained using motion compensation. However, in practice, the bad quality of
-the estimated motion undermines the final result.
-
-%\begin{align*}
-%	d(\ma p_{xt}, \ma p_{ys}) %= [g_x\ast_x g_t \ast_t \left(u(x + \,\cdot\,,t + \,\cdot\,) -  u(y + \,\cdot\,,s + \,\cdot\,)\right)^2](0,0)\\
-%		 &= \iint g_x(\rho)g_t(\tau) f(\rho,\tau)d\tau d\rho\\
-%		 &= \iint g_x(\rho)g_t(\tau) f(\rho + v(\tau),0) d\tau d\rho\\
-%		 &= \iint g_x(\rho - v(\tau))g_t(\tau) f(\rho,0) d\tau d\rho\\
-%		 &= \int f(\rho,0)\int g_x(\rho - v(\tau))g_t(\tau)  d\tau d\rho\\
-%		 &= \int f(\rho,0)h(\rho) d\rho\\
-%\end{align*}
-
-%after some manipulations the distance 
-%can be written as the convolution with a spatial kernel:
-%\begin{equation*}
-%	d(\ma p_{xt}, \ma p_{ys}) = [h \ast_x \left(u(x + \,\cdot\,,t) -  u(y + \,\cdot\,,s)\right)^2](0),
-%\end{equation*}
-%where 
-%\[
-%	h(\xi) = [g_t \ast g_x(v\,\cdot\,)](\xi/v) 
-%		= \int g_t(\eta)g_x(\xi - v\eta)d\eta.
-%\]
-
-\pcomment{
-\begin{itemize}
-%	\item Justify why 3D patches: Greater distance noise reduction with roughly the same 
-%		degree of self-similarity. One way to see this is that the 3D patches can be 
-%		seen, for a video in which the brightness constancy assumption holds, as a 2D patch
-%		by back-projecting all the slices to the first frame.
-	\item Relation with respect other iterative methods found in the literature
-		(SOS, twicing, diffusion, BM3D, I-SA-BM4D).
-	\item Variation of the results tables for different sequences.
-\end{itemize}}
-
-\subsection{Estimation of the covariance matrix}
-
 \section{Description of the algorithm}
+\label{sec:algorithm}
 
@@
 \subsection{Implementation details}
+\label{sse:implementation}
 
@@
 
-\paragraph{Speed-ups} To accelerate the computation we apply two tricks
-considered in \cite{Lebrun2013ipol}. The first one visits a patch each $n$
-patches (similar to \cite{Dabov2007tip}). The second trick consists on the following.
-After filtering the patches in a group, these patches are not considered again
-as reference patches for a group. This reduces the number of groups of patches
-that need to be processed by a factor of $n$.
-\todo{Also describe that the 4 neighbors are flagged as processed.}
-
-\subsection{Computational complexity}
-\label{sec:complexity}
+\subsection{Computational complexity and speed-ups}
+\label{sse:complexity}
 
 Let us consider the complexity of constructing and filtering a group of
-$n$ similar patches. Due to the speed-ups described in the
-previous section, the actual number of groups of similar patches processed
-might vary between a $1\%$ and a $10\%$ of the total number of pixels in the
-video.
-
+$n$ similar patches.
 Processing each group of similar patches is of asymptotic order $\mathcal
-O(w_x^2 w_t s_x^2 s_t + s_x^4s_t^2r + ns_x^4s_t^2)$.
-The first term comes from the exhaustive search of the $n$ most
-similar patches in the search window. 
-The second term comes from the computation of the truncated eigen-decomposition
-of the covariance matrix, and the last term contemplates computing the
-covariance matrix.
+O(w_x^2 w_t s_x^2 s_t + ns_x^4s_t^2 + s_x^4s_t^2r)$.
+The first term comes from the exhaustive search of the $n$ nearest patches in
+the search window.  The remaining terms correspond respectively to the
+computation of the covariance matrix and its truncated eigen-decomposition.
 
@@
 Let us note that there are methods for computing the $r$ principal directions
-of a set of points that do not require computing the covariance matrix\todo{referencia}. Instead
-these methods efficiently approximate a truncated SVD of the data matrix, and would 
+of a set of points that do not require computing the covariance matrix
+\cite{Halko2011}. Instead these methods efficiently approximate a truncated SVD
+of the data matrix, and would 
 allow to improve the computational complexity to $\mathcal O(w_x^2 w_t s_x^2
@@
 
-\todo{Statistics of group of patches.}
-
-\subsection{Selection of parameters}
-\label{sec:parameters}
-
-For each stage of the algorithm we need to specify 6 parameters: the spatial
-and temporal components of the patch size, $s_x$ and $s_t$, the spatial and
-temporal components of the search region, $w_x$ and $w_t$, the number of similar
-patches $n$ and the rank of the a priori covariance matrix $r$.
-When needed, we will add a subscript indicating the stage, \eg
-$n_{1}$ and $n_{2}$.
-
-\paragraph{Search region} Setting the size of the search region implies a
-trade-off between denoising performance and running time: A larger search
-region takes longer to traverse but yields better results, since more
-similar patches can be found. We fix the search
-region for both stages of the algorithm at 
-\begin{equation}
-w_x = 37 \quad \text{ and } \quad w_t = 5.
-\label{eq:search_region_parameters}
-\end{equation}
-With these values, the search region captures the $5$ frame trajectory of the
-target patch as long as it moves slower than $37/5 = 7.4$
-pixels/frame.
-
-\paragraph{Patch size} Let us consider first the spatial patch
-size $s_x$. This is a key parameter in patch-based methods that
-exploit the image self-similarity \pcomment{CITAS}. The distribution of the 
-patch distances is a non-central Chi-squared distribution \cite{Dabov2007tip}
-\pcomment{CHECK!}
-with variance 
-\[\textnormal{Var}\left\{\frac1{m}\|\ma q_1 - \ma q_2\|^2\right\} = \frac{8\sigma^2}{m}\left(\sigma^2 + \frac{\|\ma p_1 - \ma p_2\|^2}{m}\right),\]
-where $m = s_x^2s_t$ is the total number of pixels in the patch.
-Increasing the spatial patch size $s_x$ reduces the variance of the noise in the patch
-distance. 
-However, for larger
-patches it becomes less likely to find other patches with a similar texture
-pattern. The use spatio-temporal patches helps in solving this trade-off: for
-instance, with a spatio-temporal patch of size $5\times 5\times 4$, we obtain
-the same patch distance noise as with a spatial patch of size $10\times 10
-\times 1$. Moreover, if the motion in the video is approximately uniform, then the 
-amount of similar neighbors of a $5\times 5\times 4$ patch is roughly the same
-as for a $5\times 5\times 1$ patch.
-\pcomment{This discussion would be nice to have in the introduction. Furthermore,
-we could add a short computation on the relation between the distance between
-3D patches and their 2D lids. In this way, we could speak of an equivalent 
-2D patch size.}
-
-We will set the spatial patch size at \[s_x = 5\] for both stages. Larger
-patches (up to $s_x = 9$) lead to an mild improvement of the results (on
-average). This improvement comes at a considerable increase in the
-computation time, since our current implementation is $\mathcal O(s_x^4)$. Thus,
-have found that a good compromise between computation time and quality is given
-by $s_x = 5$.
-
-The impact of the temporal patch size $s_t$ will be discussed later in Section
-\ref{sec:results}, where we show results varying $s_t$ between $s_t = 1$ and $s_t = 4$.
-
-\paragraph{Rank and number of similar patches} These parameters are intimately
-linked. Together they determine the estimation of the local Gaussian models
-and thus control the bias-variance trade-off of the denoiser.
-\pcomment{This is probably inaccurate. There should be other parameters
-contributing to this.}
-
-The number of similar patches $n$ affects the estimation of the covariance
-matrix $C$.
-%Let us consider the trade-offs involved in the estimation of the covariance
-%matrix $C$.
+The computation can be substantially accelerated by reducing the 
+number of groups of patches that are jointly processed.
+Each group of patches is associated to the reference patch from which 
+the nearest neighbors are computed.
+We apply two tricks
+considered in \cite{Lebrun2013ipol} in order to reduce the number of reference patches. 
+The first one consists on visiting only 
+those patches on a coarser spatial grid with vertical and horizontal separation of $s_x/2$
+(similar to \cite{Dabov2007tip}). This reduces the number of reference patches by a
+factor of $s_x^2/4$. The second trick consists on the following.  After
+filtering the patches in a group, these patches are not considered again
+as reference patches. 
+Note that we ensure that each reference patch is filtered at least once. 
+Due to the spacing of the coarse grid, this guarantees that each pixel is
+overlapped by four reference patches on the same frame, so it will receive at
+least four contributions in the aggregation. The actual number of aggregated
+estimates for each pixel is much higher, considering the reference and
+non-reference patches (which can also be filtered) in the neighboring frames.
+
+Due to these speed-ups, the actual number of groups of similar patches processed
+depends on $n$, and varies between a $1\%$ ($n \approx 400$)  and a $10\%$ ($n
+\approx 50$) of the total number of pixels in the sequence. 
+\pcomment{Check this numbers!}
+
+\section{Discussion}
+\label{sec:discussion}
+
+\subsection{Spatio-temporal patches}
+\label{sse:spatio-temporal-patches}
+Patch-based methods filter similar patches to remove noise. When the noise is
+Gaussian, the patch similarity is determined based on the (squared) Euclidean distance 
+between patches. Due to the noise, the Euclidean distance follows a non-central
+$\chi^2$ distribution, with variance
+\[\textnormal{Var}\left\{\frac1{m}\|\ma q_1 - \ma q_2\|^2\right\} = \frac{8\sigma^2}{m}\left(\sigma^2 + \frac1{m}\|\ma p_1 - \ma p_2\|^2\right),\]
+where $\ma q_1, \ma q_2$ are the noisy versions of the patches $\ma p_1, \ma p_2$, 
+and $m$ denotes the number of pixels in the patch. The noise in the patch comparison
+can be reduced by considering larger patches.
+However, increasing the size of the patch also increases the distances between
+patches and reduces the likelihood of finding similar patches.
+%
+The additional temporal dimension in a spatio-temporal patch allows to increase
+the number of pixels in the patch, without increasing its spatial size.
+Due to the high redundancy of the video in the temporal dimension, increasing the 
+temporal size of the patch causes a much lower increase in the patch distances.
+%The high redundancy of the video in the temporal dimension, allows to have 
+%larger patches without affecting much the number of nearest neighbors of the patch.
+%
+
+Let us assume that 
+the brightness of the original video is constant along motion trajectories, so
+that $u(x,t + \tau) = u(\varphi(x,t + \tau; -\tau),t)$, where
+$\varphi(x,t+\tau;\, \cdot\, )$ denotes the motion trajectory passing though
+$(x,t + \tau)$.
+Furthermore, let us assume that the motion in the video is approximately
+translational.
+When the motion is known or can be estimated, then it is natural to consider
+motion compensated spatio-temporal patches. 
+With the assumptions we are considering, all spatial slices of a $s_x\times s_x\times s_t$ motion-compensated patch
+coincide, so the distance between two spatio-temporal patches is proportional to
+the distance of a 2D spatial patch of size $s_x\times s_x$.
+%
+As a consequence, by increasing $s_t$, on can reduce the 
+noise in the patch distance and have the same pattern of self-similarity as a 
+2D patch.
+
+However, motion estimation is challenging, and even more so in the presence of noise.
+%Most motion estimation techniques integrate spatial information either 
+%by matching 2D patches (or blocks, as they are commonly referred to in the
+%motion estimation literature) or by some spatial regularization term in an energy.
+An option that does not require motion is to use rectangular spatio-temporal patches.
+The distance between these can be also expressed as a distance between spatial patches,
+but their equivalent spatial support is larger than $s_x\times s_x$.
+
+%To see this, let us observe that the squared Euclidean distance can be expressed as
+%the convolution with a separable kernel.
+To see this, let us assume that the motion in the video is a constant translation $v$. 
+The squared Euclidean distance can be expressed as
+%\begin{multline*}
+%	d(\ma p_{xt}, \ma p_{ys})\\ %= [g_x\ast_x g_t \ast_t \left(u(x + \,\cdot\,,t + \,\cdot\,) -  u(y + \,\cdot\,,s + \,\cdot\,)\right)^2](0,0)\\
+%		 = \iint g_x(\rho)g_t(\tau) \left(u(x + \rho,t + \tau) -  u(y + \rho,s + \tau)\right)^2d\tau d\rho
+%\end{multline*}
+\[
+	d(\ma p_{xt}, \ma p_{ys}) = \iint g_x(\rho)g_t(\tau) f(\rho,\tau)d\tau d\rho
+\]
+where
+%$\ast_x, \ast_t$ denote the spatial and temporal convolution operators and 
+$f(\rho,\tau) = \left(u(x + \rho,t + \tau) -  u(y + \rho,s + \tau)\right)^2$,
+and 
+$g_xg_t$ is a separable spatio-temporal kernel which defines the
+shape of the spatio-temporal patch. For example, for a rectangular patch, $g_x$
+and $g_t$ are both box filters of sizes $s_x\times s_x$ and $s_t$ respectively.
+Because of the brightness constancy assumption, we have that $f(\rho,\tau) = f(\rho + v\tau, 0)$.
+%\pcomment{Note: this only holds if the motion at $t$ is equal than the one at $s$.}
+Using this fact, after some manipulations we can rewrite the distance as a distance between 2D patches:
+\[
+	d(\ma p_{xt}, \ma p_{ys}) = \int f(\rho,0)h(\rho) d\rho
+\]
+where \[h(\rho) = \int g_x(\rho - v\tau)g_t(\tau)  d\tau\] is the 
+equivalent spatial kernel. Note that this kernel is the result of integrating
+several shifted versions of the spatial patch kernel $g_x$ along a motion trajectory.
+%
+Thus, when the brightness constancy assumption holds under a constant
+translational motion $v$, the rectangular spatio-temporal patch is equivalent
+to a spatial patch whose support depends on $v$. When $v = 0$, then it reduces 
+to the $s_x\times s_x$ patch, and grows in the direction of the motion at $v$
+increases.
+%
+In these settings, rectangular spatio-temporal patches can be expected to perform as well
+as motion-compensated patches.
+
+For more complex types of motion, using rectangular spatio-temporal patches will result in
+a larger variability in the set of nearest neighbors of a given patch, due to the fact that
+both the spatial texture and the motion pattern may vary. At least in principle, better 
+results should be obtained using motion compensation. However, in practice, the bad quality of
+the estimated motion undermines the final result.
+
+%\begin{align*}
+%	d(\ma p_{xt}, \ma p_{ys}) %= [g_x\ast_x g_t \ast_t \left(u(x + \,\cdot\,,t + \,\cdot\,) -  u(y + \,\cdot\,,s + \,\cdot\,)\right)^2](0,0)\\
+%		 &= \iint g_x(\rho)g_t(\tau) f(\rho,\tau)d\tau d\rho\\
+%		 &= \iint g_x(\rho)g_t(\tau) f(\rho + v(\tau),0) d\tau d\rho\\
+%		 &= \iint g_x(\rho - v(\tau))g_t(\tau) f(\rho,0) d\tau d\rho\\
+%		 &= \int f(\rho,0)\int g_x(\rho - v(\tau))g_t(\tau)  d\tau d\rho\\
+%		 &= \int f(\rho,0)h(\rho) d\rho\\
+%\end{align*}
+
+%after some manipulations the distance 
+%can be written as the convolution with a spatial kernel:
+%\begin{equation*}
+%	d(\ma p_{xt}, \ma p_{ys}) = [h \ast_x \left(u(x + \,\cdot\,,t) -  u(y + \,\cdot\,,s)\right)^2](0),
+%\end{equation*}
+%where 
+%\[
+%	h(\xi) = [g_t \ast g_x(v\,\cdot\,)](\xi/v) 
+%		= \int g_t(\eta)g_x(\xi - v\eta)d\eta.
+%\]
+
+% \pcomment{
+% \begin{itemize}
+% %	\item Justify why 3D patches: Greater distance noise reduction with roughly the same 
+% %		degree of self-similarity. One way to see this is that the 3D patches can be 
+% %		seen, for a video in which the brightness constancy assumption holds, as a 2D patch
+% %		by back-projecting all the slices to the first frame.
+% 	\item Relation with respect other iterative methods found in the literature
+% 		(SOS, twicing, diffusion, BM3D, I-SA-BM4D).
+% %	\item Variation of the results tables for different sequences.
+% \end{itemize}}
+
+\subsection{Estimation of the covariance matrix}
+\label{sse:covariance-estimation}
+
+Learning the parameters of the \emph{a priori} distribution for each group of
+noisy patches amounts to estimating a covariance matrix is a high dimensional space 
+and with a limited number of samples. 
+%The latter is controlled by the $n$ parameter, which
+%should not be too high in order for the Gaussian prior to be valid.
+%
 The empirical covariance matrix $\widehat C$ converges to the true covariance matrix
 $C$ as the number of samples from the underlying Gaussian distribution grows to infinity.
-In our case, the number of samples we can ``draw'' from the Gaussian is limited:
+But in our case, the number of samples we can ``draw'' from the Gaussian is limited:
 %The Gaussian is only an approximate density model for the set of
@@
 that are not as similar to the reference patch and the Gaussian model becomes less valid.
-%
+
 Thus there is a trade-off between accuracy of Gaussian model and precision of the
-covariance matrix.
-We find a compromise to this trade-off empirically, by trying different values of this parameter on a 
-few training sequences and use the one yielding the best PSNR.
+covariance matrix. We will find a compromise to this trade-off empirically  in
+\S \ref{sec:parameters}. But it still intersting to review the literature 
+on the sample covariance matrix as an estimator of the population covariance.
 
@@
 
+\pcomment{Results of Bunea are still missing!}
+\pcomment{More detailed explanation of the results?}
+
+\section{Parameter selection}
+\label{sec:parameters}
+
+For each stage of the algorithm we need to specify 6 parameters: the spatial
+and temporal components of the patch size, $s_x$ and $s_t$, the spatial and
+temporal components of the search region, $w_x$ and $w_t$, the number of similar
+patches $n$ and the rank of the a priori covariance matrix $r$.
+When needed, we will add a subscript indicating the stage, \eg
+$n_{1}$ and $n_{2}$.
+
+\subsection{Search region and patch size}
+
+Setting the size of the search region implies a
+trade-off between denoising performance and running time: A larger search
+region takes longer to traverse but yields better results, since more
+similar patches can be found. We fix the search
+region for both stages of the algorithm at 
+\begin{equation}
+w_x = 37 \quad \text{ and } \quad w_t = 5.
+\label{eq:search_region_parameters}
+\end{equation}
+With these values, the search region captures the $5$ frame trajectory of the
+target patch as long as it moves slower than $37/5 = 7.4$
+pixels/frame.
+
+Let us now consider the spatial patch
+size $s_x$, which is a key parameter in patch-based methods \cite{Buades2006,Kervrann2006,Boulanger2007}.
+%The distribution of the 
+%patch distances is a non-central Chi-squared distribution \cite{Dabov2007tip}
+%\pcomment{CHECK!}
+%with variance 
+%\[\textnormal{Var}\left\{\frac1{m}\|\ma q_1 - \ma q_2\|^2\right\} = \frac{8\sigma^2}{m}\left(\sigma^2 + \frac{\|\ma p_1 - \ma p_2\|^2}{m}\right),\]
+%where $m = s_x^2s_t$ is the total number of pixels in the patch.
+Increasing the spatial patch size $s_x$ reduces the variance of the noise in the patch
+distance. 
+However, for larger
+patches it becomes less likely to find other patches with a similar texture
+pattern. The use spatio-temporal patches helps in solving this trade-off: for
+instance, with a spatio-temporal patch of size $5\times 5\times 4$, we obtain
+the same patch distance noise as with a spatial patch of size $10\times 10
+\times 1$. Moreover, as discussed in \S \ref{sse:spatio-temporal-patches}, for
+an approximately uniform motion, the 
+amount of similar neighbors of a $5\times 5\times 4$ patch is roughly the same
+as for a $5\times 5\times 1$ patch.
+
+We will set the spatial patch size at \[s_x = 5\] for both stages. Larger
+patches (up to $s_x = 9$) lead to an mild improvement of the results (on
+average). This improvement comes at a considerable increase in the
+computation time, since our current implementation is $\mathcal O(s_x^4)$. Thus,
+have found that a good compromise between computation time and quality is given
+by $s_x = 5$.
+
+The impact of the temporal patch size $s_t$ will be discussed later in Section
+\ref{sec:results}, where we show results varying $s_t$ between $s_t = 1$ and $s_t = 4$.
+
+\subsection{Rank and number of similar patches}
+
+The number of similar patches $n$ and the rank $r$ affect the estimation of the covariance
+matrix $C$, controlling the trade-off between the accuracy of Gaussian model
+and precision of the covariance matrix,
+which in turn has a direct effect on the denoising strength of the algorithm.
+% This have great impact on the bias-variance trade-off of the denoiser.
+%In practice, these parameters determine the denoising strength of the
+%algorithm. For example, using a large
+We find a compromise to this trade-off empirically, by trying different values of this parameter on a 
+few training sequences and use the one yielding the best PSNR.
+
+%The number of similar patches $n$ and the rank $r$ affect the estimation of the covariance
+%matrix $C$, controlling the trade-off between the accuracy of Gaussian model
+%and precision of the covariance matrix.
+
 %\prm{Intuitively speaking, by setting a lower rank we are estimating a covariance
@@
 We can interpret the results in the light of the theoretical results
-described above.
+described in \S \ref{sse:covariance-estimation}.
 For all noise levels, best results are obtained when using a larger number of
@@
 In this section we present results obtained with the proposed
-method on some classic test sequences with Gaussian noise added.
+method on some classical test sequences with Gaussian noise added.
 We consider separatedly the cases of grayscale and color videos.
@@
 which we call I-SA-BM4D, since it can be regarded as an iterative version of BM4D \cite{Maggioni2013}
-using shape adaptive 3D patches, as in \todo{REF}.  
+using shape adaptive 3D patches, as in \cite{Ercole2005}.  
 For V-BM4D, we show results corresponding to two
@@
 
-Each sequence was contaminated with white Gaussian noise of $\sigma =
+Each sequence was contaminated with AGWN of $\sigma =
 10,20,30,40$. Table \ref{tab:psnr-classic-gray} shows the
@@
 
-\pcomment{TODO: qualitative comparison.}
+For a qualitative comparison, Figure \ref{fig:results_mobile_mono}
+shows two details of the results obtained by our method and V-BM4D for the
+\emph{mobile} sequence, for noise of $\sigma = 10, 20, 40$. It can be observed
+that the proposed method preserves more details. It also exhibits a higher
+temporal consistency, as will be shown in \S \ref{sse:temporal-consistency}.
 
@@
 
-\pcomment{This paragraph has to change with the new qualitative results.}
-For a qualitative analysis we show in Figure \ref{fig:results} results obtained
-with nonlocal Bayes (setting $w_t = 5$) and V-BM4D-np. Interestingly, for $\sigma = 20$
-and $40$, V-BM4D-np is able to better recover the wallpaper texture in tennis,
-but does worse than VNLB for the foliage texture of the trees in bus. 
-%One
-%plausible reason for this is that the spatial bi-orthogonal wavelets and
-%DCT transforms used by BM4D are very well suited to the structured pattern of the
-%wallpaper.
-For high levels of noise, the wallpaper texture is masked by the noise. 
-It is possible that when comparing 2D patches the noise dominates in the
-comparison. Using spatio-temporal volumes reduces the distance noise,
-allowing to find similar patches with the same regular texture pattern.
-
-\begin{figure*}[htpb!]
-	\centering
-
-	\includegraphics[trim=0cm 7.4cm 0cm 0.5cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/orig-nisy_004.png}
-
+Figure \ref{fig:results-tennis} 
+shows two details of the results obtained by our method and V-BM4D for the
+\emph{tennis} sequence, for noise of $\sigma = 10, 20, 40$. As for grayscale
+sequences, it can be noticed that some details, such as the wallpaper texture,
+are better preserved by the proposed method. Some artifacts appear around 
+moving objects, for example the hand in the close-up of the racket,
+or the arm holding the racket in the second crop.
+%
+Patches at the boundary between an object moving over a textured background 
+do not have exact matches. In this case, it is likely that patches tracking 
+the moving object are found similar, even if the background texture captured by 
+the patches do not match, creating artifacts on the recovered texture.
+
+%\begin{figure*}[htpb!]
+%	\centering
+%
+%	\includegraphics[trim=0cm 7.4cm 0cm 0.5cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/orig-nisy_004.png}
+%
+%%	\vspace{.1cm}
+%%	\includegraphics[trim=0cm 6.9cm 0cm 0cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/vnlb_pt4-orig_004.png}
+%%
 %	\vspace{.1cm}
-%	\includegraphics[trim=0cm 6.9cm 0cm 0cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/vnlb_pt4-orig_004.png}
-%
-	\vspace{.1cm}
-	\includegraphics[trim=0cm 7.4cm 0cm 0.5cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/vnlb_pt4-vnlb_pt1_004.png}
-
-	\vspace{.1cm}
-	\includegraphics[trim=0cm 7.4cm 0cm 0.5cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/vnlb_pt4-bm4d_004.png}
-	\caption{Comparison of the results. To ease comparison and save space, we
-	juxtapose two results on each image in a checkerboard pattern. From top to
-	bottom: original and contaminated sequences, with $\sigma = 40$; result of
-	VNLB using $s_t = 1$ and $s_t = 4$; result of V-BM4D-mp and result of VNLB
-	with $s_t = 4$.}
-	\label{fig:results-army}
-\end{figure*}
+%	\includegraphics[trim=0cm 7.4cm 0cm 0.5cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/vnlb_pt4-vnlb_pt1_004.png}
+%
+%	\vspace{.1cm}
+%	\includegraphics[trim=0cm 7.4cm 0cm 0.5cm, clip=true, width=0.8\textwidth]{figs_cambridge/combined_videos/Army_s40/vnlb_pt4-bm4d_004.png}
+%	\caption{Comparison of the results. To ease comparison and save space, we
+%	juxtapose two results on each image in a checkerboard pattern. From top to
+%	bottom: original and contaminated sequences, with $\sigma = 40$; result of
+%	VNLB using $s_t = 1$ and $s_t = 4$; result of V-BM4D-mp and result of VNLB
+%	with $s_t = 4$.}
+%	\label{fig:results-army}
+%\end{figure*}
 
@@
 \subsection{Evaluating temporal consistency}
+\label{sse:temporal-consistency}
 
@@
 on the sequence. The TCE gap with V-BM4D-mp increases with the noise level. 
-\todo{Comment on these results, but after the results have been recomputed with the right parameters!}
+\pcomment{TODO: Comment on these results, but after the results have been
+recomputed with the right parameters!}
+
+Another way of assessing the temporal consistency of the result is to visualize a 
+slice of the video volume at a fixed row (or column). Figure \ref{fig:time-diff} shows
+a horizontal slice of the \emph{mobile} sequence. Each row in the images shown corresponds
+to a different frame. The gray tube corresponds to a ball which is hit by a
+black train entering from the left. For high levels of noise, the result of V-BM4D
+shows a high frequence jittering in the temporal (vertical) dimension, a consequence
+of the flickering on the video sequence. On the other hand, the result of the
+video non-local Bayes method, shows a much slower variation in time.
 
@@
 
-We presented a Bayesian video denoising algorithm assuming a Gaussian model for similar patches. 
-We show preliminary results and compare it with two methods from the
-state-of-the-art, V-BM3D and V-BM4D.
-The resulting method does not require motion estimation.%, and as such it shows
-%lower temporal coherency than V-BM4D.
-In terms of PSNR
-the results obtained show state-of-the-art performance for low levels of noise.
-For higher levels of noise the performance is comparable to V-BM3D and improves
-over the default version of V-BM4D.
+We presented a Bayesian video denoising algorithm assuming a Gaussian prior
+model for similar spatio-temporal patches. 
+The proposed method does not require motion estimation, yet it provides 
+state-of-the-art results, both in terms of PSNR and qualitatively. 
+A key element of the proposed method is the estimation of the a priori
+covariance matrices from sets of noisy spatio-temporal patches. Since
+the dimensionality of the patches is high, and the number of available 
+similar patches is limited, we additionaly assume that the prior covariance
+is of low rank. In practice this amount to keeping only the principal 
+eigenvectors of the sample covariance matrix. This desicion is analized
+in the light of theoretical results on the estimation of covariance matrices 
+and with a thorough empirical evaluation. We found that using only the 
+main eigenvectors in the second stage of the algorithm improves both
+the running time and the quality of the results.
+
+Spetial attention is devoted to the evaluation of the temporal consistency of
+the result. In particular, we propose a way to quantify the temporal
+consistency error (TCE), by measuring the temporal inconsistencies in the
+residue using a ground truth optical flow. Our method shows better performance
+also with respect proposed TCE, evaluated in synthetic videos from MPI's Sintel
+database.
+%<>% We show preliminary results and compare it with two methods from the
+%<>% state-of-the-art, V-BM3D and V-BM4D.
+%<>% The resulting method does not require motion estimation.%, and as such it shows
+%<>% %lower temporal coherency than V-BM4D.
+%<>% In terms of PSNR
+%<>% the results obtained show state-of-the-art performance for low levels of noise.
+%<>% For higher levels of noise the performance is comparable to V-BM3D and improves
+%<>% over the default version of V-BM4D.
+
+The method is still computationally expensive, and current research focus
+on speeding up the search and the Bayesian estimation.
 
@@
 \bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,image_denoising,video_denoising}
+\bibliography{IEEEabrv,image_denoising,video_denoising,covariance_estimation}
 

### 2015-10-16 tools/patch_group.m

@@ -112,22 +112,6 @@ while (goon)
 		patches.coords = load('/tmp/patches.coords.out') + 1;
 		patches.distas = load('/tmp/patches.distas.out');
 
-		indr = sub2ind(size(nisy),patches.coords(:,2), ...
-		                          patches.coords(:,1), ...
-		                          ones(size(patches.coords,1),1), ...
-		                          patches.coords(:,3));
-
-		indg = sub2ind(size(nisy),patches.coords(:,2), ...
-		                          patches.coords(:,1), ...
-		                          2*ones(size(patches.coords,1),1), ...
-		                          patches.coords(:,3));
-
-		indb = sub2ind(size(nisy),patches.coords(:,2), ...
-		                          patches.coords(:,1), ...
-		                          3*ones(size(patches.coords,1),1), ...
-		                          patches.coords(:,3));
-		nisy(indr) = 255;
-
 		patches.nisy = zeros(prms.px, prms.px, 3, prms.pt, length(patches.distas));
 		for i = 1:length(patches.distas),
 			patches.nisy(:,:,:,:,i) = nisy0(patches.coords(i,2):patches.coords(i,2)+prms.px-1,...
@@ -162,34 +146,50 @@ while (goon)
 
 		% display also eigenvectors and eigenvalues
 		mU = min(255,max(0,[m, 255*(4*U(:,1:np_viz-1) + 0.5)]));
-		mU = build_patch_image(reshape(mU,[prms.px prms.px 3 prms.pt 1+np_viz]));
+		mU = build_patch_image(reshape(mU,[prms.px prms.px 3 prms.pt np_viz]));
 		figure(3)
 		imagesc(mU/255), axis equal, axis off
 
 
 
 
-		% show search region for all frames
-		a = 0.5;
-		orig(indr(1: 5))   = a*orig(indr(1: 5))   + (1-a)*255;
-		orig(indr(6:45))   = a*orig(indr(6:45))   + (1-a)*  0;
-		orig(indr(46:end)) = a*orig(indr(46:end)) + (1-a)*  0;
-		orig(indg(1: 5))   = a*orig(indg(1: 5))   + (1-a)*  0;
-		orig(indg(6:45))   = a*orig(indg(6:45))   + (1-a)*255;
-		orig(indg(46:end)) = a*orig(indg(46:end)) + (1-a)*  0;
-		orig(indb(1: 5))   = a*orig(indb(1: 5))   + (1-a)*  0;
[…]

### 2015-10-19 doc/201507_tip/paper.tex
[doc] Draft 1 of paper, sent to JMM for feedback.

@@
 The rank also plays a role in the estimation of the covariance matrix.
-As explained in \S \ref{sec:complexity}, alleviating the computational cost is
+As explained in \S \ref{sse:complexity}, alleviating the computational cost is
 one of the reasons for using a low rank approximation of the empirical
@@
 $n_{1}$ and $n_{2}$.
+We will consider different parameter settings for color and grayscale videos.
 
@@
 
-Setting the size of the search region implies a
-trade-off between denoising performance and running time: A larger search
-region takes longer to traverse but yields better results, since more
-similar patches can be found. We fix the search
-region for both stages of the algorithm at 
-\begin{equation}
-w_x = 37 \quad \text{ and } \quad w_t = 5.
-\label{eq:search_region_parameters}
-\end{equation}
+Setting the size of the search region implies a trade-off between denoising
+performance and running time: A larger search region takes longer to traverse
+but yields better results, since more similar patches can be found. We use same 
+search region in both stages. The
+temporal search window is fixed at $w_t = 5$. The spatial search region is set at
+$w_x = 37$ for color videos and $w_x = 45$ for grayscale videos.
 With these values, the search region captures the $5$ frame trajectory of the
-target patch as long as it moves slower than $37/5 = 7.4$
-pixels/frame.
+target patch as long as it moves slower than $37/5 = 7.4$ pixels/frame (for
+color videos).
 
@@
 
-We will set the spatial patch size at \[s_x = 5\] for both stages. Larger
-patches (up to $s_x = 9$) lead to an mild improvement of the results (on
-average). This improvement comes at a considerable increase in the
-computation time, since our current implementation is $\mathcal O(s_x^4)$. Thus,
-have found that a good compromise between computation time and quality is given
-by $s_x = 5$.
+For color videos, we will set the spatial patch size at $s_x = 5$ for both
+stages, whereas for grayscale videos we use $s_x = 7$. Larger patches (up to $s_x = 9$) lead to an mild improvement of the
+results (on average). This improvement comes at a considerable increase in the
+computation time, since our current implementation is $\mathcal O(s_x^4)$.
+Thus, have found that a good compromise between computation time and quality is
+given by $s_x = 5$.
 
@@
 %
-Instead, we fix the first stage parameters at
+Instead, we fix the first stage parameters, both for color and grayscale videos
+at
 \[r_1 = s_{x,1}^2s_{t,1}\quad\quad n_{1} = 400,\]
@@
 \[r_2(\sigma) = 35 - \frac12(\sigma - 10)\quad\quad n_{2} = 100.\]
+The same values are used for color and grayscale videos.
 Note that a higher value for $n_{2}$ would give slightly worse results,
 at a lower computational cost.
+
+\begin{table}
+	\centering
+	\begin{tabular}{l | c c | c c }
+		& \multicolumn{2}{c|}{color} 
+		& \multicolumn{2}{c}{grayscale}\\
+		Stage                            & 1st    & 2nd   & 1st   & 2nd   \\\hline\hline
+		$s_x$        &  5 & 5 & 7 & 7 \\
+		$s_t$        &  1--4  & 1--4  & 1--4  & 1--4  \\
+		$w_x$        &  37    & 37    & 45    & 45    \\
+		$w_x$        &   5    & 5     & 5     & 5    \\
+		$n$          & 400    & 100   & 400   & 100  \\
+		$r$          & full   & $35 - \frac12(\sigma - 10)$    & full  & $35 - \frac12(\sigma - 10)$   \\
+%		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
+%		Beta                        & 1    & 1.2  & 1    & 1.2  & 1    & 1.2 \\\hline
+	\end{tabular}
+	\caption{Selected parameters.}
+	\label{tab:parameters}
+\end{table}
 
@@
 
-		\vspace{1cm}
-		\pcomment{TODO: Figures for grayscale sequences}
-		\vspace{1cm}
-
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s10_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s20_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s30_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s40_average_mono.eps}\\
 	\end{center}
@@
 
-		\vspace{1cm}
-		\pcomment{TODO: Figures for grayscale sequences}
-		\vspace{1cm}
-
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s10_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s20_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s30_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s40_average_mono.eps}\\
 	\end{center}
@@
 
-		\vspace{1cm}
-		\pcomment{TODO: Figures for grayscale sequences}
-		\vspace{1cm}
-
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s10_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s20_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s30_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s40_average_mono.eps}\\
 	\end{center}
@@
 
-		\vspace{1cm}
-		\pcomment{TODO: Figures for grayscale sequences}
-		\vspace{1cm}
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s10_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s20_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s30_average_mono.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s40_average_mono.eps}\\
 
@@
 	\begin{center}
-		{%\small
+		{\small
 		\renewcommand{\tabcolsep}{1.6mm}
@@
 % for i in $(cat bus_s40_pt*/measures | grep PSNR_final | sed "s/^-PSNR_final\ =\ "//); do  echo "scale=2;(((10^2)*$i)+0.5)/(10^2)" | bc; done
-	\caption{PSNRs obtained for the four classic color test sequences used in
-	\cite{Maggioni2012}. See text for details.}
+	\caption{PSNRs obtained for the classic color test sequences. See text for
+		details. \pcomment{NOTE: the values in the table need to be updated!!}}
 	\label{tab:psnr-classic-color}
@@
 	\end{center}
-	\caption{Quantitative denoising results for some classic grayscale test sequences. See text for details.}
+	\caption{Quantitative denoising results for some classic grayscale test sequences. See text for details. \pcomment{NOTE: the values in the table need to be updated!!}}
 	\label{tab:psnr-classic-gray}
@@
 We consider separatedly the cases of grayscale and color videos.
+All results were computed with the parameters shown in Table \ref{tab:parameters}.
 
@@
 	\caption{PSNRs and TCEs obtained for the four CGI sequences from MPI
-	Sintel's database. See text for details.}
+	Sintel's database. See text for details.
+	\pcomment{NOTE: the values in the table need to be updated!!}}
 	\label{tab:sintel}

### 2015-10-19 tools/psnr_vs_rank_np_images.m

@@ -1,8 +1,10 @@
 root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/';
 
-%stage2_folder = [root_folder 'table_2r_vs_2np_derf/'];
-stage2_folder = [root_folder 'tip_table_2r_vs_2np_derf/'];
-stage1_folder = [root_folder 'tip_table_1r_vs_1np_derf/'];
+%stage2_folder = [root_folder 'tip_table_2r_vs_2np_derf/'];
+%stage1_folder = [root_folder 'tip_table_1r_vs_1np_derf/'];
+
+stage2_folder = [root_folder 'tip_table_2r_vs_2np_mono/'];
+stage1_folder = [root_folder 'tip_table_1r_vs_1np_mono/'];
 
 % stage 2 ---------------------------------------------------
 
@@ -90,116 +92,117 @@ stage1_folder = [root_folder 'tip_table_1r_vs_1np_derf/'];
 %-:-% 
 %-:-% end
 
-%<+>% % USE THIS CODE TO REMOVE MISSING VALUES IN THE TABLES
-%<+>% % THIS IS USEFULL FOR DISPLAYING RESULTS WITH PLOT
-%<+>% ranks = [5,10,15,20,25,30,35,40,45,50,60,70,90,110];
-%<+>% nsims = [50:50:350];
-%<+>% seqs = {'bus', 'football', 'foreman', 'tennis'};
-%<+>% 
-%<+>% mff = zeros(length(nsims),length(ranks),length(seqs));
-%<+>% idx_r = [11,13,15,16,17,19,20,21];
-%<+>% 
-%<+>% fig_i = 1;
-%<+>% for s = 10:10:40,
-%<+>% 
-%<+>% 	ff = zeros(length(nsims),length(ranks),length(seqs));
-%<+>% 
-%<+>% 	for i = 1:length(seqs),
-%<+>% 		tmp = load([stage2_folder 'table_fpsnr_' seqs{i} '_s' num2str(s)]);
-%<+>% 		tmp(tmp == 0) = NaN;
-%<+>% 
-%<+>% 		% remove indices that have not been computed
-%<+>% 		tmp(:,idx_r) = [];
-%<+>% 		ff(:,:,i) = tmp;
-%<+>% 	end
-%<+>% 
-%<+>% 	% ------------------
[…]

### 2015-11-12 doc/201511_notes/notes.tex
[doc] Notes on empirical Wiener filter with aggregation

\documentclass[a4paper,10pt]{article}

\usepackage[english,activeacute]{babel}
\usepackage[english]{layout}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{subfig}
\usepackage{colonequals}
\usepackage[latin1]{inputenc}
\usepackage{url}
\usepackage{epsfig}
\usepackage{dsfont}

\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{setspace}
\usepackage{afterpage}
%\usepackage{showkeys}
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
% \usepackage{latexsym}

%\usepackage[left=1.2in,right=1.2in]{geometry}

% \graphicspath{{../iccv09/}}

\newcommand{\ma}[1]{\boldsymbol{#1}}
\newcommand{\tras}[1]{#1^{\mathrm{T}}}
\newcommand{\herm}[1]{#1^{\mathrm{H}}}
\newcommand{\con}[1]{#1^{\mathrm{*}}}
\newcommand{\E}{\mathds{E}}
\newcommand{\tech}[1]{\overline{#1}}
\newcommand{\nspace}{\!\!\!\!}
\newcommand{\nmbr}[1]{\oldstylenums{#1}}

\newcommand{\eg}{\emph{e.g}. } \newcommand{\Eg}{\emph{E.g}. }
\newcommand{\ie}{\emph{i.e}. } \newcommand{\Ie}{\emph{I.e}. }
\newcommand{\cf}{\emph{c.f}. } \newcommand{\Cf}{\emph{C.f}. }
\newcommand{\etc}{\emph{etc}. } \newcommand{\vs}{\emph{vs}. }
\newcommand{\wrt}{w.r.t\onedot } \newcommand{\dof}{d.o.f. }
\newcommand{\etal}{\emph{et al}. }

\newcommand{\R}{\mathds{R}}
\newcommand{\sign}{\mathrm{sign}}
\newcommand{\eps}{\varepsilon}
\newcommand{\To}{\longrightarrow}
% \newcommand{\II}{1{\hskip -2.5 pt}\hbox{I}}

% c++ code
\usepackage{listings}
\usepackage{xcolor}
\usepackage{textcomp}
\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
	backgroundcolor=\color{lbcolor},
	tabsize=4,    
%  rulecolor=,
	language=Matlab,
	basicstyle=\scriptsize\ttfamily,
	upquote=true,
	aboveskip={1.5\baselineskip},
	columns=fixed,
	showstringspaces=false,
	extendedchars=false,
	breaklines=true,
	prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
	frame=single,
	numbers=left,
	showtabs=false,
	showspaces=false,
	showstringspaces=false,
	identifierstyle=\ttfamily,
	keywordstyle=\color[rgb]{0,0,1}\ttfamily,
	commentstyle=\color[rgb]{0,0.5,0}\ttfamily,
	stringstyle=\color[rgb]{0.627,0.126,0.941}\ttfamily,
	numberstyle=\color[rgb]{0.5, 0.5, 0.5}\ttfamily,
%  \lstdefinestyle{C++}{language=C++,style=numbers}’.
}
%\lstset{
%	backgroundcolor=\color{lbcolor},
%	tabsize=4,
%	language=C++,
%	captionpos=b,
%	tabsize=3,
%	frame=lines,
%	numbers=left,
%	numberstyle=\tiny,
%	numbersep=5pt,
%	breaklines=true,
%	showstringspaces=false,
%	basicstyle=\footnotesize,
%	identifierstyle=\color{magenta},
%	keywordstyle=\color[rgb]{0,0,1},
%	commentstyle=\color{green},
%	stringstyle=\color{red}
%}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\nota}[1]{\textcolor{blue}{\textbf{#1}}}
\newcommand{\suggest}[1]{\textcolor{yellow}{#1}}
\newcommand{\add}[1]{\textcolor{green}{#1}}
\newcommand{\remove}[1]{\textcolor{red}{#1}}
\newcommand{\dosdv}[1] {#1}
\newcommand{\uncite}[1] {}
% \newcommand{\tachar}[1]{
% \setbox4=\hbox{\ } \setbox3=\hbox{#1} \hbox{#1} \kern -\wd3 \kern
% -\wd4 \raise 0.3\ht3 \hbox{ \vrule width \wd3 height 0.5pt} }

% \theoremstyle{plain}\newtheorem{theorem}{Theorem}[chapter]
% \theoremstyle{plain}\newtheorem{proposition}{Proposition}[chapter]
% \theoremstyle{plain}\newtheorem{lemma}{Lemma}[chapter]
% \theoremstyle{definition}\newtheorem{definition}{Definition}[chapter]

\title{Aggregation of empirical Wiener estimates}
\author{}
\date{}

\begin{document}

\maketitle

\section{Setting}

\paragraph{Signal.}We assume a very simple setting. Suppose we have $N$ signals in $\mathbb R^d$,
assumed to follow a Gaussian distribution
\[x_i\sim \mathcal N(0,\Lambda), \quad i\in1,\dots,N.\]
where $\Lambda =
\text{diag}(\lambda_1,\lambda_2,\dots,\lambda_d)$.

\paragraph{Observations.}We have $M$ observations of these signals, contaminated
by additive white Gaussian noise:
\[y_{ij} = x_i + n_{ij}, \quad i = 1,\dots,N, j = 1,\dots,M,\]
where $n_{ij}\sim \mathcal N(0,\sigma^2I)$.
These observations are not available simultaneously, but sequentially in $M$ batches.

\paragraph{Wiener filter.}For each of the $M$ groups of observations, we compute an empirical Wiener
estimate of the signals $x_i$:
\[\hat x_{ij} = \widehat W_jy_{ij} = \widehat W_j x_i + \widehat W_j n_{ij}.\]
The coefficients of the Wiener filter are estimated from the group of $N$ observations
available at time $j$:
\[\hat w_j(k) = \frac{\hat \lambda_k}{\hat \lambda_k + \sigma^2} =
\frac{\frac1N \sum_{i = 1}^N y_{ij}(k)^2 -\sigma^2}{\frac1N \sum_{i = 1}^N y_{ij}(k)^2} = 
1 - \sigma^2\left(\frac1N\sum_{i = 1}^N y_{ij}(k)^2\right)^{-1}.\]
Alternatively, we also defined the thresholded empirical Wiener filter
as 
\[\hat w_j^+(k) = \hat w_j(k) \cdot \frac12 (\text{sign}(\hat w_j(k)) + 1).\]

\paragraph{Aggregation.}The final estimate is done by aggregating the $M$
Wiener estimates:
\[\hat x_i = \frac1M \sum_{j = 1}^M \hat x_{ij} = x_i \frac1M \sum_{j = 1}^M
\widehat W_j + \frac1M \sum_{j = 1}^M \widehat W_jn_{ij}\]

\paragraph{Aim.}The aim is to evaluate the performance of $\hat w_j$ and $\hat
w_j^+$. For that sake, we will compute the PDF of $\hat w_j(k)$, and the PDF of the
aggregated weights. If $M$ is large, we can approximate the aggregation by an 
expectation:
\[\hat x_i(k)\to \mathbb E\{ \hat w_j(k) \} x_i(k) + \mathbb E\{w_j(k) n_{ij}(k)\}\]
where the expectation is taken over variables $n_{1j}(k), \dots, n_{Nj}(k)$,
for each $i, k$. Similarly for the thresholded coefficients.

\section{PDF of filter coefficients}

Let us for now focus on the non-thresholded filter coefficients 
\[\hat w_j(k) =  
1 - \sigma^2\left(\frac1N\sum_{i = 1}^N y_{ij}(k)^2\right)^{-1}.\]
The variance of $y_{ij}(k)$ follows a non-central chi squared distribution,
and therefore $\hat w_j(k)$ corresponds to a random variable which is the
reciprocal of a non-central chi squared distribution.

\subsection{The variance along dimension $k$}

Let us include the following notation for the variance of the observations
along dimension $k$
\[v_j(k) = \frac1N\sum_{i = 1}^Ny_{ij}(k)^2.\]

\paragraph{Scaled non-central $\chi^2$.}Let us consider
$\nu = a\sum_{i = 1}^N (\mu_i + \xi_i)^2$, where $a, N$ and $\mu_i$, $i =
1,\dots,N$ are known parameters and $\xi\sim\mathcal N(0,1)$. 
Then, $\nu$ follows a scaled non-central chi-squared distribution,
$\nu\sim\chi^2_N(\mu,a)$, where
\[\mu = \sum_{i = 1}^N \mu_i^2\]
is called the non-centrality parameter.
The PDF has the following expression:
\[f(\nu; N, \mu, a) = \frac1{2|a|} e^{-(\nu/a+\mu)/2}\left(\frac{\nu}{a\mu}\right)^{N/4 - 1/2} I_{N/2-1}(\sqrt{\mu\nu/a}),\]
where $I_{N/2-1}$ is a modified Bessel function of the first kind,
\[I_r(z) = (z/2)^r\sum_{i = 0}^\infty\frac{(z^2/4)^i}{i!\Gamma(r + i + 1)},\]
where the gamma function is a real extension of the factorial 
given by 
\[\Gamma(t) = \int_0^\infty x^{t-1}e^{-x}dx.\]
It has the property that $\Gamma(i) = (i-1)!$ for $j\in\mathbb N_+$.
The mean and variance of this distribution are given by
\[\mathbb E\{\nu\} = a(N + \mu)\quad\quad\mathbb V\{\nu\} = 2a^2(N + 2\mu).\]

\paragraph{The distribution of $v_j(k)$.}By scaling the terms in the summation
to normalize the variance, we have that 
\[v_j(k)\sim \chi^2_N\left(\frac1{\sigma^2}\sum_{i = 1}^Nx_i^2(k), \frac{\sigma^2}N\right) = \chi^2_N\left(N\hat{\text{snr}}(k), \frac{\sigma^2}N\right),\]
where we have defined 
\[\hat{\text{snr}}(k) = \frac1{N\sigma^2}\sum_{i = 1}^Nx_i^2(k).\]
Note that this ``sample signal-to-noise ratio'' cannot be computed in practice, since
it requires the knowledge of the $x_i$. It can be seen as an approximation of the
true signal to noise ratio $\lambda_k/\sigma^2$, specially for $N$ large.

The mean and variance of the sample variance are then
\begin{align*}
\mathbb E\{v_j(k)\} &= \sigma^2 + \frac1N\sum_{i = 1}^N x_i^2(k) =  \sigma^2(1 + \hat{\text{snr}}(k)),\\
\mathbb V\{v_j(k)\} &= \frac{2\sigma^2}N\left(\sigma^2 + \frac2N \sum_{i =1}^N x_i^2(k)\right) = \frac{2\sigma^4}N\left(1 + 2\hat{\text{snr}}(k)\right).
\end{align*}

\paragraph{Gaussian approximation.}In the limit when $N$ or $\mu$ tend to infinity, this distribution converges to
a Gaussian with the same mean and variance. The Gaussian approximation is valid in
our setting, since both $N$ and $\mu$ are large.

\subsection{The reciprocal of a scaled non-central chi squared}

If $\xi$ is a random variable with PDF $f$ supported in the positive axis, then
the PDF of $\nu = 1/\xi$ is $g$ given by
\[g(\nu) = 1/{\nu^2}f(1/\nu).\]
Furthermore, if $\zeta = 1 - b\nu = 1 - b/\xi$ with $b>0$, then its PDF $h$ is
given by: 
\[h(\zeta) = \frac1b g((1 - \zeta)/b) = \frac b{(1-\zeta)^2}f(b/(1-\zeta) ).\]

We have that $\hat w_j(k) = 1 - \sigma^2/v_j(k)$, thus we can obtain the PDF of the 
filter coefficient using the previous relationship for $f$ the PDF of scaled non-central
chi squared and $b = \sigma^2$. The resulting PDF has the following expression:
\begin{multline*}
	h(\omega) = \frac{N}{2(1 - \omega)^2}
\exp\left(-\frac12\left[\frac{N}{(1-\omega)} + \frac1{\sigma^2}\sum_{i=1}^Nx_i^2(k)\right]\right)\\
\left(\frac{N\sigma^2}{(1-\omega)\sum_{i = 1}^N x_i^2(k)}\right)^{N/4-1/2}
I_{N/2-1}\left(\sqrt{\frac{N}{\sigma^2(1 - \omega)}\sum_{i =
1}^Nx_i^2(k)}\right)
\end{multline*}
Or equivalently:
\begin{multline*}
	h(\omega) = \frac{N}{2(1 - \omega)^2}
	\exp\left(-\frac{N}{2}\left[\frac{1}{(1-\omega)} + \hat{\text{snr}}(k)\right]\right)\\
	\left(\frac{1}{(1-\omega)\hat{\text{snr}}(k)}\right)^{N/4-1/2}
	I_{N/2-1}\left(\sqrt{\frac{N^2}{(1 - \omega)}\hat{\text{snr}}(k)}\right)
\end{multline*}

\noindent\textcolor{red}{Is there a closed form expression for the mean and variance of this distribution?}

The weights are obtained by applying a concave function $\varphi(v) = 1 -
\sigma^2/v$, to the sample variance $v$. From Jensen's inequality, we know that
\[\mathbb E\{\hat w_j(k)\} = \mathbb E\{\varphi(v_j)\} < \varphi(\mathbb
E\{v_j\}) = 1 - \frac{1}{1 + \hat{\text{snr}}(k)}.\]

\noindent\textcolor{red}{Are there similar results bounding the variance?}

\paragraph{Gaussian approximation.}When the empirical variance can be approximated by a Gaussian, 
and its support is small compared with the concavity of $\varphi$, such that $\varphi$ can be 
assumed to be linear, then the weights are approximately Gaussian distributed. In this case,
we have that
\[\mathbb E\{\hat w_j(k)\}\approx \varphi(\mathbb E\{v_j\}) =\frac{\hat{\text{snr}}(k)}{1 + \hat{\text{snr}}(k)},\]
and that
\[\mathbb V\{\hat w_j(k)\}\approx \varphi'(\mathbb E\{v_j\})^2 \mathbb V\{v_j\}=
\frac{2}N\frac{\left(1 + 2\hat{\text{snr}}(k)\right)}{(1 + \hat{\text{snr}}(k))^4}.\]
For this Gaussian approximation to be valid, we need $N$ and/or
$\hat{\text{snr}}(k)$ to be large enough. The number of samples $N$ has the effect of 
reducing the support of the distribution, where increasing $\hat{\text{snr}}$ shifts the
distribution towards larger values of $v$, where $\varphi$ has less curvature.

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=0.9\textwidth]{weight_pdf}
	\caption{PDF of the Wiener coefficients, varying $N$, for a SNR of 0.1. The mean of each PDF
	is shown as a square on the graph. The Gaussian approximations are shown as
	the dashed curves. The dashed vertical line indicates $\varphi(\mathbb E\{v_j\})$.}
	\label{fig:wiener_pdf_N}
\end{figure}

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=0.9\textwidth]{weight_pdf-snr}
	\caption{PDF of the Wiener coefficients, varying $\hat{\text{snr}}$, for $N = 40$. The mean of each PDF
	is shown as a square on the graph. The Gaussian approximations are shown as
	the dashed curves. The dashed vertical lines indicate $\varphi(\mathbb E\{v_j\})$.}
	\label{fig:wiener_pdf_N}
\end{figure}

\section{Wiener estimates of the signal}

In the preceding sections we derived the PDF of
the weights of the empirical Wiener filter.
In the present section we will study the Wiener estimates of the signals $x_i$.

\subsection{Single Wiener estimate}

The Wiener estimate is given by
\[\hat x_{ij}(k) = \hat w_j(k) x_i(k) + \hat w_j(k)n_{ij}(k).\]
We consider that the $x_i$ are fixed, and study the effect of the noise.

As we have seen in the previous section, the filter coefficient is a random
variable depending on the noise (also on the sampled signals $x_i$, but we
are considering them fixed). The Wiener estimate $\hat x_{ij}(k)$ is given
by a product of random variables. Let us open a parenthesis to discuss the
PDF of a product of two random variables.

\paragraph{The PDF of a product of random variables.}
For two random variables $X,Y$, let $Z = XY$. The PDF of $Z$ can be computed as
\[f_Z(z) = \int_{-\infty}^{\infty} f_X(x)f_Y(z/x)\frac1{|x|}d x.\]
In our case, it seems difficult to derive a closed-form expression for the PDF
of the Wiener estimate, even if we adopt a Gaussian approximation. In the case
in which $X,Y$ are Gaussian, the distribution of the product is given by a 
linear combination of non-central chi squared random variables. This follows
from the following decomposition:
\[XY = \frac14(X + Y)^2 - \frac14(X-Y)^2.\]
Both terms are squared Gaussian random variables, and thus follow a non-central
chi squared distribution. Note also, that except if $X,Y$ have the same variance,
$X+Y$ and $X-Y$ are not independent. In this case, to compute the distribution of
the sum we require the joint distribution of $(X+Y)^2$ and $(X-Y)^2$.

%The first term is a scaling of the filter coefficient. For the second term
%we will adopt the simplifying assumption that the weight and the noise are
%independent. This is a valid approximation when $N$ is large, but becomes
%less valid when $N$ is small and $\sigma$ large, since each each realization 
%of the noise has a greater impact on the weight. The assumption of independence
%can be interpreted as if the weights were estimated using a realization of the
%noise, and then used to filter an additional independent realization.
%
%For the product of two random variables $Z = XY$, we have that
%\[XY = e^{\log X + \log Y},\]
%thus, computing the product amounts to applying a logarithm to both PDFs,
%convolving them, and applying an exponential to the result.
%The problem here is that our random variables can take negative values,
%invalidating this approach. If we assume that the weights follow a 
%Gaussian distribution, then we can express the distribution of the
%product as a linear combination of (dependent) chi squared random variables,
%because of the following relation:
%Except $X$ and $Y$ have same variance, both terms are dependent.

Instead of computing the PDF, we can compute its first and second order
moments. If we assume that $X,Y$ are independent, we have that
$\mathbb E\{XY\} = \mathbb E\{X\}\mathbb E\{Y\}$.
The variance could be computed from this equation:
\[\mathbb V\{XY\} = \mathbb E\{X^2Y^2\} - \mathbb E\{XY\}^2 = 
\mathbb V\{X\}\mathbb V\{Y\} +\mathbb V\{X\}\mathbb E\{Y\}^2 + \mathbb E\{X\}^2\mathbb V\{Y\}.\]

In our case, this amounts to
\begin{align*}
	\mathbb E\{\hat x_{ij}(k)\} &= \mathbb E\{\hat w_j(k)\}x_i(k) = \frac{\hat{\text{snr}}(k)}{1 + \hat{\text{snr}}(k)}x_i(k).\\
	\mathbb V\{\hat x_{ij}(k)\} &=  
(x_i(k)^2 + \sigma^2)
\frac{2}N\frac{\left(1 + 2\hat{\text{snr}}(k)\right)}{(1 + \hat{\text{snr}}(k))^4} + 
\sigma^2\frac{\hat{\text{snr}}(k)^2}{(1 + \hat{\text{snr}}(k))^2}.
Y\end{align*}

We can compute the bias:
\begin{multline*}
\mathbb B\{\hat x_{ij}(k)\} = \mathbb E\{\hat x_{ij}(k)-x_i(k)\} \\
= \mathbb E\{\hat w_j(k) x_i(k) - w(k)x_i(k) + w(k)x_i(k) - x_i(k)\}\\
= x_i(k)([\mathbb E\{\hat w_j(k)\} - w(k)] + [w(k) - 1])
\end{multline*}
Thus, we can decompose the bias in two terms. The first one represents the
bias between the empirical Wiener coefficient and the true Wiener coefficient.
Recall that we have that
\[\mathbb E\{\hat w_j(k)\} < \frac{\hat{\text{snr}}(k)}{1 + \hat{\text{snr}}(k)} \xrightarrow{N\to\infty} w(k).\]
The second term corresponds to the bias of the true Wiener filter, and
can be interpreted as the signal components unrecoverable from the noise.

\paragraph{Average squared bias and variance.} We can now compute the
average over the $N$ data points of the variance and the squared bias.
These quantities determine the mean squared error of the estimates.
\begin{align*}
	\frac1N\sum_{i = 1}^N\mathbb B\{\hat x_{ij}(k)\} &= \sigma^2\frac{\hat{\text{snr}}(k)}{(1 + \hat{\text{snr}}(k))^2}.\\
	\frac1N\sum_{i = 1}^N\mathbb V\{\hat x_{ij}(k)\} &=  
\sigma^2\left(\frac{2}N\frac{1 + 2\hat{\text{snr}}(k)}{(1 + \hat{\text{snr}}(k))^3} + 
\frac{\hat{\text{snr}}(k)^2}{(1 + \hat{\text{snr}}(k))^2}\right).
\end{align*}

\subsection{Aggregation of Wiener estimates}

Since we are assuming that the batches of $N$ observations are independent, 
the aggregation of $M$ Wiener estimates maintains the bias, and reduces
the variance by a factor of $M$.
%
%Thus we have that:
%\begin{align*}
%	\mathbb E\left\{\hat x_i(k)\right\} &= \frac{\hat{\text{snr}}(k)}{1 + \hat{\text{snr}}(k)}x_i(k).\\
%	\mathbb V\left\{\hat x_i(k)\right\} &=  
%(x_i(k)^2 + \sigma^2)
%\frac{2}{MN}\frac{\left(1 + 2\hat{\text{snr}}(k)\right)}{(1 + \hat{\text{snr}}(k))^4} + 
%\frac{\sigma^2}{M}\frac{\hat{\text{snr}}(k)^2}{(1 + \hat{\text{snr}}(k))^2}.
%\end{align*}
%
The aggregation attenuates the variance, but does not eliminate the bias. The bias
comes from two sources (i) we are estimating the Wiener coefficients using in every
batch the same $N$ signals, (ii) the bias of the true Wiener filter. The
resulting mean squared error is largely dominated by the bias when $M$ is large.

\paragraph{Comparison with the sample mean.}Note that in this particular
setting (having $M$ noisy versions of the same $N$
signals), a reasonable estimator is just
\[\check x_i = \frac1M\sum_{j = 1}^M y_{ij}(k).\]
This estimate is unbiased, and has a variance of $\sigma^2/M$.

From the expression of the $\mathbb V\{\hat x_{ij}\}$, it can be verified that for $N > 2$, 
\[\frac1N\mathbb V\{\hat x_i(k)\} = \frac1{MN}\sum_{i = 1}^N\mathbb V\{\hat
x_{ij}(k)\} < \sigma^2/M.\]
For $N = 2$ the equality can be achieved if
$\hat{\text{snr}}(k) = 0$. Therefore the variance of the aggregated Wiener estimates
is never larger than the variance of the sample mean. However, the bias is much
larger than $\sigma^2/M$, except for very small values of $M$.
As a consequence, the sample mean has a smaller mean square error already for
moderate values of $M$.

\subsection{The effect of thresholding}

If we consider that $M$ is large enough, we can neglect the variance,
and we can analyze the effect of thresholding in the bias.
The thresholding becomes relevant for components $k$ with a small 
signal energy. These components have already a considerable bias
due the damping of the Wiener filter, which causes signal loss.

We can analyze the first component of the bias, given by
\[b_1(\hat x_{ij}) = x_i(k)(\mathbb E\{\hat w_j(k)\} - w(k)).\]
On one hand, we have that
\[\mathbb E\{\hat w_j(k)\} < \mathbb E\{\hat w^+_j(k)\}.\]
On the other hand we have that
\[\mathbb E\{\hat w_j(k)\} < \frac{\hat{\text{snr}}(k)}{1 + \hat{\text{snr}}(k)} \xrightarrow{N\to\infty} w(k).\]
Therefore it is not easy to see a priori if the effect of the thresholding is 
negative or positive, by compensating the effect of the concave transformation.

In any case, if we consider the full bias, it seems that thresholding should be
in general positive, since it makes the filter coefficient closer to one.

\section{An experimental verification}

We perform a simple numerical simulation to verify the derivations above.
We generate $N$ random vectors in $\mathbb R^d$, with $d = 100$. These 
vectors are generated from a normal distribution given by
\[x_i\sim \mathcal N(0, 4\cdot\text{diag}[(d-1)^2,(d-2)^2,\dots,1,0]).\]
For each of the $N$ vectors, we generate $M$ noisy observations with $\sigma =
20$, and we compute $M$ empirical Wiener estimates, with and without thresholding, $\hat
x^+_{ij}$ and $\hat x_{ij}$.

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=.9\textwidth]{variance-bias}
	\caption{Squared bias and variances averaged over the $N$ points $x_i$. The variances
	correspond to the single Wiener estimate (\ie the variances after aggregation should
	be divided by $M$). The theoretical squared bias and variance and also shown
	for comparison. The variation with the component index $k$ reflects the fact that 
	each component has different signal-to-noise ratio.}
	\label{fig:bias-variance}
\end{figure}

We perform an experiment setting $N = 200$ and $M = 100$. To validate the above
derivations, we compute the empirical variance and squared bias of the single Wiener
estimates as follows:
\begin{align*}
\widehat V\{\hat x_i(k)\} &= \frac1M \sum_{j=1}^M(\hat x_{ij}(k) - \hat x_i(k))^2\\
\widehat B\{\hat x_i(k)\} &= \frac1M \sum_{j=1}^M(\hat x_{ij}(k) - x_i(k))^2 - \widehat V\{\hat x_i(k)\}
\end{align*}
Figure \ref{fig:bias-variance} plots the empirical variances and squared bias,
averaged over the $N$ vectors $x_i$ as a function of the component index $k$.
The results are shown for the thresholded and unthresholded versions of the
filter (the plots are almost identical).
We also show the theoretical variance and bias, computed from the formulas
derived above.
The variances in the plot correspond to the sigle Wiener estimate. 
Note how the variances are bellow $\sigma^2$, as predicted.
After aggregation,
this variances are reduced by a factor of $M$.
The bias however, does not change, which causes the sample mean to perform better.
In the present example the RMSE was $5.51$ for both versions of the Wiener filter,
and $1.99$ for the sample mean.

It can be oversved a slight better performance of the thresholded filter. The reason,
as discussed above, is that thresholding creates a bias for the small Wiener
weights, making them larger. This reduces the bias of the Wiener filter.

\section{Summary}

The main aim of this analysis was to find an explanation for the good performance of 
the negative weights in the NL-Bayes algorithm. We didn't achieve that objective. 
\emph{The model adopted here is too simple, and it does not replicate the behaviour of the 
NL-Bayes. On the contrary, in this setting thresholding the weights is better.}

However we did learn interesting things which might be usefull in analyzing more
complex models which might be closer to NL-Bayes. \emph{The Wiener filter is biased
(because it damps components with low SNR), and aggregation does not fix the
bias.} Furthermore, \emph{the thresholded coefficients help in reducing the bias} since
they increase the expected value of the coefficient, thus reducing the damping.

In this example we consider a single Gaussian model. Thefore there exists a
unique theoretical Wiener filter.
The situation in non-local Bayes is much more complex. 
A single patch might be part
of different Gaussian models, and for each there is a Wiener filter that needs
to be estimated. 
Furthermore, a pixel receives contributions from different patches that overlap the
pixel. This seems harder to model. In order to model this, one could consider 
the aggregation as an aggregation of images instead of patches. Each image results
from an empirical Wiener filter in a basis. This basis is built with the DCT or
PCA vectors of each non-overlapping patch. For an $s\times s$ patch, there are $s^2$
of these bases, built by shifting the non-overlapping patches. An image is computed
for each basis with a Wiener filter, and these $s^2$ images are aggregated.

In order to model this, we can consider a set of random rotations of a given basis,
and perform an empirical Wiener estimate in each rotation, before aggregating them.

\end{document}

### 2015-11-12 doc/201507_tip/paper.tex
[doc] TIP paper: Updated PSNRs for grayscale sequences

@@
 	\centering
-%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
+%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
 %	\vspace{.1cm}
@@
 	\vspace{.2cm}
-	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
+	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
 	\vspace{.2cm}
@@
 	\vspace{.2cm}
-%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
+%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
 %	\vspace{.1cm}
@@
 	\vspace{.2cm}
-	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
+	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
 	\vspace{.2cm}
@@
 	\vspace{.2cm}
-%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
+%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
 %	\vspace{.1cm}
@@
 %	\vspace{.1cm}
-%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
+%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
 %	\vspace{.1cm}
@@
 			                      & V-BM4D-tip           & \bsic{     } &       35.22  & \bsic{     } &       37.30   & \bsic{     } &       32.81   &              &              &              &       37.66   &              &              & \bsic{     } &       35.11  \\
-			                      & V-BM4D-mp            & \Bsic{34.32} &       34.95  & \Bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \Bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       33.29  & \bsic{34.62} &       35.15   & \bsic{30.80} &       31.22   & \bsic{32.34} &       32.79  & \bsic{36.21} &       37.72   & \bsic{33.20} &       33.79  & \bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 2$     & \Bsic{34.35} &       34.68  & \bsic{35.87} &       36.62   & \bsic{32.41} &       32.92   & \Bsic{34.26} &       34.78  & \bsic{36.86} & \Best{38.55}  & \Bsic{33.73} & \Best{34.38} & \Bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 3$     & \Bsic{34.34} &       35.23  & \bsic{35.63} &       37.08   & \bsic{32.39} &       33.18   & \bsic{34.02} &       35.25  & \bsic{36.57} & \Best{38.45}  & \bsic{33.45} & \Best{34.36} & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{34.25} &       35.40  & \bsic{35.39} &       37.21   & \Bsic{32.54} &       33.10   & \bsic{34.03} &       35.48  & \bsic{36.05} &       38.27   & \bsic{33.39} &       34.10  & \bsic{todo } &       todo   \\\hline
-%			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} & \Bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  & \bsic{todo } &       todo   \\\hline
+			                      & V-BM4D-mp            & \bsic{34.32} &       34.95  & \Bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \Bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 1$     & \bsic{33.16} &       33.65  & \bsic{34.69} &       35.43   & \bsic{30.74} &       31.47   & \bsic{32.18} &       33.00  & \bsic{36.75} &       38.14   & \bsic{33.21} &       33.98  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 2$     & \bsic{34.49} &       35.01  & \bsic{36.02} &       36.82   & \bsic{32.26} &       33.15   & \bsic{34.05} &       34.87  & \bsic{37.36} & \Best{38.69}  & \bsic{33.70} & \Best{34.56} & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \bsic{34.89} &       35.49  & \bsic{36.40} &       37.40   & \bsic{32.70} &       33.49   & \bsic{34.68} &       35.47  & \bsic{37.30} & \Best{38.76}  & \Bsic{33.81} & \Best{34.64} & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{35.03} &       35.70  & \bsic{36.35} &       37.63   & \Bsic{32.86} &       33.52   & \Bsic{34.91} &       35.73  & \bsic{37.06} & \Best{38.74}  & \Bsic{33.81} &       34.51  & \bsic{todo } &       todo   \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       33.29  & \bsic{34.62} &       35.15   & \bsic{30.80} &       31.22   & \bsic{32.34} &       32.79  & \bsic{36.21} &       37.72   & \bsic{33.20} &       33.79  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \Bsic{34.35} &       34.68  & \bsic{35.87} &       36.62   & \bsic{32.41} &       32.92   & \Bsic{34.26} &       34.78  & \bsic{36.86} & \Best{38.55}  & \Bsic{33.73} & \Best{34.38} & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \Bsic{34.34} &       35.23  & \bsic{35.63} &       37.08   & \bsic{32.39} &       33.18   & \bsic{34.02} &       35.25  & \bsic{36.57} & \Best{38.45}  & \bsic{33.45} & \Best{34.36} & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{34.25} &       35.40  & \bsic{35.39} &       37.21   & \Bsic{32.54} &       33.10   & \bsic{34.03} &       35.48  & \bsic{36.05} &       38.27   & \bsic{33.39} &       34.10  & \bsic{todo } &       todo   \\\hline
+%%			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} & \Bsic{todo } &       todo   \\
+%%			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} & \bsic{todo } &       todo   \\
+%%			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  & \bsic{todo } &       todo   \\\hline
 %
@@
 			                      & V-BM4D-tip           & \bsic{     } &       31.59  & \bsic{     } &       33.79   & \bsic{     } &       28.63   &              &              &              &       34.10   &              &              & \bsic{     } &       31.34  \\
-			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \Bsic{32.18} &       33.46   & \Bsic{28.12} &       28.32   & \Bsic{29.67} &       30.49  & \Bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{29.62} &       30.16  & \bsic{30.76} &       31.54   & \bsic{26.17} &       26.56   & \bsic{27.89} &       28.39  & \bsic{32.41} &       33.77   & \bsic{28.69} &       29.26  & \bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 2$     & \Bsic{30.81} &       31.37  & \bsic{31.98} &       33.08   & \bsic{27.89} &       28.41   & \Bsic{29.69} &       30.41  & \bsic{33.17} & \Best{34.97}  & \Bsic{29.32} & \Best{30.00} & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \bsic{29.88} &       31.62  & \bsic{30.60} &       33.05   & \bsic{27.50} &       28.89   & \bsic{29.02} &       30.86  & \bsic{31.23} &       34.26   & \bsic{28.51} & \Best{30.08} & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \bsic{29.49} &       31.64  & \bsic{30.10} &       32.94   & \bsic{27.47} &       29.07   & \bsic{28.86} &       31.12  & \bsic{30.51} &       33.88   & \bsic{28.26} & \Best{30.03} & \bsic{todo } &       todo   \\\hline
-%			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  & \Bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} & \bsic{todo } &       todo   \\\hline
+			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \Bsic{32.18} &       33.46   & \bsic{28.12} &       28.32   & \bsic{29.67} &       30.49  & \Bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 1$     & \bsic{29.60} &       30.32  & \bsic{30.74} &       31.71   & \bsic{26.10} &       26.81   & \bsic{27.79} &       28.64  & \bsic{32.40} &       33.82   & \bsic{28.64} &       29.46  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 2$     & \bsic{30.81} &       31.54  & \bsic{32.01} &       33.24   & \bsic{27.84} &       28.64   & \bsic{29.63} &       30.63  & \bsic{33.20} &       35.05   & \bsic{29.28} &       30.19  & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \Bsic{31.14} &       31.99  & \Bsic{32.23} &       33.81   & \bsic{28.33} &       29.18   & \bsic{30.27} &       31.38  & \bsic{33.09} &       35.29   & \Bsic{29.39} & \Best{30.35} & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{31.19} &       32.22  & \bsic{32.05} &       34.07   & \Bsic{28.49} &       29.36   & \Bsic{30.47} &       31.74  & \bsic{32.72} & \Best{35.30}  & \Bsic{29.35} & \Best{30.35} & \bsic{todo } &       todo   \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{29.62} &       30.16  & \bsic{30.76} &       31.54   & \bsic{26.17} &       26.56   & \bsic{27.89} &       28.39  & \bsic{32.41} &       33.77   & \bsic{28.69} &       29.26  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \Bsic{30.81} &       31.37  & \bsic{31.98} &       33.08   & \bsic{27.89} &       28.41   & \Bsic{29.69} &       30.41  & \bsic{33.17} & \Best{34.97}  & \Bsic{29.32} & \Best{30.00} & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{29.88} &       31.62  & \bsic{30.60} &       33.05   & \bsic{27.50} &       28.89   & \bsic{29.02} &       30.86  & \bsic{31.23} &       34.26   & \bsic{28.51} & \Best{30.08} & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \bsic{29.49} &       31.64  & \bsic{30.10} &       32.94   & \bsic{27.47} &       29.07   & \bsic{28.86} &       31.12  & \bsic{30.51} &       33.88   & \bsic{28.26} & \Best{30.03} & \bsic{todo } &       todo   \\\hline
+%%			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  & \Bsic{todo } &       todo   \\
+%%			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} & \bsic{todo } &       todo   \\
+%%			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} & \bsic{todo } &       todo   \\\hline
 %
@@
 			                      & V-BM4D-tip           & \bsic{     } &       29.72  &              &       31.75   & \bsic{     } &       26.29   &              &              &              &       31.83   &              &              & \bsic{     } &       29.25  \\
-			                      & V-BM4D-mp            & \Bsic{28.89} &       29.37  & \Bsic{29.56} &       31.02   & \Bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \Bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{27.32} &       28.20  & \bsic{27.94} &       29.14   & \bsic{23.62} &       23.96   & \bsic{25.42} &       25.82  & \bsic{29.50} &       31.08   & \bsic{26.14} &       26.69  & \bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 2$     & \bsic{28.65} &       29.51  & \Bsic{29.55} &       30.93   & \bsic{25.33} &       25.78   & \Bsic{27.31} &       27.90  & \bsic{30.70} & \Best{32.63}  & \Bsic{26.99} &       27.55  & \Bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 3$     & \bsic{27.49} &       29.71  & \bsic{27.91} &       30.91   & \bsic{24.75} &       26.36   & \bsic{26.30} &       28.43  & \bsic{28.45} &       31.95   & \bsic{25.95} & \Best{27.72} & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \bsic{26.92} &       29.64  & \bsic{27.28} &       30.73   & \bsic{24.60} &       26.60   & \bsic{26.04} &       28.68  & \bsic{27.61} &       31.50   & \bsic{25.57} & \Best{27.71} & \bsic{todo } &       todo   \\\hline
+			                      & V-BM4D-mp            & \bsic{28.89} &       29.37  & \bsic{29.56} &       31.02   & \bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \Bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 1$     & \bsic{27.33} &       28.28  & \bsic{27.96} &       29.26   & \bsic{23.57} &       24.18   & \bsic{25.36} &       26.06  & \bsic{29.53} &       31.04   & \bsic{26.11} &       26.86  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 2$     & \bsic{28.67} &       29.65  & \bsic{29.59} &       31.10   & \bsic{25.29} &       26.04   & \bsic{27.27} &       28.17  & \bsic{30.74} &       32.69   & \bsic{26.97} &       27.76  & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \bsic{29.12} &       30.13  & \Bsic{30.09} &       31.77   & \bsic{25.82} &       26.66   & \bsic{28.00} &       29.01  & \bsic{30.88} &       33.06   & \Bsic{27.17} & \Best{28.01} & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{29.26} &       30.38  & \Bsic{30.13} &       32.11   & \Bsic{26.04} &       26.93   & \Bsic{28.28} &       29.43  & \bsic{30.67} & \Best{33.19}  & \Bsic{27.20} & \Best{28.08} & \bsic{todo } &       todo   \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{27.32} &       28.20  & \bsic{27.94} &       29.14   & \bsic{23.62} &       23.96   & \bsic{25.42} &       25.82  & \bsic{29.50} &       31.08   & \bsic{26.14} &       26.69  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{28.65} &       29.51  & \Bsic{29.55} &       30.93   & \bsic{25.33} &       25.78   & \Bsic{27.31} &       27.90  & \bsic{30.70} & \Best{32.63}  & \Bsic{26.99} &       27.55  & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{27.49} &       29.71  & \bsic{27.91} &       30.91   & \bsic{24.75} &       26.36   & \bsic{26.30} &       28.43  & \bsic{28.45} &       31.95   & \bsic{25.95} & \Best{27.72} & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \bsic{26.92} &       29.64  & \bsic{27.28} &       30.73   & \bsic{24.60} &       26.60   & \bsic{26.04} &       28.68  & \bsic{27.61} &       31.50   & \bsic{25.57} & \Best{27.71} & \bsic{todo } &       todo   \\\hline
 %
@@
 			                      & V-BM4D-tip           & \bsic{     } &       28.49  & \bsic{     } &       30.35   & \bsic{     } &       24.60   &              &              &              &       30.10   &              &              & \bsic{     } &       27.81  \\
-			                      & V-BM4D-mp            & \Bsic{27.67} &       28.38  & \Bsic{27.81} &       29.37   & \Bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \Bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{25.65} &       26.83  & \bsic{25.97} &       27.49   & \bsic{21.89} &       22.25   & \bsic{23.57} &       24.11  & \bsic{27.32} &       29.03   & \bsic{24.27} &       24.97  & \bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 2$     & \bsic{27.09} &       28.27  & \bsic{27.67} &       29.46   & \bsic{23.56} &       24.06   & \Bsic{25.48} &       26.17  & \bsic{28.64} & \Best{30.90}  & \Bsic{25.21} &       25.89  & \bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 3$     & \bsic{25.66} &       28.33  & \bsic{25.93} &       29.31   & \bsic{22.84} &       24.65   & \bsic{24.35} &       26.69  & \bsic{26.31} &       30.11   & \bsic{24.11} & \Best{26.08} & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \bsic{24.98} &       28.16  & \bsic{25.18} &       29.03   & \bsic{22.62} &       24.89   & \bsic{23.98} &       26.90  & \bsic{25.41} &       29.59   & \bsic{23.64} & \Best{26.05} & \Bsic{todo } &       todo   \\\hline
-%			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} & \Bsic{todo } & \Best{todo } \\
-%			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} & \Bsic{todo } & \Best{todo } \\\hline
+			                      & V-BM4D-mp            & \Bsic{27.67} &       28.38  & \bsic{27.81} &       29.37   & \bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \Bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 1$     & \bsic{25.66} &       26.82  & \bsic{26.01} &       27.53   & \bsic{21.85} &       22.37   & \bsic{23.53} &       24.25  & \bsic{27.37} &       28.97   & \bsic{24.27} &       25.05  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 2$     & \bsic{27.12} &       28.34  & \bsic{27.73} &       29.58   & \bsic{23.53} &       24.24   & \bsic{25.46} &       26.36  & \bsic{28.71} &       30.96   & \bsic{25.20} &       26.03  & \bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 3$     & \Bsic{27.60} &       28.84  & \bsic{28.30} &       30.32   & \bsic{24.09} &       24.90   & \bsic{26.16} &       27.26  & \bsic{28.92} &       31.42   & \Bsic{25.45} &       26.34  & \Bsic{todo } &       todo   \\
+			                      & VNLB   $s_t = 4$     & \Bsic{27.75} &       29.11  & \Bsic{28.40} &       30.69   & \Bsic{24.31} &       25.19   & \Bsic{26.43} &       27.77  & \bsic{28.73} & \Best{31.57}  & \Bsic{25.50} & \Best{26.45} & \Bsic{todo } &       todo   \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{25.65} &       26.83  & \bsic{25.97} &       27.49   & \bsic{21.89} &       22.25   & \bsic{23.57} &       24.11  & \bsic{27.32} &       29.03   & \bsic{24.27} &       24.97  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{27.09} &       28.27  & \bsic{27.67} &       29.46   & \bsic{23.56} &       24.06   & \Bsic{25.48} &       26.17  & \bsic{28.64} & \Best{30.90}  & \Bsic{25.21} &       25.89  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{25.66} &       28.33  & \bsic{25.93} &       29.31   & \bsic{22.84} &       24.65   & \bsic{24.35} &       26.69  & \bsic{26.31} &       30.11   & \bsic{24.11} & \Best{26.08} & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \bsic{24.98} &       28.16  & \bsic{25.18} &       29.03   & \bsic{22.62} &       24.89   & \bsic{23.98} &       26.90  & \bsic{25.41} &       29.59   & \bsic{23.64} & \Best{26.05} & \Bsic{todo } &       todo   \\\hline
+%%			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  & \bsic{todo } &       todo   \\
+%%			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} & \Bsic{todo } & \Best{todo } \\
+%%			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} & \Bsic{todo } & \Best{todo } \\\hline
 		\end{tabular}}
 % Command to print rounded psnrs
-% for i in $(cat bus_s40_pt*/measures | grep PSNR_final | sed "s/^-PSNR_final\ =\ "//); do  echo "scale=2;(((10^2)*$i)+0.5)/(10^2)" | bc; done
+% :r !for i in $(cat /media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/tip_table_1ps7_2ps7/te*/measures | grep PSNR_basic | sed ``s/^-PSNR_basic\ =\ ''//); do  echo ``scale=2;\left( (10^2)*$i)+0.5)/(10^2)'' | bc; done \right)
 	\end{center}
-	\caption{Quantitative denoising results for some classic grayscale test sequences. See text for details. \pcomment{NOTE: the values in the table need to be updated!!}}
+	\caption{Quantitative denoising results for some classic grayscale test sequences. See text for details.}
 	\label{tab:psnr-classic-gray}

### 2015-12-10 doc/201507_tip/paper.tex
[doc] TIP paper: second draft sent to JMM with description of negative weights

--- 2015-10-16 doc/201507_tip/paper.tex
@@
 \newcommand{\padd}[1]{\pa{#1}}
-\newcommand{\pcomment}[1]{\textit{\pa{#1}}}
+%\newcommand{\pcomment}[1]{\textit{\pa{#1}}}
+\newcommand{\pcomment}[1]{}
 
@@
 
+An interesting alternative was proposed in \cite{Liu2010},
+based on non-local means.
+To denoise a target 2D patch in a frame, its forward and backward trajectories are
+determined using a robust optical flow algorithm based on \cite{Bruhn2005}. 
+Each half of the trajectory extends for $t$ frames. There are $2t + 1$ 2D patches
+centered at each point of the trajectory.
+For each of these patches, the $n$ nearest neighbors are found
+using an efficient approximate searching strategy. The target 2D patch is denoised
+by performing a weighted average of these $(2t + 1)n$ patches. The weight considers
+the patch similarity as in the original non-local means method, multiplied by a coefficient
+that decreases smoothly with the temporal distance between a source patch and the target patch.
+%
+In this way, 2D patches in the same trajectory are denoised using a smoothly
+varying non-local average of similar 2D patches. The result is a video with
+a high temporal consistency.
+
 A natural next step is to consider 3D spatio-temporal patches. This has two
@@
 provides a mechanism to impose some temporal consistency on the result, since
-now, the temporally continguous 2D spatial slices of a spatio-temporal patch
+now, the temporally contiguous 2D spatial slices of a spatio-temporal patch
 are filtered jointly. Secondly, a 3D patch has a higher number of pixels
@@
 Motion-compensated patches have the benefit that their spatial slices are very
-similar between each other (or the same, assuming purely translational pixelic
-motion). As a consequence, temporal filtering can be easily performed by
+similar between each other. As a consequence, temporal filtering can be easily performed by
 filtering inside the patch in the temporal direction. 
@@
 similar motion-compensated 3D patches starting in the same frame.
-
-%It has been shown by \cite{Liu2010} and \cite{Maggioni2011,Maggioni2012} that motion estimation can still be
-%beneficial for patch-based methods. 
-%
-An example of this is the method presented in \cite{Liu2010}. The authors
-propose a method based on non-local means. The method is described in terms of
-2D patches. To denoise a target 2D patch, the $k$ nearest neighbors in the current
-frame are found. The 2D patches in their forward and backward trajectories are
-used also to denoising the target patch. As a consequence the set of similar
-patches averaged to denoise each pixel varies smoothly along motion
-trajectories. This yields results with high temporal consistency. 
-To estimate motion, their method resorts to a robust optical flow algorithm
-based on \cite{Bruhn2005}.
 
@@
 
-In this work we present an extension to video of the non-local Bayes image
-denoising method \cite{Lebrun2013a,Lebrun2013ipol} using 3D rectangular
-patches and which does not require motion estimation. Yet, it provides
+In this work we present new Bayesian patch-based video denoising method using
+3D rectangular patches and not requiring motion estimation.
+Yet, it provides
 results which compare favourably to the current state-of-the-art,
-both quantitatively by a significant marging and qualitatively, specifically in
+both quantitatively by a significant margin and qualitatively, specifically in
 terms of the temporal consistency attained.
-The method works by learning a Gaussian \emph{a priori} model from sets of 
+In the spirit of  \cite{Lebrun2013a,Lebrun2013ipol},
+the method works by learning a Gaussian \emph{a priori} model from sets of 
 similar noisy patches. Each patch is denoised by computing the \emph{maximum a
@@
 theoretical results and supported by an empirical analysis, we add the 
-assumtion that the \emph{a priori} model is of low rank (\ie the clean patches
-lie in a lower dimensional subspace). This assumtion lowers the computational cost
+assumption that the \emph{a priori} model is of low rank (\ie the clean patches
+lie in a lower dimensional subspace). This assumption lowers the computational cost
 of the algorithm, and improves the results.
@@
 The rest of the paper is organized as follows: in \S
-\ref{sec:review_nonlocal_Bayes} we review the Bayesian patch denoising principle 
-and describe our extension to video. The final algorithm and details about its
-implementation are given in \S \ref{sec:algorithm}.
+\ref{sec:review_nonlocal_Bayes} we review our patch-based Bayesian optimal estimator for
+video denoising. The final algorithm and details about its implementation are
+given in \S \ref{sec:algorithm}.
 Some relevant aspects of the proposed method are discussed in \S
@@
 
-A patch based Bayesian algorithm can assume that the patches similar to a given
+Our fundamental assumption is that video patches similar to a given
 patch follow a Gaussian distribution.
@@
 principal directions of the covariance matrix $C$.
-Let $C = U\Lambda U^T$ denote the eigendecomposition of $C$. Then we have that
+Let $C = U\Lambda U^T$ denote the spectral decomposition of $C$. Then we have that
 \[U^T(\widetilde{\ma p} - \overline{\ma p}) \,\,\,\, = \,\,\,\, 
@@
 
-The parameters of the \textit{a priori} model, are learnt from the noisy video as
+The parameters of the \textit{a priori} model are learnt from the noisy video as
 follows. For each noisy patch $\ma q$, we select the most $n$
@@
 We will also assume that the covariance matrix has a lower rank $k$.  In this
-case, it has been shown REF PPCA that maximum likelihood estimate is given by
-truncated the spectral decomposition of $\widehat C$ to the $k$ largest
-eigenvalues.
+case, it has been shown \cite{Tipping1999} that the maximum likelihood estimate is given by
+truncating the spectral decomposition of $\widehat C$ to the $k$ largest
+eigenvalues 
 \begin{equation}
@@
 
-The Figures \ref{fig:patch_groups_pos} and \ref{fig:patch_groups_patches}
+\padd{The estimated eigenvalues are given by $\widehat \lambda_i = \widehat
+\nu_i - \sigma^2$, where $\widehat \nu_i$ are the eigenvalues of the empirical
+covariance matrix of the noisy patches. In practice, some of the smallest
+estimated eigenvalues $\widehat \nu_i$ can be smaller than $\sigma^2,$ causing
+$\widehat \lambda_i$ and the corresponding filter coefficient $w_{ii}$ to be
+negative. Negative variances do not have physical meaning, and the
+corresponding weights have a negative impact on the MAP estimate. This is an
+issue of empirical Wiener filters and it is typically addressed by zeroing out
+the negative coefficients. Later in \S
+\ref{sec:parameters} we compare the results obtained by zeroing out negative
+coefficients against using them.}
+
+Figures \ref{fig:patch_groups_pos} and \ref{fig:patch_groups_patches}
 show two examples of groups of similar $9\times 9\times 4$ patches taken from
@@
 9$ spatial slices. For the two examples shown in Figure \ref{fig:patch_groups_pos}
-the figure shows the noisy patches, the result of the MAP estimation (setting
-$r = 40$) and the mean patch together with the leading 19 principal directions.
-Since the patch is not motion-compensated, all spatial slices can be different,
+the figure shows the noisy patches, the result of the MAP estimation and the
+mean patch together with the leading 19 principal directions. The Gaussian
+models were learnt from the $n = 200$ similar patches shown in Figure
+\ref{fig:patch_groups_pos}. The MAP estimates were computed setting $r = 40$.
+Since the patch is not
+motion-compensated, all spatial slices can be different,
 and thus the same applies to the principal directions.
@@
 assumption that the patches of an image are distributed according to a Gaussian
-Mixture Model (GMM). A method is proposed to learn the parameters of the model from
+Mixture Model (GMM) which is learnt from
 the image. A GMM is also used in \cite{Zoran2011}, but it is trained from a
@@
 	In red we show the positions of the 5 nearest neighbors, in green the next 40 and in blue the rest.
-	Note the points shown correspond to the top-left pixel of the first spatial
+	Note that the points shown correspond to the top-left pixel of the first spatial
 	slice of each patch.
@@
 
-\paragraph{Handling of color} Color videos are handled as in \cite{Lebrun2013a}.
-%
-In the first stage, we express the video in a luminance-chrominance colorspace,
+\paragraph{Handling of color} %Color videos are handled as in \cite{Lebrun2013a}.
+%
+In the first stage, we express the video in a luminance-chrominance color space,
 specifically we apply the opponent color transform (see \cite{Dabov2007tip,Lebrun2013a}).
@@
 In the second stage, the patch distance is computed using the RGB patches, and
-a single \textit{a priori} Gaussian model is built for the each set
-of similar RGB patches.
+a joint \textit{a priori} Gaussian model is built for each set
+of similar RGB patches. Note that in first stage, we learn three Gaussian models
+of dimensionality $s_x^2s_t$, whereas in the second stage we learn a single 
+Gaussian model of tripled dimensionality.
 
@@
 patches is normalized by the number of elements in the patch and the number of
-channels).
+channels and the values of each channel are in the range  $[0,255]$).
 
@@
 the search window.  The remaining terms correspond respectively to the
-computation of the covariance matrix and its truncated eigen-decomposition.
+computation of the covariance matrix and its truncated spectral decomposition.
 
@@
 of its principal directions.
-Let us note that there are methods for computing the $r$ principal directions
+There are methods for computing the $r$ principal directions
 of a set of points that do not require computing the covariance matrix
@@
 We apply two tricks
-considered in \cite{Lebrun2013ipol} in order to reduce the number of reference patches. 
+considered in \cite{Dabov2007tip,Lebrun2013ipol} in order to reduce the number of reference patches. 
 The first one consists on visiting only 
-those patches on a coarser spatial grid with vertical and horizontal separation of $s_x/2$
-(similar to \cite{Dabov2007tip}). This reduces the number of reference patches by a
-factor of $s_x^2/4$. The second trick consists on the following.  After
+those patches on a coarser spatial grid with vertical and horizontal separation
+of $s_x/2$. This reduces the number of reference patches by a factor of
+$s_x^2/4$. The second trick consists on the following.  After
 filtering the patches in a group, these patches are not considered again
@@
 that $u(x,t + \tau) = u(\varphi(x,t + \tau; -\tau),t)$, where
-$\varphi(x,t+\tau;\, \cdot\, )$ denotes the motion trajectory passing though
+$\varphi(x,t+\tau;\, \cdot\, )$ denotes the motion trajectory passing through
 $(x,t + \tau)$.
@@
 %
-As a consequence, by increasing $s_t$, on can reduce the 
+As a consequence, by increasing $s_t$, one can reduce the 
 noise in the patch distance and have the same pattern of self-similarity as a 
@@
 Learning the parameters of the \emph{a priori} distribution for each group of
-noisy patches amounts to estimating a covariance matrix is a high dimensional space 
+noisy patches amounts to estimating a covariance matrix in a high dimensional space 
 and with a limited number of samples. 
@@
 covariance matrix. We will find a compromise to this trade-off empirically  in
-\S \ref{sec:parameters}. But it still intersting to review the literature 
-on the sample covariance matrix as an estimator of the population covariance.
+\S \ref{sec:parameters}.
 
@@
 %a covariance matrix in the ambient space.}
-\pcomment{Comment: This reference may not be as relevant, in the light of the 
-results known for Gaussian covariance matrices. It would be interesting to see what 
-\cite{bunea2015} says regarding covariance matrices with low-effective rank.}
+%\pcomment{Comment: This reference may not be as relevant, in the light of the 
+%results known for Gaussian covariance matrices. It would be interesting to see what 
+%\cite{bunea2015} says regarding covariance matrices with low-effective rank.}
 
 The rank also plays a role in the estimation of the covariance matrix.
-As explained in \S \ref{sec:complexity}, alleviating the computational cost is
+As explained in \S \ref{sse:complexity}, alleviating the computational cost is
 one of the reasons for using a low rank approximation of the empirical
@@
 performance. In situations in which the number of samples 
-is comparable to their dimension, the eigen-decomposition of the empirical
+is comparable to their dimension, the spectral decomposition of the empirical
 covariance matrix $\widehat C$ can have considerable errors with respect to
@@
 The case of Gaussian models with covariance matrices of the form $C = A + \sigma^2I$,
-where $A$ is does not have full rank, has been studied in the statistics and physics
+where $A$ does not have full rank, has been studied in the statistics and physics
 literature. The authors in \cite{johnstone2009,paul2007,nadler2008} study the
-limit when $n,p\to\infty$ such that $p/n\to\gamma < \infty$.
-These works show that, for a non-zero ratio $\gamma$, the empirical eigenvectors 
+limit when the number of samples $n$ and the dimension $p$ grow to infinity at
+same rate, such that $p/n\to\gamma < \infty$.  These works show that, for a
+non-zero ratio $\gamma$, the empirical eigenvectors 
 and eigenvalues are inconsistent estimators of the population ones.
@@
 \pcomment{What can we say about this bounds.}
-These larger errors between the sample eigenvectors and their population
+
+The errors between the sample eigenvectors and their population
 counterparts manifest themselves as noise, which then affects the MAP estimate.
-This suggest that better denoising should be obtained by discarding the
-eigenvectors associated with lower eigenvalues.
+%
+These asymptotic results suggest to discard the eigenvectors associated with 
+lower eigenvalues. How many should be discarded in practice when $n$ and $p$ are finite, 
+can only be fixed empirically, as we do in \$ \ref{sec:parameters}.
 
@@
 temporal components of the search region, $w_x$ and $w_t$, the number of similar
-patches $n$ and the rank of the a priori covariance matrix $r$.
+patches $n$ and the rank of the \textit{a priori} covariance matrix $r$.
 When needed, we will add a subscript indicating the stage, \eg
 $n_{1}$ and $n_{2}$.
+We will consider different parameter settings for color and grayscale videos.
 
@@
 
-Setting the size of the search region implies a
-trade-off between denoising performance and running time: A larger search
-region takes longer to traverse but yields better results, since more
-similar patches can be found. We fix the search
-region for both stages of the algorithm at 
-\begin{equation}
-w_x = 37 \quad \text{ and } \quad w_t = 5.
-\label{eq:search_region_parameters}
-\end{equation}
+Setting the size of the search region implies a trade-off between denoising
+performance and running time: A larger search region takes longer to traverse
+but yields better results, since more similar patches can be found. We use the same 
+search region in both stages. The
+temporal search window is fixed at $w_t = 5$. The spatial search region is set at
+$w_x = 37$ for color videos and $w_x = 45$ for grayscale videos.
 With these values, the search region captures the $5$ frame trajectory of the
-target patch as long as it moves slower than $37/5 = 7.4$
-pixels/frame.
+target patch as long as it moves slower than $37/5 = 7.4$ pixels/frame (for
+color videos).
 
@@
 %where $m = s_x^2s_t$ is the total number of pixels in the patch.
-Increasing the spatial patch size $s_x$ reduces the variance of the noise in the patch
-distance. 
-However, for larger
-patches it becomes less likely to find other patches with a similar texture
-pattern. The use spatio-temporal patches helps in solving this trade-off: for
-instance, with a spatio-temporal patch of size $5\times 5\times 4$, we obtain
-the same patch distance noise as with a spatial patch of size $10\times 10
-\times 1$. Moreover, as discussed in \S \ref{sse:spatio-temporal-patches}, for
-an approximately uniform motion, the 
-amount of similar neighbors of a $5\times 5\times 4$ patch is roughly the same
-as for a $5\times 5\times 1$ patch.
-
-We will set the spatial patch size at \[s_x = 5\] for both stages. Larger
-patches (up to $s_x = 9$) lead to an mild improvement of the results (on
-average). This improvement comes at a considerable increase in the
-computation time, since our current implementation is $\mathcal O(s_x^4)$. Thus,
-have found that a good compromise between computation time and quality is given
-by $s_x = 5$.
+%*% Increasing the spatial patch size $s_x$ reduces the variance of the noise in the patch
+%*% distance. 
+%*% However, for larger
+%*% patches it becomes less likely to find other patches with a similar texture
+%*% pattern. The use spatio-temporal patches helps in solving this trade-off: for
+%*% instance, with a spatio-temporal patch of size $5\times 5\times 4$, we obtain
+%*% the same patch distance noise as with a spatial patch of size $10\times 10
+%*% \times 1$. Moreover, as discussed in \S \ref{sse:spatio-temporal-patches}, for
+%*% an approximately uniform motion, the 
+%*% amount of similar neighbors of a $5\times 5\times 4$ patch is roughly the same
+%*% as for a $5\times 5\times 1$ patch.
+%
+For color videos, we will set the spatial patch size at $s_x = 5$ for both
+stages, whereas for grayscale videos we use $s_x = 7$. Larger patches (up to $s_x = 9$) lead to an mild improvement of the
+results (on average). This improvement comes at a considerable increase in the
+computation time, since our current implementation is $\mathcal O(s_x^4)$.
+Thus, have found that a good compromise between computation time and quality is
+given by $s_x = 5$.
 
@@
 The number of similar patches $n$ and the rank $r$ affect the estimation of the covariance
-matrix $C$, controlling the trade-off between the accuracy of Gaussian model
-and precision of the covariance matrix,
+matrix $C$, controlling the trade-off between the accuracy of the Gaussian model
+and the precision of the covariance matrix,
 which in turn has a direct effect on the denoising strength of the algorithm.
@@
 %algorithm. For example, using a large
-We find a compromise to this trade-off empirically, by trying different values of this parameter on a 
-few training sequences and use the one yielding the best PSNR.
+We found a compromise to this trade-off empirically, by trying different values
+of this parameter on a few training sequences and keeping the one that yields
+the best PSNR on average.
 
@@
 
-The plots in Figure \ref{fig:rank1-nsim1-bpsnr} show the PSNR of the basic
-estimate as a function of the rank $r_1$, for several values of $n_{1}$.
-The curves correspond to an average over 20 frames clips 
-extracted from four classical test
-sequences, namely \emph{bus}, \emph{foreman}, \emph{football} and \emph{tennis}.
-The sequences were contaminated with AGWN of standard deviation $\sigma = 10,
-20, 30, 40$. 
-%
-%
-We can interpret the results in the light of the theoretical results
-described in \S \ref{sse:covariance-estimation}.
-For all noise levels, best results are obtained when using a larger number of
-samples $n_1$. All curves of fixed $n_1$ show a maximum at a given rank lower than
-the dimensionality of the patch. As the noise level increases, this optimal rank
-shifts to the left. This makes sense, since less eigenvectors are reliable estimates.
-%
-Also, for a fixed noise level, the optimal rank is smaller for smaller values of $n_1$.
-Smaller groups obtained by keeping only the
+The plots in Figure \ref{fig:rank1-nsim1-psnr-color} show the PSNRs of the
+basic and final estimates as a function of the rank $r_1$, for several values
+of $n_{1}$. The curves correspond to an average over 20 frames clips extracted
+from four classical test color sequences, namely \emph{bus}, \emph{foreman},
+\emph{football} and
+\emph{tennis}. The sequences were contaminated with
+AGWN of standard deviation $\sigma = 10, 20, 30, 40$. 
+Figure \ref{fig:rank1-nsim1-psnr-gray} shows the results for a
+grayscale version of the same sequences. 
+%
+%
+
+\padd{For the basic estimate, we show two set of curves. The dashed curves were
+obtained by zeroing out negative eigenvalues of the estimated a priori covariance
+matrix $\widehat C$, computed according to \eqref{eq:learn_parameters}. The continuous curves 
+were obtained by retaining negative eigenvalues. In this case the MAP is estimated
+with an empirical Wiener filter that may have some negative coefficients.}
+
+\padd{For lower values of the rank parameter $r$, both curves coincide, since the first
+eigenvalues are positive. 
+For all noise levels, all curves of fixed $n_1$ present a first peak at a low value of the rank $r$.
+The behaviour of the basic estimate around this peak can be
+interpreted in the light of the theoretical results described in \S
+\ref{sse:covariance-estimation}.
+As the noise level increases, the rank at which the peak is attained
+shifts to the left. This makes sense, as the reliability of the computed eigenvectors
+decrease with increasing noise.
+%
+Also, for a fixed noise level, when the number of samples $n_1$ increases, the value
+of the peak increases also, and so does the rank at which it is attained.
+This is again explainable, as smaller groups obtained by keeping only the
 most similar patches have less modes of variation, and thus a worse signal-to-noise ratio
-in the eigenvectors with lower eigenvalues.
+in the eigenvectors with lower eigenvalues.}
 %As the group of patches grows
@@
 
-The results obtained for the final estimate when varying the second stage
-parameters $n_2$ and $r_2$ show a different behaviour, as shown in Figure
+%The eigenvalues of $\widehat C$ are given by $\hat \lambda_i = \widehat \nu_i -
+%\sigma^2$, where $\widehat \nu_i$ are the eigenvalues of the empirical
+%\emph{a posteriori} covariance matrix.
+%In practice due to the estimation errors, several
+%$\widehat \nu_i$ are smaller than $\sigma^2$. These translate into negative
+%coefficients $w_{ii}$ in the empirical Wiener filter \eqref{eq:wiener_coeffs},
+%which result in a poorer estimation of the MAP.
+\padd{As the rank parameter increases, both curves diverge. 
+The dashed curves become almost constant at the point when
+most eigenvalues become negative. After that point increasing the
+rank has no effect if the negative eigenvalues are zeroed out.
+%
+Surprisingly, these negative coefficients have a positive effect on the final 
+result, creating the second peak for high values of the rank shown by the
+continuous plots. Currently we do not have an explanation for this behaviour
+although it is related to the aggregation: even if the estimated MAP for the
+patches in each group have larger errors, after aggregation these errors seem
+to cancel, yielding an overall better estimate of the clean image.}
+
+\padd{The final estimate shows the same qualitative behaviour with respect to the first
+stage parameters. The dashed curves obtained by zeroing out the negative
+eigenvalues are not shown to avoid cluttering the figure. Essentially the
+second step has the effect of reducing the differences between results obtained
+with different parameters. Based on these curves, we fix the first stage parameters at
+$n_1 = 300$ and $r_1 = 95$ for color videos, and at $n_1 = 300$ and $r_1 = 180$ for grayscale videos.}
+
+Using these parameters for the first stage, we analyzed the impact when varying the second stage
+parameters $n_2$ and $r_2$. The plots obtained are shown in Figure
 \ref{fig:rank2-nsim2-fpsnr}.
-These curves where obtained fixing the first stage parameters at $n_1 = 400$
-and $r_1 = 100$ (full rank).
-\pcomment{It doesn't make much sense considering $r_1 = 100$ after saying that
-is best to consider a low $r_1$.}
-%
-In the second stage best results are found with a much smaller value
-for $n_{2}$ than in the first stage.
-%
-The reason for this is that in the second stage the sample covariance is computed
-using patches from the basic estimate, with a much lower noise level.
-In this setting, there is no gain in increasing the number of patches,
-and there seems to be a loss possibly due to the fact that smaller groups of patches
+%
+Note that in this case, the \emph{a
+priori} covariance matrix is estimated from the basic estimate (without having
+to subtract $\sigma^2I$). As a consequence, the are no negative filter coefficients.
+%
+In the second stage the quality drops when
+using a number of patches $n_2$ higher than $100$. This differs from the first stage,
+where a larger $n_1$ yielded a better PSNR.
+The reason for this lies probably in the fact that the patches have less noise,
+and a good estimate of the leading eigenvectors of the covariance matrix can be obtained
+with less patches. Furthermore, smaller groups of patches
 are better modelled by a Gaussian distribution.
-\pcomment{I don't have an explanation for the curves for $\sigma = 10$. Precisely
-in the lower noise level, the PSNR drops when $n_2$ is reduced, except for lower ranks.
-This contradicts the argument given: for less noise, it should be always better to consider
-less patches, not only for lower ranks.}
-
-So far we have studied the parameters affecting the MAP estimation for each stage 
-independently. However, to determine the optimal parameters, we need to look at
-them jointly. The first stage parameters maximizing the PSNR of the basic
-estimate, yield a suboptimal result in terms of the end PSNR.
-%
-Figure \ref{fig:rank1-nsim1-bpsnr-fpsnr} plots for the PSNR of the first and
-second stages obtained when varying $n_1$ and $r_1$ as in Figure
-\ref{fig:rank1-nsim1-bpsnr}. It can be observed, that the 
-results with the highest basic and final PSNR do not coincide.
-%
-The aims of the first and second stage are different: the output 
-of the first stage is used as an oracle in the second stage. As such, it can
-have more variance but it should have a small bias. The reason is that the
-second stage is robust to some noise in the basic estimate, but
-the signal components lost in the first stage are harder to recover.
-\pcomment{The figure shows actually the opposite!!}
-
-Due the coupling of the first and second stages, determining the optimal values
-for the ranks $r_1, r_2$ and the number of patches $n_1,n_2$ requires a four
-dimensional parameter search.
-%
-Instead, we fix the first stage parameters at
-\[r_1 = s_{x,1}^2s_{t,1}\quad\quad n_{1} = 400,\]
-which we found to give good results. In doing so, we are being conservative and
-use the full rank covariance matrix to eliminate the least signal components.
-%
-We then run a parameter search to determine $r_2$ and $n_{2}$.
-The results is the ones shown in Figure \ref{fig:rank1-nsim1-fpsnr}. From here
-establish the following values as a function of $\sigma$:
-%\[r_2(\sigma) = 40 - \frac13(\sigma - 10)\quad\quad n_{2} = 150.\]
-\[r_2(\sigma) = 35 - \frac12(\sigma - 10)\quad\quad n_{2} = 100.\]
-Note that a higher value for $n_{2}$ would give slightly worse results,
-at a lower computational cost.
+%\pcomment{I don't have an explanation for the curves for $\sigma = 10$. Precisely
+%in the lower noise level, the PSNR drops when $n_2$ is reduced, except for lower ranks.
+%This contradicts the argument given: for less noise, it should be always better to consider
+%less patches, not only for lower ranks.} 
+Based on these plots, we set the following values for the parameters
+\[r_2(\sigma) = 30 - \frac12(\sigma - 10),\quad\quad n_{2} = 100.\]
+
+All parameters are summarized in Table \ref{tab:parameters}.
+
+%Note that due to the coupling of the first and second stages, determining the
+%optimal values for the ranks $r_1, r_2$ and the number of patches $n_1,n_2$
+%would require a four dimensional parameter search which would be to costly.
+%
+%Instead, we fixed the first stage parameters, both for color and grayscale videos
+%at
+%\[r_1 = s_{x,1}^2s_{t,1}\quad\quad n_{1} = 400,\]
+%which we found to give good results. In doing so, we were conservative and
+%used the full rank covariance matrix to eliminate the least signal components.
+%%
+%We then ran a parameter search to determine $r_2$ and $n_{2}$.
+%The results are the ones shown in Figure \ref{fig:rank1-nsim1-psnr-gray}. This led
+%us to establish the following values as a function of $\sigma$:
+%%\[r_2(\sigma) = 40 - \frac13(\sigma - 10)\quad\quad n_{2} = 150.\]
+%\[r_2(\sigma) = 35 - \frac12(\sigma - 10)\quad\quad n_{2} = 100.\]
+%The same values are used for color and grayscale videos.
+%Note that a higher value for $n_{2}$ would give slightly worse results,
+%at a lower computational cost.
+
+\begin{table}
+	\centering
+	\begin{tabular}{l | c c | c c }
+		& \multicolumn{2}{c|}{color} 
+		& \multicolumn{2}{c}{grayscale}\\
+		Stage                            & 1st    & 2nd   & 1st   & 2nd   \\\hline\hline
+		$s_x$        &  5 & 5 & 7 & 7 \\
+		$s_t$        &  1--4  & 1--4  & 1--4  & 1--4  \\
+		$w_x$        &  37    & 37    & 45    & 45    \\
+		$w_x$        &   5    & 5     & 5     & 5    \\
+		$n$          & 300    & 100   & 300   & 100  \\
+		$r$          & 95   & $30 - \frac12(\sigma - 10)$    & 180  & $30 - \frac12(\sigma - 10)$   \\
+%		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
+%		Beta                        & 1    & 1.2  & 1    & 1.2  & 1    & 1.2 \\\hline
+	\end{tabular}
+	\caption{Selected parameters.}
+	\label{tab:parameters}
+\end{table}
 
@@
 	\begin{center}
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s10_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s20_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s30_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s40_average_derf.eps}\\
-
-		\vspace{1cm}
-		\pcomment{TODO: Figures for grayscale sequences}
-		\vspace{1cm}
-
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s10_average_derf_neg-vs-pos-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s20_average_derf_neg-vs-pos-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s30_average_derf_neg-vs-pos-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s40_average_derf_neg-vs-pos-weights.eps}\\
+
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s10_average_derf_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s20_average_derf_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s30_average_derf_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s40_average_derf_neg-weights.eps}\\
 	\end{center}
-	\caption{Basic estimate PSNR, averaged over four sequences, when varying the
-		second stage parameters $r_1$ and $n_1$. From left to right, results for
-		$\sigma = 10, 20, 30, 40$. In the top row: results for RGB sequences, bottom
-		row, results for grayscale sequences.} 
-	\label{fig:rank1-nsim1-bpsnr}
+	\caption{PSNR averaged over four color sequences, when varying the
+		first stage parameters $r_1$ and $n_1$. Top row, PSNR of the basic
+		estimate; bottom row: final estimate. From left to right, results for
+		$\sigma = 10, 20, 30, 40$.} 
+	\label{fig:rank1-nsim1-psnr-color}
 \end{figure*}
+
+%-% \begin{figure*}[htpb!]
+%-% 	\begin{center}
+%-% 		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s10_average_derf.eps}%
+%-% 		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s20_average_derf.eps}%
+%-% 		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s30_average_derf.eps}%
+%-% 		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s40_average_derf.eps}\\
+%-% 
+%-% 		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s10_average_mono.eps}%
+%-% 		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s20_average_mono.eps}%
+%-% 		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s30_average_mono.eps}%
+%-% 		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s40_average_mono.eps}\\
+%-% 	\end{center}
+%-% 	\caption{PSNRs of final vs. basic estimate. Averages over four sequences, when varying the
+%-% 		second stage parameters $r_1$ and $n_1$. From left to right, results for
+%-% 		$\sigma = 10, 20, 30, 40$. Top: results for RGB sequences; bottom:
+%-% 		results for grayscale sequences. The width of the line is proportional to
+%-% 		the rank. \pcomment{These plots contradict the argument in favour of using
+%-% 		full rank in the first stage (supposedly introducing a higher variance, but a
+%-% 		smaller bias). It turns out, that (1) the final PSNR is pretty much
+%-% 		correlated with the basic PSNR, and (2) the optimal rank for the final
+%-% 		estimate is lower than that of the basic estimate. I do not have an explanation for this.}} 
+%-% 	\label{fig:rank1-nsim1-bpsnr-fpsnr}
+%-% \end{figure*}
 
@@
 	\begin{center}
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s10_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s20_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s30_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr-fpsnr_r1-np1-curves_s40_average_derf.eps}\\
-
-		\vspace{1cm}
-		\pcomment{TODO: Figures for grayscale sequences}
-		\vspace{1cm}
-
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s10_average_mono_neg-vs-pos-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s20_average_mono_neg-vs-pos-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s30_average_mono_neg-vs-pos-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s40_average_mono_neg-vs-pos-weights.eps}\\
+
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s10_average_mono_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s20_average_mono_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s30_average_mono_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s40_average_mono_neg-weights.eps}\\
 	\end{center}
-	\caption{PSNRs of final vs. basic estimate. Averages over four sequences, when varying the
-		second stage parameters $r_1$ and $n_1$. From left to right, results for
-		$\sigma = 10, 20, 30, 40$. Top: results for RGB sequences; bottom:
-		results for grayscale sequences. The width of the line is proportional to
-		the rank. \pcomment{These plots contradict the argument in favour of using
-		full rank in the first stage (supposedly introducing a higher variance, but a
-		smaller bias). It turns out, that (1) the final PSNR is pretty much
-		correlated with the basic PSNR, and (2) the optimal rank for the final
-		estimate is lower than that of the basic estimate. I do not have an explanation for this.}} 
-	\label{fig:rank1-nsim1-bpsnr-fpsnr}
+	\caption{PSNR averaged over four grayscale sequences, when varying the
+		first stage parameters $r_1$ and $n_1$. Top row, PSNR of the basic
+		estimate; bottom row: final estimate. From left to right, results for
+		$\sigma = 10, 20, 30, 40$.} 
+	\label{fig:rank1-nsim1-psnr-gray}
 \end{figure*}
@@
 	\begin{center}
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s10_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s20_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s30_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s40_average_derf.eps}\\
-
-		\vspace{1cm}
-		\pcomment{TODO: Figures for grayscale sequences}
-		\vspace{1cm}
-
-	\end{center}
-	\caption{Final estimate PSNR, averaged over four sequences, when varying the
-		second stage parameters $r_1$ and $n_1$. From left to right, results for
-		$\sigma = 10, 20, 30, 40$. In the top row: results for RGB sequences, bottom
-		row, results for grayscale sequences.} 
-	\label{fig:rank1-nsim1-fpsnr}
-\end{figure*}
-
-\begin{figure*}[htpb!]
-	\begin{center}
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s10_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s20_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s30_average_derf.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s40_average_derf.eps}\\
-
-		\vspace{1cm}
-		\pcomment{TODO: Figures for grayscale sequences}
-		\vspace{1cm}
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s10_average_derf_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s20_average_derf_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s30_average_derf_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s40_average_derf_neg-weights.eps}\\
+
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s10_average_mono_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s20_average_mono_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s30_average_mono_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s40_average_mono_neg-weights.eps}\\
 
@@
 	\begin{center}
-		{%\small
+		{\small
 		\renewcommand{\tabcolsep}{1.6mm}
 		\renewcommand{\arraystretch}{1.3}
-		\begin{tabular}{ c | l |c c | c c | c c | c c | c c | c c}
+		\begin{tabular}{ c | l |c c | c c | c c | c c | c c | c}
 			\hline
-			\rule{0pt}{10pt}$\sigma$ & Method            & \multicolumn{2}{c}{Tennis}  & \multicolumn{2}{c}{Coastguard}&\multicolumn{2}{c}{Foreman}& \multicolumn{2}{c}{Bus}     &\multicolumn{2}{c|}{Football}& \multicolumn{2}{c}{Average}\\\hline
+			\rule{0pt}{10pt}$\sigma$ & Method            & \multicolumn{2}{c}{Tennis}  & \multicolumn{2}{c}{Coastguard}&\multicolumn{2}{c}{Foreman}& \multicolumn{2}{c}{Bus}     &\multicolumn{2}{c|}{Football}& Average\\\hline
 			\multirow{1}{*}{$ 5$}
-%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
-			                      & V-BM3D               & \bsic{     } &       39.45  & \bsic{     } &       40.18  & \bsic{     } &       40.16  & \bsic{     } &       39.07  & \bsic{     } &              & \bsic{     } &              \\
-			                      & V-BM4D-tip           & \bsic{     } & \best{39.98} & \bsic{     } & \best{41.13} & \bsic{     } & \best{41.38} & \bsic{     } & \best{40.21} & \bsic{     } & \best{     } & \bsic{     } & \best{     } \\
-			                      & V-BM4D-mp            & \bsic{39.61} &       39.60  & \bsic{40.20} &       40.28  & \bsic{40.73} &       40.78  & \bsic{39.45} &       39.56  & \bsic{39.91} &       40.00  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{38.73} &       39.26  & \bsic{40.90} &       41.38  & \bsic{41.19} &       41.82  & \bsic{39.85} &       40.32  & \bsic{41.10} &       41.64  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 2$     & \bsic{39.56} &       40.05  & \bsic{41.61} &       42.08  & \bsic{41.75} &       42.42  & \bsic{40.10} &       40.73  & \bsic{41.29} &       41.88  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \bsic{39.82} &       40.16  & \Bsic{41.75} &       42.39  & \Bsic{41.85} &       42.57  & \Bsic{40.16} &       40.96  & \Bsic{41.27} &       41.85  & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{39.92} & \Best{40.03} & \Bsic{41.76} & \Best{42.41} & \Bsic{41.84} & \Best{42.48} & \Bsic{40.18} & \Best{40.92} & \Bsic{41.23} & \Best{41.67} & \Bsic{todo } & \Best{todo } \\\hline
+%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              &              \\
+			                      & V-BM3D               & \bsic{     } &       39.45  & \bsic{     } &       40.18  & \bsic{     } &       40.16  & \bsic{     } &       39.07  & \bsic{     } &              &       39.71  \\
+			                      & V-BM4D-tip           & \bsic{     } & \best{39.98} & \bsic{     } & \best{41.13} & \bsic{     } & \best{41.38} & \bsic{     } & \best{40.21} & \bsic{     } & \best{     } & \best{40.68} \\
+			                      & V-BM4D-mp            & \bsic{39.61} &       39.60  & \bsic{40.20} &       40.28  & \bsic{40.73} &       40.78  & \bsic{39.45} &       39.56  & \bsic{39.91} &       40.00  &       40.06  \\
+			                      & VNLB   $s_t = 1$     & \bsic{38.83} &       39.37  & \bsic{41.05} &       41.49  & \bsic{41.41} &       41.95  & \bsic{40.05} &       40.43  & \bsic{41.30} &       41.75  &       40.81  \\
+			                      & VNLB   $s_t = 2$     & \bsic{39.70} & \Best{40.15} & \bsic{41.76} &       42.25  & \bsic{42.01} & \Best{42.56} & \bsic{40.33} &       40.97  & \bsic{41.50} & \Best{41.97} &       41.48  \\
+			                      & VNLB   $s_t = 3$     & \bsic{40.00} & \Best{40.16} & \Bsic{41.94} & \Best{42.45} & \Bsic{42.14} & \Best{42.61} & \Bsic{40.43} & \Best{41.12} & \Bsic{41.50} & \Best{41.85} & \Best{41.59} \\
+			                      & VNLB   $s_t = 4$     & \Bsic{40.11} &      {40.01} & \Bsic{41.95} & \Best{42.38} & \Bsic{42.15} &       42.48  & \Bsic{40.47} &       41.02  & \Bsic{41.44} &      {41.61} &       41.47  \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{38.73} &       39.26  & \bsic{40.90} &       41.38  & \bsic{41.19} &       41.82  & \bsic{39.85} &       40.32  & \bsic{41.10} &       41.64  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{39.56} &       40.05  & \bsic{41.61} &       42.08  & \bsic{41.75} &       42.42  & \bsic{40.10} &       40.73  & \bsic{41.29} &       41.88  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{39.82} &       40.16  & \Bsic{41.75} &       42.39  & \Bsic{41.85} &       42.57  & \Bsic{40.16} &       40.96  & \Bsic{41.27} &       41.85  & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{39.92} & \Best{40.03} & \Bsic{41.76} & \Best{42.41} & \Bsic{41.84} & \Best{42.48} & \Bsic{40.18} & \Best{40.92} & \Bsic{41.23} & \Best{41.67} & \Bsic{todo } & \Best{todo } \\\hline
 %
 			\multirow{1}{*}{$10$}
-%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
-			                      & V-BM3D               & \bsic{     } &       36.04  & \bsic{     } &       36.82  & \bsic{     } &       37.52  & \bsic{     } &       34.96  & \bsic{     } &              & \bsic{     } &              \\
-			                      & V-BM4D-tip           & \bsic{     } & \best{36.42} & \bsic{     } & \best{37.27} & \bsic{     } &       37.92  & \bsic{     } &       36.23  & \bsic{     } &              & \bsic{     } &              \\
-			                      & V-BM4D-mp            & \bsic{35.64} &       35.90  & \bsic{36.06} &       36.30  & \bsic{36.96} &       37.21  & \bsic{35.10} &       35.38  & \bsic{35.79} &       36.08  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{34.54} &       35.16  & \bsic{36.81} &       37.23  & \bsic{37.25} &       38.01  & \bsic{35.47} &       36.21  & \bsic{36.88} &       37.69  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 2$     & \bsic{35.67} &       36.28  & \bsic{37.42} &       38.10  & \Bsic{37.87} &       38.82  & \Bsic{35.82} &       36.69  & \Bsic{37.11} &       38.02  & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \bsic{35.94} &       36.61  & \Bsic{37.56} &       38.50  & \Bsic{37.93} &       39.08  & \Bsic{35.88} &       36.98  & \Bsic{37.03} &       38.08  & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{36.02} & \Best{36.73} & \Bsic{37.50} & \Best{38.64} & \Bsic{37.83} & \Best{39.12} & \Bsic{35.87} & \Best{37.11} & \Bsic{36.91} & \Best{38.03} & \Bsic{todo } & \Best{todo } \\\hline
+%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              &              \\
+			                      & V-BM3D               & \bsic{     } &       36.04  & \bsic{     } &       36.82  & \bsic{     } &       37.52  & \bsic{     } &       34.96  & \bsic{     } &              &       36.34  \\
+			                      & V-BM4D-tip           & \bsic{     } & \best{36.42} & \bsic{     } & \best{37.27} & \bsic{     } &       37.92  & \bsic{     } &       36.23  & \bsic{     } &              &       36.96  \\
+			                      & V-BM4D-mp            & \bsic{35.64} &       35.90  & \bsic{36.06} &       36.30  & \bsic{36.96} &       37.21  & \bsic{35.10} &       35.38  & \bsic{35.79} &       36.08  &       36.20  \\
+			                      & VNLB   $s_t = 1$     & \bsic{34.67} &       35.30  & \bsic{36.95} &       37.30  & \bsic{37.47} &       38.16  & \bsic{35.81} &       36.38  & \bsic{37.17} &       37.81  &       36.78  \\
+			                      & VNLB   $s_t = 2$     & \bsic{35.88} &       36.42  & \bsic{37.68} &       38.27  & \bsic{38.26} &       39.02  & \bsic{36.24} &       36.97  & \Bsic{37.46} & \Best{38.17} &       37.67  \\
+			                      & VNLB   $s_t = 3$     & \bsic{36.20} &       36.72  & \Bsic{37.89} &       38.63  & \Bsic{38.39} & \Best{39.24} & \Bsic{36.38} & \Best{37.25} & \Bsic{37.43} & \Best{38.18} & \Best{37.96} \\
+			                      & VNLB   $s_t = 4$     & \Bsic{36.31} & \Best{36.81} & \Bsic{37.91} & \Best{38.73} & \Bsic{38.40} & \Best{39.24} & \Bsic{36.42} & \Best{37.34} & \Bsic{37.34} &       38.07  & \Best{38.03} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{34.54} &       35.16  & \bsic{36.81} &       37.23  & \bsic{37.25} &       38.01  & \bsic{35.47} &       36.21  & \bsic{36.88} &       37.69  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{35.67} &       36.28  & \bsic{37.42} &       38.10  & \Bsic{37.87} &       38.82  & \Bsic{35.82} &       36.69  & \Bsic{37.11} &       38.02  & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{35.94} &       36.61  & \Bsic{37.56} &       38.50  & \Bsic{37.93} &       39.08  & \Bsic{35.88} &       36.98  & \Bsic{37.03} &       38.08  & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{36.02} & \Best{36.73} & \Bsic{37.50} & \Best{38.64} & \Bsic{37.83} & \Best{39.12} & \Bsic{35.87} & \Best{37.11} & \Bsic{36.91} & \Best{38.03} & \Bsic{todo } & \Best{todo } \\\hline
 %
 			\multirow{1}{*}{$15$}
-			                      & CIFIC                & \bsic{     } &       32.76  & \bsic{     } &              & \bsic{     } &              & \bsic{     } &       33.47  & \bsic{     } &       31.59  & \bsic{     } &              \\
-%			                      & V-BM3D               & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
-%			                      & V-BM4D-tip           & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } \\
-			                      & V-BM4D-mp            & \bsic{33.10} &       33.67  & \bsic{33.66} &       34.05  & \bsic{34.78} &       35.17  & \bsic{32.59} &       33.02  & \bsic{33.34} &       33.82  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{32.31} &       32.94  & \bsic{34.32} &       34.95  & \bsic{35.06} &       35.97  & \bsic{33.04} &       33.83  & \bsic{34.62} &       35.50  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 2$     & \bsic{33.36} &       34.12  & \bsic{35.24} &       36.03  & \bsic{35.74} &       36.82  & \bsic{33.39} &       34.29  & \bsic{34.83} &       35.83  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \bsic{33.59} &       34.58  & \Bsic{35.33} &       36.38  & \Bsic{35.74} &       37.05  & \Bsic{33.42} &       34.57  & \Bsic{34.72} &       35.88  & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{33.64} & \Best{34.78} & \Bsic{35.21} & \Best{36.52} & \Bsic{35.57} & \Best{37.11} & \Bsic{33.37} & \Best{34.76} & \Bsic{34.54} & \Best{35.86} & \Bsic{todo } & \Best{todo } \\\hline
-%
+			                      & CIFIC                & \bsic{     } &       32.76  & \bsic{     } &              & \bsic{     } &              & \bsic{     } &       33.47  & \bsic{     } &       31.59  &              \\
+%			                      & V-BM3D               & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              &              \\
+%			                      & V-BM4D-tip           & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \best{     } \\
+			                      & V-BM4D-mp            & \bsic{33.10} &       33.67  & \bsic{33.66} &       34.05  & \bsic{34.78} &       35.17  & \bsic{32.59} &       33.02  & \bsic{33.34} &       33.82  &       33.98  \\
+			                      & VNLB   $s_t = 1$     & \bsic{32.43} &       33.05  & \bsic{34.44} &       35.05  & \bsic{35.26} &       36.07  & \bsic{33.41} &       34.00  & \bsic{34.90} &       35.59  &       34.54  \\
+			                      & VNLB   $s_t = 2$     & \bsic{33.60} &       34.31  & \bsic{35.55} &       36.17  & \bsic{36.17} &       36.99  & \bsic{33.85} &       34.61  & \Bsic{35.23} & \Best{35.98} &       35.52  \\
+			                      & VNLB   $s_t = 3$     & \bsic{33.98} &       34.72  & \Bsic{35.75} &       36.51  & \Bsic{36.28} & \Best{37.19} & \Bsic{33.97} &       34.96  & \Bsic{35.19} & \Best{36.00} &       35.85  \\
+			                      & VNLB   $s_t = 4$     & \Bsic{34.13} & \Best{34.88} & \Bsic{35.77} & \Best{36.62} & \Bsic{36.30} & \Best{37.22} & \Bsic{34.01} & \Best{35.13} & \bsic{35.10} & \Best{35.93} & \Best{35.96} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{32.31} &       32.94  & \bsic{34.32} &       34.95  & \bsic{35.06} &       35.97  & \bsic{33.04} &       33.83  & \bsic{34.62} &       35.50  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{33.36} &       34.12  & \bsic{35.24} &       36.03  & \bsic{35.74} &       36.82  & \bsic{33.39} &       34.29  & \bsic{34.83} &       35.83  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{33.59} &       34.58  & \Bsic{35.33} &       36.38  & \Bsic{35.74} &       37.05  & \Bsic{33.42} &       34.57  & \Bsic{34.72} &       35.88  & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{33.64} & \Best{34.78} & \Bsic{35.21} & \Best{36.52} & \Bsic{35.57} & \Best{37.11} & \Bsic{33.37} & \Best{34.76} & \Bsic{34.54} & \Best{35.86} & \Bsic{todo } & \Best{todo } \\\hline
 			\multirow{1}{*}{$20$}
-%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
-			                      & V-BM3D               & \bsic{     } &       32.54  & \bsic{     } &       33.39  & \bsic{     } &       34.49  & \bsic{     } &       31.03  & \bsic{     } &              & \bsic{     } &              \\
-			                      & V-BM4D-tip           & \bsic{     } & \best{32.88} & \bsic{     } & \best{33.61} & \bsic{     } & \best{34.62} & \bsic{     } & \best{32.27} & \bsic{     } & \best{     } & \bsic{     } & \best{     } \\
-			                      & V-BM4D-mp            & \bsic{31.33} &       31.98  & \bsic{31.91} &       32.44  & \bsic{33.16} &       33.70  & \bsic{30.81} &       31.34  & \bsic{31.58} &       32.22  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{30.78} &       31.38  & \bsic{32.95} &       33.45  & \bsic{33.71} &       34.37  & \bsic{31.60} &       32.19  & \bsic{33.20} &       33.85  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 2$     & \bsic{32.13} &       32.69  & \bsic{33.98} &       34.36  & \bsic{34.55} &       35.41  & \bsic{32.13} &       32.80  & \bsic{33.52} &       34.27  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \bsic{32.53} &       33.12  & \Bsic{34.14} &       34.74  & \Bsic{34.69} &       35.75  & \Bsic{32.27} &       33.13  & \Bsic{33.50} &       34.35  & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{32.67} & \Best{33.32} & \Bsic{34.13} & \Best{34.92} & \Bsic{34.60} & \Best{35.86} & \Bsic{32.31} & \Best{33.34} & \Bsic{33.41} & \Best{34.34} & \Bsic{todo } & \Best{todo } \\\hline
+%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              &              \\
+			                      & V-BM3D               & \bsic{     } &       32.54  & \bsic{     } &       33.39  & \bsic{     } &       34.49  & \bsic{     } &       31.03  & \bsic{     } &              &       32.86  \\
+			                      & V-BM4D-tip           & \bsic{     } & \best{32.88} & \bsic{     } & \best{33.61} & \bsic{     } & \best{34.62} & \bsic{     } & \best{32.27} & \bsic{     } & \best{     } & \best{33.35} \\
+			                      & V-BM4D-mp            & \bsic{31.33} &       31.98  & \bsic{31.91} &       32.44  & \bsic{33.16} &       33.70  & \bsic{30.81} &       31.34  & \bsic{31.58} &       32.22  &       32.37  \\
+			                      & VNLB   $s_t = 1$     & \bsic{30.81} &       31.54  & \bsic{32.96} &       33.56  & \bsic{33.71} &       34.47  & \bsic{31.63} &       32.36  & \bsic{33.19} &       33.95  &       32.98  \\
+			                      & VNLB   $s_t = 2$     & \bsic{32.14} &       32.87  & \bsic{33.96} &       34.49  & \bsic{34.52} &       35.58  & \bsic{32.16} &       33.07  & \Bsic{33.51} & \Best{34.42} &       34.00  \\
+			                      & VNLB   $s_t = 3$     & \bsic{32.52} &       33.23  & \Bsic{34.10} &       34.89  & \Bsic{34.62} & \Best{35.86} & \Bsic{32.29} &       33.40  & \Bsic{33.47} & \Best{34.45} &       34.35  \\
+			                      & VNLB   $s_t = 4$     & \Bsic{32.67} & \Best{33.39} & \Bsic{34.13} & \Best{35.04} & \Bsic{34.66} & \Best{35.91} & \Bsic{32.33} & \Best{33.58} & \Bsic{33.42} & \Best{34.38} & \Best{34.48} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{30.78} &       31.38  & \bsic{32.95} &       33.45  & \bsic{33.71} &       34.37  & \bsic{31.60} &       32.19  & \bsic{33.20} &       33.85  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{32.13} &       32.69  & \bsic{33.98} &       34.36  & \bsic{34.55} &       35.41  & \bsic{32.13} &       32.80  & \bsic{33.52} &       34.27  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{32.53} &       33.12  & \Bsic{34.14} &       34.74  & \Bsic{34.69} &       35.75  & \Bsic{32.27} &       33.13  & \Bsic{33.50} &       34.35  & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{32.67} & \Best{33.32} & \Bsic{34.13} & \Best{34.92} & \Bsic{34.60} & \Best{35.86} & \Bsic{32.31} & \Best{33.34} & \Bsic{33.41} & \Best{34.34} & \Bsic{todo } & \Best{todo } \\\hline
+%
 %
 			\multirow{1}{*}{$25$}
-			                      & CIFIC                & \bsic{     } &       29.74  & \bsic{     } &              & \bsic{     } &              & \bsic{     } &       30.48  & \bsic{     } &       28.82  & \bsic{     } &              \\
-%			                      & V-BM3D               & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
-%			                      & V-BM4D-tip           & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } \\
-			                      & V-BM4D-mp            & \bsic{30.01} &       30.73  & \bsic{30.60} &       31.24  & \bsic{31.91} &       32.59  & \bsic{29.46} &       30.07  & \bsic{30.22} &       30.96  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{29.67} &       30.27  & \bsic{31.51} &       32.18  & \bsic{32.43} &       33.30  & \bsic{30.39} &       30.95  & \bsic{31.92} &       32.74  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 2$     & \bsic{30.88} &       31.57  & \bsic{32.79} &       33.40  & \bsic{33.46} &       34.30  & \bsic{30.89} &       31.50  & \bsic{32.34} &       33.16  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \bsic{31.30} &       32.05  & \Bsic{33.00} &       33.73  & \Bsic{33.60} &       34.61  & \Bsic{31.01} &       31.83  & \Bsic{32.32} &       33.22  & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{31.44} & \Best{32.30} & \Bsic{32.97} & \Best{33.88} & \Bsic{33.51} & \Best{34.73} & \Bsic{31.02} & \Best{32.05} & \Bsic{32.20} & \Best{33.21} & \Bsic{todo } & \Best{todo } \\\hline
+			                      & CIFIC                & \bsic{     } &       29.74  & \bsic{     } &              & \bsic{     } &              & \bsic{     } &       30.48  & \bsic{     } &       28.82  &              \\
+%			                      & V-BM3D               & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              &              \\
+%			                      & V-BM4D-tip           & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \bsic{     } & \best{     } & \best{     } \\
+			                      & V-BM4D-mp            & \bsic{30.01} &       30.73  & \bsic{30.60} &       31.24  & \bsic{31.91} &       32.59  & \bsic{29.46} &       30.07  & \bsic{30.22} &       30.96  &       31.16  \\
+			                      & VNLB   $s_t = 1$     & \bsic{29.69} &       30.41  & \bsic{31.51} &       32.30  & \bsic{32.41} &       33.39  & \bsic{30.41} &       31.10  & \bsic{31.91} &       32.81  &       31.80  \\
+			                      & VNLB   $s_t = 2$     & \bsic{30.88} &       31.76  & \bsic{32.75} &       33.54  & \bsic{33.42} &       34.41  & \bsic{30.91} &       31.78  & \Bsic{32.32} & \Best{33.27} &       32.87  \\
+			                      & VNLB   $s_t = 3$     & \bsic{31.27} &       32.18  & \Bsic{32.93} &       33.85  & \Bsic{33.52} & \Best{34.72} & \Bsic{31.01} &       32.12  & \Bsic{32.28} & \Best{33.30} &       33.22  \\
+			                      & VNLB   $s_t = 4$     & \Bsic{31.47} & \Best{32.39} & \Bsic{32.99} & \Best{33.97} & \Bsic{33.59} & \Best{34.79} & \Bsic{31.05} & \Best{32.32} & \Bsic{32.23} & \Best{33.26} & \Best{33.37} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{29.67} &       30.27  & \bsic{31.51} &       32.18  & \bsic{32.43} &       33.30  & \bsic{30.39} &       30.95  & \bsic{31.92} &       32.74  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{30.88} &       31.57  & \bsic{32.79} &       33.40  & \bsic{33.46} &       34.30  & \bsic{30.89} &       31.50  & \bsic{32.34} &       33.16  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{31.30} &       32.05  & \Bsic{33.00} &       33.73  & \Bsic{33.60} &       34.61  & \Bsic{31.01} &       31.83  & \Bsic{32.32} &       33.22  & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{31.44} & \Best{32.30} & \Bsic{32.97} & \Best{33.88} & \Bsic{33.51} & \Best{34.73} & \Bsic{31.02} & \Best{32.05} & \Bsic{32.20} & \Best{33.21} & \Bsic{todo } & \Best{todo } \\\hline
 %
 			\multirow{1}{*}{$40$}
-%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              \\
-			                      & V-BM3D               & \bsic{     } &       29.20  & \bsic{     } & \best{29.99} & \bsic{     } &       31.17  & \bsic{     } &       27.34  & \bsic{     } &              & \bsic{     } &              \\
-			                      & V-BM4D-tip           & \bsic{     } & \best{29.52} & \bsic{     } & \best{30.00} & \bsic{     } & \best{31.30} & \bsic{     } &       28.32  & \bsic{     } &              & \bsic{     } &              \\
-			                      & V-BM4D-mp            & \bsic{27.34} &       28.14  & \bsic{27.81} &       28.73  & \bsic{29.01} &       30.09  & \bsic{26.67} &       27.44  & \bsic{27.45} &       28.35  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{27.17} &       28.04  & \bsic{28.80} &       29.72  & \bsic{29.72} &       30.85  & \bsic{27.64} &       28.32  & \bsic{29.13} &       30.11  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 2$     & \bsic{28.43} &       29.38  & \bsic{30.16} &       31.03  & \bsic{30.84} &       32.09  & \bsic{28.21} &       29.07  & \bsic{29.63} &       30.67  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \Bsic{28.84} &       29.83  & \Bsic{30.40} &       31.32  & \Bsic{30.99} &       32.50  & \Bsic{28.31} &       29.38  & \Bsic{29.64} &       30.76  & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{28.97} & \Best{30.05} & \Bsic{30.36} & \Best{31.45} & \Bsic{30.89} & \Best{32.65} & \Bsic{28.29} & \Best{29.57} & \Bsic{29.52} & \Best{30.76} & \Bsic{todo } & \Best{todo } \\\hline
+%			                      & CIFIC                & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              & \bsic{     } &              &              \\
+			                      & V-BM3D               & \bsic{     } &       29.20  & \bsic{     } & \best{29.99} & \bsic{     } &       31.17  & \bsic{     } &       27.34  & \bsic{     } &              &       29.43  \\
+			                      & V-BM4D-tip           & \bsic{     } & \best{29.52} & \bsic{     } & \best{30.00} & \bsic{     } & \best{31.30} & \bsic{     } &       28.32  & \bsic{     } &              &       29.78  \\
+			                      & V-BM4D-mp            & \bsic{27.34} &       28.14  & \bsic{27.81} &       28.73  & \bsic{29.01} &       30.09  & \bsic{26.67} &       27.44  & \bsic{27.45} &       28.35  &       28.60  \\
+			                      & VNLB   $s_t = 1$     & \bsic{27.17} &       28.17  & \bsic{28.76} &       29.79  & \bsic{29.66} &       30.86  & \bsic{27.64} &       28.43  & \bsic{29.08} &       30.12  &       29.31  \\
+			                      & VNLB   $s_t = 2$     & \bsic{28.40} &       29.52  & \bsic{30.10} &       31.14  & \bsic{30.77} &       32.19  & \bsic{28.20} &       29.31  & \Bsic{29.59} &       30.75  &       30.54  \\
+			                      & VNLB   $s_t = 3$     & \Bsic{28.78} &       29.89  & \bsic{30.30} &       31.40  & \bsic{30.89} &       32.57  & \Bsic{28.29} &       29.60  & \Bsic{29.58} & \Best{30.82} &       30.87  \\
+			                      & VNLB   $s_t = 4$     & \Bsic{29.07} & \Best{30.11} & \Bsic{30.44} & \Best{31.59} & \Bsic{31.03} & \Best{32.71} & \Bsic{28.35} & \Best{29.79} & \Bsic{29.61} & \Best{30.81} & \Best{31.05} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{27.17} &       28.04  & \bsic{28.80} &       29.72  & \bsic{29.72} &       30.85  & \bsic{27.64} &       28.32  & \bsic{29.13} &       30.11  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{28.43} &       29.38  & \bsic{30.16} &       31.03  & \bsic{30.84} &       32.09  & \bsic{28.21} &       29.07  & \bsic{29.63} &       30.67  & \bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \Bsic{28.84} &       29.83  & \Bsic{30.40} &       31.32  & \Bsic{30.99} &       32.50  & \Bsic{28.31} &       29.38  & \Bsic{29.64} &       30.76  & \Bsic{todo } &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{28.97} & \Best{30.05} & \Bsic{30.36} & \Best{31.45} & \Bsic{30.89} & \Best{32.65} & \Bsic{28.29} & \Best{29.57} & \Bsic{29.52} & \Best{30.76} & \Bsic{todo } & \Best{todo } \\\hline
 		\end{tabular}}
@@
 % for i in $(cat bus_s40_pt*/measures | grep PSNR_final | sed "s/^-PSNR_final\ =\ "//); do  echo "scale=2;(((10^2)*$i)+0.5)/(10^2)" | bc; done
-	\caption{PSNRs obtained for the four classic color test sequences used in
-	\cite{Maggioni2012}. See text for details.}
+	\caption{PSNRs obtained for the classic color test sequences. See text for
+		details.}
 	\label{tab:psnr-classic-color}
@@
 		\renewcommand{\arraystretch}{1.3}
-		\begin{tabular}{ c | l |c c | c c | c c | c c | c c | c c | c c}
+		\begin{tabular}{ c | l |c c | c c | c c | c c | c c | c c | c }
 			\hline
 			\rule{0pt}{6pt}$\sigma$ & Method             & \multicolumn{2}{c}{Tennis}  & \multicolumn{2}{c}{Salesman} &\multicolumn{2}{c}{Fl.
-garden}& \multicolumn{2}{c}{Mobile}  & \multicolumn{2}{c}{Bicycle}  & \multicolumn{2}{c|}{Stefan} & \multicolumn{2}{c}{Average} \\\hline
+garden}& \multicolumn{2}{c}{Mobile}  & \multicolumn{2}{c}{Bicycle}  & \multicolumn{2}{c|}{Stefan} &      Average \\\hline
 			\multirow{1}{*}{$10$}
-			                      & I-SA-BM4D            & \bsic{     } & \Best{36.45} & \bsic{     } & \Best{40.49}  & \bsic{     } & \Best{34.46}  & \bsic{     } & \Best{37.03} &              &               &              &              & \bsic{     } &       37.13  \\
-			                      & V-BM4D-tip           & \bsic{     } &       35.22  & \bsic{     } &       37.30   & \bsic{     } &       32.81   &              &              &              &       37.66   &              &              & \bsic{     } &       35.11  \\
-			                      & V-BM4D-mp            & \Bsic{34.32} &       34.95  & \Bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \Bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       33.29  & \bsic{34.62} &       35.15   & \bsic{30.80} &       31.22   & \bsic{32.34} &       32.79  & \bsic{36.21} &       37.72   & \bsic{33.20} &       33.79  & \bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 2$     & \Bsic{34.35} &       34.68  & \bsic{35.87} &       36.62   & \bsic{32.41} &       32.92   & \Bsic{34.26} &       34.78  & \bsic{36.86} & \Best{38.55}  & \Bsic{33.73} & \Best{34.38} & \Bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 3$     & \Bsic{34.34} &       35.23  & \bsic{35.63} &       37.08   & \bsic{32.39} &       33.18   & \bsic{34.02} &       35.25  & \bsic{36.57} & \Best{38.45}  & \bsic{33.45} & \Best{34.36} & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \Bsic{34.25} &       35.40  & \bsic{35.39} &       37.21   & \Bsic{32.54} &       33.10   & \bsic{34.03} &       35.48  & \bsic{36.05} &       38.27   & \bsic{33.39} &       34.10  & \bsic{todo } &       todo   \\\hline
-%			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} & \Bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  & \bsic{todo } &       todo   \\\hline
+			                      & I-SA-BM4D            & \bsic{     } & \Best{36.45} & \bsic{     } & \Best{40.49}  & \bsic{     } & \Best{34.46}  & \bsic{     } & \Best{37.03} &              &               &              &              &              \\
+			                      & V-BM4D-tip           & \bsic{     } &       35.22  & \bsic{     } &       37.30   & \bsic{     } &       32.81   &              &              &              &       37.66   &              &              &       35.75  \\
+			                      & V-BM4D-mp            & \bsic{34.32} &       34.95  & \Bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \Bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  &       35.57  \\
+			                      & VNLB   $s_t = 1$     & \bsic{33.26} &       33.71  & \bsic{34.84} &       35.51   & \bsic{30.86} &       31.62   & \bsic{32.40} &       33.14  & \bsic{36.83} &       38.22   & \bsic{33.33} &       34.07  &       34.77  \\
+			                      & VNLB   $s_t = 2$     & \bsic{34.54} &       35.05  & \bsic{36.05} &       36.89   & \bsic{32.38} &       33.19   & \bsic{34.21} &       35.03  & \bsic{37.34} & \Best{38.80}  & \Bsic{33.80} & \Best{34.64} &       35.98  \\
+			                      & VNLB   $s_t = 3$     & \bsic{34.88} &       35.50  & \bsic{36.25} &       37.45   & \Bsic{32.80} &       33.38   & \Bsic{34.75} &       35.57  & \bsic{37.16} & \Best{38.88}  & \Bsic{33.88} & \Best{34.60} & \Best{36.30} \\
+			                      & VNLB   $s_t = 4$     & \Bsic{34.99} &       35.66  & \bsic{36.32} &       37.56   & \Bsic{32.79} &       33.31   & \Bsic{34.80} &       35.74  & \bsic{37.15} &      {38.75}  & \bsic{33.78} &       34.36  & \Best{36.32} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{33.16} &       33.65  & \bsic{34.69} &       35.43   & \bsic{30.74} &       31.47   & \bsic{32.18} &       33.00  & \bsic{36.75} &       38.14   & \bsic{33.21} &       33.98  &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{34.49} &       35.01  & \bsic{36.02} &       36.82   & \bsic{32.26} &       33.15   & \bsic{34.05} &       34.87  & \bsic{37.36} & \Best{38.69}  & \bsic{33.70} & \Best{34.56} &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{34.89} &       35.49  & \bsic{36.40} &       37.40   & \bsic{32.70} &       33.49   & \bsic{34.68} &       35.47  & \bsic{37.30} & \Best{38.76}  & \Bsic{33.81} & \Best{34.64} &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{35.03} &       35.70  & \bsic{36.35} &       37.63   & \Bsic{32.86} &       33.52   & \Bsic{34.91} &       35.73  & \bsic{37.06} & \Best{38.74}  & \Bsic{33.81} &       34.51  &       todo   \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       33.29  & \bsic{34.62} &       35.15   & \bsic{30.80} &       31.22   & \bsic{32.34} &       32.79  & \bsic{36.21} &       37.72   & \bsic{33.20} &       33.79  &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \Bsic{34.35} &       34.68  & \bsic{35.87} &       36.62   & \bsic{32.41} &       32.92   & \Bsic{34.26} &       34.78  & \bsic{36.86} & \Best{38.55}  & \Bsic{33.73} & \Best{34.38} &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \Bsic{34.34} &       35.23  & \bsic{35.63} &       37.08   & \bsic{32.39} &       33.18   & \bsic{34.02} &       35.25  & \bsic{36.57} & \Best{38.45}  & \bsic{33.45} & \Best{34.36} &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{34.25} &       35.40  & \bsic{35.39} &       37.21   & \Bsic{32.54} &       33.10   & \bsic{34.03} &       35.48  & \bsic{36.05} &       38.27   & \bsic{33.39} &       34.10  &       todo   \\\hline
+%%			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} &       todo   \\
+%%			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} &       todo   \\
+%%			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  &       todo   \\\hline
 %
 			\multirow{1}{*}{$20$}
-			                      & I-SA-BM4D            & \bsic{     } & \Best{33.36} & \bsic{     } & \Best{37.52}  & \bsic{     } & \Best{31.35}  & \bsic{     } & \Best{33.47} &              &               &              &              & \bsic{     } &       34.08  \\
-			                      & V-BM4D-tip           & \bsic{     } &       31.59  & \bsic{     } &       33.79   & \bsic{     } &       28.63   &              &              &              &       34.10   &              &              & \bsic{     } &       31.34  \\
-			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \Bsic{32.18} &       33.46   & \Bsic{28.12} &       28.32   & \Bsic{29.67} &       30.49  & \Bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{29.62} &       30.16  & \bsic{30.76} &       31.54   & \bsic{26.17} &       26.56   & \bsic{27.89} &       28.39  & \bsic{32.41} &       33.77   & \bsic{28.69} &       29.26  & \bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 2$     & \Bsic{30.81} &       31.37  & \bsic{31.98} &       33.08   & \bsic{27.89} &       28.41   & \Bsic{29.69} &       30.41  & \bsic{33.17} & \Best{34.97}  & \Bsic{29.32} & \Best{30.00} & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 3$     & \bsic{29.88} &       31.62  & \bsic{30.60} &       33.05   & \bsic{27.50} &       28.89   & \bsic{29.02} &       30.86  & \bsic{31.23} &       34.26   & \bsic{28.51} & \Best{30.08} & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \bsic{29.49} &       31.64  & \bsic{30.10} &       32.94   & \bsic{27.47} &       29.07   & \bsic{28.86} &       31.12  & \bsic{30.51} &       33.88   & \bsic{28.26} & \Best{30.03} & \bsic{todo } &       todo   \\\hline
-%			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  & \Bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} & \bsic{todo } &       todo   \\\hline
+			                      & I-SA-BM4D            & \bsic{     } & \Best{33.36} & \bsic{     } & \Best{37.52}  & \bsic{     } & \Best{31.35}  & \bsic{     } & \Best{33.47} &              &               &              &              &              \\
+			                      & V-BM4D-tip           & \bsic{     } &       31.59  & \bsic{     } &       33.79   & \bsic{     } &       28.63   &              &              &              &       34.10   &              &              &       32.03  \\
+			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \Bsic{32.18} &       33.46   & \bsic{28.12} &       28.32   & \bsic{29.67} &       30.49  & \bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  &       31.85  \\
+			                      & VNLB   $s_t = 1$     & \bsic{29.64} &       30.38  & \bsic{30.78} &       31.77   & \bsic{26.25} &       26.91   & \bsic{28.00} &       28.75  & \bsic{32.41} &       33.88   & \bsic{28.74} &       29.52  &       30.74  \\
+			                      & VNLB   $s_t = 2$     & \bsic{30.81} &       31.57  & \bsic{31.93} &       33.29   & \bsic{27.95} &       28.72   & \bsic{29.76} &       30.76  & \bsic{33.10} &       35.17   & \Bsic{29.35} &       30.27  &       32.19  \\
+			                      & VNLB   $s_t = 3$     & \bsic{31.06} &       32.00  & \bsic{31.98} &       33.85   & \Bsic{28.39} &       29.18   & \bsic{30.28} &       31.49  & \Bsic{32.83} & \Best{35.42}  & \Bsic{29.41} & \Best{30.40} &      {32.61} \\
+			                      & VNLB   $s_t = 4$     & \Bsic{31.26} &       32.24  & \Bsic{32.14} &       33.97   & \Bsic{28.41} &       29.32   & \Bsic{30.39} &       31.76  & \Bsic{32.91} &      {35.32}  & \Bsic{29.35} & \Best{30.36} & \Best{32.71} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{29.60} &       30.32  & \bsic{30.74} &       31.71   & \bsic{26.10} &       26.81   & \bsic{27.79} &       28.64  & \bsic{32.40} &       33.82   & \bsic{28.64} &       29.46  &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{30.81} &       31.54  & \bsic{32.01} &       33.24   & \bsic{27.84} &       28.64   & \bsic{29.63} &       30.63  & \bsic{33.20} &       35.05   & \bsic{29.28} &       30.19  &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \Bsic{31.14} &       31.99  & \Bsic{32.23} &       33.81   & \bsic{28.33} &       29.18   & \bsic{30.27} &       31.38  & \bsic{33.09} &       35.29   & \Bsic{29.39} & \Best{30.35} &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{31.19} &       32.22  & \bsic{32.05} &       34.07   & \Bsic{28.49} &       29.36   & \Bsic{30.47} &       31.74  & \bsic{32.72} & \Best{35.30}  & \Bsic{29.35} & \Best{30.35} &       todo   \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{29.62} &       30.16  & \bsic{30.76} &       31.54   & \bsic{26.17} &       26.56   & \bsic{27.89} &       28.39  & \bsic{32.41} &       33.77   & \bsic{28.69} &       29.26  &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \Bsic{30.81} &       31.37  & \bsic{31.98} &       33.08   & \bsic{27.89} &       28.41   & \Bsic{29.69} &       30.41  & \bsic{33.17} & \Best{34.97}  & \Bsic{29.32} & \Best{30.00} &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{29.88} &       31.62  & \bsic{30.60} &       33.05   & \bsic{27.50} &       28.89   & \bsic{29.02} &       30.86  & \bsic{31.23} &       34.26   & \bsic{28.51} & \Best{30.08} &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \bsic{29.49} &       31.64  & \bsic{30.10} &       32.94   & \bsic{27.47} &       29.07   & \bsic{28.86} &       31.12  & \bsic{30.51} &       33.88   & \bsic{28.26} & \Best{30.03} &       todo   \\\hline
+%%			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  &       todo   \\
+%%			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} &       todo   \\
+%%			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} &       todo   \\\hline
 %
 			\multirow{1}{*}{$30$}
-			                      & I-SA-BM4D            & \bsic{     } & \Best{31.62} & \bsic{     } & \Best{36.05}  & \bsic{     } & \Best{29.09}  & \bsic{     } & \Best{30.36} &              &               &              &              & \bsic{     } &       32.25  \\
-			                      & V-BM4D-tip           & \bsic{     } &       29.72  &              &       31.75   & \bsic{     } &       26.29   &              &              &              &       31.83   &              &              & \bsic{     } &       29.25  \\
-			                      & V-BM4D-mp            & \Bsic{28.89} &       29.37  & \Bsic{29.56} &       31.02   & \Bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \Bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{27.32} &       28.20  & \bsic{27.94} &       29.14   & \bsic{23.62} &       23.96   & \bsic{25.42} &       25.82  & \bsic{29.50} &       31.08   & \bsic{26.14} &       26.69  & \bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 2$     & \bsic{28.65} &       29.51  & \Bsic{29.55} &       30.93   & \bsic{25.33} &       25.78   & \Bsic{27.31} &       27.90  & \bsic{30.70} & \Best{32.63}  & \Bsic{26.99} &       27.55  & \Bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 3$     & \bsic{27.49} &       29.71  & \bsic{27.91} &       30.91   & \bsic{24.75} &       26.36   & \bsic{26.30} &       28.43  & \bsic{28.45} &       31.95   & \bsic{25.95} & \Best{27.72} & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \bsic{26.92} &       29.64  & \bsic{27.28} &       30.73   & \bsic{24.60} &       26.60   & \bsic{26.04} &       28.68  & \bsic{27.61} &       31.50   & \bsic{25.57} & \Best{27.71} & \bsic{todo } &       todo   \\\hline
+			                      & I-SA-BM4D            & \bsic{     } & \Best{31.62} & \bsic{     } & \Best{36.05}  & \bsic{     } & \Best{29.09}  & \bsic{     } & \Best{30.36} &              &               &              &              &              \\
+			                      & V-BM4D-tip           & \bsic{     } &       29.72  &              &       31.75   & \bsic{     } &       26.29   &              &              &              &       31.83   &              &              &       29.90  \\
+			                      & V-BM4D-mp            & \bsic{28.89} &       29.37  & \bsic{29.56} &       31.02   & \bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \Bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  &       29.72  \\
+			                      & VNLB   $s_t = 1$     & \bsic{27.31} &       28.32  & \bsic{27.92} &       29.28   & \bsic{23.68} &       24.21   & \bsic{25.49} &       26.12  & \bsic{29.47} &       31.10   & \bsic{26.16} &       26.89  &       28.23  \\
+			                      & VNLB   $s_t = 2$     & \bsic{28.62} &       29.67  & \bsic{29.49} &       31.13   & \bsic{25.38} &       26.05   & \bsic{27.35} &       28.25  & \bsic{30.62} &       32.78   & \bsic{27.01} &       27.79  &       29.91  \\
+			                      & VNLB   $s_t = 3$     & \bsic{28.99} &       30.13  & \bsic{29.86} &       31.79   & \Bsic{25.88} &       26.63   & \bsic{27.98} &       29.08  & \bsic{30.62} &       33.16   & \Bsic{27.17} & \Best{28.03} &       30.43  \\
+			                      & VNLB   $s_t = 4$     & \Bsic{29.47} &       30.47  & \Bsic{30.31} &       32.08   & \Bsic{25.95} &       26.88   & \Bsic{28.17} &       29.46  & \Bsic{30.98} & \Best{33.37}  & \Bsic{27.21} & \Best{28.11} & \Best{30.70} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{27.33} &       28.28  & \bsic{27.96} &       29.26   & \bsic{23.57} &       24.18   & \bsic{25.36} &       26.06  & \bsic{29.53} &       31.04   & \bsic{26.11} &       26.86  &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{28.67} &       29.65  & \bsic{29.59} &       31.10   & \bsic{25.29} &       26.04   & \bsic{27.27} &       28.17  & \bsic{30.74} &       32.69   & \bsic{26.97} &       27.76  &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{29.12} &       30.13  & \Bsic{30.09} &       31.77   & \bsic{25.82} &       26.66   & \bsic{28.00} &       29.01  & \bsic{30.88} &       33.06   & \Bsic{27.17} & \Best{28.01} &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{29.26} &       30.38  & \Bsic{30.13} &       32.11   & \Bsic{26.04} &       26.93   & \Bsic{28.28} &       29.43  & \bsic{30.67} & \Best{33.19}  & \Bsic{27.20} & \Best{28.08} &       todo   \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{27.32} &       28.20  & \bsic{27.94} &       29.14   & \bsic{23.62} &       23.96   & \bsic{25.42} &       25.82  & \bsic{29.50} &       31.08   & \bsic{26.14} &       26.69  &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{28.65} &       29.51  & \Bsic{29.55} &       30.93   & \bsic{25.33} &       25.78   & \Bsic{27.31} &       27.90  & \bsic{30.70} & \Best{32.63}  & \Bsic{26.99} &       27.55  &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{27.49} &       29.71  & \bsic{27.91} &       30.91   & \bsic{24.75} &       26.36   & \bsic{26.30} &       28.43  & \bsic{28.45} &       31.95   & \bsic{25.95} & \Best{27.72} &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \bsic{26.92} &       29.64  & \bsic{27.28} &       30.73   & \bsic{24.60} &       26.60   & \bsic{26.04} &       28.68  & \bsic{27.61} &       31.50   & \bsic{25.57} & \Best{27.71} &       todo   \\\hline
 %
 			\multirow{1}{*}{$40$}
-			                      & I-SA-BM4D            & \bsic{     } & \Best{30.79} & \bsic{     } & \Best{35.12}  & \bsic{     } & \Best{27.56}  & \bsic{     } & \Best{28.93} &              &               &              &              & \bsic{     } &       31.16  \\
-			                      & V-BM4D-tip           & \bsic{     } &       28.49  & \bsic{     } &       30.35   & \bsic{     } &       24.60   &              &              &              &       30.10   &              &              & \bsic{     } &       27.81  \\
-			                      & V-BM4D-mp            & \Bsic{27.67} &       28.38  & \Bsic{27.81} &       29.37   & \Bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \Bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  & \bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 1$     & \bsic{25.65} &       26.83  & \bsic{25.97} &       27.49   & \bsic{21.89} &       22.25   & \bsic{23.57} &       24.11  & \bsic{27.32} &       29.03   & \bsic{24.27} &       24.97  & \bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 2$     & \bsic{27.09} &       28.27  & \bsic{27.67} &       29.46   & \bsic{23.56} &       24.06   & \Bsic{25.48} &       26.17  & \bsic{28.64} & \Best{30.90}  & \Bsic{25.21} &       25.89  & \bsic{todo } &       todo   \\
-										 & VNLB   $s_t = 3$     & \bsic{25.66} &       28.33  & \bsic{25.93} &       29.31   & \bsic{22.84} &       24.65   & \bsic{24.35} &       26.69  & \bsic{26.31} &       30.11   & \bsic{24.11} & \Best{26.08} & \Bsic{todo } &       todo   \\
-			                      & VNLB   $s_t = 4$     & \bsic{24.98} &       28.16  & \bsic{25.18} &       29.03   & \bsic{22.62} &       24.89   & \bsic{23.98} &       26.90  & \bsic{25.41} &       29.59   & \bsic{23.64} & \Best{26.05} & \Bsic{todo } &       todo   \\\hline
-%			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  & \bsic{todo } &       todo   \\
-%			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} & \Bsic{todo } & \Best{todo } \\
-%			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} & \Bsic{todo } & \Best{todo } \\\hline
+			                      & I-SA-BM4D            & \bsic{     } & \Best{30.79} & \bsic{     } & \Best{35.12}  & \bsic{     } & \Best{27.56}  & \bsic{     } & \Best{28.93} &              &               &              &              &              \\
+			                      & V-BM4D-tip           & \bsic{     } &       28.49  & \bsic{     } &       30.35   & \bsic{     } &       24.60   &              &              &              &       30.10   &              &              &       28.39  \\
+			                      & V-BM4D-mp            & \Bsic{27.67} &       28.38  & \bsic{27.81} &       29.37   & \bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  &       28.23  \\
+			                      & VNLB   $s_t = 1$     & \bsic{25.62} &       26.83  & \bsic{25.93} &       27.55   & \bsic{21.93} &       22.35   & \bsic{23.60} &       24.30  & \bsic{27.26} &       29.03   & \bsic{24.28} &       25.06  &       26.44  \\
+			                      & VNLB   $s_t = 2$     & \bsic{27.04} &       28.32  & \bsic{27.59} &       29.59   & \bsic{23.59} &       24.16   & \bsic{25.50} &       26.40  & \bsic{28.55} &       31.04   & \bsic{25.21} &       26.02  &       28.28  \\
+			                      & VNLB   $s_t = 3$     & \Bsic{27.44} &       28.82  & \bsic{28.05} &       30.32   & \bsic{24.12} &       24.76   & \bsic{26.12} &       27.28  & \bsic{28.62} &       31.50   & \bsic{25.42} &       26.31  &       28.85  \\
+			                      & VNLB   $s_t = 4$     & \Bsic{28.08} &       29.24  & \Bsic{28.74} &       30.72   & \Bsic{24.25} &       25.06   & \Bsic{26.40} &       27.82  & \Bsic{29.17} & \Best{31.82}  & \Bsic{25.56} & \Best{26.47} & \Best{29.21} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{25.66} &       26.82  & \bsic{26.01} &       27.53   & \bsic{21.85} &       22.37   & \bsic{23.53} &       24.25  & \bsic{27.37} &       28.97   & \bsic{24.27} &       25.05  &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{27.12} &       28.34  & \bsic{27.73} &       29.58   & \bsic{23.53} &       24.24   & \bsic{25.46} &       26.36  & \bsic{28.71} &       30.96   & \bsic{25.20} &       26.03  &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \Bsic{27.60} &       28.84  & \bsic{28.30} &       30.32   & \bsic{24.09} &       24.90   & \bsic{26.16} &       27.26  & \bsic{28.92} &       31.42   & \Bsic{25.45} &       26.34  &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{27.75} &       29.11  & \Bsic{28.40} &       30.69   & \Bsic{24.31} &       25.19   & \Bsic{26.43} &       27.77  & \bsic{28.73} & \Best{31.57}  & \Bsic{25.50} & \Best{26.45} &       todo   \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{25.65} &       26.83  & \bsic{25.97} &       27.49   & \bsic{21.89} &       22.25   & \bsic{23.57} &       24.11  & \bsic{27.32} &       29.03   & \bsic{24.27} &       24.97  &       todo   \\
+%			                      & VNLB   $s_t = 2$     & \bsic{27.09} &       28.27  & \bsic{27.67} &       29.46   & \bsic{23.56} &       24.06   & \Bsic{25.48} &       26.17  & \bsic{28.64} & \Best{30.90}  & \Bsic{25.21} &       25.89  &       todo   \\
+%			                      & VNLB   $s_t = 3$     & \bsic{25.66} &       28.33  & \bsic{25.93} &       29.31   & \bsic{22.84} &       24.65   & \bsic{24.35} &       26.69  & \bsic{26.31} &       30.11   & \bsic{24.11} & \Best{26.08} &       todo   \\
+%			                      & VNLB   $s_t = 4$     & \bsic{24.98} &       28.16  & \bsic{25.18} &       29.03   & \bsic{22.62} &       24.89   & \bsic{23.98} &       26.90  & \bsic{25.41} &       29.59   & \bsic{23.64} & \Best{26.05} &       todo   \\\hline
+%%			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  &       todo   \\
+%%			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} &      {todo } \\
+%%			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} &      {todo } \\\hline
 		\end{tabular}}
 % Command to print rounded psnrs
-% for i in $(cat bus_s40_pt*/measures | grep PSNR_final | sed "s/^-PSNR_final\ =\ "//); do  echo "scale=2;(((10^2)*$i)+0.5)/(10^2)" | bc; done
+% :r !for i in $(cat /media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/tip_table_1ps7_2ps7/te*/measures | grep PSNR_basic | sed ``s/^-PSNR_basic\ =\ ''//); do  echo ``scale=2;\left( (10^2)*$i)+0.5)/(10^2)'' | bc; done \right)
 	\end{center}
@@
 method on some classical test sequences with Gaussian noise added.
-We consider separatedly the cases of grayscale and color videos.
+We consider separately the cases of grayscale and color videos.
+All results were computed with the parameters shown in Table \ref{tab:parameters}.
+The actual sequences can be downloaded from the project's
+website\footnote{\url{http://dev.ipol.im/~pariasm/video_nlbayes/}} in uncompressed format.
 
@@
 We present denoising results on six classic test sequences used commonly in the
-literature. We compare against two state-of-the-art methods: V-BM4D
+literature. We compared against two state-of-the-art methods: V-BM4D
 \cite{Maggioni2012}, and the method of Li, Zhang and Dai \cite{LiZhangDai2011}
@@
 \cite{LiZhangDai2011}. This method builds uppon BM4D, which in \cite{Maggioni2013}
-is applied to volumetric imagery. The authors explore its applicability to video 
+is applied to volumetric imagery. The authors explored its applicability to video 
 and the results show that it is inferior to V-BM4D, at least 
@@
 \emph{mobile} sequence, for noise of $\sigma = 10, 20, 40$. It can be observed
-that the proposed method preserves more details. It also exhibits a higher
-temporal consistency, as will be shown in \S \ref{sse:temporal-consistency}.
+that the proposed method preserves the fine details betters, such as the thin
+lines of the drawing in the first example, or the calendar numbers in the
+second example. It also exhibits a higher temporal consistency, as will be
+shown in \S \ref{sse:temporal-consistency}.
 
@@
 
-As with grayscale videos, we compare our method with V-BM4D using two parameter profiles:
+As for grayscale videos, we compared our method with V-BM4D using two parameter profiles:
 V-BM4D-tip corresponds to the results reported in \cite{Maggioni2012}, and
@@
 of the implementation available online \cite{bm4dcode}.
-In addition, we also compare our method with CIFIC \cite{Dai2013}, a recent
+In addition, we also compared our method with CIFIC \cite{Dai2013}, a recent
 state-of-the-art method.
@@
 sequences, it can be noticed that some details, such as the wallpaper texture,
-are better preserved by the proposed method. Some artifacts appear around 
-moving objects, for example the hand in the close-up of the racket,
-or the arm holding the racket in the second crop.
-%
-Patches at the boundary between an object moving over a textured background 
-do not have exact matches. In this case, it is likely that patches tracking 
-the moving object are found similar, even if the background texture captured by 
-the patches do not match, creating artifacts on the recovered texture.
+are better preserved by the proposed method. 
+%-% Some artifacts appear around 
+%-% moving objects, for example the hand in the close-up of the racket,
+%-% or the arm holding the racket in the second crop.
+%-% Patches at the boundary between an object moving over a textured background 
+%-% do not have exact matches. In this case, it is likely that patches tracking 
+%-% the moving object are found similar, even if the background texture captured by 
+%-% the patches do not match, creating artifacts on the recovered texture.
 
@@
 An important aspect of the quality of any video processing algorithm is the 
-temporal consistency of the result. Similar to previous works \cite{Liu2010, Sutour2014}
-we evaluate quantitatively the temporal consistency of our denoising results.
-To that aim run VNLB and V-BM4D-mp on four sequences of MPI Sintel's training
+temporal consistency of the result. In line to previous works \cite{Liu2010, Sutour2014}
+we evaluated quantitatively the temporal consistency of our denoising results.
+To that aim we ran VNLB and V-BM4D-mp on four sequences of MPI Sintel's training
 dataset. These are CGI color sequences with ground truth forward optical flow, which we
@@
 between frames $t$ and $t +1$.
-We use the optical flow to evaluate the variations along motion trajectories
-added by the denoising algorithm. To that aim we estimate the derivative along
+We used the optical flow to evaluate the variations along motion trajectories
+added by the denoising algorithm. To that aim we estimated the derivative along
 motion trajectories of the denoising error $e = \widetilde u - u$ as follows:
@@
 domain. The occlusion set $\mathcal K$ is also provided in MPI Sintel's database.
-Note that since the optical flow is sub-pixelic, the value of $e(x + v(x,t),t+1)$
-needs to be interpolated. We use bilinear interpolation.
+Note that since the optical flow has sub-pixel accuracy, the value of $e(x + v(x,t),t+1)$
+needs to be interpolated. We used bilinear interpolation.
 
@@
 Table \ref{tab:sintel} shows the PSNR and the TCE results obatained for four sequences of the
-Sintel's database, and four levels of noise. For non-local Bayes, we show results obtained with 
+Sintel's database, and four levels of noise. For VNLB, we show results obtained with 
 the temporal patch length $s_t$ varying from $1$ to $4$. We can observe that the best results
@@
 	\begin{center}
-		{%\small
+		{\small
 		\renewcommand{\tabcolsep}{1.6mm}
 		\renewcommand{\arraystretch}{1.3}
-%		\begin{tabular}{ c | l |c c | c c | c c | c c | c c}
-%			\hline
-%			\rule{0pt}{10pt}         & Sequence          &\multicolumn{2}{c|}{Bamboo 1}&\multicolumn{2}{c|}{Bandage 1}&\multicolumn{2}{c|}{Cave 4} &\multicolumn{2}{c|}{Market 5}& \multicolumn{2}{c}{Average} \\
-%			\rule{0pt}{10pt}$\sigma$ & Method            & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         & TCE          & PSNR         \\\hline
-%			\multirow{1}{*}{$10$}
-%			                      & V-BM4D-mp            & \bsic{37.47} &       38.85  & \bsic{38.67} &       40.02  & \bsic{37.30} &       38.40  & \bsic{39.52} &       40.41  & \bsic{38.24} &       39.42  \\
-%			                      & VNLB   $s_t = 1$     & \bsic{37.48} &       39.74  & \bsic{39.85} &       41.83  & \Bsic{38.80} & \Best{40.82} & \Bsic{42.16} & \Best{44.10} & \bsic{39.57} &       41.62  \\
-%			                      & VNLB   $s_t = 2$     & \bsic{39.01} &       41.10  & \Bsic{40.74} & \Best{42.40} & \bsic{38.70} &       40.65  & \Bsic{42.23} & \Best{44.14} & \Bsic{40.17} & \Best{42.07} \\
-%			                      & VNLB   $s_t = 3$     & \bsic{39.40} & \Best{41.37} & \Bsic{40.74} & \Best{42.36} & \bsic{38.50} &       40.35  & \Bsic{42.17} & \Best{44.08} & \Bsic{40.20} & \Best{42.04} \\
-%			                      & VNLB   $s_t = 4$     & \Bsic{39.44} & \Best{41.33} & \bsic{40.51} &       42.12  & \bsic{38.30} &       40.05  & \bsic{42.07} &       43.97  & \bsic{40.08} &       41.86  \\\hline
-%%
-%			\multirow{1}{*}{$20$}
-%			                      & V-BM4D-mp            & \bsic{33.23} &       34.70  & \bsic{34.63} &       35.98  & \bsic{33.85} &       34.94  & \bsic{35.30} &       36.13  & \bsic{34.25} &       35.44  \\
-%			                      & VNLB   $s_t = 1$     & \bsic{33.19} &       35.53  & \bsic{35.60} &       37.76  & \bsic{35.35} &       37.31  & \bsic{37.90} &       39.88  & \bsic{35.51} &       37.62  \\
-%			                      & VNLB   $s_t = 2$     & \bsic{34.95} &       36.93  & \bsic{37.03} &       38.69  & \Bsic{35.60} & \Best{37.52} & \Bsic{38.60} & \Best{40.52} & \bsic{36.55} &       38.41  \\
-%			                      & VNLB   $s_t = 3$     & \bsic{35.48} &       37.40  & \Bsic{37.27} & \Best{38.86} & \Bsic{35.54} & \Best{37.43} & \Bsic{38.60} & \Best{40.54} & \Bsic{36.72} & \Best{38.56} \\
-%			                      & VNLB   $s_t = 4$     & \Bsic{35.65} & \Best{37.54} & \Bsic{37.26} & \Best{38.84} & \bsic{35.44} &       37.32  & \Bsic{38.50} & \Best{40.48} & \Bsic{36.71} & \Best{38.55} \\\hline
-%%
-%			\multirow{1}{*}{$40$}
-%			                      & V-BM4D-mp            & \bsic{29.07} &       30.46  & \bsic{30.45} &       31.82  & \bsic{30.50} &       31.57  & \bsic{30.93} &       31.74  & \bsic{30.24} &       31.40  \\
-%			                      & VNLB   $s_t = 1$     & \bsic{29.25} &       31.57  & \bsic{31.44} &       33.67  & \bsic{31.70} &       33.70  & \bsic{33.47} &       35.44  & \bsic{31.46} &       33.60  \\
-%			                      & VNLB   $s_t = 2$     & \bsic{31.18} &       32.99  & \bsic{33.40} &       35.06  & \Bsic{32.60} & \Best{34.61} & \bsic{34.76} &       36.63  & \bsic{32.98} &       34.82  \\
-%			                      & VNLB   $s_t = 3$     & \bsic{31.69} &       33.46  & \Bsic{33.76} & \Best{35.32} & \Bsic{32.70} & \Best{34.69} & \Bsic{34.91} & \Best{36.79} & \Bsic{33.27} & \Best{35.07} \\
-%			                      & VNLB   $s_t = 4$     & \Bsic{31.88} & \Best{33.64} & \Bsic{33.82} & \Best{35.37} & \Bsic{32.70} & \Best{34.66} & \Bsic{34.89} & \Best{36.77} & \Bsic{33.22} & \Best{35.11} \\\hline
-%		\end{tabular}}
 		\begin{tabular}{ c | l |c c | c c | c c | c c | c c}
@@
 			                      & V-BM4D-mp            & \bsic{37.47} &       38.85  & \bsic{38.67} &       40.02  & \bsic{37.30} &       38.40  & \bsic{39.52} &       40.41  & \bsic{38.24} &       39.42  \\
-			                      & VNLB   $s_t = 1$     & \bsic{37.00} &       39.57  & \bsic{39.70} &       41.82  & \Bsic{38.58} & \Best{40.77} & \Bsic{42.20} & \Best{44.38} & \bsic{39.37} &       41.64  \\
-										 & VNLB   $s_t = 2$     & \bsic{38.46} &       40.85  & \Bsic{40.49} & \Best{42.37} & \Bsic{38.52} & \Best{40.70} & \Bsic{42.22} & \Best{44.38} & \Bsic{39.92} & \Best{42.08} \\
-			                      & VNLB   $s_t = 3$     & \bsic{38.87} & \Best{41.19} & \Bsic{40.59} & \Best{42.46} & \bsic{38.42} &       40.60  & \bsic{42.09} &       44.25  & \Bsic{39.99} & \Best{42.13} \\
-										 & VNLB   $s_t = 4$     & \Bsic{38.99} & \Best{41.28} & \Bsic{40.55} & \Best{42.42} & \bsic{38.32} &       40.50  & \bsic{41.93} &       44.09  & \Bsic{39.94} & \Best{42.07} \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{37.18} &       39.78  & \bsic{39.74} &       41.92  & \Bsic{38.62} & \Best{40.81} & \bsic{42.34} & \best{44.51} & \bsic{39.47} &       41.64  \\
+			                      & VNLB   $s_t = 2$     & \bsic{38.69} &       41.08  & \bsic{40.64} & \Best{42.55} & \Bsic{38.63} & \Best{40.82} & \Bsic{42.47} & \Best{44.61} & \Bsic{40.11} & \Best{42.08} \\
+			                      & VNLB   $s_t = 3$     & \Bsic{39.08} & \Best{41.39} & \Bsic{40.75} & \Best{42.64} & \Bsic{38.56} & \Best{40.74} & \bsic{42.36} &       44.51  & \Bsic{40.19} & \Best{42.13} \\
+			                      & VNLB   $s_t = 4$     & \Bsic{39.04} & \Best{41.34} & \bsic{40.61} & \best{42.49} & \bsic{38.43} &       40.63  & \bsic{42.04} &       44.18  & \bsic{40.03} & \Best{42.07} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{37.00} &       39.57  & \bsic{39.70} &       41.82  & \Bsic{38.58} & \Best{40.77} & \Bsic{42.20} & \Best{44.38} & \bsic{39.37} &       41.64  \\
+%			                      & VNLB   $s_t = 2$     & \bsic{38.46} &       40.85  & \Bsic{40.49} & \Best{42.37} & \Bsic{38.52} & \Best{40.70} & \Bsic{42.22} & \Best{44.38} & \Bsic{39.92} & \Best{42.08} \\
+%			                      & VNLB   $s_t = 3$     & \bsic{38.87} & \Best{41.19} & \Bsic{40.59} & \Best{42.46} & \bsic{38.42} &       40.60  & \bsic{42.09} &       44.25  & \Bsic{39.99} & \Best{42.13} \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{38.99} & \Best{41.28} & \Bsic{40.55} & \Best{42.42} & \bsic{38.32} &       40.50  & \bsic{41.93} &       44.09  & \Bsic{39.94} & \Best{42.07} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{37.48} &       39.74  & \bsic{39.85} &       41.83  & \Bsic{38.80} & \Best{40.82} & \Bsic{42.16} & \Best{44.10} & \bsic{39.57} &       41.62  \\
+%			                      & VNLB   $s_t = 2$     & \bsic{39.01} &       41.10  & \Bsic{40.74} & \Best{42.40} & \bsic{38.70} &       40.65  & \Bsic{42.23} & \Best{44.14} & \Bsic{40.17} & \Best{42.07} \\
+%			                      & VNLB   $s_t = 3$     & \bsic{39.40} & \Best{41.37} & \Bsic{40.74} & \Best{42.36} & \bsic{38.50} &       40.35  & \Bsic{42.17} & \Best{44.08} & \Bsic{40.20} & \Best{42.04} \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{39.44} & \Best{41.33} & \bsic{40.51} &       42.12  & \bsic{38.30} &       40.05  & \bsic{42.07} &       43.97  & \bsic{40.08} &       41.86  \\\hline
 %
@@
 			                      & V-BM4D-mp            & \bsic{33.23} &       34.70  & \bsic{34.63} &       35.98  & \bsic{33.85} &       34.94  & \bsic{35.30} &       36.13  & \bsic{34.25} &       35.44  \\
-			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       35.58  & \bsic{35.44} &       37.79  & \bsic{34.94} &       37.11  & \bsic{37.80} &       39.83  & \bsic{35.29} &       37.58  \\
-			                      & VNLB   $s_t = 2$     & \bsic{34.71} &       36.98  & \bsic{36.90} &       38.78  & \Bsic{35.28} & \Best{37.47} & \Bsic{38.61} & \Best{40.79} & \bsic{36.38} &       38.50  \\
-			                      & VNLB   $s_t = 3$     & \bsic{35.18} &       37.40  & \Bsic{37.16} & \Best{38.94} & \Bsic{35.28} & \Best{37.47} & \Bsic{38.67} & \Best{40.83} & \Bsic{36.57} & \Best{38.66} \\
-										 & VNLB   $s_t = 4$     & \Bsic{35.34} & \Best{37.54} & \Bsic{37.17} & \Best{38.95} & \Bsic{35.23} & \Best{37.42} & \Bsic{38.59} & \Best{40.72} & \Bsic{36.58} & \Best{38.65} \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{33.12} &       35.72  & \bsic{35.34} &       37.76  & \bsic{34.87} &       37.02  & \bsic{37.59} &       39.53  & \bsic{35.23} &       37.58  \\
+			                      & VNLB   $s_t = 2$     & \bsic{34.89} &       37.17  & \bsic{36.90} &       38.82  & \Bsic{35.31} & \Best{37.51} & \Bsic{38.54} & \Best{40.72} & \bsic{36.41} &       38.50  \\
+			                      & VNLB   $s_t = 3$     & \Bsic{35.32} & \Best{37.55} & \Bsic{37.15} & \Best{38.97} & \Bsic{35.32} & \Best{37.52} & \Bsic{38.59} & \Best{40.76} & \Bsic{36.60} & \Best{38.66} \\
+			                      & VNLB   $s_t = 4$     & \Bsic{35.29} & \Best{37.50} & \Bsic{37.06} & \best{38.85} & \Bsic{35.25} & \Best{37.47} & \bsic{38.32} & \best{40.43} & \bsic{36.48} & \Best{38.65} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       35.58  & \bsic{35.44} &       37.79  & \bsic{34.94} &       37.11  & \bsic{37.80} &       39.83  & \bsic{35.29} &       37.58  \\
+%			                      & VNLB   $s_t = 2$     & \bsic{34.71} &       36.98  & \bsic{36.90} &       38.78  & \Bsic{35.28} & \Best{37.47} & \Bsic{38.61} & \Best{40.79} & \bsic{36.38} &       38.50  \\
+%			                      & VNLB   $s_t = 3$     & \bsic{35.18} &       37.40  & \Bsic{37.16} & \Best{38.94} & \Bsic{35.28} & \Best{37.47} & \Bsic{38.67} & \Best{40.83} & \Bsic{36.57} & \Best{38.66} \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{35.34} & \Best{37.54} & \Bsic{37.17} & \Best{38.95} & \Bsic{35.23} & \Best{37.42} & \Bsic{38.59} & \Best{40.72} & \Bsic{36.58} & \Best{38.65} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{33.19} &       35.53  & \bsic{35.60} &       37.76  & \bsic{35.35} &       37.31  & \bsic{37.90} &       39.88  & \bsic{35.51} &       37.62  \\
+%			                      & VNLB   $s_t = 2$     & \bsic{34.95} &       36.93  & \bsic{37.03} &       38.69  & \Bsic{35.60} & \Best{37.52} & \Bsic{38.60} & \Best{40.52} & \bsic{36.55} &       38.41  \\
+%			                      & VNLB   $s_t = 3$     & \bsic{35.48} &       37.40  & \Bsic{37.27} & \Best{38.86} & \Bsic{35.54} & \Best{37.43} & \Bsic{38.60} & \Best{40.54} & \Bsic{36.72} & \Best{38.56} \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{35.65} & \Best{37.54} & \Bsic{37.26} & \Best{38.84} & \bsic{35.44} &       37.32  & \Bsic{38.50} & \Best{40.48} & \Bsic{36.71} & \Best{38.55} \\\hline
 %
@@
 			                      & V-BM4D-mp            & \bsic{29.07} &       30.46  & \bsic{30.45} &       31.82  & \bsic{30.50} &       31.57  & \bsic{30.93} &       31.74  & \bsic{30.24} &       31.40  \\
-			                      & VNLB   $s_t = 1$     & \bsic{29.03} &       31.57  & \bsic{30.93} &       33.36  & \bsic{30.82} &       32.77  & \bsic{32.81} &       34.69  & \bsic{30.90} &       33.10  \\
-			                      & VNLB   $s_t = 2$     & \bsic{31.02} &       33.09  & \bsic{33.11} &       35.09  & \bsic{32.08} &       34.25  & \bsic{34.52} &       36.60  & \bsic{32.68} &       34.76  \\
-										 & VNLB   $s_t = 3$     & \bsic{31.49} &       33.56  & \bsic{33.58} & \Best{35.41} & \Bsic{32.34} & \Best{34.55} & \Bsic{34.82} & \Best{36.96} & \Bsic{33.06} & \Best{35.12} \\
-			                      & VNLB   $s_t = 4$     & \Bsic{31.66} & \Best{33.73} & \Bsic{33.69} & \Best{35.47} & \Bsic{32.37} & \Best{34.59} & \Bsic{34.82} & \Best{36.95} & \Bsic{33.14} & \Best{35.19} \\\hline
+			                      & VNLB   $s_t = 1$     & \bsic{29.04} &       31.61  & \bsic{30.64} &       33.11  & \bsic{30.52} &       32.46  & \bsic{32.43} &       34.19  & \bsic{30.66} &       33.10  \\
+			                      & VNLB   $s_t = 2$     & \bsic{31.16} &       33.25  & \bsic{33.01} &       35.06  & \bsic{31.99} &       34.12  & \bsic{34.36} &       36.39  & \bsic{32.63} &       34.76  \\
+			                      & VNLB   $s_t = 3$     & \Bsic{31.64} & \Best{33.72} & \bsic{33.54} & \Best{35.41} & \Bsic{32.29} & \best{34.50} & \Bsic{34.70} & \Best{36.82} & \Bsic{33.04} & \Best{35.12} \\
+			                      & VNLB   $s_t = 4$     & \Bsic{31.72} & \Best{33.79} & \Bsic{33.65} & \Best{35.42} & \Bsic{32.38} & \Best{34.63} & \bsic{34.60} & \best{36.71} & \Bsic{33.09} & \Best{35.19} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{29.03} &       31.57  & \bsic{30.93} &       33.36  & \bsic{30.82} &       32.77  & \bsic{32.81} &       34.69  & \bsic{30.90} &       33.10  \\
+%			                      & VNLB   $s_t = 2$     & \bsic{31.02} &       33.09  & \bsic{33.11} &       35.09  & \bsic{32.08} &       34.25  & \bsic{34.52} &       36.60  & \bsic{32.68} &       34.76  \\
+%			                      & VNLB   $s_t = 3$     & \bsic{31.49} &       33.56  & \bsic{33.58} & \Best{35.41} & \Bsic{32.34} & \Best{34.55} & \Bsic{34.82} & \Best{36.96} & \Bsic{33.06} & \Best{35.12} \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{31.66} & \Best{33.73} & \Bsic{33.69} & \Best{35.47} & \Bsic{32.37} & \Best{34.59} & \Bsic{34.82} & \Best{36.95} & \Bsic{33.14} & \Best{35.19} \\\hline
+%			                      & VNLB   $s_t = 1$     & \bsic{29.25} &       31.57  & \bsic{31.44} &       33.67  & \bsic{31.70} &       33.70  & \bsic{33.47} &       35.44  & \bsic{31.46} &       33.60  \\
+%			                      & VNLB   $s_t = 2$     & \bsic{31.18} &       32.99  & \bsic{33.40} &       35.06  & \Bsic{32.60} & \Best{34.61} & \bsic{34.76} &       36.63  & \bsic{32.98} &       34.82  \\
+%			                      & VNLB   $s_t = 3$     & \bsic{31.69} &       33.46  & \Bsic{33.76} & \Best{35.32} & \Bsic{32.70} & \Best{34.69} & \Bsic{34.91} & \Best{36.79} & \Bsic{33.27} & \Best{35.07} \\
+%			                      & VNLB   $s_t = 4$     & \Bsic{31.88} & \Best{33.64} & \Bsic{33.82} & \Best{35.37} & \Bsic{32.70} & \Best{34.66} & \Bsic{34.89} & \Best{36.77} & \Bsic{33.22} & \Best{35.11} \\\hline
 		\end{tabular}}
@@
 		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_bm4d_s40_row220_col040-180_fra080-220.png}\\
+%		               \hspace{0.2\textwidth}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_bm4d_s10_row220_col040-180_fra080-220.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_bm4d_s20_row220_col040-180_fra080-220.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_bm4d_s40_row220_col040-180_fra080-220.png}\\
+%		               \hspace{0.2\textwidth}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt1_s10_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt1_s20_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt1_s40_row220_col040-180_fra080-220_neg-weights.png}\\
+%		               \hspace{0.2\textwidth}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt1_s10_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt1_s20_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt1_s40_row220_col040-180_fra080-220_neg-weights.png}\\
+%		               \hspace{0.2\textwidth}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt2_s10_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt2_s20_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt2_s40_row220_col040-180_fra080-220_neg-weights.png}\\
+%		               \hspace{0.2\textwidth}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt2_s10_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt2_s20_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt2_s40_row220_col040-180_fra080-220_neg-weights.png}\\
+%		               \hspace{0.2\textwidth}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt3_s10_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt3_s20_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt3_s40_row220_col040-180_fra080-220_neg-weights.png}\\
+%		               \hspace{0.2\textwidth}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt3_s10_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt3_s20_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt3_s40_row220_col040-180_fra080-220_neg-weights.png}\\
 		               \hspace{0.2\textwidth}%
-		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_bm4d_s10_row220_col040-180_fra080-220.png}%
-		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_bm4d_s20_row220_col040-180_fra080-220.png}%
-		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_bm4d_s40_row220_col040-180_fra080-220.png}\\
+		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt4_s10_row220_col040-180_fra080-220_neg-weights.png}%
+		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt4_s20_row220_col040-180_fra080-220_neg-weights.png}%
+		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt4_s40_row220_col040-180_fra080-220_neg-weights.png}\\
 %		               \hspace{0.2\textwidth}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt2_s10_row220_col040-180_fra080-220.png}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt2_s20_row220_col040-180_fra080-220.png}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt2_s40_row220_col040-180_fra080-220.png}\\
-%		               \hspace{0.2\textwidth}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt2_s10_row220_col040-180_fra080-220.png}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt2_s20_row220_col040-180_fra080-220.png}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt2_s40_row220_col040-180_fra080-220.png}\\
-%		               \hspace{0.2\textwidth}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt3_s10_row220_col040-180_fra080-220.png}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt3_s20_row220_col040-180_fra080-220.png}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt3_s40_row220_col040-180_fra080-220.png}\\
-%		               \hspace{0.2\textwidth}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt3_s10_row220_col040-180_fra080-220.png}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt3_s20_row220_col040-180_fra080-220.png}%
-%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt3_s40_row220_col040-180_fra080-220.png}\\
-		               \hspace{0.2\textwidth}%
-		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt4_s10_row220_col040-180_fra080-220.png}%
-		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt4_s20_row220_col040-180_fra080-220.png}%
-		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_vnlb_pt4_s40_row220_col040-180_fra080-220.png}\\
-		               \hspace{0.2\textwidth}%
-		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt4_s10_row220_col040-180_fra080-220.png}%
-		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt4_s20_row220_col040-180_fra080-220.png}%
-		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt4_s40_row220_col040-180_fra080-220.png}\\
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt4_s10_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt4_s20_row220_col040-180_fra080-220_neg-weights.png}%
+%		\includegraphics[width=0.2\textwidth]{figs/temporal_slices/slice_mobile_mono_diff_vnlb_pt4_s40_row220_col040-180_fra080-220_neg-weights.png}\\
 %		\includegraphics[trim=3.5cm 2cm 1.5cm .5cm, clip=true, width=0.3\textwidth]{figs/time_diff_vnlb_s10.png}
@@
 state-of-the-art results, both in terms of PSNR and qualitatively. 
-A key element of the proposed method is the estimation of the a priori
+A key element of the proposed method is the estimation of the \textit{a priori}
 covariance matrices from sets of noisy spatio-temporal patches. Since
 the dimensionality of the patches is high, and the number of available 
-similar patches is limited, we additionaly assume that the prior covariance
-is of low rank. In practice this amount to keeping only the principal 
-eigenvectors of the sample covariance matrix. This desicion is analized
+similar patches is limited, we additionally assume that the prior covariance
+is of low rank. In practice this amounts to keeping only the principal 
+eigenvectors of the sample covariance matrix. This decision is analyzed
 in the light of theoretical results on the estimation of covariance matrices 
@@
 
-Spetial attention is devoted to the evaluation of the temporal consistency of
+Special attention is devoted to the evaluation of the temporal consistency of
 the result. In particular, we propose a way to quantify the temporal

### 2015-12-10 doc/201506_cambridge_slides/figures_local/derf_generate_details.m

@@ -6,48 +6,62 @@ base_path = '/media/pariasm/tera/funes/denoising/';
 bm4d_path = [base_path 'algos/results/VBM4D/'];
 orig_path = [base_path 'data/derf/'];
 %nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps5_2ps5_2wx37_2r16_2np160/'];
-nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/'];
+%nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/'];
+nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/tip_table_1ps7_2ps7-neg/'];
+%nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/tip_table_1ps5_2ps5-neg/'];
 
 
 % generated tiles ------------------- %
-% tennis       050-090-030 150+150+30 %
-% tennis       040-150-070 150+150+30 %
-% bus          060-020-020 150+150+30 %
-% bus          110-150-010 150+150+30 %
-% stefan_mono  090-180-265 150+150+30 %
-% stefan_mono  060-130-005 150+150+30 %
-% mobile_mono  060-060-080 100+100+30 %
-% mobile_mono  188-188-065 100+100+30 %
-% ----------------------------------- %
 
-ti = 060;
-tj = 060;
-tt = 080;
-tile_i = [ti:ti + 100];
-tile_j = [tj:tj + 100];
-tile_t = [tt:tt +  30];
-
-addpath '../../../tools/';
-
-% sequence data
-seqnames = {'football_mono','mobile_mono','stefan_mono','tennis_mono'};
-first    = {1              , 1           , 1           , 1           };
-last     = {260            , 300         , 300         , 150         };
+%seqnames = {'football_mono','mobile_mono','stefan_mono','tennis_mono'};
+%first    = {1              , 1           , 1           , 1           };
+%last     = {260            , 300         , 300         , 150         };
 %seqnames = {'bus','coastguard','foreman','tennis'};
[…]

### 2015-12-10 doc/201506_cambridge_slides/figures_local/images_local_copy.sh

@@ -80,131 +80,131 @@ mkdir -p figures_local/VBM4D/tennis_mp_s20
 mkdir -p figures_local/VBM4D/tennis_mp_s40
 
 cp /media/pariasm/tera/funes/denoising/data/derf/mobile_mono/tile188-188-065*.png                                                                      figures_local/data/derf/mobile_mono
-cp /media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/mobile_mono_s10_pt4/tile188-188-065*.png    figures_local/vnlb3d_mono/mobile_mono_s10_pt4
-cp /media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/mobile_mono_s20_pt4/tile188-188-065*.png    figures_local/vnlb3d_mono/mobile_mono_s20_pt4
-cp /media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/mobile_mono_s40_pt4/tile188-188-065*.png    figures_local/vnlb3d_mono/mobile_mono_s40_pt4
-cp /media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/mobile_mono_s10_pt4/tile188-188-065*.png    figures_local/vnlb3d_mono/mobile_mono_s10_pt4
-cp /media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/mobile_mono_s20_pt4/tile188-188-065*.png    figures_local/vnlb3d_mono/mobile_mono_s20_pt4
-cp /media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/mobile_mono_s40_pt4/tile188-188-065*.png    figures_local/vnlb3d_mono/mobile_mono_s40_pt4
+cp /media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/tip_table_1ps7_1ps7-neg/mobile_mono_s10_pt4/tile188-188-065*.png    figures_local/vnlb3d_mono/mobile_mono_s10_pt4
[…]

### 2015-12-10 doc/201507_tip/average_psnr.m

@@ -1,29 +1,108 @@
-bsc10 = [34.32 33.99 33.47 34.22 34.22 
-         34.33 34.44 33.82 34.91 34.91 
-         34.53 34.74 33.81 34.70 34.70 
-         34.18 34.41 33.47 34.18 34.18];
-                                       
-bsc20 = [30.54 29.67 29.04 30.16 30.16 
-         30.73 29.83 29.38 30.96 30.96 
-         30.82 30.15 29.33 30.67 30.67 
-         30.25 29.74 28.89 29.96 29.96];
-                                       
-bsc40 = [27.67 24.64 24.47 26.67 26.67 
-         27.14 25.43 25.18 27.23 27.23 
-         27.63 26.15 25.44 27.37 27.37 
-         27.81 26.45 25.50 27.31 27.31];
-         
-fnl10 = [34.95 34.11 33.68 34.95 34.95
-         34.62 34.67 34.23 35.61 35.61
-         35.15 35.31 34.29 35.67 35.67
-         35.32 35.54 34.13 35.61 35.61];
-                                      
-fnl20 = [31.08 30.49 29.69 31.06 31.06
-         31.24 30.34 29.90 31.82 31.82
-         31.66 31.09 30.02 31.83 31.83
-         31.69 31.35 29.97 31.66 31.66];
-                                      
-fnl40 = [28.38 26.02 25.64 27.62 27.62
-         28.15 26.06 25.81 28.24 28.24
-         28.62 26.94 26.12 28.42 28.42
-         28.86 27.46 26.24 28.45 28.45];
+% bsc10 = [34.32 33.99 33.47 34.22 34.22 
+%          34.33 34.44 33.82 34.91 34.91 
+%          34.53 34.74 33.81 34.70 34.70 
+%          34.18 34.41 33.47 34.18 34.18];
+%                                        
+% bsc20 = [30.54 29.67 29.04 30.16 30.16 
+%          30.73 29.83 29.38 30.96 30.96 
+%          30.82 30.15 29.33 30.67 30.67 
+%          30.25 29.74 28.89 29.96 29.96];
+%                                        
+% bsc40 = [27.67 24.64 24.47 26.67 26.67 
+%          27.14 25.43 25.18 27.23 27.23 
+%          27.63 26.15 25.44 27.37 27.37 
[…]

### 2015-12-10 tools/generate_time_slices_for_tip.m

@@ -3,10 +3,12 @@
 
 % path to data
 base_path = '/media/pariasm/tera/funes/denoising/';
+base_path = '~/Work/denoising/';
 bm4d_path = [base_path 'algos/results/VBM4D/'];
 orig_path = [base_path 'data/derf/'];
 %nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps5_2ps5_2wx37_2r16_2np160/'];
-nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/'];
+%nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/'];
+nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/tip_table_1ps7_2ps7-neg/'];
 
 % sequence data
 seqnames = {'football_mono','mobile_mono','stefan_mono','tennis_mono'};
@@ -20,7 +22,7 @@ sequences = struct('name',seqnames,'first',first,'last',last);
 clear seqnames first last
 
 % parameters
-sigma = '10';
+sigma = '40';
 
 addpath '../../time_filter/src/';
 
@@ -28,7 +30,7 @@ for seqi = [2],%1:length(sequences),
 
 	seq = sequences(seqi);
 
-	for pt = 2:7,
+	for pt = 1:4,
 		if pt < 5,
 			u_pat = [nlb3_path seq.name '_s' sigma '_pt' num2str(pt) '/deno_%03d.png']; % nlb3 pt4
 			out_name = ['_vnlb_pt' num2str(pt) '_s' sigma];
@@ -67,7 +69,7 @@ for seqi = [2],%1:length(sequences),
 	u = load_sequence(u_pat, seq.first, seq.last);
 	slice_orig = squeeze(u(220,40:180,:,80:220))';
 
-	for pt = 2:5,
+	for pt = 1:4,
 		if pt < 5,
 			u_pat = [nlb3_path seq.name '_s' sigma '_pt' num2str(pt) '/deno_%03d.png']; % nlb3 pt4
 			out_name = ['_diff_vnlb_pt' num2str(pt) '_s' sigma];

### 2015-12-10 tools/psnr_vs_rank_np_images.m

@@ -1,10 +1,11 @@
 root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/';
+root_folder =  '../results/vnlbayes/';
 
-%stage2_folder = [root_folder 'tip_table_2r_vs_2np_derf/'];
-%stage1_folder = [root_folder 'tip_table_1r_vs_1np_derf/'];
+stage2_folder = [root_folder 'tip_table_2r_vs_2np_derf-neg/'];
+stage1_folder = [root_folder 'tip_table_1r_vs_1np_derf-neg/'];
 
-stage2_folder = [root_folder 'tip_table_2r_vs_2np_mono/'];
-stage1_folder = [root_folder 'tip_table_1r_vs_1np_mono/'];
+%stage2_folder = [root_folder 'tip_table_2r_vs_2np_mono-neg/'];
+%stage1_folder = [root_folder 'tip_table_1r_vs_1np_mono-neg/'];
 
 % stage 2 ---------------------------------------------------
 
@@ -96,11 +97,13 @@ stage1_folder = [root_folder 'tip_table_1r_vs_1np_mono/'];
 %(!)% % THIS IS USEFULL FOR DISPLAYING RESULTS WITH PLOT
 %(!)% %ranks = [5,10,15,20,25,30,35,40,45,50,60,70,90,110];
 %(!)% ranks = [5,10,15,20,25,30,35,40,50,70,90,110];
+%(!)% ranks = [5,10,15,20,25,30,35,40,45,60,80,100,120];
 %(!)% nsims = [50:50:350];
 %(!)% seqs = {'bus', 'football', 'foreman', 'tennis'};
 %(!)% 
 %(!)% mff = zeros(length(nsims),length(ranks),length(seqs));
-%(!)% idx_r = [9,11,12,13,15,16,17,19,20,21];
+%(!)% %idx_r = [9,11,12,13,15,16,17,19,20,21];
+%(!)% idx_r = [10,11,13,14,15,17,18,19,21,22,23];
 %(!)% 
 %(!)% fig_i = 1;
 %(!)% for s = 10:10:40,
@@ -128,7 +131,7 @@ stage1_folder = [root_folder 'tip_table_1r_vs_1np_mono/'];
 %(!)% 	for ii = length(nsims):-1:1,
 %(!)% 		color = [0.14*(ii-1) 1-0.14*(ii-1) 1-0.14*(ii-1) ];
[…]

### 2015-12-10 doc/201511_report_plein-phare/report_plein-phare.tex
[doc] Report Plein-Phare

--- 2015-12-10 doc/201507_tip/paper.tex
@@
 %
-\documentclass[10pt, journal, twocolumn, final, a4paper]{IEEEtran}
+\documentclass[10pt, a4paper]{article}
 %
@@
 
-% allow for compress references ranges (IEEEtran_HOWTO S.VII)
+% allow for compress references ranges
 % noadjust removes a leading space before the []
@@
 
-%\usepackage[left=1.2in,right=1.2in]{geometry}
+\usepackage[left=1.0in,right=1.0in]{geometry}
+\usepackage{pdflscape}
+\usepackage{hyperref}
 
@@
 % pablo's commands for comments and suggested modifications
-\newcommand{\pa}[1]{\textcolor{cyan}{#1}}
+%\newcommand{\pa}[1]{\textcolor{cyan}{#1}}
+\newcommand{\pa}[1]{#1}
 \newcommand{\psub}[2]{\pa{\sout{#1}}\pa{/#2}}
@@
 
-\begin{document}
-
 \title{A Non-local Bayesian Video Denoising Method}
+\date{}
 
@@
 math\'ematiques et de leurs applications} (CMLA), \'Ecole Normale Sup\'eriore
-de Cachan, 61 Av. du Pr\'esident Wilson, F-94230 Cachan, France}}
-
-\markboth{IEEE Transactions of Image Processing,~Vol.~X, No.~X, Month~2015}%
-{Arias, Morel: A Non-local Bayesian Video Denoising Method}
+de Cachan, 61 Av. du Pr\'esident Wilson, F-94230 Cachan, France}
+\\[1ex] CMLA, ENS Cachan}
+
+\makeatletter         
+\def\@maketitle{
+\raggedright
+\begin{center}
+	{\huge \bfseries \sffamily \@title }\\[8ex] 
+	{\Large \bfseries \sffamily Report for the Project }\\
+	\includegraphics[width = 80mm]{Plein-Phare.png}\\[8ex]
+	{\Large  \@author}\\[4ex] 
+\end{center}}
+\makeatother
+
+\begin{document}
 
@@
 \end{abstract}
-
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-	video denoising, Bayesian methods, patch-based methods
-\end{IEEEkeywords}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
 
@@
 	\centering
-%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
+%	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}
+%	\hfill
+%	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
 %	\vspace{.1cm}
-	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
+	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}
+	\hfill
+	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
 	\vspace{.2cm}
-	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
+	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}
+	\hfill
+	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
 	\vspace{.2cm}
-	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
+	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}
+	\hfill
+	\includegraphics[width = .49\columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
 	\vspace{.2cm}
-%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
-%	\vspace{.1cm}
-	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
-	\vspace{.2cm}
-	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
-	\vspace{.2cm}
-	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
-	\vspace{.2cm}
-%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
-%	\vspace{.1cm}
-%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
-%	\vspace{.1cm}
-%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
-%	\vspace{.1cm}
-%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
-%	\vspace{.1cm}
 	\caption{For each of the two sets of patches of Fig. \ref{fig:patch_groups_pos} we show
@@
 
-\subsection{Search region and patch size}
-
-Setting the size of the search region implies a trade-off between denoising
-performance and running time: A larger search region takes longer to traverse
-but yields better results, since more similar patches can be found. We use the same 
-search region in both stages. The
-temporal search window is fixed at $w_t = 5$. The spatial search region is set at
-$w_x = 37$ for color videos and $w_x = 45$ for grayscale videos.
-With these values, the search region captures the $5$ frame trajectory of the
-target patch as long as it moves slower than $37/5 = 7.4$ pixels/frame (for
-color videos).
-
-Let us now consider the spatial patch
-size $s_x$, which is a key parameter in patch-based methods \cite{Buades2006,Kervrann2006,Boulanger2007}.
-%The distribution of the 
-%patch distances is a non-central Chi-squared distribution \cite{Dabov2007tip}
-%\pcomment{CHECK!}
-%with variance 
-%\[\textnormal{Var}\left\{\frac1{m}\|\ma q_1 - \ma q_2\|^2\right\} = \frac{8\sigma^2}{m}\left(\sigma^2 + \frac{\|\ma p_1 - \ma p_2\|^2}{m}\right),\]
-%where $m = s_x^2s_t$ is the total number of pixels in the patch.
-%*% Increasing the spatial patch size $s_x$ reduces the variance of the noise in the patch
-%*% distance. 
-%*% However, for larger
-%*% patches it becomes less likely to find other patches with a similar texture
-%*% pattern. The use spatio-temporal patches helps in solving this trade-off: for
-%*% instance, with a spatio-temporal patch of size $5\times 5\times 4$, we obtain
-%*% the same patch distance noise as with a spatial patch of size $10\times 10
-%*% \times 1$. Moreover, as discussed in \S \ref{sse:spatio-temporal-patches}, for
-%*% an approximately uniform motion, the 
-%*% amount of similar neighbors of a $5\times 5\times 4$ patch is roughly the same
-%*% as for a $5\times 5\times 1$ patch.
-%
-For color videos, we will set the spatial patch size at $s_x = 5$ for both
-stages, whereas for grayscale videos we use $s_x = 7$. Larger patches (up to $s_x = 9$) lead to an mild improvement of the
-results (on average). This improvement comes at a considerable increase in the
-computation time, since our current implementation is $\mathcal O(s_x^4)$.
-Thus, have found that a good compromise between computation time and quality is
-given by $s_x = 5$.
-
-The impact of the temporal patch size $s_t$ will be discussed later in Section
-\ref{sec:results}, where we show results varying $s_t$ between $s_t = 1$ and $s_t = 4$.
-
-\subsection{Rank and number of similar patches}
-
-The number of similar patches $n$ and the rank $r$ affect the estimation of the covariance
-matrix $C$, controlling the trade-off between the accuracy of the Gaussian model
-and the precision of the covariance matrix,
-which in turn has a direct effect on the denoising strength of the algorithm.
-% This have great impact on the bias-variance trade-off of the denoiser.
-%In practice, these parameters determine the denoising strength of the
-%algorithm. For example, using a large
-We found a compromise to this trade-off empirically, by trying different values
-of this parameter on a few training sequences and keeping the one that yields
-the best PSNR on average.
-
-%The number of similar patches $n$ and the rank $r$ affect the estimation of the covariance
-%matrix $C$, controlling the trade-off between the accuracy of Gaussian model
-%and precision of the covariance matrix.
-
-%\prm{Intuitively speaking, by setting a lower rank we are estimating a covariance
-%matrix in a lower dimensional subspace. Then, according to
-%\cite{Vershynin2012}, we require a smaller number of samples for a given
-%precision.} \pcomment{The previous argument is not good. I would like to have
-%some theoretical estimate on the number of samples to approximate a lower
-%rank covariance matrix, or equivalently, the number of samples to approximate
-%the largest principal directions. The point I would like to make, is that
-%the number of similar patches required is less if one only wants to estimate
-%the first principal eigenvectors. Maybe the answer lies in \cite{Halko2011}.}
-
-The plots in Figure \ref{fig:rank1-nsim1-psnr-color} show the PSNRs of the
-basic and final estimates as a function of the rank $r_1$, for several values
-of $n_{1}$. The curves correspond to an average over 20 frames clips extracted
-from four classical test color sequences, namely \emph{bus}, \emph{foreman},
-\emph{football} and
-\emph{tennis}. The sequences were contaminated with
-AGWN of standard deviation $\sigma = 10, 20, 30, 40$. 
-Figure \ref{fig:rank1-nsim1-psnr-gray} shows the results for a
-grayscale version of the same sequences. 
-%
-%
-
-\padd{For the basic estimate, we show two set of curves. The dashed curves were
-obtained by zeroing out negative eigenvalues of the estimated a priori covariance
-matrix $\widehat C$, computed according to \eqref{eq:learn_parameters}. The continuous curves 
-were obtained by retaining negative eigenvalues. In this case the MAP is estimated
-with an empirical Wiener filter that may have some negative coefficients.}
-
-\padd{For lower values of the rank parameter $r$, both curves coincide, since the first
-eigenvalues are positive. 
-For all noise levels, all curves of fixed $n_1$ present a first peak at a low value of the rank $r$.
-The behaviour of the basic estimate around this peak can be
-interpreted in the light of the theoretical results described in \S
-\ref{sse:covariance-estimation}.
-As the noise level increases, the rank at which the peak is attained
-shifts to the left. This makes sense, as the reliability of the computed eigenvectors
-decrease with increasing noise.
-%
-Also, for a fixed noise level, when the number of samples $n_1$ increases, the value
-of the peak increases also, and so does the rank at which it is attained.
-This is again explainable, as smaller groups obtained by keeping only the
-most similar patches have less modes of variation, and thus a worse signal-to-noise ratio
-in the eigenvectors with lower eigenvalues.}
-%As the group of patches grows
-%bigger, patches in the group are not as similar anymore, and a higher rank is
-%needed to allow for additional modes of variation.
-
-%The eigenvalues of $\widehat C$ are given by $\hat \lambda_i = \widehat \nu_i -
-%\sigma^2$, where $\widehat \nu_i$ are the eigenvalues of the empirical
-%\emph{a posteriori} covariance matrix.
-%In practice due to the estimation errors, several
-%$\widehat \nu_i$ are smaller than $\sigma^2$. These translate into negative
-%coefficients $w_{ii}$ in the empirical Wiener filter \eqref{eq:wiener_coeffs},
-%which result in a poorer estimation of the MAP.
-\padd{As the rank parameter increases, both curves diverge. 
-The dashed curves become almost constant at the point when
-most eigenvalues become negative. After that point increasing the
-rank has no effect if the negative eigenvalues are zeroed out.
-%
-Surprisingly, these negative coefficients have a positive effect on the final 
-result, creating the second peak for high values of the rank shown by the
-continuous plots. Currently we do not have an explanation for this behaviour
-although it is related to the aggregation: even if the estimated MAP for the
-patches in each group have larger errors, after aggregation these errors seem
-to cancel, yielding an overall better estimate of the clean image.}
-
-\padd{The final estimate shows the same qualitative behaviour with respect to the first
-stage parameters. The dashed curves obtained by zeroing out the negative
-eigenvalues are not shown to avoid cluttering the figure. Essentially the
-second step has the effect of reducing the differences between results obtained
-with different parameters. Based on these curves, we fix the first stage parameters at
-$n_1 = 300$ and $r_1 = 95$ for color videos, and at $n_1 = 300$ and $r_1 = 180$ for grayscale videos.}
-
-Using these parameters for the first stage, we analyzed the impact when varying the second stage
-parameters $n_2$ and $r_2$. The plots obtained are shown in Figure
-\ref{fig:rank2-nsim2-fpsnr}.
-%
-Note that in this case, the \emph{a
-priori} covariance matrix is estimated from the basic estimate (without having
-to subtract $\sigma^2I$). As a consequence, the are no negative filter coefficients.
-%
-In the second stage the quality drops when
-using a number of patches $n_2$ higher than $100$. This differs from the first stage,
-where a larger $n_1$ yielded a better PSNR.
-The reason for this lies probably in the fact that the patches have less noise,
-and a good estimate of the leading eigenvectors of the covariance matrix can be obtained
-with less patches. Furthermore, smaller groups of patches
-are better modelled by a Gaussian distribution.
-%\pcomment{I don't have an explanation for the curves for $\sigma = 10$. Precisely
-%in the lower noise level, the PSNR drops when $n_2$ is reduced, except for lower ranks.
-%This contradicts the argument given: for less noise, it should be always better to consider
-%less patches, not only for lower ranks.} 
-Based on these plots, we set the following values for the parameters
-\[r_2(\sigma) = 30 - \frac12(\sigma - 10),\quad\quad n_{2} = 100.\]
-
-All parameters are summarized in Table \ref{tab:parameters}.
-
-%Note that due to the coupling of the first and second stages, determining the
-%optimal values for the ranks $r_1, r_2$ and the number of patches $n_1,n_2$
-%would require a four dimensional parameter search which would be to costly.
-%
-%Instead, we fixed the first stage parameters, both for color and grayscale videos
-%at
-%\[r_1 = s_{x,1}^2s_{t,1}\quad\quad n_{1} = 400,\]
-%which we found to give good results. In doing so, we were conservative and
-%used the full rank covariance matrix to eliminate the least signal components.
-%%
-%We then ran a parameter search to determine $r_2$ and $n_{2}$.
-%The results are the ones shown in Figure \ref{fig:rank1-nsim1-psnr-gray}. This led
-%us to establish the following values as a function of $\sigma$:
-%%\[r_2(\sigma) = 40 - \frac13(\sigma - 10)\quad\quad n_{2} = 150.\]
-%\[r_2(\sigma) = 35 - \frac12(\sigma - 10)\quad\quad n_{2} = 100.\]
-%The same values are used for color and grayscale videos.
-%Note that a higher value for $n_{2}$ would give slightly worse results,
-%at a lower computational cost.
-
-\begin{table}
-	\centering
-	\begin{tabular}{l | c c | c c }
-		& \multicolumn{2}{c|}{color} 
-		& \multicolumn{2}{c}{grayscale}\\
-		Stage                            & 1st    & 2nd   & 1st   & 2nd   \\\hline\hline
-		$s_x$        &  5 & 5 & 7 & 7 \\
-		$s_t$        &  1--4  & 1--4  & 1--4  & 1--4  \\
-		$w_x$        &  37    & 37    & 45    & 45    \\
-		$w_x$        &   5    & 5     & 5     & 5    \\
-		$n$          & 300    & 100   & 300   & 100  \\
-		$r$          & 95   & $30 - \frac12(\sigma - 10)$    & 180  & $30 - \frac12(\sigma - 10)$   \\
-%		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
-%		Beta                        & 1    & 1.2  & 1    & 1.2  & 1    & 1.2 \\\hline
-	\end{tabular}
-	\caption{Selected parameters.}
-	\label{tab:parameters}
-\end{table}
-
-%Intuitively, smaller groups obtained by keeping only the most similar patches have 
-%only a few modes of variation and thus are better modelled with a low rank
-%covariance matrix. As the group of patches grows bigger, patches in the group
-%are not as similar anymore, and a higher rank is needed to model these additional 
-%variation.
-%To find appropriate values for these parameters, we compute denoising results
-%varying the rank $r$ and the number of similar patches $n$, while
-%keeping all other parameters fixed. Results are computed for four 20 frames clips
-%extracted from the sequences \emph{bus}, \emph{foreman}, \emph{football} and
-%\emph{tennis}, adding noise of $\sigma = 10, 20, 40$.
-%%
-%We do this for each stage, starting by the second.
-%
-%On this first experiment, the parameters of the first stage are fixed at:
-%\[w_x = 37,\,\,w_t = 5\,\,s_x = 5,\,\,s_t = 4,\,\,n = 375,\,\,r = 100.\]
-%\todo{Check these parameters}
-%Note that $r = 100$ is the full rank.
-%For the second stage, we fix $w_x = 37$, $w_t = 5$, $s_x = 5$ and $s_t = 3$, while varying 
-%$r$ in $10,20,\dots,80$ and $n$ in $50, 150,200,250$.
-%The results can be visualized in Figure \ref{fig:rank-nsim-image-stage2}. The images in the 
-%figure show the PSNR loss in dB with respect to the maximum value attained at each noise level.
-%White means 0dB (\ie the set of parameters where the maximum was attained) and black means a loss
-%greater or equal than 1dB.
-%
-%We can observe that, at constant $n$ there is an optimal value for the rank. Bellow
-%these value the PSNR drops sharply, and above it, the decay is slower. The
-%optimal rank for a given $n$ increases with $n$ and decreases with $\sigma$.
-%Best results are obtained for small $n$. However, this also entails a higher running time, 
-%since it increases the number of groups of similar patches that need to be
-%processed. We found a good compromise by setting $n = 150$ and $r$ as a decreasing function of $\sigma$:
-%\[r(\sigma) = 40 - \frac1{10}(\sigma - 40),\]
-%which corresponds to a line through $(s=10, r = 40)$ and $(s=40, r = 30)$.
-%
-%We now perform a similar search for the first stage, setting the second step parameters as:
-%\[w_x = 37,\,\,w_t = 5\,\,s_x = 5,\,\,s_t = 3,\,\,n = 150,\,\,r(\sigma).\]
-%The first stage parameters are as before, expect that we now vary $r$ in $10,20,\dots,100$
-%and $n$ in $50,100,\dots,650$. Results are shown in Figure
-%\ref{fig:rank-nsim-image-stage1}. Note that since our objective is to maximize
-%the final PSNR, we show here the final PSNR. 
-%The final and the basic PSNRs do not always
-%have the same behaviour. Improving the basic PSNR does not always lead to an
-%improvement in the final one. The reason for this is that it is preferable to
-%apply a conservative noise reduction leaving some noise in the basic estimate
-%(high variance but small bias). In the second step, this residual noise has
-%little effect on the estimation of the patch distances and the \emph{a priori} covariance
-%matrix. On the other hand, applying a more aggressive denoising in first step
-%might increase the basic PSNR, but the second step cannot recover the lost
-%signal components.
-%
-%In fact, best results are obtained using the full rank covariance matrix. 
-%In accordance to these observations, we will set the first values for $r$ and $n$ as:
-%\begin{equation}
-%	r = s_x^2s_t \quad\quad n = 350.
-%	\label{eq:stage1_parameters}
-%\end{equation}
-
-%
-%
-%
-%First we fix the parameters of the second stage at 
-%\[r = 16,\,\, n = 160,\,\, s_x = 5,\,\, s_t = 3,\,\, w_x = 37,\,\, w_t = 5,\]
-%and vary the parameters of the first stage. We considered ranks $r = 8, 16, 32, 64$,   
-%patch sizes $s_x = 3,5,7,9$ and number of patches $n = 80, 160, 320, 640$.
-%For all $4^3 = 64$ combinations, we considered three levels of noise $\sigma = 10, 20, 40$
-%and run our method on four sequences. The
-%sequences used were \emph{army, dog dance, evergreen} and \emph{walking} from
-%the Middlebury optical flow benchmark \cite{middleburyOflow}.
-%The sequences have 8 frames of size $584 \times 388$ (\emph{army}) and $640
-%\times 480$ (\emph{dog dance, evergreen} and \emph{walking}).
-%These sequences were chosen to have some variety of motions, textures, etc.
-%
-%Figure \ref{fig:rank-px-nsim-table-stage1} shows for each configuration of
-%parameters and level of noise, the average PSNR over the four sequences. The
-%cyan bars correspond to the basic estimate and the ones in magenta to the final
-%estimate.
-%
-%It can be observed that several parameter configurations can give very similar
-%results. For example, with $\sigma = 10$, equivalent results can be obtained 
-%with $s_x = 3, r = 16, n = 80$, $s_x = 5, r = 32, n = 160$
-%or  $s_x = 7, r = 64, n = 320$.
-%The one with the least computational cost is chosen. This means,
-%smaller patches sizes, smaller ranks, and a larger number of similar patches.
-%
-%Another thing to notice is that the final and the basic PSNRs do not always
-%have the same behaviour. Improving the basic PSNR does not always lead to an
-%improvement in the final one. The reason for this is that it is preferable to
-%apply a conservative noise reduction leaving some noise in the basic estimate
-%(high variance but small bias). In the second step, this residual noise has
-%little effect on the estimation of the patch distances and the \emph{a priori} covariance
-%matrix. On the other hand, applying a more aggressive denoising in first step
-%might increase the basic PSNR, but the second step cannot recover the lost
-%signal components.
-%
-%The strength of the denoising is controlled through the rank and the number of
-%patches in the group. For lower levels of noise, \ie $\sigma = 10$, better
-%PSRNs can be achieved with a higher rank and using a smaller number of similar
-%patches. When increasing the noise, the rank should be decreased and the number 
-%of similar patches increased.
-%
-%In accordance to these observations, we will set the parameters as a function of
-%$\sigma$ as follows:
-%\begin{equation}
-%	s_t = 5,\quad\quad r = \min(640/\sigma, r_{\text{max}}), \quad\quad n = 16\sigma.
-%	\label{eq:stage1_parameters}
-%\end{equation}
-%%\begin{align}
-%%	s_t &= 5\\
-%%	r &= \min(640/\sigma, r_{\text{max}}) \\
-%%	n &= 16\sigma. 
-%%	\label{eq:stage1_parameters}
-%%\end{align}
-%We set the maximum rank to be $r_{\text{max}} = \min(128,s_x^2s_t)$. Note that
-%$r = s_x^2s_t$ corresponds to the full rank.
-%
-%We now search for the optimum parameters for the second stage, setting the 
-%first stage parameters according to \eqref{eq:stage1_parameters}. The temporal
-%patch size is again set as $s_t = 3$ for both stages and the search regions are
-%kept as in \eqref{eq:search_region_parameters}. Figure
-%\ref{fig:rank-px-nsim-table-stage2} shows the average PSNRs over the four
-%sequences, obtained for each parameter configuration and each noise level.
-%
-%From these results, we fix the parameters as follows:
-%\begin{equation}
-%	s_x = 5,\quad r = \max( \min(320/\sigma, r_{\text{max}}), r_{\text{min}}), \quad n = 160.
-%	\label{eq:stage1_parameters}
-%\end{equation}
-%For the second stage, we set $r_{\text{max}} = \min(64,s_x^2s_t)$ and $r_{\text{min}} = 16$.
-
-%We will fix the temporal size and for the
-%temporal size of the patch we will vary it between $s_t = 1$ and $s_t = 4$ in
-%the results section.
-
 \begin{figure*}[htpb!]
@@
 	\label{fig:rank1-nsim1-psnr-color}
+
+	\begin{center}
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s10_average_mono_neg-vs-pos-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s20_average_mono_neg-vs-pos-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s30_average_mono_neg-vs-pos-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s40_average_mono_neg-vs-pos-weights.eps}\\
+
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s10_average_mono_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s20_average_mono_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s30_average_mono_neg-weights.eps}%
+		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s40_average_mono_neg-weights.eps}\\
+	\end{center}
+	\caption{PSNR averaged over four grayscale sequences, when varying the
+		first stage parameters $r_1$ and $n_1$. Top row, PSNR of the basic
+		estimate; bottom row: final estimate. From left to right, results for
+		$\sigma = 10, 20, 30, 40$.} 
+	\label{fig:rank1-nsim1-psnr-gray}
 \end{figure*}
@@
 	\begin{center}
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s10_average_mono_neg-vs-pos-weights.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s20_average_mono_neg-vs-pos-weights.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s30_average_mono_neg-vs-pos-weights.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/bpsnr_r1-np1-curves_s40_average_mono_neg-vs-pos-weights.eps}\\
-
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s10_average_mono_neg-weights.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s20_average_mono_neg-weights.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s30_average_mono_neg-weights.eps}%
-		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r1-np1-curves_s40_average_mono_neg-weights.eps}\\
-	\end{center}
-	\caption{PSNR averaged over four grayscale sequences, when varying the
-		first stage parameters $r_1$ and $n_1$. Top row, PSNR of the basic
-		estimate; bottom row: final estimate. From left to right, results for
-		$\sigma = 10, 20, 30, 40$.} 
-	\label{fig:rank1-nsim1-psnr-gray}
-\end{figure*}
-
-\begin{figure*}[htpb!]
-	\begin{center}
 		\includegraphics[width=.25\textwidth]{figs/params_tables/fpsnr_r2-np2-curves_s10_average_derf_neg-weights.eps}%
@@
 
+\subsection{Search region and patch size}
+
+Setting the size of the search region implies a trade-off between denoising
+performance and running time: A larger search region takes longer to traverse
+but yields better results, since more similar patches can be found. We use the same 
+search region in both stages. The
+temporal search window is fixed at $w_t = 5$. The spatial search region is set at
+$w_x = 37$ for color videos and $w_x = 45$ for grayscale videos.
+With these values, the search region captures the $5$ frame trajectory of the
+target patch as long as it moves slower than $37/5 = 7.4$ pixels/frame (for
+color videos).
+
+Let us now consider the spatial patch
+size $s_x$, which is a key parameter in patch-based methods \cite{Buades2006,Kervrann2006,Boulanger2007}.
+%The distribution of the 
+%patch distances is a non-central Chi-squared distribution \cite{Dabov2007tip}
+%\pcomment{CHECK!}
+%with variance 
+%\[\textnormal{Var}\left\{\frac1{m}\|\ma q_1 - \ma q_2\|^2\right\} = \frac{8\sigma^2}{m}\left(\sigma^2 + \frac{\|\ma p_1 - \ma p_2\|^2}{m}\right),\]
+%where $m = s_x^2s_t$ is the total number of pixels in the patch.
+%*% Increasing the spatial patch size $s_x$ reduces the variance of the noise in the patch
+%*% distance. 
+%*% However, for larger
+%*% patches it becomes less likely to find other patches with a similar texture
+%*% pattern. The use spatio-temporal patches helps in solving this trade-off: for
+%*% instance, with a spatio-temporal patch of size $5\times 5\times 4$, we obtain
+%*% the same patch distance noise as with a spatial patch of size $10\times 10
+%*% \times 1$. Moreover, as discussed in \S \ref{sse:spatio-temporal-patches}, for
+%*% an approximately uniform motion, the 
+%*% amount of similar neighbors of a $5\times 5\times 4$ patch is roughly the same
+%*% as for a $5\times 5\times 1$ patch.
+%
+For color videos, we will set the spatial patch size at $s_x = 5$ for both
+stages, whereas for grayscale videos we use $s_x = 7$. Larger patches (up to $s_x = 9$) lead to an mild improvement of the
+results (on average). This improvement comes at a considerable increase in the
+computation time, since our current implementation is $\mathcal O(s_x^4)$.
+Thus, have found that a good compromise between computation time and quality is
+given by $s_x = 5$.
+
+The impact of the temporal patch size $s_t$ will be discussed later in Section
+\ref{sec:results}, where we show results varying $s_t$ between $s_t = 1$ and $s_t = 4$.
+
+\subsection{Rank and number of similar patches}
+
+The number of similar patches $n$ and the rank $r$ affect the estimation of the covariance
+matrix $C$, controlling the trade-off between the accuracy of the Gaussian model
+and the precision of the covariance matrix,
+which in turn has a direct effect on the denoising strength of the algorithm.
+% This have great impact on the bias-variance trade-off of the denoiser.
+%In practice, these parameters determine the denoising strength of the
+%algorithm. For example, using a large
+We found a compromise to this trade-off empirically, by trying different values
+of this parameter on a few training sequences and keeping the one that yields
+the best PSNR on average.
+
+%The number of similar patches $n$ and the rank $r$ affect the estimation of the covariance
+%matrix $C$, controlling the trade-off between the accuracy of Gaussian model
+%and precision of the covariance matrix.
+
+%\prm{Intuitively speaking, by setting a lower rank we are estimating a covariance
+%matrix in a lower dimensional subspace. Then, according to
+%\cite{Vershynin2012}, we require a smaller number of samples for a given
+%precision.} \pcomment{The previous argument is not good. I would like to have
+%some theoretical estimate on the number of samples to approximate a lower
+%rank covariance matrix, or equivalently, the number of samples to approximate
+%the largest principal directions. The point I would like to make, is that
+%the number of similar patches required is less if one only wants to estimate
+%the first principal eigenvectors. Maybe the answer lies in \cite{Halko2011}.}
+
+The plots in Figure \ref{fig:rank1-nsim1-psnr-color} show the PSNRs of the
+basic and final estimates as a function of the rank $r_1$, for several values
+of $n_{1}$. The curves correspond to an average over 20 frames clips extracted
+from four classical test color sequences, namely \emph{bus}, \emph{foreman},
+\emph{football} and
+\emph{tennis}. The sequences were contaminated with
+AGWN of standard deviation $\sigma = 10, 20, 30, 40$. 
+Figure \ref{fig:rank1-nsim1-psnr-gray} shows the results for a
+grayscale version of the same sequences. 
+%
+%
+
+\padd{For the basic estimate, we show two set of curves. The dashed curves were
+obtained by zeroing out negative eigenvalues of the estimated a priori covariance
+matrix $\widehat C$, computed according to \eqref{eq:learn_parameters}. The continuous curves 
+were obtained by retaining negative eigenvalues. In this case the MAP is estimated
+with an empirical Wiener filter that may have some negative coefficients.}
+
+\padd{For lower values of the rank parameter $r$, both curves coincide, since the first
+eigenvalues are positive. 
+For all noise levels, all curves of fixed $n_1$ present a first peak at a low value of the rank $r$.
+The behaviour of the basic estimate around this peak can be
+interpreted in the light of the theoretical results described in \S
+\ref{sse:covariance-estimation}.
+As the noise level increases, the rank at which the peak is attained
+shifts to the left. This makes sense, as the reliability of the computed eigenvectors
+decrease with increasing noise.
+%
+Also, for a fixed noise level, when the number of samples $n_1$ increases, the value
+of the peak increases also, and so does the rank at which it is attained.
+This is again explainable, as smaller groups obtained by keeping only the
+most similar patches have less modes of variation, and thus a worse signal-to-noise ratio
+in the eigenvectors with lower eigenvalues.}
+%As the group of patches grows
+%bigger, patches in the group are not as similar anymore, and a higher rank is
+%needed to allow for additional modes of variation.
+
+%The eigenvalues of $\widehat C$ are given by $\hat \lambda_i = \widehat \nu_i -
+%\sigma^2$, where $\widehat \nu_i$ are the eigenvalues of the empirical
+%\emph{a posteriori} covariance matrix.
+%In practice due to the estimation errors, several
+%$\widehat \nu_i$ are smaller than $\sigma^2$. These translate into negative
+%coefficients $w_{ii}$ in the empirical Wiener filter \eqref{eq:wiener_coeffs},
+%which result in a poorer estimation of the MAP.
+\padd{As the rank parameter increases, both curves diverge. 
+The dashed curves become almost constant at the point when
+most eigenvalues become negative. After that point increasing the
+rank has no effect if the negative eigenvalues are zeroed out.
+%
+Surprisingly, these negative coefficients have a positive effect on the final 
+result, creating the second peak for high values of the rank shown by the
+continuous plots. Currently we do not have an explanation for this behaviour
+although it is related to the aggregation: even if the estimated MAP for the
+patches in each group have larger errors, after aggregation these errors seem
+to cancel, yielding an overall better estimate of the clean image.}
+
+\padd{The final estimate shows the same qualitative behaviour with respect to the first
+stage parameters. The dashed curves obtained by zeroing out the negative
+eigenvalues are not shown to avoid cluttering the figure. Essentially the
+second step has the effect of reducing the differences between results obtained
+with different parameters. Based on these curves, we fix the first stage parameters at
+$n_1 = 300$ and $r_1 = 95$ for color videos, and at $n_1 = 300$ and $r_1 = 180$ for grayscale videos.}
+
+Using these parameters for the first stage, we analyzed the impact when varying the second stage
+parameters $n_2$ and $r_2$. The plots obtained are shown in Figure
+\ref{fig:rank2-nsim2-fpsnr}.
+%
+Note that in this case, the \emph{a
+priori} covariance matrix is estimated from the basic estimate (without having
+to subtract $\sigma^2I$). As a consequence, the are no negative filter coefficients.
+%
+In the second stage the quality drops when
+using a number of patches $n_2$ higher than $100$. This differs from the first stage,
+where a larger $n_1$ yielded a better PSNR.
+The reason for this lies probably in the fact that the patches have less noise,
+and a good estimate of the leading eigenvectors of the covariance matrix can be obtained
+with less patches. Furthermore, smaller groups of patches
+are better modelled by a Gaussian distribution.
+%\pcomment{I don't have an explanation for the curves for $\sigma = 10$. Precisely
+%in the lower noise level, the PSNR drops when $n_2$ is reduced, except for lower ranks.
+%This contradicts the argument given: for less noise, it should be always better to consider
+%less patches, not only for lower ranks.} 
+Based on these plots, we set the following values for the parameters
+\[r_2(\sigma) = 30 - \frac12(\sigma - 10),\quad\quad n_{2} = 100.\]
+
+All parameters are summarized in Table \ref{tab:parameters}.
+
+%Note that due to the coupling of the first and second stages, determining the
+%optimal values for the ranks $r_1, r_2$ and the number of patches $n_1,n_2$
+%would require a four dimensional parameter search which would be to costly.
+%
+%Instead, we fixed the first stage parameters, both for color and grayscale videos
+%at
+%\[r_1 = s_{x,1}^2s_{t,1}\quad\quad n_{1} = 400,\]
+%which we found to give good results. In doing so, we were conservative and
+%used the full rank covariance matrix to eliminate the least signal components.
+%%
+%We then ran a parameter search to determine $r_2$ and $n_{2}$.
+%The results are the ones shown in Figure \ref{fig:rank1-nsim1-psnr-gray}. This led
+%us to establish the following values as a function of $\sigma$:
+%%\[r_2(\sigma) = 40 - \frac13(\sigma - 10)\quad\quad n_{2} = 150.\]
+%\[r_2(\sigma) = 35 - \frac12(\sigma - 10)\quad\quad n_{2} = 100.\]
+%The same values are used for color and grayscale videos.
+%Note that a higher value for $n_{2}$ would give slightly worse results,
+%at a lower computational cost.
+
+\begin{table}
+	\centering
+	\begin{tabular}{l | c c | c c }
+		& \multicolumn{2}{c|}{color} 
+		& \multicolumn{2}{c}{grayscale}\\
+		Stage                            & 1st    & 2nd   & 1st   & 2nd   \\\hline\hline
+		$s_x$        &  5 & 5 & 7 & 7 \\
+		$s_t$        &  1--4  & 1--4  & 1--4  & 1--4  \\
+		$w_x$        &  37    & 37    & 45    & 45    \\
+		$w_x$        &   5    & 5     & 5     & 5    \\
+		$n$          & 300    & 100   & 300   & 100  \\
+		$r$          & 95   & $30 - \frac12(\sigma - 10)$    & 180  & $30 - \frac12(\sigma - 10)$   \\
+%		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
+%		Beta                        & 1    & 1.2  & 1    & 1.2  & 1    & 1.2 \\\hline
+	\end{tabular}
+	\caption{Selected parameters.}
+	\label{tab:parameters}
+\end{table}
+
+%Intuitively, smaller groups obtained by keeping only the most similar patches have 
+%only a few modes of variation and thus are better modelled with a low rank
+%covariance matrix. As the group of patches grows bigger, patches in the group
+%are not as similar anymore, and a higher rank is needed to model these additional 
+%variation.
+%To find appropriate values for these parameters, we compute denoising results
+%varying the rank $r$ and the number of similar patches $n$, while
+%keeping all other parameters fixed. Results are computed for four 20 frames clips
+%extracted from the sequences \emph{bus}, \emph{foreman}, \emph{football} and
+%\emph{tennis}, adding noise of $\sigma = 10, 20, 40$.
+%%
+%We do this for each stage, starting by the second.
+%
+%On this first experiment, the parameters of the first stage are fixed at:
+%\[w_x = 37,\,\,w_t = 5\,\,s_x = 5,\,\,s_t = 4,\,\,n = 375,\,\,r = 100.\]
+%\todo{Check these parameters}
+%Note that $r = 100$ is the full rank.
+%For the second stage, we fix $w_x = 37$, $w_t = 5$, $s_x = 5$ and $s_t = 3$, while varying 
+%$r$ in $10,20,\dots,80$ and $n$ in $50, 150,200,250$.
+%The results can be visualized in Figure \ref{fig:rank-nsim-image-stage2}. The images in the 
+%figure show the PSNR loss in dB with respect to the maximum value attained at each noise level.
+%White means 0dB (\ie the set of parameters where the maximum was attained) and black means a loss
+%greater or equal than 1dB.
+%
+%We can observe that, at constant $n$ there is an optimal value for the rank. Bellow
+%these value the PSNR drops sharply, and above it, the decay is slower. The
+%optimal rank for a given $n$ increases with $n$ and decreases with $\sigma$.
+%Best results are obtained for small $n$. However, this also entails a higher running time, 
+%since it increases the number of groups of similar patches that need to be
+%processed. We found a good compromise by setting $n = 150$ and $r$ as a decreasing function of $\sigma$:
+%\[r(\sigma) = 40 - \frac1{10}(\sigma - 40),\]
+%which corresponds to a line through $(s=10, r = 40)$ and $(s=40, r = 30)$.
+%
+%We now perform a similar search for the first stage, setting the second step parameters as:
+%\[w_x = 37,\,\,w_t = 5\,\,s_x = 5,\,\,s_t = 3,\,\,n = 150,\,\,r(\sigma).\]
+%The first stage parameters are as before, expect that we now vary $r$ in $10,20,\dots,100$
+%and $n$ in $50,100,\dots,650$. Results are shown in Figure
+%\ref{fig:rank-nsim-image-stage1}. Note that since our objective is to maximize
+%the final PSNR, we show here the final PSNR. 
+%The final and the basic PSNRs do not always
+%have the same behaviour. Improving the basic PSNR does not always lead to an
+%improvement in the final one. The reason for this is that it is preferable to
+%apply a conservative noise reduction leaving some noise in the basic estimate
+%(high variance but small bias). In the second step, this residual noise has
+%little effect on the estimation of the patch distances and the \emph{a priori} covariance
+%matrix. On the other hand, applying a more aggressive denoising in first step
+%might increase the basic PSNR, but the second step cannot recover the lost
+%signal components.
+%
+%In fact, best results are obtained using the full rank covariance matrix. 
+%In accordance to these observations, we will set the first values for $r$ and $n$ as:
+%\begin{equation}
+%	r = s_x^2s_t \quad\quad n = 350.
+%	\label{eq:stage1_parameters}
+%\end{equation}
+
+%
+%
+%
+%First we fix the parameters of the second stage at 
+%\[r = 16,\,\, n = 160,\,\, s_x = 5,\,\, s_t = 3,\,\, w_x = 37,\,\, w_t = 5,\]
+%and vary the parameters of the first stage. We considered ranks $r = 8, 16, 32, 64$,   
+%patch sizes $s_x = 3,5,7,9$ and number of patches $n = 80, 160, 320, 640$.
+%For all $4^3 = 64$ combinations, we considered three levels of noise $\sigma = 10, 20, 40$
+%and run our method on four sequences. The
+%sequences used were \emph{army, dog dance, evergreen} and \emph{walking} from
+%the Middlebury optical flow benchmark \cite{middleburyOflow}.
+%The sequences have 8 frames of size $584 \times 388$ (\emph{army}) and $640
+%\times 480$ (\emph{dog dance, evergreen} and \emph{walking}).
+%These sequences were chosen to have some variety of motions, textures, etc.
+%
+%Figure \ref{fig:rank-px-nsim-table-stage1} shows for each configuration of
+%parameters and level of noise, the average PSNR over the four sequences. The
+%cyan bars correspond to the basic estimate and the ones in magenta to the final
+%estimate.
+%
+%It can be observed that several parameter configurations can give very similar
+%results. For example, with $\sigma = 10$, equivalent results can be obtained 
+%with $s_x = 3, r = 16, n = 80$, $s_x = 5, r = 32, n = 160$
+%or  $s_x = 7, r = 64, n = 320$.
+%The one with the least computational cost is chosen. This means,
+%smaller patches sizes, smaller ranks, and a larger number of similar patches.
+%
+%Another thing to notice is that the final and the basic PSNRs do not always
+%have the same behaviour. Improving the basic PSNR does not always lead to an
+%improvement in the final one. The reason for this is that it is preferable to
+%apply a conservative noise reduction leaving some noise in the basic estimate
+%(high variance but small bias). In the second step, this residual noise has
+%little effect on the estimation of the patch distances and the \emph{a priori} covariance
+%matrix. On the other hand, applying a more aggressive denoising in first step
+%might increase the basic PSNR, but the second step cannot recover the lost
+%signal components.
+%
+%The strength of the denoising is controlled through the rank and the number of
+%patches in the group. For lower levels of noise, \ie $\sigma = 10$, better
+%PSRNs can be achieved with a higher rank and using a smaller number of similar
+%patches. When increasing the noise, the rank should be decreased and the number 
+%of similar patches increased.
+%
+%In accordance to these observations, we will set the parameters as a function of
+%$\sigma$ as follows:
+%\begin{equation}
+%	s_t = 5,\quad\quad r = \min(640/\sigma, r_{\text{max}}), \quad\quad n = 16\sigma.
+%	\label{eq:stage1_parameters}
+%\end{equation}
+%%\begin{align}
+%%	s_t &= 5\\
+%%	r &= \min(640/\sigma, r_{\text{max}}) \\
+%%	n &= 16\sigma. 
+%%	\label{eq:stage1_parameters}
+%%\end{align}
+%We set the maximum rank to be $r_{\text{max}} = \min(128,s_x^2s_t)$. Note that
+%$r = s_x^2s_t$ corresponds to the full rank.
+%
+%We now search for the optimum parameters for the second stage, setting the 
+%first stage parameters according to \eqref{eq:stage1_parameters}. The temporal
+%patch size is again set as $s_t = 3$ for both stages and the search regions are
+%kept as in \eqref{eq:search_region_parameters}. Figure
+%\ref{fig:rank-px-nsim-table-stage2} shows the average PSNRs over the four
+%sequences, obtained for each parameter configuration and each noise level.
+%
+%From these results, we fix the parameters as follows:
+%\begin{equation}
+%	s_x = 5,\quad r = \max( \min(320/\sigma, r_{\text{max}}), r_{\text{min}}), \quad n = 160.
+%	\label{eq:stage1_parameters}
+%\end{equation}
+%For the second stage, we set $r_{\text{max}} = \min(64,s_x^2s_t)$ and $r_{\text{min}} = 16$.
+
+%We will fix the temporal size and for the
+%temporal size of the patch we will vary it between $s_t = 1$ and $s_t = 4$ in
+%the results section.
+
 %For the experiments shown in \S \ref{sec:results} we used the following 
@@
 % offset
+
+\section{Results}
+\label{sec:results}
+
+In this section we present results obtained with the proposed
+method on some classical test sequences with Gaussian noise added.
+We consider separately the cases of grayscale and color videos.
+All results were computed with the parameters shown in Table \ref{tab:parameters}.
+The actual sequences can be downloaded from the project's
+website\footnote{\url{http://dev.ipol.im/~pariasm/video_nlbayes/}} in uncompressed format.
+
+\subsection{Results on grayscale videos}
+
+We present denoising results on six classic test sequences used commonly in the
+literature. We compared against two state-of-the-art methods: V-BM4D
+\cite{Maggioni2012}, and the method of Li, Zhang and Dai \cite{LiZhangDai2011}
+which we call I-SA-BM4D, since it can be regarded as an iterative version of BM4D \cite{Maggioni2013}
+using shape adaptive 3D patches, as in \cite{Ercole2005}.  
+For V-BM4D, we show results corresponding to two
+different choices of parameters. The method labeled V-BM4D-tip
+corresponds to the results reported
+in \cite{Maggioni2012}. The results labeled V-BM4D-mp were
+obtained using the implementation available online \cite{bm4dcode}. This
+implementation provides three parameter profiles of increasing quality and
+complexity: ``low complexity profile'', ``normal profile'' and ``modified
+profile''. We show the results obtained with the modified profile.
+
+Each sequence was contaminated with AGWN of $\sigma =
+10,20,30,40$. Table \ref{tab:psnr-classic-gray} shows the
+PSNR values obtained after denoising. For our method, we show results varying the temporal
+component of the patch size between $s_t = 1$ (2D patch) and $s_t = 4$ frames.
+For our method and V-BM4D-mp we show the PSNR of the basic estimate as well.
+
+The best results by a large margin are the ones reported in
+\cite{LiZhangDai2011}. This method builds uppon BM4D, which in \cite{Maggioni2013}
+is applied to volumetric imagery. The authors explored its applicability to video 
+and the results show that it is inferior to V-BM4D, at least 
+for low to moderate noise levels. The method of Li, Zhang and Dai \cite{LiZhangDai2011} 
+considers shape adaptive patches, and performs several iterations. In each iteration,
+the previous iterate is used as an oracle to compute patch distances.
+\padd{An additional difference is that the oracle is not used to determine the
+signal components for the Wiener filter. Instead, these are estimated with a fixed
+point iteration from the original noisy patches.}
+
+We can see that our results outperform the ones of V-BM4D, for all sequences and 
+for all noise levels. The results reported by \cite{LiZhangDai2011} show that there
+is still room for improvement (albeit perhaps at a higher computational cost).
+%
+We have attempted iterating our method as in \cite{LiZhangDai2011},
+but we have not found yet a significant improvement. Something similar was
+reported in \cite{Lebrun2013ipol,Lebrun2013a} for the NL-Bayes method in still
+images. %It may be that the current parameters are not suitable for
+%iteration. 
+A more systematic study is has to be conducted before drawing any
+conclusions about iterative versions of the algorithm.
+%This is the matter of ongoing work, but is out of the scope of the paper.
+%Still, it is early to exclude iteration as an valid option to
+%further improve the denoising performance.
+
+For a qualitative comparison, Figure \ref{fig:results_mobile_mono}
+shows two details of the results obtained by our method and V-BM4D for the
+\emph{mobile} sequence, for noise of $\sigma = 10, 20, 40$. It can be observed
+that the proposed method preserves the fine details betters, such as the thin
+lines of the drawing in the first example, or the calendar numbers in the
+second example. It also exhibits a higher temporal consistency, as will be
+shown in \S \ref{sse:temporal-consistency}.
+
+Regarding the running time, let us note that the modified profile has a
+computation time lower to that of our method. Running with a
+single core in an Intel Xeon X7560 (2.27GHz) CPU, 
+our current implementation takes on average $XXs$ per frame for a video of CIF
+resolution ($352\times288$). V-BM4D takes $44s$ with the modified profile.
+The running times of \cite{LiZhangDai2011} are not reported, but we expect them
+to be significantly higher given that the algorithm is iterative, with each iteration 
+being comparable to one of the stages of V-BM4D.
+\pcomment{TODO: Compute running times!!!}
+\pcomment{We should include computation times for grayscale videos, instead of color}
 
@@
 
+\begin{landscape}
 \begin{table*}[htp!]
@@
 \end{table*}
+\end{landscape}
 
@@
 %\end{table*}
-
-\section{Results}
-\label{sec:results}
-
-In this section we present results obtained with the proposed
-method on some classical test sequences with Gaussian noise added.
-We consider separately the cases of grayscale and color videos.
-All results were computed with the parameters shown in Table \ref{tab:parameters}.
-The actual sequences can be downloaded from the project's
-website\footnote{\url{http://dev.ipol.im/~pariasm/video_nlbayes/}} in uncompressed format.
-
-\subsection{Results on grayscale videos}
-
-We present denoising results on six classic test sequences used commonly in the
-literature. We compared against two state-of-the-art methods: V-BM4D
-\cite{Maggioni2012}, and the method of Li, Zhang and Dai \cite{LiZhangDai2011}
-which we call I-SA-BM4D, since it can be regarded as an iterative version of BM4D \cite{Maggioni2013}
-using shape adaptive 3D patches, as in \cite{Ercole2005}.  
-For V-BM4D, we show results corresponding to two
-different choices of parameters. The method labeled V-BM4D-tip
-corresponds to the results reported
-in \cite{Maggioni2012}. The results labeled V-BM4D-mp were
-obtained using the implementation available online \cite{bm4dcode}. This
-implementation provides three parameter profiles of increasing quality and
-complexity: ``low complexity profile'', ``normal profile'' and ``modified
-profile''. We show the results obtained with the modified profile.
-
-Each sequence was contaminated with AGWN of $\sigma =
-10,20,30,40$. Table \ref{tab:psnr-classic-gray} shows the
-PSNR values obtained after denoising. For our method, we show results varying the temporal
-component of the patch size between $s_t = 1$ (2D patch) and $s_t = 4$ frames.
-For our method and V-BM4D-mp we show the PSNR of the basic estimate as well.
-
-The best results by a large margin are the ones reported in
-\cite{LiZhangDai2011}. This method builds uppon BM4D, which in \cite{Maggioni2013}
-is applied to volumetric imagery. The authors explored its applicability to video 
-and the results show that it is inferior to V-BM4D, at least 
-for low to moderate noise levels. The method of Li, Zhang and Dai \cite{LiZhangDai2011} 
-considers shape adaptive patches, and performs several iterations. In each iteration,
-the previous iterate is used as an oracle to compute patch distances.
-\padd{An additional difference is that the oracle is not used to determine the
-signal components for the Wiener filter. Instead, these are estimated with a fixed
-point iteration from the original noisy patches.}
-
-We can see that our results outperform the ones of V-BM4D, for all sequences and 
-for all noise levels. The results reported by \cite{LiZhangDai2011} show that there
-is still room for improvement (albeit perhaps at a higher computational cost).
-%
-We have attempted iterating our method as in \cite{LiZhangDai2011},
-but we have not found yet a significant improvement. Something similar was
-reported in \cite{Lebrun2013ipol,Lebrun2013a} for the NL-Bayes method in still
-images. %It may be that the current parameters are not suitable for
-%iteration. 
-A more systematic study is has to be conducted before drawing any
-conclusions about iterative versions of the algorithm.
-%This is the matter of ongoing work, but is out of the scope of the paper.
-%Still, it is early to exclude iteration as an valid option to
-%further improve the denoising performance.
-
-For a qualitative comparison, Figure \ref{fig:results_mobile_mono}
-shows two details of the results obtained by our method and V-BM4D for the
-\emph{mobile} sequence, for noise of $\sigma = 10, 20, 40$. It can be observed
-that the proposed method preserves the fine details betters, such as the thin
-lines of the drawing in the first example, or the calendar numbers in the
-second example. It also exhibits a higher temporal consistency, as will be
-shown in \S \ref{sse:temporal-consistency}.
-
-Regarding the running time, let us note that the modified profile has a
-computation time lower to that of our method. Running with a
-single core in an Intel Xeon X7560 (2.27GHz) CPU, 
-our current implementation takes on average $XXs$ per frame for a video of CIF
-resolution ($352\times288$). V-BM4D takes $44s$ with the modified profile.
-The running times of \cite{LiZhangDai2011} are not reported, but we expect them
-to be significantly higher given that the algorithm is iterative, with each iteration 
-being comparable to one of the stages of V-BM4D.
-\pcomment{TODO: Compute running times!!!}
-\pcomment{We should include computation times for grayscale videos, instead of color}
 
@@
 
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,image_denoising,video_denoising,covariance_estimation}
+\bibliographystyle{plain}
+\bibliography{image_denoising,video_denoising,covariance_estimation}
 

### 2016-07-20 tools/compute_bayes_estimate.m
[tools] minor

@@ -18,18 +18,25 @@ if isempty(bsic),
 	sigma_bsic = sigma;
 end
 
-
 % center
 %mean_nisy = 128 + 0*mean(nisy, 2);
 %mean_bsic = 128 + 0*mean(bsic, 2);
 mean_nisy = mean(nisy, 2);
 mean_bsic = mean(bsic, 2);
-nisy = nisy - mean_nisy*ones(1,n);
-bsic = bsic - mean_bsic*ones(1,n);
+%nisy = Diag(wwx)*(nisy - mean_nisy*ones(1,n));
+%bsic = Diag(wwx)*(bsic - mean_bsic*ones(1,n));
+
+nisy = (nisy - mean_nisy*ones(1,n));
+bsic = (bsic - mean_bsic*ones(1,n));
 
 if ~isempty(orig),
 	orig = orig - mean_nisy*ones(1,n);
 end
+
+
+% use window (spatial only)
+%SigmaNoise = sigma^2*U'*diag(wwx.^2)*U;
+
 
 
 if isempty(S),
@@ -37,6 +44,11 @@ if isempty(S),
 	if isempty(U),
 		% covariance matrix
 		C = 1/n*bsic*bsic';
+
+		% redefine rank as...
+		if (rank >= 0), rank = min(rank, n-1);
+		else            rank = min(d   , n-1);
+		end
 		
 		% eigendecomposition
 		if rank > 0 && rank < d,
@@ -50,6 +62,7 @@ if isempty(S),
 	else
 		% project data vectors onto basis
 		S = diag(mean((U'*bsic).^2,2));
+%		S = diag(mean((U'*diag(wwx)*bsic).^2,2));
 	end
 	
 	

### 2016-07-20 tools/nlbayes.m

@@ -6,16 +6,16 @@
 
 
 % parameters
-prms1.wx = 37;
-prms1.wt = 2;
-prms1.px = 7;
+prms1.wx = 25;
+prms1.wt = 0;
+prms1.px = 5;
 prms1.pt = 3;
 prms1.np = 10;
 prms1.r  = -1;
 
-prms2.wx = 37;
+prms2.wx = 25;
 prms2.wt = 2;
-prms2.px = 7;
+prms2.px = 5;
 prms2.pt = 3;
 prms2.np = 10;
 prms2.r  = -1;
@@ -88,8 +88,10 @@ orig = orig(cropy(1):cropy(2),cropx(1):cropx(2),:,cropt(1):cropt(2));
 %disp(20*log10(255/sqrt(norm(o(:) - d5p(:))^2/length(o(:)))))
 
 prms1.filter_type = 'neg';
-[deno1_neg, aggw1, bias1_neg] = nlbayes_step(nisy, []       , orig, sigma, prms1);
-[deno2_neg, aggw2, bias2_neg] = nlbayes_step(nisy, deno1_neg, orig, sigma, prms2);
+%[deno1_neg, aggw1, bias1_neg] = nlbayes_step(nisy, []       , orig, sigma, prms1);
+%[deno2_neg, aggw2, bias2_neg] = nlbayes_step(nisy, deno1_neg, orig, sigma, prms2);
+[deno1_neg, aggw1, bias1_neg] = nlbayes_step(nisy, []       , [], sigma, prms1);
+[deno2_neg, aggw2, bias2_neg] = nlbayes_step(nisy, deno1_neg, [], sigma, prms2);
 
 b1n = bias1_neg(5:end-5,5:end-5,:,:);
 b2n = bias2_neg(5:end-5,5:end-5,:,:);

### 2016-07-20 src/NlBayes/VideoNLBayes.h
minor

@@ -17,8 +17,8 @@
 #include "../Utilities/Utilities.h"
 #include "LibDCT.h"
 
-#define DEBUG_SHOW_WEIGHT
-#define DEBUG_COMPUTE_GROUP_ERROR
+//#define DEBUG_SHOW_WEIGHT
+//#define DEBUG_COMPUTE_GROUP_ERROR
 //#define DEBUG_SHOW_PATCH_GROUPS
 
 namespace VideoNLB

### 2016-07-20 doc/201503_dxo/slides_dxo.tex

% \documentclass{beamer}
\documentclass[mathserif]{beamer}

\mode<presentation> {
% \usetheme{Madrid}
%\usetheme{default}
\usetheme{Boadilla}
% \usecolortheme{beaver}
% \usecolortheme{rose}
}
% removes navigation symbols
\setbeamertemplate{navigation symbols}{}

\usepackage[english,activeacute]{babel}
\usepackage[english]{layout}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{pgf}
%\usepackage{movie15}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage[multidot]{grffile}
\usepackage{ucs}
% \usepackage[T1]{fontenc}
%\usepackage{subfigure}

% from rida's preamble
\usepackage{epsfig,xspace}
\usepackage{setspace}
\usepackage{threeparttable}
\usepackage{subfloat}
\usepackage{pstricks,pst-node}
\usepackage[normal,tight,center]{subfigure}
\usepackage{pifont}
\usepackage{multimedia}
%\usepackage{media9}
%\usepackage{enumitem}
\usepackage{animate}
\usepackage{caption}
\usepackage{multirow}

% the following is used to bind frames with the same frame number
\usepackage{etoolbox}

\newcounter{multipleslide}

\makeatletter%
\newcommand{\multipleframe}{%
\setcounter{multipleslide}{\value{framenumber}}
\stepcounter{multipleslide}
\patchcmd{\beamer@@tmpl@footline}% <cmd>
	{\insertframenumber}% <search>
	{\themultipleslide}% <replace>
	{}% <success>
	{}% <failure>
}
\newcommand{\restoreframe}{%
\patchcmd{\beamer@@tmpl@footline}% <cmd>
	{\themultipleslide}% <search>
	{\insertframenumber}% <replace>
	{}% <success>
	{}% <failure>
\setcounter{framenumber}{\value{multipleslide}}%
}
\makeatother%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Running 'pdflatex --shell-escape...' will automatically recognize
% the eps files in the includegraphics and convert them to pdf.
% No file rename nor change to the document is needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{ifpdf}
\ifpdf
\DeclareGraphicsRule{.eps}{pdf}{.pdf}{`epstopdf #1}
\usepackage{epstopdf}
\epstopdfsetup{suffix=-\SourceExt-converted-to}
\pdfcompresslevel=0   %\pdfcompresslevel=9
\pdfcompresslevel0
\fi

% para poder incluir figuras .pdftex del xfig
\DeclareGraphicsRule{.pdftex}{pdf}{.pdftex}{}

\newcommand{\nada}[1]   {}

\newcommand{\ma}[1]{\boldsymbol{#1}}
\newcommand{\ie}{\textit{i.e.} }
\newcommand{\eg}{\textit{e.g.} }
\newcommand{\etal}{\textit{et al}. }
\newcommand{\tras}[1]{#1^{\mathrm{T}}}
\newcommand{\herm}[1]{#1^{\mathrm{H}}}
\newcommand{\con}[1]{#1^{\mathrm{*}}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\tech}[1]{\overline{#1}}
\newcommand{\nspace}{\!\!\!\!}
\newcommand{\nmbr}[1]{\oldstylenums{#1}}

\newcommand{\eps}{\varepsilon}
\newcommand{\R}{{\mathbb R}}
\newcommand{\Q}{{\mathbb Q}}
\newcommand{\N}{{\mathbb N}}
\newcommand{\Z}{{\mathbb Z}}
\newcommand{\C}{{\mathcal C}}
\renewcommand{\H}{{\mathcal H}}
\newcommand{\F}{{\mathcal F}}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\median}{median}

\definecolor{MyOrange}  {cmyk}{0,0.73,1.0,0}
\definecolor{MyGreen}   {cmyk}{1,0,1,0.0}

% Rida's colors and commands
\definecolor{Red}{rgb}{0.9,0.0,0.1}
\definecolor{Brown}{rgb}{0.55,0.27,0.1}
\definecolor{Brownie}{rgb}{0.75,0.27,0.1}
\definecolor{Yellow}{rgb}{1,1,0}
\definecolor{White}{rgb}{1,1,1}
\definecolor{formule}{rgb}{0.75,0.27,0.1}
\definecolor{formule}{rgb}{.7,1,0}
\definecolor{violet}{rgb}{0.7,0,.9}
\definecolor{darkgreen}{rgb}{0,.7,0}

%\newcommand{\reference}[1] {{\scriptsize \color{gray}  #1 }} 
\newcommand{\reference}[1] {{\color{gray}  #1 }} 
\newcommand{\rmk}[1]{{\color{Red} #1}}

%\theoremstyle{plain}\newtheorem{theorem}{Theorem}[chapter]
%\theoremstyle{plain}\newtheorem{proposition}{Proposition}[chapter]
%\theoremstyle{plain}\newtheorem{lemma}{Lemma}[chapter]
%\theoremstyle{definition}\newtheorem{definition}{Definition}[chapter]

% New definition of square root:
% it renames \sqrt as \oldsqrt
\let\oldsqrt\sqrt
% it defines the new \sqrt in terms of the old one
\def\sqrt{\mathpalette\DHLhksqrt}
\def\DHLhksqrt#1#2{%
\setbox0=\hbox{$#1\oldsqrt{#2\,}$}\dimen0=\ht0
\advance\dimen0-0.2\ht0
\setbox2=\hbox{\vrule height\ht0 depth -\dimen0}%
{\box0\lower0.4pt\box2}}

%gets rid of bottom navigation bars
% \setbeamertemplate{footline}[frame number]{}

%gets rid of navigation symbols
\setbeamertemplate{navigation symbols}{}

\title[Video denoising]{$\,$ \\ $\,$ \\ Preliminary results on patch-based video denoising}
\author[Pablo Arias]{Pablo Arias\\ Jean-Michel Morel\vspace{.5cm}\\ $\,$ \\ $\,$ \\ $\,$ \\
Meeting CMLA-DxO \\March 17, 2015}
\institute[CMLA]{}
\date[]{}

%\author[Pablo Arias]{Pablo Arias$^*$, Vicent Caselles$^*$, Gabriele Facciolo$^\dagger$ \\ Rida Sadek$^*$, Guillermo Sapiro$^\ddagger$ \\ $\,$ \\  $\,$ \\ $\,$ \\ $\,$ \\
%\institute[UPF]{* Universitat Pompeu Fabra\\ $\dagger$ ENS Cachan \\ $\ddagger$ Duke University}

% \AtBeginSection[]  % "Beamer, do the following at the start of every section"
% {\begin{frame}<beamer>
% \frametitle{Outline} % make a frame titled "Outline"
% \tableofcontents[currentsection]  % show TOC and highlight current section
% \end{frame}}
%
% \AtBeginSubsection[]  % "Beamer, do the following at the start of every section"
% {\begin{frame}<beamer>
% \frametitle{Outline} % make a frame titled "Outline"
% \tableofcontents[currentsection,currentsubsection]  % show TOC and highlight current section
% \end{frame}}

\graphicspath{{./figures/}}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

% \begin{frame}{Gradient-domain video editing}
% 	\begin{center}
% 		\includegraphics[width=0.19\textwidth]{figures_rida/vid_edit/screen_seq_screen_025_cropped}
% 		\includegraphics[width=0.19\textwidth]{figures_rida/vid_edit/screen_seq_mask_red_031_cropped}
% 		\includegraphics[width=0.19\textwidth]{figures_rida/vid_edit/screen_seq_mask_red_037_cropped}
% 		\includegraphics[width=0.19\textwidth]{figures_rida/vid_edit/screen_seq_mask_red_041_cropped}
% 		\includegraphics[width=0.19\textwidth]{figures_rida/vid_edit/screen_seq_screen_045_cropped}	 
% 		\\
% 		\includegraphics[width=0.19\textwidth]{figures_rida/vid_edit/screen_seq_screen_025_cropped}
% 		\includegraphics[width=0.19\textwidth]{figures_rida/vid_edit/screen_seq_screen_031_cropped}
% 		\includegraphics[width=0.19\textwidth]{figures_rida/vid_edit/screen_seq_screen_037_cropped}
% 		\includegraphics[width=0.19\textwidth]{figures_rida/vid_edit/screen_seq_screen_041_cropped}
% 		\includegraphics[width=0.19\textwidth]{figures_rida/vid_edit/screen_seq_screen_045_cropped}\\
% 	\end{center}
% \end{frame}

\section{Introduction}

\begin{frame}{Introduction}

	We are exploring several patch-based approaches for video denoising.
	We have currently extended to video:

	\vspace{.2cm}

	\begin{enumerate}
		\item[1.] non-local Bayes (based on IPOL C++ code of Marc Lebrun)
		\item[2.] a two-stage version of non-local means (based on same code)
	\end{enumerate}

	\vspace{1cm}

	IPOL demos for both methods, together with:

	\vspace{.2cm}

	\begin{enumerate}
		\item[1.] Video BM3D (Matlab/C code by Dabov, Danieyan, Foi; only grayscale)
		\item[2.] BM4D (Matlab/C code by Maggioni, Foi)
	\end{enumerate}

\end{frame}

\begin{frame}{Video NL-Bayes}

	Straightforward adaptation of non-local Bayes to video: patches are
	searched for in a spatio-temporal search window, of size $W_x \times W_x
	\times W_t$.

	\pause

	\vspace{.6cm}

	Parameters based on default parameters for NL-Bayes for images:
	\vspace{.2cm}
	\begin{itemize} \itemsep=.2cm
		\item $W_t$ selected by user
		\item The number of similar patches $N_{\text{sim}}$ used for the
			Bayesian estimation step: 
			\[N_{\text{sim}} = N_{\text{sim},0} W_t,\]
			where $N_{\text{sim},0}$ default parameter for image NL-Bayes.
		\item Rest of parameters are the default ones from image NL-Bayes.
	\end{itemize}

	\vspace{1cm}

\end{frame}

\begin{frame}{Video two-stage NL-Means}

	As in Video NL-Bayes, we build groups of similar patches which are jointly
	denoised.

	\vspace{.5cm}

	Instead of performing the Bayesian group estimation, we estimate each patch
	in the group by \structure{averages weighted by patch similarity} of the
	group patches, as in NL-means.

	\vspace{.5cm}

	Patches in group are then \structure{aggregated to form an image}.

	\vspace{.5cm}

	Two stages: basic and final estimates. In the final stage, the basic
	estimate is used to build the groups of similar patches and to compute the
	similarity weights.

\end{frame}

\multipleframe
\begin{frame}{Video two-stage NL-Means}

	\structure{Basic estimate:} For each $x$:

	\begin{enumerate}
		\item[1.] Build a group $\mathcal G_x$ of patches similar to $\hat p_x$ ($L^2$
			distance between $Y$ component).

		\item[2.] For each noisy patch $\hat p_y$ in the group $\mathcal G_x$:

	\[p_y^{\text{NLM},b} = \frac1{C}\sum_{\hat p_z\in\mathcal G_x} w(\hat p_y, \hat p_z)\hat p_z.\]

		Weights computed following [Buades, Coll, Morel; IPOL'13]:

	\[\quad\displaystyle w(\hat p_y, \hat p_z) = \exp\left(-\frac1{h_b^2}\max(\|\hat p_y - \hat p_z\|_Y^2, 2\sigma^2/3)\right)\]

		\item[3.] Aggregate the estimated patches $p_y^{\text{NLM},b}$ on an image $u_b$.

	\end{enumerate}

\end{frame}

\begin{frame}{Video two-stage NL-Means}

	\structure{Final estimate:} For each $x$:

	\begin{enumerate}
		\item[1.] Build a group $\mathcal G_x$ of noisy patches such that their basic
			estimate is similar to $p_x^b$ ($L^2$ distance
			between color patches of $y_b)$.

		\item[2.] For each noisy patch $\hat p_y$ in the group $\mathcal G^n_x$:

	\[p_y^{\text{NLM},f} = \frac1{C}\sum_{\hat p_z\in\mathcal G_x} w(p^b_y, p^b_z)\hat p_z.\]

		Weights computed following [Buades, Coll, Morel; IPOL'13]:

	\[w(p^b_y, p^b_z) = \exp\left(-\frac1{h_f^2}\max(\|p^b_y - p^b_z\|_{\text{RGB}}^2, 2\gamma\sigma^2)\right).\]

		\item[3.] Aggregate the estimated patches $p_y^{\text{NLM},f}$ on an image $u$.

	\end{enumerate}

\end{frame}
\restoreframe

\begin{frame}{Video two-stage NL-Means}

	\begin{itemize} \itemsep=.4cm
		\item $W_t$ selected by user.
		\item Rest of patch search parameters based on default parameters of
			Video NL-Bayes.
		\item Parameters for basic NL-means estimate based on default parameters
			in [Buades, Coll, Morel; IPOL'13]. 
		\item Parameters for final NL-means estimate set by trial-and-error based
			on a few results.
	\end{itemize}

	\vspace{1cm}

\end{frame}

\multipleframe
\begin{frame}{Video BM3D}

	As in Video NL-Bayes, groups of similar patches are jointly denoised. Groups
	are considered 3D signals, which are filtered in a 3D separable transformed
	domain.

	\vspace{.7cm}

	\structure{Basic estimate:} For each $x$:

	\begin{enumerate}\itemsep=.5cm
		\item[1.] Build a 3D group $\mathcal G_x$ of noisy patches similar to
			$\hat p_x$ (using $L^2$ distance between $Y$ component and predictive
			search).

		\item[2.] Hard thresholding on separable transform domain (separable
			bi-orthogonal wavelet on spatial axes + Haar wavelet
			on group axis).

		\item[3.] Aggregate the estimated patches on an image $u_b$, the
			basic estimate.

	\end{enumerate}

\end{frame}

\begin{frame}{Video BM3D}

	As in Video NL-Bayes, groups of similar patches are jointly denoised. Groups
	are considered 3D signals, which are filtered in a 3D separable transformed
	domain.

	\vspace{.7cm}

	\structure{Final estimate:} For each $x$:

	\begin{enumerate}\itemsep=.5cm
		\item[1.] Build 3D groups $\mathcal G_x$ of noisy patches \structure{and
			basic patches} similar to $p^b_x$ (using $L^2$ distance between $Y$
			component \structure{of basic estimate} and predictive search).

		\item[2.] \structure{Wiener filtering} on separable transform domain (\structure{2D DTC} on spatial
			axes + Haar wavelet on group axis). \structure{Coefficients of Wiener filter are estimated
			from the transformed basic group.}

		\item[3.] Aggregate the estimated patches on an image $u_f$, the
			\structure{final estimate}.

	\end{enumerate}

\end{frame}
\restoreframe

\multipleframe
\begin{frame}{Video BM4D}

	Collaborative filtering of \structure{spatio-temporal 3D patches}: a patch
	that spans several frames. In each frame, the top-left corner follows a
	motion trajectory.

	\vspace{.6cm}

	\structure{Basic estimate:}
	\begin{enumerate} \itemsep=.5cm
		\item[1.] For each $x$ build a trajectory $\text{Traj}(x)$ of a variable
			number of frames (block matching in noisy video $+$ temporal smoothing).
		\item[2.] For each $x$, let $p_x$ be the spatio-temporal patch at $x$:
			\begin{enumerate} \itemsep=.2cm
				\item[2.1.] Build a 4D group $\mathcal G_x$ by stacking 3D noisy
					spatio-temporal patches similar to $p_x$ ($L^2$ distance between
					$Y$ component).
				\item[2.2.] Thresholding in transform domain of 4D group
					using separable 4D transform. Different basis for different
					spatial, temporal and ``group'' dimensions.
				\item[2.3.] Weighted aggregation based on 4D transform sparsity.
			\end{enumerate}
	\end{enumerate}

\end{frame}

\begin{frame}{Video BM4D}

	Collaborative filtering of \structure{spatio-temporal 3D patches}: a patch
	that spans several frames. In each frame, the top-left corner follows a
	motion trajectory.

	\vspace{.6cm}

	\structure{Final estimate:}
	\begin{enumerate} \itemsep=.5cm
		\item[1.] For each $x$ build a trajectory $\text{Traj}(x)$ of a variable
			number of frames (block matching in \structure{basic estimate} $+$ temporal smoothing).
		\item[2.] For each $x$, let $p_x$ be the spatio-temporal patch at $x$:
			\begin{enumerate} \itemsep=.2cm
				\item[2.1.] Build a 4D group $\mathcal G_x$ by stacking 3D noisy
					spatio-temporal patches similar to $p_x$ ($L^2$ distance in
					\structure{basic estimate}).
				\item[2.2.] \structure{Wiener filtering} in transform domain of 4D
					group using separable 4D transform. Different basis for
					different spatial, temporal and ``group'' dimensions.
				\item[2.3.] Weighted aggregation based on 4D \structure{filtered coefficients}.
			\end{enumerate}
	\end{enumerate}

\end{frame}
\restoreframe

\begin{frame}[fragile]{IPOL demos and results}
	Demos on:\\
	\verb+http://dev.ipol.im/~pariasm/ipol_demo/video_nlbayes/+\\
	\verb+http://dev.ipol.im/~pariasm/ipol_demo/vbm3d/+\\
	\verb+http://dev.ipol.im/~pariasm/ipol_demo/vbm4d/+

	\vspace{2cm}

	Show results\dots

\end{frame}

\multipleframe
\begin{frame}{PSNRs of basic estimates}

	{\small
	\begin{tabular}{| c | c |c c c c c|}
		\hline \hline
		$\sigma$  & Method \textbackslash Video & Army & DogDance & Evergreen & Mequon & Walking \\\hline\hline
		\multirow{5}{*}{$10$} & BM4D           & \textbf{37.48} & \textbf{35.60} & \textbf{35.29} & \textbf{37.89} & \textbf{38.67} \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &         34.17  &         33.31  &         32.99  &         34.76  &         34.82  \\%\cline{2-7}
		                      & VNLB $W_t = 1$ &         36.16  &         34.67  &         34.26  &         37.09  &         37.22  \\%\cline{2-7}
		                      & VNLB $W_t = 2$ &         36.46  &         34.82  &         34.40  &         37.33  &         37.58  \\\hline
%									 
		\multirow{5}{*}{$25$} & BM4D           & \textbf{32.24} & \textbf{31.07} & \textbf{30.48} &         32.89  & \textbf{33.54} \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &         30.10  &         29.47  &         29.02  &         30.88  &         30.95  \\%\cline{2-7}
		                      & VNLB $W_t = 1$ &         31.89  &         30.80  &         30.28  &         32.84  &         32.96  \\%\cline{2-7}
		                      & VNLB $W_t = 2$ &         32.18  &         30.97  &         30.45  & \textbf{33.10} &         33.26  \\\hline
%									 
		\multirow{5}{*}{$40$} & BM4D           & \textbf{29.53} & \textbf{28.59} &         27.93  &         29.94  & \textbf{30.55} \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &         26.99  &         26.58  &         26.23  &         27.56  &         27.59  \\%\cline{2-7}
		                      & VNLB $W_t = 1$ &         29.10  &         28.25  &         27.82  &         29.77  &         29.85  \\%\cline{2-7}
									 & VNLB $W_t = 2$ &         29.46  &         28.50  & \textbf{28.07} & \textbf{30.13} &         30.25  \\\hline\hline
	\end{tabular}}

\end{frame}

\begin{frame}{PSNRs of final estimates}

	{\small
	\begin{tabular}{| c | c |c c c c c|}
		\hline \hline
		$\sigma$  & Method \textbackslash Video & Army & DogDance & Evergreen & Mequon & Walking \\\hline\hline
		\multirow{5}{*}{$10$} & BM4D           & \textbf{37.77} & \textbf{35.70} & \textbf{35.40} &         38.09  &         38.85  \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &         36.38  &         34.88  &         34.27  &         37.90  &         38.10  \\%\cline{2-7}
		                      & VNLB $W_t = 1$ &         37.17  &         35.31  &         34.80  & \textbf{38.79} & \textbf{39.16} \\%\cline{2-7}
		                      & VNLB $W_t = 2$ &         37.18  &         35.27  &         34.77  &         38.64  &         39.10  \\\hline
%									 
		\multirow{5}{*}{$25$} & BM4D           &         32.91  & \textbf{31.50} & \textbf{30.94} &         33.60  &         34.27  \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &         32.11  &         30.88  &         30.18  &         33.30  &         33.19  \\%\cline{2-7}
		                      & VNLB $W_t = 1$ &         33.07  &         31.45  &         30.70  &         34.28  &         34.14  \\%\cline{2-7}
		                      & VNLB $W_t = 2$ & \textbf{33.19} &         31.44  &         30.69  & \textbf{34.34} & \textbf{34.31} \\\hline
%									 
		\multirow{5}{*}{$40$} & BM4D           &         30.42  & \textbf{29.29} &         28.65  &         31.02  & \textbf{31.64} \\%\cline{2-7}
		                      & VNLB $W_t = 0$ &         29.51  &         28.48  &         27.90  &         30.30  &         30.15  \\%\cline{2-7}
		                      & VNLB $W_t = 1$ &         30.62  &         29.19  &         28.61  &         31.31  &         31.11  \\%\cline{2-7}
									 & VNLB $W_t = 2$ & \textbf{30.81} &         29.24  & \textbf{28.66} & \textbf{31.43} &         31.35  \\\hline\hline
	\end{tabular}}

\end{frame}
\restoreframe

% \section{Experimental results}
% 
% %%%%%%%%%%%%%BOB Experiment%%%%%%%%%%%%%%%%%%%%%%%%
% \multipleframe
% 	\begin{frame}{Experimental results: One lid setting}
% 		\begin{center}
% 			\animategraphics[autoplay,loop,height=5cm]{8}{figures_rida/pres/bob_ori/}{002}{032}
% 		\end{center}
% 
% 		\centerline{Fast illumination change. \structure{Original Sequence}}
% 	\end{frame}
% 	
% 	
% 	\begin{frame}{Experimental results: One lid setting}
% 		\begin{center}
% 			\animategraphics[autoplay,loop,height=5cm]{8}{figures_rida/pres/bob_editing/}{002}{032}
% 		\end{center}
% 
% 		\centerline{Fast illumination change: \structure{Editing Domain}}
% 	\end{frame}
% 	
% 	
% 	\begin{frame}{Experimental results: One lid setting}
% 		\begin{center}
% 			\animategraphics[autoplay,loop,height=5cm]{8}{figures_rida/pres/bob_out/}{002}{032}
% 		\end{center}
% 
% 		\centerline{Fast illumination change: \structure{Output}}
% 	\end{frame}
% 
% 	
% \begin{frame}{Experimental results: One lid setting}
% 
% 	\begin{center}
% 		%output
% 		\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_gbc_003}
% 		\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_gbc_013}
% 		\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_gbc_019}
% 		\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_gbc_020}
% 		\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_gbc_029}
% 
% 		%output BC
% 		\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_bc_003}
% 		\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_bc_013}
% 		\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_bc_019}
% 		\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_bc_020}
% 		\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_bc_029}
% 
% 	%	%output BC filtered with mu = 10
% 	%	\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_bcf_m10_003}
% 	%	\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_bcf_m10_013}
% 	%	\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_bcf_m10_019}
% 	%	\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_bcf_m10_020}
% 	%	\includegraphics[width=0.195\textwidth]{figures_rida/vid_edit/DSCD_norm_bcf_m10_029}
% 	\end{center}
% 
% 	\begin{center}
% 	\structure{Norm of the convective derivative.} 
% 	\end{center}
% \end{frame}
% 
% \restoreframe

\begin{frame}{Next steps}
	\begin{itemize}\itemsep=1cm
	  \item Tune parameters - patch size and search region.
	  \item Use coarse motion estimate to displace search region along frames.
	  \item Detect still regions to enforce temporal consistency. 
	  \item Address stair-casing problem.
	  \item Compare against classical video denoising algorithms (e.g. temporal median).
  \end{itemize}
\end{frame}

\begin{frame}{}
	\centering
   \vspace{1.7cm}
   \textcolor{MyOrange}{\textbf{\Huge{Merci.}}}\\
   \vspace{5cm}
\end{frame}

% 
%

\end{document}

### 2016-07-20 doc/201503_vnlmeans/report.tex

\documentclass[a4paper,10pt]{article}

\usepackage[english,activeacute]{babel}
\usepackage[english]{layout}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{subfig}
\usepackage{colonequals}
\usepackage[latin1]{inputenc}
\usepackage{url}
\usepackage{epsfig}
%\usepackage{dsfont}

\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{setspace}
\usepackage{afterpage}
%\usepackage{showkeys}
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
% \usepackage{latexsym}

\usepackage[left=1.2in,right=1.2in]{geometry}

% \graphicspath{{../iccv09/}}

% NOTE: COMMENT !!
\newcommand{\mathds}[1]{\mathbb{#1}}

\newcommand{\ma}[1]{\boldsymbol{#1}}
\newcommand{\tras}[1]{#1^{\mathrm{T}}}
\newcommand{\herm}[1]{#1^{\mathrm{H}}}
\newcommand{\con}[1]{#1^{\mathrm{*}}}
\newcommand{\E}{\mathds{E}}
\newcommand{\tech}[1]{\overline{#1}}
\newcommand{\nspace}{\!\!\!\!}
\newcommand{\nmbr}[1]{\oldstylenums{#1}}

\newcommand{\eg}{\emph{e.g}. } \newcommand{\Eg}{\emph{E.g}. }
\newcommand{\ie}{\emph{i.e}. } \newcommand{\Ie}{\emph{I.e}. }
\newcommand{\cf}{\emph{c.f}. } \newcommand{\Cf}{\emph{C.f}. }
\newcommand{\etc}{\emph{etc}. } \newcommand{\vs}{\emph{vs}. }
\newcommand{\wrt}{w.r.t\onedot } \newcommand{\dof}{d.o.f. }
\newcommand{\etal}{\emph{et al}. }

\newcommand{\R}{\mathds{R}}
\newcommand{\sign}{\mathrm{sign}}
\newcommand{\eps}{\varepsilon}
\newcommand{\To}{\longrightarrow}
% \newcommand{\II}{1{\hskip -2.5 pt}\hbox{I}}

% c++ code
\usepackage{listings}
\usepackage{xcolor}
\usepackage{textcomp}
\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
	backgroundcolor=\color{lbcolor},
	tabsize=4,    
%  rulecolor=,
	language=Matlab,
	basicstyle=\scriptsize\ttfamily,
	upquote=true,
	aboveskip={1.5\baselineskip},
	columns=fixed,
	showstringspaces=false,
	extendedchars=false,
	breaklines=true,
	prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
	frame=single,
	numbers=left,
	showtabs=false,
	showspaces=false,
	showstringspaces=false,
	identifierstyle=\ttfamily,
	keywordstyle=\color[rgb]{0,0,1}\ttfamily,
	commentstyle=\color[rgb]{0,0.5,0}\ttfamily,
	stringstyle=\color[rgb]{0.627,0.126,0.941}\ttfamily,
	numberstyle=\color[rgb]{0.5, 0.5, 0.5}\ttfamily,
%  \lstdefinestyle{C++}{language=C++,style=numbers}’.
}
%\lstset{
%	backgroundcolor=\color{lbcolor},
%	tabsize=4,
%	language=C++,
%	captionpos=b,
%	tabsize=3,
%	frame=lines,
%	numbers=left,
%	numberstyle=\tiny,
%	numbersep=5pt,
%	breaklines=true,
%	showstringspaces=false,
%	basicstyle=\footnotesize,
%	identifierstyle=\color{magenta},
%	keywordstyle=\color[rgb]{0,0,1},
%	commentstyle=\color{green},
%	stringstyle=\color{red}
%}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\nota}[1]{\textcolor{blue}{\textbf{#1}}}
\newcommand{\suggest}[1]{\textcolor{yellow}{#1}}
\newcommand{\add}[1]{\textcolor{green}{#1}}
\newcommand{\remove}[1]{\textcolor{red}{#1}}
\newcommand{\dosdv}[1] {#1}
\newcommand{\uncite}[1] {}
% \newcommand{\tachar}[1]{
% \setbox4=\hbox{\ } \setbox3=\hbox{#1} \hbox{#1} \kern -\wd3 \kern
% -\wd4 \raise 0.3\ht3 \hbox{ \vrule width \wd3 height 0.5pt} }

% \theoremstyle{plain}\newtheorem{theorem}{Theorem}[chapter]
% \theoremstyle{plain}\newtheorem{proposition}{Proposition}[chapter]
% \theoremstyle{plain}\newtheorem{lemma}{Lemma}[chapter]
% \theoremstyle{definition}\newtheorem{definition}{Definition}[chapter]

% New definition of square root:
% it renames \sqrt as \oldsqrt
\let\oldsqrt\sqrt
% it defines the new \sqrt in terms of the old one
\def\sqrt{\mathpalette\DHLhksqrt}
\def\DHLhksqrt#1#2{%
\setbox0=\hbox{$#1\oldsqrt{#2\,}$}\dimen0=\ht0
\advance\dimen0-0.2\ht0
\setbox2=\hbox{\vrule height\ht0 depth -\dimen0}%
{\box0\lower0.4pt\box2}}

\title{Video denoising with non-local means}
\author{}
\date{}

\begin{document}

\maketitle
\abstract{Brief description of an extension of the non-local
means algorithm to video denoising.}

\section*{Overview}

This implementation of non-local means comes from modifying the non-local Bayes
algorithm. The only difference is that groups patches are denoised via averages
weighted by similarity, instead of the empirical Bayes estimate of non-local Bayes.

The code in Listing \ref{src:main-overview} shows an overview of the the
algorithm. The first step computes an initial basic estimate which is used as an
oracle for the second step. In the second step, the basic estimate is used
to compute patch distances and similarity weights. We now provide some details
about both steps:

\section*{Step 1: basic estimate}

\paragraph{Patch distances:} The video is converted to YUV colorspace, and only
the Y component is used for the computation of distances and similarity
weights.

\paragraph{Search for similar patches:} We search for similar patches of size
$s_1\times s_1$ in a spatio-temporal window of size $W_{x,1}\times W_{x,1}\times
W_{t,1}$ centered around the current pixel $x = (x_0, x_1, t)$. From all
patches in the search window, we keep only
the $N_{\text{sim},1}$ most similar. This set of patches is the output of the
patch search stage. We denoted it by $\mathcal G_x$, and call it \verb+group+
in the pseudo-code.

\paragraph{Non-local means estimate:} The group of $N_{\text{sim},1}$ patches
is denoised via similarity weighted averages. Consider a noisy patch $\hat p_y\in \mathcal
G_x$. Then its non-local means estimate is given by
\[p_y^{\text{NLM},1} = \frac1{C(\hat p_y; \mathcal G_x)}\sum_{\hat p_z\in\mathcal G_x} w(\hat p_y, \hat p_z)\hat p_z,\]
where $w(\hat p_y, \hat p_z)$ is the similarity weight between patches $\hat
p_y$ and $\hat p_z$ and $C(\hat p_y; \mathcal G_x)$ is a normalization
constant, and the similarity is computed following BUADESIPOL:
\[w(\hat p_y, \hat p_z) = \exp\left(-\frac1{h_1^2}\max(\|\hat p_y - \hat p_z\|_Y^2, 2\sigma^2/3)\right),\]
where $\|\,\cdot\,\|_Y$ is the Euclidean norm of the Y component. The factor
$1/3$ in the above formula is because we are working with the $Y$
component.

\paragraph{Aggregation:} The estimated pathes of $\mathcal G_x$
are aggregated into their original positions. The result of this aggregation is
the output of the first step: the \emph{basic estimate}. The positions of these
patches are labeled as processed. Optionally to reduce computations, we can label
their 4 spatial neighbors as being also processed, as in NL-Bayes.

\section*{Step 2: final estimate}

\paragraph{Search for similar patches:} Patches are of size
$s_2\times s_2$, and the search is performed in a spatio-temporal window of
size $W_{x,2}\times W_{x,2}\times W_{t,2}$ centered around the current pixel $x
= (x_0, x_1, t)$. In the second stage, the distance between patches is computed
using the RGB components of the basic estimate. Two sets of patches are built,
taking patches from the basic estimate in $\mathcal G^b_x$ and their noisy versions
in $\mathcal G_x^n$.

The number of similar patches kept is adaptive. Let $d_{N_{\text{sim},2}}$
be the distance between the reference patch and its $N_{\text{sim},2}$ most similar patch.
All patches with a distance
to the reference patch smaller than $\max(\tau_2, d_{N_{\text{sim},2}})$ are kept.
Thus, $N_{\text{sim},2}$ is a lower bound on the number of similar patches.

\paragraph{Non-local means estimate:} As in step 1, the group $\mathcal G_x^n$ of patches
is denoised via similarity weighted averages. The similarity weight is computed
from the corresponding patches in $\mathcal G_x^b$. Thus, for a noisy patch
$\hat p_y\in \mathcal
G_x^n$, we have:
\[p_y^{\text{NLM},2} = \frac1{C(p^b_y; \mathcal G^b_x)}\sum_{\hat p_z\in\mathcal G^n_x} w(p^b_y, p^b_z)\hat p_z.\]
The similarity $w(\hat p_y, \hat p_z)$ is computed as in step 1, but using the
RGB components:
\[w(p^b_y, p^b_z) = \exp\left(-\frac1{h_2^2}\max(\|p^b_y - p^b_z\|_{\text{RGB}}^2, 2\sigma^2)\right).\]

\paragraph{Aggregation:} As in step 1.

\begin{lstlisting}[%
	float=h,
	caption={Overview of main function},
	label=src:main-overview,
	xleftmargin=.9cm,
	xrightmargin=.9cm]
function final_vid = videoNLMeans(noisy_vid, params1, params2)

%%%%%%%%
% step 1
%%%%%%%%

% convert to YUV colorspace
noisy_vid = convertRGBtoYUV(noisy_vid);

% label all pixels as non-processed
processed = Video(width, height, nframes, false);

% initialize basic estimate as zero
basic_vid = Video(width, height, nframes, channels, 0);

% process video
for x = 1:noisy_vid.nPixels,
	if processed(x) == false,
		% search for similar patches around the reference one
		group = getSimilarPatchesStep1(noisy_vid, x, params1);

		% denoise patches in group via similarity-weighted averages
		group = nlMeansEstimateStep1(group, params1);

		% aggregate group over basic estimate. update processed pixels
		[basic_vid, processed] = aggregateStep1(basic_vid, processed, group, params1);
	end
end

% convert back to RGB colorspace
noisy_vid = convertYUVtoRGB(noisy_vid);
basic_vid = convertYUVtoRGB(basic_vid);

%%%%%%%%
% step 2
%%%%%%%%

% label all pixels as non-processed
processed = Video(width, height, nframes, false);

% initialize final estimate as zero
final_vid = Video(width, height, nframes, channels, 0);

% process video
for x = 1:noisy_vid.nPixels,
	if processed(x) == false,
		% search for similar patches around the reference one
		[group_noisy, group_basic] = getSimilarPatchesStep2(noisy_vid, basic_vid, x, params2);

		% denoise patches in group via similarity-weighted averages
		group_basic = nlMeansEstimateStep2(group_noisy, group_basic, params2);

		% aggregate group estimate, and update mask of processed pixels
		[final_vid, processed] = aggregateStep2(final_vid, processed, group, params2);
	end
end
\end{lstlisting}

\section*{Parameters}

Parameters used in the patch search: $W_{x,i}, W_{t,i}, N_{\text{sim},i}$ and
$\tau_2$, are computed as a function of $\sigma$, following the empirical rules
provided in LEBRUNIPOL.

Parameters $s_1$ and $h_1$ are computed as a function of $\sigma/\sqrt{3}$ following 
the empirical rules provided in BUADESIPOL for color images. In principle,
the parameters for grayscale images of BUADESIPOL should be better since weights are
computed based on the Y component, but performed worse on the Middleburry
sequences.

Parameters $s_2$ and $h_2$ were set by trial and error.

\end{document}

### 2016-07-20 doc/201504_acivs/paper.tex

@@
 		\multirow{5}{*}{$10$} & V-BM4D \cite{Maggioni2012} & \best{36.42} & \best{37.27} &       37.92  &       36.23  \\
+		                      & V-BM4D-mp                  &       35.90  &       36.30  &       37.21  &       35.38  \\
 		                      & V-BM4D-np                  &       35.56  &       36.20  &       36.90  &       35.09  \\
@@
 %									 
-		\multirow{5}{*}{$20$} & V-BM4D  \cite{Maggioni2012}       & \best{32.88} & \best{33.61} & \best{34.62} &       32.27  \\
+		\multirow{5}{*}{$20$} & V-BM4D \cite{Maggioni2012} & \best{32.88} & \best{33.61} & \best{34.62} & \best{32.27} \\
+		                      & V-BM4D-mp                  &       31.98  &       32.44  &       33.70  &       31.34  \\
 		                      & V-BM4D-np                  &       31.67  &       32.24  &       33.34  &       30.95  \\
@@
 									 & VNLB $n_t = 3$             &       31.26  &       33.35  &       34.25  &       32.11  \\
-									 & VNLB $n_t = 5$ &       31.49  &       33.55  &       34.45  & \best{32.35} \\\hline
+									 & VNLB $n_t = 5$             &       31.49  & \best{33.55} &       34.45  & \best{32.35} \\\hline
 %									 
 		\multirow{5}{*}{$40$} & V-BM4D \cite{Maggioni2012} & \best{29.52} & \best{30.00} & \best{31.30} &       28.32  \\
+		                      & V-BM4D-mp                  &       28.14  &       28.73  &       30.09  &       27.44  \\
 		                      & V-BM4D-np                  &       27.97  &       28.43  &       29.69  &       27.02  \\
-		                      & V-BM3D        &       29.20  &       29.99  &       31.17  &       27.34  \\
+									 & V-BM3D                     &       29.20  & \best{29.99} &       31.17  &       27.34  \\
 		                      & VNLB $n_t = 0$             &       27.43  &       28.88  &       30.15  &       27.60  \\
@@
 	\end{center}
-	\caption{PSNRs obtained for the four classic color test sequences reported in
+	\caption{PSNRs obtained for the four classic color test sequences used in
 	\cite{Maggioni2012}. See text for details.}
-	\label{tab:psnr}
+	\label{tab:psnr-classic}
 \end{table}
@@
 	dataset \cite{middleburyOflow}. See text for details.}
-	\label{tab:psnr}
+	\label{tab:psnr-middlebury}
 \end{table}
@@
 dimension, we tested our method considering temporal search ranges of $1, 3$ and $5$ frames.
-The results are shown in Table \ref{tab:psnr}. The proposed method is labeled VNLB.
+The results are shown in Table \ref{tab:psnr-classic}. The proposed method is labeled VNLB.
 For these sequences, the best results were obtained with
@@
 
-For comparison, we also show the result of V-BM3D and two versions of V-BM4D.
+For comparison, we also show the result of V-BM3D and three versions of V-BM4D.
 The method labeled V-BM4D-\cite{Maggioni2012} corresponds to the results reported
-in \cite{Maggioni2012}. The result labeled V-BM4D-np was obtained using the implementation
-available online \cite{bm4dcode}. This implementation provides three parameter
-profiles of increasing quality and complexity: ``low complexity profile'', ``normal
-profile'' and ``modified profile''. The results shown here were obtained with the
-``normal profile'' which is the default. We have included this result, because
-it has a computation time comparable to the one of our method. Running with a
+in \cite{Maggioni2012}. The results labeled V-BM4D-np and V-BM4D-mp were
+obtained using the implementation available online \cite{bm4dcode}. This
+implementation provides three parameter profiles of increasing quality and
+complexity: ``low complexity profile'', ``normal profile'' and ``modified
+profile''. We show the results obtained with the normal (V-BM4D-np) and
+modified (V-BM4D-mp) profiles.
+Let us note that the normal profile has a
+computation time comparable to our method. Running with a
 single core in a Intel Xeon X7560 (2.27GHz) CPU, 
-our current implementation takes on average $9s$ per frame. V-BM4D takes $12s$
-per frame with the normal profile and three times more with the modified profile.
+our current implementation takes on average $10s$ per frame for a video of CIF
+resolution ($352\times288$). V-BM4D takes $13s$ per frame with the normal
+profile and $44s$ with the modified profile.
 
@@
 optical flow Middlebury dataset (the sequences have 8 frames each), and compare
-agaist V-BM4D-np. For these sequences, the proposed method outpeforms V-BM4D-np.
+agaist V-BM4D-np (see table \ref{tab:psnr-middlebury}. For these sequences, the
+proposed method outpeforms V-BM4D-np.
 

### 2016-07-20 doc/201504_vnlbayes_workplan/workplan.tex

--- 2016-07-20 doc/201503_vnlmeans/report.tex
@@
 \usepackage{epsfig}
-%\usepackage{dsfont}
+\usepackage{dsfont}
 
@@
 
-\usepackage[left=1.2in,right=1.2in]{geometry}
+%\usepackage[left=1.2in,right=1.2in]{geometry}
 
 % \graphicspath{{../iccv09/}}
-
-% NOTE: COMMENT !!
-\newcommand{\mathds}[1]{\mathbb{#1}}
 
@@
 
-\title{Video denoising with non-local means}
+\title{Temporal consistency in Video NL-Bayes}
 \author{}
@@
 \maketitle
-\abstract{Brief description of an extension of the non-local
-means algorithm to video denoising.}
+\abstract{Strategies for achieving temporal consistency in video
+NL-Bayes using 2D patches.}
 
-\section*{Overview}
+\subsection*{Overview}
 
-This implementation of non-local means comes from modifying the non-local Bayes
-algorithm. The only difference is that groups patches are denoised via averages
-weighted by similarity, instead of the empirical Bayes estimate of non-local Bayes.
+NL-Bayes groups similar 2D patches and denoise them jointly with a
+Wiener shrinkage operator, by assuming that the prior distribution of
+the noiseless group is Gaussian. This approach is able to achieve
+high PSNRs, however
+\begin{enumerate}
+	\item for high noise power the results lack temporal consistency,
+		and
+	\item it is computationally costly.
+\end{enumerate}
 
-The code in Listing \ref{src:main-overview} shows an overview of the the
-algorithm. The first step computes an initial basic estimate which is used as an
-oracle for the second step. In the second step, the basic estimate is used
-to compute patch distances and similarity weights. We now provide some details
-about both steps:
+In order to tackle both issues, we will try to use motion
+information. First to achieve temporal consistent results, and
+second to speed-up the search for similar patches by searching
+in a smaller area around the motion trajectory.
+%
+In a first stage, we will forget about the computational cost, and
+focus on achieving high quality, temporal consistent results.
 
-\section*{Step 1: basic estimate}
+\bigskip
 
-\paragraph{Patch distances:} The video is converted to YUV colorspace, and only
-the Y component is used for the computation of distances and similarity
-weights.
+\bigskip
 
-\paragraph{Search for similar patches:} We search for similar patches of size
-$s_1\times s_1$ in a spatio-temporal window of size $W_{x,1}\times W_{x,1}\times
-W_{t,1}$ centered around the current pixel $x = (x_0, x_1, t)$. From all
-patches in the search window, we keep only
-the $N_{\text{sim},1}$ most similar. This set of patches is the output of the
-patch search stage. We denoted it by $\mathcal G_x$, and call it \verb+group+
-in the pseudo-code.
+\begin{figure}[htpb!]
+	\centering
+	\includegraphics[width=0.33\textwidth]{figs/approach1}%
+	\includegraphics[width=0.33\textwidth]{figs/approach2}%
+	\includegraphics[width=0.33\textwidth]{figs/approach3}
+	\caption{Diagrams of three approaches for a 1D video. Motion
+	trajectories are represented by the gray doted lines. Patches
+	in the patch group for pixel $(x,t)$ are shown as vertical bars.
+   From left to right, A1, A2 and A3.}
+	\label{fig:3_approaches}
+\end{figure}
 
-\paragraph{Non-local means estimate:} The group of $N_{\text{sim},1}$ patches
-is denoised via similarity weighted averages. Consider a noisy patch $\hat p_y\in \mathcal
-G_x$. Then its non-local means estimate is given by
-\[p_y^{\text{NLM},1} = \frac1{C(\hat p_y; \mathcal G_x)}\sum_{\hat p_z\in\mathcal G_x} w(\hat p_y, \hat p_z)\hat p_z,\]
-where $w(\hat p_y, \hat p_z)$ is the similarity weight between patches $\hat
-p_y$ and $\hat p_z$ and $C(\hat p_y; \mathcal G_x)$ is a normalization
-constant, and the similarity is computed following BUADESIPOL:
-\[w(\hat p_y, \hat p_z) = \exp\left(-\frac1{h_1^2}\max(\|\hat p_y - \hat p_z\|_Y^2, 2\sigma^2/3)\right),\]
-where $\|\,\cdot\,\|_Y$ is the Euclidean norm of the Y component. The factor
-$1/3$ in the above formula is because we are working with the $Y$
-component.
+We propose four strategies. The difference is on how we build the patch 
+group $G(x,t)$ of patches similar to the one on $(x,t)$.
+By testing these approaches we should evaluate if we can impose temporal 
+consistency by manipulating the set of similar patches, which seems to 
+be the simplest approach. 
+\begin{enumerate}
+	\item[\textbf{A0.}] $G(x,t)$ is built by considering similar
+		patches in a spatio-temporal region centered at the motion
+		trajectory through $(x,t)$. 
+	\item[\textbf{A1.}] $G(x,t)$ is built by considering patches in the motion trajectory
+		through $(x,t)$. This approach only exploits temporal redundancy. The amount
+		of noise reduction will be bounded by the length of the trajectories.
+	\item[\textbf{A2.}] $G(x,t)$ is build from the motion trajectory through $(x,t)$,
+		plus some similar patches which are not require to lie on the motion
+		trajectory.
+	\item[\textbf{A3.}] $G(x,t)$ is build from the motion trajectory through $(x,t)$,
+		plus some similar patches which are not require to lie on the motion
+		trajectory, toghether with their motion trajectory.
+\end{enumerate}
 
-\paragraph{Aggregation:} The estimated pathes of $\mathcal G_x$
-are aggregated into their original positions. The result of this aggregation is
-the output of the first step: the \emph{basic estimate}. The positions of these
-patches are labeled as processed. Optionally to reduce computations, we can label
-their 4 spatial neighbors as being also processed, as in NL-Bayes.
+\bigskip
 
-\section*{Step 2: final estimate}
+\bigskip
 
-\paragraph{Search for similar patches:} Patches are of size
-$s_2\times s_2$, and the search is performed in a spatio-temporal window of
-size $W_{x,2}\times W_{x,2}\times W_{t,2}$ centered around the current pixel $x
-= (x_0, x_1, t)$. In the second stage, the distance between patches is computed
-using the RGB components of the basic estimate. Two sets of patches are built,
-taking patches from the basic estimate in $\mathcal G^b_x$ and their noisy versions
-in $\mathcal G_x^n$.
+\subsection*{Motion estimation and its reliability}
 
-The number of similar patches kept is adaptive. Let $d_{N_{\text{sim},2}}$
-be the distance between the reference patch and its $N_{\text{sim},2}$ most similar patch.
-All patches with a distance
-to the reference patch smaller than $\max(\tau_2, d_{N_{\text{sim},2}})$ are kept.
-Thus, $N_{\text{sim},2}$ is a lower bound on the number of similar patches.
+All the previous approaches rely on an estimate of the motion. Computing a 
+reliable motion estimate in the presence of noise is itself a problem.
+to compute in the presence of high noise.
 
-\paragraph{Non-local means estimate:} As in step 1, the group $\mathcal G_x^n$ of patches
-is denoised via similarity weighted averages. The similarity weight is computed
-from the corresponding patches in $\mathcal G_x^b$. Thus, for a noisy patch
-$\hat p_y\in \mathcal
-G_x^n$, we have:
-\[p_y^{\text{NLM},2} = \frac1{C(p^b_y; \mathcal G^b_x)}\sum_{\hat p_z\in\mathcal G^n_x} w(p^b_y, p^b_z)\hat p_z.\]
-The similarity $w(\hat p_y, \hat p_z)$ is computed as in step 1, but using the
-RGB components:
-\[w(p^b_y, p^b_z) = \exp\left(-\frac1{h_2^2}\max(\|p^b_y - p^b_z\|_{\text{RGB}}^2, 2\sigma^2)\right).\]
+We will start by testing optical flow algorithms. We should identify 
+algorithms that are less sensitive to noise. Also, we can use some tricks
+to reduce the noise level:
+\begin{enumerate}
+	\item Estimate motion on a zoomed-out version of the image (as a side
+		effect, this is good for computational cost)
+	\item Apply a temporal filter. If the motion is uniform (no acceleration)
+		temporal filtering conmutes with the warping induced by the motion, thus
+		corresponding pixels can still be matched. For a short-time temporal
+		filter we could gain some noise reduction for motions that have a small
+		acceleration. 
+	\item Other\dots ?
+\end{enumerate}
 
-\paragraph{Aggregation:} As in step 1.
+\bigskip
 
-\begin{lstlisting}[%
-	float=h,
-	caption={Overview of main function},
-	label=src:main-overview,
-	xleftmargin=.9cm,
-	xrightmargin=.9cm]
-function final_vid = videoNLMeans(noisy_vid, params1, params2)
+\bigskip
 
-%%%%%%%%
-% step 1
-%%%%%%%%
+\subsection*{Work plan}
 
-% convert to YUV colorspace
-noisy_vid = convertRGBtoYUV(noisy_vid);
-
-% label all pixels as non-processed
-processed = Video(width, height, nframes, false);
-
-% initialize basic estimate as zero
-basic_vid = Video(width, height, nframes, channels, 0);
-
-% process video
-for x = 1:noisy_vid.nPixels,
-	if processed(x) == false,
-		% search for similar patches around the reference one
-		group = getSimilarPatchesStep1(noisy_vid, x, params1);
-
-		% denoise patches in group via similarity-weighted averages
-		group = nlMeansEstimateStep1(group, params1);
-
-		% aggregate group over basic estimate. update processed pixels
-		[basic_vid, processed] = aggregateStep1(basic_vid, processed, group, params1);
-	end
-end
-
-% convert back to RGB colorspace
-noisy_vid = convertYUVtoRGB(noisy_vid);
-basic_vid = convertYUVtoRGB(basic_vid);
-
-%%%%%%%%
-% step 2
-%%%%%%%%
-
-% label all pixels as non-processed
-processed = Video(width, height, nframes, false);
-
-% initialize final estimate as zero
-final_vid = Video(width, height, nframes, channels, 0);
-
-% process video
-for x = 1:noisy_vid.nPixels,
-	if processed(x) == false,
-		% search for similar patches around the reference one
-		[group_noisy, group_basic] = getSimilarPatchesStep2(noisy_vid, basic_vid, x, params2);
-
-		% denoise patches in group via similarity-weighted averages
-		group_basic = nlMeansEstimateStep2(group_noisy, group_basic, params2);
-
-		% aggregate group estimate, and update mask of processed pixels
-		[final_vid, processed] = aggregateStep2(final_vid, processed, group, params2);
-	end
-end
-\end{lstlisting}
-
-\section*{Parameters}
-
-Parameters used in the patch search: $W_{x,i}, W_{t,i}, N_{\text{sim},i}$ and
-$\tau_2$, are computed as a function of $\sigma$, following the empirical rules
-provided in LEBRUNIPOL.
-
-Parameters $s_1$ and $h_1$ are computed as a function of $\sigma/\sqrt{3}$ following 
-the empirical rules provided in BUADESIPOL for color images. In principle,
-the parameters for grayscale images of BUADESIPOL should be better since weights are
-computed based on the Y component, but performed worse on the Middleburry
-sequences.
-
-Parameters $s_2$ and $h_2$ were set by trial and error.
+\begin{enumerate}
+	\item Evaluate different optical flow algorithms and their
+		robustness to noise. Evaluate the effect of zooming the image
+		out and temporal smoothing.
+	\item Implement and test approach A0.
+	\item Implement and test approach A1.
+	\item Implement and test approach A2.
+	\item Implement and test approach A3.
+\end{enumerate}
 

### 2016-07-20 doc/201505_vnbayes3d/slides_vnlb3d.tex

@@
 
-\multipleframe
 \begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
@@
 
-\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_army.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_walking.eps}
-	\end{center}
-
-\end{frame}
-
-\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_army.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_walking.eps}
-	\end{center}
-
-\end{frame}
-
-\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_army.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_walking.eps}
-	\end{center}
-
-\end{frame}
-\restoreframe
-
-\multipleframe
-\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_army.eps}%
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_walking.eps}
-	\end{center}
-
-\end{frame}
-
-\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_army.eps}%
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_walking.eps}
-	\end{center}
-
-\end{frame}
-
-\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_army.eps}%
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_walking.eps}
-	\end{center}
-
+%\multipleframe
+%\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_walking.eps}
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_walking.eps}
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_walking.eps}
+%	\end{center}
+%\end{frame}
+%\restoreframe
+%
+%\multipleframe
+%\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_walking.eps}
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_walking.eps}
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - rank vs. number of patches, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_walking.eps}
+%	\end{center}
+%\end{frame}
+%\restoreframe
+
+\begin{frame}{Average PSNR and running time - rank vs. number of patches, stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r2-np2-bars_s40_average.eps}\\
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_r2-np2-bars_s40_average.eps}\\
+	\end{center}
 \end{frame}
@@
 \end{frame}
-\restoreframe
-
-\multipleframe
+
 \begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
@@
 
-\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_army.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_walking.eps}
-	\end{center}
-
-\end{frame}
-
-\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_army.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_walking.eps}
-	\end{center}
-
-\end{frame}
-
-\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_army.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_walking.eps}
-	\end{center}
-
-\end{frame}
-\restoreframe
+%\multipleframe
+%\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_walking.eps}
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_walking.eps}
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches, stage 1}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_walking.eps}
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_walking.eps}
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_walking.eps}
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_walking.eps}
+%	\end{center}
+%\end{frame}
+%\restoreframe
+
+\begin{frame}{Average PSNR and running time - rank vs. number of patches, stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_s40_average.eps}\\
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_average.eps}\\
+	\end{center}
+\end{frame}
 
 \multipleframe
-\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_army.eps}%
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s10_walking.eps}
-	\end{center}
-
-\end{frame}
-
-\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_army.eps}%
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s20_walking.eps}
-	\end{center}
-
-\end{frame}
-
-\begin{frame}{Running time tables - rank vs. number of patches, stage 1}
-
-	\begin{center}
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_army.eps}%
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_dogdance.eps}%
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_evergreen.eps}\\
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_mequon.eps}%
-		\includegraphics[width=.33\textwidth]{time_r1-np1-bars_s40_walking.eps}
-	\end{center}
-
-\end{frame}
-
 \begin{frame}{Conclusions - rank vs. number of patches, stage 1}
@@
 \begin{frame}{Conclusions - rank vs. number of patches, stage 1}
-	Based on this observations, we propose the following parameters:
+	Based on these observations, we propose the following parameters:
 	\[r = 160\quad\quad n_{\text{sim}} = \max(15\sigma,cr).\]
@@
 \end{frame}
-
 \restoreframe
 
+\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
+
+	We set the following parameters fixed, and spatial search region and the
+	spatial pach size in the second step. We also vary the rank in the second
+	step.
+
+	\begin{center}
+	\begin{tabular}{l | c c | c c | c c }
+		& \multicolumn{2}{c|}{$\sigma = 10$} 
+		& \multicolumn{2}{c|}{$\sigma = 20$} 
+		& \multicolumn{2}{c}{$\sigma = 40$} \\
+		                            & 1st  & 2nd  & 1st  & 2nd  & 1st  & 2nd \\\hline\hline
+		Patch size (spatial)        &  5   &      &  5   &      &  5   &     \\
+		Patch size (temporal)       &  4   &   4  &  4   &   4  &  4   &   4 \\
+		Number of patches           & 150  & 160  & 300  & 160  & 600  & 160 \\
+		Rank of cov. matrix         & 16   &      & 16   &      & 16   &     \\
+		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
+		Spatial search window       & 13   &      & 37   &      & 37   &     \\
+		Temporal search range       & 5    & 5    & 5    & 5    & 5    & 5   \\\hline
+	\end{tabular}
+	\end{center}
+
+\end{frame}
+
+%\multipleframe
+%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 10$ and $r = 16$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 10$ and $r = 32$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 10$ and $r = 64$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 20$ and $r = 16$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 20$ and $r = 32$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 20$ and $r = 64$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 40$ and $r = 16$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 40$ and $r = 32$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_army.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 40$ and $r = 64$.
+%	\end{center}
+%\end{frame}
+%\restoreframe
+
+%\multipleframe
+%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 10$ and $r = 16$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 10$ and $r = 32$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 10$ and $r = 64$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 20$ and $r = 16$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 20$ and $r = 32$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 20$ and $r = 64$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 40$ and $r = 16$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 40$ and $r = 32$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{Running time tables - spatial search region vs. spatial patch size, stage 2}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_army.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_dogdance.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_evergreen.eps}\\
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_mequon.eps}%
+%		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 40$ and $r = 64$.
+%	\end{center}
+%\end{frame}
+%\restoreframe
+
+\multipleframe
+\begin{frame}{Average PSNR and unning time - spatial search region vs. patch, stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r16_s40_average.eps}\\
+		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r16_s40_average.eps}\\
+	\end{center}
+	\begin{center}
+	Average results for $r = 16$, and $\sigma = 10, 20, 40$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{Average PSNR and unning time - spatial search region vs. patch, stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r32_s40_average.eps}\\
+		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r32_s40_average.eps}\\
+	\end{center}
+	\begin{center}
+	Average results for $r = 32$, and $\sigma = 10, 20, 40$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{Average PSNR and unning time - spatial search region vs. patch, stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_wx2-px2-bars_r64_s40_average.eps}\\
+		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_wx2-px2-bars_r64_s40_average.eps}\\
+	\end{center}
+	\begin{center}
+	Average results for $r = 64$, and $\sigma = 10, 20, 40$.
+	\end{center}
+\end{frame}
+\restoreframe
+
+\begin{frame}{Conclusions - spatial search region vs. spatial patch size, stage 2}
+
+	From the preceeding results, we conclude that:
+	\begin{itemize}\itemsep=.2cm
+		\item For $\sigma = 10$, it's better to use small patches $s_x = 3$ and higher rank $r = 32$. 
+		\item For $\sigma = 10$, increasing the rank favours all patch sizes, but
+			higher patch sizes improve more. For $s_x = 5$ the improvement is
+			around $0.5$dB, and around $0.8$dB for $s_x = 9$.
+		\item For $\sigma > 10$, it's better to use $s_x = 5$. 
+		\item For $\sigma = 20$, there is some improvement when increasing the rank (around $0.1$dB and $0.2$dB). 
+		\item For $\sigma = 40$, increasing the rank gives worse results. 
+		\item Increasing the search region improves the results. The improvement is higher for low
+			noise ($\sigma = 10$) and for large patches.
+	\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Forget about tables - PSNR cubes}
+
+	From the preceending experiment, it becomes clear that there is a strong
+	relation between four parameters: patch size (in time and space), rank and
+	number of similar patches. We will fix the search range and focus on the
+	relation between these parameters.
+
+	\bigskip
+
+	To simplify the analysis, we will consider a fixed temporal size for the 
+	patch $s_t = 3$. And sample a parameters cube varying 
+	\[s_x = 3, 5, 7, 9 \quad\quad r = 8, 16, 32, 64 \quad\text{and}\quad n_{\text{sim}} = 80, 160, 320, 640.\]
+
+	We start by the fisrt step. The rest of the parameters are fixed as follows:
+
+	\begin{center}
+	\begin{tabular}{l | c c | c c | c c }
+		& \multicolumn{2}{c|}{$\sigma = 10$} 
+		& \multicolumn{2}{c|}{$\sigma = 20$} 
+		& \multicolumn{2}{c}{$\sigma = 40$} \\
+		                            & 1st  & 2nd  & 1st  & 2nd  & 1st  & 2nd \\\hline\hline
+		Patch size (spatial)        &      &   5  &      &   5  &      &   5 \\
+		Patch size (temporal)       &  3   &   3  &  3   &   3  &  3   &   3 \\
+		Number of patches           &      & 160  &      & 160  &      & 160 \\
+		Rank of cov. matrix         &      &  16  &      &  16  &      &  16 \\
+		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
+		Spatial search window       & 37   &  37  & 37   &  37  & 37   &  37 \\
+		Temporal search range       & 5    & 5    & 5    & 5    & 5    & 5   \\\hline
+	\end{tabular}
+	\end{center}
+
+\end{frame}
+
+%\multipleframe
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s10_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s10_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s10_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s10_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 10$ and $s_x = 3$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s10_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s10_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s10_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s10_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 10$ and $s_x = 5$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s10_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s10_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s10_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s10_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 10$ and $s_x = 7$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s10_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s10_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s10_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s10_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 10$ and $s_x = 9$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s20_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s20_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s20_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s20_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 20$ and $s_x = 3$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s20_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s20_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s20_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s20_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 20$ and $s_x = 5$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s20_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s20_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s20_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s20_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 20$ and $s_x = 7$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s20_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s20_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s20_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s20_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 20$ and $s_x = 9$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s40_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s40_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s40_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px3_s40_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 40$ and $s_x = 3$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s40_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s40_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s40_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px5_s40_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 40$ and $s_x = 5$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s40_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s40_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s40_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px7_s40_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 40$ and $s_x = 7$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s40_army.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s40_dogdance.eps}\\
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s40_evergreen.eps}
+%		\includegraphics[width=.38\textwidth]{psnr_r1-np1-bars_1px9_s40_walking.eps}
+%	\end{center}
+%	\begin{center}
+%	Results for $\sigma = 40$ and $s_x = 9$.
+%	\end{center}
+%\end{frame}
+%\restoreframe
+
+%\multipleframe
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px3_s10_average.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px3_s20_average.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px3_s40_average.eps}
+%	\end{center}
+%	\begin{center}
+%	Average results for $\sigma = 10, 20, 40$ and $s_x = 3$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px5_s10_average.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px5_s20_average.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px5_s40_average.eps}
+%	\end{center}
+%	\begin{center}
+%	Average results for $\sigma = 10, 20, 40$ and $s_x = 5$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px7_s10_average.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px7_s20_average.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px7_s40_average.eps}
+%	\end{center}
+%	\begin{center}
+%	Average results for $\sigma = 10, 20, 40$ and $s_x = 7$.
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}{PSNR tables - rank vs. number of patches - stage 1}
+%	\begin{center}
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px9_s10_average.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px9_s20_average.eps}%
+%		\includegraphics[width=.33\textwidth]{psnr_r1-np1-bars_1px9_s40_average.eps}
+%	\end{center}
+%	\begin{center}
+%	Average results for $\sigma = 10, 20, 40$ and $s_x = 9$.
+%	\end{center}
+%\end{frame}
+%\restoreframe
+
+\multipleframe
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r8_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r8_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r8_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 8$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r16_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r16_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r16_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 16$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r32_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r32_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r32_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 32$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r64_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r64_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px1-np1-bars_1r64_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 64$.
+	\end{center}
+\end{frame}
+\restoreframe
+
+\multipleframe
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r8_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r8_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r8_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 8$. 
+	\bigskip
+
+	Zoom in of previous graphs.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r16_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r16_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r16_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 16$. 
+	\bigskip
+
+	Zoom in of previous graphs.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r32_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r32_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r32_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 32$. 
+	\bigskip
+
+	Zoom in of previous graphs.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r64_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r64_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px1-np1-bars_1r64_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 64$. 
+	\bigskip
+
+	Zoom in of previous graphs.
+	\end{center}
+\end{frame}
+\restoreframe
+
+\multipleframe
+\begin{frame}{Running time - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r8_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r8_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r8_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 8$.
+
+	\bigskip
+
+	Note: the running times for $r = 8$ and $n_{\text{sim}} = 80$ are \\
+	distorted because the server was overloaded.
+	\end{center}
+\end{frame}
+
+\begin{frame}{Running time - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r16_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r16_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r16_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 16$.
+
+	\bigskip
+
+	Note: the running times for $r = 8$ and $n_{\text{sim}} = 80$ are \\
+	distorted because the server was overloaded.
+	\end{center}
+\end{frame}
+
+\begin{frame}{Running time - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r32_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r32_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r32_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 32$.
+
+	\bigskip
+
+	Note: the running times for $r = 8$ and $n_{\text{sim}} = 80$ are \\
+	distorted because the server was overloaded.
+	\end{center}
+\end{frame}
+
+\begin{frame}{Running time - patch size vs. number of patches - stage 1}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r64_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r64_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px1-np1-bars_1r64_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 64$.
+
+	\bigskip
+
+	Note: the running times for $r = 8$ and $n_{\text{sim}} = 80$ are \\
+	distorted because the server was overloaded.
+	\end{center}
+\end{frame}
+\restoreframe
+
+\multipleframe
+\begin{frame}{Conclusions - rank, number of patches and patch size, stage 1}
+
+	\begin{center}
+		Table showing the positions of the parameters that maximize the final PSNR:
+
+		\medskip
+
+		{\small
+		\begin{tabular}{r ||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||}
+				$s_x \backslash n_{\text{sim}}$  & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} \\\hline
+		  3 &  &  &  &  &x &x &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  5 &  &  &  &  &  &  &  &  &  &x &  &  &  &X &x &x \\[.1cm]\hline
+		  7 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  9 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+%         8           16          32          64
+		$\sigma=10$& \multicolumn{4}{c||}{$r =  8$} & 
+		\multicolumn{4}{c||}{$r = 16$} & 
+		\multicolumn{4}{c||}{$r = 32$} & 
+		\multicolumn{4}{c||}{$r = 64$} 
+		\end{tabular}}
+
+		\medskip
+
+		{\small
+		\begin{tabular}{r ||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||}
+				$s_x \backslash n_{\text{sim}}$  & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} \\\hline
+		  3 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  5 &  &  &  &  &  &  &  &  &  &  &X &x &  &  &x &x \\[.1cm]\hline
+		  7 &  &  &  &  &  &x &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  9 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+%         8           16          32          64
+		$\sigma=20$& \multicolumn{4}{c||}{$r =  8$} & 
+		\multicolumn{4}{c||}{$r = 16$} & 
+		\multicolumn{4}{c||}{$r = 32$} & 
+		\multicolumn{4}{c||}{$r = 64$} 
+		\end{tabular}}
+
+		\medskip
+
+		{\small
+		\begin{tabular}{r ||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||}
+				$s_x \backslash n_{\text{sim}}$  & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} \\\hline
+		  3 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  5 &  &  &x &  &  &  &  &X &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  7 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  9 &  &x &  &  &  &x &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+%         8           16          32          64
+		$\sigma=40$& \multicolumn{4}{c||}{$r =  8$} & 
+		\multicolumn{4}{c||}{$r = 16$} & 
+		\multicolumn{4}{c||}{$r = 32$} & 
+		\multicolumn{4}{c||}{$r = 64$} 
+		\end{tabular}}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{Conclusions - rank, number of patches and patch size, stage 1}
+
+	TODO: explanation of these results!
+
+\end{frame}
+
+\begin{frame}{Conclusions - rank, number of patches and patch size, stage 1}
+	\begin{center}
+	Based on these observations, we propose the following parameters:
+	\[s_x = 5 \quad\quad r = \min(640/\sigma,s_x^2s_t,r_{\text{max}})\quad\quad n_{\text{sim}} = 16\sigma.\]
+	\end{center}
+\end{frame}
+\restoreframe
+
+\begin{frame}{PSNR cubes for the 2nd stage}
+
+	With the optimal parameters found for the fist stage, we now explore the
+	cube of parameters of the second stage.
+
+	\bigskip
+
+	As before, to simplify the analysis, we will consider a fixed temporal size for the 
+	patch $s_t = 3$. We sample the following parameters cube:
+	\[s_x = 3, 5, 7, 9 \quad\quad r = 8, 16, 32, 64 \quad\text{and}\quad n_{\text{sim}} = 80, 160, 320, 640.\] 
+	The rest of the parameters are fixed as follows:
+
+	\begin{center}
+	\begin{tabular}{l | c c | c c | c c }
+		& \multicolumn{2}{c|}{$\sigma = 10$} 
+		& \multicolumn{2}{c|}{$\sigma = 20$} 
+		& \multicolumn{2}{c}{$\sigma = 40$} \\
+		                            & 1st  & 2nd  & 1st  & 2nd  & 1st  & 2nd \\\hline\hline
+		Patch size (spatial)        &  5   &      &  5   &      &  5   &     \\
+		Patch size (temporal)       &  3   &   3  &  3   &   3  &  3   &   3 \\
+		Number of patches           & 160  &      & 320  &      & 640  &     \\
+		Rank of cov. matrix         & 64   &      & 32   &      & 16   &     \\
+		Distance threshold $\tau$   & n/a  & 432  & n/a  & 432  & n/a  & 432 \\
+		Spatial search window       & 37   &  37  & 37   &  37  & 37   &  37 \\
+		Temporal search range       & 5    & 5    & 5    & 5    & 5    & 5   \\\hline
+	\end{tabular}
+	\end{center}
+
+\end{frame}
+
+\multipleframe
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s10_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s10_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s10_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s10_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 10$ and $r = 8$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s10_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s10_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s10_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s10_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 10$ and $r = 16$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s10_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s10_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s10_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s10_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 10$ and $r = 32$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s10_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s10_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s10_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s10_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 10$ and $r = 64$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s20_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s20_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s20_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s20_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 20$ and $r = 8$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s20_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s20_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s20_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s20_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 20$ and $r = 16$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s20_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s20_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s20_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s20_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 20$ and $r = 32$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s20_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s20_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s20_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s20_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 20$ and $r = 64$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s40_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s40_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s40_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r8_s40_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 40$ and $r = 8$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s40_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s40_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s40_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r16_s40_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 40$ and $r = 16$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s40_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s40_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s40_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r32_s40_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 40$ and $r = 32$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s40_army.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s40_dogdance.eps}\\
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s40_evergreen.eps}
+		\includegraphics[width=.38\textwidth]{psnr_px2-np2-bars_2r64_s40_walking.eps}
+	\end{center}
+	\begin{center}
+	Results for $\sigma = 40$ and $r = 64$.
+	\end{center}
+\end{frame}
+\restoreframe
+
+\multipleframe
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r8_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r8_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r8_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 8$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r16_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r16_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r16_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 16$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r32_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r32_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r32_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 32$.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r64_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r64_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{psnr_px2-np2-bars_2r64_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 64$.
+	\end{center}
+\end{frame}
+\restoreframe
+
+\multipleframe
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r8_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r8_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r8_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 8$. 
+	\bigskip
+
+	Zoom in of previous graphs.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r16_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r16_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r16_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 16$. 
+	\bigskip
+
+	Zoom in of previous graphs.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r32_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r32_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r32_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 32$. 
+	\bigskip
+
+	Zoom in of previous graphs.
+	\end{center}
+\end{frame}
+
+\begin{frame}{PSNR tables - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r64_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r64_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{zoom_psnr_px2-np2-bars_2r64_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 64$. 
+	\bigskip
+
+	Zoom in of previous graphs.
+	\end{center}
+\end{frame}
+\restoreframe
+
+\multipleframe
+\begin{frame}{Running time - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r8_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r8_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r8_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 8$.
+
+	\bigskip
+
+	Note: the running times for $r = 8$ and $n_{\text{sim}} = 80$ are \\
+	distorted because the server was overloaded.
+	\end{center}
+\end{frame}
+
+\begin{frame}{Running time - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r16_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r16_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r16_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 16$.
+
+	\bigskip
+
+	Note: the running times for $r = 8$ and $n_{\text{sim}} = 80$ are \\
+	distorted because the server was overloaded.
+	\end{center}
+\end{frame}
+
+\begin{frame}{Running time - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r32_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r32_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r32_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 32$.
+
+	\bigskip
+
+	Note: the running times for $r = 8$ and $n_{\text{sim}} = 80$ are \\
+	distorted because the server was overloaded.
+	\end{center}
+\end{frame}
+
+\begin{frame}{Running time - patch size vs. number of patches - stage 2}
+	\begin{center}
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r64_s10_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r64_s20_average.eps}%
+		\includegraphics[width=.33\textwidth]{time_px2-np2-bars_2r64_s40_average.eps}
+	\end{center}
+	\begin{center}
+	Average results for $\sigma = 10, 20, 40$ and $r = 64$.
+
+	\bigskip
+
+	Note: the running times for $r = 8$ and $n_{\text{sim}} = 80$ are \\
+	distorted because the server was overloaded.
+	\end{center}
+\end{frame}
+\restoreframe
+
+\multipleframe
+\begin{frame}{Conclusions - rank, number of patches and patch size, stage 2}
+
+	\begin{center}
+		Table showing the positions of the parameters that maximize the final PSNR:
+
+		\medskip
+
+		{\small
+		\begin{tabular}{r ||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||}
+				$s_x \backslash n_{\text{sim}}$  & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} \\\hline
+		  3 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  5 &  &  &  &  &  &  &  &  &  &x &  &  &  &  &x &  \\[.1cm]\hline
+		  7 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &x &  \\[.1cm]\hline
+		  9 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+%         8           16          32          64
+		$\sigma=10$& \multicolumn{4}{c||}{$r =  8$} & 
+		\multicolumn{4}{c||}{$r = 16$} & 
+		\multicolumn{4}{c||}{$r = 32$} & 
+		\multicolumn{4}{c||}{$r = 64$} 
+		\end{tabular}}
+
+		\medskip
+
+		{\small
+		\begin{tabular}{r ||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||}
+				$s_x \backslash n_{\text{sim}}$  & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} \\\hline
+		  3 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  5 &  &  &  &  &  &x &  &  &  &  &x &  &  &  &  &  \\[.1cm]\hline
+		  7 &  &  &  &  &  &  &  &  &  &  &x &  &  &  &  &  \\[.1cm]\hline
+		  9 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &x &x \\[.1cm]\hline
+%         8           16          32          64
+		$\sigma=20$& \multicolumn{4}{c||}{$r =  8$} & 
+		\multicolumn{4}{c||}{$r = 16$} & 
+		\multicolumn{4}{c||}{$r = 32$} & 
+		\multicolumn{4}{c||}{$r = 64$} 
+		\end{tabular}}
+
+		\medskip
+
+		{\small
+		\begin{tabular}{r ||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||p{.1cm}|p{.1cm}|p{.1cm}|p{.1cm}||}
+				$s_x \backslash n_{\text{sim}}$  & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} & {\tiny 80} & {\tiny 160} & {\tiny 320} & {\tiny 640} \\\hline
+		  3 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  5 &  &  &  &  &  &x &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+		  7 &  &  &  &  &  &x &x &  &x &x &  &  &  &  &x &  \\[.1cm]\hline
+		  9 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\[.1cm]\hline
+%         8           16          32          64
+		$\sigma=40$& \multicolumn{4}{c||}{$r =  8$} & 
+		\multicolumn{4}{c||}{$r = 16$} & 
+		\multicolumn{4}{c||}{$r = 32$} & 
+		\multicolumn{4}{c||}{$r = 64$} 
+		\end{tabular}}
+	\end{center}
+
+\end{frame}
+
+\begin{frame}{Conclusions - rank, number of patches and patch size, stage 2}
+
+	TODO: explanation of these results!
+
+\end{frame}
+
+\begin{frame}{Conclusions - rank, number of patches and patch size, stage 2}
+	\begin{center}
+	Based on these observations, we propose the following parameters for the second stage:
+	\[s_x = 5 \quad\quad r = \max(\min(320/\sigma,s_x^2s_t,r_{\text{max}}), r_{\text{min}})\quad\quad n_{\text{sim}} = 160,\]
+	where $r_{\text{min}} = 16$.
+	\end{center}
+\end{frame}
+\restoreframe
+
 \end{document}

### 2016-07-20 doc/201507_tip/paper.tex

@@
 \begin{abstract}
-	The quality provided by image/video sensors increases steadily, and
-	for a fixed spatial resolution the sensor noise has been gradually reduced.
-	However, modern sensors are also capable of acquiring at higher spatial
-	resolutions which are still affected by noise, specially at low lighting
-	conditions. The situation is even worse in video cameras, where the capture
-	time is bounded by the frame rate. The noise in the video degrades its visual 
-	quality and hinders its analysis.
-	In this paper we present a new video denoising method extending 
-	the non-local Bayes image denoising algorithm. The method does not require 
-	motion estimation, and yet preliminary results show that it outperforms the
-	state-of-the-art methods in terms of PSNR.
+In this paper we present a new patch-based empirical Bayesian video denoising algorithm.
+The method builds a Bayesian model for each group of similar space-time
+patches. These patches are not motion compensated, and therefore avoid the
+risk of inaccuracies caused by motion estimation errors. The main drawback of empirical Bayesian
+methods is the computational load for estimating rich statistics in high
+dimension. We therefore explore dimensionality reduction strategies on groups
+of similar patches. Our analysis, based on the literature
+on empirical covariance estimation, leads to a significant complexity
+reduction and better denoising performance. A comparison on classic benchmark
+videos demonstrates improved visual quality and an increased PSNR with respect
+to state-of-the-art video denoising methods.
 \end{abstract}
@@
 other hand, the output of the denoising algorithm should be temporally
-consistent according to the motion of the original sequence.
+consistent with to the motion of the original sequence, which is an essential
+quality criterion.
 
@@
 %
-While these methods exploit spatio-temporal redundancy, they do not impose
-coherence of the trajectories, resulting in flickering
-artifacts which become noticeable for high levels of noise.
 
@@
 
-Motion-compensated patches have the benefit that their spatial slices are very
-similar between each other. As a consequence, temporal filtering can be easily performed by
+Motion-compensated patches have the benefit that their spatial slices are 
+to between each other. As a consequence, temporal filtering can be easily performed by
 filtering inside the patch in the temporal direction. 
@@
 
-One of the main difficulties in using motion-compensated patches is estimating
-motion. Motion estimation is a paramount problem in noiseless sequences, and
-noise makes it much harder.
+One of the main difficulties in using motion-compensated patches is motion
+estimation in the presence of noise.
 
 Rectangular 3D patches offer an appealing
-alternative, since they do not require estimating motion. 
+alternative, since they do not require motion estimation.
 In \cite{Protter2007,Protter2009} the authors extend the K-SVD \cite{Elad2006}
@@
 Each rectangular 3D patch results from the combination of a 2D texture and a
-motion pattern. For arbitrary motion, each combination of texture and motion is
-not likely to occur together again. Thus rectangular 3D patches should have
-less repeatability in the video compared to motion compensated patches.  An
-exception is when the motion is a global translation of the frame, in which
-case, the motion pattern is equal for each patch. Furthermore, if there is no
-acceleration (uniform motion), rectangular 3D patches are constant along motion
-trajectories. Global uniform motion is indeed a too restrictive model, but in
-many cases, it is a valid approximation in a local neighborhood in space and
-time.
+motion pattern. For arbitrary motion it would seem that each combination of
+texture and motion is unlikely to repeat across the video. Thus rectangular 3D
+patches should have less repeatability in the video compared to motion
+compensated patches. 
+This objection is mitigated in two ways. First, if the motion is uniform on the
+trajectory, rectangular 3D patches will be similar along the trajectory.
+Second, if the motion pattern is spatially homogeneous in a region of the
+image, then the image self-similarity still extends to space-time patches
+starting at the same frame, regardless of the complexity of the motion.
 
@@
 
-In this work we present new Bayesian patch-based video denoising method using
+In this work we present a new Bayesian patch-based video denoising method using
 3D rectangular patches and not requiring motion estimation.
@@
 both quantitatively by a significant margin and qualitatively, specifically in
-terms of the temporal consistency attained.
+terms of temporal consistency.
 In the spirit of  \cite{Lebrun2013a,Lebrun2013ipol},
@@
 posteriori} (MAP) with the estimated prior.
-Learning the Gaussian prior amounts to estimating a covariance matrix with a
-limited number of samples in a high dimensional space. Motivated by recent 
+The main difficulty of such a method is the problem of estimation a high
+dimensional covariance matrix with a limited number of samples. 
+%
+There are two possible solutions to this problem. One that works in image
+denoising, is to estimate a fixed \cite{Zoran2011} or an image dependent
+Gaussian mixture model \cite{Chatterjee2012}.  The computational burden of the first
+strategy is huge, but it is paid once, as it delivers to a fixed prior. And it
+shows excellent performance. Yet its extension to video is challenging because
+of the curse of dimensionality. The second strategy, of estimating a different
+Gaussian mixture from each video, also raises serious complexity issues. Thus
+we shall stick to the idea of using video redundancy to build a local Gaussian
+model for each patch.
+%
+Motivated by recent 
 theoretical results and supported by an empirical analysis, we add the 
-assumption that the \emph{a priori} model is of low rank (\ie the clean patches
+assumption that the \emph{a priori} local patch model is of low rank (\ie the clean patches
 lie in a lower dimensional subspace). This assumption lowers the computational cost
@@
 The rest of the paper is organized as follows: in \S
-\ref{sec:review_nonlocal_Bayes} we review our patch-based Bayesian optimal estimator for
-video denoising. The final algorithm and details about its implementation are
+\ref{sec:review_nonlocal_Bayes} we describe the proposed patch-based Bayesian optimal estimator for
+video denoising. The resulting algorithm and details about its implementation are
 given in \S \ref{sec:algorithm}.
-Some relevant aspects of the proposed method are discussed in \S
-\ref{sec:discussion}.
+The structure of spatio-temporal  patches and the issues of the estimation of
+their covariance are discussed in \ref{sec:discussion}.
 In \S \ref{sec:parameters}
@@
 The parameters of the \textit{a priori} model are learnt from the noisy video as
-follows. For each noisy patch $\ma q$, we select the most $n$
+follows. For each noisy patch $\ma q$, we select the $n$ most
 similar 3D patches found in a search region centered at $\ma q$. The
@@
 
-Let us note by $\ma q_i$, $i = 1, \dots, n$ the set of patches
+Let us denote by $\ma q_i$, $i = 1, \dots, n$ the set of patches
 similar to $\ma q$ (with $\ma q_1 = \ma q$). We assume that these 
-patches correspond to different noisy observations of the Gaussian linear model
+patches correspond to noisy observations of the Gaussian linear model
 \eqref{eq:prior} and \eqref{eq:obs}. The corresponding marginal distribution is given by
@@
 
-We will also assume that the covariance matrix has a lower rank $k$.  In this
+We will also assume that the covariance matrix has a lower rank $r$.  In this
 case, it has been shown \cite{Tipping1999} that the maximum likelihood estimate is given by
-truncating the spectral decomposition of $\widehat C$ to the $k$ largest
+truncating the spectral decomposition of $\widehat C$ to the $r$ largest
 eigenvalues 
 \begin{equation}
-\widehat C_k = \sum_{i = 1}^k\widehat \lambda_i\widehat U_i\widehat U_i^T,
+\widehat C_r = \sum_{i = 1}^r\widehat \lambda_i\widehat U_i\widehat U_i^T,
 \end{equation}
@@
 
-\padd{The estimated eigenvalues are given by $\widehat \lambda_i = \widehat
+The estimated eigenvalues are given by $\widehat \lambda_i = \widehat
 \nu_i - \sigma^2$, where $\widehat \nu_i$ are the eigenvalues of the empirical
@@
 \ref{sec:parameters} we compare the results obtained by zeroing out negative
-coefficients against using them.}
+coefficients against using them.
 
@@
 models were learnt from the $n = 200$ similar patches shown in Figure
-\ref{fig:patch_groups_pos}. The MAP estimates were computed setting $r = 40$.
-Since the patch is not
-motion-compensated, all spatial slices can be different,
-and thus the same applies to the principal directions.
+\ref{fig:patch_groups_pos}. The MAP estimates were computed setting the rank $r = 40$.
+%Since the patch is not
+%motion-compensated, its spatial slices can have little correlation.
+%The same applies to the spatial slices of the principal directions.
 The spatial slices of the principal directions show oscillating patterns, with
-increasing frequency. In some cases these patterns are localized in a part of
-the spatial slice.
+increasing frequency. 
+In some cases these patterns are localized in a smaller region.
+%
+These oscillations are oriented in the direction of the
+dominant edges in the corresponding slices of the patches in the group.
 
@@
 
-Other methods for image denoising have been proposed in the
-literature based on Gaussian models for the patch density. In \cite{Yu2012},
+Using a Gaussian patch model for for image denoising has several antecedents.
+In \cite{Yu2012},
 the authors introduce a framework for solving inverse problems, based on the
@@
 database of $2\cdot 10^6$ patches randomly sampled from the Berkeley database.
-
-In \cite{Zhang2010} a PCA-based algorithm is introduced which is equivalent to 
-the nonlocal Bayes method. In fact, nonlocal Bayes can be regarded as a Bayesian 
-interpretation of \cite{Zhang2010}.
-
+In \cite{Zhang2010} an algorithm that applies PCA on groups of similar patches
+is introduced. It can be interpreted as a non-local empirical Bayesian method.
+%
 The BLS-GSM method \cite{Portilla2003} (Bayes least square estimate of Gaussian
@@
 	In red we show the positions of the 5 nearest neighbors, in green the next 40 and in blue the rest.
-	Note that the points shown correspond to the top-left pixel of the first spatial
+	The points shown correspond to the top-left pixel of the first spatial
 	slice of each patch.
@@
 \cite{Dabov2007tip,Dabov2007v,Maggioni2012,Lebrun2013a} we perform two stages, described in 
-Algorithms \ref{alg:nlbayes} and \ref{alg:nlbayes2}. In the first stage we
-compute a \emph{basic} estimate, which we denote $\widetilde u^{(1)}$.
-
-In the second stage computes the final estimate $\widetilde u^{(2)}$ using the
+Algorithms \ref{alg:nlbayes} and \ref{alg:nlbayes2}. The first stage 
+computes a \emph{basic} estimate, which we denote $\widetilde u^{(1)}$.
+
+The second stage computes the final estimate $\widetilde u^{(2)}$ using the
 basic estimate as an oracle. This entails two modifications with respect to the
@@
 the basic estimate are drawn from the \textit{a priori} Gaussian model and use
-them to learn the mean and covariance matrix. Note that in the second stage,
+them to learn the mean and covariance matrix. In the second stage,
 when estimating the covariance matrix, we assume that the patches of the basic
@@
 threshold $\tau$.  As in \cite{Lebrun2013ipol}, we set $\tau = 4$ (the distance between
-patches is normalized by the number of elements in the patch and the number of
-channels and the values of each channel are in the range  $[0,255]$).
+patches is jointly normalized by the number of elements in the patch, the number of
+channels, and the values of each channel are in the range  $[0,255]$).
 
@@
 considered in \cite{Dabov2007tip,Lebrun2013ipol} in order to reduce the number of reference patches. 
-The first one consists on visiting only 
+The first one consists in visiting only 
 those patches on a coarser spatial grid with vertical and horizontal separation
 of $s_x/2$. This reduces the number of reference patches by a factor of
-$s_x^2/4$. The second trick consists on the following.  After
-filtering the patches in a group, these patches are not considered again
-as reference patches. 
-Note that we ensure that each reference patch is filtered at least once. 
-Due to the spacing of the coarse grid, this guarantees that each pixel is
-overlapped by four reference patches on the same frame, so it will receive at
-least four contributions in the aggregation. The actual number of aggregated
-estimates for each pixel is much higher, considering the reference and
-non-reference patches (which can also be filtered) in the neighboring frames.
+$s_x^2/4$. The second acceleration trick is to give up taking as reference
+patch the patches that have been already once filtered in another group. 
+%Note that we ensure that each reference patch is filtered at least once. 
+%Due to the spacing of the coarse grid, this guarantees that each pixel is
+%overlapped by four reference patches on the same frame, so it will receive at
+%least four contributions in the aggregation. The actual number of aggregated
+%estimates for each pixel is much higher, considering the reference and
+%non-reference patches (which can also be filtered) in the neighboring frames.
+The actual number of aggregated estimates for each pixel remains anyway high,
+simply because each pixel is contained in 100 different patches, and at least
+25 of them have been filtered, either as reference patches, or as patches
+similar to a reference patch.
 
 Due to these speed-ups, the actual number of groups of similar patches processed
-depends on $n$, and varies between a $1\%$ ($n \approx 400$)  and a $10\%$ ($n
-\approx 50$) of the total number of pixels in the sequence. 
+depends on $n$, and varies across video sequences. We have measured empirically
+that it ranges roughly from $1\%$ ($n \approx 400$) to $10\%$ ($n \approx 50$) of the total
+number of pixels in the sequence. 
 \pcomment{Check this numbers!}
@@
 limit when the number of samples $n$ and the dimension $p$ grow to infinity at
-same rate, such that $p/n\to\gamma < \infty$.  These works show that, for a
+the same rate, $p/n\to\gamma < \infty$.  These works show that, for a
 non-zero ratio $\gamma$, the empirical eigenvectors 
@@
 Furthermore, the smaller eigenvalues and their eigenvectors will have a higher
-error and eventually, if the signal-to-noise ratio drops bellow $\sqrt{\gamma}$, 
+error and eventually, if the signal-to-noise ratio drops below $\sqrt{\gamma}$, 
 the eigenvector is confused with the noise and the resulting estimate will be,
@@
 lower eigenvalues. How many should be discarded in practice when $n$ and $p$ are finite, 
-can only be fixed empirically, as we do in \$ \ref{sec:parameters}.
+can only be fixed empirically, as we do in \S \ref{sec:parameters}.
 
@@
 
-The number of similar patches $n$ and the rank $r$ affect the estimation of the covariance
+The number $n$ of similar patches and the rank $r$ affect the estimation of the covariance
 matrix $C$, controlling the trade-off between the accuracy of the Gaussian model
@@
 
-\padd{For the basic estimate, we show two set of curves. The dashed curves were
+{For the basic estimate, we show two sets of curves. The dashed curves were
 obtained by zeroing out negative eigenvalues of the estimated a priori covariance
@@
 
-\padd{For lower values of the rank parameter $r$, both curves coincide, since the first
+{For lower values of the rank parameter $r$, both curves coincide, since the first
 eigenvalues are positive. 
-For all noise levels, all curves of fixed $n_1$ present a first peak at a low value of the rank $r$.
+For all noise levels, all curves with fixed $n_1$ present a first peak at a low value of the rank $r$.
 The behaviour of the basic estimate around this peak can be
@@
 shifts to the left. This makes sense, as the reliability of the computed eigenvectors
-decrease with increasing noise.
+decreases with increasing noise.
 %
@@
 This is again explainable, as smaller groups obtained by keeping only the
-most similar patches have less modes of variation, and thus a worse signal-to-noise ratio
+most similar patches have fewer modes of variation, and thus a worse signal-to-noise ratio
 in the eigenvectors with lower eigenvalues.}
@@
 %which result in a poorer estimation of the MAP.
-\padd{As the rank parameter increases, both curves diverge. 
+{As the rank parameter increases, both curves diverge. 
 The dashed curves become almost constant at the point when
@@
 result, creating the second peak for high values of the rank shown by the
-continuous plots. Currently we do not have an explanation for this behaviour
-although it is related to the aggregation: even if the estimated MAP for the
+continuous plots.
+%Currently we do not have an explanation for this behaviour
+%although it is related to the aggregation:
+Even if the estimated MAP for the
 patches in each group have larger errors, after aggregation these errors seem
@@
 
-\padd{The final estimate shows the same qualitative behaviour with respect to the first
+{The final estimate shows the same qualitative behaviour with respect to the first
 stage parameters. The dashed curves obtained by zeroing out the negative
@@
 second step has the effect of reducing the differences between results obtained
-with different parameters. Based on these curves, we fix the first stage parameters at
+with different parameters. Based on these curves, we fixed the first stage parameters at
 $n_1 = 300$ and $r_1 = 95$ for color videos, and at $n_1 = 300$ and $r_1 = 180$ for grayscale videos.}
@@
 priori} covariance matrix is estimated from the basic estimate (without having
-to subtract $\sigma^2I$). As a consequence, the are no negative filter coefficients.
+to subtract $\sigma^2I$). As a consequence, there are no negative filter coefficients.
 %
@@
 %		20, 40$. In each image, the contrast has been stretched so that white
-%		corresponds to the maximum PSNR and black to a decay of 1dB bellow the
+%		corresponds to the maximum PSNR and black to a decay of 1dB below the
 %		maximum. 
@@
 the previous iterate is used as an oracle to compute patch distances.
-\padd{An additional difference is that the oracle is not used to determine the
+{An additional difference is that the oracle is not used to determine the
 signal components for the Wiener filter. Instead, these are estimated with a fixed
@@
 %iteration. 
-A more systematic study is has to be conducted before drawing any
+A more systematic study should be conducted before drawing any
 conclusions about iterative versions of the algorithm.
@@
 
-Regarding the running time, let us note that the modified profile has a
-computation time lower to that of our method. Running with a
-single core in an Intel Xeon X7560 (2.27GHz) CPU, 
-our current implementation takes on average $XXs$ per frame for a video of CIF
-resolution ($352\times288$). V-BM4D takes $44s$ with the modified profile.
-The running times of \cite{LiZhangDai2011} are not reported, but we expect them
-to be significantly higher given that the algorithm is iterative, with each iteration 
-being comparable to one of the stages of V-BM4D.
-\pcomment{TODO: Compute running times!!!}
-\pcomment{We should include computation times for grayscale videos, instead of color}
+% Regarding the running time, let us note that the modified profile has a
+% lower computation time than our method. Running with a
+% single core in an Intel Xeon X7560 (2.27GHz) CPU, 
+% our current implementation takes on average $XXs$ per frame for a video of CIF
+% resolution ($352\times288$). V-BM4D takes $44s$ with the modified profile.
+% The running times of \cite{LiZhangDai2011} are not reported, but we expect them
+% to be significantly higher given that the algorithm is iterative, with each iteration 
+% being itself far more complex to one of the stages of V-BM4D.
+% \pcomment{TODO: Compute running times!!!}
+% \pcomment{We should include computation times for grayscale videos, instead of color}
 
@@
 \right.\]
-Here $\mathcal K$ is the set of pixels that are occluded or escape out of the video
+Here $\mathcal K$ is the set of pixels that are occluded or get out of the video
 domain. The occlusion set $\mathcal K$ is also provided in MPI Sintel's database.
@@
 
-Table \ref{tab:sintel} shows the PSNR and the TCE results obatained for four sequences of the
+Table \ref{tab:sintel} shows the PSNR and the TCE results obtained for four sequences of the
 Sintel's database, and four levels of noise. For VNLB, we show results obtained with 
@@
 We presented a Bayesian video denoising algorithm assuming a Gaussian prior
-model for similar spatio-temporal patches. 
+model for each group of similar spatio-temporal patches. 
 The proposed method does not require motion estimation, yet it provides 
@@
 the dimensionality of the patches is high, and the number of available 
-similar patches is limited, we additionally assume that the prior covariance
+similar patches is limited, we additionally assumed that the prior covariance
 is of low rank. In practice this amounts to keeping only the principal 
-eigenvectors of the sample covariance matrix. This decision is analyzed
+eigenvectors of the sample covariance matrix. This decision was analyzed
 in the light of theoretical results on the estimation of covariance matrices 
@@
 
-Special attention is devoted to the evaluation of the temporal consistency of
-the result. In particular, we propose a way to quantify the temporal
+Special attention was devoted to the evaluation of the temporal consistency of
+the result. In particular, we proposed a way to quantify the temporal
 consistency error (TCE), by measuring the temporal inconsistencies in the
-residue using a ground truth optical flow. Our method shows better performance
-also with respect proposed TCE, evaluated in synthetic videos from MPI's Sintel
+residue using a ground truth optical flow. Our method also shows a better performance
+for the proposed TCE, evaluated in synthetic videos from MPI's Sintel
 database.
@@
 
-The method is still computationally expensive, and current research focus
+The method is still computationally expensive, and current research focuses
 on speeding up the search and the Bayesian estimation.

### 2016-07-20 doc/201511_notes/notes.tex

@@
 
+Figures \ref{fig:wiener_pdf_N} and \ref{fig:wiener_pdf_snr} show some examples of 
+the weights distribution, together with the Gaussian approximation, for some values of
+$N$ and $\hat{\text{snr}}$.
+
 \begin{figure}[htpb!]
@@
 	the dashed curves. The dashed vertical lines indicate $\varphi(\mathbb E\{v_j\})$.}
-	\label{fig:wiener_pdf_N}
+	\label{fig:wiener_pdf_snr}
 \end{figure}
@@
 
-The main aim of this analysis was to find an explanation for the good performance of 
-the negative weights in the NL-Bayes algorithm. We didn't achieve that objective. 
-\emph{The model adopted here is too simple, and it does not replicate the behaviour of the 
-NL-Bayes. On the contrary, in this setting thresholding the weights is better.}
+The model adopted here is too simple, and it does not replicate the behaviour of the 
+NL-Bayes. On the contrary, in this setting thresholding the weights is better.
 
-However we did learn interesting things which might be usefull in analyzing more
-complex models which might be closer to NL-Bayes. \emph{The Wiener filter is biased
-(because it damps components with low SNR), and aggregation does not fix the
-bias.} Furthermore, \emph{the thresholded coefficients help in reducing the bias} since
-they increase the expected value of the coefficient, thus reducing the damping.
+The Wiener filter is biased (because it damps components with low SNR), and
+aggregation does not fix the bias. 
+Furthermore, the thresholded
+coefficients help in reducing the bias since they increase the expected value
+of the coefficient, thus reducing the damping.
 
-In this example we consider a single Gaussian model. Thefore there exists a
-unique theoretical Wiener filter.
-The situation in non-local Bayes is much more complex. 
-A single patch might be part
-of different Gaussian models, and for each there is a Wiener filter that needs
-to be estimated. 
-Furthermore, a pixel receives contributions from different patches that overlap the
-pixel. This seems harder to model. In order to model this, one could consider 
-the aggregation as an aggregation of images instead of patches. Each image results
-from an empirical Wiener filter in a basis. This basis is built with the DCT or
+In this example we consider a single Gaussian model, and consequently a unique
+Wiener filter.
+The situation in non-local Bayes is more complex. 
+A single patch might participate 
+in different Gaussian models, each with its own Wiener filter. 
+Furthermore, a pixel receives contributions from different patches overlapping
+it. This seems harder to model. One could consider the
+an aggregation of image estimates instead of patches. Each image results
+from an empirical Wiener filter in a basis built with the DCT or
 PCA vectors of each non-overlapping patch. For an $s\times s$ patch, there are $s^2$
-of these bases, built by shifting the non-overlapping patches. An image is computed
-for each basis with a Wiener filter, and these $s^2$ images are aggregated.
+of these bases, that correspond to shifts of the non-overlapping grid of patches. An
+Wiener estimate of the image is computed for each basis, and these $s^2$ images
+are aggregated.
+
+This is a different type of aggregation: 
+a single observation is filtered in multiple bases, instead filtering multiple
+observations in the same basis.
 

### 2016-07-21 tools/patch_group_image.m
[tools] Add some old m scripts

@@ -1,0 +1,280 @@
+% loads a video and allows the user to select a pixel
+% for the selected pixel, it displays the locations 
+% of the most similar patches
+
+%clear all
+
+
+% parameters
+prms.wx = 201;
+prms.wt = 0;
+prms.px = 4;
+prms.pt = 1;
+prms.np = 200;
+sigma = 20;
+
+% path to data
+%base_path = '../../../data/';
+base_path = '../build/';
+
+% image data
+%orig_path = [base_path 'images/tune/'];
+%seq.name = 'Girl.png';
+orig_path = base_path;
+seq.name = 'bsic41.png';
+seq.first = 0;
+seq.last  = 0;
+%seq.pattern = [orig_path 'girl.png'];
+seq.pattern = [orig_path 'bsic41.png'];
+
+% % sequence data
+% orig_path = [base_path 'data/derf/'];
+% seq.name = 'bus';
+% seq.first = 1;
+% seq.last  = 150;
+% seq.pattern = [orig_path seq.name '/%03d.png'];
+
+% load
+orig = load_sequence(seq.pattern, seq.first, seq.last);
+nisy = orig + 0*sigma*randn(size(orig));
+nisy0 = nisy;
+orig0 = orig;
+
+[HH WW CC FF] = size(nisy);
+
+% show sequence
+goon = 1;
+frame = 1;
+
+main_fig_h = figure(1);
+imagesc(uint8(nisy(:,:,:,frame)));
+main_axes_h = gca;
+axis equal, axis off
+
+key = '';
+set(main_fig_h,'KeyPressFcn', @(~, evt) assignin('base', 'key', evt.Key)); 
+
+
+% build DCT basis
+cx = cos((1/2 + [0:prms.px-1]') * [0:prms.px-1]*pi/prms.px);
+ct = cos((1/2 + [0:prms.pt-1]') * [0:prms.pt-1]*pi/prms.pt);
+
+cx(:,1) = cx(:,1  ) / sqrt(prms.px); 
+ct(:,1) = ct(:,1  ) / sqrt(prms.pt); 
+cx(:,2:prms.px) = cx(:,2:prms.px) * sqrt(2/prms.px); 
+ct(:,2:prms.pt) = ct(:,2:prms.pt) * sqrt(2/prms.pt); 
+
+U = zeros(prms.px*prms.px*prms.pt, prms.px*prms.px*prms.pt);
+
+% window
[…]

### 2016-07-21 tools/psnr_vs_np1_np2_ag_images_compare.m

@@ -1,0 +1,182 @@
+root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d-dct/results/';
+root_folder =  '/home/pariasm/Work/denoising/projects/video_nlbayes3d-dct/results/';
+
+stage1_folder_m1 = [root_folder 'table_1np_vs_2np_vs_1ag_vs_2ag_img-color_1ctrY_1thY_1px8_2px4/'];
+
+method1 = 'WIE1pos';
+
+nsims1_m1 = [10 40 100 200];
+nsims2_m1 = [10 20 40 60];
+ag1s_m1  = [5 10 20 60 100 0];
+ag2s_m1  = [5 10 20 60 100 0];
+seqs = {...
+'alley',...
+'building1',...
+'computer',...
+'dice',...
+'girl',...
+'street1',...
+'traffic',...
+'trees'};
+
+sigmas = [10,40];
+
+eff_m1 = zeros(length(nsims1_m1),length(ag1s_m1),length(nsims2_m1),length(sigmas));
+ebb_m1 = zeros(length(nsims1_m1),length(ag1s_m1),length(nsims2_m1),length(sigmas));
+
+eff_m2 = zeros(length(nsims1_m1),length(ag1s_m1),length(nsims2_m1),length(sigmas));
+ebb_m2 = zeros(length(nsims1_m1),length(ag1s_m1),length(nsims2_m1),length(sigmas));
+                                                              
+
+fig_i = 10;
+for sidx = 1:length(sigmas), s = sigmas(sidx);
+
+	% load final m1
+	ff_m1 = nan(length(ag1s_m1),length(ag2s_m1),length(nsims1_m1),length(nsims2_m1),length(seqs));
+	for i = 1:length(seqs),
+		tmp = load([stage1_folder_m1 'table_fpsnr_' seqs{i} '_s' num2str(s)]);
+		tmp(tmp == 0) = NaN;
+
+		j = 0;
+		for n1 = 1:length(nsims1_m1),
+		for n2 = 1:length(nsims2_m1),
+			ff_m1(:,:,n1,n2,i) = tmp([1:length(ag1s_m1)] + length(ag1s_m1)*j,:); j = j+1;
+		end
+		end
+	end
+
+	% load basic m1
[…]

### 2016-07-21 tools/psnr_vs_np1_np2_b1_images_compare.m

@@ -1,0 +1,242 @@
+root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d-dct/results/';
+root_folder =  '/home/pariasm/Work/denoising/projects/video_nlbayes3d-dct/results/';
+
+%stage1_folder_m1 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1lzd_2wie_1px8_2px8/'];
+stage1_folder_m1 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1ctrY_1thN_1px8_2px8/'];
+stage1_folder_m2 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1ctrY_1thY_1px8_2px8/'];
+%stage1_folder_m1 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1thY_1mu3_2muN_1px8_2px8/'];
+%stage1_folder_m2 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1ctrY_1thY_b2f_1px8_2px8/'];
+%stage1_folder_m2 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1thN_1mu3_2muN_1px8_2px8/'];
+%stage1_folder_m1 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1softB_1px8_2px8/'];
+%stage1_folder_m2 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1softB_b2f_1px8_2px8/'];
+%stage1_folder_m1 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1linrT_1px8_2px8/'];
+%stage1_folder_m1 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1hardT_1px8_2px8/'];
+%stage1_folder_m1 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1softB_1px8_2px8/'];
+%stage1_folder_m2 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1hardT_1px8_2px8/'];
+%stage1_folder_m1 = [root_folder 'table_1np_vs_2np_vs_2b_img-color_1thB_2thB_1px8_2px8/'];
+%stage1_folder_m2 = [root_folder 'table_1np_vs_2np_vs_2b_img-color_1wiN_2wie_1px8_2px8/'];
+
[…]

### 2016-07-21 tools/psnr_vs_np1_np2_bm_images_compare.m

@@ -1,0 +1,238 @@
+root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d-dct/results/';
+root_folder =  '/home/pariasm/Work/denoising/projects/video_nlbayes3d-dct/results/';
+
+% this scripts generates plots comparing the results obtained with filtering
+% of the mean with those obtained without it.
+
+stage1_folder_m1 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1thY_1muH_2muN_1px8_2px8/'];
+stage1_folder_m2 = [root_folder 'table_1np_vs_2np_vs_1b_img-color_1ctrY_1thY_1px8_2px8/'];
+
+method1 = 'WIE1muHWIE2';
+method2 = 'WIE1WIE2';
+
+nsims1_m1 = [10 20 30 40 100];
+nsims1_m2 = [10 20 30 40 100];
+nsims2_m1 = [6 10 20 40 60];
+nsims2_m2 = [6 10 20 40 60];
+%b1s_m1 = [0.8 1.0 1.2 1.4 1.6 1.8 2.0 2.2 2.4 2.6 2.8 3.0 3.2 3.4];
+%b1s_m1 = [0.70 : 0.05 : 1.45];
+%b1s_m1 = [0.4 0.8 1.0 1.2 1.6 2.0];
+b1s_m1 = [0.4 : 0.2 : 2.2];
+b1s_m2 = [0.70 : 0.05 : 1.45];
+
+seqs = {...
+'alley',...
+'building1',...
+'computer',...
+'dice',...
+'girl',...
+'street1',...
+'traffic',...
+'trees'};
+
+sigmas = [10,40];
+
+eff_m1 = zeros(length(nsims2_m1),length(b1s_m1),length(nsims1_m1),length(sigmas));
+ebb_m1 = zeros(length(nsims2_m1),length(b1s_m1),length(nsims1_m1),length(sigmas));
+                                                              
+eff_m2 = zeros(length(nsims2_m2),length(b1s_m2),length(nsims1_m2),length(sigmas));
+ebb_m2 = zeros(length(nsims2_m2),length(b1s_m2),length(nsims1_m2),length(sigmas));
+
+
+% indices to be removed
+idx_n1_m2 = [];
+idx_n1_m1 = [];
+
+idx_n2_m2 = [];
[…]

### 2016-07-21 tools/psnr_vs_np1_np2_images_1cntrYvsN_img.m

@@ -1,0 +1,219 @@
+root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d-dct/results/';
+root_folder =  '/home/pariasm/Work/denoising/projects/video_nlbayes3d-dct/results/';
+
+
+% stage1_folder_pos = [root_folder 'table_1np_vs_2np_img-color_1cntrY_2cntrY_1px8_2px8_pos/'];
+% stage1_folder_neg = [root_folder 'table_1np_vs_2np_img-color_1cntrN_2cntrY_1px8_2px8_pos/'];
+
+stage1_folder_pos = [root_folder 'table_1np_vs_2np_img-color_1cntrY_2cntrY_1px8_2px8_pos/'];
+stage1_folder_neg = [root_folder 'table_1np_vs_2np_img-color_1cntrY_2cntrN_1px8_2px8_pos/'];
+
+
+% stage 1 ---------------------------------------------------
+nsims1_p = [4 6 8 10 15 20 30 40 50 60 80 100];
+nsims1_n = [4 6 8 10 15 20 30 40 50 60 80 100];
+nsims2_p = [4 6 8 10 15 20 30 40 50 60 80 100];
+nsims2_n = [1 2 3 4 6 8 10 15 20 30 40 50 60 80 100];
+seqs = {...
+'alley',...
+'book',...
+'building1',...
+'building2',...
+'computer',...
+'dice',...
+'flowers1',...
+'flowers2',...
+'gardens',...
+'girl',...
+'hallway',...
+'man1',...
+'man2',...
+'plaza',...
+'statue',...
+'street1',...
+'street2',...
+'traffic',...
+'trees',...
+'valldemossa',...
+'yard'};
+
+sigmas = [10,20,40];
+
+eff_p = zeros(length(nsims1_p),length(nsims2_p),length(sigmas));
+ebb_p = zeros(length(nsims1_p),length(nsims2_p),length(sigmas));
+
+eff_n = zeros(length(nsims1_n),length(nsims2_n),length(sigmas));
+ebb_n = zeros(length(nsims1_n),length(nsims2_n),length(sigmas));
+
+
+% indices to be removed
+idx_n1_n = [];
+idx_n1_p = [];
+
+idx_n2_n = [];
+idx_n2_p = [];
+
+fig_i = 10;
[…]

### 2016-07-21 tools/psnr_vs_np1_np2_images_compare.m

@@ -1,0 +1,158 @@
+root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d-dct/results/';
+root_folder =  '/home/pariasm/Work/denoising/projects/video_nlbayes3d-dct/results/';
+
+stage1_folder_pos = [root_folder 'table_1np_vs_2np_img-color_1ctrY_1thN_1px4_2px4/'];
+stage1_folder_neg = [root_folder 'table_1np_vs_2np_img-color_1ctrY_1thN_1px8_2px4/'];
+%stage1_folder_neg = [root_folder 'table_1np_vs_2np_img-color_1thN_2thN_1px8_2px8/'];
+
+method1 = 'WIn4WIE4';
+method2 = 'WIn8WIE4';
+
+% stage 1 ---------------------------------------------------
+nsims1_p = [10 40 100];
+nsims1_n = [10 40 100];
+nsims2_p = [6 10 20 40 60 100];
+nsims2_n = [6 10 20 40 60 100];
+seqs = {...
+'alley',...
+'building1',...
+'computer',...
+'dice',...
+'girl',...
+'street1',...
+'traffic',...
+'trees'};
+
+sigmas = [10,40];
+
+eff_p = zeros(length(nsims1_p),length(nsims2_p),length(sigmas));
+ebb_p = zeros(length(nsims1_p),length(nsims2_p),length(sigmas));
+
+eff_n = zeros(length(nsims1_n),length(nsims2_n),length(sigmas));
+ebb_n = zeros(length(nsims1_n),length(nsims2_n),length(sigmas));
+
+
+% indices to be removed
+idx_n1_n = [];
+idx_n1_p = [];
+
+idx_n2_n = [];
+idx_n2_p = [];
+
+fig_i = 10;
+for sidx = 1:length(sigmas), s = sigmas(sidx);
+
+	% load final neg
+	ff_n = nan(length(nsims1_n),length(nsims2_n),length(seqs));
+	for i = 1:length(seqs),
+		tmp = load([stage1_folder_neg 'table_fpsnr_' seqs{i} '_s' num2str(s)]);
+		tmp(tmp == 0) = NaN;
+
+		tmp(:,idx_n2_n) = [];
+		tmp(idx_n1_n,:) = [];
+		ff_n(:,:,i) = tmp;
+	end
+
+	% load basic neg
[…]

### 2016-07-21 tools/psnr_vs_np1_np2_images_posvsneg_img.m

@@ -1,0 +1,212 @@
+root_folder =  '/media/pariasm/tera/funes/denoising/projects/video_nlbayes3d-dct/results/';
+root_folder =  '/home/pariasm/Work/denoising/projects/video_nlbayes3d-dct/results/';
+
+
+stage1_folder_pos = [root_folder 'table_1np_vs_2np_img-color_1cntrY_2cntrY_1px8_2px8_pos/'];
+stage1_folder_neg = [root_folder 'table_1np_vs_2np_img-color_1cntrY_2cntrY_1px8_2px8_neg/'];
+
+
+% stage 1 ---------------------------------------------------
+nsims1 = [4 6 8 10 15 20 30 40 50 60 80 100];
+nsims2_p = [4 6 8 10 15 20 30 40 50 60 80 100];
+nsims2_n = [4 6 8 10 15 20 30 40 50 60 80 100];
+seqs = {...
+'alley',...
+'book',...
+'building1',...
+'building2',...
+'computer',...
+'dice',...
+'flowers1',...
+'flowers2',...
+'gardens',...
+'girl',...
+'hallway',...
+'man1',...
+'man2',...
+'plaza',...
+'statue',...
+'street1',...
+'street2',...
+'traffic',...
+'trees',...
+'valldemossa',...
+'yard'};
+
+sigmas = [10,20,40];
+
+eff_p = zeros(length(nsims1),length(nsims2_p),length(sigmas));
+ebb_p = zeros(length(nsims1),length(nsims2_p),length(sigmas));
+
+eff_n = zeros(length(nsims1),length(nsims2_n),length(sigmas));
+ebb_n = zeros(length(nsims1),length(nsims2_n),length(sigmas));
+
+
+% indices to be removed
+idx_n1_n = [];
+idx_n1_p = [];
+
+idx_n2_n = [];
+idx_n2_p = [];
+
+fig_i = 10;
+for sidx = 1:length(sigmas), s = sigmas(sidx);
+
+	% load final neg
+	ff_n = nan(length(nsims1),length(nsims2_n),length(seqs));
+%	for i = 1:length(seqs),
+%		tmp = load([stage1_folder_neg 'table_fpsnr_' seqs{i} '_s' num2str(s)]);
+%		tmp(tmp == 0) = NaN;
+%
+%		tmp(:,idx_n2_n) = [];
[…]

### 2016-07-21 tools/train_parameters_step1.m

@@ -1,0 +1,140 @@
+results_folder_m1 =  '/home/pariasm/Work/denoising/projects/video_nlbayes3d-dct/results/train_gray_step1_neg/';
+results_folder_m2 =  '/home/pariasm/Work/denoising/projects/video_nlbayes3d-dct/results/train_gray_step1_pos/';
+
+nsims1 = [20 30 40 50 60];
+nsims2 = [10 20 40];
+px1s = [4 6 8 12];
+wx1s = [11 21 31 41];
+
+seqs = {...
+'gray_alley',...
+'gray_building1',...
+'gray_computer',...
+'gray_dice',...
+'gray_girl',...
+'gray_street1',...
+'gray_traffic',...
+'gray_trees'};
+
+sigmas = [5,10,20,30,40,60];
+
+nsigmas = length(sigmas);
+nnsims1 = length(nsims1);
+nnsims2 = length(nsims2);
+npx1s   = length(px1s);
+nwx1s   = length(wx1s);
+
+ff_m1 = nan(nwx1s,nnsims1,npx1s,nnsims2,nsigmas,length(seqs));
+bb_m1 = nan(nwx1s,nnsims1,npx1s,nnsims2,nsigmas,length(seqs));
+ff_m2 = nan(nwx1s,nnsims1,npx1s,nnsims2,nsigmas,length(seqs));
+bb_m2 = nan(nwx1s,nnsims1,npx1s,nnsims2,nsigmas,length(seqs));
+                                                              
+% load data
+for isig = 1:nsigmas, s = sigmas(isig);
+for iseq = 1:length(seqs),
+	f = load(sprintf('%stable_fpsnr_%s_s%02d', results_folder_m1, seqs{iseq}, s));
+	b = load(sprintf('%stable_bpsnr_%s_s%02d', results_folder_m1, seqs{iseq}, s));
+
+	j = 0;
+	for inp2 = 1:nnsims2,
+	for ipx1 = 1:npx1s, j = j + 1;
+		ff_m1(:,:,ipx1,inp2,isig,iseq) = f([1:nwx1s] + nwx1s*(j-1),:);
+		bb_m1(:,:,ipx1,inp2,isig,iseq) = b([1:nwx1s] + nwx1s*(j-1),:);
+	end
+	end
+
+	f = load(sprintf('%stable_fpsnr_%s_s%02d', results_folder_m2, seqs{iseq}, s));
[…]

### 2016-07-21 tools/train_parameters_step2.m

@@ -1,0 +1,145 @@
+results_folder_m1 =  '/home/pariasm/Work/denoising/projects/video_nlbayes3d-dct/results/train_color_step2_neg/';
+results_folder_m2 =  '/home/pariasm/Work/denoising/projects/video_nlbayes3d-dct/results/train_color_step2_pos/';
+
+nsims1 = [10, 20, 30, 40, 60];
+nsims2 = [5, 10, 15, 20, 30];
+px2s  = [3, 4, 6];
+wx2s  = [11, 21, 31, 41];
+
+%nsims1 = [20 30 40 50 60];
+%nsims2 = [10 20 40];
+%px1s = [4 6 8 12];
+%wx1s = [11 21 31 41];
+
+seqs = {...
+'alley',...
+'building1',...
+'computer',...
+'dice',...
+'girl',...
+'street1',...
+'traffic',...
+'trees'};
+
+sigmas = [5,10,20,30,40];
+
+nsigmas = length(sigmas);
+nnsims2 = length(nsims2);
+nnsims1 = length(nsims1);
+npx2s   = length(px2s);
+nwx2s   = length(wx2s);
+
+ff_m1 = nan(nwx2s,nnsims2,npx2s,nnsims1,nsigmas,length(seqs));
+bb_m1 = nan(nwx2s,nnsims2,npx2s,nnsims1,nsigmas,length(seqs));
+ff_m2 = nan(nwx2s,nnsims2,npx2s,nnsims1,nsigmas,length(seqs));
+bb_m2 = nan(nwx2s,nnsims2,npx2s,nnsims1,nsigmas,length(seqs));
+                                                              
+% load data
+for isig = 1:nsigmas, s = sigmas(isig);
+for iseq = 1:length(seqs),
+	f = load(sprintf('%stable_fpsnr_%s_s%02d', results_folder_m1, seqs{iseq}, s));
+	b = load(sprintf('%stable_bpsnr_%s_s%02d', results_folder_m1, seqs{iseq}, s));
+
+	j = 0;
+	for inp1 = 1:nnsims1,
+	for ipx2 = 1:npx2s, j = j + 1;
+		ff_m1(:,:,ipx2,inp1,isig,iseq) = f([1:nwx2s] + nwx2s*(j-1),:);
+		bb_m1(:,:,ipx2,inp1,isig,iseq) = b([1:nwx2s] + nwx2s*(j-1),:);
+	end
+	end
+
[…]

### 2016-07-21 tools/vid2col_ch.m

@@ -1,0 +1,77 @@
+% Video version of im2col_ch. Rearranges video blocks into columns.
+% For a multichannel video, the vectorized blocks of each channel are staked
+% vertically in the output.
+%
+% USAGE: patches = vid2col_ch(vid, [ph pw pf], mode)
+%
+%  -> vid      : input video (height x width x channels x frames)
+%  -> ph,pw,pf : patch size
+%  -> mode     : either 'distinct' of 'sliding'
+%
+%  <- patches : output patches (ph pw ch pf x n)
+function patches = vid2col_ch(vid, psz, mode)
+
+	if nargin < 3,
+		mode = 'sliding';
+	end
+
+	ph = psz(1);
+	pw = psz(2);
+	pf = psz(3);
+	[h w c f] = size(vid);
+
+	if pf <= f,
+
+		% patch dimension (single channel)
+		pdim = prod(psz);
+		pdim2D = prod(psz(1:2));
+		pdim2Dc = pdim2D*c;
+
+		% get the number of patches that fit in each dimension
+		if strcat(mode,'sliding')
+			time_step = 1;
+			nt = f - pf + 1;
+			nx = w - pw + 1;
+			ny = h - ph + 1;
+		else
+			time_step = pf;
+			nt = ceil(f/pf);
+			nx = ceil(w/pw);
+			ny = ceil(h/ph);
+		end
+		nxy = nx*ny;
+
+		% get the number of patches per frame from first frame, first channel
+		patches = zeros(c*pdim, nx*ny*nt);
+
+
+		if strcat(mode,'sliding')
+
+			for t = 1:f,
+
+				tmin = max(t - pf + 1,1);
+				tmax = min(f - pf + 1,t);
+
+				for k = 0:c-1,
+					patches2D = im2col(vid(:,:,k+1,t),[ph pw], mode);
+
+					for t1 = tmax:-1:tmin,
+						patches((t-t1)*pdim2Dc + k*pdim2D + [1:pdim2D], (t1-1)*nxy + [1:nxy]) = patches2D;
+					end
+				end
+			end
+
+		else
+
+			error('This mode is not yet implemented')
+
+		end
+
+	else
+		patches = [];
+	end
+
+end
+
+
+

### 2016-07-21 src/NlBayes/LibMatrix.cpp
Remove low-rank SVD with id library

@@ -28,15 +28,6 @@
 #include <cblas.h>
 #include <lapacke.h>
 
-extern"C"
-{
-void iddr_aidi_(int *m, int *n, int *krank, double w[]);
-
-void iddr_asvd_(int *m, int *n, double *a, int *krank, double *w,
-                double *u, double *v, double *s, int *ier);
-}
-
-
 using namespace std;
 
 /**
@@ -389,59 +380,6 @@ int matrixSVD(
 		);
 
 	return(info);
-}
-
-/**
- * @brief Compute approximated low-rank SVD.
- *
- * NOTES:
- * - matrices are stored in column-major ordering
- * - columns of input matrices are contiguous in memory
- * - the output o_U contains the left singular vectors as columns, and is
- *   stored in column-major ordering (or as rows in row-major ordering)
- * - the output o_V contains the right singular vectors as columns, stored
- *   in column-major ordering (or as rows in row-major ordering)
- * - if the workspace vectors are empty, they are resized internally
- *
- * @param i_mat: m x n input matrix;
- * @param p_m  : rows of the matrix;
- * @param p_n  : cols of the matrix;
- * @param p_k  : rank;
- * @param o_S  : vector with min(m,n,k) singular values
- * @param o_U  : m x min(m,n,k) matrix with min(m,n,k) left singular values
- * @param o_V  : n x min(m,n,k) matrix with min(m,n,k) right singular values
- * @param i_work : id_dist's workspace
- *
- * @return none.
- **/
-int matrixLRSVD(
-	std::vector<double> &i_mat
-,	int p_n
-,	int p_m
-,	int p_k
-,	std::vector<double> &o_S
-,	std::vector<double> &o_U
-,	std::vector<double> &o_V
-,	std::vector<double> &i_work
-){
-
-	int k2 = p_k + 16;
-
-	int lwinit = (2*k2 + 17)*p_n + 27*p_m + 100;
-	int lwwork = (2*k2 + 28)*p_m + (6*k2 + 21)*p_n + 25*k2*k2 + 100;
-
-	o_S.resize(k2);      // singular values in descending order.
-	o_U.resize(p_m*k2);  // columns contain left  sigular vectors
-	o_V.resize(p_n*k2);  // columns contain right sigular vectors
-	i_work.resize(std::max(lwinit, lwwork));
-
-	int ier;
-
[…]

### 2016-07-21 src/NlBayes/VideoNLBayes.cpp

@@ -2880,140 +2880,6 @@ float computeBayesEstimateStep1_LR_SVD_LAPACK(
 }
 
 /**
- * @brief Implementation of computeBayesEstimateStep1_LR computing the
- * principal directions of the a priori covariance matrix. This functions
- * computes an approximate partial SVD of the data matrix using id_dist.
- *
- * See computeBayesEstimateStep1_LR for information about the arguments.
- **/
-float computeBayesEstimateStep1_LR_SVD_IDDIST(
-	std::vector<std::vector<float> > &io_group
-,	matWorkspace &i_mat
-,	unsigned &io_nInverseFailed
-,	nlbParams const& p_params
-,	const unsigned p_nSimP
-){
-	//! Parameters initialization
-	const float sigma2 = p_params.beta * p_params.sigma * p_params.sigma;
-	const unsigned sPC  = p_params.sizePatch * p_params.sizePatch
-	                    * p_params.sizePatchTime;
-	const unsigned r    = p_params.rank;
-
-	//! Variances
-	float  rank_variance = 0.f;
-	float total_variance = 0.f;
-
-	for (unsigned c = 0; c < io_group.size(); c++)
-	{
-		//! Center 3D groups around their baricenter
-		centerData(io_group[c], i_mat.baricenter, p_nSimP, sPC);
-
-		//! Compute SVD
-		{
-			// convert data to double
-			i_mat.svd_ddata.resize(io_group[c].size());
-			std::vector<double>::iterator ddata = i_mat.svd_ddata.begin();
-			std::vector<float >::iterator fdata =  io_group[c].begin();
-			for (int i = 0; i < io_group[c].size(); ++i)
-				*ddata++ = (double)*fdata++;
-
-			// compute low rand SVD
-			int info = matrixLRSVD(i_mat.svd_ddata, sPC, p_nSimP, r,
-					i_mat.svd_dS, i_mat.svd_dV, i_mat.svd_dU,
-					i_mat.svd_dwork);
-
-			/* NOTE: What does matrixLRSVD return?
-			 *
-			 * matrixSVD assumes that matrices are stored by columns.
-			 * If X is the data matrix stored by rows, matrixSVD computes the SVD of
[…]

### 2016-07-21 src/NlBayes/LibMatrix.cpp
Remove: NL-Bayes MAP estimation; EIGs and SVDs; dependency on Lapacke.

@@ -26,7 +26,6 @@
 #include <cstdio>
 
 #include <cblas.h>
-#include <lapacke.h>
 
 using namespace std;
 
@@ -119,72 +118,6 @@ void transposeMatrix(
 }
 
 /**
- * @brief Compute the covariance matrix.
- *
- * @param i_patches: set of patches of size (nb x N);
- * @param o_covMat: will contain patches' * patches;
- * @param p_N : size of a patch;
- * @param p_nb: number of similar patches in the set of patches.
- *
- * @return none.
- **/
-void covarianceMatrix(
-	vector<float> const& i_patches
-,	vector<float> &o_covMat
-,	const unsigned p_nb
-,	const unsigned p_N
-){
-	const float coefNorm = 1.f / (float) (p_nb);
-
-	for (unsigned i = 0; i < p_N; i++)
-	for (unsigned j = 0; j < i + 1; j++) {
-		float val = 0.f;
-		for (unsigned k = 0; k < p_nb; k++)
-			val += i_patches[i * p_nb + k] * i_patches[j * p_nb + k];
-
-		o_covMat[i * p_N + j] = val * coefNorm;
-		o_covMat[i + j * p_N] = val * coefNorm;
-	}
-}
-
-/**
- * @brief Multiply two matrix A * B. (all matrices stored in row order).
- *
- * @param o_mat = array containing n by l product matrix at exit;
- * @param i_A = input array containing n by m matrix;
- * @param i_B = input array containing m by l matrix;
- * @param p_n, p_m, p_l = dimension parameters of arrays.
- *
- * @return  none.
- **/
-void productMatrix(
-	vector<float> &o_mat
-,	vector<float> const& i_A
-,	vector<float> const& i_B
-,	const unsigned p_n
-,	const unsigned p_m
-,	const unsigned p_l
-){
-	vector<float> q0(p_m, 0.f);
-
-	for (unsigned i = 0; i < p_l; i++) {
-		for (unsigned k = 0; k < p_m; k++) {
-			q0[k] = i_B[i + k * p_l];
-		}
-
-		for (unsigned j = 0; j < p_n; j++) {
-			float z = 0.f;
-
-			for (unsigned k = 0; k < p_m; k++) {
-				z += i_A[j * p_m + k] * q0[k];
-			}
-
-			o_mat[i + j * p_l] = z;
-		}
-	}
-}
-
-/**
  * @brief Multiply two matrix A * B. It uses BLAS SGEMM.
  *
[…]

### 2016-07-21 src/NlBayes/LibMatrix.h

@@ -46,42 +46,6 @@ void transposeMatrix(
 );
 
 /**
- * @brief Compute the covariance matrix.
- *
- * @param i_patches: set of patches of size (nb x N);
- * @param o_covMat: will contain patches' * patches;
- * @param p_N : size of a patch;
- * @param p_nb: number of similar patches in the set of patches.
- *
- * @return none.
- **/
-void covarianceMatrix(
-	std::vector<float> const& i_patches
-,	std::vector<float> &o_covMat
-,	const unsigned p_nb
-,	const unsigned p_N
-);
-
-/**
- * @brief Multiply two matrix A * B. (all matrices stored in row order).
- *
- * @param o_mat = array containing n by l product matrix at exit;
- * @param i_A = input array containing n by m matrix;
- * @param i_B = input array containing m by l matrix;
- * @param p_n, p_m, p_l = dimension parameters of arrays.
- *
- * @return  none.
- **/
-void productMatrix(
-	std::vector<float> &o_mat
-,	std::vector<float> const& i_A
-,	std::vector<float> const& i_B
-,	const unsigned p_n
-,	const unsigned p_m
-,	const unsigned p_l
-);
-
-/**
  * @brief Multiply two matrix A * B. It uses BLAS SGEMM.
  *
  * @param o_AB = array containing n by l product matrix at exit;
@@ -106,103 +70,6 @@ void productMatrix(
 ,	const bool p_colMajor = true
 ,	unsigned lda = 0
 ,	unsigned ldb = 0
-);
-
-/**
- * @brief Compute a specified number of eigenvectors and eigenvalues of a
- * symmetric matrix.
- *
- * NOTES:
- * - matrices are stored in column-major ordering
- * - columns of input matrices are contiguous in memory
- * - only the upper triangular triangular part of o_mat is used
- * - the upper triangular part of o_mat is destroyed
- * - the output o_U contains the eigenvectors as columns, and is
- *   stored ini column-major ordering (i.e. it returns the eigenvectors
- *   as rows in row-major ordering)
- *
- * @param i_mat: contains input matrix;
- * @param p_n  : size of the matrix;
- * @param p_r  : number of eigenvectors and eigenvalues.
- * @param o_S  : vector with the r eigenvalues
- * @param o_U  : matrix with the r eigenvectors
- *
- * @return none.
- **/
-int matrixEigs(
-	std::vector<float> &i_mat
-,	const unsigned p_n
-,	const unsigned p_r
-,	std::vector<float> &o_S
[…]

### 2016-07-21 src/NlBayes/VideoNLBayes.cpp

@@ -28,7 +28,7 @@
 
 #include "VideoNLBayes.h"
 #include "LibMatrix.h"
-#include "../Utilities/Utilities.h"
+#include "Utilities.h"
 
 #ifdef _OPENMP
 #include <omp.h>
@@ -106,23 +106,10 @@
  * the basic estimate is used only in the computation of the patch distances.*/
 //#define NOISY_COVARIANCE2
 
-/* Decouple the frames of the 3D patches in the 2nd step. This implies that
- * each frame is considered independent of the others. Thus instead of
- * computing a single Gaussian model of dimensionality st*ch*sx*sx, we compute
- * st Gaussian models each of dimensionality ch*sx*sx. This greatly reduces the
- * computation time, but also the quality.*/
-//#define FRAMES_DECOUPLED
-
 /* Use Gaussian (of the group variance) decay for the group aggregation weights.
  * The default is a logistic threshold. */
 //#define GAUSSIAN_GROUP_AGGREGATION_WEIGHTS
 
-
-/* Choose implementation for low-rank Bayes estimate in both steps. If both
- * options are commented, the spectral decomposition of the covariance matrix
- * is computed using LAPACK's low-rank eigs */
-//#define USE_SVD_LAPACK
-//#define USE_SVD_IDDIST
 
 //#define CENTRED_SEARCH
 
@@ -279,11 +266,7 @@ void initializeNlbParameters(
 	o_params.doPasteBoost = true;
 
 	//! Color space to be used
-#ifndef DCT_BASIS
-	o_params.colorSpace = (p_step == 1) ? YUV : RGB;
-#else
 	o_params.colorSpace = YUV;
-#endif
 }
 
 /*	depend on sigma:
@@ -516,20 +499,17 @@ std::vector<float> runNlBayes(
 	//! Print compiler options
 	if (p_prms1.verbose)
 	{
-#ifdef USE_FFTW 
-		printf(ANSI_BCYN "USE_FFTW > \n" ANSI_RST);
-#endif
 #ifdef DCT_BASIS
 		printf(ANSI_BCYN "DCT_BASIS > Using DCT basis\n" ANSI_RST);
+#endif
+#ifdef USE_FFTW 
+		printf(ANSI_BCYN "USE_FFTW > \n" ANSI_RST);
 #endif
 #ifdef DCT_DONT_CENTER1
[…]

### 2016-07-21 src/NlBayes/VideoNLBayes.h

@@ -391,32 +391,6 @@ int computeHomogeneousAreaStep2(
 );
 
 /**
- * @brief Compute the Bayes estimation.
- *
- * @param io_group: contains all similar patches. Will contain estimates for all similar patches;
- * @param i_mat: contains :
- *		- groupTranspose: allocated memory. Used to contain the transpose of io_groupNoisy;
- *		- baricenter: allocated memory. Used to contain the baricenter of io_groupBasic;
- *		- covMat: allocated memory. Used to contain the covariance matrix of the 3D group;
- *		- covMatTmp: allocated memory. Used to process the Bayes estimate;
- *		- tmpMat: allocated memory. Used to process the Bayes estimate;
- * @param io_nInverseFailed: update the number of failed matrix inversion;
- * @param p_params: see processStep1 for more explanation.
- * @param p_nSimP: number of similar patches.
- * @param aggreWeights: output aggregation weights.
- *
- * @return none.
- **/
-float computeBayesEstimateStep1_FR(
-	std::vector<std::vector<float> > &io_group
-,	matWorkspace &i_mat
-,	unsigned &io_nInverseFailed
-,	nlbParams const& p_params
-,	const unsigned p_nSimP
-,	std::vector<std::vector<float> > &aggreWeights 
-);
-
-/**
  * @brief Compute the Bayes estimation assuming a low rank covariance matrix.
  *
  * @param io_group: contains all similar patches. Will contain estimates for all similar patches;
@@ -433,44 +407,13 @@ float computeBayesEstimateStep1_FR(
  *
  * @return none.
  **/
-float computeBayesEstimateStep1_LR(
+float computeBayesEstimateStep1(
 	std::vector<std::vector<float> > &io_group
 ,	matWorkspace &i_mat
 ,	unsigned &io_nInverseFailed
 ,	nlbParams const& p_params
 ,	const unsigned p_nSimP
 ,	std::vector<std::vector<float> > &aggreWeights 
-);
-
-/**
- * @brief Compute the Bayes estimation.
- *
- * @param i_groupNoisy: contains all similar patches in the noisy video;
- * @param io_groupBasic: contains all similar patches in the basic video. Will contain estimates
- *			for all similar patches;
- * @param i_mat: contains :
- *		- groupTranspose: allocated memory. Used to contain the transpose of io_groupNoisy;
[…]

### 2016-07-21 src/unit_tests/testLibMatrix.cpp
Remove: NL-Bayes unit tests.

@@ -1,234 +1,0 @@
-/*
- * Copyright (c) 2015, Pablo Arias <pariasm@gmail.com>
- * All rights reserved.
- *
- * This program is free software: you can use, modify and/or
- * redistribute it under the terms of the GNU General Public
- * License as published by the Free Software Foundation, either
- * version 3 of the License, or (at your option) any later
- * version. You should have received a copy of this license along
- * this program. If not, see <http://www.gnu.org/licenses/>.
- */
-
-#include <iostream>
-#include <cstdio>
-#include <cstdlib>
-#include <fstream>
-
-#include <string>
-#include <sstream>
-
-#include "Utilities.h"
-#include "VideoNLBayes.h"
-#include "LibMatrix.h"
-#include "cmd_option.h"
-
-#include <algorithm>
-
-/**
- * @file   testVideoNLBayes.cpp
- * @brief  Executable file to test VideoNLBayes
- *
- *
- *
- * @author PABLO ARIAS  <pariasm@gmail.com>
- **/
-
-void print_matrix(
-	std::vector<float> &matrix
-,	unsigned rows
-,	unsigned cols
-,	std::string filename
-){
-	FILE *file = fopen(filename.c_str(),"w");
-
-	// print output
-	for(int i = 0; i < rows; i++)
-	{
-		for(int j = 0; j < cols; j++)
-		{
-			fprintf(file, "%.16g ", matrix[i*cols + j]);
-		}
-		fprintf(file, "\n");
-	}
-
-	fclose(file);
-}
-
-// Assumes row-major ordering
-void print_matrix(
-	std::vector<double> &matrix
-,	unsigned rows
-,	unsigned cols
-,	std::string filename
-){
-	FILE *file = fopen(filename.c_str(),"w");
-
-	// print output
-	for(int i = 0; i < rows; i++)
-	{
-		for(int j = 0; j < cols; j++)
-		{
-			fprintf(file, "%.16g ", matrix[i*cols + j]);
-		}
-		fprintf(file, "\n");
-	}
-
-	fclose(file);
-}
-
-void print_video_size(const std::string& name, const Video<float>& vid)
-{
-	printf("%s", name.c_str());
-	printf("\tFrames: %d - Channels: %d - Height: %d - Width %d\n", 
-			vid.sz.frames, vid.sz.channels, vid.sz.height, vid.sz.width);
-}
-
-/**
- * @brief For a point in the image, computes the patch group and the
[…]

### 2016-07-21 src/unit_tests/testVideoNLBayes.cpp

@@ -1,760 +1,0 @@
-/*
- * Copyright (c) 2015, Pablo Arias <pariasm@gmail.com>
- * All rights reserved.
- *
- * This program is free software: you can use, modify and/or
- * redistribute it under the terms of the GNU General Public
- * License as published by the Free Software Foundation, either
- * version 3 of the License, or (at your option) any later
- * version. You should have received a copy of this license along
- * this program. If not, see <http://www.gnu.org/licenses/>.
- */
-
-#include <iostream>
-#include <stdio.h>
-#include <stdlib.h>
-#include <fstream>
-
-#include <string>
-#include <sstream>
-
-#include "Utilities.h"
-#include "VideoNLBayes.h"
-#include "LibMatrix.h"
-#include "cmd_option.h"
-
-#include <algorithm>
-
-/**
- * @file   testVideoNLBayes.cpp
- * @brief  Executable file to test VideoNLBayes
- *
- *
- *
- * @author PABLO ARIAS  <pariasm@gmail.com>
- **/
-
-// Assumes row-major ordering
-void print_matrix(
-	std::vector<float> &matrix
-,	unsigned rows
-,	unsigned cols
-,	std::string filename
-){
-	FILE *file = fopen(filename.c_str(),"w");
-
-	// print output
-	for(int i = 0; i < rows; i++)
-	{
-		for(int j = 0; j < cols; j++)
-		{
-			fprintf(file, "%.16g ", matrix[i*cols + j]);
-		}
-		fprintf(file, "\n");
-	}
-
-	fclose(file);
-}
-
-// Assumes row-major ordering
-void print_matrix(
-	std::vector<double> &matrix
-,	unsigned rows
-,	unsigned cols
-,	std::string filename
-){
-	FILE *file = fopen(filename.c_str(),"w");
-
-	// print output
-	for(int i = 0; i < rows; i++)
-	{
-		for(int j = 0; j < cols; j++)
-		{
-			fprintf(file, "%.16g ", matrix[i*cols + j]);
-		}
-		fprintf(file, "\n");
-	}
-
-	fclose(file);
-}
-
-namespace VideoNLB
-{
-	std::vector<std::pair<float, unsigned> > estimateSimilarPatchesStep1_debug(
-		Video<float> const& i_im
-	,	std::vector<std::vector<float> > &o_group
-	,	std::vector<unsigned> &o_index
[…]

### 2016-07-21 src/core/VideoNLBayes.h
Nicer folder names

@@ -13,8 +13,8 @@
 #ifndef VIDEO_NL_BAYES_H_INCLUDED
 #define VIDEO_NL_BAYES_H_INCLUDED
 
-#include "../Utilities/LibVideoT.hpp"
-#include "../Utilities/Utilities.h"
+#include "../utils/LibVideoT.hpp"
+#include "../utils/Utilities.h"
 #include "LibDCT.h"
 
 //#define DEBUG_SHOW_WEIGHT

### 2016-07-21 src/main_vnlb.cpp

@@ -19,9 +19,9 @@
 #include <string>
 #include <sstream>
 
-#include "Utilities/Utilities.h"
-#include "NlBayes/VideoNLBayes.h"
-#include "Utilities/cmd_option.h"
+#include "utils/Utilities.h"
+#include "core/VideoNLBayes.h"
+#include "utils/cmd_option.h"
 
 using namespace std;
 

### 2016-07-21 src/core/nldct.cpp
Renamed VideoNLBayes.h/cpp

@@ -12,11 +12,13 @@
  */
 
 /**
- * @file VideoNLBayes.cpp
- * @brief Video NL-Bayes denoising functions
+ * @file nldct.cpp
+ * @brief NL-DCT image & video denoising functions
  *
- * @author Marc Lebrun <marc.lebrun.ik@gmail.com>
  * @author Pablo Arias <pariasm@gmail.com>
+ *
+ * Based on NL-Bayes code from
+ * Marc Lebrun <marc.lebrun.ik@gmail.com>
  **/
 
 #include <stdexcept>
@@ -26,7 +28,7 @@
 #include <math.h>
 #include <float.h>
 
-#include "VideoNLBayes.h"
+#include "nldct.h"
 #include "LibMatrix.h"
 #include "Utilities.h"
 

### 2016-07-21 src/main_vnlb.cpp

@@ -20,7 +20,7 @@
 #include <sstream>
 
 #include "utils/Utilities.h"
-#include "core/VideoNLBayes.h"
+#include "core/nldct.h"
 #include "utils/cmd_option.h"
 
 using namespace std;

### 2016-07-21 src/tests/patch_group.cpp

@@ -19,7 +19,7 @@
 #include <sstream>
 
 #include "Utilities.h"
-#include "VideoNLBayes.h"
+#include "nldct.h"
 #include "cmd_option.h"
 
 #include <algorithm>

### 2016-07-21 src/core/LibDCT.cpp
Renamed LibMatrix.h/cpp

@@ -15,7 +15,7 @@
 #include <cstdio>
 #include <cmath>
 
-#include "LibMatrix.h"
+#include "matrix_funs.h"
 
 #ifdef _OPENMP
 #include <omp.h>

### 2016-07-21 src/core/matrix_funs.cpp

@@ -12,14 +12,14 @@
  */
 
 /**
- * @file LibMatrix.cpp
+ * @file matrix_funs.cpp
  * @brief Tools for matrix manipulation, based on ccmath functions
  *        by Daniel A. Atkinson.
  *
  * @author Marc Lebrun <marc.lebrun.ik@gmail.com>
  **/
 
-#include "LibMatrix.h"
+#include "matrix_funs.h"
 #include <iostream>
 #include <cmath>
 #include <cstdlib>

### 2016-07-21 src/core/nldct.cpp

@@ -29,7 +29,7 @@
 #include <float.h>
 
 #include "nldct.h"
-#include "LibMatrix.h"
+#include "matrix_funs.h"
 #include "Utilities.h"
 
 #ifdef _OPENMP

### 2016-07-21 src/tests/testLibDCT.cpp

@@ -22,7 +22,7 @@
 #include "Utilities.h"
 #include "LibDCT.h"
 #include "LibVideoT.hpp"
-#include "LibMatrix.h"
+#include "matrix_funs.h"
 
 
 /**

### 2016-07-21 src/core/dct_handler.cpp
Renamed LibDCT.h/cpp

@@ -10,7 +10,7 @@
  * this program. If not, see <http://www.gnu.org/licenses/>.
  */
 
-#include "LibDCT.h"
+#include "dct_handler.h"
 #include <cstdlib>
 #include <cstdio>
 #include <cmath>

### 2016-07-21 src/core/nldct.h

@@ -15,7 +15,7 @@
 
 #include "../utils/LibVideoT.hpp"
 #include "../utils/Utilities.h"
-#include "LibDCT.h"
+#include "dct_handler.h"
 
 //#define DEBUG_SHOW_WEIGHT
 //#define DEBUG_COMPUTE_GROUP_ERROR

### 2016-07-21 src/tests/test_dct_handler.cpp

@@ -20,7 +20,7 @@
 #include <sstream>
 
 #include "Utilities.h"
-#include "LibDCT.h"
+#include "dct_handler.h"
 #include "LibVideoT.hpp"
 #include "matrix_funs.h"
 

### 2016-07-21 src/core/nldct.cpp
Renamed Utilities.h/cpp

@@ -30,7 +30,7 @@
 
 #include "nldct.h"
 #include "matrix_funs.h"
-#include "Utilities.h"
+#include "utilities.h"
 
 #ifdef _OPENMP
 #include <omp.h>

### 2016-07-21 src/core/nldct.h

@@ -14,7 +14,7 @@
 #define VIDEO_NL_BAYES_H_INCLUDED
 
 #include "../utils/LibVideoT.hpp"
-#include "../utils/Utilities.h"
+#include "../utils/utilities.h"
 #include "dct_handler.h"
 
 //#define DEBUG_SHOW_WEIGHT

### 2016-07-21 src/main_vnlb.cpp

@@ -19,7 +19,7 @@
 #include <string>
 #include <sstream>
 
-#include "utils/Utilities.h"
+#include "utils/utilities.h"
 #include "core/nldct.h"
 #include "utils/cmd_option.h"
 

### 2016-07-21 src/tests/patch_group.cpp

@@ -18,7 +18,7 @@
 #include <string>
 #include <sstream>
 
-#include "Utilities.h"
+#include "utilities.h"
 #include "nldct.h"
 #include "cmd_option.h"
 

### 2016-07-21 src/tests/testLibVideoT.cpp

@@ -19,7 +19,7 @@
 #include <string>
 #include <sstream>
 
-#include "Utilities.h"
+#include "utilities.h"
 #include "LibVideoT.hpp"
 
 
@@ -182,7 +182,7 @@ class Video
 		void saveVideoAscii(const std::string i_prefix, 
 		                    unsigned i_firstFrame, unsigned i_frameStep = 1) const;
 
-		//! Utilities
+		//! utilities
 		unsigned index(unsigned x, unsigned y, unsigned t, unsigned c) const;
 		void coords(unsigned index, unsigned& x, unsigned& y, unsigned& t, unsigned& c) const;
 

### 2016-07-21 src/tests/test_dct_handler.cpp

@@ -19,7 +19,7 @@
 #include <string>
 #include <sstream>
 
-#include "Utilities.h"
+#include "utilities.h"
 #include "dct_handler.h"
 #include "LibVideoT.hpp"
 #include "matrix_funs.h"

### 2016-07-21 src/utils/LibImages.cpp

@@ -18,7 +18,7 @@
  **/
 
 #include "LibImages.h"
-#include "Utilities.h"
+#include "utilities.h"
 #include "mt19937ar.h"
 
 #include <unistd.h> // getpid

### 2016-07-21 src/utils/LibVideoT.hpp

@@ -22,7 +22,7 @@
 
 
 #include "mt19937ar.h"
-#include "Utilities.h"
+#include "utilities.h"
 
 /**
  * @brief Structure containing size informations of a video.
@@ -396,7 +396,7 @@ inline T Video<T>::getPixelSymmetric(
 }
 
 
-//! Utilities for video
+//! utilities for video
 namespace VideoUtils
 {
 	/**

### 2016-07-21 src/utils/utilities.cpp

@@ -12,12 +12,12 @@
 
 /**
  * @file utilities.cpp
- * @brief Utilities functions.
+ * @brief utilities functions.
  *
  * @author Marc Lebrun <marc.lebrun.ik@gmail.com>
  **/
 
-#include "Utilities.h"
+#include "utilities.h"
 
 #include <math.h>
 #include <omp.h>

### 2016-07-21 src/utils/LibVideoT.cpp
Renamed LibImages.h/cpp

@@ -20,7 +20,7 @@
 #include "LibVideoT.hpp"
 
 //#include <fftw3.h>
-#include "LibImages.h"
+#include "lib_image.h"
 
 #include <cstdio>
 #include <cstdlib> // EXIT_FAILURE

### 2016-07-21 src/utils/lib_image.cpp

@@ -11,13 +11,13 @@
  */
 
 /**
- * @file LibImages.cpp
+ * @file lib_image.cpp
  * @brief Usefull functions on images
  *
  * @author Marc Lebrun <marc.lebrun.ik@gmail.com>
  **/
 
-#include "LibImages.h"
+#include "lib_image.h"
 #include "utilities.h"
 #include "mt19937ar.h"
 

### 2016-07-21 src/utils/utilities.h

@@ -13,7 +13,7 @@
 #define UTILITIES_H_INCLUDED
 
 #include <vector>
-#include "LibImages.h"
+#include "lib_image.h"
 
 /**
  * @brief Convenient function to use the sort function provided by the vector library.

### 2016-07-21 src/core/nldct.h
Renamed LibVideoT.h/cpp

@@ -13,7 +13,7 @@
 #ifndef VIDEO_NL_BAYES_H_INCLUDED
 #define VIDEO_NL_BAYES_H_INCLUDED
 
-#include "../utils/LibVideoT.hpp"
+#include "../utils/lib_videot.hpp"
 #include "../utils/utilities.h"
 #include "dct_handler.h"
 

### 2016-07-21 src/tests/test_dct_handler.cpp

@@ -21,12 +21,12 @@
 
 #include "utilities.h"
 #include "dct_handler.h"
-#include "LibVideoT.hpp"
+#include "lib_videot.hpp"
 #include "matrix_funs.h"
 
 
 /**
- * @file   testLibVideoT.cpp
+ * @file   testlib_videot.cpp
  * @brief  Executable file to test libVideoT
  *
  *

### 2016-07-21 src/tests/test_lib_videot.cpp

@@ -20,11 +20,11 @@
 #include <sstream>
 
 #include "utilities.h"
-#include "LibVideoT.hpp"
+#include "lib_videot.hpp"
 
 
 /**
- * @file   testLibVideoT.cpp
+ * @file   testlib_videot.cpp
  * @brief  Executable file to test libVideoT
  *
  *

### 2016-07-21 src/utils/lib_videot.cpp

@@ -11,13 +11,13 @@
  */
 
 /**
- * @file LibVideoT.cpp
- * @brief Spetializations of template functions defined in LibVideoT.hpp
+ * @file lib_videot.cpp
+ * @brief Spetializations of template functions defined in lib_videot.hpp
  *
  * @author Pablo Arias <pariasm@gmail.com>
  **/
 
-#include "LibVideoT.hpp"
+#include "lib_videot.hpp"
 
 //#include <fftw3.h>
 #include "lib_image.h"

### 2016-07-21 src/core/nldct.cpp
Tau distance threshold for step 1.

@@ -369,9 +369,7 @@ void setNSimilarPatches(nlbParams& prms, unsigned nSimilarPatches)
  **/
 void setTau(nlbParams& prms, const VideoSize &size, float tau)
 {
-	prms.tau = (!prms.isFirstStep) 
-	         ? tau * tau * prms.sizePatch * prms.sizePatch * size.channels
-	         : 0.f;
+	prms.tau = tau * tau * prms.sizePatch * prms.sizePatch * size.channels;
 }
 
 /**
@@ -393,8 +391,7 @@ void printNlbParameters(
 	printf("\t\tPatch size                  = %d\n"       , i_prms.sizePatch);
 	printf("\t\tPatch size temporal         = %d\n"       , i_prms.sizePatchTime);
 	printf("\t\tNumber of patches           = %d\n"       , i_prms.nSimilarPatches);
-	if (!i_prms.isFirstStep) printf("\t\tDistance threshold (tau)    = %g\n"       , i_prms.tau);
-	else                     printf("\t\tDistance threshold (tau)    = N/A\n"      );
+	printf("\t\tDistance threshold (tau)    = %g\n"       , i_prms.tau);
 	printf("\t\tSpatial search window       = %dx%d\n"    , i_prms.sizeSearchWindow, i_prms.sizeSearchWindow);
 	printf("\t\tTemporal search range       = [-%d,%d]\n" , i_prms.sizeSearchTimeRangeBwd, i_prms.sizeSearchTimeRangeBwd);
 	printf("\t\tSpatial border added        = %d\n"       , i_prms.boundary);
@@ -1035,7 +1032,8 @@ unsigned processNlBayes(
 
 	//! Used matrices during Bayes' estimate
 	const unsigned patch_dim = step1 ? sPx * sPx * sPt : sPx * sPx * sPt * sz.channels;
-	const unsigned patch_num = step1 ? p_params.nSimilarPatches : sWx * sWx * sWt;
+//	const unsigned patch_num = step1 ? p_params.nSimilarPatches : sWx * sWx * sWt;
+	const unsigned patch_num = sWx * sWx * sWt;
 
 	//! Matrices used for Bayes' estimate
 	vector<unsigned> index(patch_num);
@@ -1466,25 +1464,27 @@ unsigned estimateSimilarPatchesStep1(
[…]

### 2016-07-21 src/main_vnlb.cpp

@@ -83,6 +83,7 @@ int main(int argc, char **argv)
 	const float beta2       = clo_option("-b2" ,-1.f, "> Noise correction factor beta, step 2");
 	const float beta_mean1  = clo_option("-bm1",-1.f, "> Noise correction factor beta for mean, step 1");
 	const float beta_mean2  = clo_option("-bm2",-1.f, "> Noise correction factor beta for mean, step 2");
+	const float tau1        = clo_option("-t1" ,-1.f, "> Step 1 distance threshold");
 	const float tau2        = clo_option("-t2" ,-1.f, "> Step 2 distance threshold");
 	const float p_aggre1    = clo_option("-pag1", 0.f, "> Decay of per-patch aggregation weights, step 1");
 	const float p_aggre2    = clo_option("-pag2", 0.f, "> Decay of per-patch aggregation weights, step 2");
@@ -171,6 +172,7 @@ int main(int argc, char **argv)
 		if (beta2         >= 0) prms2.beta = beta2;
 		if (beta_mean1    >= 0) prms1.betaMean = beta_mean1;
 		if (beta_mean2    >= 0) prms2.betaMean = beta_mean2;
+		if (tau1          >= 0) VideoNLB::setTau(prms1, tmp, tau1);
 		if (tau2          >= 0) VideoNLB::setTau(prms2, tmp, tau2);
 
 		prms1.rank = rank1;
@@ -249,6 +251,7 @@ int main(int argc, char **argv)
 	if (beta2         >= 0) prms2.beta = beta2;
 	if (beta_mean1    >= 0) prms1.betaMean = beta_mean1;
 	if (beta_mean2    >= 0) prms2.betaMean = beta_mean2;
+	if (tau1          >= 0) VideoNLB::setTau(prms1, noisy.sz, tau1);
 	if (tau2          >= 0) VideoNLB::setTau(prms2, noisy.sz, tau2);
 
 	prms1.rank = rank1;
@@ -266,6 +269,8 @@ int main(int argc, char **argv)
 
 	//! Percentage or processed groups of patches over total number of pixels
 	std::vector<float> groupsRatio;
+
+	printf("%f %f\n",tau1,prms1.tau);
 
 	//! Run denoising algorithm
 #ifndef DEBUG_COMPUTE_GROUP_ERROR

### 2016-07-21 src/core/nldct.cpp
Better normalization for tau1.

@@ -53,7 +53,7 @@
  * coefficient is set to zero. This applies whenever the Gaussian model is
  * estimated from the noisy patches: in the first step, or in the second step
  * if NOISY_COVARIANCE2 option is defined. */
-//#define THRESHOLD_WEIGHTS1
+#define THRESHOLD_WEIGHTS1
 //#define THRESHOLD_WEIGHTS2
 
 /* Uses an adaptation of Li,Zhand,Dai fixed point iteration to estimate the
@@ -369,7 +369,8 @@ void setNSimilarPatches(nlbParams& prms, unsigned nSimilarPatches)
  **/
 void setTau(nlbParams& prms, const VideoSize &size, float tau)
 {
-	prms.tau = tau * tau * prms.sizePatch * prms.sizePatch * size.channels;
+	prms.tau = tau * tau * prms.sizePatch * prms.sizePatch * 
+	           prms.sizePatchTime * (prms.isFirstStep ? 1 : size.channels);
 }
 
 /**

### 2016-07-21 src/main_vnlb.cpp

@@ -270,8 +270,6 @@ int main(int argc, char **argv)
 	//! Percentage or processed groups of patches over total number of pixels
 	std::vector<float> groupsRatio;
 
-	printf("%f %f\n",tau1,prms1.tau);
-
 	//! Run denoising algorithm
 #ifndef DEBUG_COMPUTE_GROUP_ERROR
 	groupsRatio = VideoNLB::runNlBayes(noisy, basic, final, prms1, prms2);

### 2016-07-21 doc/201504_acivs/figs/time_coherence_image.m
Deleted documentation from nlbayes

@@ -1,28 +1,0 @@
-v1 = mean(single(imread('/data/pablo/boucantrin/denoising/projects/video_nlbayes/results/vnlbayes/table_1ps5_2ps5_2wx37_2np93/tennis_s40_tr2/deno_121.png')),3);
-v2 = mean(single(imread('/data/pablo/boucantrin/denoising/projects/video_nlbayes/results/vnlbayes/table_1ps5_2ps5_2wx37_2np93/tennis_s40_tr2/deno_122.png')),3);
-v3 = mean(single(imread('/data/pablo/boucantrin/denoising/projects/video_nlbayes/results/vnlbayes/table_1ps5_2ps5_2wx37_2np93/tennis_s40_tr2/deno_123.png')),3);
-v4 = mean(single(imread('/data/pablo/boucantrin/denoising/projects/video_nlbayes/results/vnlbayes/table_1ps5_2ps5_2wx37_2np93/tennis_s40_tr2/deno_124.png')),3);
-v5 = mean(single(imread('/data/pablo/boucantrin/denoising/projects/video_nlbayes/results/vnlbayes/table_1ps5_2ps5_2wx37_2np93/tennis_s40_tr2/deno_125.png')),3);
-
-td1 = abs(v1 - v2) + ...
-      abs(v2 - v2) + ...
-      abs(v3 - v3) + ...
-      abs(v4 - v5) / 4;
-
-td1 = min(td1/20*255,255);
-
-u1 = mean(single(imread('/data/pablo/purple/dev/results/VBM4D/tennis_s40/deno_121.png')),3);
-u2 = mean(single(imread('/data/pablo/purple/dev/results/VBM4D/tennis_s40/deno_122.png')),3);
-u3 = mean(single(imread('/data/pablo/purple/dev/results/VBM4D/tennis_s40/deno_123.png')),3);
-u4 = mean(single(imread('/data/pablo/purple/dev/results/VBM4D/tennis_s40/deno_124.png')),3);
-u5 = mean(single(imread('/data/pablo/purple/dev/results/VBM4D/tennis_s40/deno_125.png')),3);
-
-td2 = abs(u1 - u2) + ...
-      abs(u2 - u2) + ...
-      abs(u3 - u3) + ...
-      abs(u4 - u5) / 4;
-
-td2 = min(td2/20*255,255);
-
-imwrite(uint8(td1),'time_diff_vnlb_s40.png');
-imwrite(uint8(td2),'time_diff_bm4d_s40.png');

### 2016-07-21 doc/201506_cambridge_slides/figures_local/derf_generate_details.m

@@ -1,125 +1,0 @@
-% combines different denoising results for in the same video,
-% for visualization purposes
-
-% path to data
-base_path = '/media/pariasm/tera/funes/denoising/';
-bm4d_path = [base_path 'algos/results/VBM4D/'];
-orig_path = [base_path 'data/derf/'];
-%nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps5_2ps5_2wx37_2r16_2np160/'];
-%nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/table_1ps7_2ps5_2wx45_r16/'];
-nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/tip_table_1ps7_2ps7-neg/'];
-%nlb3_path = [base_path 'projects/video_nlbayes3d/results/vnlbayes/tip_table_1ps5_2ps5-neg/'];
-
-
-% generated tiles ------------------- %
-
-%seqnames = {'football_mono','mobile_mono','stefan_mono','tennis_mono'};
-%first    = {1              , 1           , 1           , 1           };
-%last     = {260            , 300         , 300         , 150         };
-%seqnames = {'bus','coastguard','foreman','tennis'};
-%first    = {1    , 1          , 1       , 1      };
-%last     = {150  , 300        , 300     , 150    };
-
-% color
-
-%---% seq.name = 'tennis'; seq.first = 1; seq.last = 150;
-%---% ti=050; tj=090; tt=030; wi=150; wj=150; wt=30;
-%---% 
-%---% seq.name = 'tennis'; seq.first = 1; seq.last = 150;
-%---% ti=040; tj=150; tt=070; wi=150; wj=150; wt=30;
-%---% 
-%---% seq.name = 'bus'; seq.first = 1; seq.last = 150;
-%---% ti=060; tj=020; tt=020; wi=150; wj=150; wt=30;
-%---% 
-%---% seq.name = 'bus'; seq.first = 1; seq.last = 150;
-%---% ti=110; tj=150; tt=010; wi=150; wj=150; wt=30;
-
-% grayscale
-
-%---% seq.name = 'stefan_mono'; seq.first = 1; seq.last = 300;
[…]

### 2016-07-21 doc/201506_cambridge_slides/figures_local/images_local_copy.sh

@@ -1,210 +1,0 @@
-mkdir -p figures_local/data/derf/mobile_mono
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s10_pt4
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s20_pt4
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s40_pt4
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s10_pt4
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s20_pt4
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s40_pt4
-mkdir -p figures_local/VBM4D/mobile_mono_mp_s10
-mkdir -p figures_local/VBM4D/mobile_mono_mp_s20
-mkdir -p figures_local/VBM4D/mobile_mono_mp_s40
-mkdir -p figures_local/data/derf/mobile_mono
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s10_pt4
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s20_pt4
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s40_pt4
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s10_pt4
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s20_pt4
-mkdir -p figures_local/vnlb3d_mono/mobile_mono_s40_pt4
-mkdir -p figures_local/VBM4D/mobile_mono_mp_s10
-mkdir -p figures_local/VBM4D/mobile_mono_mp_s20
-mkdir -p figures_local/VBM4D/mobile_mono_mp_s40
-mkdir -p figures_local/data/derf/stefan_mono
-mkdir -p figures_local/vnlb3d_mono/stefan_mono_s10_pt4
-mkdir -p figures_local/vnlb3d_mono/stefan_mono_s20_pt4
-mkdir -p figures_local/vnlb3d_mono/stefan_mono_s40_pt4
-mkdir -p figures_local/vnlb3d_mono/stefan_mono_s10_pt4
-mkdir -p figures_local/vnlb3d_mono/stefan_mono_s20_pt4
-mkdir -p figures_local/vnlb3d_mono/stefan_mono_s40_pt4
-mkdir -p figures_local/VBM4D/stefan_mono_mp_s10
[…]

### 2016-07-21 doc/201507_tip/average_psnr.m

@@ -1,108 +1,0 @@
-% bsc10 = [34.32 33.99 33.47 34.22 34.22 
-%          34.33 34.44 33.82 34.91 34.91 
-%          34.53 34.74 33.81 34.70 34.70 
-%          34.18 34.41 33.47 34.18 34.18];
-%                                        
-% bsc20 = [30.54 29.67 29.04 30.16 30.16 
-%          30.73 29.83 29.38 30.96 30.96 
-%          30.82 30.15 29.33 30.67 30.67 
-%          30.25 29.74 28.89 29.96 29.96];
-%                                        
-% bsc40 = [27.67 24.64 24.47 26.67 26.67 
-%          27.14 25.43 25.18 27.23 27.23 
-%          27.63 26.15 25.44 27.37 27.37 
-%          27.81 26.45 25.50 27.31 27.31];
-%          
-% fnl10 = [34.95 34.11 33.68 34.95 34.95
-%          34.62 34.67 34.23 35.61 35.61
-%          35.15 35.31 34.29 35.67 35.67
-%          35.32 35.54 34.13 35.61 35.61];
-%                                       
-% fnl20 = [31.08 30.49 29.69 31.06 31.06
-%          31.24 30.34 29.90 31.82 31.82
-%          31.66 31.09 30.02 31.83 31.83
-%          31.69 31.35 29.97 31.66 31.66];
-%                                       
-% fnl40 = [28.38 26.02 25.64 27.62 27.62
-%          28.15 26.06 25.81 28.24 28.24
-%          28.62 26.94 26.12 28.42 28.42
-%          28.86 27.46 26.24 28.45 28.45];
-
-fnl05 = [ 39.45 40.18 40.16 39.07  
-			 39.98 41.13 41.38 40.21  
-			 39.60 40.28 40.78 39.56  
-			 39.37 41.49 41.95 40.43  
-			 40.15 42.25 42.56 40.97  
-			 40.16 42.45 42.61 41.12  
-			 40.01 42.38 42.48 41.02 ];
-%                                  
-fnl10 = [ 36.04 36.82 37.52 34.96  
-			 36.42 37.27 37.92 36.23  
-			 35.90 36.30 37.21 35.38  
-			 35.30 37.30 38.16 36.38  
-			 36.42 38.27 39.02 36.97  
-			 36.72 38.63 39.24 37.25  
-			 36.81 38.73 39.24 37.34 ];
[…]

### 2016-07-21 prof/analysis_step2_eigs_vs_inv.m
Deleted prof/ and some reorganization

@@ -1,102 +1,0 @@
-% data
-
-
-% s10 -------------------------------------------------------------------
-cov2_fr = 0.2094;
-cov2_lr = 0.3409;
-
-covinv2_fr = 0.4139; % * step2_fr
-coveig2_lr = 0.6220; % * step2_lr
-
-mprod2_fr = 1 - cov2_fr - covinv2_fr;
-mprod2_lr = 1 - cov2_lr - coveig2_lr;
-
-%
-% (time matrix eigs) / (time matrix inv)
-%
-covdecomp2_lr_over_fr = cov2_fr / cov2_lr * coveig2_lr / covinv2_fr;
-disp(['s40 | Reduction in cov matrix decomposition:' ])
-disp(covdecomp2_lr_over_fr)
-
-%
-% (time matrix prod low rank) / (time matrix prod full rank)
-%
-matrixprod2_lr_over_fr = cov2_fr / cov2_lr * mprod2_lr / mprod2_fr;
-disp(['s40 | Reduction in matrix product for group denoising:' ])
-disp(matrixprod2_lr_over_fr)
-
-%
-% (time step 2 low rank) / (time step 2 full rank)
-%
-step2_lr_over_fr = cov2_fr / cov2_lr;
-disp(['s40 | Overall reduction in step 2 bayes estimate:' ])
-disp(step2_lr_over_fr)
-
-
-
-
-% s20 -------------------------------------------------------------------
-cov2_fr = 0.2094;
-cov2_lr = 0.3409;
-
-covinv2_fr = 0.4139; % * step2_fr
-coveig2_lr = 0.6220; % * step2_lr
-
-mprod2_fr = 1 - cov2_fr - covinv2_fr;
-mprod2_lr = 1 - cov2_lr - coveig2_lr;
-
-%
-% (time matrix eigs) / (time matrix inv)
-%
-covdecomp2_lr_over_fr = cov2_fr / cov2_lr * coveig2_lr / covinv2_fr;
-disp(['s40 | Reduction in cov matrix decomposition:' ])
-disp(covdecomp2_lr_over_fr)
-
-%
-% (time matrix prod low rank) / (time matrix prod full rank)
-%
-matrixprod2_lr_over_fr = cov2_fr / cov2_lr * mprod2_lr / mprod2_fr;
-disp(['s40 | Reduction in matrix product for group denoising:' ])
-disp(matrixprod2_lr_over_fr)
-
-%
[…]

### 2016-07-21 prof/analysis_step2_idsvd_vs_eigs.m

@@ -1,24 +1,0 @@
-% data
-
-
-prodmatrix2_eigs  = 0.0285;
-prodmatrix2_idsvd = 0.1392;
-
-matrixsvd2_idsvd = 0.6220; % * step2_lr
-matrixeig2_eigs  = 0.6338; % * step2_fr
-
-%
-% (time matrix eigs) / (time matrix inv)
-%
-covdecomp2_idsvd_over_eigs = prodmatrix2_eigs / prodmatrix2_idsvd * matrixsvd2_idsvd / matrixeig2_eigs;
-disp(['s10 | Reduction in computation of principal directions:' ])
-disp(covdecomp2_idsvd_over_eigs)
-
-%
-% (time step 2 low rank) / (time step 2 full rank)
-%
-step2_lr_over_fr = prodmatrix2_eigs / prodmatrix2_idsvd;
-disp(['Overall reduction in step 2 bayes estimate:' ])
-disp(step2_lr_over_fr)
-
-

### 2016-07-21 doc/201602_ms-nl-dct/main.tex
Added multiscale nl-dct report

%------------------------------------------------------------------------------
% IPOL LaTeX style guide and Example
% by rafael grompone von gioi, nicolas limare, jose-luis lisani and others
%------------------------------------------------------------------------------

% IPOL class is based on the standard LaTeX article class is used
% essentially in the same way. The layout must not be changed. Special
% IPOL commands are used to set the title, authors and abstract.

\documentclass{ipol}

% Do not use math notations and greek letters in the title.
\ipolSetTitle{DCT denoising}

% Author names must be separated with commas (,), not "and" or "&".
\ipolSetAuthors{First Author \ipolAuthorMark{1},
                Second Author\ipolAuthorMark{2}}

% Affiliations must contain the department, institution and country.
% Use a professional email address (no gmail, yahoo, etc).
% Do not add postal address.
\ipolSetAffiliations{%
\ipolAuthorMark{1} Department, Institution, Country
                   (\texttt{user@server.net})\\
\ipolAuthorMark{2} Department, Institution, Country
                   (\texttt{username@mailserver.edu})}

%------------------------------------------------------------------------------

% The link hereafter points to IPOL documentation for convenience
% in this document but must be replaced in your manuscript.
% The preprint link will not be known before the first preprint page
% is created. For early preprint versions, just don't use this command
% and the link will be set to the IPOL journal DOI address.
\ipolPreprintLink{http://www.ipol.im/}

%------------------------------------------------------------------------------

% Add packages and definitions here.
% Keep the package list as small as possible and include the package
% sources (packagename.sty) with your article source.
% These packages are loaded by the IPOL class or considered standard,
% and need not be provided with their source if they are used:
%   color, hyperref, graphicx, rotating
%   amsmath, amssymb, amsthm
% For algorithms, please use the algorithm2e package instead of
% algorithmx for simplicity and a uniform style.

% times new roman font
%\usepackage{mathptmx}

\usepackage[vlined,ruled]{algorithm2e}
% define input and output keywords
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
% define comment style
\SetKwComment{Comment}{}{}
\newcommand{\mycmtsty}[1]{\em \small #1}
\SetCommentSty{mycmtsty}

% Use \newtheorem{} for remarks and definitions.
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\newtheorem*{remark}{Remark}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\newcommand{\ma}[1]{\boldsymbol{#1}}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

%------------------------------------------------------------------------------

\usepackage{fancyvrb}
\VerbatimFootnotes % allows verbatim text in footnotes

\begin{document}

% IPOL encourages authors to do joint submissions to IPOL and
% SIIMS (SIAM Journal of Imaging Science). Upon acceptance, cross
% references are placed between both articles. The environment
% ipolSIIMS is used to set the standard header, before the
% abstract. Uncoment these lines if you prepare an IPOL+SIIMS article:

%\begin{ipolSIIMS}
%This IPOL article is related to a companion publication in the SIAM
%Journal on Imaging Sciences:\\
%Author Names, ``Article Title.''
%\textsl{SIAM Journal on Imaging Sciences}, vol.~X, no.~X,
%pp.~N--M, YYYY. \url{http://dx.doi.org/10.1137/XXXXXXXXX}
%\end{ipolSIIMS}

%------------------------------------------------------------------------------
% The abstract of an IPOL article must be informative and summarize all
% important parts of the article.

\begin{ipolAbstract}
Study of several variants of the DCT denoising algorithm. Some of them attain the quality of Non-Local Bayes at a tenth of the cost. On line demo available at the address: \url{http://dev.ipol.im/~facciolo/ipol_demo/dct2step}.
\end{ipolAbstract}

%------------------------------------------------------------------------------
% Use the source code info to briefly explain what can be found as
% software code in the IPOL article.
% Do not use the phrasing "...the IPOL web part of this article."

\begin{ipolCode}
The source code section briefly explains what the source code
published with the article contains, all in a single paragraph. For
example: The reviewed source code and documentation for this algorithm
are available from \href{\ipolLink}{the web page of this
  article}. Compilation and usage instruction are included in the
\verb|README.txt| file of the archive.
\end{ipolCode}

%------------------------------------------------------------------------------
% Use the supplementary files info to add explanations about other
% files published with the article.

\begin{ipolSupp}
The supplementary files section provides explanations about other
files published with the article, all in a single paragraph. Mention
clearly if they are reviewed or not. For example: A reference dataset,
to be used for further comparisons, is provided with the article and
peer-reviewed. A Matlab interface (not reviewed) is also available for
convenience.
\end{ipolSupp}

%------------------------------------------------------------------------------
% All papers need key words. Key words are lowercase except for proper
% names and acronyms, and separated with commas. Only use plain text.

\ipolKeywords{first, second, third, fourth}

%------------------------------------------------------------------------------
% Article content starts here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Basic 2 step DCT denoising}
The simplest DCT denosing algorithm as described by Yu and Sapiro in \cite{dct2011} consists in a threshold of a patch-wise DCT of the image and aggregation of the resulting patches. Color images are first pre-processed with to de-correlate the input colors. Algorithm \ref{alg:dct} summarized it. Unlike the implementation of Yu and Sapiro the algorithm below  only uses a small amount of memory to process the image, as the extraction and processing of each patch is performed in a single loop, which can also be parallelized. Moreover, using the FFTW library to compute the DCT transforms further accelerates the processing.

Let us note that although thresholding the DCT of a single patch introduces ringing artifacts, the patch-wise aggregation limits them in the final result.

A guide image is a clean but not completely restored result, which could be used to determine the power spectrum of underlying signal. Algorithm \ref{alg:dct2} shows how to use a guide image as an oracle for a Wiener filter.
The two-step DCT denoising is then summarized in algorithm \ref{alg:2stepdct}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Iterated DCT denoising}

Following the previous argument one should continue applying the Wiener step on using the previous result as guide (as in algorithm \ref{alg:iterated}). In table \ref{tab:compare} we see a consistent improvement with respect to the basic 2-step result. 
In figures \ref{fig:res4}, \ref{fig:res8}, and \ref{fig:res16} we can compare the results obtained with different windows sizes.
In general the results get sharper with iterations, but in the process some artifacts are also amplified.

\begin{algorithm}
\DontPrintSemicolon
\Input{Noisy image $Y$, noise level $\sigma$, block size $s$}
\Output{Denoised image $X$}

$G \gets  \text{DCTdenoisingHard}(Y,\sigma, s)$\;

$X \gets  \text{DCTdenoisingWiener}(Y,G,\sigma, s)$\;

\caption{two-step DCT Denoising}
\label{alg:2stepdct}

\end{algorithm}

\begin{algorithm}
\DontPrintSemicolon
\Input{Noisy image $Y$, noise level $\sigma$, block size $s$}
\Output{Denoised image $X$}

$G \gets  \text{DCTdenoisingHard}(Y,\sigma, s)$\;

\For{$iter \gets 1 \ldots 10$ } {
$X \gets  \text{DCTdenoisingWiener}(Y,G,\sigma, s)$\;
$G \gets X$\;
}
\caption{Iterated DCT Denoising}
\label{alg:iterated}

\end{algorithm}

\begin{algorithm}
\DontPrintSemicolon
\Input{Noisy image $Y$, noise level $\sigma$, block size $s$}
\Output{Denoised image $X$}

$X, W \gets  0$\;

$Y \gets   \text{DecorrelateColors}(Y)$\;
\For{$patch \in \Omega$}{
	$ \widehat{b} \gets  \text{DCT}(\text{ExtractPatch}(Y, patch, s))$\;
    \For{$\omega \in supp(\widehat{b})$}{

    	\If{$|\widehat{b}(\omega)|^2 < 3\sigma^2$}{
        	$\widehat{b}(\omega) \gets  0$\;
        }
    }
	$ {b} \gets  \text{IDCT}(\widehat{b})$\;
    $X(\Omega_{patch}) \gets  b $\;
    $W(\Omega_{patch}) \gets  W(\Omega_{patch}) +1 $\;

}

    $ X \gets  X / W$ \;
	$X \gets   \text{UndoDecorrelateColors}(X)$\;

\caption{DCT Denoising - Hard thresholding}

\label{alg:dct}

\end{algorithm}

\begin{algorithm}
\DontPrintSemicolon
\Input{Noisy image $Y$, guide $G$, noise level $\sigma$, block size $s$}
\Output{Denoised image $X$}

$X, W \gets  0$\;

$Y \gets  \text{DecorrelateColors}(Y)$\;
$G \gets  \text{DecorrelateColors}(G)$\;

\For{$patch \in \Omega$}{

	$ \widehat{b} \gets  \text{DCT}(\text{ExtractPatch}(Y, patch, s))$\;
  	$ \widehat{g} \gets  \text{DCT}(\text{ExtractPatch}(G, patch, s))$\;

    \For{$\omega \in supp(\widehat{b})$}{
    	$ \widehat{b}(\omega) \gets   \widehat{b}(\omega) \left({\displaystyle \frac{|\widehat{g}(\omega)|^2 }{|\widehat{g}(\omega)|^2 +\sigma^2}}\right)$
    }
	$ {b} \gets  \text{IDCT}(\widehat{b})$\;
    $X(\Omega_{patch}) \gets  b $\;
    $W(\Omega_{patch}) \gets  W(\Omega_{patch}) +1 $\;

}

    $ X \gets  X / W$ \;
	$X \gets  \text{UndoDecorrelateColors}(X)$\;

\caption{DCT Denoising - Wiener}

\label{alg:dct2}

\end{algorithm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multiscale DCT denoising}

The multiscale DCT denoising uses Nicola Pierazzo's multiscaler algorithm for cutting and recomposing the results computed at different scales \cite{multiscaler2016}. Both the causal and non-causal multiscale algorithms produce similar results (we show the causal). 
We observe in table \ref{tab:compare} that only for small patch sizes the result improves with respect to the 2-step single-scale DCT denoising. The results with multiscale shown in figures \ref{fig:res4}, \ref{fig:res8}, and \ref{fig:res16} are smoother than their single scales counterparts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Iterated, guided multiscale DCT denoising}

We tested the iterated multiscale algorithm described in algorithm \ref{alg:itermulti}. The iterations are applied on the complete non-causal multiscale algorithm, using the result of the previous iteration as guide. The results are reported in table \ref{tab:compare}.

\begin{algorithm}[h!]
\caption{Iterated guided multiscale DCT Denoising}
\label{alg:itermulti}
\Input{Noisy image $Y$,  noise level $\sigma$, block size $s$, and $n_{scales}$}
\Output{Denoised image $combined$}

     $G \gets \text{DCTdenoising2step}(Y,  \sigma, 8)$ \hfill  \tcc{Bootstrap iterations with a good guide (block\_sz=8)}

  \For{$iter \gets 1 \ldots 10$}{

  $combined \gets$ NULL \hfill \tcc{{Non-causal multiscale}}
  \For{$scale \gets n_{scales} - 1, \ldots, 0$}{
     $Y_s \gets\text{ExtractScale}(Y,  scale)$\;
     $G_s \gets\text{ExtractScale}(G,  scale)$\;
     $X_s \gets\text{DCTdenoisingWiener}(Y_s, G_s, \sigma, s)$\;

   $combined \gets \text{MergeCoarse}(X_s, combined)$\;

  }
  $G\gets combined $  \hfill \tcc{Update guide}
  }

\end{algorithm}

The best results are obtained with $4\times 4$ windows, improving on the results of multiscale DCT, and iterated DCT  by 0.1 dB.
Note that the best result of iterated DCT is obtained with windows of $16\times 16$ ( 16 times slower than $4\times 4$), thus algorithm \ref{alg:itermulti} is also cheaper. Figure \ref{fig:psnr_iter} shows the evolution of the PSNR with the iterations.

The results are noticeably sharper than the ones of DCT denoising but also have several small artifacts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Postprocess with DA3D}

The DA3D post-process \cite{Pierazzo2015} uses a guide image to produce an improved denoised result. In the last section of table \ref{tab:compare} are compared the PSNRs of various  post-processed results obtained with DA3D, concretely including NL-Bayes \cite{Lebrun2013}, NL-Bayes Multiscale and several Multiscale DCT denoising.

Note that the results obtained using DCT denoising guides improve substantially in terms of PSNR, the results are comparable to those of NL-Bayes. This is because da3d suppresses most of the artifacts of DCT denoising as seen in figure \ref{fig:da3d}. 
In particular the result of \emph{"dct4 multi4 + da3d"} exhibits very little residual ringing.

In terms of efficiency the difference is substantial. For the  1.3MP image shown in figure \ref{fig:da3d} the computation (on a 4-cores computer) of \emph{"dct4 multi4 + da3d"} takes 30 seconds, while \emph{"NL-Bayes multi3 + da3d"} takes 5 minutes 10 seconds (ten times slower!).

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = .9\textwidth]{f/graphPSNR_dct4_multi_iter} 
\caption{{\bf PSNR evolution} for iterated guided multiscale DCT denoising ($w=4$), starting from DCT 2-step ($w=8$).}
\label{fig:psnr_iter}
\end{center}
\end{figure}

\begin{table}%[h!]
\caption{Results obtained on the image \emph{Sans\_bruit\_1} with noise $\sigma =50$. }
\begin{center}
\begin{tabular}{l|c}
\bf Algo & \bf PSNR \\
\hline
NL-Bayes & 28.194\\
NL-Bayes multi3& 28.305\\

\hline
\hline

dct4 1step& 24.897 \\ 
dct4 2step& 25.312 \\
dct4 iter10& 25.505 \\
% ./dctdenoising_multiscale.sh  $n $s rr.tif "-w 4" 4; imgerr PSNR $o rr.tif;
dct4 multi4 &  27.747\\

\hline
dct8 1step& 26.917 \\ 
dct8 2step& 27.294 \\
dct8 iter10& 27.471 \\
dct8 multi4 &  27.779\\

\hline
dct16 1step& 27.329 \\
%./dctdenoising -w 16 $n $s rr.tif; imgerr PSNR $o rr.tif; iion rr.tif dct16_2step.png;     for i in `seq 1 10`; do ./dctdenoising -w 16 $n $s -2 rr.tif rr.tif; imgerr PSNR $o rr.tif; done; iion rr.tif dct16_iter10.png 
dct16 2step& 27.680 \\
dct16 iter10& 27.840 \\
dct16 multi4 &  27.483\\

\hline
\hline
dct4 multi4 iter10& 27.878 \\
dct8 multi4 iter10& 27.993 \\

\hline
\hline
NL-Bayes + da3d & 28.485\\
NL-Bayes multi3 + da3d & 28.624\\
dct4 multi4 + da3d &  28.374\\
dct8 multi4 + da3d &  28.355\\
dct16 multi4 + da3d &  28.206\\
dct4 multi4 iter10 + da3d& 28.503 \\
dct8 multi4 iter10 + da3d& 28.515 \\
\end{tabular}
\end{center}
\label{tab:compare}
\end{table}%

%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htbp]
\begin{center}
\begin{tabular}{cc}

\includegraphics[width = .44\textwidth]{f/dct4_1step} &
\includegraphics[width = .44\textwidth]{f/dct4_2step} \\
dct4 1step (24.897) & dct4 2step (25.312) \\
\includegraphics[width = .44\textwidth]{f/dct4_iter10} &
\includegraphics[width = .44\textwidth]{f/dct4_multi4} \\
dct4 iter10 (25.505) &  dct4 multi4 (27.747)\\

\end{tabular}
\caption{{\bf results} of algorithms \ref{alg:dct}, \ref{alg:2stepdct},  \ref{alg:iterated}, and Pierazzo's multiscale DCT \cite{multiscaler2016},  all using  $4 \times 4$ windows.}
\label{fig:res4}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\begin{tabular}{cc}

\includegraphics[width = .44\textwidth]{f/dct8_1step} &
\includegraphics[width = .44\textwidth]{f/dct8_2step} \\
dct8 1step (26.917) & dct8 2step (27.294) \\
\includegraphics[width = .44\textwidth]{f/dct8_iter10} &
\includegraphics[width = .44\textwidth]{f/dct8_multi4} \\
dct8 iter10 (27.471) &  dct8 multi4 (27.779)\\

\end{tabular}
\caption{{\bf results} of algorithms \ref{alg:dct}, \ref{alg:2stepdct},  \ref{alg:iterated}, and Pierazzo's multiscale DCT \cite{multiscaler2016},  all using  $8 \times 8$ windows.}
\label{fig:res8}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\begin{tabular}{cc}

\includegraphics[width = .44\textwidth]{f/dct16_1step} &
\includegraphics[width = .44\textwidth]{f/dct16_2step} \\
dct16 1step (27.329) & dct16 2step (27.680) \\
\includegraphics[width = .44\textwidth]{f/dct16_iter10} &
\includegraphics[width = .44\textwidth]{f/dct16_multi4} \\
dct16 iter10 (27.840) &  dct16 multi4 (27.483)\\

\end{tabular}
\caption{{\bf results} of algorithms \ref{alg:dct}, \ref{alg:2stepdct},  \ref{alg:iterated}, and Pierazzo's multiscale DCT \cite{multiscaler2016},  all using  $16 \times 16$ windows.}
\label{fig:res16}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
\begin{center}
\begin{tabular}{cc}

\includegraphics[width = .44\textwidth]{f/orig} &
\includegraphics[width = .44\textwidth]{f/noisy} \\
original noiseless  & nosiy ($\sigma=50$) \\

\includegraphics[width = .44\textwidth]{f/nlb} &
\includegraphics[width = .44\textwidth]{f/nlb_multi3} \\
 NL-Bayes (28.194) &  NL-Bayes multi3 (28.305)  \\

\includegraphics[width = .44\textwidth]{f/dct4_multi4_iter10}&
\includegraphics[width = .44\textwidth]{f/dct8_multi4_iter10}\\
dct4 multi4 iter10 (27.878) &  dct8 multi4 iter10 (27.993) \\

\end{tabular}
\caption{{\bf results} of NL-Bayes \cite{multiscaler2016} and algorithm \ref{alg:itermulti} for two window sizes}
\label{fig:itermulti}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
\begin{center}
\begin{tabular}{cc}

\includegraphics[width = .44\textwidth]{f/nlb_da3d} &
\includegraphics[width = .44\textwidth]{f/nlb_multi3_da3d} \\
NL-Bayes+ da3d (28.485)    & NL-Bayes multi3 + da3d (28.624)  \\

\includegraphics[width = .44\textwidth]{f/dct4_multi4_da3d} &
\includegraphics[width = .44\textwidth]{f/dct8_multi4_da3d} \\
dct4 multi4 + da3d (28.374) &  dct8 multi4 + da3d (28.355)  \\

\includegraphics[width = .44\textwidth]{f/dct4_multi4_iter10_da3d}&
\includegraphics[width = .44\textwidth]{f/dct8_multi4_iter10_da3d}\\
dct4 multi4 iter10 + da3d (28.503) &  dct8 multi4 iter10  + da3d (28.515) \\

\end{tabular}
\caption{{\bf results} post-processed with DA3D \cite{Pierazzo2015}.}
\label{fig:da3d}
\end{center}
\end{figure}

\newpage

\section{RAW results and script calls (don't look, incorrect PSNRs)}

Using Dice, with noise $\sigma=40$

\begin{enumerate}
\item NLB single scale: 36.4 dB
\item NLB multiscale: 35.25 dB
\item DCT denoising Wiener-step using GT as guide (w=16/w=8): 36.49/34.55 dB
\item DCT denoising 2-step (w=16/w=8): 34.06/31.73 dB
\item iterated DCT denoising 2-step, 10 iterations, using DCT 2-step as initial point, (w=16/w=8/w=4): 24.88/24.74/24.01 dB
\item

\end{enumerate}

\begin{verbatim}

 1294  ./dctdenoising.ok ../diceN.tif -w 16 40 -2 ../dice.png ref16.tif; imgerr PSNR ../dice.png ref16.tif 
 1295  ./dctdenoising.ok ../diceN.tif -w 8 40 -2 ../dice.png ref8.tif; imgerr PSNR ../dice.png ref8.tif

 1299  ./dctdenoising.ok ../diceN.tif -w 16 40 dct16.tif; imgerr PSNR ../dice.png dct16.tif 
 1300  ./dctdenoising.ok ../diceN.tif -w 8 40 dct8.tif; imgerr PSNR ../dice.png dct8.tif

 1301  cp dct16.tif rr.tif; for i in `seq 1 10`; do  ./dctdenoising ../diceN.tif -w 16 40 -2  rr.tif rr.tif; imgerr PSNR ../dice.png rr.tif;   done; cp rr.tif rr16.tiff

 1302  cp dct8.tif rr.tif; for i in `seq 1 10`; do  ./dctdenoising ../diceN.tif -w 8 40 -2  rr.tif rr.tif; imgerr PSNR ../dice.png rr.tif;   done; cp rr.tif rr8.tiff

 1314  ./dctdenoising_multiscale.sh ../diceN.tif 40 /tmp/dm4.tif  "-w 4 " 4; imgerr PSNR ../dice.png /tmp/dm4.tif
 1316  ./dctdenoising_multiscale.sh ../diceN.tif 40 /tmp/dm8.tif  "-w 8 " 4; imgerr PSNR ../dice.png /tmp/dm8.tif
 1317  ./dctdenoising_multiscale.sh ../diceN.tif 40 /tmp/dm16.tif  "-w 16 " 4; imgerr PSNR ../dice.png /tmp/dm16.tif

w=4
s=50
../b/dctdenoising -w 8 $n $s rr.tif; 
for i in `seq 1 10`; do
	../multi/dctdenoising_multiscale_guided.sh $n rr.tif $s /tmp/t.tif "-w ${w}" 5; 
	imgerr PSNR /tmp/t.tif $o; 
	cp /tmp/t.tif rr.tif; 
done
cp rr.tif /tmp/xm_guided4_dct8.tif

\end{verbatim}

\section{Non-local DCT denoising}

We explore in the following a non-local version of the block DCT denoising
algorithm. This approach is complementary to the multiscale approach and both 
could be combined together.

The idea of the non-local DCT algorithm is to group together similar patches.
This is mainly motivated by two reasons:
\begin{itemize}
	\item A group of similar patches could be centered before denoinsing using
		DCT shrinkage. With the center removed, we expect to alleviate the problem
		of ringing around contrasted image edges. A contrasted edge should dominate the
		patch distance and therefore would be present in all patches in the
		group. If the group's baricenter captures the edge, it will be removed from the
		centered patches. In practice, the patches in the group might be slightly shifted.
		The mean patch would then be a smoothed version of the edge, which means that
		the centered patches will have some high frequency components due to the edge residual.
	\item The group of similar patches provides more reliable estimates of the signal 
		statistics. This is useful for estimating the optimal shrinkage functions from the 
		patches in the group.
\end{itemize}

We focus on two-step approaches such as the ones outlined in Algorithms 
\ref{alg:2step_nldct}, \ref{alg:nldct1} and \ref{alg:nldct1}. Both steps
follow the same scheme. For each patch $p$, the $n$ nearest neighbors are 
searched for in a search window centered at $p$. The resulting group of
patches is filtered by a DCT shrinkage operator. The filtered patches are 
aggregated on the denoised image estimate. The second step uses the output
of the first step to determine the $n$ nearest neighbors and to guide the 
DCT shrinkage. In the following we will describe different options to use as
shrinkage operators.

\begin{algorithm}
\DontPrintSemicolon
\Input{Noisy image $Y$, noise level $\sigma$, block size $s$}
\Output{Denoised image $X$}
$G \gets  \text{NLDCT-Shrinkage}(Y,\sigma, s)$\;
$X \gets  \text{NLDCT-GuidedShrinkage}(Y,G,\sigma, s)$\;
\caption{Two-step NL-DCT Denoising}
\label{alg:2step_nldct}
\end{algorithm}

\begin{algorithm}
\DontPrintSemicolon
\Input{Noisy image $Y$, noise level $\sigma$, block size $s$, search radius $w$, number of NN $n$}
\Output{Denoised image $X$}
$X, W \gets  0$\;
$Y \gets   \text{DecorrelateColors}(Y)$\;
\For{$p \in \Omega$}{
	$\mathcal I \gets \text{SearchNearestNeighbors}(G,p,s,w,n)$\;
	$\mathcal P \gets \text{ExtractPatches}(Y,\mathcal I,s)$\;
	$\widehat{\mathcal P} \gets  \text{DCTGuidedShrinkGroup}(\mathcal P)$\;
	$X\gets \text{AggregatePatchesInGroup}(X, \mathcal I, \widehat{\mathcal P})$\;
	$W\gets \text{AggregateWeightsInGroup}(W, \mathcal I)$\;
}
$ X \gets  X / W$ \;
$X \gets   \text{UndoDecorrelateColors}(X)$\;
\caption{NL-DCT shrinkage}
\label{alg:nldct1}
\end{algorithm}

\begin{algorithm}
\DontPrintSemicolon
\Input{Noisy image $Y$, guide $G$, noise level $\sigma$, block size $s$, search radius $w$, number of NN $n$}
\Output{Denoised image $X$}
$X, W \gets  0$\;
$Y \gets   \text{DecorrelateColors}(Y)$\;
$G \gets   \text{DecorrelateColors}(G)$\;
\For{$p \in \Omega$}{
	$\mathcal I \gets \text{SearchNearestNeighbors}(G,p,s,w,n)$\;
	$\mathcal P \gets \text{ExtractPatches}(Y,\mathcal I,s)$\;
	$\mathcal G \gets \text{ExtractPatches}(G,\mathcal I,s)$\;
	$\widehat{\mathcal P} \gets  \text{DCTGuidedShrinkGroup}(\mathcal P,\mathcal G)$\;
	$X\gets \text{AggregatePatchesInGroup}(X, \mathcal I, \widehat{\mathcal P})$\;
	$W\gets \text{AggregateWeightsInGroup}(W, \mathcal I)$\;
}
$ X \gets  X / W$ \;
$X \gets   \text{UndoDecorrelateColors}(X)$\;
\caption{NL-DCT guided shrinkage}
\label{alg:nldct2}
\end{algorithm}

\subsection{Bayesian shrinkage operators for unitary transforms}

Most common shrinkage operators can be given a Bayesian interpretation with a
prior in the family of \emph{generalized Gaussian distributions}. This is often 
desirable since the Bayesian setting provides principled ways to set the parameters
given estimates of the signal statistics.
The following discussion was adapted from \cite{Moulin1999} and \cite{Elad2006shrinkage}.

We consider a signal $\ma p\in\mathbb R^d$ that we want to estimate from a
noisy observation $\ma q = \ma p + \ma n$, where $\ma n \sim \mathcal
N(0,\sigma I)$ is AWGN. In our setting the signal is typically a patch
extracted from a larger image. We will estimate $\ma p$ by assuming a suitable
prior distribution $\mathbb P(\ma p)$ and computing the MAP:
\[\hat{\ma p} = \argmin \frac1{2\sigma^2}\|\ma p - \ma q\|^2 - \ln \mathbb P(\ma p).\]

We consider priors in the following family of generalized Gaussian distributions:
\begin{equation}
	\mathbb P(\ma p\,|\,\bar{\ma p}, \Lambda, U, \nu) = 
	\left(\frac{\nu\eta(\nu)}{2\Gamma(1/\nu)}\right)^d\frac1{|\Lambda|^{1/2}}
	\exp\left(-\|\eta(\nu)\Lambda^{-1/2}U^T(\ma p - \bar{\ma p}) \|_{\nu}^\nu\right),
	\label{eeq:ggd-family}
\end{equation}
where $\Gamma$ is the gamma function, 
$U$ is an orthogonal matrix,
$\Lambda = \text{Diag}(\lambda_1,\lambda_2,\dots,\lambda_d)$ is a positive
definite diagonal matrix, $\|\,\cdot\,\|_\nu$ is the $\nu$-norm in $\mathbb
R^d$ for $\nu > 0$, 
$\eta(\nu) = \Gamma(3/\nu)^{1/2}\Gamma(1/\nu)^{-1/2}$
is a normalization factor, 
and $\bar{\ma p}$ is the mean of the distribution.  The
parameter $\nu$ is called the \emph{shape parameter}. With $\nu = 2$
recover the Gaussian distribution with covariance matrix $\Sigma = U\Lambda U^T$.
This allows us to interpret the $U$ as the orthonormal basis of principal
directions and $\lambda_i$ as analog to the variance along principal direction $\ma u_i$.

Decreasing the value of $\nu$ has the effect of 
increasing the tails and the probability of values close to the mean. When
$\nu \leqslant 1$, it can be shown that the resulting MAP favours sparse
solutions. A common choice in the wavelet denoising literature is to set $\nu = 1$, 
the \emph{Laplace distribution}. This follows from the observation that the
statistics of wavelet coefficients in natural images follows a GGD-like
distribution with shape parameter $\nu \leqslant 1$, and the Laplace
distribution is attractive for its computational simplicity.

This multivariate GGD can be factorized 
as the product of one dimensional GGDs along the principal directions.%
\footnote{There are other definitions of the multivariate GGD for which this
factorization does not hold. In particular, the multivariate GGD can be defined using the
$2$-norm instead of the $\nu$-norm. In this case, $\mathbb P(\ma
p\,|\,\bar{\ma p}, \Sigma,\nu) \propto \exp\left(-\frac12\|\Sigma^{-1/2}(\ma p
- \bar{\ma p}) \|_2^{2\nu}\right)$. When $\nu = 2$ the Gaussian distribution is recovered. Except in this case,
this PDF cannot be written as a product of 1D GGD. 
This definition maintains the level sets of the Gaussian distribution: ellipses
centered at $\bar{\ma p}$.  The definition given above with the $\nu$-norm
given above is anisotropic and depends on the choice of the
coordinate system.}
Define the principal components as $\ma \alpha = U^T(\ma p - \bar{\ma p})$. Then
\begin{equation}
	\mathbb P(\ma p\,|\,\bar{\ma p}, \Lambda, U, \nu) = \prod_{i =1}^d
	\frac{\nu\eta(\nu)}{2\Gamma(1/\nu)}\frac1{\lambda_i^{1/2}}
	\exp\left(-\left(\frac{\eta(\nu)|\alpha_i - \bar{\alpha}_i|}{\lambda_i^{1/2}}\right)^{\nu} \right).
	\label{eeq:ggd-family-factorized}
\end{equation}
Each principal component is therefore independent from the others.

\subsubsection{Inference}

The independent of components
greatly simplifies the computation of the MAP, which is decomposed into $d$
one-dimensional optimization problems%
\footnote{Note that the MAP is separable only if the noise PDF is a function of
the 2-norm $\|\ma p - \ma q\|$.}.
Indeed, since $\|\ma p - \ma q\| = \|\ma \alpha - \ma \beta\|$, for $\ma \beta =
U^T\ma q$, we can express the MAP as follows
\[\hat{\ma \alpha} = \argmin \sum_{i = 1}^d\frac1{2\sigma^2} (\alpha_i -
\beta_i)^2 + \frac{\nu(\eta)^{\nu}}{\lambda_i^{\nu/2}}{|\alpha_i - \bar{\alpha}_i|^\nu}.\]

Let us now focus on the solution of the $i$-th principal component. We will
redefine $\ma \alpha$ and $\ma \beta$ as the centered variables $\ma \alpha -
\bar{\ma \alpha}$ and $\ma \beta - \bar{\ma \alpha}$. Then we have
\[\hat \alpha_i = \argmin \frac1{2\sigma^2} (\alpha_i -
\beta_i)^2 + \frac{\nu(\eta)^{\nu}}{\lambda_i^{\nu/2}}{|\alpha_i - \bar{\alpha}_i|^\nu}.\]
If $\nu \leqslant 1$ this function is non-differentiable at $\alpha_i = 0$.
The minimizer can be located in $\alpha_i = 0$ or in the zeros of its derivative: 
\[\beta_i = \alpha_i + \frac{\nu\eta(\nu)^{\nu}\sigma^2}{\lambda_i^{\nu/2}}|\alpha_i|^{\nu-1}.\]

We will distinguish three cases: $\nu = 2$, $\nu = 1$ and $\nu \to 0$. The case $\nu = 2$
corresponds to the Wiener filter. When $\nu = 1$, we can express the solution
with a soft-thresholding operator:
\[\hat\alpha_i = \left\{
\begin{array}{l l}
	0,& \displaystyle\text{if }|\beta_i| < \sqrt{2} \sigma^2{\lambda_i^{-1/2}},\\
	\displaystyle\beta_i - \sqrt{2} \sigma^2{\lambda_i^{-1/2}}\text{sign}(\beta_i),&\text{else.}
\end{array}
\right.\]

When $\nu\to 0$, \cite{Moulin1999} showed that the solution converges can be
obtained as the following hard-thresholding operator:
\[\hat\alpha_i = \left\{
\begin{array}{l l}
	0,& \displaystyle\text{if }|\beta_i| < \tau_\nu,\\
	\displaystyle\beta_i,&\text{else,}
\end{array}
\right.\]
with $\tau_\nu = \sigma/\nu^{1/2}\cdot\sqrt{6\sqrt{3}/e}$. Note that in this limit
case the threshold grows to infinity as $\nu$ approaches $0$. Since it does
not depend on the variance $\lambda_i$, this result can be interpreted as a
Bayesian justification for the common practice of hard thresholding all
components with the same threshold value.

\subsubsection{Parameter estimation}

We will assume that $U, \nu$ and $\sigma$ are known. In this work $U$ corresponds
to the DCT basis and $\nu$ is a parameter of the algorithm.
%
We wish to estimate the parameters of the a priori distribution
from the observed noisy data or from a oracle image. For $\nu = 2$ (Gaussian
prior) one can use in both cases closed form formulas for the \emph{maximum
likelihood estimators} (MLE). For the $\nu = 1$ (the Laplace distribution)
the MLE can be expressed in closed form only in the case in which the available 
data is clean. Assume that we available $n$ samples from the Laplace distribution
$\alpha_{j1}, \alpha_{j2},\dots,\alpha_{jn}$. The MLE are given by:
\begin{equation}
	\hat{\bar \alpha}_i = \text{median}(\alpha_{1i}, \alpha_{2i},\dots,\alpha_{ni}),\quad\quad
	\hat \lambda_i = 2 \left(\frac1n\sum_{j = 1}^n |\alpha_{ji} - \hat{\bar \alpha}_i|\right)^2.
	\label{eeq:mle_laplace}
\end{equation}

When the available data is noisy $\beta_{1i},\beta_{2i}, \dots, \beta_{ni}$, one
can estimate the variance via the sample variance since $\mathbb V(\beta_i) =
\lambda_i + \sigma^2$. Thus
\[\hat{\lambda}_i = \frac1n\sum_{i = 1}^n (\beta_{ij} - \hat{\bar \beta}_i)^2 - \sigma^2.\]
An additional approach is to mimic the MLE estimator for the noisy data:
\[\hat \lambda_i = 2\left(\frac1n\sum_{j = 1}^n|\beta_{ji} -
\hat{\bar \beta}_i|\right)^2 - \sigma^2.\]
\textcolor{red}{This needs a theoretical justification! In practice it works.}
The mean $\hat{\bar \beta}_i$ can be estimated either through the sample mean or the
median.
\textcolor{red}{TODO: it would be nice to know if one way is better than the other.
Essentially, the Laplace distribution can generate ``outliers'' because of its heavy tail
that can affect estimators based on sample averages. For this reason,
estimators based on median and absolute values are preferred, specially if the signals variance
$\lambda_i$ is high.}

\subsection{Group sparsity}

Another criterion suitable for non-local DCT denoising is to consider a joint PDF for 
the set of similar patches. In this scenario, individual patches in the set are not 
consider independent. Using suitable norms in $\mathbb R^{d\times n}$, one could for
example assume that all patches share the same sparsity pattern. This could be accomplished
with a GGD with the following norm:
\[\|\ma A\|_{p,q} = 
	\left(\sum_{i = 1}^d\left(\sum_{j = 1}^n \alpha_{ij}^q\right)^{p/q}\right)^{1/p}.
\]
Here $\ma A$ denotes the stack of the components of then $n$ patches in the
group. \textcolor{red}{It might be interesting to look into this in more detail.
Probably the MAP computation does not allow for a closed form expression and
a .}

\subsection{Other approaches}

We can try other approaches that do not fall under the previous Bayesian setting.
\textcolor{red}{They might be Bayesian still with a prior in a different family of
distribtions.}

\paragraph{Soft thresholding with universal threshold.} In his classic paper
Donoho and Johnstone \cite{Donoho1994} they propose to use hard and soft
wavelet thresholding with a universal threshold, dependent on the noise variance,
but independent of the signal. They show that when the dimensionality of the signal 
grows to infinity, the asymptotic approximation error of these methods, in the 
minimax sense had a nearly optimal decay rate. It was noted that the proposed
thresholds were too aggressive and provided oversmoothed estimates. Under a Bayesian 
perspective, in \cite{Moulin1999} showed that the universal threshold corresponded to
a very pessimistic assumption about the signal-to-noise ratio. In practice,
we will perform tests with soft and hard thresholds independent of the signal variance.

The threshold will be set proportional to the noise variance:
\[\hat\alpha_i = \left\{
\begin{array}{l l}
	0,& \displaystyle\text{if }\beta_i^2 < (\gamma\sigma)^2,\\
	\displaystyle\beta_i - (\gamma\sigma)^2\text{sign}(\beta_i),&\text{else.}
\end{array}
\right.\]
Recall that $\alpha_i$ and $\beta_i$ refer to the centered coefficients.

\paragraph{Linear shrinkage filters.} A cheap way to force group sparsity
\textcolor{red}{(is it heuristic or does it have some theoretical
justification?)} is to define a linear shrinkage filters by thresholding
the coefficient sample variances, instead of their individual values.
We will introduce the following notation for the signals empirical variance:
\[\hat \sigma_{\beta,i}^2 = \frac1n\sum_{i=1}^n\beta_i^2.\]
%
For instance, we can apply the following linear hard thresholding filter:
\[\hat\alpha_i = \left\{
\begin{array}{l l}
	0,& \displaystyle\text{if }\hat\sigma_{\beta,i} < \gamma\sigma,\\
	\beta_i,&\text{else.}
\end{array}
\right.\]
Analogously, we could define the linear soft-thresholding filter:
\[\hat\alpha_i = 
	\left\{
\begin{array}{l l}
	0,& \displaystyle\text{if }\hat\sigma_{\beta,i} < \gamma\sigma,\\
	\beta_i\left(\displaystyle1 - \gamma^2\frac{\sigma^2}{\hat\sigma_{\beta,i}^2}\right),&\text{else.}
\end{array}
\right.\]
This corresponds to a thresholded Wiener filter. The coefficient in 
the above equation comes from applying to the $\beta_i$ the same shrinkage ratio
that a soft thresholding operator would cause on $\hat \sigma_{\beta,i}^2$.
\textcolor{red}{We could also apply the soft-thresholding
operator on the standard deviation instead of the variance, which would
yield an expression without the squares.}

\subsection{Other alternatives}

\paragraph{Zero mean prior.}
Before computing the MAP estimate of a noisy patch, the parameters of the \emph{a
priori} distribution must be estimated from the data. Depending on the number of 
data available, the complexity of the model than can be effectively learnt. In this
sense, non-local methods have a clear advantage over local methods, since they 
can use a population of patches. Local methods only have available the $d$ transformed 
coefficients of the noisy patch $\ma \beta$. This data is insufficient to fit 
a mean $\bar {\ma \alpha}$ and the variances $\Lambda$ ($2d$ coefficients).
As a consequence they assume that the prior distribution to have zero mean, and 
estimate the variances as $\hat \lambda_i = \max(\beta_i^2 - \sigma^2,0)$.

Non-local methods have enough patches to estimate both mean and variances. Indeed
empirical results show that non-local methods assuming a zero mean perform worse.

\paragraph{Estimating the mean patch in the 2nd stage.}
On the second step, we can center using the sample average of the basic estimate,
or that of the noisy image, as in the IPOL implementation of NL-Bayes. In our
experiments, best results are obtained using the basic estimate. The reason might be that
in the second step, the number of patches that yields best results is very
small (around 10 or less patches).

\paragraph{Estimating the variances in the 2nd stage.} A similar question can be 
asked regarding the estimation of the variances in the second step: should we use
the basic estimate or the noisy data? As with the
estimation of mean patch, we found that the performance drops significantly when 
using the noisy patches. However, we should note that related approaches for 
video denoising iterate patch-based Wiener filtering with variances computed 
from the noisy data \cite{LiZhangDai2011}.

\subsection{Results with NL-DCT algorithms}

In this section we compare some of the variants discussed above. We first 
perform tests changing the first step method, while keeping fixed the second
step. Once we determine the best option for the first step, we test different 
second step alternatives.

For each step we need to set the following parameters: the patch size $s$, the
search size $w$, the number of patches $n$ and the shrinkage 
strength $\gamma$. The latter controls the shrinkage by amplifying or
attenuated the noise level $\gamma\sigma$.

In all experiments shown in this section we will show PSNR curves varying $n_1$,
$n_2$ and either $\gamma_1$ for the first step tests or $\gamma_2$ for the
second step tests. 
We use patches of size $8\times 8$ and
search regions of size $21\times 21$ pixels. This parameters have a significant
effect on the performance. Once we determine the estimation method for each stage, 
we will explore changing these parameters.

\subsubsection{The noise correction factor $\gamma$ in the first step}

For some of the following experiments, we will show results varying a parameter
$\gamma$ that controls the denoising strength. To achieve this, we implement
the shrinkage formulae with an observation noise level $\gamma\sigma$. A higher value
of $\gamma$ causes a more aggressive denoising. In threshold based methods, $\gamma$ 
can be used to control the threshold value.

In the first step, the noise variance $\sigma^2$ is used not only in the shrinkage 
formulae, but also to estimate the signal variance. The correction factor $\gamma$ could be
considered here here as well. This causes an additional effect: increasing the
value of $\gamma$, decreases also the estimated signal variance, causing a more
pronounced effect in the denoising strength.

In Figure \ref{fig:wie1_gmap-vs-gall} we compare the results obtained using both approaches with the
Wiener filter in both steps. We consider two cases: thresholding or allowing
negative weights in the first step. We use the following names to refer to the methods:
\begin{center}
\begin{tabular}{c l}
	\verb+pos-gmap+ & First step Wiener; weight thresholding; $\gamma\sigma$ in MAP only\\
	\verb+pos-gall+ & First step Wiener; weight thresholding; $\gamma\sigma$ everywhere \\
	\verb+neg-gmap+ & First step Wiener; no weight thresholding; $\gamma\sigma$ in MAP only\\
	\verb+neg-gall+ & First step Wiener; no weight thresholding; $\gamma\sigma$ everywhere \\
\end{tabular}
\end{center}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1WIE2-vs-WIEB2F1WIE2_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1WIE2-vs-WIEB2F1WIE2_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1WIE2-vs-WIEB2F1WIE2_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1WIE2-vs-WIEB2F1WIE2_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1WIE2-vs-WIEB2F1WIE2_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1WIE2-vs-WIEB2F1WIE2_fpsnr_np2-g-curves_1np100_s40_average.eps}\\

	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-WInB2F1WIE2_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-WInB2F1WIE2_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-WInB2F1WIE2_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-WInB2F1WIE2_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-WInB2F1WIE2_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-WInB2F1WIE2_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{Noise correction factor with empirical Wiener filter. First two
		rows: \texttt{pos-gmap} (squares) vs. \texttt{pos-gall} (circles), last
		two rows: \texttt{neg-gmap} (squares) vs. \texttt{neg-gall} (circles).
		For each pair of rows, the first one shows the final PSNR for $\sigma =
		10$ and the second one for $\sigma = 40$. In each plot the PSNR is shown
		as a function of $\gamma_1$, for several values of $n_2$ (see legends).
		Each column corresponds to values of $n_1 = 10, 40, 100$. }
	\label{fig:wie1_gmap-vs-gall}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np100_s40_average.eps}\\

%	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np010_s10_average.eps}%
%	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np040_s10_average.eps}%
%	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
%	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np010_s40_average.eps}%
%	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np040_s40_average.eps}%
%	\includegraphics[width=.33\textwidth]{f/nldct/WIn1WIE2-vs-STBB2F1WIE2_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{Noise correction factor with Bayesian soft-thresholding.
		The first step corresponds to a Bayesian soft-thresholding operator, 
		using the \texttt{gmap} (squares) or \texttt{gall} (circles) schemes. 
		The second step corresponds to the Wiener filter.
		The first row shows the final PSNR for $\sigma =
		10$ and the second one for $\sigma = 40$. In each plot the PSNR is shown
		as a function of $\gamma_1$, for several values of $n_2$ (see legends).
		Each column corresponds to values of $n_1 = 10, 40, 100$. }
	\label{fig:stb1_gmap-vs-gall}
\end{figure}

The plot show that:
\begin{enumerate}
	\item Both with negative or positive weights, the peak performance is
		attained with the same set of parameters $n_1, n_2, \gamma_1$.
	\item With positive weights, \verb+pos-gall+ can achieve a slightly peak performance.
		As expected, the curves of \verb+pos-gmap+ are smoother.
	\item With negative weights, both noise correction approaches have the same
		peak performance. The curves of \verb+pos-gmap+ is smoother only for
		$\gamma \geqslant 1$, but drops abruptly when $\gamma < 1$.
\end{enumerate}

The reason for the last observation might be the following. The filter weights
for \verb+neg-gmap+ are as follows:
\[
	w_i^{\text{\texttt{neg-gmap}}} = 
	\frac{\mathbb{SV}\{\beta_{i}\} - \sigma^2}
	     {\mathbb{SV}\{\beta_{i}\} - (1-\gamma^2)\sigma^2},
	\quad\quad 
	w_i^{\text{\texttt{neg-gall}}} = 
	\frac{\mathbb{SV}\{\beta_{i}\} - \gamma^2\sigma^2}
	     {\mathbb{SV}\{\beta_{i}\}},
\]
where $\mathbb{SV}\{\beta_{i}\}$ denotes the sample variance operator.
Depending on the approach $\gamma$ appears in the denominator or the numerator. 
When it appears in the numerator, using $\gamma < 1$ can lead to instabilities when
$\mathbb{SV}\{\beta_{i}\} -\sigma^2 \approx -\gamma^2\sigma^2 > 0$.
This does not occur when the negative coefficients are thresholded since 
$\mathbb{SV}\{\beta_{i}\} -\sigma^2 \geqslant 0 > -\gamma^2\sigma^2$.

The question about the noise correction scheme also afects the Bayesian
soft-thresholding techniques. In this case, the value of the soft-threshold
depends both on the signal variance and the noise. We thus have the following
options:
\[
	\tau_i^{\text{\texttt{gmap}}} = 
	\frac{\sqrt{2}\gamma^2\sigma^2}{\sqrt{(\mathbb{SV}\{\beta_{i}\} - \sigma^2)_+}},
	\quad\quad 
	\tau_i^{\text{\texttt{gall}}} = 
	\frac{\sqrt{2}\gamma^2\sigma^2}{\sqrt{(\mathbb{SV}\{\beta_{i}\} - \gamma^2\sigma^2)_+}}.
\]
Using $\gamma$ only for the MAP computation has less impact on the threshold value.
Figure \ref{fig:stb1_gmap-vs-gall} compares the both approaches. We observe a similar
peack performance for both methods, with smoother curves for the \texttt{gmap} approach.
In both cases the threshold $\tau$ is a increasing continuous function of $\gamma$, which
means that the peak value should be the same, only with different values of
$\gamma$ in both cases.

%For the rest of the section we use the \verb+gall+ approach.
\textcolor{red}{\textbf{NOTE:} Since the \texttt{gmap} is more stable, and has almost
the same peak performance, we should adopt it. The experiments in the rest of
the report have been done using the \texttt{gall} approach. The conclusions
won't change much if we had used the \texttt{gmap} still,  
some of the experiments should be recomputed using
\texttt{gmap}.}

\clearpage
\subsubsection{Methods for the first step}
In a first set of experiments we try the different alternatives for the first
step. For the second step we use in all cases a guided Wiener filter, where the
variances and the mean are estimated from the output of the first step.
The estimation methods we consider are the following:
\begin{center}
\begin{tabular}{c l}
	\verb+WIE1-pos+ & Empirical Wiener filtering with thresholding of negative weights\\
	\verb+WIE1-neg+ & Empirical Wiener filtering without thresholding of negative weights\\
	\verb+HTH1-lin+ & Linear hard-thresholding filter\\
	\verb+STH1-bay+ & Bayesian soft-thresholding operator\\
	\verb+HTH1-ctn+ & Hard-thresholding operator (constant threshold for all coefficients)\\
	\verb+STH1-ctn+ & Soft-thresholding operator (constant threshold for all coefficients)\\
\end{tabular}
\end{center}

Figures
\ref{fig:WIE1neg-vs-WIE1pos},
\ref{fig:WIE1neg-vs-HTH1lin},
\ref{fig:HTH1lin-vs-STH1bay},
\ref{fig:STH1bay-vs-HTH1ctn} and 
\ref{fig:HTH1ctn-vs-STH1ctn} show a series of comparison between pairs of methods. The PSNR values
in the graphs correspon to the average computed over the images:
\begin{center}
\begin{tabular}{c c c c c c c c}
	\texttt{alley.png} &
	\texttt{computer.png} &
	\texttt{girl.png} &
	\texttt{traffic.png} \\
	\texttt{building1.png} &
	\texttt{dice.png} &
	\texttt{street1.png} &
	\texttt{trees.png} 
\end{tabular}
\end{center}

The results show the following conclusions:
\begin{enumerate}
	\item All methods achieve best results with $n_1 = 40$, both for $\sigma = 10$ and $40$.
	\item Almost all methods achieve best results with $n_2 = 10$, both for
		$\sigma = 10$ and $n_2 = 20$ for $\sigma = 40$.
	\item Ordering the methods by their perfomance we have that
		\begin{center}
			\texttt{WIE1-neg} $\approx$ 
			\texttt{HTH1-lin} $\gtrsim$
			\texttt{WIE1-pos} $\approx$
			\texttt{STH1-bay} $>$
			\texttt{HTH1-ctn} $>$
			\texttt{STH1-ctn}.
		\end{center}
		Thus we have four methods with a very similar performance, and two of
		them which are clearly worse, which are the ones applying a constant hard
		or soft threshold to all coefficients.
\end{enumerate}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_bpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_bpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_bpsnr_np2-g-curves_1np100_s10_average.eps}\\

	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_bpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_bpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-WIE1pos_bpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{\texttt{WIE1-pos} (squares) vs. \texttt{WIE1-neg} (circles). The first
	row shows the final PSNR for $\sigma = 10$. In each plot the PSNR is shown
	as a function of $\gamma_1$, for several values of $n_2$ (see legends). Each
	column corresponds to values of $n_1 = 10, 40, 100$. The second row shows the
	corresponding basic PSNR as a function of $\gamma$ (note that the basic PSNR does
	not depend on $n_2$). The 3rd and 4th rows show the results obtained for $\sigma = 40$.}
	\label{fig:WIE1neg-vs-WIE1pos}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_bpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_bpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_bpsnr_np2-g-curves_1np100_s10_average.eps}\\

	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_bpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_bpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIE1neg-vs-HTH1lin_bpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{\texttt{WIE1-neg} (squares) vs. \texttt{HTH1-lin} (circles). The first
	row shows the final PSNR for $\sigma = 10$. In each plot the PSNR is shown
	as a function of $\gamma_1$, for several values of $n_2$ (see legends). Each
	column corresponds to values of $n_1 = 10, 40, 100$. The second row shows the
	corresponding basic PSNR as a function of $\gamma$ (note that the basic PSNR does
	not depend on $n_2$). The 3rd and 4th rows show the results obtained for $\sigma = 40$.}
	\label{fig:WIE1neg-vs-HTH1lin}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_bpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_bpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_bpsnr_np2-g-curves_1np100_s10_average.eps}\\

	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_bpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_bpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1lin_bpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{\texttt{STH1-bay} (squares) vs. \texttt{HTH1-lin} (circles). The first
	row shows the final PSNR for $\sigma = 10$. In each plot the PSNR is shown
	as a function of $\gamma_1$, for several values of $n_2$ (see legends). Each
	column corresponds to values of $n_1 = 10, 40, 100$. The second row shows the
	corresponding basic PSNR as a function of $\gamma$ (note that the basic PSNR does
	not depend on $n_2$). The 3rd and 4th rows show the results obtained for $\sigma = 40$.}
	\label{fig:HTH1lin-vs-STH1bay}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_bpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_bpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_bpsnr_np2-g-curves_1np100_s10_average.eps}\\

	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_bpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_bpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STH1bay-vs-HTH1ctn_bpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{\texttt{STH1-bay} (squares) vs. \texttt{HTH1-ctn} (circles). The first
	row shows the final PSNR for $\sigma = 10$. In each plot the PSNR is shown
	as a function of $\gamma_1$, for several values of $n_2$ (see legends). Each
	column corresponds to values of $n_1 = 10, 40, 100$. The second row shows the
	corresponding basic PSNR as a function of $\gamma$ (note that the basic PSNR does
	not depend on $n_2$). The 3rd and 4th rows show the results obtained for $\sigma = 40$.}
	\label{fig:STH1bay-vs-HTH1ctn}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_bpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_bpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_bpsnr_np2-g-curves_1np100_s10_average.eps}\\

	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_bpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_bpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/HTH1ctn-vs-STH1ctn_bpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{\texttt{HTH1-ctn} (squares) vs. \texttt{STH1-ctn} (circles). The first
	row shows the final PSNR for $\sigma = 10$. In each plot the PSNR is shown
	as a function of $\gamma_1$, for several values of $n_2$ (see legends). Each
	column corresponds to values of $n_1 = 10, 40, 100$. The second row shows the
	corresponding basic PSNR as a function of $\gamma$ (note that the basic PSNR does
	not depend on $n_2$). The 3rd and 4th rows show the results obtained for $\sigma = 40$.}
	\label{fig:HTH1ctn-vs-STH1ctn}
\end{figure}

\clearpage
\subsubsection{Methods for the second step}
Based on the results obtained for the different first step methods, we will choose
the one among the ones with better performance, and test different estimation 
methods for the second step.
For the second step we use in all cases a guided Wiener filter, where the
variances and the mean are estimated from the output of the first step.
The estimation methods we consider are the following:
\begin{center}
\begin{tabular}{c l}
	\verb+WIn1+ & $1$st step empirical Wiener filtering with negative weights\\
	\verb+WIE2+ & $2$nd step empirical Wiener filtering with thresholding of negative weights\\
	\verb+STBi+ & $i$-th step Bayesian soft-thresholding operator\\
\end{tabular}
\end{center}

Figures 
\ref{fig:STB1STB2-vs-WIn1WIE2} and
\ref{fig:STB1WIE2-vs-WIn1WIE2}
compare the performance of different combinations resulting from using the
Bayesian soft-thresholding operator or the Wiener filter in both steps.
The results show that the Wiener filter outperforms the Laplacian prior.

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.33\textwidth]{f/nldct/STB1STB2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1STB2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1STB2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np100_s10_average.eps}\\

	\includegraphics[width=.33\textwidth]{f/nldct/STB1STB2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1STB2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1STB2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{\texttt{WIn1-WIE2} (squares) vs. \texttt{STB1-STB2} (circles). The first
	row shows the final PSNR for $\sigma = 10$. In each plot the PSNR is shown
	as a function of $\gamma_2$, for several values of $n_2$ (see legends). Each
	column corresponds to values of $n_1 = 10, 40, 100$. The second row shows the
	corresponding basic PSNR as a function of $\gamma$ (note that the basic PSNR does
	not depend on $n_2$). The 3rd and 4th rows show the results obtained for $\sigma = 40$.}
	\label{fig:STB1STB2-vs-WIn1WIE2}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np100_s10_average.eps}\\

	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/STB1WIE2-vs-WIn1WIE2_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{\texttt{WIn1-WIE2} (squares) vs. \texttt{STB1-WIE2} (circles). See
	caption of Figure \ref{fig:STB1STB2-vs-WIn1WIE2}.}
	\label{fig:STB1WIE2-vs-WIn1WIE2}
\end{figure}

\clearpage

\subsubsection{Size of the patch}

In this section we study the effect of varying the patch size between two
patch sizes, $4$ and $8$. We will consider the Wiener filter in both stages,
and run experiments both with positive and negative weights in the first step.
We vary the number of patches of each scale.
The methods are denoted by
\begin{center}
	\begin{tabular}{l l}
	\texttt{WInpWIEq}& Wiener, negative weights and patch of \texttt{p},
	                  guided Wiener with patch of $\texttt{q}$\\
	\texttt{WIEpWIEq}& Wiener, thresholded weights and patch of \texttt{p},
	                  guided Wiener with patch of $\texttt{q}$\\
\end{tabular}
\end{center}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.33\textwidth]{f/nldct/WIn8WIE8-vs-WIn8WIE4_fpsnr_1np-np2-curves_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIn8WIE8-vs-WIn8WIE4_fpsnr_1np-np2-curves_s40_average.eps}\\

	\includegraphics[width=.33\textwidth]{f/nldct/WIn4WIE4-vs-WIn8WIE4_fpsnr_1np-np2-curves_s10_average.eps}%
	\includegraphics[width=.33\textwidth]{f/nldct/WIn4WIE4-vs-WIn8WIE4_fpsnr_1np-np2-curves_s40_average.eps}\\
	\caption{Top: \texttt{WIn8WIE8} (circles) vs. \texttt{WIn8WIE4} (squares). 
	Bottom: \texttt{WIn4WIE4} (circles) vs. \texttt{WIn8WIE4} (squares). 
	From left to right, final PSNR for $\sigma = 10, 40$.
	In each plot the PSNR is shown
	as a function of $n_2$, for $n_1 = 10, 40, 100$ (see legends).}
	\label{fig:STB1STB2-vs-WIn1WIE2}
\end{figure}

\subsubsection{Comparison with BM3D}

It is interesting to compare the best PSNR attained by any of the variants above, with the 
best PSNR from BM3D.
The following table shows the PSNR, and the RMSE for \texttt{NL-DCT} and
\texttt{BM3D}.
\begin{center}
	\begin{tabular}{l | c c }
		$\sigma$ & 10 & 40 \\\hline
		\texttt{NL-DCT (WIn8WIE8)} & 36.46 - 3.83  & 29.67 - 8.38  \\
		\texttt{NL-DCT (WIn8WIE4)} & 36.71 - 3.73  & {\it 29.72 - 8.33}  \\
		\texttt{NL-DCT (WIn4WIE4)} & {\it 36.74 - 3.71}  & 29.55 - 8.50  \\
		\texttt{BM3D}              & 36.73 - 3.71  & 29.41 - 8.63  \\
\end{tabular}
\end{center}

\clearpage
\subsubsection{Filtering of the sample mean}

One of the differences between BM3D and the NL-DCT is that BM3D filters the
sample mean. In this section we will test two different strategies for
filtering the sample mean.

\paragraph{BM3D's mean filtering.}The first approach is taken from BM3D. We denote by $\lambda_{\mu}$ the 
variance associated with the sample mean. BM3D filters the mean with the
following Wiener filter:
\[
	w^{\text{BM3D}}_{\mu,i} = 
	\left(1 + \frac{\sigma^2}{\hat \lambda^{\text{BM3D}}_{\mu,1}}\right)^{-1}
\]
Thus we have, for each step
\[
	w^{\text{BM3D},1}_{\mu,i} = \max\left\{0, 1 - \frac{\sigma^2}{n(\ma u_i^T\bar{\ma q})^2}\right\},
	\quad\quad
	w^{\text{BM3D},2}_{\mu,i} = \frac{n(\ma u_i^T\bar{\ma q}_o)^2}{n(\ma u_i^T\bar{\ma q}_o)^2 + \sigma^2}.
\]
In the second step, the noisy sample mean is filtered. This implies that the
mean is not computed from the basic estimate.
Also, the filtering of the mean has to be performed at the beginning. Once the 
filtered mean has been computed, it is used to compute the MAP for the rest 
of the patches. In particular, the variances of the a priori distribution have
to be computed using the filtered mean.

\paragraph{Hyper-Bayesian mean filtering.}The problem with the first approach is that it does not follow from the
Bayesian formulation we have used so far. However, a similar effect can
be obtained by using an hyperprior on the mean: we assume that the mean
$\mu$ of the patch Gaussian model follows another a priori Gaussian
distribution $\mu\sim\mathcal N(\mu_0,C_{\mu_0})$. We assume that $\mu_0 = 0$
and that $C_{\mu_0}$ is diagonalized over the DCT basis, having variances
$\lambda_{\mu,i}$ along each direction. This approach yields a more aggressive
filtering of the mean:
\[
	w^{\text{NLH}}_{\ma\mu,i}
	= \left(1 + \frac{\sigma^2 + \hat \lambda_{\ma p,i}^{\text{NLH}}}{n\hat \lambda^{\text{NLH}}_{\ma\mu,i}}\right)^{-1},
\]
where we denoted by $\lambda_{\ma p,i}$ the variance of the a priori Gaussian of
patches to differentiate it from $\lambda_{\ma \mu,i}$.

The estimation of the parameters now is more complicated. We have a set 
of coupled equations:
\begin{align}
	\hat \lambda^{\text{NLH},1}_{\ma p,i} &= 
		\max\{0,\frac1n\sum_{j = 1}^n (\ma q_{ij} - \hat {\ma \mu}^{\text{NLH},1}_i)^2
		- \sigma^2\}
		\label{eq:nlh-varp}\\
%
	\hat \lambda^{\text{NLH},1}_{\ma\mu,i} &= 
		\max\{0, \bar{\ma q}_i^2 - n^{-1}(\hat \lambda_{\ma p,i}^{\text{NLH},1} + \sigma^2)\}
		\label{eq:nlh-varmu}\\
%
	\hat{\ma\mu}^{\text{NLH},1}_i &=
		\frac{n\hat{\lambda}_{\ma\mu,i}^{\text{NLH},1}}
		     {n\hat{\lambda}_{\ma\mu,i}^{\text{NLH},1} + 
			    \hat{\lambda}_{\ma  p,i}^{\text{NLH},1} + \sigma^2} \cdot \bar{\ma q}_i	
		\label{eq:nlh-wienermu}
\end{align}
To simplify notation, we assume that the patches coordinates are expressed in
the DCT basis.
Equation \eqref{eq:nlh-varp} estimates the variances of the patch distribution
and it depends on the mean estimate. Equation \eqref{eq:nlh-varmu} estimates the
variances of the distribution of the mean patch, and depends on the patch 
variances. To solve the set of equations we initailize $\hat{\ma\mu}^{\text{NLH},1}$ as 
the sample mean, and iterate a few times. We have empirically observed that this
fixed point scheme converges. Aguerrebere et al. CITE prove the convergence of a
similar iterative scheme.
After the iteration converges it is important to update the patch variances using
the estimated mean patch.

For the second step, the patch variances and the mean patch variances are estimated
from the basic estimate. In the estimation of the patch variances, the sample mean 
of the basic patches is used. These variances are then used to filter the
noisy average patch and the noisy patches. The noisy sample mean is filtered with 
the following filter coefficients:
\[
	w^{\text{NLH},2}_{\ma\mu,i} =
		\max\left\{0, \frac{n\bar{\ma q}_o^2 - 
		\hat \lambda_{\ma z,i}^{\text{NLH},2}}{n\bar{\ma q}_o^2 + \sigma^2}\right\}.
\]

In Figures \ref{fig:mu-filtering-bm3d} and \ref{fig:mu-filtering-hyper} we show 
the results of \texttt{WIE1-WIE2} for $\gamma = 1$, with and without mean filtering,
for the BM3D's approach and the hyper Bayesian approach.
In Figure \ref{fig:mu-filtering-bm3d} we show results obtained when filtering
the mean in the first step, and in the second step. We can see that the results
obtained by filtering the mean in the second step are decidedly worse than without
mean filtering. In the second step, with no mean filtering, the mean is
computed using the basic estimate. This seems to be better than the filtering the
mean of the noisy patches.

In the fisrt step, the filtered mean yields significantly better results when
$n_1$ is small (10, 20), specially for $\sigma = 40$. Still, even with this improvement, 
the best results are obtained by increasing $n_1$ (around $n_1 \approx 40$. For those values
of $n_1$, filtering the mean can give a better result, but the difference becomes very small.

In conclusion, it seems that the non-local patch-similarity is a stronger denoising 
mechanism than DCT shrinkage. There is no relevant gain by considering smaller groups and filtering
mean.

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1mu3WIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1mu3WIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np020_s10_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1mu3WIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np030_s10_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1mu3WIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1mu3WIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1mu3WIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1mu3WIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np020_s40_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1mu3WIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np030_s40_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1mu3WIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1mu3WIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np100_s40_average.eps}\\

	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\hspace{.4\textwidth}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\hspace{.4\textwidth}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{Filtering of the mean using BM3D's approach. First two rows: mean
		filtering in step 1, last two rows: mean filtering in step 2.  For each
		pair of rows, the first one shows the final PSNR for $\sigma = 10$ and
		the second one for $\sigma = 40$. In each plot the PSNR is shown as a
		function of $\gamma_\mu$, for several values of $n_2$ (see legends). The
		dashed black line represents the maximum PSNR attained without filtering
		the mean (restricted to $\gamma = 1$). Each column corresponds to values
		of $n_1 = 10, 20, 30, 40, 100$. }
	\label{fig:mu-filtering-bm3d}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1muHWIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np010_s10_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1muHWIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np020_s10_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1muHWIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np030_s10_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1muHWIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np040_s10_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1muHWIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1muHWIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np010_s40_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1muHWIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np020_s40_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1muHWIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np030_s40_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1muHWIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np040_s40_average.eps}%
	\includegraphics[width=.2\textwidth]{f/nldct/WIE1muHWIE2-vs-WIE1WIE2_fpsnr_np2-g-curves_1np100_s40_average.eps}\\

%	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np010_s10_average.eps}%
%	\hspace{.4\textwidth}%
%	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np040_s10_average.eps}%
%	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np100_s10_average.eps}\\
%	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np010_s40_average.eps}%
%	\hspace{.4\textwidth}%
%	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np040_s40_average.eps}%
%	\includegraphics[width=.2\textwidth]{f/nldct/WIE1WIE2mu3-vs-WIE1WIE2_fpsnr_np2-g-curves_1np100_s40_average.eps}\\
	\caption{Filtering of the mean by imposing a zero mean hyperprior in step 1.
		The first row shows the final PSNR for $\sigma = 10$ and the second one
		for $\sigma = 40$. In each plot the PSNR is shown as a function of
		$\gamma_\mu$, for several values of $n_2$ (see legends).  The dashed
		black line represents the maximum PSNR attained without filtering the
		mean (restricted to $\gamma = 1$).  Each column corresponds to values of
		$n_1 = 10, 20, 30, 40, 100$. }
	\label{fig:mu-filtering-hyper}
\end{figure}

\clearpage

\subsubsection{Windowed patches}

We study the use of windowed patches to check if they improve some artifacts
appearing in the results. We consider a window function $\kappa$ which multiplies
each patch component. Therefore, we now transform the windowed patches:
\[\ma \alpha = U^TK(\ma p - \overline{\ma p}),\]
where $K = \text{Diag}(\kappa)$ is a diagonal matrix applying the window. The noise
in the windowed patches is not white anymore. The covariance matrix in the spatial
domain is given by $\Sigma_{\kappa\ma n} = \mathbb E\{K\ma n\ma n^TK\} = \sigma^2K^2$,
where $K^2 = \text{Diag}(\kappa^2)$. On the transformed domain, the covariance matrix
of the noise is $\Sigma_{U^T\kappa\ma n} = \mathbb E\{U^TK\ma n\ma n^TKU\} = \sigma^2U^TK^2U$.

This complicates the computations, since now the \emph{a priori} covariance
matrix and the a posteriori covariance matrix have different eigenvectors.
We can assume that the eigenvectors of the \emph{a priori} covariance matrix
are given by a fixed basis $U$. The MAP is given by
\begin{align*}
\hat{\ma p}_\kappa - K\overline{\ma p} &=  
                     C_{K\ma p} (C_{K\ma p} + C_{K\ma n})^{-1} K(\ma q - \overline{\ma p}) \\
\Rightarrow 
U^T\hat{\ma p}_\kappa - U^TK\overline{\ma p}  
&= \Lambda U^T  (U\Lambda U^T + C_{K\ma n})^{-1} K(\ma q - \overline{\ma p}) \\
&= \Lambda (\Lambda + \sigma^2U^TK^2U)^{-1} U^TK(\ma q - \overline{\ma p}) \\
\end{align*}

Another difficulty is how to learn the model parameters in the first step. The MLE 
corresponds to 
\[\hat C_{K\ma p} = \mathbb{SC}\{K\ma q_i\} - C_{K\ma n}.\]
Due to the assumption that 
$\hat C_{K\ma p}$ is diagonalized over $U$, we have that 
\begin{align*}
\hat \Lambda_{K\ma p} &= U^T\mathbb{SC}\{K\ma q_i\}U - U^TC_{K\ma n}U\\
&= \mathbb{SC}\{U^TK\ma q_i\} - \sigma^2U^T\text{Diag}(K^2)U.
\end{align*}

\subsubsection{Aggregation: weighting according to fitness to Gaussian model}

We test different aggregation schemes to see if they improve the results. Based on
CITA-IRANIES, we weight each patch to reflect how well does it fit the Gaussian model.
For that aim, we use Gaussian weights based on the Mahalanobis distance:
\[w(q_i) = \exp\left(-\frac1{2\gamma_{\text{agg}}} 
\langle \ma q_i - \overline{\ma q}, C_{\ma q}^{-1}(\ma q_i - \overline{\ma q})\rangle\right). \]

To determine the effect on the PSNR, we compute the average PSNR obtained over
the 8 test images, for different values of $n_1, n_2, \gamma_{\text{agg},1}$
and $\gamma_{\text{agg},2}$.

Figure \ref{fig:patch_mahalanobis_agg} shows the results obtained by averaging the PSNR
in the 8 test sequences. The plots show that the effect of the aggregation is negligible.

\begin{figure}[ht!]
	\centering
	\includegraphics[width=.25\textwidth]{f/nldct/WIE1pos_fpsnr_np2-gagg-curves_1np010_s10_average.eps}%
	\includegraphics[width=.25\textwidth]{f/nldct/WIE1pos_fpsnr_np2-gagg-curves_1np040_s10_average.eps}%
	\includegraphics[width=.25\textwidth]{f/nldct/WIE1pos_fpsnr_np2-gagg-curves_1np100_s10_average.eps}%
	\includegraphics[width=.25\textwidth]{f/nldct/WIE1pos_fpsnr_np2-gagg-curves_1np200_s10_average.eps}\\
	\includegraphics[width=.25\textwidth]{f/nldct/WIE1pos_fpsnr_np2-gagg-curves_1np010_s40_average.eps}%
	\includegraphics[width=.25\textwidth]{f/nldct/WIE1pos_fpsnr_np2-gagg-curves_1np040_s40_average.eps}%
	\includegraphics[width=.25\textwidth]{f/nldct/WIE1pos_fpsnr_np2-gagg-curves_1np100_s40_average.eps}%
	\includegraphics[width=.25\textwidth]{f/nldct/WIE1pos_fpsnr_np2-gagg-curves_1np200_s40_average.eps}\\

	\caption{Results obtained with the Mahalanobis aggregation weights. The
		first row shows the final PSNR for $\sigma = 10$ and the second one for
		$\sigma = 40$. 
		Each column corresponds to values of $n_1 = 10, 40, 100, 200$. 
		In each plot the PSNR is
		shown as a function of $\gamma_{\text{agg},1}$, for several values of $n_2$ (see
		legends). For each value of $n_1,n_2$ we show two curves: one showing the maximum
		value obtained varying $\gamma_{\text{agg},2}$ and the other showing the minimum.
		The value at $\gamma_{\text{agg},1} = 110$ actually corresponds to
		$\gamma_{\text{agg},1} = \infty$, \textit{i.e.} flat weights.
		}
	\label{fig:patch_mahalanobis_agg}
\end{figure}

These results show that the gain in performance that can be obtained with this
weighting scheme is marginal.

\subsubsection{Aggregation: weights according to group fitness to the basis}

Since we are using a fixed basis, some groups of patches might not be well modelled
by it. There are several strategies to determine if the group is not well modelled:
\begin{enumerate}
	\item the total variance of the noisy patches \textcolor{cyan}{running tests in avocat}
	\item the total variance of the clean patches \textcolor{cyan}{not implemented yet}
	\item the total sum of the filter coefficients \textcolor{cyan}{shows a nice
		linear correlation with the error, but it seems hard to determine where
		is the line located.}
\end{enumerate}

Once we determine the right quantity, we need to find how we compute the
aggregation weights. Examples could be Gaussian decay, a logistic sigmoid function,
inverse of the measured quantity, etc. It would be nice to determine which is the 
optimal weight given that we have a quantity that is linearly correlated with the
patch error, in terms of maximizing the PSNR after aggregation.

We have conducted preliminary experiments using a logistic sigmoid function of the 
total group variance (the mean of the variances along each component) for the noisy
patches. We have found that:
\begin{itemize}
	\item high variance is located at groups containing patches of
		\begin{enumerate}
			\item textures
			\item edges
			\item unique features
		\end{enumerate}
	\item the groups with largest average patch MSE (the mean MSE for the patches in
		the group) are also located on this regions
	\item the logistic-of-variance aggregation weights improve the results only when disabling the
		\textit{paste trick}. 
	\item the improvement is less significant for larger $\sigma$.
\end{itemize}

\subsection{Results with NL-DCT and the multiscaler}

We present preliminary results using the multiscaler in conjunction with the NL-DCT algorithm.
For the multiscaler, we use two diadic scales, with a recomposition factor of $0.7$.
For the NL-DCT we consider patches of size $4\times 4$ in both stages searched in a $21\times 21$ region.
We look for $40$ patches in the first stage and for $10$, if $\sigma = 10$, or $20$,
if $\sigma= 40$, in the second. We compare results using positive and negative Wiener weights.

\begin{center}
\begin{tabular}{l | c c | c c }
								 &\multicolumn{2}{c|}{$\sigma = 10$}&\multicolumn{2}{c}{$\sigma = 40$} \\
                         & {\tt NL-DCT-neg}&{\tt MS-NL-DCT-neg} &{\tt NL-DCT-neg} &{\tt MS-NL-DCT-neg} \\\hline
		\texttt{alley    } & {    34.82} & {    34.83}    & {    27.71} & {\bf 27.87}    \\
		\texttt{building1} & {\bf 35.65} & {    35.58}    & {    28.30} & {\bf 28.40}    \\
		\texttt{computer } & {\bf 36.36} & {    36.20}    & {\bf 28.91} & {    28.88}    \\
		\texttt{dice     } & {    43.02} & {\bf 43.08}    & {    36.42} & {\bf 36.67}    \\
		\texttt{girl     } & {    41.40} & {\bf 41.46}    & {    35.51} & {\bf 35.86}    \\
		\texttt{street1  } & {\bf 36.12} & {    36.06}    & {    29.07} & {\bf 29.15}    \\
		\texttt{traffic  } & {\bf 34.79} & {    34.68}    & {    27.33} & {    27.36}    \\
		\texttt{trees    } & {    31.44} & {    31.41}    & {    23.21} & {    23.25}    \\\hline
		Average            & {    36.70} & {    36.66}    & {    29.56} & {\bf 29.68}    \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{l | c c | c c }
								 &\multicolumn{2}{c|}{$\sigma = 10$}&\multicolumn{2}{c}{$\sigma = 40$} \\
                         & {\tt NL-DCT-pos}&{\tt MS-NL-DCT-pos} &{\tt NL-DCT-pos} &{\tt MS-NL-DCT-pos} \\\hline
		\texttt{alley    } & {    34.84} & {    34.83}    & {    27.82} & {\bf 27.92}    \\
		\texttt{building1} & {\bf 35.66} & {    35.58}    & {    28.30} & {\bf 28.37}    \\
		\texttt{computer } & {\bf 36.37} & {    36.19}    & {\bf 28.89} & {    28.81}    \\
		\texttt{dice     } & {    43.07} & {\bf 43.12}    & {    35.39} & {\bf 35.58}    \\
		\texttt{girl     } & {    41.49} & {    41.51}    & {    34.75} & {\bf 35.03}    \\
		\texttt{street1  } & {\bf 36.14} & {    36.07}    & {    29.06} & {\bf 29.10}    \\
		\texttt{traffic  } & {\bf 34.79} & {    34.68}    & {    27.39} & {    27.38}    \\
		\texttt{trees    } & {    31.44} & {    31.41}    & {    23.25} & {    23.28}    \\\hline
		Average            & {\bf 36.72} & {    36.67}    & {    29.36} & {\bf 29.43}    \\
\end{tabular}
\end{center}

\bibliographystyle{siam}
\bibliography{image_denoising, video_denoising}

\end{document}

### 2016-07-21 doc/201602_ms-nl-dct/test.m

@@ -1,0 +1,68 @@
+% generate laplace distributed values
+for sg = 2.^[0:.5:8],
+
+n = 40;
+mu = 10;
+%sg = 5;
+sg_noise = 10;
+
+sg
+
+
+a_mle_mu    = zeros(5000,1);
+a_mle_sg    = zeros(5000,1);
+a_mean_mu   = zeros(5000,1);
+a_mean_sg   = zeros(5000,1);
+b_mean_mu   = zeros(5000,1);
+b_mean_sg   = zeros(5000,1);
+b_median_mu = zeros(5000,1);
+b_median_sg = zeros(5000,1);
+for xx = 1:5000;
+	alpha = laprnd(n,1,mu,sg);
+	beta  = alpha + sg_noise * randn(n,1);
+
+
+	% MLE estimators from clean data
+	a_mle_mu(xx) = median(alpha);
+	a_mle_sg(xx) = sqrt(2)*mean(abs(alpha - a_mle_mu(xx)));
+
+	% mean and variance from clean data
+	a_mean_mu(xx) = mean(alpha);
+	a_mean_sg(xx) = sqrt(mean((alpha - a_mean_mu(xx)).^2));
+
+	% estimators from noisy data
+	b_mean_mu(xx) = mean(beta);
+	b_mean_sg(xx) = sqrt(mean((beta - b_mean_mu(xx)).^2) - sg_noise*sg_noise);
+
+	b_median_mu(xx) = median(beta);
+	b_median_sg(xx) = sqrt(mean((beta - b_median_mu(xx)).^2) - sg_noise*sg_noise);
+
+	% this is not actually an mle estimator, but we called mle by analogy
+	% with the mle estimator from alpha
+	b_mle_mu(xx) = median(beta);
+	b_mle_sg(xx) = sqrt(2*mean(abs(beta - b_mle_mu(xx)))^2 - sg_noise*sg_noise);
+end
+
+
+
+%figure(1), clf, hold on
+%plot(sort(abs(mu - a_mle_mu)),'k')
+%plot(sort(abs(mu - a_mean_mu)),'r')
+%plot(sort(abs(mu - b_median_mu)),'k--')
+%plot(sort(abs(mu - b_mean_mu)),'r--')
+%hold off
+%axis([0 5000 0 50])
+%
+figure(2), clf, hold on
+plot(sort(abs(sg - a_mle_sg)),'k')
[…]
